### 2019-05-05 Math/paper.tex
Adding math and stuff.

\documentclass[12pt]{article}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{mathtools}

\title{Multimatrices and Their Derivatives}
\author{Ernest Kirstein}
\date{\today}

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\newtheorem{theorem}{Theorem}[section]

\newtheoremstyle{case}{}{}{}{}{}{:}{ }{}
\theoremstyle{case}
\newtheorem{case}{Case}

\DeclareMathOperator{\Dim}{Dim}
%\newcommand{\mmult}[1]{\stackrel{\times}{#1}}
%\newcommand{\mmult}[1]{\underset{#1}{\times}}
\newcommand{\mmult}[1]{\text{\raisebox{1ex}{$\underset{#1}{\times}$}}}

\begin{document}

\maketitle

\begin{abstract}
I was working my way through the implementation of a machine learning system as
a hobby project and I was having a hell of a time wrapping my head around the
existing notation for derivatives of matrix equations. Every notation system
either requires users to pull apart the matricies they're working with or otherwise
bypass the issue of taking derivatives of matrix equations.

So, I came up with a system of my own. And, much to my surprise, some of the
results I came up with were surprisingly elegant. For example, I proved a
multidimensional version of the derivative chain rule (Thm. \ref{mmm_chain_rule})
that's more consise than anything I've found in other works.

This book is about my exploration into multidimensional matricies - multimatricies -
and how they can simplify derivatives of matrix equations.
\end{abstract}

\section{Defining the Derivative}

Let's consider a traditional matrix equation.
We'll define some matricies $M$ and $X$ such that
$|M| = |X| = \left< 3,5 \right>$
and \[M_{r,c} = \sin(X_{r,c})\]
Or more simply, \[M = \sin(X)\]

\noindent
The partial derivatives of this equation are simple enough. Assuming that all elements
of $X$ are independent,
\[
\frac{\partial M_{r_1,c_1}}{\partial X_{r_2,c_2}} = 
\left\{
	\begin{array}{ll}
		\cos(X_{r_2,c_2})  & \mbox{if } r_1 = r_2 \mbox{ and } c_1 = c_2 \\
		0 & \mbox{otherwise}
	\end{array}
\right.
\]
Which can also be writen more simply using Kronecker deltas,
\[
\frac{\partial M_{r_1,c_1}}{\partial X_{r_2,c_2}} = 
\cos (X_{r_2, c_2}) \delta_{r_1 r_2} \delta_{c_1 c_2}
\]

\noindent
But what about the complete deriative? What would that even mean? What sort of
mathmatical object would represent the entire derivative of $M$ with respect to $X$.

\[\frac{dM}{dX} = \mbox{ ? }\]

If this were a function that mapped a vector to a scalar, you might say that the
complete derivate was the gradient. But in this case, our function's output is more
than a simple scalar and even our dependent variable is more complex than a vector.

By looking at the partial derivatives, we can come to some understanding of the
dimensionality of the complete derivative. Each combination of input and output
element has its own partial derivative, so it makes sense that the total size
of the complete derivative should be the product of the size of $M$ and the size
of $X$.

And so, the size of the complete derivate would be,
\[
\mbox{size}\left(\frac{dM}{dX}\right) = \mbox{size}(M) \mbox{size}(X)
\]
And perhaps we could even let this help us define the 'shape' of the complete
derivative. This complete derivative would need to be composed of partial
derivatives, so it would make sense to just smush the shapes of the input
matrix and the output matrix together,
\begin{align*}
\left|\frac{dM}{dX}\right| &= |M| \oplus |X| \\
 &= \left< 3, 5 \right> \oplus \left< 3, 5 \right> \\
 &= \left< 3, 5, 3, 5 \right>
\end{align*}
Where $\oplus$ is the concatenate operator.

The ordering here is arbitrary, there is no reason why the dimensionality of
of the independent variable \textit{needs} to be concatenated with to the right of the
dimensionality of the output. What's important is that the dimensionality of
both output and indepenedent variable are preserved - but let us declare this to
be our convention for the remainder of this article.

We have, therefore, a multidimensional object with four indicies. Suppose we try to
pull a single partial derivative from this complete derivative, what could our
notation look like? Four underscript indicies would be unwieldy, so maybe something
like this:
\[
\frac{dM}{dX}[1,2,3,4] = \frac{\partial M_{1,2}}{\partial X_{3,4}}
\]

And since we're defining our own notation, let's go ahead and define our original
matricies in a similar manner:
\[
\frac{dM}{dX}[1,2,3,4] = \frac{\partial M[1,2]}{\partial X[3,4]}
\]

So what is this object we've defined? In all ways that matter, it seams to be
a multidimensional matrix. It has four dimensions of indices, rather than just
a row and column, but each uniquely indexed cell in this object may have a
unique value, just like a standard two dimensional matrix.

\begin{definition}[Multimatrix]
Let's define a bit of notation. A multimatrix $M$ is a multidimensional matrix
that has some shape, $|M| \in \mathbb{N}^n$, where $n$ is the number of
dimensions of $M$.

We'll say that if $\vec{v} = |M|$, then any $\bar{v} \in \mathbb{N}^n$ is a valid
index of $M$ if and only if value of $\bar{v}$ is less than or equal to the value
of it's parallel index in $\vec{v}$. That is, $\forall i: 1 \le \bar{v}_i \le \vec{v}_i$.

We can further simplify that notation for our set of valid indicies. Let's say we have
some $\vec{v} \in \mathbb{N}^n$ that defines the shape of some matrix. Then well
define the set of valid indicies of that matrix to be $\Dim(\vec{v})$.

Each value of $M$ is a real value, so we'll define the set of all real valued
multidimensional matricies with shape $\vec{v}$ as $\mathbb{R}^{\vec{v}}$.

We'll use the notation $M[\bar{v}]$ to reference any individual scalar value of $M$
at indicies $\bar{v} \in \Dim(|M|)$. 
\end{definition}

Going back to our original motivating problem, we can express our derivative
notation thusly,

\begin{definition}[Multimatrix on Multimatrix Derivative]
\label{mm_derivative}
Let $F(X)$ be some function from $\mathbb{R}^{\vec{x}}$ to $\mathbb{R}^{\vec{f}}$.
The complete derivative of $F$ with respect to $X$ is therefore in
$\mathbb{R}^{\vec{f} \oplus \vec{x}}$. That is,
\[ |F(X)| = \vec{f} \]
\[ |X| = \vec{x} \]
\[ \left|\frac{dF}{dX}\right| = \vec{f} \oplus \vec{x} \]
\[
\forall \bar{f} \in \Dim(\vec{f}),
        \bar{x} \in \Dim(\vec{x}):
\]
\[
\frac{dF}{dX}[\bar{f} \oplus \bar{x}] =
\frac{\partial F[\bar{f}]}{\partial X[\bar{x}]}
\]
\end{definition}

But, of course, there are other combinations of functions than from one
multimatrix to another. You might have a function from a multimatrix to a
scalar (such as summing up all the values of a multimatrix), or from a scalar
to a multimatrix (such as filling a multimatrix with a single scalar value).

We can define the total derivative for those cases as well.

\begin{definition}[Scalar on Multimatrix Derivative]
\label{sm_derivative}
Let $f(X)$ be some function from $\mathbb{R}^{\vec{x}}$ to $\mathbb{R}$.
The complete derivative of $f$ with respect to $X$ is therefore in
$\mathbb{R}^{\vec{x}}$. That is,
\begin{align*}
f(X) &\in \mathbb{R} \\
|X| &= \vec{x} \\
\left|\frac{df}{dX}\right| &= \vec{x}
\end{align*}
\[
\forall \bar{x} \in \Dim(\vec{x}):
        \frac{df}{dX}[\bar{x}] =
        \frac{\partial f}{\partial X[\bar{x}]}
\]
\end{definition}

\begin{definition}[Multimatrix on Scalar Derivative]
\label{ms_derivative}
Let $F(x)$ be some function from $\mathbb{R}$ to $\mathbb{R}^{\vec{f}}$.
The complete derivative of $F$ with respect to $X$ is therefore in
$\mathbb{R}^{\vec{f}}$. That is,
\begin{align*}
|F(x)| &= \vec{f} \\
x &\in \mathbb{R} \\
\left|\frac{dF}{dx}\right| &= \vec{f}
\end{align*}
\[
\forall \bar{f} \in \Dim(\vec{f}):
        \frac{dF}{dx}[\bar{f}] =
        \frac{\partial F[\bar{f}]}{\partial x}
\]
\end{definition}

Ok, that's neat and all but what does that actually mean? Can we answer our motivating 
question?
\[\frac{dM}{dX} = ? \]
Well... sort of. We can say that the total derivative of $M$ with respect to $X$ is
a matrix with shape $|M| \oplus |X|$, who's elements we can define as,
\[\forall \bar{m} \in \Dim(|M|), \bar{x} \in \Dim(|X|):\]
\begin{align*}
\left( \frac{dM}{dX} \right)[\bar{m} \oplus \bar{x}]
&= \frac{\partial M[\bar{m}]}{\partial X[\bar{x}]} \\
&= \delta_{\bar{m}\bar{x}}\cos(\bar{x})
\end{align*}

Which isn't a huge improvement over our original notation. What would be great is
if we could define the total derivative without going down into the partial derivatives
at all, which we'll be able to do in later sections. As a sneak peak, that'll look
like this:
\[
\frac{dM}{dX} = I^3(|X|) \mmult{||X||} \cos(X)
\]

But that single line will require defining something I'm going to call a cubic
identity, $I^3(|X|)$, as well as multimatrix multiplication.

\subsection*{Sample Problems}
TODO

\section{Multimatrix Multiplication}

Multiplication of traditional matricies is one of those things that, when you
first learn about it, you wonder "Who the hell defined it this way?" And then
when you see it used in practice, you slowly come to understand they why behind
it.

Just to review, for two matricies $A$ and $B$, multipication is only defined
for $A \times B = C$ if $A$ has the same number of columns as $B$ has rows.
That is, if $|A| = \left< r_a, c_a \right>$ and $|B| = \left< r_b, c_b \right>$
then $A \times B$ is valid if and only if $c_a = r_b$. And furthermore,
the remaining dimensions of $A$ and $B$ define the diminsions of $C$,
$|C| = \left< r_a, c_b \right>$. Each element of $C$ is a sum of the product of
every combination of the corresponding row of $A$ and the corresponding column of
$B$,

\[ C[r_a, c_b] = \sum_{\forall i} A[r_a, i] B[i, c_b] \]

So now consider how we would multiply two matricies $A$ and $B$ if they had more
than two dimensions. Let's use a concrete example to make the problems more apparent.
Let $|A| = \left<5,7,7\right>$ and $|B| = \left<7,7,2,4\right>$.
First of all, can we even multiply the two together? Hm... maybe? $|A|$ ends with
$\left<\ldots, 7\right>$ and $|B|$ starts with $\left<7,\ldots\right>$ so it would
make sense that we can somehow squish them together into something. By that reasoning,
the shape of our after-multiplication output would use the remaining dimensions
$\left<5, 7, 7, 2, 4\right> = |A \times B|$.

But $|A|$ also ends with $\left<\ldots, 7, 7\right>$ and $|B|$ starts with
$\left<7, 7\ldots\right>$ so maybe our multiplication operation should work on that
additional dimension, leaving us with $\left<5, 2, 4\right> = |A \times B|$.
But the first definition looks like it could still be useful! It could let us cover 
two dimensional matrix multiplication completely within our definition. This second
definition seems more... multidimensional but it also seems to arbitrarily depend
on the shape of the two matricies.

So - a compromize. Maybe multimatrix isn't a binary operation. Maybe it's a trinary
operation. There's some component of, ``How many dimensions are you combining?'' inherent
in the operation. So we can distinguish our two types of multiplication, and indeed
an infinite number of types of multiplication, with a new operator, $\mmult{n}$ where
$|A \mmult{1} B| = \left<5, 7, 7, 2, 4\right>$ and 
$|A \mmult{2} B| = \left<5, 2, 4\right>$.

But the shape is only a small component of the multipliation  operation. Let's
just jump into the formal definition and I'll explain with an example:

\begin{definition}[Multimatrix Multiplication]
\label{mm_mult}
Let $A$ and $B$ be multimatricies such that $|A| = \vec{a} \oplus \vec{c}$,
$|B| = \vec{c} \oplus \vec{b}$, and $|\vec{c}| = n$.
Then $|A \mmult{n} B| = \vec{a} \oplus \vec{b}$ and
\[
\forall \bar{a} \in \Dim(\vec{a}), \bar{b} \in \Dim(\vec{b}):
(A \mmult{n}  B)[\bar{a} \oplus \bar{b}] =
\sum_{\forall \bar{c} \in \Dim(\vec{c})}
  A[\bar{a} \oplus \bar{c}] B[\bar{c} \oplus \bar{b}]
\]
\end{definition}

Like two dimensional matrix multiplication, multimatrix multiplication is
\textit{not} communicative. And it is only weakly associative. That sounds like
nonsense, but here's what I mean:

\begin{theorem}[Associativity of Multimatrix Multiplication]
\label{mm_associativity}
Let $A$, $B$, and $C$ be multimatricies and $n$ and $m$ in
$\left\{ 0 \right\} \cup \mathbb{Z}^{+}$.
If both operations $(A \mmult{n} B) \mmult{m} C$ and $A \mmult{n} (B \mmult{m} C)$
are valid dimensionally, then
\[ (A \mmult{n} B) \mmult{m} C = A \mmult{n} (B \mmult{m} C) \]
\end{theorem}
\begin{proof}
Let $A$, $B$, and $C$ be matricies such that the calculations
$(A \mmult{n} B) \mmult{m} C$ and $A \mmult{n} (B \mmult{m} C)$ are both valid.
Then the following vectors must be true by the definiton of multimatrix
multiplication (Thm. \ref{mm_mult}).

\noindent
Since $A \mmult{n} B$ is defined,
\[
  \exists \vec{a}, \vec{n}, \vec{b_1} :
  |\vec{n}| = n \land |A| = \vec{a} \oplus \vec{n} \land |B| = \vec{n} \oplus \vec{b_1} 
\]
Since $B \mmult{m} C$ is defined,
\[
  \exists \vec{b_2}, \vec{m}, \vec{c} :
  |\vec{m}| = m \land |B| = \vec{b_2} \oplus \vec{m} \land |C| = \vec{m} \oplus \vec{c}
\]
Since $(A \mmult{n} B) \mmult{m} C$ is defined, $|\vec{m}| = m$, and $\vec{m}$ is
already established as the left $m$ length portion of $|C|$,
\[ \exists \vec{l} : |A \mmult{n} B| = \vec{l} \oplus \vec{m} \]
Since $A \mmult{n} (B \mmult{m} C)$ is defined, $|\vec{n}| = n$, and $\vec{n}$ is
already established as the right $n$ length portion of $|A|$,
\[ \exists \vec{r} : |B \mmult{m} C| = \vec{n} \oplus \vec{r} \]
We can see that,
\begin{align*}
  |B| &= \vec{n} \oplus \vec{b_1} \\
      &= \vec{b_2} \oplus \vec{m}
\end{align*}
\[ \therefore \vec{n} \oplus \vec{b_1} = \vec{b_2} \oplus \vec{m} \]
So we end up with two cases. Either $\vec{n}$ and $\vec{m}$ overlap in $|B|$, or
they don't.
\begin{case}
$\vec{n}$ and $\vec{m}$ overlap. So we can suppose the existence of
three vectors, $\vec{n_l}$, $\vec{x}$, and $\vec{m_r}$ such that $\vec{x}$
represents the overlapping portion of $\vec{n}$ and $\vec{m}$, so
\[ |B| =  \vec{n_l} \oplus \vec{x} \oplus \vec{m_r} \]
\[ \vec{n} = \vec{n_l} \oplus \vec{x} \]
And,
\[ \vec{m} = \vec{x} \oplus \vec{m_r} \]

Since $|A| = \vec{a} \oplus \vec{n}$ and $|C| = \vec{m} \oplus \vec{c}$,
by the definition of multimatrix multiplication,
\[ |A \mmult{n} B| = \vec{a} \oplus \vec{m_r} \]
And,
\[ |B \mmult{m} C| = \vec{n_l} \oplus \vec{c} \]
But because we've presupposed that $(A \mmult{n} B) \mmult{m} C$ is a valid operation,
we know that the rightmost porton of $|A \mmult{n} B|$ must be $\vec{m}$, so
$\vec{a}$ must be divisible into some vector $\vec{a_l}$ and $\vec{x}$ so that
\[ |A \mmult{n} B| = \vec{a_l} \oplus \vec{x} \oplus \vec{m_r} \]
\[ \vec{a} = \vec{a_l} \oplus \vec{x} \]
By the same reasoning, since $A \mmult{m} (B \mmult{m} C)$ is a valid operation,
there must exist some $\vec{c_r}$ such that
\[ |B \mmult{m} C| = \vec{n_l} \oplus \vec{x} \oplus \vec{c_r} \]
and
\[ \vec{c} = \vec{x} \oplus \vec{c_r} \]

Subsituting in those derived values, we'll see that the expanded version of
our multimatrix shapes become,
\[ |A| = \vec{a_l} \oplus \vec{x} \oplus \vec{n_l} \oplus \vec{x} \]
\[ |B| = \vec{n_l} \oplus \vec{x} \oplus \vec{m_r} \]
\[ |C| = \vec{x} \oplus \vec{m_r} \oplus \vec{x} \oplus \vec{c_r} \]

It's then clear that the shapes of both associations are equal,
\[ |(A \mmult{m} B) \mmult{n} C| = \vec{a_l} \oplus \vec{x} \oplus \vec{c_r} \]
\[ |A \mmult{m} (B \mmult{n} C)| = \vec{a_l} \oplus \vec{x} \oplus \vec{c_r} \]
Which is a necessary, but not sufficient condition for our proof that
$(A \mmult{m} B) \mmult{n} C = A \mmult{m} (B \mmult{n} C)$. We now need to prove
that each of the elements of each resulting multimatrix are the same.

\end{case}

\[
  \vec{b_2} \oplus \vec{c} = \vec{n} \oplus \vec{r}
\]
\[
  \vec{l} \oplus \vec{c} = \vec{a} \oplus \vec{r}
\]
\[
  ((A \mmult{n} B) \mmult{m} C)[\bar{l} \oplus \bar{c}] =
	\sum_{\forall \bar{m}} (A \mmult{n} B)[\bar{l} \oplus \bar{m}]C[\bar{m} \oplus \bar{c}]
\]

\end{proof}

\begin{theorem}[M.M.M. Chain Rule]
\label{mmm_chain_rule}
Let $F(G)$ be a function $\mathbb{R}^{\vec{g}} \rightarrow \mathbb{R}^{\vec{f}}$
and $G(X)$ be a function $\mathbb{R}^{\vec{x}} \rightarrow \mathbb{R}^{\vec{g}}$.
\[
\frac{dF(G(X))}{dX} = \frac{dF}{dG} \mmult{|\vec{g}|} \frac{dG}{dX}
\]
\end{theorem}
\begin{proof}
By the definition of a derivative (\ref{mm_derivative}),
\[
\forall \bar{f} \in \Dim(\vec{f}), \bar{g} \in \Dim(\vec{g}):
\frac{dF(G)}{dG}[\bar{f} \oplus \bar{g}]
= \frac{\partial F(G)[\bar{f}]}{\partial G[\bar{g}]}
\]
\[
\forall \bar{g} \in \Dim(\vec{g}), \bar{x} \in \Dim(\vec{x}):
\frac{dG(X)}{dX}[\bar{g} \oplus \bar{x}]
= \frac{\partial G(X)[\bar{g}]}{\partial X[\bar{x}]}
\]
By the scalar total derivative rule,
\[
\frac{\partial F(G(X))[\bar{f}]}{\partial X[\bar{x}]}
= \sum_{\forall \bar{g} \in \Dim(\vec{g})} 
\frac{\partial F(G)[\bar{f}]}{\partial G[\bar{g}]}
\frac{\partial G(X)[\bar{g}]}{\partial X[\bar{x}]}
\]
Substituting in our above definitions this yields,
\[
\frac{\partial F(G(X))[\bar{f}]}{\partial X[\bar{x}]}
= \sum_{\forall \bar{g} \in \Dim(\vec{g})} 
\frac{dF(G)}{dG}[\bar{f} \oplus \bar{g}]
\frac{dG(X)}{dX}[\bar{g} \oplus \bar{x}]
\]
And again, by the definition of a derivative (\ref{mm_derivative}),
\[
\forall \bar{f} \in \Dim(\vec{f}), \bar{x} \in \Dim(\vec{x}):
\frac{dF(G(X))}{dX}[\bar{f} \oplus \bar{x}]
= \frac{\partial F(G(X))[\bar{f}]}{\partial X[\bar{x}]}
\]
Therefore,
\[
\frac{dF(G(X))}{dX}[\bar{f} \oplus \bar{x}]
= \sum_{\forall \bar{g} \in \Dim(\vec{g})} 
\frac{dF(G)}{dG}[\bar{f} \oplus \bar{g}]
\frac{dG(X)}{dX}[\bar{g} \oplus \bar{x}]
\]
Which, taking a look at the definition of multidimensional matrix multiplication
(\ref{mm_mult}), tells us that,
\[
\frac{dF(G(X))}{dX} = \frac{dF}{dG} \mmult{|\vec{g}|} \frac{dG}{dX}
\]
\end{proof}

\begin{theorem}[S.M.M. Chain Rule]
\label{smm_chain_rule}
Let $f(G)$ be a function $\mathbb{R}^{\vec{g}} \rightarrow \mathbb{R}$
and $G(X)$ be a function $\mathbb{R}^{\vec{x}} \rightarrow \mathbb{R}^{\vec{g}}$.
\[
\frac{df(G(X))}{dX} = \frac{df}{dG} \mmult{|\vec{g}|} \frac{dG}{dX}
\]
\end{theorem}
\begin{proof}
By the definitions of a derivative
(\ref{sm_derivative} and \ref{mm_derivative} respectively),
\[
\forall \bar{g} \in \Dim(\vec{g}):
\frac{df(G)}{dG}[\bar{g}]
= \frac{\partial f(G)}{\partial G[\bar{g}]}
\]
\[
\forall \bar{g} \in \Dim(\vec{g}), \bar{x} \in \Dim(\vec{x}):
\frac{dG(X)}{dX}[\bar{g} \oplus \bar{x}]
= \frac{\partial G(X)[\bar{g}]}{\partial X[\bar{x}]}
\]
By the scalar total derivative rule,
\[
\frac{\partial f(G(X))}{\partial X[\bar{x}]}
= \sum_{\forall \bar{g} \in \Dim(\vec{g})} 
\frac{\partial f(G)}{\partial G[\bar{g}]}
\frac{\partial G(X)[\bar{g}]}{\partial X[\bar{x}]}
\]
Substituting in our above definitions this yields,
\[
\frac{\partial f(G(X))}{\partial X[\bar{x}]}
= \sum_{\forall \bar{g} \in \Dim(\vec{g})} 
\frac{df(G)}{dG}[\bar{g}]
\frac{dG(X)}{dX}[\bar{g} \oplus \bar{x}]
\]
Again, by the definition of a derivative (\ref{sm_derivative}),
\[
\frac{df(G(X))}{dX}[\bar{x}] =
\frac{\partial f(G(X))}{\partial X[\bar{x}]}
\]
Therefore,
\[
\frac{df(G(X))}{dX}[\bar{x}]
= \sum_{\forall \bar{g} \in \Dim(\vec{g})} 
\frac{df(G)}{dG}[\bar{g}]
\frac{dG(X)}{dX}[\bar{g} \oplus \bar{x}]
\]
Which, by the definition of multidimensional multipliction (\ref{mm_mult}),
implies that,
\[
\frac{df(G(X))}{dX} = \frac{df(G)}{dG} \mmult{|\vec{g}|} \frac{dG(X)}{dX}
\]
\end{proof}

\begin{theorem}[M.S.M. Chain Rule]
\label{msm_chain_rule}
Let $F(g)$ be a function $\mathbb{R} \rightarrow \mathbb{R}^{\vec{f}}$
and $g(X)$ be a function $\mathbb{R}^{\vec{x}} \rightarrow \mathbb{R}$.
\[
\frac{dF(g(X))}{dX} = \frac{dF}{dg} \mmult{0} \frac{dg}{dX}
\]
\end{theorem}
\begin{proof}
TODO
\end{proof}

\begin{theorem}[M.M.S. Chain Rule]
\label{mms_chain_rule}
Let $F(G)$ be a function $\mathbb{R}^{\vec{g}} \rightarrow \mathbb{R}^{\vec{f}}$
and $G(x)$ be a function $\mathbb{R} \rightarrow \mathbb{R}^{\vec{g}}$.
\[
\frac{dF(G(x))}{dx} = \frac{dF}{dG} \mmult{|\vec{g}|} \frac{dG}{dx}
\]
\end{theorem}
\begin{proof}
TODO
\end{proof}

\begin{theorem}[S.S.M. Chain Rule]
\label{ssm_chain_rule}
Let $f(g)$ be a function $\mathbb{R} \rightarrow \mathbb{R}$
and $g(X)$ be a function $\mathbb{R}^{\vec{x}} \rightarrow \mathbb{R}$.
\[
\frac{df(g(X))}{dX} = \frac{df}{dg} \frac{dg}{dX}
\]
\end{theorem}
\begin{proof}
TODO
\end{proof}

\begin{theorem}[S.M.S. Chain Rule]
\label{sms_chain_rule}
Let $f(G)$ be a function $\mathbb{R}^{\vec{g}} \rightarrow \mathbb{R}$
and $G(x)$ be a function $\mathbb{R} \rightarrow \mathbb{R}^{\vec{g}}$.
\[
\frac{df(G(X))}{dx} = \frac{df}{dG} \mmult{|\vec{g}|} \frac{dG}{dx}
\]
\end{theorem}
\begin{proof}
TODO
\end{proof}

\begin{theorem}[M.S.S. Chain Rule]
\label{mss_chain_rule}
Let $F(g)$ be a function $\mathbb{R} \rightarrow \mathbb{R}^{\vec{f}}$
and $g(x)$ be a function $\mathbb{R} \rightarrow \mathbb{R}$.
\[
\frac{dF(g(x))}{dx} = \frac{dF}{dg} \frac{dg}{dx}
\]
\end{theorem}
\begin{proof}
TODO
\end{proof}

\end{document}

### 2019-05-05 LetterClassifier/genetic.cc

@@ -2,24 +2,26 @@
 #include <fstream>
 #include <iostream>
 #include <random>
+#include <sstream>
 #include <string>
 #include <vector>
 
 using std::string;
 using std::vector;
 
-namespace smiley {
+namespace genetic {
 
 constexpr int kWidth = 20;
 constexpr int kHeight = 20;
+constexpr int kNumLetters = 26;
 
 struct Sample {
   vector<float> data;
-  bool isSmiley;
+  char letter;
 };
 
-void ParseSample(const string& line, bool isSmiley, Sample* out) {
-  out->isSmiley = isSmiley;
+void ParseSample(const string& line, char letter, Sample* out) {
+  out->letter = letter;
   for (const auto& c : line) {
     if (c == '0') {
       out->data.push_back(0);
@@ -37,11 +39,7 @@ void ParseSample(const string& line, bool isSmiley, Sample* out) {
 }
 
 std::ostream& operator<<(std::ostream& o, const Sample& s) {
-  if (s.isSmiley) {
-    o << "=)";
-  } else {
-    o << "=(";
-  }
+  o << "Letter: " << s.letter;
   for (int y = 0; y < kHeight; y++) {
     o << std::endl;
     for (int x = 0; x < kWidth; x++) {
@@ -51,7 +49,7 @@ std::ostream& operator<<(std::ostream& o, const Sample& s) {
   return o;
 }
 
-void ReadSamples(const string& file, bool areSmiles, vector<Sample>* out) {
+void ReadSamples(const string& file, char letter, vector<Sample>* out) {
   string line;
   std::ifstream in(file);
   if (!in.is_open()) {
@@ -60,13 +58,13 @@ void ReadSamples(const string& file, bool areSmiles, vector<Sample>* out) {
   }
   while (std::getline(in, line)) {
     Sample sample;
-    ParseSample(line, areSmiles, &sample);
+    ParseSample(line, letter, &sample);
     out->push_back(std::move(sample));
   }
 }
 
 struct ModelState {
-  float weights[kWidth*kHeight];
+  float weights[kWidth*kHeight*kNumLetters];
 };
 
 // Get the initial weights, each as an independent normal variable.
@@ -76,63 +74,47 @@ ModelState InitModel() {
   std::normal_distribution<float> randNorm(0, 1);
   
   ModelState state;
-  for (int i = 0; i < kWidth*kHeight; i++) {
+  for (int i = 0; i < kWidth*kHeight*kNumLetters; i++) {
     state.weights[i] = randNorm(gen);
[…]

### 2019-05-05 LetterClassifier/mmatrix.cc

@@ -1,0 +1,105 @@
+#include "mmatrix.h"
+
+#include <stdexcept>
+
+namespace mmatrix {
+
+using std::string;
+using std::vector;
+
+bool Type::implies(const string& other_class_name) const {
+  return other_class_name == class_name_;
+}
+
+const Type MMatrixInterface::type_ = Type("::mmatrix::MMatrixInterface");
+const Type* MMatrixInterface::type() const {
+  return &type_;
+}
+
+DenseMMatrix::DenseMMatrix(const vector<int>& shape) : shape_(shape) {
+  int total_size = 1;
+  for (int i = 0; i < shape.size(); i++) {
+    total_size *= shape[i];
+  }
+  values_ = vector<float>(total_size, 0);
+}
+float DenseMMatrix::get(const vector<int>& indices) const {
+  return values_[ToValueIndex(shape_, indices)];
+}
+void DenseMMatrix::set(const vector<int>& indices, float value) {
+  values_[ToValueIndex(shape_, indices)] = value;
+}
+const vector<int>& DenseMMatrix::shape() const {
+  return shape_;
+}
+
+int ToValueIndex(const vector<int>& shape, const vector<int>& indices) {
+  int vindex = 0;
+  int multiplier = 1;
+  for (int i = 0; i < shape.size(); i++) {
+    if (indices[i] < 0 || indices[i] >= shape[i]) {
+      throw std::out_of_range("ToValueIndex out of range.");
+    }
+    vindex += indices[i] * multiplier;
+    multiplier *= shape[i];
+  }
+  return vindex;
+}
+void FromValueIndex(const vector<int>& shape, int vindex, vector<int>* indices) {
+  for (int i = 0; i < shape.size(); i++) {
+    (*indices)[i] = vindex % shape[i];
+    vindex = vindex/shape[i];
+  }
+}
+
+void Multiply(int n, const MMatrixInterface* a, const MMatrixInterface* b,
+    MMatrixInterface* out) {
+  // ||a|| = l + n
+  // ||b|| = n + r
+  int l = a->shape().size()-n;
+  int r = b->shape().size()-n;
+  if (l < 0 || r < 0) {
+    throw std::out_of_range("Invalid multiplication size");
+  }
+  int midBound = 1;
+  for (int i = 0; i < n; i++) {
+    if (a->shape()[l+i] != b->shape()[i]) {
[…]

### 2019-05-05 LetterClassifier/mmatrix.h

@@ -1,0 +1,60 @@
+#ifndef MMATRIX_H
+#define MMATRIX_H
+
+#include <string>
+#include <vector>
+
+namespace mmatrix {
+
+class Type {
+ public:
+  // Class names must be unique to the class of matrix.
+  Type(const std::string& class_name) : class_name_(class_name) {}
+  virtual ~Type() = default;
+  const std::string& className() const { return class_name_; }
+  // Returns true if this matrix can be cast to an instance of the given other type.
+  virtual bool implies(const std::string& other_class_name) const;
+ private:
+  std::string class_name_;
+};
+
+class MMatrixInterface {
+ public:
+  virtual ~MMatrixInterface() = default;
+  // Returns the value stored at the given indices.
+  virtual float get(const std::vector<int>& indices) const = 0;
+  // Stores a value at the given indicies. Each index must be within it's
+  // dimension defined by shape().
+  virtual void set(const std::vector<int>& indices, float value) = 0;
+  // Returns the shape (size of dimensions) of this matrix.
+  virtual const std::vector<int>& shape() const = 0;
+  // Returns the most generic type "::mmatrix::MMatrixInterface" by default.
+  virtual const Type* type() const;
+ private:
+  const static Type type_;
+};
+
+class DenseMMatrix : public MMatrixInterface {
+ public:
+  DenseMMatrix(const std::vector<int>& shape);
+  ~DenseMMatrix() = default;
+
+  float get(const std::vector<int>& indices) const override;
+  void set(const std::vector<int>& indices, float value) override;
+  const std::vector<int>& shape() const override;
+
+ private:
+  std::vector<float> values_;
+  std::vector<int> shape_;
+};
+
+int ToValueIndex(const std::vector<int>& shape, const std::vector<int>& indices);
+void FromValueIndex(const std::vector<int>& shape, int vindex,
+    std::vector<int>* indices);
+
+void Multiply(int n, const MMatrixInterface* a,
+  const MMatrixInterface* b, MMatrixInterface* out);
+
+}  // namespace mmatrix
+
+#endif

### 2019-05-05 LetterClassifier/test_mmatrix.cc

@@ -1,0 +1,105 @@
+#include "mmatrix.h"
+
+#include <iostream>
+#include <cstdlib>
+#include <vector>
+
+using mmatrix::DenseMMatrix;
+using mmatrix::ToValueIndex;
+using mmatrix::FromValueIndex;
+using std::vector;
+
+void TestToFromVIndex() {
+  std::cout << "TestToFromVIndex..." << std::endl;
+  vector<int> shape = {7,5,3};
+  int vi = ToValueIndex(shape, {5,3,1});
+  vector<int> indices(3, 0);
+  FromValueIndex(shape, vi, &indices);
+  if (indices[0] != 5) {
+    std::cerr << "TestToFromVIndex Err at 0 index." << std::endl;
+    exit(1);
+  }
+  if (indices[1] != 3) {
+    std::cerr << "TestToFromVIndex Err at 1 index." << std::endl;
+    exit(1);
+  }
+  if (indices[2] != 1) {
+    std::cerr << "TestToFromVIndex Err at 2 index." << std::endl;
+    exit(1);
+  }
+}
+
+void TestDenseMMatrixGetSet() {
+  std::cout << "TestDenseMMatrixGetSet..." << std::endl;
+  DenseMMatrix m({3,3,2});
+  m.set({0,0,0}, 1);
+  m.set({0,0,1}, 2);
+  m.set({0,1,0}, 3);
+  m.set({0,1,1}, 4);
+  m.set({0,2,0}, 5);
+  m.set({0,2,1}, 6);
+
+  m.set({1,0,0}, 7);
+  m.set({1,0,1}, 8);
+  m.set({1,1,0}, 9);
+  m.set({1,1,1}, 10);
+  m.set({1,2,0}, 11);
+  m.set({1,2,1}, 12);
+
+  m.set({2,0,0}, 13);
+  m.set({2,0,1}, 14);
+  m.set({2,1,0}, 15);
+  m.set({2,1,1}, 16);
+  m.set({2,2,0}, 17);
+  m.set({2,2,1}, 18);
+
+  for (int a = 0; a < 3; a++) {
+    for (int b = 0; b < 3; b++) {
+      for (int c = 0; c < 2; c++) {
+        float expected = a*6+b*2+c+1;
+        if (m.get({a,b,c}) != expected) {
+          std::cerr << "Unexpected result in TestDenseMMatrixGetSet" << std::endl;
+          std::exit(0);
+        }
+      }
+    }
[…]

### 2019-05-10 Math/paper.tex
Some more progress on the math.

@@
 
+\newtheoremstyle{ppart}{}{}{}{}{}{:}{ }{}
+\theoremstyle{ppart}
+\newtheorem{ppart}{Part}
+
 \DeclareMathOperator{\Dim}{Dim}
+\DeclareMathOperator{\Ident}{I}
 %\newcommand{\mmult}[1]{\stackrel{\times}{#1}}
@@
 \[
-\frac{dM}{dX} = I^3(|X|) \mmult{||X||} \cos(X)
+\frac{dM}{dX} = \Ident^3(|X|) \mmult{||X||} \cos(X)
 \]
@@
 But that single line will require defining something I'm going to call a cubic
-identity, $I^3(|X|)$, as well as multimatrix multiplication.
+identity, $\Ident^3(|X|)$, as well as multimatrix multiplication.
 
@@
 Let $A$ and $B$ be multimatricies such that $|A| = \vec{a} \oplus \vec{c}$,
-$|B| = \vec{c} \oplus \vec{b}$, and $|\vec{c}| = n$.
-Then $|A \mmult{n} B| = \vec{a} \oplus \vec{b}$ and
+$|B| = \vec{c} \oplus \vec{b}$, and $|\vec{c}| = n$ with
+$n \in \left\{ 0 \right\} \cup \mathbb{Z}^{+}$. We shall call $n$ the 'size'
+of the multiplication operation.
+The shape of the result is defined, $|A \mmult{n} B| = \vec{a} \oplus \vec{b}$
+and the value of the result is defined,
 \[
@@
 \textit{not} communicative. And it is only weakly associative. That sounds like
-nonsense, but here's what I mean:
+nonsense, but here's what I mean.
+
+Multimatrix multiplication may not even make sense dimensionally when you move
+around parentheses. Take for example multimatricies $A$, $B$, and $C$ such that,
+$|A| = \left<5,3,2\right>$,
+$|B| = \left<2,7\right>$, and
+$|C| = \left<3,7,2\right>$ where you should be able to see that
+$(A \mmult{1} B) \mmult{2} C$ is a valid operation since
+$|A \mmult{1} B| = \left<5,3,7\right>$ and
+$|(A \mmult{1} B) \mmult{2} C| = \left<5,7\right>$. But
+$A \mmult{1} (B \mmult{2} C)$ isn't a valid set of operations since even
+$B \mmult{2} C$ is an invalid operation.
+
+But even when the dimensional analysis makes sense, multimatrix multiplication
+may not be associative. Take, for example, multimatricies $A$, $B$, and $C$ such
+that $|A| = \left<2,2,2,2\right>$, $|B| = \left<2,2,2\right>$, and
+$|C| = \left<2,2,2,2\right>$. Let,
+\[
+ A[\bar{a}] = 
+	\left\{
+		\begin{array}{ll}
+			1 & \mbox{if } \bar{a} = \left<1,1,1,2\right> \\
+			0 & \mbox{otherwise}
+		\end{array}
+	\right.
+\]
+\[
+ B[\bar{b}] = 
+	\left\{
+		\begin{array}{ll}
+			1 & \mbox{if } \bar{b} = \left<1,2,1\right> \\
+			0 & \mbox{otherwise}
+		\end{array}
+	\right.
+\]
+And
+\[
+ C[\bar{c}] = 
+	\left\{
+		\begin{array}{ll}
+			1 & \mbox{if } \bar{c} = \left<1,1,1,1\right> \\
+			0 & \mbox{otherwise}
+		\end{array}
+	\right.
+\]
+Then,
+\[
+ (A \mmult{2} B)[\bar{x}] = 
+	\left\{
+		\begin{array}{ll}
+			1 & \mbox{if } \bar{x} = \left<1,1,1\right> \\
+			0 & \mbox{otherwise}
+		\end{array}
+	\right.
+\]
+So,
+\[
+ ((A \mmult{2} B) \mmult{2} C)[\bar{x}] = 
+	\left\{
+		\begin{array}{ll}
+			1 & \mbox{if } \bar{x} = \left<1,1\right> \\
+			0 & \mbox{otherwise}
+		\end{array}
+	\right.
+\]
+But, $(B \mmult{2} C)[\bar{x}] = 0$ so $(A \mmult{2} (B \mmult{2} C))[\bar{x}] = 0$
+Which goes to show that even though both $(A \mmult{2} B) \mmult{2} C$ and
+$A \mmult{2} (B \mmult{2} C)$ are valid calculations which result in multimatrixes
+of the same dimensionality, they are not equal so multiplicative associativity
+doesn't hold.
+
+However, there are a broad catagory of cases where associativity \textit{does} hold:
 
@@
 \label{mm_associativity}
-Let $A$, $B$, and $C$ be multimatricies and $n$ and $m$ in
+Let $A$, $B$, and $C$ be multimatricies and $m$ and $n$ in
 $\left\{ 0 \right\} \cup \mathbb{Z}^{+}$.
-If both operations $(A \mmult{n} B) \mmult{m} C$ and $A \mmult{n} (B \mmult{m} C)$
-are valid dimensionally, then
-\[ (A \mmult{n} B) \mmult{m} C = A \mmult{n} (B \mmult{m} C) \]
+If both operations $(A \mmult{m} B) \mmult{n} C$ and $A \mmult{m} (B \mmult{n} C)$
+are valid dimensionally and $m+n \le ||B||$, then,
+\[ (A \mmult{m} B) \mmult{n} C = A \mmult{m} (B \mmult{n} C) \]
 \end{theorem}
@@
 Let $A$, $B$, and $C$ be matricies such that the calculations
-$(A \mmult{n} B) \mmult{m} C$ and $A \mmult{n} (B \mmult{m} C)$ are both valid.
-Then the following vectors must be true by the definiton of multimatrix
-multiplication (Thm. \ref{mm_mult}).
+$(A \mmult{m} B) \mmult{n} C$ and $A \mmult{m} (B \mmult{n} C)$ are both valid
+and $m + n \le ||B||$.
+Then the following must be true by the definiton of multimatrix multiplication
+(Def. \ref{mm_mult}).
 
 \noindent
-Since $A \mmult{n} B$ is defined,
+Since $A \mmult{m} B$ is defined,
 \[
-  \exists \vec{a}, \vec{n}, \vec{b_1} :
-  |\vec{n}| = n \land |A| = \vec{a} \oplus \vec{n} \land |B| = \vec{n} \oplus \vec{b_1} 
+ \exists \vec{a}, \vec{m}, \vec{b_1} :
+ |\vec{m}| = m \land |A| = \vec{a} \oplus \vec{m} \land |B| = \vec{m} \oplus \vec{b_1} 
 \]
-Since $B \mmult{m} C$ is defined,
+Since $B \mmult{n} C$ is defined,
 \[
-  \exists \vec{b_2}, \vec{m}, \vec{c} :
-  |\vec{m}| = m \land |B| = \vec{b_2} \oplus \vec{m} \land |C| = \vec{m} \oplus \vec{c}
+ \exists \vec{b_2}, \vec{n}, \vec{c} :
+ |\vec{n}| = n \land |B| = \vec{b_2} \oplus \vec{n} \land |C| = \vec{n} \oplus \vec{c}
 \]
-Since $(A \mmult{n} B) \mmult{m} C$ is defined, $|\vec{m}| = m$, and $\vec{m}$ is
-already established as the left $m$ length portion of $|C|$,
-\[ \exists \vec{l} : |A \mmult{n} B| = \vec{l} \oplus \vec{m} \]
-Since $A \mmult{n} (B \mmult{m} C)$ is defined, $|\vec{n}| = n$, and $\vec{n}$ is
-already established as the right $n$ length portion of $|A|$,
-\[ \exists \vec{r} : |B \mmult{m} C| = \vec{n} \oplus \vec{r} \]
-We can see that,
+Since $|B| = \vec{m} \oplus \vec{b_1} = \vec{b_2} \oplus \vec{n}$ and
+$||B|| \ge |\vec{m}| + |\vec{n}|$, it must follow that,
+\[
+ \exists \vec{b} :
+ |B| = \vec{m} \oplus \vec{b} \oplus \vec{n}
+\]
+Even if $\vec{b}$ is an empty vector. Then,
+\[ |A \mmult{m} B| = \vec{a} \oplus \vec{b} \oplus \vec{n} \]
+\[ |(A \mmult{m} B) \mmult{n} C| = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
+\[ |B \mmult{n} C| = \vec{m} \oplus \vec{b} \oplus \vec{c} \]
+\[ |A \mmult{m} (B \mmult{n} C)| = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
+So,
+\[ |(A \mmult{m} B) \mmult{n} C| = |A \mmult{m} (B \mmult{n} C)| \]
+Which is necessary, but not sufficient, for our proof.
+
+Looking at each element of the result matricies, let $j$ and $k$ be the values
+of some parallel cells in $(A \mmult{m} B) \mmult{n} C$ and
+$A \mmult{m} (B \mmult{n} C)$ respectively. Then for some indicies of those cells,
+$\bar{a} \oplus \bar{b} \oplus \bar{c} \in
+\Dim(\vec{a} \oplus \vec{b} \oplus \vec{c})$,
 \begin{align*}
-  |B| &= \vec{n} \oplus \vec{b_1} \\
-      &= \vec{b_2} \oplus \vec{m}
+ j
+ &= ((A \mmult{m} B) \mmult{n} C)[\bar{a} \oplus \bar{b} \oplus \bar{c}] \\
+ &= \sum_{\forall \bar{n} \in \Dim(\vec{n})}
+ (A \mmult{m} B)[\bar{a} \oplus \bar{b} \oplus \bar{n}]
+ C[\bar{n} \oplus \bar{c}] \\
+ &= \sum_{\forall \bar{n}}
+ \left(
+  \sum_{\forall \bar{m} \in \Dim(\vec{m})}
+	A[\bar{a} \oplus \bar{m}]B[\bar{m} \oplus \bar{b} \oplus \bar{n}]
+ \right)
+ C[\bar{n} \oplus \bar{c}] \\
+ &= \sum_{\forall \bar{n}, \bar{m}}
+ A[\bar{a} \oplus \bar{m}]
+ B[\bar{m} \oplus \bar{b} \oplus \bar{n}]
+ C[\bar{n} \oplus \bar{c}] \\
+ &= \sum_{\forall \bar{m}, \bar{n}}
+ A[\bar{a} \oplus \bar{m}]
+ B[\bar{m} \oplus \bar{b} \oplus \bar{n}]
+ C[\bar{n} \oplus \bar{c}] \\
+ &= \sum_{\forall \bar{m}}
+ A[\bar{a} \oplus \bar{m}]
+ \left(
+ \sum_{\forall \bar{n}}
+  B[\bar{m} \oplus \bar{b} \oplus \bar{n}]
+  C[\bar{n} \oplus \bar{c}]
+ \right) \\
+ &= \sum_{\forall \bar{m}}
+ A[\bar{a} \oplus \bar{m}]
+ (B \mmult{n} C)[\bar{m} \oplus \bar{b} \oplus \bar{c}] \\
+ &= (A \mmult{m} (B \mmult{n} C))[\bar{a} \oplus \bar{b} \oplus \bar{c}] \\
+ &= k
 \end{align*}
-\[ \therefore \vec{n} \oplus \vec{b_1} = \vec{b_2} \oplus \vec{m} \]
-So we end up with two cases. Either $\vec{n}$ and $\vec{m}$ overlap in $|B|$, or
-they don't.
-\begin{case}
-$\vec{n}$ and $\vec{m}$ overlap. So we can suppose the existence of
-three vectors, $\vec{n_l}$, $\vec{x}$, and $\vec{m_r}$ such that $\vec{x}$
-represents the overlapping portion of $\vec{n}$ and $\vec{m}$, so
-\[ |B| =  \vec{n_l} \oplus \vec{x} \oplus \vec{m_r} \]
-\[ \vec{n} = \vec{n_l} \oplus \vec{x} \]
-And,
-\[ \vec{m} = \vec{x} \oplus \vec{m_r} \]
+Since $(A \mmult{m} B) \mmult{n} C$ and $A \mmult{m} (B \mmult{n} C)$ are both
+the same shape and every cell with the same index in each is equal, the two
+values must be equal.
+\end{proof}
 
-Since $|A| = \vec{a} \oplus \vec{n}$ and $|C| = \vec{m} \oplus \vec{c}$,
-by the definition of multimatrix multiplication,
-\[ |A \mmult{n} B| = \vec{a} \oplus \vec{m_r} \]
-And,
-\[ |B \mmult{m} C| = \vec{n_l} \oplus \vec{c} \]
-But because we've presupposed that $(A \mmult{n} B) \mmult{m} C$ is a valid operation,
-we know that the rightmost porton of $|A \mmult{n} B|$ must be $\vec{m}$, so
-$\vec{a}$ must be divisible into some vector $\vec{a_l}$ and $\vec{x}$ so that
-\[ |A \mmult{n} B| = \vec{a_l} \oplus \vec{x} \oplus \vec{m_r} \]
-\[ \vec{a} = \vec{a_l} \oplus \vec{x} \]
-By the same reasoning, since $A \mmult{m} (B \mmult{m} C)$ is a valid operation,
-there must exist some $\vec{c_r}$ such that
-\[ |B \mmult{m} C| = \vec{n_l} \oplus \vec{x} \oplus \vec{c_r} \]
+Multiplicative identities for multimatricies depend on the shape of the
+multimatrix they are being multiplied against, just as for regular matricies.
+However, the multiplicative identity also greatly depends on the size of
+the particular multiplication operation.
+
+\begin{definition}[Multimatrix Identities]
+\label{mm_ident}
+Let us define $\Ident^n(\vec{v})$ as the $n^{\text{th}}$ order identity with base shape
+$\vec{v}$. This $\Ident^n(\vec{v})$ is a multimatrix with shape,
+\[ |\Ident^n(\vec{v})| = \bigoplus_{i \in [1, n]} \vec{v} \]
+That is, it's shape is $n$ successive concatinations of $\vec{v}$.
+Let each element of $\Ident^n(\vec{v})$ is defined as,
+\[ \forall \bar{v_1}, \bar{v_2}, \ldots, \bar{v_n} \text{ each in } \Dim(\vec{v}) : \]
+\[
+ \Ident^n(\vec{v})[\bar{v_1}, \bar{v_2}, \ldots, \bar{v_n}]
+ = \left\{
+	\begin{array}{ll}
+		1 & \mbox{if } \bar{v_1} = \bar{v_2} = \ldots = \bar{v_n} \\
+		0 & \mbox{otherwise}
+	\end{array}
+ \right.
+\]
+
+In particular, let us call $\Ident^2(\vec{v})$ the square identity of $\vec{v}$ and
+$\Ident^3(\vec{v})$ the cubic identity of $\vec{v}$.
+\end{definition}
+
+That definition seems rather arbitrary, but you'll see various orders of identity
+pop up in derivatives down the line. For now, let's just look at how the
+square identity it relates to a multiplication operation.
+
+\begin{theorem}[Multimatrix Multiplicative Identity]
+For all $\vec{m}$ and $\vec{n}$ on which the operations are valid,
+\[
+ A \mmult{|\vec{m}|} \Ident^2(\vec{m}) = A
+\]
 and
-\[ \vec{c} = \vec{x} \oplus \vec{c_r} \]
+\[
+ \Ident^2(\vec{n}) \mmult{|\vec{n}|} A = A
+\]
+\end{theorem}
+\begin{proof}
+\begin{ppart}
+Let $A$ be a matrix with shape $|A| = \vec{a} \oplus \vec{m}$.
+Then by the definition of multimatrix multiplication (Def. \ref{mm_mult}),
+\[ \forall \bar{a} \in \Dim(\vec{a}), \bar{m_1} \in \Dim(\vec{m}) : \]
+\[
+ (A \mmult{|\vec{m}|} \Ident^2(\vec{m}))[\bar{a} \oplus \bar{m_1}]
+ =
+ \sum_{\forall \bar{m_2} \in \Dim(\vec{m})}
+ A[\bar{a} \oplus \bar{m_2}] \Ident^2(\vec{m})[\bar{m_2} \oplus \bar{m_1}]
+\]
+Then, by the definition of $\Ident^2(\vec{m})$ (Def. \ref{mm_ident}) it follows
+that,
+\begin{align*}
+ (A \mmult{|\vec{m}|} \Ident^2(\vec{m}))[\bar{a} \oplus \bar{m_1}]
+ &=
+ \left(
+  \sum_{\forall \bar{m_2} \ne \bar{m_1}}
+  A[\bar{a} \oplus \bar{m_2}] (0)
+ \right)
+ +
+ \left(
+  \sum_{\forall \bar{m_2} = \bar{m_1}}
+  A[\bar{a} \oplus \bar{m_2}] (1)
+ \right) \\
+ \\
+ &= 0 + A[\bar{a} \oplus \bar{m_1}] \\
+ &= A[\bar{a} \oplus \bar{m_1}]
+\end{align*}
+Therefore $A \mmult{|\vec{m}|} \Ident^2(\vec{m}) = A$
+\end{ppart}
+\begin{ppart}
+Let $A$ be a matrix with shape $|A| = \vec{n} \oplus \vec{a}$.
+Then by the definition of multimatrix multiplication (Def. \ref{mm_mult}),
+\[ \forall  \bar{n_1} \in \Dim(\vec{n}), \bar{a} \in \Dim(\vec{a}) : \]
+\[
+ (\Ident^2(\vec{n}) \mmult{|\vec{n}|} A)[\bar{n_1} \oplus \bar{a}]
+ =
+ \sum_{\forall \bar{n_2} \in \Dim(\vec{n})}
+ \Ident^2(\vec{n})[\bar{n_1} \oplus \bar{n_2}]A[\bar{n_2} \oplus \bar{a}] 
+\]
+Then, by the definition of $\Ident^2(\vec{n})$ (Def. \ref{mm_ident}) it follows
+that,
+\begin{align*}
+ (\Ident^2(\vec{n}) \mmult{|\vec{n}|} A)[\bar{n_1} \oplus \bar{a}]
+ &=
+ \left(
+  \sum_{\forall \bar{n_2} \ne \bar{n_1}}
+  (0) A[\bar{n_2} \oplus \bar{a}]
+ \right)
+ +
+ \left(
+  \sum_{\forall \bar{n_2} = \bar{n_1}}
+  (1) A[\bar{n_2} \oplus \bar{a}]
+ \right) \\
+ \\
+ &= 0 + A[\bar{n_1} \oplus \bar{a}] \\
+ &= A[\bar{n_1} \oplus \bar{a}]
+\end{align*}
+Therefore $\Ident^2(\vec{n}) \mmult{|\vec{n}|} A = A$
+\end{ppart}
+\end{proof}
 
-Subsituting in those derived values, we'll see that the expanded version of
-our multimatrix shapes become,
-\[ |A| = \vec{a_l} \oplus \vec{x} \oplus \vec{n_l} \oplus \vec{x} \]
-\[ |B| = \vec{n_l} \oplus \vec{x} \oplus \vec{m_r} \]
-\[ |C| = \vec{x} \oplus \vec{m_r} \oplus \vec{x} \oplus \vec{c_r} \]
+The square identity also pops up in the derivative of a multimatrix
+with respect to itself.
 
-It's then clear that the shapes of both associations are equal,
-\[ |(A \mmult{m} B) \mmult{n} C| = \vec{a_l} \oplus \vec{x} \oplus \vec{c_r} \]
-\[ |A \mmult{m} (B \mmult{n} C)| = \vec{a_l} \oplus \vec{x} \oplus \vec{c_r} \]
-Which is a necessary, but not sufficient condition for our proof that
-$(A \mmult{m} B) \mmult{n} C = A \mmult{m} (B \mmult{n} C)$. We now need to prove
-that each of the elements of each resulting multimatrix are the same.
-
-\end{case}
-
+\begin{theorem}[Self Derivative]
+Let $X$ be a multimatrix with independent elements. Then,
+\[ \frac{dX}{dX} = \Ident^2(|X|) \]
+\end{theorem}
+\begin{proof}
+Let $X$ be a multimatrix of shape $|X|=\vec{x}$ with independent elements.
+By the derivative definition (Def. \ref{mm_derivative}),
 \[
-  \vec{b_2} \oplus \vec{c} = \vec{n} \oplus \vec{r}
+ \forall \bar{x_1} \in \Dim(\vec{x}),
+         \bar{x_2} \in \Dim(\vec{x}):
 \]
 \[
-  \vec{l} \oplus \vec{c} = \vec{a} \oplus \vec{r}
+ \frac{dX}{dX}[\bar{x_1} \oplus \bar{x_2}] = 
+ \frac{\partial X[\bar{x_1}]}{\partial X[\bar{x_2}]}
 \]
-\[
-  ((A \mmult{n} B) \mmult{m} C)[\bar{l} \oplus \bar{c}] =
-	\sum_{\forall \bar{m}} (A \mmult{n} B)[\bar{l} \oplus \bar{m}]C[\bar{m} \oplus \bar{c}]
-\]
+Since each element of $X$ is independent with respect to itself,
+\begin{align*}
+ \frac{dX}{dX}[\bar{x_1} \oplus \bar{x_2}]
+ &= \left\{
+	\begin{array}{ll}
+		1 & \mbox{if } \bar{x_1} = \bar{x_2} \\
+		0 & \mbox{otherwise}
+	\end{array}
+ \right. \\
+ &= \Ident^2(\vec{x})[\bar{x_1} \oplus \bar{x_2}]
+\end{align*}
+Therefore $dX/dX = \Ident^2(|X|)$
+\end{proof}
 
+The cubic identity, strangely enough, pops up in the derivative of elementwise
+functions.
+
+\begin{theorem}[Elementwise Derivative]
+Let $M$ be an element wise function on $X$. That is, Let $M(X)$ be a function
+such that,
+\[ M(X) : \mathbb{R}^{\vec{x}} \to \mathbb{R}^{\vec{x}} \]
+And which applies the same scalar function to each element of $X$, 
+\[ M(X)[\bar{x}] = m(X[\bar{x}]) \]
+Also, let $M'$ be the elementwise function on $X$ which applies the derivative
+of $M$'s associated scalar function to each element of $X$. That is,
+\[ M'(X)[\bar{x}] = m'(X[\bar{x}]) \]
+Then,
+\[ \frac{dM}{dX} = \Ident^3(|X|) \mmult{||X||} M'(X) \]
+\end{theorem}
+\begin{proof}
+By the definition of a multimatrix derivative,
+\[ \forall \bar{m} \in \Dim(|M|), \bar{x} \in \Dim(|X|) : \]
+\begin{align*}
+ \frac{dM}{dX}[\bar{m} \oplus \bar{x}]
+ &= \frac{\partial M[\bar{m}]}{\partial X[\bar{x}]} \\
+ &= \frac{\partial m(X[\bar{m}])}{\partial X[\bar{x}]} \\
+ &= \left\{
+	\begin{array}{ll}
+		m'(X[\bar{m}]) & \mbox{if } \bar{m} = \bar{x} \\
+		0 & \mbox{otherwise}
+	\end{array}
+ \right. \\
+ &= \delta_{\bar{m} \bar{x}} m'(X[\bar{m}])
+\end{align*}
+Since, by our definition of elementwise function, $|M| = |X|$, we can
+say that, 
+\begin{align*}
+ (\Ident^3(|X|) \mmult{||X||} M'(X))[\bar{m} \oplus \bar{x}]
+ &= \sum_{\forall \bar{y} \in \Dim(|X|)}
+ \Ident^3(|X|)[\bar{m} \oplus \bar{x} \oplus \bar{y}] M'(X)[\bar{y}] \\
+ &= \sum_{\forall \bar{y} \in \Dim(|X|)}
+ \Ident^3(|X|)[\bar{m} \oplus \bar{x} \oplus \bar{y}] m'(X[\bar{y}]) \\
+ &= \sum_{\forall \bar{y} = \bar{m} = \bar{x}}
+ \Ident^3(|X|)[\bar{m} \oplus \bar{x} \oplus \bar{y}] m'(X[\bar{y}]) \\
+ &= \left\{
+	\begin{array}{ll}
+		m'(X[\bar{m}]) & \mbox{if } \bar{m} = \bar{x} \\
+		0 & \mbox{otherwise}
+	\end{array}
+ \right. \\
+ &= \delta_{\bar{m} \bar{x}} m'(X[\bar{m}])
+\end{align*}
+Therefore $dM/dX = \Ident^3(|X|) \mmult{||X||} M'(X)$
+\end{proof}
+
+\begin{theorem}[Identity Contraction]
+For all $m, n, k \in \mathbb{Z}^+$ and $\vec{x}$ as a valid multimatrix shape,
+where $m > k$ and $n > k$,
+\[ \Ident^m(\vec{x}) \mmult{k|\vec{x}|} \Ident^n(\vec{x}) = \Ident^{m+n-2k}(\vec{x}) \]
+\end{theorem}
+\begin{proof}
+TODO
+\end{proof}
+
+\begin{theorem}[Communicative Identity Multiplication]
+\[ \Ident^n(\vec{x}) \mmult{k|\vec{x}|} A = A \mmult{k|\vec{x}|} \Ident^n(\vec{x}) \]
+\end{theorem}
+\begin{proof}
+TODO
+\end{proof}
+
+\subsection*{Sample Problems}
+TODO
+
+\section{Other Operations With Multimatricies}
+Other operations include...
+
+\begin{definition}[Multimatrix Scalar Multiplication]
+\[ sA = ...\]
+\end{definition}
+
+\subsection{Addition}
+
+\begin{definition}[Multimatrix Addition]
+Bla
+\[ A + B = C \]
+\end{definition}
+
+\begin{theorem}[Communicative Property of Multimatrix Addition]
+Bla
+\[ A + B = B + A \]
+\end{theorem}
+\begin{proof}
+TODO
+\end{proof}
+
+\begin{theorem}[Associative Property of Multimatrix Addition]
+\[ (A + B) + C = A + (B + C) \]
+\end{theorem}
+\begin{proof}
+TODO
+\end{proof}
+
+\begin{theorem}[Multimatrix on Multimatrix Distributive Property]
+\[ A \mmult{n} (B + C) = A \mmult{n} B + A \mmult{n} C \]
+\end{theorem}
+\begin{proof}
+TODO
+\end{proof}
+
+\begin{theorem}[Scalar on Multimatrix Distributive Property]
+\[ s(A + B) = sA + sB \]
+\end{theorem}
+\begin{proof}
+TODO
 \end{proof}
@@
 
+\section{Integration}
+
+I think, I'm not sure, but I think that the integral of a multimatrix function should
+be defined,
+
+\[
+ \int_A^B F(X) dX = \lim_{n \to \infty}
+ \sum_{i=1}^n
+  F\left(A+\frac{i}{n}(B-A)\right)
+  \mmult{||X||}
+  \left(\frac{B-A}{n}\right)
+\]
+
+Which, I have very little idea what that means geometriclly, but
+if you let $G(X) = \int_A^X F(Y) dY$ you seem to end up with $dG/dX = F(X)$.
+
+Maybe... well look at it this way. $F(X)$ is a function which produces some,
+afine-like transformation multimatrix for multimatricies of shape $|X|$,
+since it must have a right hand shape of $\ldots \oplus |X|$. This integration
+occures over a linear path of $X$ as it moves from $A$ to $B$ applying that
+transformation and adding up the results of the transformed multimatricies with
+a weight proportional to the step size.
+
+So, it's sort of like a line integral but not really. They're related somehow.
 \end{document}

### 2019-05-10 LetterClassifier/test_mmatrix.cc

@@ -96,10 +96,82 @@ void TestMMatrixMultiplication() {
   }
 }
 
+void TestMMatrixMultiplicationAssociation() {
+  std::cout << "TestMMatrixMultiplicationAssociation..." << std::endl;
+
+  DenseMMatrix a({2,2,2,2});
+  a.set({0,0,0,0}, 0);
+  a.set({0,0,0,1}, 1);
+  a.set({0,0,1,0}, 0);
+  a.set({0,0,1,1}, 0);
+  a.set({0,1,0,0}, 0);
+  a.set({0,1,0,1}, 0);
+  a.set({0,1,1,0}, 0);
+  a.set({0,1,1,1}, 0);
+  a.set({1,0,0,0}, 0);
+  a.set({1,0,0,1}, 0);
+  a.set({1,0,1,0}, 0);
+  a.set({1,0,1,1}, 0);
+  a.set({1,1,0,0}, 0);
+  a.set({1,1,0,1}, 0);
+  a.set({1,1,1,0}, 0);
+  a.set({1,1,1,1}, 0);
+
+  DenseMMatrix b({2,2,2});
+  b.set({0,0,0}, 0);
+  b.set({0,0,1}, 0);
+  b.set({0,1,0}, 1);
+  b.set({0,1,1}, 0);
+  b.set({1,0,0}, 0);
+  b.set({1,0,1}, 0);
+  b.set({1,1,0}, 0);
+  b.set({1,1,1}, 0);
+  
+  DenseMMatrix c({2,2,2,2});
+  c.set({0,0,0,0}, 1);
+  c.set({0,0,0,1}, 0);
+  c.set({0,0,1,0}, 0);
+  c.set({0,0,1,1}, 0);
+  c.set({0,1,0,0}, 0);
+  c.set({0,1,0,1}, 0);
+  c.set({0,1,1,0}, 0);
+  c.set({0,1,1,1}, 0);
+  c.set({1,0,0,0}, 0);
+  c.set({1,0,0,1}, 0);
+  c.set({1,0,1,0}, 0);
+  c.set({1,0,1,1}, 0);
+  c.set({1,1,0,0}, 0);
+  c.set({1,1,0,1}, 0);
+  c.set({1,1,1,0}, 0);
+  c.set({1,1,1,1}, 0);
+
+  DenseMMatrix ab({2,2,2});
+  DenseMMatrix bc({2,2,2});
+  DenseMMatrix ab_c({2,2,2});
[…]

### 2019-05-12 LetterClassifier/mmatrix.cc
Adding some useful mmatrix functions

@@ -1,16 +1,28 @@
 #include "mmatrix.h"
 
+#include <cmath>
 #include <stdexcept>
 
 namespace mmatrix {
 
 using std::string;
+using std::unique_ptr;
 using std::vector;
 
 bool Type::implies(const string& other_class_name) const {
   return other_class_name == class_name_;
 }
 
+float MMatrixInterface::get(int i) const {
+  vector<int> indices(shape().size(), 0);
+  FromValueIndex(shape(), i, &indices);
+  return get(indices);
+}
+void MMatrixInterface::set(int i, float value) {
+  vector<int> indices(shape().size(), 0);
+  FromValueIndex(shape(), i, &indices);
+  set(indices, value);
+}
 const Type MMatrixInterface::type_ = Type("::mmatrix::MMatrixInterface");
 const Type* MMatrixInterface::type() const {
   return &type_;
@@ -22,6 +34,12 @@ DenseMMatrix::DenseMMatrix(const vector<int>& shape) : shape_(shape) {
     total_size *= shape[i];
   }
   values_ = vector<float>(total_size, 0);
+}
+float DenseMMatrix::get(int i) const {
+  return values_[i];
+}
+void DenseMMatrix::set(int i, float value) {
+  values_[i] = value;
 }
 float DenseMMatrix::get(const vector<int>& indices) const {
   return values_[ToValueIndex(shape_, indices)];
@@ -54,6 +72,9 @@ void FromValueIndex(const vector<int>& shape, int vindex, vector<int>* indices) 
 
 void Multiply(int n, const MMatrixInterface* a, const MMatrixInterface* b,
     MMatrixInterface* out) {
+  if (a == nullptr || b == nullptr || out == nullptr) {
+    throw std::invalid_argument("Multiply cannot take null arguments.");
+  }
   // ||a|| = l + n
   // ||b|| = n + r
   int l = a->shape().size()-n;
@@ -82,24 +103,65 @@ void Multiply(int n, const MMatrixInterface* a, const MMatrixInterface* b,
     }
     rBound *= b->shape()[n+i];
   }
-  vector<int> aIndices(a->shape().size(), 0);
-  vector<int> bIndices(b->shape().size(), 0);
-  vector<int> outIndices(out->shape().size(), 0);
   for (int vl = 0; vl < lBound; vl++) {
     for (int vr = 0; vr < rBound; vr++) {
       float sum = 0;
[…]

### 2019-05-12 LetterClassifier/mmatrix.h

@@ -1,6 +1,7 @@
 #ifndef MMATRIX_H
 #define MMATRIX_H
 
+#include <memory>
 #include <string>
 #include <vector>
 
@@ -23,6 +24,12 @@ class MMatrixInterface {
   virtual ~MMatrixInterface() = default;
   // Returns the value stored at the given indices.
   virtual float get(const std::vector<int>& indices) const = 0;
+  // Returns the value stored at the given indices represented by i.
+  // See ToValueIndex.
+  virtual float get(int i) const;
+  // Stores a value at the given indicies represented by i.
+  // See ToValueIndex.
+  virtual void set(int i, float value);
   // Stores a value at the given indicies. Each index must be within it's
   // dimension defined by shape().
   virtual void set(const std::vector<int>& indices, float value) = 0;
@@ -39,6 +46,8 @@ class DenseMMatrix : public MMatrixInterface {
   DenseMMatrix(const std::vector<int>& shape);
   ~DenseMMatrix() = default;
 
+  float get(int i) const override;
+  void set(int i, float value) override;
   float get(const std::vector<int>& indices) const override;
   void set(const std::vector<int>& indices, float value) override;
   const std::vector<int>& shape() const override;
@@ -54,6 +63,16 @@ void FromValueIndex(const std::vector<int>& shape, int vindex,
 
 void Multiply(int n, const MMatrixInterface* a,
   const MMatrixInterface* b, MMatrixInterface* out);
+
+// Throws an error when matricies aren't even the same shape.
+// Epsilon is an optional small positive value under which differences are
+// still considered "equal". So, if epsilon=0.0001, then technically different
+// matricies a and b will still be considered equal if none of their elements
+// differ by more than 0.0001.
+bool AreEqual(const MMatrixInterface* a, const MMatrixInterface* b, float epsilon = 0);
+
+// Returns an n'th order identity with the given base_shape.
+std::unique_ptr<MMatrixInterface> Ident(int n, const std::vector<int>& base_shape);
 
 }  // namespace mmatrix
 

### 2019-05-12 LetterClassifier/test_mmatrix.cc

@@ -4,10 +4,9 @@
 #include <cstdlib>
 #include <vector>
 
-using mmatrix::DenseMMatrix;
-using mmatrix::ToValueIndex;
-using mmatrix::FromValueIndex;
+using namespace mmatrix;
 using std::vector;
+using std::unique_ptr;
 
 void TestToFromVIndex() {
   std::cout << "TestToFromVIndex..." << std::endl;
@@ -17,15 +16,15 @@ void TestToFromVIndex() {
   FromValueIndex(shape, vi, &indices);
   if (indices[0] != 5) {
     std::cerr << "TestToFromVIndex Err at 0 index." << std::endl;
-    exit(1);
+    std::exit(1);
   }
   if (indices[1] != 3) {
     std::cerr << "TestToFromVIndex Err at 1 index." << std::endl;
-    exit(1);
+    std::exit(1);
   }
   if (indices[2] != 1) {
     std::cerr << "TestToFromVIndex Err at 2 index." << std::endl;
-    exit(1);
+    std::exit(1);
   }
 }
 
@@ -154,16 +153,65 @@ void TestMMatrixMultiplicationAssociation() {
   Multiply(2, &ab, &c, &ab_c);
   Multiply(2, &a, &bc, &a_bc);
 
+  bool are_equal = true;
   for (int i = 0; i < 2; i++) {
     for (int j = 0; j < 2; j++) {
       for (int k = 0; k < 2; k++) {
         if (ab_c.get({i,j,k}) != a_bc.get({i,j,k})) {
-          std::cout << i << ", " << j << ", " << k << std::endl;
-          std::cout << "  ab_c:" << ab_c.get({i,j,k}) << std::endl;
-          std::cout << "  a_bc:" << a_bc.get({i,j,k}) << std::endl;
+          are_equal = false;
+          // std::cout << i << ", " << j << ", " << k << std::endl;
+          // std::cout << "  ab_c:" << ab_c.get({i,j,k}) << std::endl;
+          // std::cout << "  a_bc:" << a_bc.get({i,j,k}) << std::endl;
         }
       }
     }
+  }
+  if (are_equal) {
+    std::cerr << "ab_c and a_bc are equal but should not be" << std::endl;
+    std::exit(1);
+  }
+}
+
+void TestIdentityMultiplication() {
+  std::cout << "TestIdentityMultiplication..." << std::endl;
+
+  DenseMMatrix a({7,3,5});
+  for (int i = 0; i < 7*3*5; i++) {
+    a.set(i, i);
+  }
+  
[…]

### 2019-05-17 Math/paper.tex
Adding some useful mmatrix functions
Doing a bit of work on integration.

@@
 \usepackage{mathtools}
+\usepackage{pdflscape}
 
@@
 \newtheorem{theorem}{Theorem}[section]
+\newtheorem{corollary}{Corollary}[theorem]
 
@@
 \DeclareMathOperator{\Ident}{I}
+\DeclareMathOperator{\Tran}{Tran}
 %\newcommand{\mmult}[1]{\stackrel{\times}{#1}}
@@
 
+\begin{definition}[Multimatrix Subtractin]
+\[ A - B = A + (-1)B \]
+\end{definition}
+
 \begin{theorem}[Communicative Property of Multimatrix Addition]
@@
 \end{proof}
+
+\subsection{Transposition}
+
+\begin{definition}[Multimatrix Transposition]
+Let $|X| = \vec{l} \oplus \vec{r}$ where $|\vec{l}| = l$ and $|\vec{r}| = r$
+\[ |\Tran(X, l)| = \vec{r} \oplus \vec{l} \]
+And,
+\[ \forall \bar{l} \in \Dim(\vec{l}), \bar{r} \in \Dim(\vec{r}) : \]
+\[ \Tran(X, l)[\bar{r} \oplus \bar{l}] = X[\bar{l} \oplus \bar{r}] \]
+\end{definition}
+
+\subsection*{Sample Problems}
+TODO
+
+\section{Derivative Rules}
+
+\begin{theorem}[Right Multiplicative Derivative]
+\[ \frac{d(A \mmult{n} X)}{dX} = A \mmult{n} \Ident^2(|X|) \]
+\end{theorem}
+\begin{proof}
+TODO
+\end{proof}
+
+\begin{theorem}[Left Multiplicative Derivative]
+\[ \frac{d(X \mmult{n} A)}{dX} = \Ident^2(|X \mmult{n} A|) \mmult{n} \Tran(A, n) \]
+\end{theorem}
+\begin{proof}
+TODO
+\end{proof}
+
+\begin{theorem}[Transpose Derivative]
+$|X| = \vec{l} \oplus \vec{r}$
+\[
+ \frac{d\Tran(X, |\vec{l}|)}{dX} =
+ \Tran(\Ident^2(\vec{r}) \mmult{0} \Ident^2(\vec{l}), |\vec{r}|)
+\]
+\end{theorem}
+\begin{proof}
+\begin{align*}
+ \frac{d\Tran(X, |\vec{l}|)}{dX}
+ [\bar{r_1} \oplus \bar{l_1} \oplus \bar{l_2} \oplus \bar{r_2}]
+ &= \delta_{\bar{r_1}\bar{r_2}} \delta_{\bar{l_1}\bar{l_2}} \\
+ &= \delta_{\bar{r_2}\bar{r_1}} \delta_{\bar{l_1}\bar{l_2}} \\
+ &=
+  \Ident^2(|\vec{r}|)[\bar{r_2}\oplus\bar{r_1}]
+  \Ident^2(|\vec{l}|)[\bar{l_1}\oplus\bar{l_2}] \\
+ &=
+ 	\left(
+		\Ident^2(|\vec{r}|)
+		\mmult{0}
+		\Ident^2(|\vec{l}|)
+	\right)
+	[\bar{r_2}\oplus\bar{r_1}\oplus\bar{l_1}\oplus\bar{l_2}] \\
+ &=
+  \Tran(
+    \Ident^2(|\vec{r}|)
+	  \mmult{0}
+    \Ident^2(|\vec{l}|)
+  , |\vec{r}|) 
+ [\bar{r_1} \oplus \bar{l_1} \oplus \bar{l_2} \oplus \bar{r_2}]
+\end{align*}
+\end{proof}
+
+\begin{theorem}[Addition Rule]
+\[ \frac{d(F(X) + G(X))}{dX} = \frac{dF(X)}{dX} + \frac{dG(X)}{dX} \]
+\end{theorem}
+\begin{proof}
+TODO
+\end{proof}
+
+\begin{theorem}[Scalar Multiplication Rule]
+\[ \frac{d(sF(X))}{dX} = s\frac{dF(X)}{dX} \]
+\end{theorem}
+\begin{proof}
+TODO
+\end{proof}
+
+\begin{landscape}
+\begin{theorem}[Multiplication Rule]
+Let $|F| = \vec{f} \oplus \vec{c}$, $|G| = \vec{c} \oplus \vec{g}$,
+and $|X| = \vec{x}$. Then,
+\begin{align*}
+ \frac{d\left(F(X) \mmult{|\vec{c}|} G(X)\right)}{dX} =
+ F(X) \mmult{|\vec{c}|} \frac{dG(X)}{dX} +
+ \Tran\left(
+   \Tran(G(X), |\vec{c}|)
+	   \mmult{|\vec{c}|}
+	 \Tran\left(\frac{dF(X)}{dX}, |\vec{f}|\right),
+   |\vec{g} \oplus \vec{x}|
+ \right)
+\end{align*}
+\end{theorem}
+\begin{proof}
+\[
+ \forall
+  \bar{f} \in \Dim(\vec{f}),
+	\bar{g} \in \Dim(\vec{g}),
+	\bar{x} \in \Dim(\vec{x})
+ :
+\]
+\begin{align*}
+ \frac{d\left(F(X) \mmult{|\vec{c}|} G(X)\right)}{dX}
+  [\bar{f} \oplus \bar{g} \oplus \bar{x}]
+ &= \frac{
+ 			\partial \left(F(X) \mmult{|\vec{c}|} G(X)\right)[\bar{f} \oplus \bar{g}]
+		}{
+ 			\partial X[\bar{x}]
+		} \\
+ &= \frac{
+ 			\partial \left(
+				\sum_{\forall \bar{c} \in \Dim(\vec{c})}
+				 F(X)[\bar{f} \oplus \bar{c}] G(X)[\bar{c} \oplus \bar{g}]
+			\right)
+		}{
+ 			\partial X[\bar{x}]
+		} \\
+ &= \sum_{\forall \bar{c} \in \Dim(\vec{c})}
+    \frac{
+			\partial F(X)[\bar{f} \oplus \bar{c}] G(X)[\bar{c} \oplus \bar{g}]
+		}{
+		  \partial X[\bar{x}]
+	  }\\
+ &= \sum_{\forall \bar{c} \in \Dim(\vec{c})}
+		F(X)[\bar{f} \oplus \bar{c}]
+    \frac{\partial G(X)[\bar{c} \oplus \bar{g}]}{\partial X[\bar{x}]}
+		+
+    \frac{\partial F(X)[\bar{f} \oplus \bar{c}]}{\partial X[\bar{x}]}
+		G(X)[\bar{c} \oplus \bar{g}] \\
+ &=
+	 \left(
+		\sum_{\forall \bar{c}}
+			F(X)[\bar{f} \oplus \bar{c}]
+			\frac{\partial G(X)[\bar{c} \oplus \bar{g}]}{\partial X[\bar{x}]}
+	 \right)
+	 +
+	 \left(
+		\sum_{\forall \bar{c}}
+			\frac{\partial F(X)[\bar{f} \oplus \bar{c}]}{\partial X[\bar{x}]}
+			G(X)[\bar{c} \oplus \bar{g}]
+	 \right) \\
+ &=
+ 	 l + r
+\end{align*}
+\begin{align*}
+ l
+ &=
+	\sum_{\forall \bar{c}}
+		F(X)[\bar{f} \oplus \bar{c}]
+		\frac{\partial G(X)[\bar{c} \oplus \bar{g}]}{\partial X[\bar{x}]} \\
+ &=
+	\sum_{\forall \bar{c}}
+		F(X)[\bar{f} \oplus \bar{c}]
+		\frac{dG(X)}{dX}[\bar{c} \oplus \bar{g} \oplus \bar{x}] \\
+ &=
+	 \left( F(X) \mmult{|\vec{c}|} \frac{dG(X)}{dX} \right)
+	 [\bar{f} \oplus \bar{g} \oplus \bar{x}]
+\end{align*}
+\begin{align*}
+ r
+ &=
+	\sum_{\forall \bar{c}}
+		\frac{\partial F(X)[\bar{f} \oplus \bar{c}]}{\partial X[\bar{x}]}
+		G(X)[\bar{c} \oplus \bar{g}] \\
+ &=
+	\sum_{\forall \bar{c}}
+		\frac{dF(X)}{dX}[\bar{f} \oplus \bar{c} \oplus \bar{x}]
+		G(X)[\bar{c} \oplus \bar{g}] \\
+ &=
+	\sum_{\forall \bar{c}}
+		\Tran\left(\frac{dF(X)}{dX}, |\vec{f}|\right)
+			[\bar{c} \oplus \bar{x} \oplus \bar{f}]
+		\Tran(G(X), |\vec{c}|)[\bar{g} \oplus \bar{c}] \\
+ &=
+	\sum_{\forall \bar{c}}
+		\Tran(G(X), |\vec{c}|)[\bar{g} \oplus \bar{c}]
+		\Tran\left(\frac{dF(X)}{dX}, |\vec{f}|\right)
+			[\bar{c} \oplus \bar{x} \oplus \bar{f}] \\
+ &=
+  \left(
+		\Tran(G(X), |\vec{c}|) \mmult{|\vec{c}|}
+		\Tran\left(\frac{dF(X)}{dX}, |\vec{f}|\right)
+	\right)[\bar{g} \oplus \bar{x} \oplus \bar{f}] \\
+ &= 
+  \Tran\left(
+		\Tran(G(X), |\vec{c}|) \mmult{|\vec{c}|}
+		\Tran\left(\frac{dF(X)}{dX}, |\vec{f}|\right)
+		, |\vec{g} \oplus \vec{x}|
+	\right)[\bar{f} \oplus \bar{g} \oplus \bar{x}]
+\end{align*}
+Therefore 
+\[
+ \frac{d\left(F(X) \mmult{|\vec{c}|} G(X)\right)}{dX}
+  [\bar{f} \oplus \bar{g} \oplus \bar{x}]
+\]
+\begin{align*}
+	=& 
+	\left( F(X) \mmult{|\vec{c}|} \frac{dG(X)}{dX} \right)
+	[\bar{f} \oplus \bar{g} \oplus \bar{x}] \\
+	&+
+  \Tran\left(
+		\Tran(G(X), |\vec{c}|) \mmult{|\vec{c}|}
+		\Tran\left(\frac{dF(X)}{dX}, |\vec{f}|\right)
+		, |\vec{g} \oplus \vec{x}|
+	\right)[\bar{f} \oplus \bar{g} \oplus \bar{x}] \\
+\end{align*}
+\[
+	=
+  \left\{
+		\left( F(X) \mmult{|\vec{c}|} \frac{dG(X)}{dX} \right)
+		+
+		\Tran\left(
+			\Tran(G(X), |\vec{c}|) \mmult{|\vec{c}|}
+			\Tran\left(\frac{dF(X)}{dX}, |\vec{f}|\right)
+			, |\vec{g} \oplus \vec{x}|
+		\right)
+	\right\}
+	[\bar{f} \oplus \bar{g} \oplus \bar{x}]
+\]
+\end{proof}
+\end{landscape}
+
+\subsection{Chain Rules}
 
@@
 transformation and adding up the results of the transformed multimatricies with
-a weight proportional to the step size.
+a weight proportional to the step size... and in the direction of the step.
 
 So, it's sort of like a line integral but not really. They're related somehow.
+
+\begin{landscape}
+Let's see if I can prove that theory,
+\begin{theorem}[Fundamental Rule of Multimatrix Calculus]
+Let $G(X) = \int_A^X F(Y) dY$ then $dG(X)/dX = F(X)$.
+\end{theorem}
+\begin{proof}
+\begin{align*}
+	G(X)
+	&= \int_A^X F(Y) dY \\
+	&= 
+		\lim_{n \to \infty}
+	 	\sum_{i=1}^n
+		  F\left(A+\frac{i}{n}(X-A)\right)
+		  \mmult{||Y||}
+		  \left(\frac{X-A}{n}\right)
+\end{align*}
+\begin{alignat*}{3}
+	\frac{dG(X)}{dX}
+	&=&&
+	  \frac{
+			d \left\{
+			\lim_{n \to \infty}
+			\sum_{i=1}^n
+				F\left(A+\frac{i}{n}(X-A)\right)
+				\mmult{||Y||}
+				\left(\frac{X-A}{n}\right)
+			\right\}
+		}{dX} \\
+	&=&&
+		\lim_{n \to \infty}
+		\frac{
+			d \left\{
+			\sum_{i=1}^n
+				F\left(A+\frac{i}{n}(X-A)\right)
+				\mmult{||Y||}
+				\left(\frac{X-A}{n}\right)
+			\right\}
+		}{dX} \\
+	&=&&
+		\lim_{n \to \infty}
+		\sum_{i=1}^n
+			\frac{
+				d \left\{
+					F\left(A+\frac{i}{n}(X-A)\right)
+					\mmult{||Y||}
+					\left(\frac{X-A}{n}\right)
+				\right\}
+			}{dX} \\
+	&=&&
+		\lim_{n \to \infty}
+			\sum_{i=1}^n
+				F\left(A+\frac{i}{n}(X-A)\right)
+					\mmult{||Y||}
+					\frac{d \left(\frac{X-A}{n}\right)}{dX}
+				\\&&&+
+				\Tran\left(
+					\Tran\left(\frac{X-A}{n}, ||Y||\right)
+					\mmult{||Y||}
+					\Tran\left(\frac{
+						d \left\{F\left(A+\frac{i}{n}(X-A)\right)\right\}
+					}{dX}, |\vec{f}|\right),
+					|\vec{x} \oplus \vec{x}|
+				\right) \\
+	&=&&
+		\lim_{n \to \infty}
+			\sum_{i=1}^n
+				F\left(A+\frac{i}{n}(X-A)\right)
+					\mmult{||Y||}
+					\frac{1}{n}\Ident^2(|X|)
+				\\&&&+
+				\Tran\left(
+					\frac{X-A}{n}
+					\mmult{||Y||}
+					\Tran\left(
+						\frac{dF(X)}{dX}
+						\mmult{|X|}
+						\frac{i}{n}\Ident^2(|X|), |\vec{f}|\right),
+					|\vec{x} \oplus \vec{x}|
+				\right) \\
+	&=&&
+		\lim_{n \to \infty}
+			\sum_{i=1}^n
+				\frac{1}{n}F\left(A+\frac{i}{n}(X-A)\right)
+				\\&&&+
+				\Tran\left(
+					\frac{X-A}{n}
+					\mmult{||Y||}
+					\Tran\left(
+						\frac{i}{n}\frac{dF(X)}{dX}
+						, |\vec{f}|\right),
+					|\vec{x} \oplus \vec{x}|
+				\right)
+\end{alignat*}
+At this point I'm fairly stuck.
+\end{proof}
+\end{landscape}
 \end{document}

### 2019-05-17 LetterClassifier/mmatrix.cc
Adding sparse matrix.

@@ -9,9 +9,16 @@ using std::string;
 using std::unique_ptr;
 using std::vector;
 
-bool Type::implies(const string& other_class_name) const {
-  return other_class_name == class_name_;
+namespace internal {
+
+bool Type::hasProperty(TypeProperty property) const {
+  return properties_.find(property) != properties_.end();
 }
+void Type::addProperty(TypeProperty property) {
+  properties_.insert(property);
+}
+
+} // namespace internal
 
 float MMatrixInterface::get(int i) const {
   vector<int> indices(shape().size(), 0);
@@ -23,8 +30,15 @@ void MMatrixInterface::set(int i, float value) {
   FromValueIndex(shape(), i, &indices);
   set(indices, value);
 }
-const Type MMatrixInterface::type_ = Type("::mmatrix::MMatrixInterface");
-const Type* MMatrixInterface::type() const {
+float MMatrixInterface::get(const vector<int>& indices) const {
+  return get(ToValueIndex(shape(), indices));
+}
+void MMatrixInterface::set(const vector<int>& indices, float value) {
+  set(ToValueIndex(shape(), indices), value);
+}
+const internal::Type MMatrixInterface::type_ =
+  internal::Type("::mmatrix::MMatrixInterface");
+const internal::Type* MMatrixInterface::type() const {
   return &type_;
 }
 
@@ -41,15 +55,42 @@ float DenseMMatrix::get(int i) const {
 void DenseMMatrix::set(int i, float value) {
   values_[i] = value;
 }
-float DenseMMatrix::get(const vector<int>& indices) const {
-  return values_[ToValueIndex(shape_, indices)];
-}
-void DenseMMatrix::set(const vector<int>& indices, float value) {
-  values_[ToValueIndex(shape_, indices)] = value;
-}
 const vector<int>& DenseMMatrix::shape() const {
   return shape_;
 }
+
+SparseMMatrix::SparseMMatrix(const std::vector<int>& shape) : shape_(shape) {}
+float SparseMMatrix::get(int i) const {
+  const auto v = values_.find(i);
+  if (v != values_.end()) {
+    return v->second;
+  }
+  return 0;
+}
+void SparseMMatrix::set(int i, float value) {
+  if (value == 0) {
+    const auto it = values_.find(i);
+    if (it != values_.end()) {
+      values_.erase(it);
+    }
+  } else {
+    values_[i] = value;
+  }
+}
[…]

### 2019-05-17 LetterClassifier/mmatrix.h

@@ -3,27 +3,38 @@
 
 #include <memory>
 #include <string>
+#include <unordered_map>
+#include <unordered_set>
 #include <vector>
 
 namespace mmatrix {
 
+namespace internal {
+
+typedef uint64_t TypeProperty;
+constexpr TypeProperty kTypeProperty_Sparse = 1;
+
 class Type {
  public:
-  // Class names must be unique to the class of matrix.
   Type(const std::string& class_name) : class_name_(class_name) {}
   virtual ~Type() = default;
   const std::string& className() const { return class_name_; }
-  // Returns true if this matrix can be cast to an instance of the given other type.
-  virtual bool implies(const std::string& other_class_name) const;
+  // Returns true if this matrix has the specified property.
+  bool hasProperty(TypeProperty property) const;
+  // This should only be called by the class setting up the types.
+  void addProperty(TypeProperty property);
  private:
   std::string class_name_;
+  std::unordered_set<TypeProperty> properties_;
 };
+
+}  // namespace internal
 
 class MMatrixInterface {
  public:
   virtual ~MMatrixInterface() = default;
   // Returns the value stored at the given indices.
-  virtual float get(const std::vector<int>& indices) const = 0;
+  virtual float get(const std::vector<int>& indices) const;
   // Returns the value stored at the given indices represented by i.
   // See ToValueIndex.
   virtual float get(int i) const;
@@ -32,13 +43,13 @@ class MMatrixInterface {
   virtual void set(int i, float value);
   // Stores a value at the given indicies. Each index must be within it's
   // dimension defined by shape().
-  virtual void set(const std::vector<int>& indices, float value) = 0;
+  virtual void set(const std::vector<int>& indices, float value);
   // Returns the shape (size of dimensions) of this matrix.
   virtual const std::vector<int>& shape() const = 0;
   // Returns the most generic type "::mmatrix::MMatrixInterface" by default.
-  virtual const Type* type() const;
+  virtual const internal::Type* type() const;
  private:
-  const static Type type_;
+  const static internal::Type type_;
 };
 
 class DenseMMatrix : public MMatrixInterface {
@@ -46,15 +57,34 @@ class DenseMMatrix : public MMatrixInterface {
   DenseMMatrix(const std::vector<int>& shape);
   ~DenseMMatrix() = default;
 
+  using MMatrixInterface::get;
+  using MMatrixInterface::set;
   float get(int i) const override;
[…]

### 2019-05-20 MMatrix/mmatrix.cc
Moving the multimatrix library into it's own folder.

@@ -158,6 +158,54 @@ void Multiply(int n, const MMatrixInterface* a, const MMatrixInterface* b,
   }
 }
 
+void Multiply(int n, const SparseMMatrix* a, const SparseMMatrix* b,
+    MMatrixInterface* out) {
+  if (a == nullptr || b == nullptr || out == nullptr) {
+    throw std::invalid_argument("Multiply cannot take null arguments.");
+  }
+  // ||a|| = l + n
+  // ||b|| = n + r
+  int l = a->shape().size()-n;
+  int r = b->shape().size()-n;
+  if (l < 0 || r < 0) {
+    throw std::out_of_range("Invalid multiplication size");
+  }
+  int midBound = 1;
+  for (int i = 0; i < n; i++) {
+    if (a->shape()[l+i] != b->shape()[i]) {
+      throw std::out_of_range("Invalid multiplication shapes.");
+    }
+    midBound *= b->shape()[i];
+  }
+  int lBound  = 1;
+  for (int i = 0; i < l; i++) {
+    if (a->shape()[i] != out->shape()[i]) {
+      throw std::out_of_range("Invalid left output multiplication shape.");
+    }
+    lBound *= a->shape()[i];
+  }
+  int rBound = 1;
+  for (int i = 0; i < r; i++) {
+    if (b->shape()[n+i] != out->shape()[l+i]) {
+      throw std::out_of_range("Invalid right output multiplication shape.");
+    }
+    rBound *= b->shape()[n+i];
+  }
+  // TODO: take advantage of sparse multiplication
+  for (int vl = 0; vl < lBound; vl++) {
+    for (int vr = 0; vr < rBound; vr++) {
+      float sum = 0;
+      for (int vm = 0; vm < midBound; vm++) {
+        int va = vl+vm*lBound;
+        int vb = vm+vr*midBound;
+        sum += a->get(va)*b->get(vb);
+      }
+      int vo = vl+vr*lBound;
+      out->set(vo, sum);
+    }
+  }
+}
+
 bool AreEqual(const MMatrixInterface* a, const MMatrixInterface* b, float epsilon) {
   if (a == nullptr || b == nullptr) {
     throw std::invalid_argument("AreEqual cannot take null arguments.");

### 2019-05-20 MMatrix/mmatrix.h

@@ -1,9 +1,9 @@
 #ifndef MMATRIX_H
 #define MMATRIX_H
 
+#include <map>
 #include <memory>
 #include <string>
-#include <unordered_map>
 #include <unordered_set>
 #include <vector>
 
@@ -80,9 +80,17 @@ class SparseMMatrix : public MMatrixInterface {
   const std::vector<int>& shape() const override;
 
   const internal::Type* type() const override;
+
+  std::map<int, float>::iterator begin() { return values_.begin(); }
+  std::map<int, float>::iterator end() { return values_.end(); }
+  std::map<int, float>::const_iterator cbegin() { return values_.cbegin(); }
+  std::map<int, float>::const_iterator cend() { return values_.cend(); }
+  std::map<int, float>::const_iterator begin() const { return values_.cbegin(); }
+  std::map<int, float>::const_iterator end() const { return values_.cend(); }
  private:
   // Maps the value index to non-zero values.
-  std::unordered_map<int, float> values_;
+  std::map<int, float> values_;
+
   std::vector<int> shape_;
   const static internal::Type type_;
 };
@@ -93,6 +101,9 @@ void FromValueIndex(const std::vector<int>& shape, int vindex,
 
 void Multiply(int n, const MMatrixInterface* a,
   const MMatrixInterface* b, MMatrixInterface* out);
+
+void Multiply(int n, const SparseMMatrix* a, const SparseMMatrix* b,
+  MMatrixInterface* out);
 
 // Throws an error when matricies aren't even the same shape.
 // Epsilon is an optional small positive value under which differences are

### 2019-05-21 Math/paper.tex
Proving distributive properties.

@@
 \usepackage{pdflscape}
+\usepackage{etoolbox}
 
@@
 \newtheorem{corollary}{Corollary}[theorem]
-
-\newtheoremstyle{case}{}{}{}{}{}{:}{ }{}
-\theoremstyle{case}
-\newtheorem{case}{Case}
+\newtheorem{lemma}[theorem]{Lemma}
 
@@
 \newtheorem{ppart}{Part}
+\AtBeginEnvironment{proof}{\setcounter{ppart}{0}}
 
@@
 \begin{definition}[Multimatrix Identities]
-\label{mm_ident}
+\label{mm_mult_ident}
 Let us define $\Ident^n(\vec{v})$ as the $n^{\text{th}}$ order identity with base shape
@@
 \begin{theorem}[Multimatrix Multiplicative Identity]
+\label{mm_ident}
 For all $\vec{m}$ and $\vec{n}$ on which the operations are valid,
@@
 
+Multimatrix identities also tend to cancel eachother out when multiplied by
+multiples of their base shape lengths.
+
+\begin{landscape}
 \begin{theorem}[Identity Contraction]
@@
 \begin{proof}
-TODO
-\end{proof}
-
-\begin{theorem}[Communicative Identity Multiplication]
-\[ \Ident^n(\vec{x}) \mmult{k|\vec{x}|} A = A \mmult{k|\vec{x}|} \Ident^n(\vec{x}) \]
-\end{theorem}
-\begin{proof}
-TODO
-\end{proof}
+Consider that for some indicies
+$\{\bar{a_1}, \bar{a_2}, \ldots \bar{a}_{m-k}\}$
+and $\{\bar{b_1}, \bar{b_2}, \ldots \bar{b}_{n-k}\}$ where each
+$\bar{a_i} \in \Dim(\vec{x})$ and each $\bar{b_i} \in \Dim(\vec{x})$,
+
+\begin{align*}
+&\left( \Ident^m(\vec{x}) \mmult{k|\vec{x}|} \Ident^n(\vec{x}) \right)
+[\bar{a_1} \oplus \bar{a_2} \oplus \ldots \bar{b_1} \oplus \bar{b_2} \oplus \ldots] = \\
+&\sum_{\forall \bar{c_1}, \bar{c_2}, \ldots \bar{c_k} \in \Dim(\vec{x})}
+\Ident^m(\vec{x})
+[\bar{a_1} \oplus \bar{a_2} \oplus \ldots \bar{c_1} \oplus \bar{c_2} \oplus \ldots]
+\Ident^n(\vec{x})
+[\bar{c_1} \oplus \bar{c_2} \oplus \ldots \bar{b_1} \oplus \bar{b_2} \oplus \ldots]
+\end{align*}
+
+Consider that $\Ident^m(\vec{x})
+[\bar{a_1} \oplus \bar{a_2} \oplus \ldots \bar{c_1} \oplus \bar{c_2} \oplus \ldots]$
+will be 0 whenever the any $\bar{c_i} \ne \bar{c_j}$ - we can simplify that to all
+the same $c$.
+
+\begin{align*}
+&\left( \Ident^m(\vec{x}) \mmult{k|\vec{x}|} \Ident^n(\vec{x}) \right)
+[\bar{a_1} \oplus \bar{a_2} \oplus \ldots \bar{b_1} \oplus \bar{b_2} \oplus \ldots] = \\
+&\sum_{\forall \bar{c} \in \Dim(\vec{x})}
+\Ident^m(\vec{x})
+[\bar{a_1} \oplus \bar{a_2} \oplus \ldots \bar{c} \oplus \bar{c} \oplus \ldots]
+\Ident^n(\vec{x})
+[\bar{c} \oplus \bar{c} \oplus \ldots \bar{b_1} \oplus \bar{b_2} \oplus \ldots]
+\end{align*}
+
+Consider also that there can be at most one $\bar{c}$ for which
+$\bar{c} = \bar{a_1} = \bar{a_2} \ldots$. And since our right hand side is
+the sum of products of ones and zeros, we can therefore conclude it is either 1 or 0.
+
+We can futher reason that the right hand side can only be one when all of the
+$\bar{a_i}$ and all of the $\bar{b_i}$ equal $\bar{c}$. Furthermore, if all
+$\bar{a_i}$ and all $\bar{b_i}$ are equal then that $\bar{c}$ must exist since it can
+be any value in the range of all $\bar{a_i}$ and $\bar{b_i}$ and this is not a
+zero width multiplication ($k >= 1$). Therefore,
+
+\begin{align*}
+\left( \Ident^m(\vec{x}) \mmult{k|\vec{x}|} \Ident^n(\vec{x}) \right)
+[\bar{a_1} \oplus \bar{a_2} \oplus \ldots \bar{b_1} \oplus \bar{b_2} \oplus \ldots] =
+\left\{
+  \begin{array}{ll}
+    1 & \mbox{if } \bar{a_1} = \bar{a_2} = \ldots = \bar{b_1} = \bar{b_2} = \ldots \\
+    0 & \mbox{otherwise}
+  \end{array}
+\right.
+\end{align*}
+
+Which is an identity matrix! And since the dimensional rules of multimatrix 
+multiplication show that,
+
+\[
+ \left|\left| \Ident^m(\vec{x}) \mmult{k|\vec{x}|} \Ident^n(\vec{x}) \right|\right|
+ =
+ ||\Ident^m(\vec{x})|| + ||\Ident^n(\vec{x})|| - 2k|\vec{x}|
+\]
+
+We've shown that,
+
+\[ \Ident^m(\vec{x}) \mmult{k|\vec{x}|} \Ident^n(\vec{x}) = \Ident^{m+n-2k}(\vec{x}) \]
+\end{proof}
+\end{landscape}
 
@@
 \begin{definition}[Multimatrix Scalar Multiplication]
-\[ sA = ...\]
+Let $s \in \mathbb{R}$ and $A, B \in \mathbb{R}^{\vec{x}}$. If
+\[ sA = As = B \]
+Then
+\[ \forall \bar{x} \in \Dim(\vec{x}):
+   B[\bar{x}] = (s)(A[\bar{x}]) \]
+In other words, multiplying $A$ by a scalar $s$ simply multiplies each of
+it's elements by that scalar.
 \end{definition}
@@
 \begin{definition}[Multimatrix Addition]
-Bla
+Let $A, B, C \in \mathbb{R}^{\vec{x}}$. If
 \[ A + B = C \]
+Then
+\[ \forall \bar{x} \in \Dim(\vec{x}):
+   C[\bar{x}] = A[\bar{x}] + B[\bar{x}] \]
+In other words, adding two multimatricies (which must be of the same shape) results
+in a multimatrix of the same shape with elements which are the sum of the corresponding
+elements of the added multimatricies.
 \end{definition}
 
-\begin{definition}[Multimatrix Subtractin]
+\begin{definition}[Multimatrix Subtraction]
+Let $A, B \in \mathbb{R}^{\vec{x}}$. Then,
 \[ A - B = A + (-1)B \]
+It should be obvious that, as with scalars, multimatrix subtraction is the
+inverse of addition. In other words, $(A + B) - B = A$
 \end{definition}
 
+As with scalar, vector, or regular matrix addition, multimatrix addition is
+communicative. 
 \begin{theorem}[Communicative Property of Multimatrix Addition]
-Bla
+Let $A, B \in \mathbb{R}^{\vec{x}}$. Then,
 \[ A + B = B + A \]
@@
 \begin{proof}
-TODO
-\end{proof}
+Let $C = A + B$ then,
+\[ \forall \bar{x} \in \Dim(\vec{x}) : C[\bar{x}] = A[\bar{x}] + B[\bar{x}] \]
+By standard scalar addition rules that also means that,
+$C[\bar{x}] = B[\bar{x}] + A[\bar{x}]$. So $C = B + A = A + B$.
+\end{proof}
+
+It's similarly trial to show that multimatrix addition is associative.
 
 \begin{theorem}[Associative Property of Multimatrix Addition]
+Let $A, B, C \in \mathbb{R}^{\vec{x}}$. Then,
 \[ (A + B) + C = A + (B + C) \]
@@
 \begin{proof}
-TODO
-\end{proof}
-
+For all $\bar{x} \in \Dim(\vec{x})$,
+\begin{align*}
+\left( (A+B)+C \right)[\bar{x}]
+&= (A[\bar{x}]+B[\bar{x}])+C[\bar{x}] \\
+&= A[\bar{x}]+(B[\bar{x}]+C[\bar{x}]) \\
+&= \left( A+(B+C) \right)[\bar{x}]
+\end{align*}
+\end{proof}
+
+A little less obvious is that multimatrix multiplication can be distributed over
+it's addition.
+
+\begin{landscape}
 \begin{theorem}[Multimatrix on Multimatrix Distributive Property]
+If $|A| = \vec{a} \oplus \vec{n}$ and $|B|=|C|=\vec{n} \oplus \vec{r}$ then,
 \[ A \mmult{n} (B + C) = A \mmult{n} B + A \mmult{n} C \]
-\end{theorem}
-\begin{proof}
-TODO
-\end{proof}
-
+Similarly, if $|C| = \vec{n} \oplus \vec{c}$ and $|A|=|B|=\vec{l} \oplus \vec{n}$ then,
+\[ (A + B) \mmult{n} C = A \mmult{n} C + B \mmult{n} C \]
+\end{theorem}
+\begin{proof}
+\begin{ppart}
+Let $|A| = \vec{a} \oplus \vec{n}$ and $|B|=|C|=\vec{n} \oplus \vec{r}$.
+So, $\forall \bar{a} \in \Dim(\vec{a}), \bar{r} \in \Dim(\vec{r}) :$
+\begin{align*}
+ \left( A \mmult{n} (B + C) \right)[\bar{a} \oplus \bar{r}]
+ &= \sum_{\forall \bar{n} \in \Dim(\vec{n})}
+    A[\bar{a} \oplus \bar{n}] (B + C)[\bar{n} \oplus \bar{r}] \\
+ &= \sum_{\forall \bar{n} \in \Dim(\vec{n})}
+    A[\bar{a} \oplus \bar{n}] (B[\bar{n} \oplus \bar{r}] + C[\bar{n} \oplus \bar{r}]) \\
+ &= \sum_{\forall \bar{n} \in \Dim(\vec{n})}
+    A[\bar{a} \oplus \bar{n}] B[\bar{n} \oplus \bar{r}]
+  + A[\bar{a} \oplus \bar{n}]C[\bar{n} \oplus \bar{r}] \\
+ &= \left( \sum_{\forall \bar{n} \in \Dim(\vec{n})}
+    A[\bar{a} \oplus \bar{n}] B[\bar{n} \oplus \bar{r}] \right)
+    +
+    \left( \sum_{\forall \bar{n} \in \Dim(\vec{n})}
+    A[\bar{a} \oplus \bar{n}]C[\bar{n} \oplus \bar{r}] \right) \\
+ &= \left( A \mmult{n} B \right)[\bar{a} \oplus \bar{r}] +
+     \left( A \mmult{n} C \right)[\bar{a} \oplus \bar{r}]
+\end{align*}
+So $A \mmult{n} (B + C) = A \mmult{n} B + A \mmult{n} C$
+\end{ppart}
+\begin{ppart}
+Let $|C| = \vec{n} \oplus \vec{c}$ and $|A|=|B|=\vec{l} \oplus \vec{n}$.
+So, $\forall \bar{c} \in \Dim(\vec{c}), \bar{l} \in \Dim(\vec{l}) :$
+\begin{align*}
+ \left( (A + B) \mmult{n} C \right)[\bar{l} \oplus \bar{c}]
+ &= \sum_{\forall \bar{n} \in \Dim(\vec{n})}
+    (A+B)[\bar{l} \oplus \bar{n}] C[\bar{n} \oplus \bar{c}] \\
+ &= \sum_{\forall \bar{n} \in \Dim(\vec{n})}
+    (A[\bar{l} \oplus \bar{n}]+B[\bar{l} \oplus \bar{n}])C[\bar{n} \oplus \bar{c}] \\
+ &= \sum_{\forall \bar{n} \in \Dim(\vec{n})}
+    A[\bar{l} \oplus \bar{n}]C[\bar{n} \oplus \bar{c}]
+    +B[\bar{l} \oplus \bar{n}]C[\bar{n} \oplus \bar{c}] \\
+ &= \left(\sum_{\forall \bar{n} \in \Dim(\vec{n})}
+    A[\bar{l} \oplus \bar{n}]C[\bar{n} \oplus \bar{c}]\right)
+    +
+    \left(\sum_{\forall \bar{n} \in \Dim(\vec{n})}
+    B[\bar{l} \oplus \bar{n}]C[\bar{n} \oplus \bar{c}]\right) \\
+ &= \left(A \mmult{n} C\right)[\bar{l} \oplus \bar{c}]
+    +\left(B \mmult{n} C\right)[\bar{l} \oplus \bar{c}]
+\end{align*}
+So $(A+B) \mmult{n} C = A \mmult{n} C + B \mmult{n} C$ 
+\end{ppart}
+\end{proof}
+\end{landscape}
+
+But it should be obvious that that the same applies to scalar 
+multiplication distributing over multimatrix addition..
 \begin{theorem}[Scalar on Multimatrix Distributive Property]
+If $s \in \mathbb{R}$ and $A, B \in \mathbb{R}^{\vec{x}}$ then,
 \[ s(A + B) = sA + sB \]
@@
 \begin{proof}
-TODO
+Let $s \in \mathbb{R}$ and $A, B \in \mathbb{R}^{\vec{x}}$.
+Then for all $\bar{x} \in \Dim(\vec{x})$
+\begin{align*}
+(s(A+B))[\bar{x}]
+&= (s)((A+B)[\bar{x}]) \\
+&= (s)(A[\bar{x}] + B[\bar{x}]) \\
+&= (s)(A[\bar{x}]) + s(B[\bar{x}])
+\end{align*}
+Therefore $s(A+B) = sA + sB$
 \end{proof}
@@
 \end{align*}
+Which each become,
 \begin{align*}
@@
 Therefore 
-\[
+\begin{alignat*}{3}
  \frac{d\left(F(X) \mmult{|\vec{c}|} G(X)\right)}{dX}
   [\bar{f} \oplus \bar{g} \oplus \bar{x}]
-\]
-\begin{align*}
-	=& 
+  &=&&
   \left( F(X) \mmult{|\vec{c}|} \frac{dG(X)}{dX} \right)
   [\bar{f} \oplus \bar{g} \oplus \bar{x}] \\
-	&+
+  &&&+
   \Tran\left(
@@
   \right)[\bar{f} \oplus \bar{g} \oplus \bar{x}] \\
-\end{align*}
-\[
-	=
+  &=&&
   \left\{
-		\left( F(X) \mmult{|\vec{c}|} \frac{dG(X)}{dX} \right)
+    \begin{array}{l}
+      \left( F(X) \mmult{|\vec{c}|} \frac{dG(X)}{dX} \right) \\
       +
@@
       \right)
+    \end{array}
   \right\}
   [\bar{f} \oplus \bar{g} \oplus \bar{x}]
-\]
+\end{alignat*}
 \end{proof}

### 2019-05-27 Math/paper.tex
Finished proving all transposition theorems.

@@
 
+\begin{theorem}[Inverse Transpose]
+If $|X| = \vec{l} \oplus \vec{r}$
+\[ \Tran(\Tran(X, |\vec{l}|), |\vec{r}|) = X \]
+\end{theorem}
+\begin{proof}
+Let $|X| = \vec{l} \oplus \vec{r}$ then
+$\forall \bar{l} \in \Dim(\vec{l}), \bar{r} \in \Dim(\vec{r}) : $
+\[ \Tran(X, |\vec{l}|)[\bar{r} \oplus \bar{l}] = X[\bar{l} \oplus \bar{r}] \]
+And so,
+\begin{align*}
+	\Tran(\Tran(X, |\vec{l}|), |\vec{r}|)[\bar{l} \oplus \bar{r}]
+	&= \Tran(X, |\vec{l}|)[\bar{r} \oplus \bar{l}] \\
+	&= X[\bar{l} \oplus \bar{r}] \\
+\end{align*}
+Therefore, 
+\[ \Tran(\Tran(X, |\vec{l}|), |\vec{r}|) = X \]
+\end{proof}
+
+\begin{theorem}[Identity Transpose]
+\[ \Tran(\Ident^n(\vec{x}), k|\vec{x}|) = \Ident^n(\vec{x}) \]
+\end{theorem}
+\begin{proof}
+Consider that for some ordered set of indicies
+$\{\bar{x}_1, \bar{x}_2, \ldots \bar{x}_n\} = X$ such that each
+$\bar{x}_i \in X \implies \bar{x}_i \in \Dim(\vec{x})$.
+Let $X'$ be some ordered permutation of $X$, then we can reason that,
+\begin{align*}
+ \Ident^n(\vec{x})\left[\bigoplus X'\right]
+ &= 
+	\left\{
+  \begin{array}{ll}
+    1 & \mbox{if all } \bar{x}_i \in X' \mbox{ are equal.}\\
+    0 & \mbox{otherwise}
+  \end{array}
+	\right.\\
+ &= 
+	\left\{
+  \begin{array}{ll}
+    1 & \mbox{if all } \bar{x}_i \in X \mbox{ are equal.}\\
+    0 & \mbox{otherwise}
+  \end{array}
+	\right.\\
+ &=\Ident^n(\vec{n})\left[\bigoplus X\right]
+\end{align*}
+Since for
+$X' = \left\{\bar{x}_{k+1}, \bar{x}_{k+2} \ldots \bar{x}_{n},
+\bar{x}_1, \bar{x}_2 \ldots \bar{x}_k\right\}$
+\begin{align*}
+  \Tran(\Ident^n(\vec{x}), k|\vec{x}|)\left[\bigoplus X'\right]
+	&=
+  \Ident^n(\vec{x})\left[\bigoplus X\right]\\
+	&=
+  \Ident^n(\vec{x})\left[\bigoplus X'\right]
+\end{align*}
+Therefore
+$\Tran(\Ident^n(\vec{x}), k|\vec{x}|) = \Ident^n(\vec{x})$
+\end{proof}
+
+\begin{theorem}[Transposition of Multimatrix Multiplication]
+\label{mm_tran_mult}
+Let $|A| = \vec{a} \oplus \vec{c}$ and $|B| = \vec{c} \oplus \vec{b}$ then
+\[
+ \Tran(A \mmult{|\vec{c}|} B, |\vec{a}|)
+ =  \Tran(B, |\vec{c}|) \mmult{|\vec{c}|} \Tran(A, |\vec{a}|)
+\]
+\end{theorem}
+\begin{proof}
+Let $\bar{a} \in \Dim(\vec{a})$ and $\bar{b} \in \Dim(\vec{b})$.
+Then,
+\begin{align*}
+	\Tran(A \mmult{|\vec{c}|} B, |\vec{a}|)[\bar{b} \oplus \bar{a}]
+	&=
+	\left(A \mmult{|\vec{c}|} B \right)[\bar{a} \oplus \bar{b}] \\
+	&=
+	\sum_{\forall \bar{c} \in \Dim(\vec{c})}
+	A[\bar{a} \oplus \bar{c}] B[\bar{c} \oplus \bar{b}] \\
+	&=
+	\sum_{\forall \bar{c} \in \Dim(\vec{c})}
+	B[\bar{c} \oplus \bar{b}] A[\bar{a} \oplus \bar{c}] \\
+	&=
+	\sum_{\forall \bar{c} \in \Dim(\vec{c})}
+	\Tran(B, |\vec{c}|)[\bar{b} \oplus \bar{c}]
+	\Tran(A, |\vec{a}|)[\bar{c} \oplus \bar{a}] \\
+	&=
+	\left(\Tran(B, |\vec{c}|) \mmult{|\vec{c}|} \Tran(A, |\vec{a}|) \right)
+	[\bar{b} \oplus \bar{a}]
+\end{align*}
+\end{proof}
+
 \subsection*{Sample Problems}
@@
 
-\begin{theorem}[Right Multiplicative Derivative]
-\[ \frac{d(A \mmult{n} X)}{dX} = A \mmult{n} \Ident^2(|X|) \]
-\end{theorem}
-\begin{proof}
-TODO
-\end{proof}
-
-\begin{theorem}[Left Multiplicative Derivative]
-\[ \frac{d(X \mmult{n} A)}{dX} = \Ident^2(|X \mmult{n} A|) \mmult{n} \Tran(A, n) \]
-\end{theorem}
-\begin{proof}
-TODO
-\end{proof}
-
 \begin{theorem}[Transpose Derivative]
+\label{tran_derivative}
 $|X| = \vec{l} \oplus \vec{r}$
@@
 \end{proof}
+
+\begin{theorem}[Right Multiplicative Derivative]
+\label{right_mult_derivative}
+\[ \frac{d(A \mmult{n} X)}{dX} = A \mmult{n} \Ident^2(|X|) \]
+\end{theorem}
+\begin{proof}
+TODO
+\end{proof}
+
+\begin{landscape}
+\begin{theorem}[Left Multiplicative Derivative]
+\label{left_mult_derivative}
+\[ \frac{d(X \mmult{n} A)}{dX} = \Ident^2(|X \mmult{n} A|) \mmult{n} \Tran(A, n) \]
+\end{theorem}
+\begin{proof}
+Let $|X| = \vec{x} \oplus \vec{n}$ and $|A| = \vec{n} \oplus \vec{a}$. Then,
+for all
+$\bar{x}_1, \bar{x}_2 \in \Dim(\vec{x}), \bar{a}_1 \in \Dim(\vec{a}),
+\bar{n}_1 \in \Dim(\vec{n}):$
+\begin{align*}
+	\frac{d(X \mmult{n} A)}{dX}
+	[\bar{x}_1 \oplus \bar{a}_1 \oplus \bar{x}_2 \oplus \bar{n}_1]
+	&= 
+	\frac{
+		\partial (X \mmult{n} A) [\bar{x}_1 \oplus \bar{a}_1]
+	}{\partial X[\bar{x}_2 \oplus \bar{n}_1]} \\
+	&= 
+	\frac{
+		\partial \left(
+			\sum_{\forall \bar{n}_2 \in \Dim(\vec{n})}
+			X[\bar{x}_1 \oplus \bar{n}_2] A[\bar{n}_2 \oplus \bar{a}_1]
+		\right)
+	}{\partial X[\bar{x}_2 \oplus \bar{n}_1]} \\
+	&= 
+	\sum_{\forall \bar{n}_2 \in \Dim(\vec{n})}
+	\frac{
+		\partial \left(
+			X[\bar{x}_1 \oplus \bar{n}_2] A[\bar{n}_2 \oplus \bar{a}_1]
+		\right)
+	}{\partial X[\bar{x}_2 \oplus \bar{n}_1]} \\
+	&= 
+	\sum_{\forall \bar{n}_2 \in \Dim(\vec{n})}
+	\delta_{\bar{x}_1\bar{x}_2}
+	\delta_{\bar{n}_1\bar{n}_2}
+	A[\bar{n}_2 \oplus \bar{a}_1] \\
+	&= 
+	\delta_{\bar{x}_1\bar{x}_2}
+	A[\bar{n}_1 \oplus \bar{a}_1]
+\end{align*}
+We can also show that,
+\begin{align*}
+	\left(\Ident^2(|X \mmult{n} A|) \mmult{n} \Tran(A, n)\right)
+	[\bar{x}_1 \oplus \bar{a}_1 \oplus \bar{x}_2 \oplus \bar{n}_1]
+	&=
+	\sum_{\forall \bar{a}_2 \in \Dim(\vec{a}_1)}
+	\Ident^2(|X \mmult{n} A|)[\bar{x}_1 \oplus \bar{a}_1 \oplus \bar{x}_2 \oplus \bar{a}_2]
+	\Tran(A, n)[\bar{a}_2 \oplus \bar{n}_1] \\
+	&=
+	\sum_{\forall \bar{a}_2 \in \Dim(\vec{a})}
+	\delta_{\bar{x}_1 \bar{x}_2} \delta_{\bar{a}_1 \bar{a}_2}
+	\Tran(A, n)[\bar{a}_2 \oplus \bar{n}_1] \\
+	&=
+	\sum_{\forall \bar{a}_2 \in \Dim(\vec{a})}
+	\delta_{\bar{x}_1 \bar{x}_2} \delta_{\bar{a}_1 \bar{a}_2}
+	A[\bar{n}_1 \oplus \bar{a}_2] \\
+	&=
+	\delta_{\bar{x}_1 \bar{x}_2}
+	A[\bar{n}_1 \oplus \bar{a}_1]
+\end{align*}
+Then since,
+\[
+	\frac{d(X \mmult{n} A)}{dX}
+	[\bar{x}_1 \oplus \bar{a}_1 \oplus \bar{x}_2 \oplus \bar{n}_1]
+	=
+	\left(\Ident^2(|X \mmult{n} A|) \mmult{n} \Tran(A, n)\right)
+	[\bar{x}_1 \oplus \bar{a}_1 \oplus \bar{x}_2 \oplus \bar{n}_1]
+\]
+we have shown that,
+\[
+	\frac{d(X \mmult{n} A)}{dX}
+	=
+	\Ident^2(|X \mmult{n} A|) \mmult{n} \Tran(A, n)
+\]
+\end{proof}
+\end{landscape}
 
@@
 At this point I'm fairly stuck.
-\end{proof}
+
+Ok, lets think of this in another way. Is this true?
+\[
+	\lim_{\epsilon \to 0}
+	\frac{
+		G(X+\epsilon H) - G(X)
+	}{\epsilon}
+	=
+	F(X) \mmult{||X||} H
+\]
+Where $SS(H) = 1$. More specifically, $H = \frac{X-A}{\sqrt{SS(X-A)}}$
+
+\begin{align*}
+\lim_{\epsilon \to 0}
+\frac{
+	G(X+\epsilon H) - G(X)
+}{\epsilon}
+&= 
+\lim_{\epsilon \to 0}
+\frac{
+	\left( \int_A^{X+\epsilon H} F(Y) dY \right) - \left( \int_A^X F(Y) dY \right)
+}{\epsilon} \\
+&= 
+\lim_{\epsilon \to 0}
+\frac{
+	\int_X^{X+\epsilon H} F(Y) dY
+}{\epsilon}
+\end{align*}
+\end{proof}
+
 \end{landscape}

### 2019-06-04 Math/paper.tex
Adding some additional theories.

@@
 \AtBeginEnvironment{proof}{\setcounter{ppart}{0}}
+\AtBeginEnvironment{align}{\setcounter{equation}{0}}
+\AtBeginEnvironment{alignat}{\setcounter{equation}{0}}
 
@@
 \DeclareMathOperator{\Tran}{Tran}
+\DeclareMathOperator{\SoS}{\mathbb{S}}
+\DeclareMathOperator{\Softmax}{Softmax}
+\DeclareMathOperator{\Sum}{\Sigma}
 %\newcommand{\mmult}[1]{\stackrel{\times}{#1}}
@@
 \end{abstract}
+
+\newpage
+
+\tableofcontents
+
+\newpage
 
@@
 
+A final useful theorem happens to involve 0 overlap multiplication, which seams at first
+nonsensical given our definition of multiplication,
+but if you notice that the each element of a
+multiplication result is the sum over every index in the dimensionality of the
+portion of the shape vector of that overlapping length, and you consider that every
+vector could be said to 'start' and 'end' with an empty vector (as the concatenation of
+an empty vector does not change the vector), then it makes sense that this zero-length
+overlap always exists and is one and only one vector. That is, $\{\}$.
+
+\begin{theorem}[Zero Overlap Multiplication]
+So if $|A| = \vec{a}$ and $|B| = \vec{b}$, for every $\bar{a} \in \Dim(\vec{a})$
+and $\bar{b} \in \Dim(\vec{b}):$
+
+\[ (A \mmult{0} B)[\bar{a} \oplus \bar{b}] = A[\bar{a}] B[\bar{b}] \]
+\end{theorem}
+
 \subsection*{Sample Problems}
@@
 Other operations include...
+
+\subsection{Scalars}
 
@@
 \end{definition}
+
+Note that by our definitions of scalar and multimatrix derivatives and multiplication,
+we can model scalars in either case as multimatricies with shape $\{\}$.
+
+\begin{theorem}[Empty Shape Multimatrix and Scalar Multiplication Equivalence]
+\label{s_mm_mult_equiv}
+For any multiplication operation defined between multimatricies and scalars,
+the scalar may be replaced by an equivalent empty-shaped multimatrix who's
+single value is that of the scalar.
+
+In other words, let $s \in \mathbb{R}$ and $S \in \mathbb{R}^{\{\}}$ such that
+$S[\{\}] = s$. Then, for any multimatrix $A$, 
+\[ sA = As = S \mmult{0} A = A \mmult{0} S \]
+\end{theorem}
+\begin{proof}
+Let $|A| = \vec{a}$. Then for all $\bar{a} \in \Dim(\vec{a})$,
+\begin{align*}
+	(sA)[\bar{a}]
+	&= (s)A[\bar{a}] \\
+	&= A[\bar{a}](s) \\
+	&= (As)[\bar{a}]
+\end{align*}
+So $sA = As$. Also,
+\begin{align}
+	(sA)[\bar{a}]
+	&= (s)A[\bar{a}] \\
+	&= S[\{\}]A[\bar{a}] \\
+	&= \sum_{\forall \bar{c} \in \Dim(\{\})}
+		S[\{\} \oplus \bar{c}]A[\bar{c} \oplus \bar{a}] \\
+	&= (S \mmult{0} A)[\{\} \oplus \bar{a}] \\
+	&= (S \mmult{0} A)[\bar{a}] \\
+\end{align}
+Note that step 3 is valid because $\bar{c}$ can only be $\{\}$ and
+$\{\} \oplus \bar{a} = \bar{a}$. So, $sA = S \mmult{0} A$.
+Finally, by similiar reasoning,
+\begin{align*}
+	(sA)[\bar{a}]
+	&= (s)A[\bar{a}] \\
+	&= A[\bar{a}](s) \\
+	&= A[\bar{a}]S[\{\}] \\
+	&= \sum_{\forall \bar{c} \in \Dim(\{\})}
+		A[\bar{a} \oplus \bar{c}] S[\bar{c} \oplus \{\}] \\
+	&= (A \mmult{0} S)[\bar{a} \oplus \{\}] \\
+	&= (A \mmult{0} S)[\bar{a}]
+\end{align*}
+So $sA = A \mmult{0} S$. Therefore we've shown that
+$sA = As = S \mmult{0} A = A \mmult{0} S$
+\end{proof}
+
+Noticing this lead me to suspect that the same might be true of my definitions
+of the derivative rules. A quick check confirmed that the dimensionality
+worked out, and it seems intuitive that we would always be able to treat scalars
+as empty-shape multimatricies if multiplication workes, but let's formalize that
+assertion.
+
+\begin{theorem}[Empty Shape Multimatrix and Scalar Domain Derivative Equivalence]
+\label{s_mm_domain_equiv}
+Let $F(x)$ be a function $F : \mathbb{R} \to \mathbb{R}^{\vec{f}}$. And let
+$G(X)$ be an equivalent function, $G : \mathbb{R}^{\{\}} \to \mathbb{R}^{\vec{f}}$
+such that for all $X \in \mathbb{R}^{\{\}}$ it is true that $G(X) = F(X[\{\}])$
+Then,
+\[ \frac{dF(x)}{dx} = \frac{dG(X)}{dX} \]
+\end{theorem}
+\begin{proof}
+TODO
+\end{proof}
+
+\begin{theorem}[Empty Shape Multimatrix and Scalar Range Derivative Equivalence]
+\label{s_mm_range_equiv}
+Let $f(X)$ be a function $f : \mathbb{R}^{\vec{x}} \to \mathbb{R}$. And let
+$F(X)$ be an equivalent function, $F : \mathbb{R}^{\vec{x}} \to \mathbb{R}^{\{\}}$
+such that for all $X \in \mathbb{R}^{\vec{x}}$ it is true that $F(X)[\{\}] = f(X)$
+Then,
+\[ \frac{df(X)}{dX} = \frac{dF(X)}{dX} \]
+\end{theorem}
+\begin{proof}
+TODO
+\end{proof}
 
@@
 
+\begin{theorem}[Communicativity of scalar Multiplication and Transposition]
+\[ s\Tran(A, x) = \Tran(sA, x) \]
+\end{theorem}
+\begin{proof}
+TODO
+\end{proof}
+
+\begin{theorem}[Stacked Transposition]
+\[ \Tran(\Tran(A, x), y) = \Tran(A, x+y) \]
+\end{theorem}
+\begin{proof}
+TODO
+\end{proof}
+
 \subsection*{Sample Problems}
@@
 
-\section{Derivative Rules}
+\section{Generic Derivative Rules}
 
@@
 \begin{proof}
-TODO
-\end{proof}
-
+Let $|F(X)| = |G(X)| = \vec{f}$ and $|X| = \vec{x}$. Then,
+$\forall \bar{f} \in \Dim(\vec{f}), \bar{x} \in \Dim(\vec{x}):$
+\begin{align*}
+	\frac{d(F(X) + G(X))}{dX}[\bar{f} \oplus \bar{x}]
+	&=
+	\frac{\partial (F(X) + G(X))[\bar{f}]}{\partial X[\bar{x}]} \\
+	&=
+	\frac{\partial (F(X)[\bar{f}] + G(X)[\bar{f}])}{\partial X[\bar{x}]} \\
+	&=
+	\frac{\partial F(X)[\bar{f}]}{\partial X[\bar{x}]} +
+	\frac{\partial G(X)[\bar{f}]}{\partial X[\bar{x}]} \\
+	&=
+	\frac{dF(X)}{dX}[\bar{f} \oplus \bar{x}]+
+	\frac{dG(X)}{dX}[\bar{f} \oplus \bar{x}]
+\end{align*}
+So $d(F(X) + G(X))/dX = dF(X)/dX + dG(X)/dX$
+\end{proof}
+
+A rule for derivatives involving scalar multiplication also seems generally
+useful. Of course, by the Theorem \ref{s_mm_mult_equiv}, this is just a very specific
+case of Theorem \ref{right_mult_derivative} but the proof is simple and worth
+the additional ink, I think,
 \begin{theorem}[Scalar Multiplication Rule]
@@
 \begin{proof}
-TODO
+Let $|F(X)| = \vec{f}$ and $|X| = \vec{x}$. Then
+$\forall \bar{f} \in \Dim(\vec{f}), \bar{x} \in \Dim(\vec{x}):$
+\begin{align*}
+	\frac{d(sF(X))}{dX}[\bar{f} \oplus \bar{x}]
+	&=
+	\frac{\partial (sF(X))[\bar{f}]}{\partial X[\bar{x}]} \\
+	&=
+	\frac{\partial (s)(F(X)[\bar{f}])}{\partial X[\bar{x}]} \\
+	&=
+	s\frac{\partial F(X)[\bar{f}]}{\partial X[\bar{x}]} \\
+	&=
+	s\frac{dF(X)}{dX}[\bar{f} \oplus \bar{x}]
+\end{align*}
+Therefore $d(sF(X))/dX = s(dF(X)/dX)$
 \end{proof}
@@
 
-\subsection{Chain Rules}
-
-\begin{theorem}[M.M.M. Chain Rule]
+\begin{theorem}[Chain Rule]
 \label{mmm_chain_rule}
@@
 and $G(X)$ be a function $\mathbb{R}^{\vec{x}} \rightarrow \mathbb{R}^{\vec{g}}$.
+Then,
 \[
@@
 \]
-By the scalar total derivative rule,
+By the scalar total derivative rule \cite{wiki:totalderiv},
 \[
@@
 
-\begin{theorem}[S.M.M. Chain Rule]
-\label{smm_chain_rule}
-Let $f(G)$ be a function $\mathbb{R}^{\vec{g}} \rightarrow \mathbb{R}$
-and $G(X)$ be a function $\mathbb{R}^{\vec{x}} \rightarrow \mathbb{R}^{\vec{g}}$.
-\[
-\frac{df(G(X))}{dX} = \frac{df}{dG} \mmult{|\vec{g}|} \frac{dG}{dX}
-\]
-\end{theorem}
-\begin{proof}
-By the definitions of a derivative
-(\ref{sm_derivative} and \ref{mm_derivative} respectively),
-\[
-\forall \bar{g} \in \Dim(\vec{g}):
-\frac{df(G)}{dG}[\bar{g}]
-= \frac{\partial f(G)}{\partial G[\bar{g}]}
-\]
-\[
-\forall \bar{g} \in \Dim(\vec{g}), \bar{x} \in \Dim(\vec{x}):
-\frac{dG(X)}{dX}[\bar{g} \oplus \bar{x}]
-= \frac{\partial G(X)[\bar{g}]}{\partial X[\bar{x}]}
-\]
-By the scalar total derivative rule,
-\[
-\frac{\partial f(G(X))}{\partial X[\bar{x}]}
-= \sum_{\forall \bar{g} \in \Dim(\vec{g})} 
-\frac{\partial f(G)}{\partial G[\bar{g}]}
-\frac{\partial G(X)[\bar{g}]}{\partial X[\bar{x}]}
-\]
-Substituting in our above definitions this yields,
-\[
-\frac{\partial f(G(X))}{\partial X[\bar{x}]}
-= \sum_{\forall \bar{g} \in \Dim(\vec{g})} 
-\frac{df(G)}{dG}[\bar{g}]
-\frac{dG(X)}{dX}[\bar{g} \oplus \bar{x}]
-\]
-Again, by the definition of a derivative (\ref{sm_derivative}),
-\[
-\frac{df(G(X))}{dX}[\bar{x}] =
-\frac{\partial f(G(X))}{\partial X[\bar{x}]}
-\]
-Therefore,
-\[
-\frac{df(G(X))}{dX}[\bar{x}]
-= \sum_{\forall \bar{g} \in \Dim(\vec{g})} 
-\frac{df(G)}{dG}[\bar{g}]
-\frac{dG(X)}{dX}[\bar{g} \oplus \bar{x}]
-\]
-Which, by the definition of multidimensional multipliction (\ref{mm_mult}),
-implies that,
-\[
-\frac{df(G(X))}{dX} = \frac{df(G)}{dG} \mmult{|\vec{g}|} \frac{dG(X)}{dX}
-\]
-\end{proof}
-
-\begin{theorem}[M.S.M. Chain Rule]
-\label{msm_chain_rule}
-Let $F(g)$ be a function $\mathbb{R} \rightarrow \mathbb{R}^{\vec{f}}$
-and $g(X)$ be a function $\mathbb{R}^{\vec{x}} \rightarrow \mathbb{R}$.
-\[
-\frac{dF(g(X))}{dX} = \frac{dF}{dg} \mmult{0} \frac{dg}{dX}
-\]
-\end{theorem}
-\begin{proof}
+\section{Machine Learning Specific Derivatives}
 TODO
-\end{proof}
-
-\begin{theorem}[M.M.S. Chain Rule]
-\label{mms_chain_rule}
-Let $F(G)$ be a function $\mathbb{R}^{\vec{g}} \rightarrow \mathbb{R}^{\vec{f}}$
-and $G(x)$ be a function $\mathbb{R} \rightarrow \mathbb{R}^{\vec{g}}$.
-\[
-\frac{dF(G(x))}{dx} = \frac{dF}{dG} \mmult{|\vec{g}|} \frac{dG}{dx}
-\]
+
+\begin{definition}[Sum]
+Let $\Sum(X)$ be the function $\Sum : \mathbb{R}^{\vec{x}} \to \mathbb{R}$
+such that \[ \Sum(X) = \sum_{\forall \bar{x} \in \Dim(\vec{x})} X[\bar{x}] \]
+\end{definition}
+
+\begin{theorem}[Derivative of Sum]
+\[\frac{d\Sum(X)}{dX} = 1^{|X|}\]
 \end{theorem}
@@
 
-\begin{theorem}[S.S.M. Chain Rule]
-\label{ssm_chain_rule}
-Let $f(g)$ be a function $\mathbb{R} \rightarrow \mathbb{R}$
-and $g(X)$ be a function $\mathbb{R}^{\vec{x}} \rightarrow \mathbb{R}$.
-\[
-\frac{df(g(X))}{dX} = \frac{df}{dg} \frac{dg}{dX}
-\]
-\end{theorem}
-\begin{proof}
+\begin{definition}[Sum of Squares]
+Let $\SoS(X)$ be the function $\SoS : \mathbb{R}^{\vec{x}} \to \mathbb{R}$
+such that 
+\[ \SoS(X) = \sum_{\forall \bar{x} \in \Dim(\vec{x})} X[\bar{x}]^2 \]
+\end{definition}
+
+\begin{theorem}[Derivative of Sum of Squares]
+\[ \frac{d \SoS(X)}{dX} = 2X \]
+\end{theorem}
+\begin{proof}
+Notice that $\SoS(X) = X \mmult{|\vec{x}|} X$...
+
 TODO
@@
 
-\begin{theorem}[S.M.S. Chain Rule]
-\label{sms_chain_rule}
-Let $f(G)$ be a function $\mathbb{R}^{\vec{g}} \rightarrow \mathbb{R}$
-and $G(x)$ be a function $\mathbb{R} \rightarrow \mathbb{R}^{\vec{g}}$.
-\[
-\frac{df(G(X))}{dx} = \frac{df}{dG} \mmult{|\vec{g}|} \frac{dG}{dx}
-\]
-\end{theorem}
-\begin{proof}
+\begin{definition}[Softmax]
+Let $\Softmax(X)$ be the function
+$\Softmax : \mathbb{R}^{\vec{X}} \to \mathbb{R}^{\vec{X}}$
+such that $\forall \bar{x} \in \Dim(\vec{x}):$
+\[
+  \Softmax(X)[\bar{x}] = \frac{
+		\exp(X[\bar{x}])
+	}{
+		\sum_{\forall \bar{c} \in \Dim(\vec{x})} \exp(X[\bar{c}])
+	}
+\]
+\end{definition}
+
+\begin{landscape}
+\begin{theorem}[Derivative of Softmax]
 TODO
-\end{proof}
-
-\begin{theorem}[M.S.S. Chain Rule]
-\label{mss_chain_rule}
-Let $F(g)$ be a function $\mathbb{R} \rightarrow \mathbb{R}^{\vec{f}}$
-and $g(x)$ be a function $\mathbb{R} \rightarrow \mathbb{R}$.
-\[
-\frac{dF(g(x))}{dx} = \frac{dF}{dg} \frac{dg}{dx}
-\]
-\end{theorem}
-\begin{proof}
+\begin{align*}
+	\frac{d\Softmax(X)}{dX}
+	&=
+	\Ident^3(|X|) \mmult{||X||} \Softmax(X)
+  -\Softmax(X) \mmult{0} \Softmax(X) \\
+	&=
+	\left(\Ident^3(|X|) - \Softmax(X) \mmult{0} \Ident^2(|X|) \right)
+	\mmult{||X||} \Softmax(X)
+\end{align*}
+\end{theorem}
+\begin{proof}
+Notice that 
+\[
+	\Softmax(X) = \exp(X) \mmult{0} \left( \Sum(\exp(X)) \right)^{-1}
+\]
+So,
+\begin{alignat}{3}
+	\frac{d\Softmax(X)}{dX}
+	&=&&
+	\frac{d \left( \exp(X) \mmult{0} \left( \Sum(\exp(X)) \right)^{-1} \right)}{dX} \\
+	&=&&
+	\exp(X) \mmult{0} \frac{d \left( \Sum(\exp(X)) \right)^{-1}}{dX}
+	\nonumber\\&&&+
+	\Tran\left(
+		\Tran\left(
+			\left( \Sum(\exp(X)) \right)^{-1}
+			,0
+		\right)
+		\mmult{0}
+		\Tran\left(
+			\frac{d \exp(X)}{dX}
+			,|\vec{x}|
+		\right)
+		,|\{\} \oplus \vec{x}|
+	\right) \\
+	&=&&
+	\exp(X) \mmult{0} \frac{d \left( \Sum(\exp(X)) \right)^{-1}}{dX}
+	\nonumber\\&&&+
+	\Tran\left(
+		\left( \Sum(\exp(X)) \right)^{-1}
+		\mmult{0}
+		\Tran\left(
+			\frac{d \exp(X)}{dX}
+			,|\vec{x}|
+		\right)
+		,|\vec{x}|
+	\right) \\
+	&=&&
+	\exp(X) \mmult{0} \left(
+		-\left( \Sum(\exp(X)) \right)^{-2}
+		\mmult{0}
+		\frac{d\Sum(\exp(X))}{dX}
+	\right)
+	\nonumber\\&&&+
+	\Tran\left(
+		\left( \Sum(\exp(X)) \right)^{-1}
+		\mmult{0}
+		\Tran\left(
+			\Ident^3(|X|) \mmult{||X||} \exp(X)
+			,|\vec{x}|
+		\right)
+		,|\vec{x}|
+	\right) \\
+	&=&&
+	\exp(X) \mmult{0} \left(
+		-\left( \Sum(\exp(X)) \right)^{-2}
+		\mmult{0}
+		1^{|X|}
+		\mmult{||X||}
+		\Ident^3(|X|)
+		\mmult{||X||}
+		\exp(X)
+	\right)
+	\nonumber\\&&&+
+	\Tran\left(
+		\Tran\left(
+			\left( \Sum(\exp(X)) \right)^{-1}
+			\mmult{0}
+			\Ident^3(|X|) \mmult{||X||} \exp(X)
+		,|\vec{x}|
+		\right)
+		,|\vec{x}|
+	\right) \\
+	&=&&
+	-\Softmax(X) \mmult{0} \left(
+		\left( \Sum(\exp(X)) \right)^{-1}
+		\mmult{0}
+		\Ident^2(|X|)
+		\mmult{||X||}
+		\exp(X)
+	\right)
+	\nonumber\\&&&+
+	\Tran\left(
+		\Tran\left(
+			\Ident^3(|X|) \mmult{||X||} \Softmax(X)
+		,|\vec{x}|
+		\right)
+	,|\vec{x}|
+	\right) \\
+	&=&&
+	-\Softmax(X) \mmult{0} \Softmax(X)
+	+
+	\Tran\left(
+		\Ident^3(|X|) \mmult{||X||} \Softmax(X)
+		,2|\vec{x}|
+	\right) \\
+	&=&&
+	\Ident^3(|X|) \mmult{||X||} \Softmax(X)
+  -\Softmax(X) \mmult{0} \Softmax(X) \\
+	&=&&
+	\Ident^3(|X|) \mmult{||X||} \Softmax(X)
+	-\Softmax(X) \mmult{0} \Ident^2(|X|) \mmult{||X||} \Softmax(X) \\
+	&=&&
+	\left(\Ident^3(|X|) - \Softmax(X) \mmult{0} \Ident^2(|X|) \right)
+	\mmult{||X||} \Softmax(X)
+\end{alignat}
+Let's just verify that against the Wikipedia \cite{wiki:softmax} result:
+\begin{align*}
+	\frac{\partial \Softmax(X)[\bar{x}_1]}{\partial X[\bar{x}_2]}
+	&=
+	\left\{
+		\left(\Ident^3(|X|) - \Softmax(X) \mmult{0} \Ident^2(|X|) \right)
+		\mmult{||X||} \Softmax(X)
+	\right\}
+	[\bar{x}_1 \oplus \bar{x}_2] \\
+	&=
+	\sum_{\forall \bar{x}_3}
+	\left(\Ident^3(|X|) - \Softmax(X) \mmult{0} \Ident^2(|X|) \right)
+	[\bar{x}_1 \oplus \bar{x}_2 \oplus \bar{x}_3]
+	\Softmax(X)[\bar{x}_3] \\
+	&=
+	\sum_{\forall \bar{x}_3}
+	\left(
+		\delta_{\bar{x}_1 \bar{x}_2 \bar{x}_3}
+		- \Softmax(X)[\bar{x}_1] \delta_{\bar{x}_2 \bar{x}_3}
+	\right)
+	\Softmax(X)[\bar{x}_3] \\
+	&=
+	(\delta_{\bar{x}_1 \bar{x}_2} - \Softmax(X)[\bar{x}_1])
+	\Softmax(X)[\bar{x}_2] \\
+	&= \left\{
+  \begin{array}{ll}
+    (1-\Softmax(X)[\bar{x}_1])\Softmax(X)[\bar{x}_2]
+			& \mbox{if } \bar{x}_1 = \bar{x}_2 \\
+    (0-\Softmax(X)[\bar{x}_1])\Softmax(X)[\bar{x}_2]
+			& \mbox{otherwise}
+  \end{array}
+	\right. \\
+	&= \left\{
+  \begin{array}{ll}
+    \Softmax(X)[\bar{x}_1]-\Softmax(X)[\bar{x}_1]^2
+			& \mbox{if } \bar{x}_1 = \bar{x}_2 \\
+    -\Softmax(X)[\bar{x}_1])\Softmax(X)[\bar{x}_2]
+			& \mbox{otherwise}
+  \end{array}
+	\right. \\
+	&= \left\{
+  \begin{array}{ll}
+    (1-\Softmax(X)[\bar{x}_2])\Softmax(X)[\bar{x}_2]
+			& \mbox{if } \bar{x}_1 = \bar{x}_2 \\
+    (0-\Softmax(X)[\bar{x}_2])\Softmax(X)[\bar{x}_1]
+			& \mbox{otherwise}
+  \end{array}
+	\right. \\
+	&= (\delta_{\bar{x}_1 \bar{x}_2} - \Softmax(X)[\bar{x}_2])
+	\Softmax(X)[\bar{x}_1]
+\end{align*}
+And it looks like we're good. I wrote this proof before backreferencing the wiki
+page, so that's a good sign.
+\end{proof}
+\end{landscape}
+
+\begin{definition}[Feed Forward Neural Net Layer]
+Feed forward neural nets are described all over the place so I won't go into too
+much detail here. In short, for every layer except the input layer there is some
+previous layer which feeds into current layer via a fully-connected network of
+weights.
+
+Let $L_{i-1}$ be the activations of the the previous layer and $L_i$ the activations
+of the current layer. Each of these can be modeled as a multimatrix. As an the weighted
+connections between them, $W_i$. Finally, there is an activation function
+$a(X) : \mathbb{R}^{|X|} \to \mathbb{R}^{|X|}$ which is an elementwise function,
+often the sigmoid function, or ReLU, or some variant thereof. It's unimportant for this
+definition.
+
+\[ L_i = a(L_{i-1} \mmult{||L_{i-1}||} W_i) \]
+\end{definition}
+
+\begin{theorem}[Derivative of FFNN Layer]
+\[ \frac{dL_i}{dW_j} = ? \]
+\end{theorem}
+\begin{proof}
+\begin{ppart} When $i < j$,
+$L_i$ does not depend on $W_j$, so 
+$\forall \bar{x} \in \Dim(|L_i|), \bar{y} \in \Dim(|W_j|)$
+$\frac{dL_i}{dW_j} = 0$
+\end{ppart}
+\begin{ppart} $i = j$
 TODO
+\end{ppart}
+\begin{ppart} $i > j$
+TODO
+\end{ppart}
 \end{proof}
@@
 \end{proof}
-
 \end{landscape}
+
+\bibliography{paper}
+\bibliographystyle{ieeetr}
+
 \end{document}

### 2019-06-06 Math/paper.tex
Adding example of multimatrix multiplication.

@@
 
+\theoremstyle{plain}
 \newtheorem{theorem}{Theorem}[section]
@@
 \newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{example}{Example}[section]
 
@@
 So, I came up with a system of my own. And, much to my surprise, some of the
-results I came up with were surprisingly elegant. For example, I proved a
+results I came up with were kind of elegant. For example, I proved a
 multidimensional version of the derivative chain rule (Thm. \ref{mmm_chain_rule})
-that's more consise than anything I've found in other works.
-
-This book is about my exploration into multidimensional matricies - multimatricies -
-and how they can simplify derivatives of matrix equations.
+that's more consise than anything I've seen in my (admitedly limited) experience.
+
+The ultimate goal of this notation system was to provide a way to take derivatives
+of matrix equations without having to break apart matricies into their constituent
+parts. I knew I succeeded when I was able to derive the derivative of the softmax
+function completely in my own notation (Thm. \ref{softmax_derivative}).
+
+Not knowing what else to do with the results, I've written this paper (short book?)
+about my amature exploration into multidimensional matricies -
+multimatricies - and how they can simplify derivatives of matrix equations.
 \end{abstract}
@@
 both output and indepenedent variable are preserved - but let us declare this to
-be our convention for the remainder of this article.
+be our convention for the remainder of this work.
 
@@
 \begin{definition}[Multimatrix]
-Let's define a bit of notation. A multimatrix $M$ is a multidimensional matrix
-that has some shape, $|M| \in \mathbb{N}^n$, where $n$ is the number of
-dimensions of $M$.
+Let's define this bit of notation formally. A multimatrix $M$ is a multidimensional
+matrix that has some shape, $|M| \in \mathbb{N}^n$, where $n \in \mathbb{Z}^+ \cup \{0\}$
+is the number of dimensions of $M$.
 
@@
 
-But that single line will require defining something I'm going to call a cubic
-identity, $\Ident^3(|X|)$, as well as multimatrix multiplication.
+But that single line will require defining multimatrix multiplication and
+something I'll call a cubic identity, $\Ident^3(|X|)$.
 
@@
 Multiplication of traditional matricies is one of those things that, when you
-first learn about it, you wonder "Who the hell defined it this way?" And then
-when you see it used in practice, you slowly come to understand they why behind
-it.
+first learn about it, makes you wonder ``What crosseyed weirdo defined it this way?''
+And then, after seeing it used in practice, you slowly come to understand the
+reason behind the madness. Let me warn you now - multimatrix multiplication will
+feel the same way.
 
@@
 two dimensional matrix multiplication completely within our definition. This second
-definition seems more... multidimensional but it also seems to arbitrarily depend
-on the shape of the two matricies.
-
-So - a compromize. Maybe multimatrix isn't a binary operation. Maybe it's a trinary
-operation. There's some component of, ``How many dimensions are you combining?'' inherent
+definition seems more... er... multidimensional... but it also seems to
+arbitrarily depend on the shape of the two matricies.
+
+What we really need is an operation which covers both lines of reasoning but that
+seems impossible with a binary operaiton. So maybe multimatrix isn't a binary operation.
+Maybe it's a trinary operation. There's some component of, 
+``How many dimensions are you combining?'' inherent
 in the operation. So we can distinguish our two types of multiplication, and indeed
@@
 $|B| = \vec{c} \oplus \vec{b}$, and $|\vec{c}| = n$ with
-$n \in \left\{ 0 \right\} \cup \mathbb{Z}^{+}$. We shall call $n$ the 'size'
+$n \in \{0\} \cup \mathbb{Z}^{+}$. We shall call $n$ the 'size' or the 'width'
 of the multiplication operation.
@@
 \end{definition}
+
+\newpage
+\begin{example}
+Let $|A| = \left<2, 3, 2\right>$ and $|B| = \left<3, 2, 2\right>$
+\begin{table}[h!]
+\begin{center}
+\begin{tabular}{c c c | c}
+$\bar{a}_1$ & $\bar{a}_2$ & $\bar{a}_3$ & $A[\bar{a}]$ \\
+\hline
+1           & 1           & 1           & -0.5         \\
+1           & 1           & 2           & 1            \\
+1           & 2           & 1           & 2            \\
+1           & 2           & 2           & -1           \\
+1           & 3           & 1           & 5            \\
+1           & 3           & 2           & 1            \\
+2           & 1           & 1           & 3            \\
+2           & 1           & 2           & -7           \\
+2           & 2           & 1           & 5            \\
+2           & 2           & 2           & 2            \\
+2           & 3           & 1           & -3           \\
+2           & 3           & 2           & -1
+\end{tabular}
+\end{center}
+\end{table}
+
+\begin{table}[h!]
+\begin{center}
+\begin{tabular}{c c c | c}
+$\bar{b}_1$ & $\bar{b}_2$ & $\bar{b}_3$ & $B[\bar{b}]$ \\
+\hline
+1           & 1           & 1           & 1            \\
+1           & 1           & 2           & 0            \\
+1           & 2           & 1           & 1            \\
+1           & 2           & 2           & 0            \\
+2           & 1           & 1           & 1            \\
+2           & 1           & 2           & 0            \\
+2           & 2           & 1           & 1            \\
+2           & 2           & 2           & 0            \\
+3           & 1           & 1           & 1            \\
+3           & 1           & 2           & 0            \\
+3           & 2           & 1           & 1            \\
+3           & 2           & 2           & 0
+\end{tabular}
+\end{center}
+\end{table}
+
+You given $|A|$ and $|B|$, and by our definition of multimatrix multiplication,
+you can see that $|A \mmult{2} B| = \left<2, 2\right>$. And the values of the
+resulting multimatrix are defined:
+
+\begin{table}[h!]
+\begin{center}
+\begin{tabular}{c c | c | c | c}
+$\bar{x}_1$ & $\bar{x}_2$ & $(A \mmult{2} B)[\bar{x}]$ & = & = \\
+\hline
+1 & 1 &
+  $A[1,1,1]B[1,1,1] + A[1,1,2]B[1,2,1] +$ & $(-0.5)(1) + (1)(1) +$ & 7.5 \\
+&&$A[1,2,1]B[2,1,1] + A[1,2,2]B[2,2,1] +$ & $(2)(1) + (-1)(1) +$ & \\
+&&$A[1,3,1]B[3,1,1] + A[1,3,2]B[3,2,1]$   & $(5)(1) + (1)(1)$ & \\
+1 & 2 &
+  $A[1,1,1]B[1,1,2] + A[1,1,2]B[1,2,2] +$ & $(-0.5)(0) + (1)(0) +$ & 0 \\
+&&$A[1,2,1]B[2,1,2] + A[1,2,2]B[2,2,2] +$ & $(2)(0) + (-1)(0) +$ & \\
+&&$A[1,3,1]B[3,1,2] + A[1,3,2]B[3,2,2]$   & $(5)(0) + (1)(0)$ & \\
+2 & 1 &
+  $A[2,1,1]B[1,1,1] + A[2,1,2]B[1,2,1] +$ & $(3)(1) + (-7)(1) +$ & 1 \\
+&&$A[2,2,1]B[2,1,1] + A[2,2,2]B[2,2,1] +$ & $(5)(1) + (2)(1) +$ & \\
+&&$A[2,3,1]B[3,1,1] + A[2,3,2]B[3,2,1]$   & $(-3)(1) + (1)(1)$ & \\
+2 & 2 &
+  $A[2,1,1]B[1,1,2] + A[2,1,2]B[1,2,2] +$ & $(3)(0) + (-7)(0) +$ & 0 \\
+&&$A[2,2,1]B[2,1,2] + A[2,2,2]B[2,2,2] +$ & $(5)(0) + (2)(0) +$ & \\
+&&$A[2,3,1]B[3,1,2] + A[2,3,2]B[3,2,2]$   & $(-3)(0) + (1)(0)$ &
+\end{tabular}
+\end{center}
+\end{table}
+
+\end{example}
+\newpage
 
@@
 $|A \mmult{1} B| = \left<5,3,7\right>$ and
-$|(A \mmult{1} B) \mmult{2} C| = \left<5,7\right>$. But
+$|(A \mmult{1} B) \mmult{2} C| = \left<5,2\right>$. But
 $A \mmult{1} (B \mmult{2} C)$ isn't a valid set of operations since even
@@
 
-\noindent
-Since $A \mmult{m} B$ is defined,
-\[
- \exists \vec{a}, \vec{m}, \vec{b_1} :
- |\vec{m}| = m \land |A| = \vec{a} \oplus \vec{m} \land |B| = \vec{m} \oplus \vec{b_1} 
-\]
-Since $B \mmult{n} C$ is defined,
-\[
- \exists \vec{b_2}, \vec{n}, \vec{c} :
- |\vec{n}| = n \land |B| = \vec{b_2} \oplus \vec{n} \land |C| = \vec{n} \oplus \vec{c}
-\]
+Since $A \mmult{m} B$ is defined, there exist vectors $\vec{a}, \vec{m},$ and
+$\vec{b_1}$ such that 
+$|\vec{m}| = m$,
+$|A| = \vec{a} \oplus \vec{m}$,
+and
+$|B| = \vec{m} \oplus \vec{b_1}$
+
+Since $B \mmult{n} C$ is defined, there exist vectors $\vec{b_2}, \vec{n},$ and
+$\vec{c}$ such that
+$|\vec{n}| = n$,
+$|B| = \vec{b_2} \oplus \vec{n}$
+and
+$|C| = \vec{n} \oplus \vec{c}$
+
 Since $|B| = \vec{m} \oplus \vec{b_1} = \vec{b_2} \oplus \vec{n}$ and
-$||B|| \ge |\vec{m}| + |\vec{n}|$, it must follow that,
-\[
- \exists \vec{b} :
+$||B|| \ge |\vec{m}| + |\vec{n}|$, it must follow that, there is some vector $\vec{b}$
+such that,
+\[
  |B| = \vec{m} \oplus \vec{b} \oplus \vec{n}
@@
 \begin{theorem}[Derivative of Softmax]
-TODO
+\label{softmax_derivative}
 \begin{align*}

### 2019-06-16 Math/paper.tex
Adding some humor and an exercise.

@@
 \usepackage{etoolbox}
+\usepackage{csquotes}
+\usepackage[normalem]{ulem}
 
@@
 \newtheorem{definition}{Definition}[section]
+\newtheorem{exercise}{Exercise}[section]
 
@@
 \newtheorem{ppart}{Part}
+
+\newtheoremstyle{solution}{}{}{}{}{}{:}{\newline}{Exercise \thmnumber{#2} Solution}
+\theoremstyle{solution}
+\newtheorem{solution}{Solution}
+
+\AtBeginEnvironment{subsection}{\setcounter{solution}{0}}
 \AtBeginEnvironment{proof}{\setcounter{ppart}{0}}
@@
 \begin{abstract}
-I was working my way through the implementation of a machine learning system as
-a hobby project and I was having a hell of a time wrapping my head around the
-existing notation for derivatives of matrix equations. Every notation system
-either requires users to pull apart the matricies they're working with or otherwise
-bypass the issue of taking derivatives of matrix equations.
-
-So, I came up with a system of my own. And, much to my surprise, some of the
-results I came up with were kind of elegant. For example, I proved a
+I was working my way through a hobby programming project, trying to manifest Skynet
+as more than the apocalyptic fever dream James Cameron, and ran into a problem.
+The existing notation for taking derivatives of matrix equations is so
+deliberately obtuse as to suggest that some hidden cabal of mathematicians is
+actively working to sabotage our glorious yet-to-be-built robot overlords.
+That sort of justice cannot stand!
+
+I thus set out to invent a system of my own. Much to my surprise, some of the
+results with were rather elegant. For example, I stumbled upon a
 multidimensional version of the derivative chain rule (Thm. \ref{mmm_chain_rule})
-that's more consise than anything I've seen in my (admitedly limited) experience.
-
-The ultimate goal of this notation system was to provide a way to take derivatives
+that's nearly as consise as the same rule for scalars.
+
+The ultimate goal of this notation system was to \sout{bring about the downfall
+of humanity} figure out a way to take derivatives
 of matrix equations without having to break apart matricies into their constituent
-parts. I knew I succeeded when I was able to derive the derivative of the softmax
+parts. I knew I had succeeded when I was able to derive the derivative of the softmax
 function completely in my own notation (Thm. \ref{softmax_derivative}).
 
-Not knowing what else to do with the results, I've written this paper (short book?)
-about my amature exploration into multidimensional matricies -
+Now, not knowing what else to do with the results, I've written this paper
+(short book?) about my amature exploration into multidimensional matricies -
 multimatricies - and how they can simplify derivatives of matrix equations.
@@
 
-Let's consider a traditional matrix equation.
-We'll define some matricies $M$ and $X$ such that
-$|M| = |X| = \left< 3,5 \right>$
-and \[M_{r,c} = \sin(X_{r,c})\]
-Or more simply, \[M = \sin(X)\]
-
-\noindent
-The partial derivatives of this equation are simple enough. Assuming that all elements
-of $X$ are independent,
-\[
-\frac{\partial M_{r_1,c_1}}{\partial X_{r_2,c_2}} = 
+\begin{displayquote}
+``If you're a bit touched, like I am, you may want to make a dedicated tool.'' -
+This Old Tony, `Making Springs At Home'
+\end{displayquote}
+
+Let's consider a traditional matrix equation. As is traditional, one matrix
+$X$ shall represent the scientific education level of undergraduates, who happen
+to work in a densely packed 3 by 5 grid - which is also traditional. Then let
+$B$ represent the belief each of those undergradutes has in a higher power,
+which, as we all know, fluctuates with respect to their scientific education in
+a sinusoidal pattern (Weinersmith, 2010 \cite{weinersmith:education}).
+
+Formally, the shape of these two matricies are defined,
+$|B| = |X| = \left< 3,5 \right>$.
+And each element of $B$ will be the sine of the corresponding element of
+$X$. That is, \[B_{r,c} = \sin(X_{r,c})\]
+Which I'll write more simply as, \[B = \sin(X)\]
+
+Now, I would call the derivative of any element of $B$ with respect to any element
+of $X$ a partial derivative of that function. Since
+$\partial B_{r_1, c_1}/\partial X_{r_2, c_2}$ is defined by the rate of change of
+\textit{one} undergraduate's belief in a higher power with respect to \textit{one}
+undergraduate's education level - it only represents a change to part of the whole
+system. 
+We can calculate this partial derivative easily enough,
+\[
+\frac{\partial B_{r_1,c_1}}{\partial X_{r_2,c_2}} = 
 \left\{
@@
 \]
-Which can also be writen more simply using Kronecker deltas,
-\[
-\frac{\partial M_{r_1,c_1}}{\partial X_{r_2,c_2}} = 
+Every student's belief in a higher power changes with respect to their own
+scientific education level, but does not change with respect to other students'
+scientific education. No mater how much I teach Jane about photosynthesis, I'm
+not going to change Joe's mind about divine mysteries.
+
+This can also be writen more simply using Kronecker deltas \cite{wiki:kronecker},
+which should make one feel particularly intellegent as Kronecker deltas were used
+by Einstein (and presumably someone named Kronecker) \cite{wiki:einstein}.
+\[
+\frac{\partial B_{r_1,c_1}}{\partial X_{r_2,c_2}} = 
 \cos (X_{r_2, c_2}) \delta_{r_1 r_2} \delta_{c_1 c_2}
@@
 
-\noindent
-But what about the complete deriative? What would that even mean? What sort of
-mathmatical object would represent the entire derivative of $M$ with respect to $X$.
-
-\[\frac{dM}{dX} = \mbox{ ? }\]
+But what about the complete deriative?
+What sort of mathmatical object would represent the entire derivative
+of $B$ with respect to $X$?
+I need a mathematical object which perfectly
+encapsulates the rate of change of \textit{all} the undergraduates' beliefs in a
+higher power with respect to \textit{every} undergraduates' scientific education
+and my current toolkit does not serve that need!
+
+\[\frac{dB}{dX} = \mbox{ ? }\]
 
@@
 element has its own partial derivative, so it makes sense that the total size
-of the complete derivative should be the product of the size of $M$ and the size
+of the complete derivative should be the product of the size of $B$ and the size
 of $X$.
@@
 \[
-\mbox{size}\left(\frac{dM}{dX}\right) = \mbox{size}(M) \mbox{size}(X)
+\mbox{size}\left(\frac{dB}{dX}\right) = \mbox{size}(B) \mbox{size}(X)
 \]
@@
 \begin{align*}
-\left|\frac{dM}{dX}\right| &= |M| \oplus |X| \\
+\left|\frac{dB}{dX}\right| &= |B| \oplus |X| \\
  &= \left< 3, 5 \right> \oplus \left< 3, 5 \right> \\
@@
 \[
-\frac{dM}{dX}[1,2,3,4] = \frac{\partial M_{1,2}}{\partial X_{3,4}}
+\frac{dB}{dX}[1,2,3,4] = \frac{\partial B_{1,2}}{\partial X_{3,4}}
 \]
@@
 \[
-\frac{dM}{dX}[1,2,3,4] = \frac{\partial M[1,2]}{\partial X[3,4]}
+\frac{dB}{dX}[1,2,3,4] = \frac{\partial B[1,2]}{\partial X[3,4]}
 \]
@@
 
-We'll say that if $\vec{v} = |M|$, then any $\bar{v} \in \mathbb{N}^n$ is a valid
-index of $M$ if and only if value of $\bar{v}$ is less than or equal to the value
-of it's parallel index in $\vec{v}$. That is, $\forall i: 1 \le \bar{v}_i \le \vec{v}_i$.
+We'll say that for the whole number vector $\vec{v}$ which describes the shape of
+$M$, then $\vec{v} = |M|$. And for any other $\bar{v} \in \mathbb{N}^n$, $\bar{v}$
+is a valid index of $M$ if and only if each value of $\bar{v}$ is less than or equal
+to the value of it's corresponding index in $\vec{v}$.
+That is, $\forall i: 1 \le \bar{v}_i \le \vec{v}_i$.
 
 We can further simplify that notation for our set of valid indicies. Let's say we have
-some $\vec{v} \in \mathbb{N}^n$ that defines the shape of some matrix. Then well
+some $\vec{v} \in \mathbb{N}^n$ that defines the shape of some matrix. Then we'll
 define the set of valid indicies of that matrix to be $\Dim(\vec{v})$.
@@
 question?
-\[\frac{dM}{dX} = ? \]
-Well... sort of. We can say that the total derivative of $M$ with respect to $X$ is
-a matrix with shape $|M| \oplus |X|$, who's elements we can define as,
-\[\forall \bar{m} \in \Dim(|M|), \bar{x} \in \Dim(|X|):\]
-\begin{align*}
-\left( \frac{dM}{dX} \right)[\bar{m} \oplus \bar{x}]
-&= \frac{\partial M[\bar{m}]}{\partial X[\bar{x}]} \\
-&= \delta_{\bar{m}\bar{x}}\cos(\bar{x})
+\[\frac{dB}{dX} = ? \]
+Well... sort of. We have to abuse the notation a little and say that $B$ and $X$ are
+just multimatricies with 2 dimensions. Then we can say that the total derivative
+of $B$ with respect to $X$ is a multimatrix with shape $|B| \oplus |X|$,
+who's elements we can define as,
+\[\forall \bar{b} \in \Dim(|B|), \bar{x} \in \Dim(|X|):\]
+\begin{align*}
+\left( \frac{dB}{dX} \right)[\bar{b} \oplus \bar{x}]
+&= \frac{\partial B[\bar{b}]}{\partial X[\bar{x}]} \\
+&= \delta_{\bar{b}\bar{x}}\cos(\bar{x})
 \end{align*}
@@
 \[
-\frac{dM}{dX} = \Ident^3(|X|) \mmult{||X||} \cos(X)
+\frac{dB}{dX} = \Ident^3(|X|) \mmult{||X||} \cos(X)
 \]
@@
 
-\subsection*{Sample Problems}
-TODO
+\subsection*{Exercises}
+
+\begin{exercise}
+Let $A$, $B$, and $C$ be multimatricies such that $|A| = \left<1,2,3\right>$,
+$|B| = \left<3,1,2\right>$ and $|C| = \left<3,2,1\right>$. For each of these
+multiplications determine if it is valid, and if so, what the resulting
+shape would be:
+\begin{enumerate}
+\item $A \mmult{2} B$
+\item $B \mmult{2} A$
+\item $A \mmult{2} C$
+\item $A \mmult{1} C$
+\end{enumerate}
+\end{exercise}
 
@@
 
-Multiplication of traditional matricies is one of those things that, when you
-first learn about it, makes you wonder ``What crosseyed weirdo defined it this way?''
-And then, after seeing it used in practice, you slowly come to understand the
-reason behind the madness. Let me warn you now - multimatrix multiplication will
-feel the same way.
+\begin{displayquote}
+``The universe is a cruel, uncaring void. The key to being happy isn't a search
+for meaning. It's to just keep yourself busy with unimportant nonsense, and eventually,
+you'll be dead.'' - Mr. Peanutbutter, BoJack Horseman
+\end{displayquote}
+
+Multiplication of traditional matricies is one of those things that, when one first
+learn about it, causes one to wonder ``By which satanic cult was this process
+proscribed?''
+And then, after seeing it used in practice, one slowly comes to understand the
+reason behind the madness. That is, that madness is the natural state of things
+and matrix multiplication is used to punish those few kind souls who dare to
+fight against the darkness.
+
+Multimatrix multiplication is much the same.
 
@@
 \begin{example}
-Let $|A| = \left<2, 3, 2\right>$ and $|B| = \left<3, 2, 2\right>$
+Let $|A| = \left<2, 3, 2\right>$ and $|B| = \left<3, 2, 2\right>$ where
+the elements of $A$ and $B$ are defined in the tables below.
 \begin{table}[h!]
@@
 
-You given $|A|$ and $|B|$, and by our definition of multimatrix multiplication,
+Given $|A|$ and $|B|$, and by our definition of multimatrix multiplication,
 you can see that $|A \mmult{2} B| = \left<2, 2\right>$. And the values of the
@@
 
-\subsection*{Sample Problems}
+\subsection*{Exercises}
 TODO
@@
 \section{Other Operations With Multimatricies}
+
+\begin{displayquote}
+``When the light turns green, you go. When the light turns red, you stop.
+But what do you do when the light turns blue with orange and lavender spots?''
+- Shel Silverstein, 'A Light in the Attic'
+\end{displayquote}
+
 Other operations include...
@@
 \section{Generic Derivative Rules}
+
+\begin{displayquote}
+``It goes without saying that all writers owe a debt to their teachers... who
+naturally bear all responsibility for any errors contained herein...''
+- Paul Rentel, 'Manifolds, Tensors, and Forms'
+\end{displayquote}
 
@@
 \section{Machine Learning Specific Derivatives}
-TODO
+
+\begin{displayquote}
+``I'm not saying Machine Learning is a portal to a demon universe, I'm just saying
+that some doors are best left unopened.'' - James Mickens, AKA `Galactic Viceroy of Research Excellence', USENIX Security '18-Q
+\end{displayquote}
 
@@
 
+\section{Solutions to the Exercises}
+
+\subsection*{Section 1 Solutions}
+
+\begin{solution}
+\begin{enumerate}
+\item[]
+\item Invalid
+\item $\left<3, 3\right>$
+\item Invalid
+\item $\left<1, 2, 2, 1\right>$
+\end{enumerate}
+\end{solution}
+
 \bibliography{paper}

### 2019-06-19 Math/paper.tex
Added exercises and exposition to Ch. 2

@@
-\documentclass[12pt]{article}
+\documentclass[12pt]{book}
 \usepackage{amsfonts}
@@
 \theoremstyle{definition}
-\newtheorem{definition}{Definition}[section]
-\newtheorem{exercise}{Exercise}[section]
+\newtheorem{definition}{Definition}[chapter]
+\newtheorem{exercise}{Exercise}[chapter]
 
 \theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[section]
+\newtheorem{theorem}{Theorem}[chapter]
 \newtheorem{corollary}{Corollary}[theorem]
 \newtheorem{lemma}[theorem]{Lemma}
-\newtheorem{example}{Example}[section]
+\newtheorem{example}{Example}[chapter]
 
@@
 
-\AtBeginEnvironment{subsection}{\setcounter{solution}{0}}
+\AtBeginEnvironment{section}{\setcounter{solution}{0}}
 \AtBeginEnvironment{proof}{\setcounter{ppart}{0}}
@@
 
-\begin{abstract}
+\chapter*{Preface}
 I was working my way through a hobby programming project, trying to manifest Skynet
-as more than the apocalyptic fever dream James Cameron, and ran into a problem.
-The existing notation for taking derivatives of matrix equations is so
-deliberately obtuse as to suggest that some hidden cabal of mathematicians is
-actively working to sabotage our glorious yet-to-be-built robot overlords.
+as more than the apocalyptic fever dream of James Cameron, and ran into a problem.
+The existing notation for taking derivatives of matrix equations is terrible.
+It's so deliberately obtuse that I could only conclude that some hidden cabal of
+mathematicians is actively working to sabotage our glorious yet-to-be-built
+robot overlords.
+
 That sort of justice cannot stand!
 
-I thus set out to invent a system of my own. Much to my surprise, some of the
-results with were rather elegant. For example, I stumbled upon a
+So, I set out to invent a system of my own. Much to my surprise, some of the
+results with were rather elegant. For example, I stumbled onto a
 multidimensional version of the derivative chain rule (Thm. \ref{mmm_chain_rule})
@@
 of matrix equations without having to break apart matricies into their constituent
-parts. I knew I had succeeded when I was able to derive the derivative of the softmax
-function completely in my own notation (Thm. \ref{softmax_derivative}).
-
-Now, not knowing what else to do with the results, I've written this paper
-(short book?) about my amature exploration into multidimensional matricies -
+parts. I knew that I had succeeded when I was able to derive the derivative of the
+softmax function completely in my own notation (Thm. \ref{softmax_derivative}).
+
+Now, not knowing what else to do with the results, I've written this book
+about my amature exploration into multidimensional matricies -
 multimatricies - and how they can simplify derivatives of matrix equations.
-\end{abstract}
-
-\newpage
 
@@
 
-\newpage
-
-\section{Defining the Derivative}
+\chapter{Defining the Derivative}
 
@@
 of $X$ a partial derivative of that function. Since
-$\partial B_{r_1, c_1}/\partial X_{r_2, c_2}$ is defined by the rate of change of
+$\partial B_{r_1, c_1}/\partial X_{r_2, c_2}$ is defined as the rate of change of
 \textit{one} undergraduate's belief in a higher power with respect to \textit{one}
@@
 higher power with respect to \textit{every} undergraduates' scientific education
-and my current toolkit does not serve that need!
+and my current toolkit doesn't work!
 
@@
 \]
-And perhaps we could even let this help us define the 'shape' of the complete
+And perhaps we could even let this help us define the `shape' of the complete
 derivative. This complete derivative would need to be composed of partial
@@
 The ordering here is arbitrary, there is no reason why the dimensionality of
-of the independent variable \textit{needs} to be concatenated with to the right of the
+of the independent variable \textit{needs} to be concatenated to the right of the
 dimensionality of the output. What's important is that the dimensionality of
-both output and indepenedent variable are preserved - but let us declare this to
-be our convention for the remainder of this work.
-
-We have, therefore, a multidimensional object with four indicies. Suppose we try to
-pull a single partial derivative from this complete derivative, what could our
-notation look like? Four underscript indicies would be unwieldy, so maybe something
-like this:
+both output and indepenedent variable are preserved. Let us declare this to
+be our convention since, for the purpose of this work, mine is the divinely revealed
+word of god, passed down to you lowly mortals who have yet to commit your
+own mad ramblings to \LaTeX.
+
+Our total derivate is therefore a multidimensional object with four indicies.
+Suppose we try to pull a single partial derivative from this complete derivative,
+what could our notation look like? Four underscript indicies would be unwieldy,
+so maybe something like this:
 \[
@@
 
-And since we're defining our own notation, let's go ahead and define our original
+And since we're defining our own notation, let's splurge and reference our original
 matricies in a similar manner:
@@
 
-So what is this object we've defined? In all ways that matter, it seams to be
+So what is this object we've defined? In all ways that matter, it seems to be
 a multidimensional matrix. It has four dimensions of indices, rather than just
 a row and column, but each uniquely indexed cell in this object may have a
-unique value, just like a standard two dimensional matrix.
+unique value, just like a standard two dimensional matrix. Let's define this
+bit of notation formaly.
 
 \begin{definition}[Multimatrix]
-Let's define this bit of notation formally. A multimatrix $M$ is a multidimensional
-matrix that has some shape, $|M| \in \mathbb{N}^n$, where $n \in \mathbb{Z}^+ \cup \{0\}$
+A multimatrix $M$ is a multidimensional object that has some shape,
+$\vec{v} \in \mathbb{N}^n$, where $n \in \mathbb{Z}^+ \cup \{0\}$
 is the number of dimensions of $M$.
 
-We'll say that for the whole number vector $\vec{v}$ which describes the shape of
+Let $\vec{v}$ be the natural number vector which describes the shape of
 $M$, then $\vec{v} = |M|$. And for any other $\bar{v} \in \mathbb{N}^n$, $\bar{v}$
@@
 
-Going back to our original motivating problem, we can express our derivative
-notation thusly,
+Going back to our original motivating problem, we (that is to say, myself and my
+split personalities whom I reference as to give my writing the percieved authority
+of more than one author) can express our derivative notation thusly,
 
@@
 if we could define the total derivative without going down into the partial derivatives
-at all, which we'll be able to do in later sections. As a sneak peak, that'll look
-like this:
+at all, which we'll be able to do in later chapters. As a sneak peak (a whole
+chapter ahead), that'll look like this:
 \[
@@
 But that single line will require defining multimatrix multiplication and
-something I'll call a cubic identity, $\Ident^3(|X|)$.
-
-\subsection*{Exercises}
+a mysterious, and possibly dangerious, entity call a cubic identity, $\Ident^3(|X|)$.
+
+\section*{Exercises}
 
 \begin{exercise}
-Let $A$, $B$, and $C$ be multimatricies such that $|A| = \left<1,2,3\right>$,
-$|B| = \left<3,1,2\right>$ and $|C| = \left<3,2,1\right>$. For each of these
-multiplications determine if it is valid, and if so, what the resulting
-shape would be:
+Are the following assertions are true or false?
 \begin{enumerate}
-\item $A \mmult{2} B$
-\item $B \mmult{2} A$
-\item $A \mmult{2} C$
-\item $A \mmult{1} C$
+\item $\left<1,1,1\right> \in \Dim(\left<5,5,5\right>)$
+\item $\left<1,1\right> \in \Dim(\left<5,5,5\right>)$
+\item $\left<1,2,3\right> \in \Dim(\left<3,2,1\right>)$
+\item $\left<3,7\right> \in \Dim(\left<3,7\right>)$
 \end{enumerate}
@@
 
-\section{Multimatrix Multiplication}
+\begin{exercise}
+Let $F(X)$ be a function from $\mathbb{R}^{\left<3,7,2\right>}$ to
+$\mathbb{R}^{\left<6, 7\right>}$. That is, $|F(X)| = \left<6,7\right>$
+and for any valid input to $F(X)$, $|X| = \left<3,7,2\right>$.
+Then what is the shape of $dF/dX$?
+\end{exercise}
+
+\begin{exercise}
+Let $f(X)$ be the sum of all values of $X$, where
+$X \in \mathbb{R}^{\left<2,3,2\right>}$. That is,
+\[ f(X) = \sum_{\forall \bar{x} \in \Dim(\left<2,3,2\right>)} X[\bar{x}] \]
+What is the shape of $df/dX$? If $\bar{v} \in \Dim(|df/dX|)$ then what is
+\[ \frac{df}{dX}[\bar{v}] = ? \]
+\end{exercise}
+
+\chapter{Multimatrix Multiplication}
 
@@
 
-Multiplication of traditional matricies is one of those things that, when one first
-learn about it, causes one to wonder ``By which satanic cult was this process
+The multiplication of traditional matricies is a calculation that, when one first
+encouters it, inspires thoughts such as ``By which satanic cult was this process
 proscribed?''
-And then, after seeing it used in practice, one slowly comes to understand the
+
+After seeing the method used in practice, one slowly comes to understand the
 reason behind the madness. That is, that madness is the natural state of things
-and matrix multiplication is used to punish those few kind souls who dare to
+and matrix multiplication is used to punish those few brave souls who dare to
 fight against the darkness.
@@
 
+Easily done. The hard part isn't doing the calculation. The hard part is
+parlaying with Sheogorath, Daedric Prince of Madness for the intellectual
+property rights.
+
 So now consider how we would multiply two matricies $A$ and $B$ if they had more
@@
 
-What we really need is an operation which covers both lines of reasoning but that
-seems impossible with a binary operaiton. So maybe multimatrix isn't a binary operation.
-Maybe it's a trinary operation. There's some component of, 
+What we really need is an operation which covers both lines of reasoning. To do
+so, we need to compleately abandon conventional algebras, and indeed any hope of
+returning to sanity. That's right, we're introducing a trinary operator.
+
+I would argue that there shall always be some component of, 
 ``How many dimensions are you combining?'' inherent
@@
 $n \in \{0\} \cup \mathbb{Z}^{+}$. We shall call $n$ the 'size' or the 'width'
-of the multiplication operation.
+or the 'overlap' of the multiplication operation.
 The shape of the result is defined, $|A \mmult{n} B| = \vec{a} \oplus \vec{b}$
@@
 \begin{example}
-Let $|A| = \left<2, 3, 2\right>$ and $|B| = \left<3, 2, 2\right>$ where
-the elements of $A$ and $B$ are defined in the tables below.
+Let $|A| = \left<2, 3, 2\right>$ and $|B| = \left<3, 2, 2\right>$. I would
+define their values in a three dimensional grid but I fear that my three dimensional
+\LaTeX skills aren't up to the task (and three dimensional monitors are quite hard to
+come by). So here is where we leave behind nice graphical representations of
+things, and I'll just define the elements of $A$ and $B$ in the tables below.
 \begin{table}[h!]
@@
 \textit{not} communicative. And it is only weakly associative. That sounds like
-nonsense, but here's what I mean.
+nonsense, and ideed it is, but I shall prove it to you.
 
@@
 But even when the dimensional analysis makes sense, multimatrix multiplication
-may not be associative. Take, for example, multimatricies $A$, $B$, and $C$ such
+may not be associative (Honestly, how could you be so naive?). 
+Take, for example, multimatricies $A$, $B$, and $C$ such
 that $|A| = \left<2,2,2,2\right>$, $|B| = \left<2,2,2\right>$, and
@@
 of the same dimensionality, they are not equal so multiplicative associativity
-doesn't hold.
+doesn't hold. It also goes to show that your intuition is bad and you should feel bad.
 
@@
 However, the multiplicative identity also greatly depends on the size of
-the particular multiplication operation.
+the particular multiplication operation. Making a confusing and frightening
+situation even more so, like loosing a troup of clowns in children's cancer ward.
 
@@
 \begin{theorem}[Self Derivative]
-Let $X$ be a multimatrix with independent elements. Then,
+Let $X$ be some multimatrix. Then,
 \[ \frac{dX}{dX} = \Ident^2(|X|) \]
@@
 \begin{proof}
-Let $X$ be a multimatrix of shape $|X|=\vec{x}$ with independent elements.
+Let $X$ be a multimatrix of shape $|X|=\vec{x}$.
 By the derivative definition (Def. \ref{mm_derivative}),
@@
 
-The cubic identity, strangely enough, pops up in the derivative of elementwise
-functions.
+The cubic identity, strangely enough, appear in the derivative of elementwise
+functions. Which is one of the reaspons I needed to expand my definition of
+identities beyond $\Ident^2(\vec{v})$, beyond my crushing identity crisis.
 
@@
 
-A final useful theorem happens to involve 0 overlap multiplication, which seams at first
-nonsensical given our definition of multiplication,
-but if you notice that the each element of a
-multiplication result is the sum over every index in the dimensionality of the
-portion of the shape vector of that overlapping length, and you consider that every
-vector could be said to 'start' and 'end' with an empty vector (as the concatenation of
-an empty vector does not change the vector), then it makes sense that this zero-length
-overlap always exists and is one and only one vector. That is, $\{\}$.
+A final useful theorem (definition?) happens to involve 0 overlap multiplication.
+You'll notice that I very carefully constructed my definition to allow for this
+definition (theorem?). Does it still count as a theorem if it's only true because
+I worked over the definition of multimatrix multiplication to make it true? I feel
+a bit like Tommy Wiseau writing my own sex scene into the script... twice... God,
+what a tool.
 
 \begin{theorem}[Zero Overlap Multiplication]
-So if $|A| = \vec{a}$ and $|B| = \vec{b}$, for every $\bar{a} \in \Dim(\vec{a})$
+Anyways, if $|A| = \vec{a}$ and $|B| = \vec{b}$, for every $\bar{a} \in \Dim(\vec{a})$
 and $\bar{b} \in \Dim(\vec{b}):$
@@
 \[ (A \mmult{0} B)[\bar{a} \oplus \bar{b}] = A[\bar{a}] B[\bar{b}] \]
-\end{theorem}
-
-\subsection*{Exercises}
-TODO
-
-\section{Other Operations With Multimatricies}
+
+\end{theorem}
+\begin{proof}
+\begin{align*}
+	(A \mmult{0} B)[\bar{a} \oplus \bar{b}]
+	&=
+	\sum_{\forall \bar{v} \in \Dim(\left<\right>)}
+	A[\bar{a} \oplus \bar{v}] B[\bar{v} \oplus \bar{b}] \\
+	&=
+	\sum_{\forall \bar{v} \in \left\{\left<\right>\right\}}
+	A[\bar{a} \oplus \bar{v}] B[\bar{v} \oplus \bar{b}] \\
+	&=
+	A[\bar{a} \oplus \left<\right>] B[\left<\right> \oplus \bar{b}] \\
+	&=
+	A[\bar{a}] B[\bar{b}] \\
+\end{align*}
+\end{proof}
+
+\section*{Exercises}
+
+\begin{exercise}
+Let $A$, $B$, and $C$ be multimatricies such that $|A| = \left<1,2,3\right>$,
+$|B| = \left<3,1,2\right>$ and $|C| = \left<3,2,1\right>$. For each of these
+multiplications determine if it is valid, and if so, what the resulting
+shape would be:
+\begin{enumerate}
+\item $A \mmult{2} B$
+\item $B \mmult{2} A$
+\item $A \mmult{2} C$
+\item $A \mmult{1} C$
+\end{enumerate}
+\end{exercise}
+
+\begin{exercise}
+In which of these cases does $A \mmult{m} (B \mmult{n} C) = (A \mmult{m} B) \mmult{n} C$?
+\begin{enumerate}
+\item When,
+	\begin{itemize}
+		\item $|A| = \left<3, 7, 9\right>$
+		\item $|B| = \left<9, 5\right>$
+		\item $|C| = \left<5, 7, 3\right>$
+		\item and $m = n = 1$
+	\end{itemize}
+\item When,
+	\begin{itemize}
+		\item $|A| = \left<6, 6, 6\right>$
+		\item $|B| = \left<6, 6, 6\right>$
+		\item $|C| = \left<6, 6, 6\right>$
+		\item and $m = n = 2$
+	\end{itemize}
+\item When,
+	\begin{itemize}
+		\item $|A| = \left<3, 5, 3\right>$
+		\item $|B| = \left<5, 3, 11\right>$
+		\item $|C| = \left<11, 2, 7\right>$
+		\item $m = 2$
+		\item and $n = 1$
+	\end{itemize}
+\item When,
+	\begin{itemize}
+		\item $|A| = \left<3, 5, 3\right>$
+		\item $|B| = \left<5, 3, 3, 5\right>$
+		\item $|C| = \left<3, 3, 5, 2\right>$
+		\item $m = 2$
+		\item and $n = 3$
+	\end{itemize}
+\end{enumerate}
+\end{exercise}
+
+\begin{exercise}
+Let $|X| = \vec{x}$. Simplify the following where possible:
+\begin{enumerate}
+\item $\Ident^5(\vec{x}) \mmult{3 |\vec{x}|} \Ident^3(\vec{x})$
+\item $\Ident^2(\vec{x}) \mmult{|\vec{x}|} X$
+\item $\Ident^3(\vec{x}) \mmult{2|\vec{x}|} X$
+\item $\Ident^2(\vec{x}) \mmult{|\vec{x}|} \left(X \mmult{|\vec{x}|} \Ident^3(|\vec{x}|)
+				\right) \mmult{2|\vec{x}|} \Ident^3(|\vec{x}|)$
+\end{enumerate}
+\end{exercise}
+
+\begin{exercise}
+Let $M$ be some multimatrix such that $|M| = \left<5,2,3\right>$. Then what is
+$dM/dM$?
+\end{exercise}
+
+\begin{exercise}
+Let $Y = \tan(X)$ be the elementwise application of the scalar tangent function to
+the elements of $X$, that is, for all $\bar{v} \in \Dim(|X|)$
+\[ Y[\bar{v}] = \tan(X[\bar{v}]) \]
+What is $dY/dX$?
+\end{exercise}
+
+\chapter{Other Operations With Multimatricies}
 
@@
 
-\subsection{Scalars}
+\section{Scalars}
 
@@
 
-\subsection{Addition}
+\section{Addition}
 
@@
 
-\subsection{Transposition}
+\section{Transposition}
 
@@
 
-\subsection*{Exercises}
+\section*{Exercises}
 TODO
 
-\section{Generic Derivative Rules}
+\chapter{Generic Derivative Rules}
 
@@
 
-\section{Machine Learning Specific Derivatives}
+\chapter{Machine Learning Specific Derivatives}
 
@@
 
-\section{Integration}
+\chapter{Integration}
 
@@
 
-\section{Solutions to the Exercises}
-
-\subsection*{Section 1 Solutions}
+\chapter{Solutions to the Exercises}
+
+\section*{Chapter 1 Solutions}
+
+\begin{solution}
+\begin{enumerate}
+\item[]
+\item True
+\item False, $\Dim(\left<5,5,5\right>)$ contains only vectors in $\mathbb{N}^3$ 
+\item False, the last value of $\left<1,2,3\right>$, $3$, is greater than it's
+						 corresponding value in $\left<3,2,1\right>$, which is $1$.
+\item True
+\end{enumerate}
+\end{solution}
+
+\begin{solution}
+\[ \left|\frac{dF}{dX}\right| = \left<6,7,3,7,2\right> \]
+\end{solution}
+
+\begin{solution}
+\[ \left|\frac{df}{dX}\right| = |X| = \left<2,3,2\right> \]
+\[ \frac{df}{dX}[\bar{v}] = 1 \]
+\end{solution}
+
+\begin{solution}
+\[ \left|\frac{df}{dX}\right| = |X| = \left<2,3,2\right> \]
+\[ \frac{df}{dX}[\bar{v}] = 1 \]
+\end{solution}
+
+\section*{Chapter 2 Solutions}
 

### 2019-06-20 Math/paper.tex
Added a proof.

@@
 
-That definition seems rather arbitrary, but you'll see various orders of identity
-pop up in derivatives down the line. For now, let's just look at how the
+That definition seems rather arbitrary but stick with me, I know what I'm
+talking about. I've got a \sout{doctorate}
+masters degree in \sout{mathematics} \sout{a real engineering field}, fine, software
+engineering. Whatever. Just look at how the
 square identity it relates to a multiplication operation.
@@
 functions. Which is one of the reaspons I needed to expand my definition of
-identities beyond $\Ident^2(\vec{v})$, beyond my crushing identity crisis.
+identities beyond $\Ident^2(\vec{v})$.
 
@@
 You'll notice that I very carefully constructed my definition to allow for this
-definition (theorem?). Does it still count as a theorem if it's only true because
-I worked over the definition of multimatrix multiplication to make it true? I feel
+definition (theorem?). Does it still count as a theorem if it only works because
+I tweeked the definition of multimatrix multiplication to make it fit? I feel
 a bit like Tommy Wiseau writing my own sex scene into the script... twice... God,
@@
 \begin{displayquote}
-``When the light turns green, you go. When the light turns red, you stop.
-But what do you do when the light turns blue with orange and lavender spots?''
-- Shel Silverstein, 'A Light in the Attic'
+``You can't just start a section with a subsection heading. At least put a quote
+in there or something,'' - Dr. William Tepfenhart 
 \end{displayquote}
 
-Other operations include...
-
 \section{Scalars}
+
+One of those obvious operations we'll need to do is multiply
+a multimatrix by a constant. I guess that means we need another definition,
 
@@
 
-Note that by our definitions of scalar and multimatrix derivatives and multiplication,
-we can model scalars in either case as multimatricies with shape $\{\}$.
+But actually, you'll find that scalars can be modeled equally well by multricies
+with the shpe $\left<\right>$. It works with multiplication and derivatives. Look:
 
@@
 
-In other words, let $s \in \mathbb{R}$ and $S \in \mathbb{R}^{\{\}}$ such that
-$S[\{\}] = s$. Then, for any multimatrix $A$, 
+In other words, let $s \in \mathbb{R}$ and $S \in \mathbb{R}^{\left<\right>}$ such that
+$S[\left<\right>] = s$. Then, for any multimatrix $A$, 
 \[ sA = As = S \mmult{0} A = A \mmult{0} S \]
@@
 	&= (s)A[\bar{a}] \\
-	&= S[\{\}]A[\bar{a}] \\
-	&= \sum_{\forall \bar{c} \in \Dim(\{\})}
-		S[\{\} \oplus \bar{c}]A[\bar{c} \oplus \bar{a}] \\
-	&= (S \mmult{0} A)[\{\} \oplus \bar{a}] \\
+	&= S[\left<\right>]A[\bar{a}] \\
+	&= \sum_{\forall \bar{c} \in \Dim(\left<\right>)}
+		S[\left<\right> \oplus \bar{c}]A[\bar{c} \oplus \bar{a}] \\
+	&= (S \mmult{0} A)[\left<\right> \oplus \bar{a}] \\
 	&= (S \mmult{0} A)[\bar{a}] \\
 \end{align}
-Note that step 3 is valid because $\bar{c}$ can only be $\{\}$ and
-$\{\} \oplus \bar{a} = \bar{a}$. So, $sA = S \mmult{0} A$.
+Note that step 3 is valid because $\bar{c}$ can only be $\left<\right>$ and
+$\left<\right> \oplus \bar{a} = \bar{a}$. So, $sA = S \mmult{0} A$.
 Finally, by similiar reasoning,
@@
 	&= A[\bar{a}](s) \\
-	&= A[\bar{a}]S[\{\}] \\
-	&= \sum_{\forall \bar{c} \in \Dim(\{\})}
-		A[\bar{a} \oplus \bar{c}] S[\bar{c} \oplus \{\}] \\
-	&= (A \mmult{0} S)[\bar{a} \oplus \{\}] \\
+	&= A[\bar{a}]S[\left<\right>] \\
+	&= \sum_{\forall \bar{c} \in \Dim(\left<\right>)}
+		A[\bar{a} \oplus \bar{c}] S[\bar{c} \oplus \left<\right>] \\
+	&= (A \mmult{0} S)[\bar{a} \oplus \left<\right>] \\
 	&= (A \mmult{0} S)[\bar{a}]
@@
 
-Noticing this lead me to suspect that the same might be true of my definitions
-of the derivative rules. A quick check confirmed that the dimensionality
-worked out, and it seems intuitive that we would always be able to treat scalars
-as empty-shape multimatricies if multiplication workes, but let's formalize that
-assertion.
+It wasn't until I noticed this that I began to suspect that the same might be true
+of the derivative rules.
+A quick check confirmed that the dimensionality worked out and it seems intuitive
+that we would always be able to treat scalars
+as empty-shape multimatricies, but let's canonize it.
 
@@
 \label{s_mm_domain_equiv}
+That really rolls off the tongue.
+
 Let $F(x)$ be a function $F : \mathbb{R} \to \mathbb{R}^{\vec{f}}$. And let
-$G(X)$ be an equivalent function, $G : \mathbb{R}^{\{\}} \to \mathbb{R}^{\vec{f}}$
-such that for all $X \in \mathbb{R}^{\{\}}$ it is true that $G(X) = F(X[\{\}])$
+$G(X)$ be an equivalent function,
+$G : \mathbb{R}^{\left<\right>} \to \mathbb{R}^{\vec{f}}$
+such that for all $X \in \mathbb{R}^{\left<\right>}$ it is true that
+$G(X) = F(X[\left<\right>])$
 Then,
@@
 \begin{proof}
-TODO
+Let $\bar{f} \in \Dim(\vec{f})$ then for $F(x)[\vec{f}] = G(X)[\vec{f}]$.
+Since $\partial F(x)[\vec{f}] / \partial x$ is defined as the rate of
+change of $F(x)[\vec{f}]$ with respect to $x$, it stands to reason that,
+$\partial F(X[\left<\right>])[\vec{f}] / \partial X[\left<\right>]$ is
+equivalent by definition. By are given $G(X) = F(X[\left<\right>])$ we
+can then also say that,
+\[
+\frac{ \partial F(X[\left<\right>])[\vec{f}] }{ \partial X[\left<\right>] }
+=
+\frac{ \partial G(X)[\vec{f}] }{ \partial X[\left<\right>] }
+\]
+Therefore, by our definitions of derivatives,
+\[
+\frac{ d F(x) }{ d x }
+=
+\frac{ d G(X) }{ d X }
+\]
 \end{proof}
@@
 \begin{theorem}[Empty Shape Multimatrix and Scalar Range Derivative Equivalence]
-\label{s_mm_range_equiv}
+\label{s_mm_range_equiv} Or `E.S.M.a.S.R.D.E', for short.
+
 Let $f(X)$ be a function $f : \mathbb{R}^{\vec{x}} \to \mathbb{R}$. And let
-$F(X)$ be an equivalent function, $F : \mathbb{R}^{\vec{x}} \to \mathbb{R}^{\{\}}$
-such that for all $X \in \mathbb{R}^{\vec{x}}$ it is true that $F(X)[\{\}] = f(X)$
+$F(X)$ be an equivalent function,
+$F : \mathbb{R}^{\vec{x}} \to \mathbb{R}^{\left<\right>}$
+such that for all $X \in \mathbb{R}^{\vec{x}}$ it is true that
+$F(X)[\left<\right>] = f(X)$
 Then,
@@
 		\right)
-		,|\{\} \oplus \vec{x}|
+		,|\left<\right> \oplus \vec{x}|
 	\right) \\

### 2019-06-24 Math/paper.tex
Adding some arguments.

@@
 \newtheorem{solution}{Solution}
+
+\newenvironment{argument}{\noindent\textit{Argument.}}{\hfill$\square$}
 
@@
 ``You can't just start a section with a subsection heading. At least put a quote
-in there or something,'' - Dr. William Tepfenhart 
+in there or something,'' - Dr. William Tepfenhart, my software architecture professor.
 \end{displayquote}
@@
 So $sA = As$. Also,
-\begin{align}
+\begin{align*}
 	(sA)[\bar{a}]
@@
 		S[\left<\right> \oplus \bar{c}]A[\bar{c} \oplus \bar{a}] \\
+	&= \sum_{\forall \bar{c} \in \{\left<\right>\}}
+		S[\left<\right> \oplus \bar{c}]A[\bar{c} \oplus \bar{a}] \\
+	&= S[\left<\right> \oplus \left<\right>]A[\left<\right> \oplus \bar{a}] \\
+	&= S[\left<\right>]A[\bar{a}] \\
 	&= (S \mmult{0} A)[\left<\right> \oplus \bar{a}] \\
 	&= (S \mmult{0} A)[\bar{a}] \\
-\end{align}
-Note that step 3 is valid because $\bar{c}$ can only be $\left<\right>$ and
-$\left<\right> \oplus \bar{a} = \bar{a}$. So, $sA = S \mmult{0} A$.
+\end{align*}
+So, $sA = S \mmult{0} A$.
 Finally, by similiar reasoning,
@@
 		A[\bar{a} \oplus \bar{c}] S[\bar{c} \oplus \left<\right>] \\
+	&= \sum_{\forall \bar{c} \in \{\left<\right>\}}
+		A[\bar{a} \oplus \bar{c}] S[\bar{c} \oplus \left<\right>] \\
+	&= A[\bar{a} \oplus \left<\right>] S[\left<\right> \oplus \left<\right>] \\
+	&= A[\bar{a}]S[\left<\right>] \\
 	&= (A \mmult{0} S)[\bar{a} \oplus \left<\right>] \\
@@
 \end{theorem}
-\begin{proof}
+\begin{argument}
 Let $\bar{f} \in \Dim(\vec{f})$ then for $F(x)[\vec{f}] = G(X)[\vec{f}]$.
@@
 \]
-\end{proof}
+\end{argument}
 
@@
 \end{theorem}
-\begin{proof}
-TODO
-\end{proof}
+\begin{argument}
+Let $\bar{x} \in \Dim(\vec{x})$. We note that as $\partial f(X) / \partial X[\bar{x}]$
+is defined as the rate of change of $f(X)$ as $X[\bar{x}]$ changes, and each value of
+$f(X)$ is equal to $F(X)[\left<\right>]$, we can reason that the rate of change of
+$F(X)[\left<\right>]$ as $X[\bar{x}]$ changes is equal to the rate of change of $f(X)$
+as $X[\bar{x}]$ changes. That is,
+\[
+	\frac{\partial f(X)}{\partial X[\bar{x}]}
+		=
+	\frac{\partial F(X)[\left<\right>]}{\partial X[\bar{x}]}
+\]
+And so by our definition of derivatives,
+\[ \frac{df(X)}{dX} = \frac{dF(X)}{dX} \]
+\end{argument}
 
 \section{Addition}
+
+Ah addition. What can I say about multimatrix addition that hasn't been
+said so many times before. Well... anything, actually. I don't think anyone's
+written about multimatrix addition before. Probably should define it first
+though.
 
@@
 
+Multimatrix subtraction is defined as the inverse of multimatrix addition.
+
 \begin{definition}[Multimatrix Subtraction]
 Let $A, B \in \mathbb{R}^{\vec{x}}$. Then,
+\[ (A + B) - B = A \]
+\end{definition}
+
+The following should be obvious,
+
+\begin{theorem}[Equivalent Addition for Subtraction]
+\label{eq_add_sub_thm}
+For any multimatricies $A$ and $B$ where $|A| = |B|$,
 \[ A - B = A + (-1)B \]
-It should be obvious that, as with scalars, multimatrix subtraction is the
-inverse of addition. In other words, $(A + B) - B = A$
-\end{definition}
+\end{theorem}
+\begin{proof}
+Left as an exercise for the reader (Exercise \ref{eq_add_sub_ex}).
+\end{proof}
 
@@
 \begin{theorem}[Communicativity of scalar Multiplication and Transposition]
+Let $s$ be a scalar, $x$ be in $\mathbb{Z}^{+} \cup \{0\}$, and $A$ be
+a multimatrix on which $\Tran(A, x)$ is defined. Then,
 \[ s\Tran(A, x) = \Tran(sA, x) \]
@@
 \begin{proof}
-TODO
+Let $|A| = \vec{x} \oplus \vec{a}$ where $|\vec{x}| = x$. Then
+let $\bar{x} \in \Dim(\vec{x})$ and $\bar{a} \in \Dim(\vec{a})$. So,
+\begin{align*}
+  (s\Tran(A, x))[\bar{a} \oplus \bar{x}]
+  &= s \Tran(A, x)[\bar{a} \oplus \bar{x}] \\
+  &= s A[\bar{x} \oplus \bar{a}] \\
+  &= (s A)[\bar{x} \oplus \bar{a}] \\
+  &= \Tran(sA, x)[\bar{a} \oplus \bar{x}]
+\end{align*}
+Therefore $s\Tran(A, x) = \Tran(sA, x)$.
 \end{proof}
@@
 \begin{proof}
-TODO
+Let $|A| = \vec{x} \oplus \vec{y} \oplus \vec{a}$ where $|\vec{x}| = x$ and
+$|\vec{y}| = y$. Note that,
+\[ |\Tran(A, x)| = \vec{y} \oplus \vec{a} \oplus \vec{x} \]
+And,
+\[ |\Tran(\Tran(A, x), y)| = \vec{a} \oplus \vec{x} \oplus \vec{y} \]
+Also that,
+\[ |\Tran(A, x+y)| = \vec{a} \oplus \vec{x} \oplus \vec{y} \]
+So $|\Tran(\Tran(A, x), y)| = \Tran(A, x+y)$ which is necessary but not
+sufficient for this proof.
+
+To show the elementwise equivalence, let $\bar{x} \in \Dim(\vec{x})$,
+$\bar{y} \in \Dim(\vec{y})$, and $\bar{a} \in \Dim(\vec{a})$. Then,
+\begin{align*}
+  \Tran(\Tran(A, x), y)[\bar{a} \oplus \bar{x} \oplus \bar{y}]
+  &= A[\bar{x} \oplus \bar{y} \oplus \bar{a}] \\
+  &= \Tran(A, x+y)[\bar{a} \oplus \bar{x} \oplus \bar{y}]
+\end{align*}
+Which shows that $\Tran(\Tran(A, x), y) = \Tran(A, x+y)$
 \end{proof}
@@
 \section*{Exercises}
+
+\begin{exercise}
+\label{eq_add_sub_ex}
+Prove Theorem \ref{eq_add_sub_thm}.
+\end{exercise}
+
 TODO

### 2019-06-24 Math/paper.tex
Adding exercises and an example for transposes.

@@
 
-The following should be obvious,
+The following should be obvious, condesendingly so,
 
@@
 
-A little less obvious is that multimatrix multiplication can be distributed over
-it's addition.
+A little less obvious, in that a coffee-deprived undergraduate might
+struggle with it for a second, is that multimatrix multiplication can be
+distributed over it's addition.
 
@@
 
-But it should be obvious that that the same applies to scalar 
-multiplication distributing over multimatrix addition..
+But it should be obvious - seriously, how have you not figured this out yet -
+that that the same applies to scalar  multiplication distributing over multimatrix
+addition..
 \begin{theorem}[Scalar on Multimatrix Distributive Property]
@@
 \section{Transposition}
+
+Multimatrix transposition clearly requires an additional parameter defining where
+the cut happens in the shape vector.
 
@@
 
+Here's an example - get out your crayons and follow along.
+
+\begin{example}
+Let's construct some multimatrix, $M$, with a shape:
+\[ |M| = \left<3,2,7,5,9\right> \]
+Then lets take the first transpose of that
+multimatrix:
+\[ |\Tran(M, 1)| = \left<2,7,5,9,3\right> \]
+And... how about the third:
+\[ |\Tran(M, 3)| = \left<5,9,3,2,7\right> \]
+You can see, it's as though I cut off the front of the shape vector and transfered
+it to the end of the vector.
+
+You do the same thing with indicies. So,
+\[ M[1,2,3,4,5] = \Tran(M, 3)[4,5,1,2,3] \]
+\end{example}
+
 \begin{theorem}[Inverse Transpose]
@@
 
-\begin{theorem}[Communicativity of scalar Multiplication and Transposition]
+\begin{theorem}[Communicativity of Scalar Multiplication and Transposition]
 Let $s$ be a scalar, $x$ be in $\mathbb{Z}^{+} \cup \{0\}$, and $A$ be
@@
 Therefore $s\Tran(A, x) = \Tran(sA, x)$.
+\end{proof}
+
+\begin{theorem}[Communicativity of Addition and Transposition]
+\label{com_add_tran_thm}
+Let $x$ be in $\mathbb{Z}^{+} \cup \{0\}$ and let $A$ and $B$ be
+multimatricies such that $|A| = |B|$ and $\Tran(A, x)$ is defined.
+Then,
+\[ \Tran(A, x) + \Tran(B, x) = \Tran(A+B, x) \]
+\end{theorem}
+\begin{proof}
+Left as an exercise for the reader (Exercise \ref{com_add_tran_ex}).
 \end{proof}
@@
 \label{eq_add_sub_ex}
-Prove Theorem \ref{eq_add_sub_thm}.
+Prove Theorem \ref{eq_add_sub_thm} which is that,
+\[ A - B = A + (-1)B \]
 \end{exercise}
 
-TODO
+\begin{exercise}
+\label{com_add_tran_ex}
+Prove Theorem \ref{com_add_tran_thm} which is that,
+\[ \Tran(A, x) + \Tran(B, x) = \Tran(A+B, x) \]
+\end{exercise}
+
+\begin{exercise}
+Let $A$ be a multimatrix such that $|A| = <1,2,3,4,5>$,
+Find the shape of the following trasnposes:
+\begin{enumerate}
+\item $|\Tran(A, 3)| = ?$
+\item $|\Tran(A, 4)| = ?$
+\item $|\Tran(A, 5)| = ?$
+\item $|\Tran(A, 0)| = ?$
+\end{enumerate}
+\end{exercise}
+
+\begin{exercise}
+Let $M$ be any multimatrix.
+Find the value, in terms of $M$, of the following equations.
+For example $\Tran(M, 1)[2,3,4,5,1] = M[1,2,3,4,5]$
+\begin{enumerate}
+\item $\Tran(M, 3)[1,2,3,4] = ?$
+\item $\Tran(M, 0)[6,5,3] = ?$
+\item $\Tran(M, 2)[1,1,1] = ?$
+\end{enumerate}
+\end{exercise}
 

### 2019-06-25 Math/paper.tex
Added right multiplicative derivative proof.

@@
 
+I'll give you a theorem here and make you prove it yourself because I'm a jerk.
+\begin{theorem}[Dimensional Set and Index Concatenation]
+\label{dim_set_ind_concat_thm}
+If $\bar{a} \in \Dim(\vec{a})$ and $\bar{b} \in \Dim(\vec{b})$ then,
+\[ \bar{a} \oplus \bar{b} \in \Dim(\vec{a} \oplus \vec{b}) \]
+\end{theorem}
+\begin{proof}
+Left as an exercise for the reader (Exercise \ref{dim_set_ind_concat_ex}).
+\end{proof}
+
 Going back to our original motivating problem, we (that is to say, myself and my
@@
 \section*{Exercises}
+
+\begin{exercise}
+\label{dim_set_ind_concat_ex}
+Prove Theorem \ref{dim_set_ind_concat_thm}. Which is that,
+\[ \bar{a} \oplus \bar{b} \in \Dim(\vec{a} \oplus \vec{b}) \]
+\end{exercise}
 
@@
 \label{right_mult_derivative}
+Let $A$ and $X$ be multimatricies such that $A \mmult{n} X$ is
+defined. Then,
 \[ \frac{d(A \mmult{n} X)}{dX} = A \mmult{n} \Ident^2(|X|) \]
@@
 \begin{proof}
-TODO
+Let $|A| = \vec{a} \oplus \vec{n}$ and $|X| = \vec{n} \oplus \vec{x}$
+where $|\vec{n}| = n$ which is equivalent to saying $A \mmult{n} X$ is defined.
+Also let $\bar{a} \in \Dim(\vec{a})$, $\bar{n} \in \Dim(\vec{n})$,
+$\bar{x}_1 \in \Dim(\vec{x})$ and $\bar{x}_2 \in \Dim(\vec{x})$.
+Then, starting with the definition of the derivative,
+\begin{align*}
+  \frac{d(A\mmult{n}X)}{dX}[\bar{a} \oplus \bar{x}_1 \oplus \bar{n} \oplus \bar{x}_2]
+  &=
+  \frac{
+    \partial (A \mmult{n} X)[\bar{a} \oplus \bar{x}_1]
+  }{
+    \partial X[\bar{n} \oplus \bar{x}_2]
+  } \\
+  &=
+  \frac{
+    \partial \left(
+      \sum_{\forall \bar{m} \in \Dim(\vec{n})}
+        A[\bar{a} \oplus \bar{m}]
+        X[\bar{m} \oplus \bar{x}_1]
+    \right)
+  }{
+    \partial X[\bar{n} \oplus \bar{x}_2]
+  } \\
+  &=
+  \sum_{\forall \bar{m} \in \Dim(\vec{n})}
+    \frac{
+      \partial 
+      A[\bar{a} \oplus \bar{m}]
+      X[\bar{m} \oplus \bar{x}_1]
+    }{
+      \partial X[\bar{n} \oplus \bar{x}_2]
+    } \\
+  &=
+  \left(
+    \sum_{\forall \bar{m} \ne \bar{n}} 0
+  \right)
+  +
+  \left(
+    \sum_{\forall \bar{m} = \bar{n}}
+    \frac{
+      \partial 
+      A[\bar{a} \oplus \bar{m}]
+      X[\bar{m} \oplus \bar{x}_1]
+    }{
+      \partial X[\bar{n} \oplus \bar{x}_2]
+    }
+  \right) \\
+  &=
+  \frac{
+    \partial 
+    A[\bar{a} \oplus \bar{n}]
+    X[\bar{n} \oplus \bar{x}_1]
+  }{
+    \partial X[\bar{n} \oplus \bar{x}_2]
+  } \\
+  &= A[\bar{a} \oplus \bar{n}] \delta_{\bar{x}_1 \bar{x}_2}
+\end{align*}
+Then, note that,
+\begin{align*}
+  A \mmult{n} \Ident^2(|X|)[\bar{a} \oplus \bar{x}_1 \oplus \bar{n} \oplus \bar{x}_2]
+  &=
+  \sum_{\forall \bar{m} \in \Dim(\vec{n})}
+  A[\bar{a} \oplus \bar{m}]
+  \Ident^2(|X|)[\bar{m} \oplus \bar{x}_1 \oplus \bar{n} \oplus \bar{x}_2] \\
+  &=
+  \sum_{\forall \bar{m} \in \Dim(\vec{n})}
+  A[\bar{a} \oplus \bar{m}]
+  \delta_{\bar{m} \bar{n}}
+  \delta_{\bar{x}_1 \bar{x}_2} \\
+  &=
+  \left(
+    \sum_{\forall \bar{m} \ne \bar{n}} 0
+  \right)
+  +
+  \left(
+    \sum_{\forall \bar{m} = \bar{n}}
+    A[\bar{a} \oplus \bar{m}]
+    \delta_{\bar{m} \bar{n}}
+    \delta_{\bar{x}_1 \bar{x}_2}
+  \right) \\
+  &=
+  A[\bar{a} \oplus \bar{n}]
+  \delta_{\bar{n} \bar{n}}
+  \delta_{\bar{x}_1 \bar{x}_2} \\
+  &=
+  A[\bar{a} \oplus \bar{n}]
+  \delta_{\bar{x}_1 \bar{x}_2}
+\end{align*}
+So, 
+\[
+  \frac{d(A\mmult{n}X)}{dX}[\bar{a} \oplus \bar{x}_1 \oplus \bar{n} \oplus \bar{x}_2]
+  =
+  A \mmult{n} \Ident^2(|X|)[\bar{a} \oplus \bar{x}_1 \oplus \bar{n} \oplus \bar{x}_2]
+\]
+For all $\bar{a}$, $\bar{x}_1$, $\bar{n}$ and $\bar{x}_2$. Therefore,
+\[
+  \frac{d(A\mmult{n}X)}{dX}
+  =
+  A \mmult{n} \Ident^2(|X|)
+\]
 \end{proof}

### 2019-06-26 Math/paper.tex
Some gramatical and formatting fixes.

@@
 \usepackage{mathtools}
+% Use pdflscape for pdf viewers
 \usepackage{pdflscape}
+% Use lscape for printing as a book
+%\usepackage{lscape}
 \usepackage{etoolbox}
@@
 
-\newtheoremstyle{solution}{}{}{}{}{}{:}{\newline}{Exercise \thmnumber{#2} Solution}
+\newcounter{solutionctr}
+\newtheoremstyle{solution}{}{}{}{}{}{:}{\newline}{
+  Exercise \refstepcounter{solutionctr}\thesolutionctr~Solution}
 \theoremstyle{solution}
 \newtheorem{solution}{Solution}
+\newcommand{\solutionsection}[1]{
+  \section{Chapter~#1 Solutions}\setcounter{solutionctr}{0}}
 
@@
 
-\AtBeginEnvironment{section}{\setcounter{solution}{0}}
 \AtBeginEnvironment{proof}{\setcounter{ppart}{0}}
@@
 \chapter*{Preface}
-I was working my way through a hobby programming project, trying to manifest Skynet
-as more than the apocalyptic fever dream of James Cameron, and ran into a problem.
+I was working my way through a hobby programming project, trying to get my
+machine to do some learning, and ran into a problem.
 The existing notation for taking derivatives of matrix equations is terrible.
@@
 mathematicians is actively working to sabotage our glorious yet-to-be-built
-robot overlords.
-
-That sort of justice cannot stand!
+AI overlords. I, for one, will not stand for such blasphemy.
 
@@
 
-\chapter{Defining the Derivative}
+\chapter{The Multimatrix and Its Derivative}
 
@@
 \end{displayquote}
+
+\section{Motivating the Multimatrix}
 
@@
 Every student's belief in a higher power changes with respect to their own
-scientific education level, but does not change with respect to other students'
+scientific education level but does not change with respect to other students'
 scientific education. No mater how much I teach Jane about photosynthesis, I'm
@@
 a multidimensional matrix. It has four dimensions of indices, rather than just
-a row and column, but each uniquely indexed cell in this object may have a
+a row and column but each uniquely indexed cell in this object may have a
 unique value, just like a standard two dimensional matrix. Let's define this
@@
 A multimatrix $M$ is a multidimensional object that has some shape,
-$\vec{v} \in \mathbb{N}^n$, where $n \in \mathbb{Z}^+ \cup \{0\}$
+$\vec{v} \in \mathbb{N}^n$, where $n \in \mathbb{N} \cup \{0\}$
 is the number of dimensions of $M$.
@@
 \end{proof}
+
+\section{Defining the Derivative}
 
@@
 
-\section*{Exercises}
+\section{Exercises}
 
@@
 
+\section{Defining Multiplication}
+
 The multiplication of traditional matricies is a calculation that, when one first
-encouters it, inspires thoughts such as ``By which satanic cult was this process
-proscribed?''
+encouters it, inspires thoughts such as, ``What the shit?'' or, ``Get me a knife,
+I gotta to stab someone.''
 
@@
 $|B| = \vec{c} \oplus \vec{b}$, and $|\vec{c}| = n$ with
-$n \in \{0\} \cup \mathbb{Z}^{+}$. We shall call $n$ the 'size' or the 'width'
+$n \in \{0\} \cup \mathbb{N}$. We shall call $n$ the 'size' or the 'width'
 or the 'overlap' of the multiplication operation.
@@
 
+\section{Rules of Multimatrix Multiplication}
+
 Like two dimensional matrix multiplication, multimatrix multiplication is
@@
 Let $A$, $B$, and $C$ be multimatricies and $m$ and $n$ in
-$\left\{ 0 \right\} \cup \mathbb{Z}^{+}$.
+$\{0\} \cup \mathbb{N}$.
 If both operations $(A \mmult{m} B) \mmult{n} C$ and $A \mmult{m} (B \mmult{n} C)$
@@
 
+\section{Multiplicative Identities}
+
 Multiplicative identities for multimatricies depend on the shape of the
@@
 \begin{theorem}[Identity Contraction]
-For all $m, n, k \in \mathbb{Z}^+$ and $\vec{x}$ as a valid multimatrix shape,
+For all $m, n, k \in \mathbb{N}$ and $\vec{x}$ as a valid multimatrix shape,
 where $m > k$ and $n > k$,
@@
 that we would always be able to treat scalars
-as empty-shape multimatricies, but let's canonize it.
+as empty-shape multimatricies but let's canonize it.
 
@@
 \begin{theorem}[Communicativity of Scalar Multiplication and Transposition]
-Let $s$ be a scalar, $x$ be in $\mathbb{Z}^{+} \cup \{0\}$, and $A$ be
+Let $s$ be a scalar, $x$ be in $\mathbb{N} \cup \{0\}$, and $A$ be
 a multimatrix on which $\Tran(A, x)$ is defined. Then,
@@
 \label{com_add_tran_thm}
-Let $x$ be in $\mathbb{Z}^{+} \cup \{0\}$ and let $A$ and $B$ be
+Let $x$ be in $\mathbb{N} \cup \{0\}$ and let $A$ and $B$ be
 multimatricies such that $|A| = |B|$ and $\Tran(A, x)$ is defined.
@@
 \begin{theorem}[Derivative of Sum]
+Let $X$ be any multimatrix, then,
 \[\frac{d\Sum(X)}{dX} = 1^{|X|}\]
@@
 \begin{proof}
-TODO
+Let $|X| = \vec{x}$ and $\bar{x} = \Dim(\vec{x})$. Then,
+\begin{align*}
+  \frac{d\Sum(X)}{dX}[\bar{x}]
+  &= \frac{\partial \Sum(X)}{\partial X[\bar{x}]} \\
+  &= \frac{
+    \partial \left(
+      \sum_{\forall \bar{y} \in \Dim(\vec{x})} X[\bar{y}]
+    \right)
+  }{
+    \partial X[\bar{x}]
+  } \\
+  &= \sum_{\forall \bar{y} \in \Dim(\vec{x})}
+  \frac{
+    \partial X[\bar{y}]
+  }{
+    \partial X[\bar{x}]
+  } \\
+  &= \left(
+    \sum_{\forall \bar{y} \ne \bar{x}} 0
+  \right)
+  +
+  \left(
+    \sum_{\forall \bar{y} = \bar{x}}
+    \frac{\partial X[\bar{y}]}{\partial X[\bar{x}]}
+  \right) \\
+  &= \frac{\partial X[\bar{x}]}{\partial X[\bar{x}]} \\
+  &= 1 \\
+  &= 1^{\vec{x}}[\bar{x}]
+\end{align*}
+So,
+\[\frac{d\Sum(X)}{dX} = 1^{|X|}\]
 \end{proof}
@@
 
-I think, I'm not sure, but I think that the integral of a multimatrix function should
+I think, I'm not sure but I think, that the integral of a multimatrix function should
 be defined,
@@
 
-Which, I have very little idea what that means geometriclly, but
+Which, I have very little idea what that means geometriclly but
 if you let $G(X) = \int_A^X F(Y) dY$ you seem to end up with $dG/dX = F(X)$.
@@
 
-\section*{Chapter 1 Solutions}
+\solutionsection{1}
 
@@
 
-\section*{Chapter 2 Solutions}
+\solutionsection{2}
 

### 2019-07-12 Math/paper.tex
Adding proof of transpose integer isomorphism.

@@
 
+\newtheoremstyle{case}{}{}{}{}{}{:}{ }{}
+\theoremstyle{case}
+\newtheorem{case}{Case}
+
 \newcounter{solutionctr}
@@
 \AtBeginEnvironment{proof}{\setcounter{ppart}{0}}
+\AtBeginEnvironment{proof}{\setcounter{case}{0}}
 \AtBeginEnvironment{align}{\setcounter{equation}{0}}
@@
 \DeclareMathOperator{\Sum}{\Sigma}
+\DeclareMathOperator{\remainder}{mod}
 %\newcommand{\mmult}[1]{\stackrel{\times}{#1}}
@@
 
-Let's consider a traditional matrix equation. As is traditional, one matrix
-$X$ shall represent the scientific education level of undergraduates, who happen
-to work in a densely packed 3 by 5 grid - which is also traditional. Then let
-$B$ represent the belief each of those undergradutes has in a higher power,
-which, as we all know, fluctuates with respect to their scientific education in
-a sinusoidal pattern (Weinersmith, 2010 \cite{weinersmith:education}).
+Let us consider a traditional matrix equation - one contrived on the spot for the
+purposes of adding an additional layer of confusion to the situation.
+
+As is tradition, let one matrix $X$ represent the scientific education level of
+undergraduates, who work in a densely packed 3 by 5 grid (which is also traditional).
+Then let $B$ represent the belief each of those undergradutes has in a higher power.
+
+It has been shown that an undergraduate's belief in a higher power fluctuates with
+respect to their scientific education in a sinusoidal pattern
+(Weinersmith, 2010 \cite{weinersmith:education}).
 
@@
 
-The ordering here is arbitrary, there is no reason why the dimensionality of
+The ordering here is arbitrary. There is no reason why the dimensionality of
 of the independent variable \textit{needs} to be concatenated to the right of the
@@
 be our convention since, for the purpose of this work, mine is the divinely revealed
-word of god, passed down to you lowly mortals who have yet to commit your
-own mad ramblings to \LaTeX.
+word of god, graciously passed down to you lowly mortals (I've typeset
+my mad ranblings with \LaTeX ~therefore they must be reasonably coherent. QED).
 
@@
 of $B$ with respect to $X$ is a multimatrix with shape $|B| \oplus |X|$,
-who's elements we can define as,
+whose elements we can define as,
 \[\forall \bar{b} \in \Dim(|B|), \bar{x} \in \Dim(|X|):\]
@@
 \begin{exercise}
-Are the following assertions are true or false?
+True or false?
 \begin{enumerate}
@@
 
-Easily done. The hard part isn't doing the calculation. The hard part is
-parlaying with Sheogorath, Daedric Prince of Madness for the intellectual
-property rights.
+Easily done. The hard part isn't doing the calculation. The hard part getting over
+your naive belief that mathematical operations should be rooted in some concrete
+concept rather than ``this is the way it's done because it makes the equations
+you'll see later work.''
 
 So now consider how we would multiply two matricies $A$ and $B$ if they had more
-than two dimensions. Let's use a concrete example to make the problems more apparent.
+than two dimensions. Let's use a concrete example to make the problems more
+structurally sound.
 Let $|A| = \left<5,7,7\right>$ and $|B| = \left<7,7,2,4\right>$.
@@
 so, we need to compleately abandon conventional algebras, and indeed any hope of
-returning to sanity. That's right, we're introducing a trinary operator.
+returning to sanity. That's right, we're introducing a ternary operator.
 
@@
 For any multiplication operation defined between multimatricies and scalars,
-the scalar may be replaced by an equivalent empty-shaped multimatrix who's
+the scalar may be replaced by an equivalent empty-shaped multimatrix whose
 single value is that of the scalar.
@@
 \begin{definition}[Multimatrix Transposition]
+\label{tran_def}
 Let $|X| = \vec{l} \oplus \vec{r}$ where $|\vec{l}| = l$ and $|\vec{r}| = r$
@@
 \[ \Tran(X, l)[\bar{r} \oplus \bar{l}] = X[\bar{l} \oplus \bar{r}] \]
+We call $l$ the index of transpose.
 \end{definition}
@@
 
-\begin{theorem}[Inverse Transpose]
-If $|X| = \vec{l} \oplus \vec{r}$
-\[ \Tran(\Tran(X, |\vec{l}|), |\vec{r}|) = X \]
-\end{theorem}
-\begin{proof}
-Let $|X| = \vec{l} \oplus \vec{r}$ then
-$\forall \bar{l} \in \Dim(\vec{l}), \bar{r} \in \Dim(\vec{r}) : $
-\[ \Tran(X, |\vec{l}|)[\bar{r} \oplus \bar{l}] = X[\bar{l} \oplus \bar{r}] \]
-And so,
-\begin{align*}
-	\Tran(\Tran(X, |\vec{l}|), |\vec{r}|)[\bar{l} \oplus \bar{r}]
-	&= \Tran(X, |\vec{l}|)[\bar{r} \oplus \bar{l}] \\
-	&= X[\bar{l} \oplus \bar{r}] \\
-\end{align*}
-Therefore, 
-\[ \Tran(\Tran(X, |\vec{l}|), |\vec{r}|) = X \]
-\end{proof}
+However, you'll see cases in later chapters of multimatrix transposes where
+the index of transpose is larger than the size of the shape matrix. So we need
+to make sense of that operation as well. Fortunately, there is a logical way
+to extend the definition. Consider that this transposition can be reasonably
+shown to be equivalent to moving the first index of the shape matrix
+to the end of the shape matrix over and over again, this can be done any number
+of times, therefore doing so for more than the size of the shape matrix still works,
+it just requires a bit of modular arithmetic.
+
+\begin{definition}[Multimatrix Transpose Extension]
+\label{tran_ext}
+For any multimatrix, the following transposes are equivalent,
+\[ \Tran(X, n) = \Tran(X, \remainder(n, ||X||)) \]
+Where $\remainder(n, ||X||)$ is the remainder of $n$ divided by $||X||$.
+That is, a value $0 \le \remainder(n, ||X||) < ||X||$ such that there exists an
+integer $k$ where, $n = k||X|| + \remainder(n, ||X||)$.
+\end{definition}
+
+This extension is consisent with the prevous definition because, for any
+index of transpose, $l$, that would be covered by the original definition,
+$0 \le l \le ||X||$, you can see that, in all but one case $\remainder(l, ||X||) = l$.
+The exception, $l = ||X||$ is covered by showing that
+$\remainder(||X||, ||X||) = 0$ and $\Tran(X, 0) = \Tran(X, ||X||)$.
+
+Thus, we (by which I mean \textit{me} since \textit{you} certainly haven't done any
+of the work) have shown a natural equivalent class \cite{book:abstract} of transpose
+operations. On multimatricies with a shape of some length $n$ there are $n$ unique
+transpose; $\Tran(X, i)$ for all $0 \le i < n$. All other transposes are equivalent
+to one of these base transposes by our extended definition.
+
+To make use of this equivalence, we need to first show how these classes are
+isomorphic \cite{book:abstract} to a more manageable group.
+
+\begin{theorem}[Isomorphism of Transpostion and Modular Integers]
+\label{tran_int_iso}
+Let $\mathbb{T}_n$ be the set of possible transpositions on multimatricies with
+shapes of length $n$. Let $\circ$ be the operation of composition. Then
+$(\mathbb{T}_n, \circ)$ is a group which is isomorphic to the group of
+integers mod $n$ under addition. That is,
+\[ (\mathbb{T}_n, \circ) \cong (\mathbb{Z}_n, +) \]
+\end{theorem}
+\begin{proof}
+I'll need to tackle this proof in two parts. First I'll need to show that
+that set of transpositions is a group under composition, then I'll need to
+provide a one-to-one and onto map that preseves the respective group operations
+between transpositions and integers mod $n$.
+
+\begin{ppart}
+To begin, I'll show that the set of all transpositions on multimatricies 
+with shapes of length $n$ form a group under composition.
+
+Let's look at the composition of some two transposes on a multimatrix.
+So, let $A$ be a multimatrix with shape of length $n$. Now let $x$ and $y$
+be indicies of transpositions. Then what is $\Tran(\Tran(A, x), y)$?
+To apply the the first transpose we need to break $|A|$ into two vectors,
+so let $|A| = \vec{l} \oplus \vec{r}$ where $|\vec{l}| = x$.
+
+Then,
+\[ |\Tran(A, x)| = \vec{r} \oplus \vec{l} \]
+And for all
+$\bar{l} \in \Dim(\vec{l})$ and $\bar{r} \in \Dim(\vec{r})$,
+\[ \Tran(A, x)[\bar{r} \oplus \bar{l}] = A[\bar{l} \oplus \bar{r}] \]
+
+Now to apply a transposition with index of transposition $y$ to $\Tran(A,x)$
+we need to break up $|\Tran(A,x)|$ into two vector, such as
+$|\Tran(A,x)| = \vec{l}' \oplus \vec{r}'$.
+
+Since we've already shown that $|\Tran(A,x)| = \vec{r} \oplus \vec{l}$
+we end up with two conceptual splits of that shape vector that need to
+be reconciled.
+
+\begin{case} $|\vec{l}'| \le |\vec{r}|$
+
+Then we can divide $|\Tran(A,x)|$ into three vectors, $\vec{a}$, $\vec{b}$, and $\vec{c}$
+such that
+\[ |\Tran(A,x)| = \vec{b} \oplus \vec{c} \oplus \vec{a} \]
+\[ \vec{l}' = \vec{b} \]
+\[ \vec{r}' = \vec{c} \oplus \vec{a} \]
+\[ \vec{r} = \vec{b} \oplus \vec{c} \]
+\[ \vec{l} = \vec{a} \]
+It helps to think of the $\oplus$ operation as a cut in two separate places in the same
+vector because of the two conceptual splits from the two transpositions to see why this
+logic is valid.
+
+So we can then say,
+\[ |A| = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
+
+And since,
+\[ |\Tran(\Tran(A, x), y)| = \vec{r}' \oplus \vec{l}' \]
+It follows that,
+\[ |\Tran(\Tran(A, x), y)| = \vec{c} \oplus \vec{a} \oplus \vec{b} \]
+
+Now, let $\bar{a} \in \Dim(\vec{a})$, $\bar{b} \in \Dim(\vec{b})$, and
+$\bar{c} \in \Dim(\vec{c})$. Notice that because of Theorem 
+\ref{dim_set_ind_concat_thm}, $\bar{c} \oplus \bar{a} \in \Dim(\vec{r}')$ and
+$\bar{b} \oplus \bar{c} \in \Dim(\vec{r})$.
+
+Continuing our definition of transposition,
+\begin{align*}
+  \Tran(\Tran(A, x), y)[\bar{c} \oplus \bar{a} \oplus \bar{b}]
+  &=
+  \Tran(A, x)[\bar{b} \oplus \bar{c} \oplus \bar{a}] \\
+  &=
+  A[\bar{a} \oplus \bar{b} \oplus \bar{c}]
+\end{align*}
+
+See now that this composit operation is also a transposition, $\Tran(A, z)$ where,
+$z = |\vec{a} \oplus \vec{b}|$.
+So by definition,
+\begin{align*}
+  |\Tran(A, z)|
+  &=
+  \vec{c} \oplus \vec{b} \oplus \vec{a} \\
+  &=
+  |\Tran(\Tran(A, x), y)|  
+\end{align*}
+And,
+\begin{align*}
+  \Tran(A, z)[\bar{c} \oplus \bar{a} \oplus \bar{b}]
+  &=
+  A[\bar{a} \oplus \bar{b} \oplus \bar{c}] \\
+  &=
+  \Tran(\Tran(A, x), y)[\bar{c} \oplus \bar{a} \oplus \bar{b}]
+\end{align*}
+\end{case}
+
+\begin{case} $|\vec{l}'| > |\vec{r}|$
+Then we can divide $|\Tran(A,x)|$ into three vectors, $\vec{a}$, $\vec{b}$, and $\vec{c}$
+such that
+\[ |\Tran(A,x)| = \vec{c} \oplus \vec{a} \oplus \vec{b} \]
+\[ \vec{l}' = \vec{c} \oplus \vec{a} \]
+\[ \vec{r}' = \vec{b} \]
+\[ \vec{r} = \vec{c} \]
+\[ \vec{l} = \vec{a} \oplus \vec{b} \]
+
+So we can then say,
+\[ |A| = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
+
+And since,
+\[ |\Tran(\Tran(A, x), y)| = \vec{r}' \oplus \vec{l}' \]
+It follows that,
+\[ |\Tran(\Tran(A, x), y)| = \vec{b} \oplus \vec{c} \oplus \vec{a} \]
+
+Now, let $\bar{a} \in \Dim(\vec{a})$, $\bar{b} \in \Dim(\vec{b})$, and
+$\bar{c} \in \Dim(\vec{c})$. Notice that because of Theorem 
+\ref{dim_set_ind_concat_thm}, $\bar{c} \oplus \bar{a} \in \Dim(\vec{l}')$ and
+$\bar{a} \oplus \bar{b} \in \Dim(\vec{l})$.
+
+Continuing our definition of transposition,
+\begin{align*}
+  \Tran(\Tran(A, x), y)[\bar{b} \oplus \bar{c} \oplus \bar{a}]
+  &=
+  \Tran(A, x)[\bar{c} \oplus \bar{a} \oplus \bar{b}] \\
+  &=
+  A[\bar{a} \oplus \bar{b} \oplus \bar{c}]
+\end{align*}
+
+See now that this composit operation is also a transposition, $\Tran(A, z)$ where,
+$z = |\vec{a}|$.
+So by definition,
+\begin{align*}
+  |\Tran(A, z)|
+  &=
+  \vec{b} \oplus \vec{c} \oplus \vec{a} \\
+  &=
+  |\Tran(\Tran(A, x), y)|  
+\end{align*}
+And,
+\begin{align*}
+  \Tran(A, z)[\bar{b} \oplus \bar{c} \oplus \bar{a}]
+  &=
+  A[\bar{a} \oplus \bar{b} \oplus \bar{c}] \\
+  &=
+  \Tran(\Tran(A, x), y)[\bar{b} \oplus \bar{c} \oplus \bar{a}]
+\end{align*}
+\end{case}
+
+So I've shown that in both cases, the composit function of two transposes is
+itself a transpose. So transposes of multimatrcies of shape of length $n$ are
+a closed group under composition. Of.
+\end{ppart}
+
+\begin{ppart}
+In this last part, I'll define a bijective map
+$\phi: \mathbb{T}_n \to \mathbb{Z}_n$ for which
+\[ \phi(\Tran_y \circ \Tran_x) = \phi(\Tran(y)) + \phi(\Tran(x)) \]
+Which is the definition of an isomorphism.
+
+Note that I'm letting $\Tran_i$ be a shorthand for ``a transposition
+with index of transposition $i$ that is in $\mathbb{T}_n$''.
+
+So let's just define $\phi$.
+\[ \phi(\Tran_i) = i \]
+Done. I'm a genious.
+
+Ok, the hard part is showing that it preserves the group operations.
+Let's go back to our example in the first part of this proof. Let $A$ be
+any multimatrix with shape length $n$. Then let there be two transpositons
+$\Tran_x$ and $\Tran_y$ which we'll apply in series. First remember that
+to define $\Tran_x$ we needed to divide $|A|$ into $|A| = \vec{l} \oplus \vec{r}$
+where $|\vec{l}| = x$. Then we'd say that
+\[ |\Tran(A, x)| = \vec{r} \oplus \vec{l} \]
+Then to further apply $\Tran(\Tran(A, x), y)$ we need to divide $|\Tran(A,x)|$
+into,
+\[ |\Tran(A, x)| = \vec{l}' \oplus \vec{r}' \]
+Where $|\vec{l}'| = y$.
+That leads to two cases,
+
+\setcounter{case}{0}
+\begin{case} $|\vec{l}'| \le |\vec{r}|$
+
+And in this case we showed that we needed to split up $|A|$ into,
+\[ |A| = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
+\[ \vec{l}' = \vec{b} \]
+\[ \vec{r}' = \vec{c} \oplus \vec{a} \]
+\[ \vec{r} = \vec{b} \oplus \vec{c} \]
+\[ \vec{l} = \vec{a} \]
+
+So that,
+\[ |\Tran(A, x)| = \vec{b} \oplus \vec{c} \oplus \vec{a} \]
+\[ |\Tran(\Tran(A, x), y)| = \vec{c} \oplus \vec{a} \oplus \vec{b} \]
+And note that,
+\[ x = |\vec{a}| \]
+\[ y = |\vec{b}| \]
+
+And we showed that the composit $\Tran_z = \Tran_y \circ \Tran_x$ was such
+that,
+\[ z = |\vec{a} \oplus \vec{b}| \]
+
+Consider that $\phi(\Tran_z) = z$, and so,
+\begin{align*}
+  z
+  &= |\vec{a} \oplus \vec{b}| \\
+  &= |\vec{a}| + |\vec{b}| \\
+  &= x + y \\
+  &= y + x \\
+  z &\equiv y + x \mod n \\
+  \phi(\Tran_z) &= \phi(\Tran_y) + \phi(\Tran_x) \\
+  \phi(\Tran_y \circ \Tran_x) &= \phi(\Tran_y) + \phi(\Tran_x)
+\end{align*}
+So in this case the isomorphism works.
+\end{case}
+
+\begin{case} $|\vec{l}'| > |\vec{r}|$
+
+And in this case we showed that we needed to split up $|A|$ into,
+\[ |A| = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
+\[ \vec{l}' = \vec{c} \oplus \vec{a} \]
+\[ \vec{r}' = \vec{b} \]
+\[ \vec{r} = \vec{c} \]
+\[ \vec{l} = \vec{a} \oplus \vec{b} \]
+
+So that,
+\[ |\Tran(A, x)| = \vec{c} \oplus \vec{a} \oplus \vec{b} \]
+\[ |\Tran(\Tran(A, x), y)| = \vec{b} \oplus \vec{c} \oplus \vec{a} \]
+And note that,
+\[ x = |\vec{a} \oplus \vec{b}| \]
+\[ y = |\vec{c} \oplus \vec{a}| \]
+
+And we showed that the composit $\Tran_z = \Tran_y \circ \Tran_x$ was such
+that,
+\[ z = |\vec{a}| \]
+
+Consider that $\phi(\Tran_z) = z$, and so,
+\begin{align*}
+  z
+  &= |\vec{a}| \\
+  &\equiv |\vec{a}| + n \mod n \\
+  &\equiv |\vec{a}| + |\vec{a} \oplus \vec{b} \oplus \vec{c}| \mod n \\
+  &\equiv |\vec{a} \oplus \vec{a} \oplus \vec{b} \oplus \vec{c}| \mod n \\
+  &\equiv |\vec{c} \oplus \vec{a} \oplus \vec{a} \oplus \vec{b}| \mod n \\
+  &\equiv |\vec{c} \oplus \vec{a}| + |\vec{a} \oplus \vec{b}| \mod n \\
+  &\equiv y + x \mod n \\
+  \phi(\Tran_z) &= \phi(\Tran_y) + \phi(\Tran_x) \\
+  \phi(\Tran_y \circ \Tran_x) &= \phi(\Tran_y) + \phi(\Tran_x)
+\end{align*}
+So also in this case the isomorphism works.
+\end{case}
+
+So, in both cases $\phi$ is a valid isomorphism between $(\mathbb{T}_n, \circ)$
+and $(\mathbb{Z}_n, +)$.
+\end{ppart}
+\end{proof}
+
+Well what does that mean? I'm so glad you asked... weirdo who doesn't know what
+an isomorphism is but is several chapters into a hobby math book. It means that...
+
+\begin{corollary}[Stacked Transpose]
+For any multimatrix $A$ whose shape is $n$ long (an $n$ dimensional multimatrix
+in other words), it is always true that
+\[ \Tran(\Tran(A, x),y) = \Tran(A, \remainder(x+y,n)) \]
+\end{corollary}
+
+\begin{example}
+Let's take a look at a concrete example. Say we have a
+multimatrix $A$ who's shape is $\left<11, 3, 7, 5\right>$. 
+Then see that,
+\[ |\Tran(A, 2)| = \left<7, 5, 11, 3\right> \]
+And applying another transpose,
+\[ |\Tran(\Tran(A, 2), 3)| = \left<3, 7, 5, 11\right> \]
+Notice that our corollary says that this double transpose should be
+equal to the transpose $\Tran(A, \remainder(2+3, 4))$ which would
+be $\Tran(A, 1)$ and indeed it is:
+\begin{align*}
+  |\Tran(A, 1)|
+  &= \left<3, 7, 5, 11\right> \\
+  &= |\Tran(\Tran(A, 2), 3)|
+\end{align*}
+\end{example}
+
+Another useful corollary from Theorem \ref{tran_int_iso} shows you how to
+undo transposition operations with other transposition operations.
+
+\begin{corollary}[Inverse Transpose]
+Let $A$ be a multimatrix such that $||A|| = n$. And let
+$x$ be some integer. Then, the inverse of $\Tran_x$ is
+$\Tran_{-x}$. That is,
+\[ \Tran(\Tran(A, x), -x) = X \]
+\end{corollary}
+
+\begin{example}
+Say you have a multimatrix, $A$, of shape $\left<2,7,1,8,3\right>$.
+Let's apply a transpose to it, $\Tran_3$, and we'll get the shape,
+\[ |\Tran(A, 3)| = \left<8,3,2,7,1\right> \]
+Now, to get back to $A$ we can apply another transpose $\Tran_{-3}$ according
+to the above corollary.
+Our extended definition of transposition (Def. \ref{tran_ext})
+tells us that this is equal to $\Tran_{\remainder(-3, 5)} = \Tran_{2}$.
+So the inverse of $\Tran_3$ is $\Tran_2$, which we can see here:
+\begin{align*}
+  |\Tran(\Tran(A, 3), 2)|
+  &= \left<2,7,1,8,3\right> \\
+  &= |A|
+\end{align*}
+\end{example}
+
+TODO: explosition
 
 \begin{theorem}[Identity Transpose]
+TODO: setup
 \[ \Tran(\Ident^n(\vec{x}), k|\vec{x}|) = \Ident^n(\vec{x}) \]
@@
 
+TODO: exposition here
+
 \begin{theorem}[Transposition of Multimatrix Multiplication]
@@
 \end{proof}
+
+TODO: exposition here
 
@@
 Left as an exercise for the reader (Exercise \ref{com_add_tran_ex}).
-\end{proof}
-
-\begin{theorem}[Stacked Transposition]
-\[ \Tran(\Tran(A, x), y) = \Tran(A, x+y) \]
-\end{theorem}
-\begin{proof}
-Let $|A| = \vec{x} \oplus \vec{y} \oplus \vec{a}$ where $|\vec{x}| = x$ and
-$|\vec{y}| = y$. Note that,
-\[ |\Tran(A, x)| = \vec{y} \oplus \vec{a} \oplus \vec{x} \]
-And,
-\[ |\Tran(\Tran(A, x), y)| = \vec{a} \oplus \vec{x} \oplus \vec{y} \]
-Also that,
-\[ |\Tran(A, x+y)| = \vec{a} \oplus \vec{x} \oplus \vec{y} \]
-So $|\Tran(\Tran(A, x), y)| = \Tran(A, x+y)$ which is necessary but not
-sufficient for this proof.
-
-To show the elementwise equivalence, let $\bar{x} \in \Dim(\vec{x})$,
-$\bar{y} \in \Dim(\vec{y})$, and $\bar{a} \in \Dim(\vec{a})$. Then,
-\begin{align*}
-  \Tran(\Tran(A, x), y)[\bar{a} \oplus \bar{x} \oplus \bar{y}]
-  &= A[\bar{x} \oplus \bar{y} \oplus \bar{a}] \\
-  &= \Tran(A, x+y)[\bar{a} \oplus \bar{x} \oplus \bar{y}]
-\end{align*}
-Which shows that $\Tran(\Tran(A, x), y) = \Tran(A, x+y)$
 \end{proof}
@@
 \begin{theorem}[Multiplication Rule]
+\label{multiplication_rule}
 Let $|F| = \vec{f} \oplus \vec{c}$, $|G| = \vec{c} \oplus \vec{g}$,
@@
 ``I'm not saying Machine Learning is a portal to a demon universe, I'm just saying
-that some doors are best left unopened.'' - James Mickens, AKA `Galactic Viceroy of Research Excellence', USENIX Security '18-Q
+that some doors are best left unopened.'' - James Mickens, AKA `Galactic Viceroy of Research Excellence', USENIX Security 2018
 \end{displayquote}
@@
 \begin{theorem}[Derivative of Sum of Squares]
+Let $X$ be any multimatrix then,
 \[ \frac{d \SoS(X)}{dX} = 2X \]
@@
 \begin{proof}
-Notice that $\SoS(X) = X \mmult{|\vec{x}|} X$...
-
-TODO
+Let $|X| = \vec{x}$. Notice that $\SoS(X) = X \mmult{|\vec{x}|} X$ since,
+$|X \mmult{|\vec{x}|} X| = \left<\right>$ and,
+\[
+  \left(X \mmult{|\vec{x}|} X\right)[\left<\right> \oplus \left<\right>]
+  =
+  \sum_{\forall \bar{x} \in \Dim(\vec{x})}
+    X[\left<\right> \oplus \bar{x}]
+    X[\bar{x} \oplus \left<\right>]
+\]
+Then, by the multiplication rule (Thm. \ref{multiplication_rule}),
+\begin{align*}
+  \frac{d\left(X \mmult{|\vec{x}|} X\right)}{dX}
+  &=
+  X \mmult{|\vec{x}|} \frac{dX}{dX} +
+  \Tran\left(
+    \Tran(X, |\vec{x}|)
+      \mmult{|\vec{x}|}
+    \Tran\left(\frac{dX}{dX}, |\vec{x}|\right),
+    |\vec{x} \oplus \vec{x}|
+  \right) \\
+  &=
+  X \mmult{|\vec{x}|} \Ident^2(|X|) +
+  \Tran\left(
+    X
+      \mmult{|\vec{x}|}
+    \Tran\left(\Ident^2(|X|), |\vec{x}|\right),
+    |\vec{x} \oplus \vec{x}|
+  \right) \\
+  &=
+  X +
+  \Tran\left(
+    X
+      \mmult{|\vec{x}|}
+    \Ident^2(|X|),
+    |\vec{x} \oplus \vec{x}|
+  \right) \\
+  &=
+  X +
+  \Tran\left(
+    X,
+    |\vec{x} \oplus \vec{x}|
+  \right) \\
+  &= X + X \\
+  &= 2X
+\end{align*}
 \end{proof}

### 2019-07-15 Math/book.tex
Hadamard Product

--- 2019-07-12 Math/paper.tex
@@
 \usepackage[normalem]{ulem}
-
-\title{Multimatrices and Their Derivatives}
+\usepackage[toc,page]{appendix}
+
+\title{%
+  Multimatrices and Their Derivatives \\
+  \large An Impractical Guide to Global Conquest}
 \author{Ernest Kirstein}
 \date{\today}
+
+\theoremstyle{plain}
+\newtheorem{theorem}{Theorem}[chapter]
 
@@
 \newtheorem{exercise}{Exercise}[chapter]
-
-\theoremstyle{plain}
-\newtheorem{theorem}{Theorem}[chapter]
 \newtheorem{corollary}{Corollary}[theorem]
@@
 \newtheorem{example}{Example}[chapter]
+\newtheorem{drule}{Rule}
 
@@
 \newcommand{\mmult}[1]{\text{\raisebox{1ex}{$\underset{#1}{\times}$}}}
+\newcommand{\dmult}[1]{\text{\raisebox{1ex}{$\underset{#1}{\,\bullet\,}$}}}
 
@@
 \chapter*{Preface}
-I was working my way through a hobby programming project, trying to get my
-machine to do some learning, and ran into a problem.
+I was working my way through a hobby programming project, trying to create a so called
+`deep fake' of Danny DeVito's face on Scarlett Johansson's body, and ran into a problem.
 The existing notation for taking derivatives of matrix equations is terrible.
 It's so deliberately obtuse that I could only conclude that some hidden cabal of
-mathematicians is actively working to sabotage our glorious yet-to-be-built
-AI overlords. I, for one, will not stand for such blasphemy.
+mathematicians is actively working to sabotage the rise of our glorious AI overlords.
+I, for one, will not stand for such heresy.
 
@@
 ``If you're a bit touched, like I am, you may want to make a dedicated tool.'' -
-This Old Tony, `Making Springs At Home'
+This Old Tony, `Making Springs At Home' \cite{youtube:tony}
 \end{displayquote}
@@
 
-I'll give you a theorem here and make you prove it yourself because I'm a jerk.
+That's a huge informtion dump so look at an example.
+
+\begin{example}
+Let $M$ be one of these newfangled `multimatrix' things. According to our
+definition, we also need to define a shape for the multimatrix. Let's
+say that our shape is $\left<5,7,9,2,3\right>$. In our notation, that
+means that,
+\[ |M| = \left<5,7,9,2,3\right> \]
+Let's name this shape vector, $|M| = \vec{m}$. Notice that this is
+a 5 dimensional multimatrix because $|\vec{m}| = 5$. Also note the
+subtle difference in $||M||$ which is 5 and $|M|$ which is $\vec{m}$.
+
+Let's look at some individual elements of $M$. We can say that,
+\[ M[5,4,3,2,1] = 3 \]
+And,
+\[ M[4,3,2,1,1] = -8.5 \]
+We can say that because we're just making up this multimatrix, but also
+because $\left<5,4,3,2,1\right>$ and $\left<4,3,2,1,1\right>$
+are both in $\Dim(\vec{m})$. That is to say, they're both valid
+indexes of $M$.
+
+Remember that $\Dim(\vec{m})$ is the set of valid indexes of $M$.
+You can tell that the size of  $\Dim(\vec{m})$ is
+$5 \times 7 \times 9 \times 2 \times 3 = 1890$, which is the number of
+elements of $M$.
+
+If $\left<5,4,3,2,1\right> = \bar{a}$ and $\left<4,3,2,1,1\right> = \bar{b}$
+then we can say that $\bar{a} \in \Dim(\vec{m})$ and $\bar{b} \in \Dim(\vec{m})$
+because both are valid indexes of $M$.
+
+We can uses the indexes to reference $M$ like this,
+\[ M[\bar{a}] = 3 \]
+And this,
+\[ M[\bar{b}] = -8.5 \]
+\end{example}
+
+Now that you seem to understand.. Don't give me that look... well if you're confused
+you should have been asking questions, moving on. Now that \textit{most of you}
+seem to have understood, I'll give you a theorem to prove.
+
 \begin{theorem}[Dimensional Set and Index Concatenation]
@@
 for meaning. It's to just keep yourself busy with unimportant nonsense, and eventually,
-you'll be dead.'' - Mr. Peanutbutter, BoJack Horseman
+you'll be dead.'' - Mr. Peanutbutter (BoJack Horseman Season 1, Episode 12
+\cite{bojack})
 \end{displayquote}
@@
 
-\[ C[r_a, c_b] = \sum_{\forall i} A[r_a, i] B[i, c_b] \]
+\[ C[r_c, c_c] = \sum_{\forall i} A[r_c, i] B[i, c_c] \]
 
@@
 concept rather than ``this is the way it's done because it makes the equations
-you'll see later work.''
+work.''
 
@@
 
+It's important to notice that this operation is identital to standard
+matrix multiplication for two dimensional multimatrices. For instance,
+if $A$ and $B$ are two dimensional multimatricies with shapes
+$|A| = \left<l_a, r_a\right>$ and $|B| = \left<l_b, r_b\right>$
+their product $A \mmult{1} B$ is valid if and only if $r_a = l_b$ and
+the result is of shape $|A \mmult{1} B| = \left<l_a, r_b\right>$.
+And of course, the value at each index
+$\left<l_c, r_c\right> \in \Dim(|A \mmult{1} B|)$ is,
+\[
+  (A \mmult{1} B)[l_c, r_c]
+  =
+  \sum_{\forall 1 \le x \le r_a} 
+  A[l_c, x] B[x, r_c]
+\]
+All of which would be the same if this was regular matrix multiplication.
+
 \section{Rules of Multimatrix Multiplication}
@@
 Like two dimensional matrix multiplication, multimatrix multiplication is
-\textit{not} communicative. And it is only weakly associative. That sounds like
+not (usually) communicative. And it is only weakly associative. That sounds like
 nonsense, and ideed it is, but I shall prove it to you.
@@
 
+TODO: exposition
+
+\begin{theorem}[Communicativity of Multiplication]
+Let $|A| = \vec{x}$ and $|B| = \vec{x}$. Then,
+\[ A \mmult{|\vec{x}|} B = B \mmult{|\vec{x}|} A \]
+\end{theorem}
+\begin{proof}
+TODO
+\end{proof}
+
 \section{Multiplicative Identities}
@@
 \begin{theorem}[Self Derivative]
+\label{self_derivative}
 Let $X$ be some multimatrix. Then,
@@
 \begin{theorem}[Elementwise Derivative]
+\label{elementwise_derivative}
 Let $M$ be an element wise function on $X$. That is, Let $M(X)$ be a function
@@
 \end{proof}
+
+\section{Multimatrix Hadamard Product}
+
+\begin{displayquote}
+TODO
+\end{displayquote}
+
+What the hell is a `Hadamard product'? The Hadamar product of two matricies
+is how one would actually expect matrix multiplication to work.
+
+In short, if two matricies, $A$ and $B$ have the same shape,
+\[ |A| = |B| = \left<r,c\right> \]
+Then their Hadamard Product, $A \bullet B$, is the same shape and each element
+is just the product of the corresponding elements of $A$ and $B$. That is,
+\[ (A \bullet B)[r,c] = A[r,c] B[r,c] \]
+
+This seems to extend quite naturally into the world of multimatricies.
+But hold on - there's a catch. While the Hadamard product only logically applies
+to regular matricies when their shapes are exactly equal, there are case where
+the Hadamard product can easily be applied to differently shaped multimatricies,
+they just need to have overlapping portions of their shape vectors, just as
+with multimatrix multiplication.
+
+\begin{definition}[Multimatrix Hadamard Product]
+\label{multi_had_prod}
+Let $A$ and $B$ be multimatricies such that $|A| = \vec{a} \oplus \vec{c}$
+and $|B| = \vec{c} \oplus \vec{b}$. Also let $c = |\vec{c}|$.
+Then, the multimatrix Hadamard product, $A \dmult{c} B$, is a multimatrix
+such that,
+\[ |A \dmult{n} B| = \vec{a} \oplus \vec{c} \oplus \vec{b} \]
+And for any $\bar{a} \in \Dim(\vec{a})$, $\bar{b} \in \Dim(\vec{b})$,
+and $\bar{c} \in \Dim(\vec{c})$,
+\[
+  (A \dmult{n} B)[\bar{a} \oplus \bar{c} \oplus \bar{b}]
+  = A[\bar{a} \oplus \bar{c}] B[\bar{c} \oplus \bar{b}]
+\]
+\end{definition}
+
+TODO: exposition
+
+\begin{theorem}[Equivalent Zero Hadamard Product and Multiplication]
+\[ A \dmult{0} B = A \mmult{0} B \]
+\end{theorem}
+\begin{proof}
+TODO: exercise?
+\end{proof}
+
+TODO: associative?
+
+TODO: exposition
+
+\begin{theorem}[Equivalent Hadamard Product and Multiplication Chains]
+When $X_1 \ldots X_{m-1}$ are all in $\mathbb{R}^{\vec{x}}$ and
+$|X_m| = \vec{x} \oplus \vec{r}$ for any $\vec{r}$,
+\[
+  (((\Ident^n(\vec{x})
+  \mmult{|\vec{x}|} X_1) \mmult{|\vec{x}|} X_2) \mmult{|\vec{x}|} X_3)
+  \ldots X_m
+  =
+  \Ident^{n-m}(\vec{x})
+  \dmult{|\vec{x}|} X_1 \dmult{|\vec{x}|} X_2 \dmult{|\vec{x}|} X_3
+  \ldots X_m
+\]
+And when $X_2 \ldots X_m$ are all in $\mathbb{R}^{\vec{x}}$ and
+$|X_1| = \vec{l} \oplus \vec{x}$ for any $\vec{l}$,
+\[
+  X_1 \mmult{|\vec{x}|} (X_2 \mmult{|\vec{x}|} (X_3
+  \ldots (X_m \mmult{|\vec{x}|} 
+  \Ident^n(\vec{x}))))
+  =
+  X_1 \dmult{|\vec{x}|} X_2 \dmult{|\vec{x}|} X_3
+  \ldots X_m \dmult{|\vec{x}|} 
+  \Ident^{n-m}(\vec{x})
+\]
+\end{theorem}
+\begin{proof}
+TODO 
+\end{proof}
+
+TODO: Communicative property
 
@@
 
-TODO: explosition
+Now that you understand the basics of transposition, let's take a look
+at some theorems involving it.
 
 \begin{theorem}[Identity Transpose]
-TODO: setup
+Let $n$ be a positive integer and let $\vec{x}$ be a positive length
+shape vector. Then for any integer $k$,
 \[ \Tran(\Ident^n(\vec{x}), k|\vec{x}|) = \Ident^n(\vec{x}) \]
@@
 \end{align*}
-Since for
+Since for the permutation
 $X' = \left\{\bar{x}_{k+1}, \bar{x}_{k+2} \ldots \bar{x}_{n},
@@
 
-TODO: exposition here
+The above theorem is useful whenever you come accross a transpose of a
+multimatrix identity.
+
+Another useful theorem for whenever you need to change the order of
+multimatrix multiplications is this one,
 
@@
 \begin{theorem}[Addition Rule]
+\label{addition_drule}
 \[ \frac{d(F(X) + G(X))}{dX} = \frac{dF(X)}{dX} + \frac{dG(X)}{dX} \]
@@
 the additional ink, I think,
+
 \begin{theorem}[Scalar Multiplication Rule]
+\label{scalar_mult_drule}
 \[ \frac{d(sF(X))}{dX} = s\frac{dF(X)}{dX} \]
@@
 
+\begin{appendices}
+
 \chapter{Solutions to the Exercises}
@@
 
-\bibliography{paper}
+\chapter{Derivative Rule List}
+
+\begin{drule}
+Self Derivative (Thm. \ref{self_derivative})
+\[ \frac{dX}{dX} = \Ident^2(|X|) \]
+\end{drule}
+
+\begin{drule}
+Elementwise Derivative (Thm. \ref{elementwise_derivative})
+\[ \frac{dM(X)}{dX} = \Ident^3(|X|) \mmult{||X||} M'(X) \]
+\end{drule}
+
+\begin{drule}
+Empty Shape Multimatrix and Scalar Domain Derivative Equivalence
+(Thm. \ref{s_mm_domain_equiv})
+\[ G(X) = F(X[\left<\right>]) \]
+Implies,
+\[ \frac{dF(x)}{dx} = \frac{dG(X)}{dX} \]
+\end{drule}
+
+\begin{drule}
+Empty Shape Multimatrix and Scalar Range Derivative Equivalence
+(Thm. \ref{s_mm_range_equiv})
+\[ F(X)[\left<\right>] = f(X) \]
+Implies,
+\[ \frac{df(X)}{dX} = \frac{dF(X)}{dX} \]
+\end{drule}
+
+\begin{drule}
+Transpose Derivative
+(Thm. \ref{tran_derivative})
+\[ |X| = \vec{l} \oplus \vec{r} \]
+Implies,
+\[
+ \frac{d\Tran(X, |\vec{l}|)}{dX} =
+ \Tran(\Ident^2(\vec{r}) \mmult{0} \Ident^2(\vec{l}), |\vec{r}|)
+\]
+\end{drule}
+
+\begin{drule}
+Right Multiplicative Derivative
+(Thm. \ref{right_mult_derivative})
+\[ \frac{d(A \mmult{n} X)}{dX} = A \mmult{n} \Ident^2(|X|) \]
+\end{drule}
+
+\begin{drule}
+Left Multiplicative Derivative
+(Thm. \ref{left_mult_derivative})
+\[ \frac{d(X \mmult{n} A)}{dX} = \Ident^2(|X \mmult{n} A|) \mmult{n} \Tran(A, n) \]
+\end{drule}
+
+\begin{drule}
+Addition Rule
+(Thm. \ref{addition_drule})
+\[ \frac{d(F(X) + G(X))}{dX} = \frac{dF(X)}{dX} + \frac{dG(X)}{dX} \]
+\end{drule}
+
+\begin{drule}
+Scalar Multiplication Rule
+(Thm. \ref{scalar_mult_drule})
+\[ \frac{d(sF(X))}{dX} = s\frac{dF(X)}{dX} \]
+\end{drule}
+
+\begin{drule}
+Multiplication Rule
+(Thm. \ref{multiplication_rule})
+
+Let $|F| = \vec{f} \oplus \vec{c}$, $|G| = \vec{c} \oplus \vec{g}$,
+and $|X| = \vec{x}$. Then,
+\begin{align*}
+ \frac{d\left(F(X) \mmult{|\vec{c}|} G(X)\right)}{dX} =&
+ F(X) \mmult{|\vec{c}|} \frac{dG(X)}{dX} + \\
+ &\Tran\left(
+   \Tran(G(X), |\vec{c}|)
+     \mmult{|\vec{c}|}
+   \Tran\left(\frac{dF(X)}{dX}, |\vec{f}|\right),
+   |\vec{g} \oplus \vec{x}|
+ \right)
+\end{align*}
+\end{drule}
+
+\begin{drule}
+Chain Rule
+(Thm. \ref{mmm_chain_rule})
+\[ \frac{dF(G(X))}{dX} = \frac{dF}{dG} \mmult{||G||} \frac{dG}{dX} \]
+\end{drule}
+
+\end{appendices}
+
+\bibliography{book}
 \bibliographystyle{ieeetr}

### 2019-07-15 Math/book.tex
Citation for Hadamard Product

@@
 
-\section{Multimatrix Hadamard Product}
-
-\begin{displayquote}
-TODO
-\end{displayquote}
-
-What the hell is a `Hadamard product'? The Hadamar product of two matricies
-is how one would actually expect matrix multiplication to work.
+\section{Hadamard Product}
+
+What the hell is a `Hadamard product'? The Hadamard product \cite{wiki:hadamard}
+of two matricies is how one would actually expect matrix multiplication to work.
 
@@
 \[ |A| = |B| = \left<r,c\right> \]
-Then their Hadamard Product, $A \bullet B$, is the same shape and each element
+Then their Hadamard product, $A \bullet B$, is the same shape and each element
 is just the product of the corresponding elements of $A$ and $B$. That is,

### 2019-08-18 Math/book.tex
Changes?

@@
 \end{proof}
+
+\section{Multiplicative Inverses}
+
+Given a multimatrix, $M$, you might ask, ``What is the multiplicative inverse of $M$?''
+And I would have to tell you that your question is not well formed.
+
+Since multimatrix multiplication is a trinary operation, you need to factor in the
+index of multipliction. Consider multiplication by $M$ a function on $X$ - some other
+multimatrix. That is, 
+\[ F(X; M, m) = M \mmult{m} X \]
+
+What we're looking for in a `multiplicative inverse' is actually a function which,
+when composed with $F$, results in $X$. That is,
+
+\[ (F^{-1} \circ F)(X) = F^{-1}(M \mmult{m} X) = X \]
+
+That inverse function, $F^{-1}$ also needs to be a multiplication operation to
+really be a `multiplicative inverse', so we can assume that it is defined by
+some multimatrix $N$ and some inverting index of multiplication $n$, such that,
+
+\[ F^{-1} (Y; N, n) = N \mmult{n} Y \]
+
+Let's say that $M$ has some shape $\vec{l} \oplus \vec{r}$ such that $|\vec{r}| = m$.
+Then it is only applicable for an $m$ overlap multiplication on some $X$ where,
+$|X| = \vec{r} \oplus \vec{x}$ for some $\vec{x}$.
+
+So since,
+\[ |M \mmult{m} X| = \vec{l} \oplus \vec{x}\]
+and
+\[ |N \mmult{n} (M \mmult{m} X)| = |X| = \vec{r} \oplus \vec{x} \]
+It must be true that, $n = |\vec{l}|$ and $|N| = \vec{r} \oplus \vec{l}$.
+
+TODO
 
@@
 \label{left_mult_derivative}
-\[ \frac{d(X \mmult{n} A)}{dX} = \Ident^2(|X \mmult{n} A|) \mmult{n} \Tran(A, n) \]
+If $|X| = \vec{x} \oplus \vec{n}$ and $|A| = \vec{n} \oplus \vec{a}$
+and $n = |\vec{n}|$ and $a = |\vec{a}|$ then,
+\[ \frac{d(X \mmult{n} A)}{dX} = \Ident^2(|X \mmult{n} A|) \mmult{a} \Tran(A, n) \]
 \end{theorem}
@@
 \begin{align*}
-	\left(\Ident^2(|X \mmult{n} A|) \mmult{n} \Tran(A, n)\right)
+	\left(\Ident^2(|X \mmult{n} A|) \mmult{a} \Tran(A, n)\right)
 	[\bar{x}_1 \oplus \bar{a}_1 \oplus \bar{x}_2 \oplus \bar{n}_1]
@@
 	=
-	\left(\Ident^2(|X \mmult{n} A|) \mmult{n} \Tran(A, n)\right)
+	\left(\Ident^2(|X \mmult{n} A|) \mmult{a} \Tran(A, n)\right)
 	[\bar{x}_1 \oplus \bar{a}_1 \oplus \bar{x}_2 \oplus \bar{n}_1]
@@
 	=
-	\Ident^2(|X \mmult{n} A|) \mmult{n} \Tran(A, n)
+	\Ident^2(|X \mmult{n} A|) \mmult{a} \Tran(A, n)
 \]

### 2019-08-18 MMatrix/test/test_mmatrix.cc

@@ -215,12 +215,41 @@ void TestIdentityMultiplication() {
   }
 }
 
+void TestSparseMultiplication() {
+  std::cout << "TestSparseMultiplication..." << std::endl;
+
+  SparseMMatrix a({2,2});
+  a.set({0,0}, 2);
+  a.set({1,1}, 7);
+  
+  SparseMMatrix b({2,3});
+  b.set({0,1}, -2);
+  b.set({0,2}, 3);
+  b.set({1,1}, 5);
+  b.set({1,2}, 6);
+
+  SparseMMatrix out({2,3});
+  Multiply(1, &a, &b, &out);
+
+  SparseMMatrix expected({2,3});
+  expected.set({0,1}, 2*-2);
+  expected.set({0,2}, 2*3);
+  expected.set({1,1}, 7*5);
+  expected.set({1,2}, 7*6);
+
+  if (!AreEqual(&out, &expected)) {
+    std::cerr << "Error multiplying sparse matricies. Should be equal." << std::endl;
+    std::exit(1);
+  }
+}
+
 int main() {
   TestToFromVIndex();
   TestDenseMMatrixGetSet();
   TestMMatrixMultiplication();
   TestMMatrixMultiplicationAssociation();
   TestIdentityMultiplication();
+  TestSparseMultiplication();
   std::cout << "All tests pass." << std::endl;
   return 0;
 }

### 2020-03-19 Math/book.tex
Adding sparse matrix multiplication.

@@
 
-Let us consider a traditional matrix equation - one contrived on the spot for the
-purposes of adding an additional layer of confusion to the situation.
-
-As is tradition, let one matrix $X$ represent the scientific education level of
-undergraduates, who work in a densely packed 3 by 5 grid (which is also traditional).
+To demonstrate how the problem with traditional matricies, let's take a look at a
+simple matrix equation.
+
+Let one matrix $X$ represent the level of scientific education level of a set of
+undergraduates who work in a densely packed 3 by 5 office.
 Then let $B$ represent the belief each of those undergradutes has in a higher power.
 
-It has been shown that an undergraduate's belief in a higher power fluctuates with
-respect to their scientific education in a sinusoidal pattern
-(Weinersmith, 2010 \cite{weinersmith:education}).
+As we all know, Weinersmith's hypothisis states that an undergraduate's belief in a
+higher power fluctuates with respect to their scientific education in a sinusoidal
+pattern (Weinersmith, 2010 \cite{weinersmith:education}).
 
@@
 \]
-And perhaps we could even let this help us define the `shape' of the complete
-derivative. This complete derivative would need to be composed of partial
-derivatives, so it would make sense to just smush the shapes of the input
-matrix and the output matrix together,
+Perhaps we could even let this help us define the `shape' of the complete
+derivative. Note that there seem to be four independent indicies to each element
+of this matrix, namely $r_1$, $c_1$, $r_2$, and $c_2$.
+And since a complete derivative would need to be composed of partial derivatives
+it would make sense to just smush the shapes of the input matrix and the output
+matrix together,
 \begin{align*}
@@
 both output and indepenedent variable are preserved. Let us declare this to
-be our convention since, for the purpose of this work, mine is the divinely revealed
-word of god, graciously passed down to you lowly mortals (I've typeset
-my mad ranblings with \LaTeX ~therefore they must be reasonably coherent. QED).
+be our convention. I've typeset it in \LaTeX ~therefore it can no longer be
+changed. Those are the rules that I've just made up and I'm backing them up with
+dozens more pages of incoherent rambling.
 
@@
 
-Let $\vec{v}$ be the natural number vector which describes the shape of
+Let $\vec{v}$ be the vector which describes the shape of
 $M$, then $\vec{v} = |M|$. And for any other $\bar{v} \in \mathbb{N}^n$, $\bar{v}$
@@
 so, we need to compleately abandon conventional algebras, and indeed any hope of
-returning to sanity. That's right, we're introducing a ternary operator.
+returning to sanity. We need... a ternary operator.
 
@@
 
-TODO: exposition
+Along the same vein, it's also true that there is a consistent time when
+multimatrix multiplication is communicative - when both multimatricies are
+the same shape and the multiplication is combining them completely into a
+scalar by combining their full width.
 
@@
 \begin{proof}
-TODO
+Let $A$, $B$, and $\vec{x}$ be as described above. Notice that then $|A \mmult{|\vec{x}|} B|$
+results in a zero dimensional multimatrix - a multimatrix with one element which is effectively
+just a scalar.
+\begin{align*}
+(A \mmult{|\vec{x}|} B)[\{\}]
+  &= \sum_{\forall \bar{x} \in \Dim(\vec{x})} A[\bar{x}]B[\bar{x}] \\
+  &= \sum_{\forall \bar{x} \in \Dim(\vec{x})} B[\bar{x}]A[\bar{x}] \\
+  &= (B \mmult{|\vec{x}|} A)[\{\}]
+\end{align*}
 \end{proof}
@@
 Consider that for some ordered set of indicies
-$\{\bar{x}_1, \bar{x}_2, \ldots \bar{x}_n\} = X$ such that each
-$\bar{x}_i \in X \implies \bar{x}_i \in \Dim(\vec{x})$.
+$\{\bar{x}_1, \bar{x}_2, \ldots \bar{x}_n\} = X$ such that for each
+$\bar{x}_i$ it is true that $\bar{x}_i \in \Dim(\vec{x})$.
 Let $X'$ be some ordered permutation of $X$, then we can reason that,

### 2020-03-19 MMatrix/src/mmatrix.cc

@@ -2,6 +2,7 @@
 
 #include <cmath>
 #include <stdexcept>
+#include <iostream>
 
 namespace mmatrix {
 
@@ -58,6 +59,11 @@ void DenseMMatrix::set(int i, float value) {
 const vector<int>& DenseMMatrix::shape() const {
   return shape_;
 }
+void DenseMMatrix::zero() {
+  for (int i = 0; i < values_.size(); i++) {
+    values_[i] = 0;
+  }
+}
 
 SparseMMatrix::SparseMMatrix(const std::vector<int>& shape) : shape_(shape) {}
 float SparseMMatrix::get(int i) const {
@@ -82,6 +88,12 @@ const std::vector<int>& SparseMMatrix::shape() const {
 }
 const internal::Type* SparseMMatrix::type() const {
   return &type_;
+}
+void SparseMMatrix::zero() {
+  values_.clear();
+}
+int SparseMMatrix::size() const {
+  return values_.size();
 }
 namespace {
 internal::Type InitSparseMMatrixType() {
@@ -191,17 +203,30 @@ void Multiply(int n, const SparseMMatrix* a, const SparseMMatrix* b,
     }
     rBound *= b->shape()[n+i];
   }
-  // TODO: take advantage of sparse multiplication
-  for (int vl = 0; vl < lBound; vl++) {
-    for (int vr = 0; vr < rBound; vr++) {
-      float sum = 0;
-      for (int vm = 0; vm < midBound; vm++) {
-        int va = vl+vm*lBound;
+
+  int a_index_ops = a->size()*rBound;
+  int b_index_ops = b->size()*lBound;
+
+  out->zero();
+  if (a_index_ops <= b_index_ops) {
+    for (const auto& a_pair : *a) {
+      int vl = a_pair.first % lBound;
+      int vm = a_pair.first / lBound;
+      for (int vr = 0; vr < rBound; vr++) {
+        int vo = vl+vr*lBound;
         int vb = vm+vr*midBound;
-        sum += a->get(va)*b->get(vb);
+        out->set(vo, out->get(vo) + a_pair.second*b->get(vb));
       }
-      int vo = vl+vr*lBound;
-      out->set(vo, sum);
+    }
+  } else {
+    for (const auto& b_pair : *b) {
+      int vm = b_pair.first % midBound;
+      int vr = b_pair.first / midBound;
+      for (int vl = 0; vl < lBound; vl++) {
[…]

### 2020-03-19 MMatrix/src/mmatrix.h

@@ -1,7 +1,7 @@
 #ifndef MMATRIX_H
 #define MMATRIX_H
 
-#include <map>
+#include <unordered_map>
 #include <memory>
 #include <string>
 #include <unordered_set>
@@ -48,6 +48,8 @@ class MMatrixInterface {
   virtual const std::vector<int>& shape() const = 0;
   // Returns the most generic type "::mmatrix::MMatrixInterface" by default.
   virtual const internal::Type* type() const;
+  // Sets all values of the matrix to zero.
+  virtual void zero() = 0;
  private:
   const static internal::Type type_;
 };
@@ -62,6 +64,7 @@ class DenseMMatrix : public MMatrixInterface {
   float get(int i) const override;
   void set(int i, float value) override;
   const std::vector<int>& shape() const override;
+  void zero() override;
 
  private:
   std::vector<float> values_;
@@ -78,18 +81,22 @@ class SparseMMatrix : public MMatrixInterface {
   float get(int i) const override;
   void set(int i, float value) override;
   const std::vector<int>& shape() const override;
+  void zero() override;
+
+  // Returns the number of non-zero values in the matrix.
+  int size() const;
 
   const internal::Type* type() const override;
 
-  std::map<int, float>::iterator begin() { return values_.begin(); }
-  std::map<int, float>::iterator end() { return values_.end(); }
-  std::map<int, float>::const_iterator cbegin() { return values_.cbegin(); }
-  std::map<int, float>::const_iterator cend() { return values_.cend(); }
-  std::map<int, float>::const_iterator begin() const { return values_.cbegin(); }
-  std::map<int, float>::const_iterator end() const { return values_.cend(); }
+  std::unordered_map<int, float>::iterator begin() { return values_.begin(); }
+  std::unordered_map<int, float>::iterator end() { return values_.end(); }
+  std::unordered_map<int, float>::const_iterator cbegin() { return values_.cbegin(); }
+  std::unordered_map<int, float>::const_iterator cend() { return values_.cend(); }
+  std::unordered_map<int, float>::const_iterator begin() const { return values_.cbegin(); }
+  std::unordered_map<int, float>::const_iterator end() const { return values_.cend(); }
  private:
   // Maps the value index to non-zero values.
-  std::map<int, float> values_;
+  std::unordered_map<int, float> values_;
 
   std::vector<int> shape_;
   const static internal::Type type_;

### 2020-03-19 MMatrix/test/test_mmatrix.cc

@@ -243,6 +243,49 @@ void TestSparseMultiplication() {
   }
 }
 
+void TestSparseMultiplicationThorough() {
+  std::cout << "TestSparseMultiplicationThorough..." << std::endl;
+
+  std::srand(314);
+
+  for (int trials = 0; trials < 100; trials++) {
+
+    SparseMMatrix a_s ({5,5,5});
+    DenseMMatrix a_d ({5,5,5});
+    a_d.zero();
+  
+    SparseMMatrix b_s ({5,5,5});
+    DenseMMatrix b_d ({5,5,5});
+    b_d.zero();
+
+    int a_vals = std::rand() % 125;
+    for(int i = 0; i < a_vals; i++) {
+      std::vector<int> index = {std::rand()%5, std::rand()%5, std::rand()%5};
+      int val = std::rand()%11-5;
+      a_s.set(index, val);
+      a_d.set(index, val);
+    }
+    int b_vals = std::rand() % 125;
+    for(int i = 0; i < b_vals; i++) {
+      std::vector<int> index = {std::rand()%5, std::rand()%5, std::rand()%5};
+      int val = std::rand()%11-5;
+      b_s.set(index, val);
+      b_d.set(index, val);
+    }
+
+    SparseMMatrix out_s({5,5});
+    DenseMMatrix out_d({5,5});
+
+    Multiply(2, &a_s, &b_s, &out_s);
+    Multiply(2, &a_d, &b_d, &out_d);
+
+    if (!AreEqual(&out_s, &out_d)) {
+      std::cerr << "Error multiplying sparse matricies. Should be equal." << std::endl;
+      std::exit(1);
+    }
+  }
+}
+
 int main() {
   TestToFromVIndex();
   TestDenseMMatrixGetSet();
@@ -250,6 +293,7 @@ int main() {
   TestMMatrixMultiplicationAssociation();
   TestIdentityMultiplication();
   TestSparseMultiplication();
+  TestSparseMultiplicationThorough();
   std::cout << "All tests pass." << std::endl;
   return 0;
 }

### 2020-03-21 MMatrix/src/mmatrix.cc
Adding different sparse matrix multiplication modes and automated selection.

@@ -10,17 +10,6 @@ using std::string;
 using std::unique_ptr;
 using std::vector;
 
-namespace internal {
-
-bool Type::hasProperty(TypeProperty property) const {
-  return properties_.find(property) != properties_.end();
-}
-void Type::addProperty(TypeProperty property) {
-  properties_.insert(property);
-}
-
-} // namespace internal
-
 float MMatrixInterface::get(int i) const {
   vector<int> indices(shape().size(), 0);
   FromValueIndex(shape(), i, &indices);
@@ -36,11 +25,6 @@ float MMatrixInterface::get(const vector<int>& indices) const {
 }
 void MMatrixInterface::set(const vector<int>& indices, float value) {
   set(ToValueIndex(shape(), indices), value);
-}
-const internal::Type MMatrixInterface::type_ =
-  internal::Type("::mmatrix::MMatrixInterface");
-const internal::Type* MMatrixInterface::type() const {
-  return &type_;
 }
 
 DenseMMatrix::DenseMMatrix(const vector<int>& shape) : shape_(shape) {
@@ -64,6 +48,9 @@ void DenseMMatrix::zero() {
     values_[i] = 0;
   }
 }
+internal::MMatrixType DenseMMatrix::type() const {
+  return internal::kMMatrixType_Dense;
+}
 
 SparseMMatrix::SparseMMatrix(const std::vector<int>& shape) : shape_(shape) {}
 float SparseMMatrix::get(int i) const {
@@ -86,8 +73,8 @@ void SparseMMatrix::set(int i, float value) {
 const std::vector<int>& SparseMMatrix::shape() const {
   return shape_;
 }
-const internal::Type* SparseMMatrix::type() const {
-  return &type_;
+internal::MMatrixType SparseMMatrix::type() const {
+  return internal::kMMatrixType_Sparse;
 }
 void SparseMMatrix::zero() {
   values_.clear();
@@ -95,14 +82,6 @@ void SparseMMatrix::zero() {
 int SparseMMatrix::size() const {
   return values_.size();
 }
-namespace {
-internal::Type InitSparseMMatrixType() {
-  internal::Type type("::mmatrix::SparseMMatrix");
-  type.addProperty(internal::kTypeProperty_Sparse);
-  return type;
-}
-} // namespace
-const internal::Type SparseMMatrix::type_ = InitSparseMMatrixType();
 
[…]

### 2020-03-21 MMatrix/src/mmatrix.h

@@ -11,22 +11,9 @@ namespace mmatrix {
 
 namespace internal {
 
-typedef uint64_t TypeProperty;
-constexpr TypeProperty kTypeProperty_Sparse = 1;
-
-class Type {
- public:
-  Type(const std::string& class_name) : class_name_(class_name) {}
-  virtual ~Type() = default;
-  const std::string& className() const { return class_name_; }
-  // Returns true if this matrix has the specified property.
-  bool hasProperty(TypeProperty property) const;
-  // This should only be called by the class setting up the types.
-  void addProperty(TypeProperty property);
- private:
-  std::string class_name_;
-  std::unordered_set<TypeProperty> properties_;
-};
+typedef uint64_t MMatrixType;
+constexpr MMatrixType kMMatrixType_Dense = 0;
+constexpr MMatrixType kMMatrixType_Sparse = 1;
 
 }  // namespace internal
 
@@ -46,12 +33,10 @@ class MMatrixInterface {
   virtual void set(const std::vector<int>& indices, float value);
   // Returns the shape (size of dimensions) of this matrix.
   virtual const std::vector<int>& shape() const = 0;
-  // Returns the most generic type "::mmatrix::MMatrixInterface" by default.
-  virtual const internal::Type* type() const;
+  // Returns the most specific class type of the MMatrix.
+  virtual internal::MMatrixType type() const = 0;
   // Sets all values of the matrix to zero.
   virtual void zero() = 0;
- private:
-  const static internal::Type type_;
 };
 
 class DenseMMatrix : public MMatrixInterface {
@@ -65,6 +50,7 @@ class DenseMMatrix : public MMatrixInterface {
   void set(int i, float value) override;
   const std::vector<int>& shape() const override;
   void zero() override;
+  internal::MMatrixType type() const override;
 
  private:
   std::vector<float> values_;
@@ -82,11 +68,10 @@ class SparseMMatrix : public MMatrixInterface {
   void set(int i, float value) override;
   const std::vector<int>& shape() const override;
   void zero() override;
+  internal::MMatrixType type() const override;
 
   // Returns the number of non-zero values in the matrix.
   int size() const;
-
-  const internal::Type* type() const override;
 
   std::unordered_map<int, float>::iterator begin() { return values_.begin(); }
   std::unordered_map<int, float>::iterator end() { return values_.end(); }
[…]

### 2020-03-21 MMatrix/test/test_mmatrix.cc

@@ -286,6 +286,19 @@ void TestSparseMultiplicationThorough() {
   }
 }
 
+void ManualTestSparseSwitch() {
+  std::cout << "ManualTestSparseSwitch..." << std::endl;
+
+  SparseMMatrix sparse({1});
+  DenseMMatrix dense({1});
+  DenseMMatrix out({1});
+
+  Multiply(1, &dense, &dense, &out);
+  Multiply(1, &sparse, &dense, &out);
+  Multiply(1, &dense, &sparse, &out);
+  Multiply(1, &sparse, &sparse, &out);
+}
+
 int main() {
   TestToFromVIndex();
   TestDenseMMatrixGetSet();
@@ -294,6 +307,7 @@ int main() {
   TestIdentityMultiplication();
   TestSparseMultiplication();
   TestSparseMultiplicationThorough();
+  ManualTestSparseSwitch();
   std::cout << "All tests pass." << std::endl;
   return 0;
 }

### 2020-04-05 Math/book.tex
Working on defining multiplicative inverses.

@@
 dimensionality of the output. What's important is that the dimensionality of
-both output and indepenedent variable are preserved. Let us declare this to
+both output and indepenedent variable are preserved and that our notation is
+consistent. Let us declare this to
 be our convention. I've typeset it in \LaTeX ~therefore it can no longer be
@@
 
-And since we're defining our own notation, let's splurge and reference our original
+And since we're defining our own notation, let's go wild and reference our original
 matricies in a similar manner:
@@
 \label{mm_ident}
-For all $\vec{m}$ and $\vec{n}$ on which the operations are valid,
+For all multimaticies, $A$, and all vectors, $\vec{m}$ and $\vec{n}$,  on which
+these operations are valid,
 \[
@@
 \end{ppart}
+\end{proof}
+
+\begin{theorem}[Multiplicative Identity Implication]
+\label{mm_ident_imp}
+Similarly, if there is a matrix $X$ of shape $\vec{x} \oplus \vec{x}$ such that
+for all matricies, $A$, for which the operation is defined,
+
+\[A \mmult{|\vec{x}|} X = A \]
+
+Then $X = \Ident^2(\vec{x})$.
+\end{theorem}
+\begin{proof}
+TODO
 \end{proof}
@@
 
-Given a multimatrix, $M$, you might ask, ``What is the multiplicative inverse of $M$?''
+Given a multimatrix, $X$, you might ask, ``What is the multiplicative inverse of $X$?''
 And I would have to tell you that your question is not well formed.
 
-Since multimatrix multiplication is a trinary operation, you need to factor in the
-index of multipliction. Consider multiplication by $M$ a function on $X$ - some other
-multimatrix. That is, 
-\[ F(X; M, m) = M \mmult{m} X \]
-
-What we're looking for in a `multiplicative inverse' is actually a function which,
-when composed with $F$, results in $X$. That is,
-
-\[ (F^{-1} \circ F)(X) = F^{-1}(M \mmult{m} X) = X \]
-
-That inverse function, $F^{-1}$ also needs to be a multiplication operation to
-really be a `multiplicative inverse', so we can assume that it is defined by
-some multimatrix $N$ and some inverting index of multiplication $n$, such that,
-
-\[ F^{-1} (Y; N, n) = N \mmult{n} Y \]
-
-Let's say that $M$ has some shape $\vec{l} \oplus \vec{r}$ such that $|\vec{r}| = m$.
-Then it is only applicable for an $m$ overlap multiplication on some $X$ where,
-$|X| = \vec{r} \oplus \vec{x}$ for some $\vec{x}$.
-
-So since,
-\[ |M \mmult{m} X| = \vec{l} \oplus \vec{x}\]
-and
-\[ |N \mmult{n} (M \mmult{m} X)| = |X| = \vec{r} \oplus \vec{x} \]
-It must be true that, $n = |\vec{l}|$ and $|N| = \vec{r} \oplus \vec{l}$.
-
-TODO
+\begin{align*}
+  (M \mmult{m} X) \mmult{n} Y &= M \\
+  |M| &= \vec{l} \oplus \vec{m} \\
+  |X| &= \vec{m} \oplus \vec{x} \\
+  |\vec{m}| &= m \\
+  |M \mmult{m} X| &= \vec{l} \oplus \vec{x} \\
+  |(M \mmult{m} X) \mmult{n} Y| &= |M| \\
+  &= \vec{l} \oplus \vec{m} \\
+  \therefore |Y| &= \vec{x} \oplus \vec{m} \\
+  n &= |\vec{x}|
+\end{align*}
+
+By Thm. \ref{mm_associativity}, we can then say that,
+
+\begin{align*}
+  (M \mmult{m} X) \mmult{n} Y &= M \mmult{m} (X \mmult{n} Y) \\
+  M &= M \mmult{m} (X \mmult{n} Y)
+\end{align*}
+
+Then by Thm. \ref{mm_ident_imp}, since $|X \mmult{n} Y| = \vec{m} \oplus \vec{m}$ and for all
+$M$ where the operation is defined $M \mmult{m} (X \mmult{n} Y) = M$, it follows that
+$X \mmult{n} Y = \Ident^2(\vec{m})$.
+
+% TODO
 

### 2020-04-08 Math/book.tex
Proving some things about multiplicative inverses.

@@
 \DeclareMathOperator{\remainder}{mod}
+\DeclareMathOperator{\RMult}{RMult}
+\DeclareMathOperator{\LMult}{LMult}
 %\newcommand{\mmult}[1]{\stackrel{\times}{#1}}
@@
 talking about. I've got a \sout{doctorate}
-masters degree in \sout{mathematics} \sout{a real engineering field}, fine, software
+masters degree in \sout{mathematics} I mean \sout{a real engineering field}, fine, software
 engineering. Whatever. Just look at how the
@@
 
-\begin{theorem}[Multiplicative Identity Implication]
+There is an obvious corollary to that which you might consider an
+alternate definition of $\Ident^2$.
+
+\begin{corollary}[Multiplicative Identity Implication]
 \label{mm_ident_imp}
-Similarly, if there is a matrix $X$ of shape $\vec{x} \oplus \vec{x}$ such that
+If there is a matrix $X$ of shape $\vec{x} \oplus \vec{x}$ such that
 for all matricies, $A$, for which the operation is defined,
@@
 Then $X = \Ident^2(\vec{x})$.
-\end{theorem}
-\begin{proof}
-TODO
+
+Or if for all matricies, $B$, for which the operation is defined,
+
+\[X \mmult{|\vec{x}|} B = B \]
+
+Then, again, $X = \Ident^2(\vec{x})$.
+\end{corollary}
+\begin{proof}
+Let $X$ be a matrix of shape $\vec{x} \oplus \vec{x}$. 
+\begin{ppart}
+If for all multimatrixes, $A$, on which $A \mmult{|\vec{x}|} X$ is defined, 
+$A \mmult{|\vec{x}|} X = A$ this implies that, in the case of $A = \Ident^2(\vec{x})$,
+
+\begin{align*}
+  A \mmult{|\vec{x}|} X &= A \\
+ \Ident^2(\vec{x}) \mmult{|\vec{x}|} X &= \Ident^2(\vec{x}) \\
+  X &= \Ident^2(\vec{x}) 
+\end{align*}
+\end{ppart}
+\begin{ppart}
+If for all multimatrixes, $B$, on which $X \mmult{|\vec{x}|} B$ is defined, 
+$X \mmult{|\vec{x}|} B = B$ this implies that, in the case of $B = \Ident^2(\vec{x})$,
+
+\begin{align*}
+  X \mmult{|\vec{x}|} B &= B \\
+  X \mmult{|\vec{x}|} \Ident^2(\vec{x}) &= \Ident^2(\vec{x}) \\
+  X &= \Ident^2(\vec{x}) 
+\end{align*}
+\end{ppart}
 \end{proof}
@@
 Given a multimatrix, $X$, you might ask, ``What is the multiplicative inverse of $X$?''
-And I would have to tell you that your question is not well formed.
-
-\begin{align*}
-  (M \mmult{m} X) \mmult{n} Y &= M \\
-  |M| &= \vec{l} \oplus \vec{m} \\
-  |X| &= \vec{m} \oplus \vec{x} \\
-  |\vec{m}| &= m \\
-  |M \mmult{m} X| &= \vec{l} \oplus \vec{x} \\
-  |(M \mmult{m} X) \mmult{n} Y| &= |M| \\
-  &= \vec{l} \oplus \vec{m} \\
-  \therefore |Y| &= \vec{x} \oplus \vec{m} \\
-  n &= |\vec{x}|
-\end{align*}
-
-By Thm. \ref{mm_associativity}, we can then say that,
-
+And I would have to tell you that your question is not well formed. Do you mean left multiplication
+or right multiplication? Multiplication by what width? It's not clear which of these specifications
+is even required: consider that multiplication is not communicative for regular 2d matricies but
+those have simple multiplicative inverses (if an inverse exists).
+
+So let's clarify what we can.
+
+\begin{definition}[Multiplicative Functions]
+Let us declare the function $\RMult[m,X](M)$ to be the function defined 
+by the tuple,
+\[ \left<m,X\right> \in \{  (\{0\} \cup \mathbb{N}) \times \mathbb{R}^{\vec{m} \oplus \vec{x}}  :  |\vec{m}| = m \} \]
+such that,
+\[ \RMult[m,X](M) : \mathbb{R}^{\vec{l} \oplus \vec{m}} \to \mathbb{R}^{\vec{l} \oplus \vec{x}} \]
+\[ \RMult[m,X](M) = M \mmult{m} X \]
+
+Let us also declare the function $\LMult[m,X](M)$ to be the function defined 
+by the tuple,
+\[ \left<m,X\right> \in \{  (\{0\} \cup \mathbb{N}) \times \mathbb{R}^{\vec{x} \oplus \vec{m}}  :  |\vec{m}| = m \} \]
+such that,
+\[ \LMult[m,X](M) : \mathbb{R}^{\vec{m} \oplus \vec{r}} \to \mathbb{R}^{\vec{x} \oplus \vec{r}} \]
+\[ \LMult[m,X](M) = X \mmult{m} M \]
+
+The the set of all these functions be $\RMult$ and $\LMult$ respectively.
+\end{definition}
+
+That will let us formally define a multiplicative inverse:
+
+\begin{definition}[Multiplicative Inverse]
+For any $\RMult[m,X]$ and $\RMult[n,Y]$ if, for all valid inputs of $\RMult[m,X]$, $M$,
+\[ \RMult[n,Y] \circ \RMult[m,X] (M) = M \]
+Then $\RMult[n,Y]$ is an inverse of $\RMult[m,X]$. In other words,
+\[ \RMult[n,Y] \in \RMult[m,X]^{-1} \]
+
+Similarly, for any $\LMult[m,X]$ and $\LMult[n,Y]$ if, for all valid inputs of $\LMult[m,X]$, $M$,
+\[ \LMult[n,Y] \circ \LMult[m,X] (M) = M \]
+Then $\LMult[n,Y]$ is an inverse of $\LMult[m,X]$. In other words,
+\[ \LMult[n,Y] \in \LMult[m,X]^{-1} \]
+\end{definition}
+
+Note that those inverses are defined as sets of operations, not individual operations. 
+You'll see why in a bit but to clear up any early confusion you should note that multimatrix
+multiplicative inverses aren't unique. For example, $\RMult[2,\Ident^2(\left<2,2\right>)]$ has
+two multiplicative inverse I can think of off the top of my head;
+$\RMult[2,\Ident^2(\left<2,2\right)]$ or
+$\RMult[1,\Ident^2(\left<2\right>)]$.
+
+\begin{theorem}[Relation of Inverse to Identity]
+If $\RMult[n,Y]$ is an inverse of $\RMult[m,X]$ where $|X| = \vec{m} \oplus \vec{x}$ and $|\vec{m}| = m$
+then $X \mmult{n} Y = \Ident^2(\vec{m})$.
+And if $\LMult[n,Y]$ is an inverse of $\LMult[m,X]$ where $|X| = \vec{x} \oplus \vec{m}$ and $|\vec{m}| = m$
+then $Y \mmult{n} X = \Ident^2(\vec{m})$.
+\end{theorem}
+\begin{proof}
+\begin{ppart}
+Let $X$ be a multimatrix such that $|X| = \vec{m} \oplus \vec{x}$ and $|\vec{m}| = m$.
+If $\RMult[n,Y]$ is the inverse of $\RMult[m,X]$ then, for all $M$,
+\begin{align*}
+  \RMult[n,Y] \circ \RMult[m,X] (M) &= M \\
+  (M \mmult{m} X) \mmult{n} Y &= M
+\end{align*}
+
+This is also true in the case where $M = \Ident^2(\vec{m})$. In which case,
+\begin{align*}
+  (\Ident^2(\vec{m}) \mmult{m} X) \mmult{n} Y &= \Ident^2(\vec{m}) \\
+  X \mmult{n} Y &= \Ident^2(\vec{m}) \\
+\end{align*}
+\end{ppart}
+\begin{ppart}
+Let $X$ be a multimatrix such that $|X| = \vec{x} \oplus \vec{m}$ and $|\vec{m}| = m$.
+If $\LMult[n,Y]$ is the inverse of $\LMult[m,X]$ then, for all $M$,
+\begin{align*}
+  \LMult[n,Y] \circ \LMult[m,X] (M) &= M \\
+  Y \mmult{n} (X \mmult{m} M) &= M
+\end{align*}
+
+This is also true in the case where $M = \Ident^2(\vec{m})$. In which case,
+\begin{align*}
+  Y \mmult{n} (X \mmult{m} \Ident^2(\vec{m})) &= \Ident^2(\vec{m}) \\
+  Y \mmult{n} X &= \Ident^2(\vec{m})
+\end{align*}
+\end{ppart}
+\end{proof}
+
+\begin{theorem}[Shape of Inverses]
+If $\RMult[n,Y]$ is an inverse of $\RMult[m,X]$ where $|X| = \vec{m} \oplus \vec{x}$ and
+$|\vec{m}| = m$ then $n \le ||X||-m$.
+
+Also, if $\LMult[n,Y]$ is an inverse of $\LMult[m,X]$ where $|X| = \vec{x} \oplus \vec{m}$ and
+$|\vec{m}| = m$ then $n \le ||X||-m$.
+\end{theorem}
+\begin{proof}
+\begin{ppart}
+Let $\RMult[n,Y]$ be an inverse of $\RMult[m,X]$ where $|X| = \vec{m} \oplus \vec{x}$ and
+$|\vec{m}| = m$.
+Let $M$ be some valid input of $\RMult[m,X]$.
+In other words, $|M| = \vec{l} \oplus \vec{m}$ for some $\vec{l}$.
+So $|M \mmult{m} X| = \vec{l} \oplus \vec{x}$.
+Since $\RMult[n,Y]$ is a valid operation on $M \mmult{m} X$, $n \le |\vec{l} \oplus \vec{x}|$.
+And since there is no restriction on $\vec{l}$ it's only useful to say that $n \le |\vec{x}|$.
+Given that $||X|| = |\vec{x}| + m$ it follows that $n \le ||X|| - m$.
+\end{ppart}
+\begin{ppart}
+Let $\LMult[n,Y]$ be an inverse of $\LMult[m,X]$ where $|X| = \vec{x} \oplus \vec{m}$ and
+$|\vec{m}| = m$.
+Let $M$ be some valid input of $\LMult[m,X]$.
+In other words, $|M| = \vec{m} \oplus \vec{r}$ for some $\vec{r}$.
+So $|X \mmult{m} M| = \vec{x} \oplus \vec{r}$.
+Since $\RMult[n,Y]$ is a valid operation on $X \mmult{m} M$, $n \le |\vec{x} \oplus \vec{r}|$.
+And since there is no restriction on $\vec{r}$ it's only useful to say that $n \le |\vec{x}|$.
+Given that $||X|| = |\vec{x}| + m$ it follows that $n \le ||X|| - m$.
+\end{ppart}
+\end{proof}
+
+\begin{theorem}[Relation of Identity to Inverse]
+If $X \mmult{n} Y = \Ident^2(\vec{m})$, $|\vec{m}| = m$, $|X| = \vec{m} \oplus \vec{x}$,
+and $n \le ||X||-m$, that implies that $\RMult[n, Y]$ is an inverse of $\RMult[m, X]$.
+
+Also,  if $Y \mmult{n} X = \Ident^2(\vec{m})$, $|\vec{m}| = m$, $|X| = \vec{x} \oplus \vec{m}$,
+and $n \le ||X||-m$, that implies that $\LMult[n, Y]$ is an inverse of $\LMult[m, X]$.
+\end{theorem}
+\begin{proof}
+\begin{ppart}
+Let $X \mmult{n} Y = \Ident^2(\vec{m})$, $|\vec{m}| = m$, $|X| = \vec{m} \oplus \vec{x}$, and $n \le ||X||-m$.
+We know that $n \le |\vec{x}|$ since $|\vec{x}| = ||X||-m$.
+Then we can split up $\vec{x}$ into $\vec{x_l} \oplus \vec{x_r}$ where $|\vec{x_r}| = n$.
+So $|Y| = \vec{x_r} \oplus \vec{y}$ for some $\vec{y}$ since $X \mmult{n} Y$ is defined.
+We can then find the shape $|X \mmult{n} Y| = \vec{m} \oplus \vec{x_l} \oplus \vec{y}$.
+Then for any $M$ such that $M \mmult{m} X$ is defined, i.e. any $M$ of shape $\vec{l} \oplus \vec{m}$ for some $\vec{l}$,
+we can tell that $M \mmult{m} (X \mmult{n} Y)$ is also defined.
+And since $n \le ||X||-m$ that implies $n+m \le ||X||$ so $M \mmult{m} (X \mmult{n} Y) = (M \mmult{m} X) \mmult{n} Y$
+by Theorem \ref{mm_associativity}.
+And if we just replace $X \mmult{n} Y$ with it's given value, then for all $M$ on which the $\RMult[m,X]$ is defined,
 \begin{align*}
   (M \mmult{m} X) \mmult{n} Y &= M \mmult{m} (X \mmult{n} Y)  \\
-  M &= M \mmult{m} (X \mmult{n} Y)
-\end{align*}
-
-Then by Thm. \ref{mm_ident_imp}, since $|X \mmult{n} Y| = \vec{m} \oplus \vec{m}$ and for all
-$M$ where the operation is defined $M \mmult{m} (X \mmult{n} Y) = M$, it follows that
-$X \mmult{n} Y = \Ident^2(\vec{m})$.
-
-% TODO
+  &= M \mmult{m} \Ident^2(\vec{m}) \\
+  &= M \\
+  \RMult[n,Y] \circ \RMult[m,X](M) &= M
+\end{align*}
+Therefore $\RMult[n,Y]$ is an inverse of $\RMult[m,X]$.
+\end{ppart}
+\begin{ppart}
+Let $Y \mmult{n} X = \Ident^2(\vec{m})$, $|\vec{m}| = m$, $|X| = \vec{x} \oplus \vec{m}$, and $n \le ||X||-m$.
+We know that $n \le |\vec{x}|$ since $|\vec{x}| = ||X||-m$.
+Then we can split up $\vec{x}$ into $\vec{x_l} \oplus \vec{x_r}$ where $|\vec{x_l}| = n$.
+So $|Y| = \vec{y} \oplus \vec{x_l}$ for some $\vec{y}$ since $Y \mmult{n} X$ is defined.
+We can then find the shape $|Y \mmult{n} X| = \vec{y} \oplus \vec{x_r} \oplus \vec{m}$.
+Then for any $M$ such that $X \mmult{m} M$ is defined, i.e. any $M$ of shape $\vec{m} \oplus \vec{r}$ for some $\vec{r}$,
+we can tell that $(Y \mmult{n} X) \mmult{m} M$ is also defined.
+And since $n \le ||X||-m$ that implies $n+m \le ||X||$ so $(Y \mmult{n} X) \mmult{m} M = Y \mmult{n} (X \mmult{m} M)$
+by Theorem \ref{mm_associativity}.
+And if we just replace $Y \mmult{n} X$ with it's given value, then for all $M$ on which the $\LMult[m,X]$ is defined,
+\begin{align*}
+  Y \mmult{n} (X \mmult{m} M) &= (Y \mmult{n} X) \mmult{m} M  \\
+  &= \Ident^2(\vec{m}) \mmult{m} M\\
+  &= M \\
+  \LMult[n,Y] \circ \LMult[m,X](M) &= M
+\end{align*}
+Therefore $\LMult[n,Y]$ is an inverse of $\LMult[m,X]$.
+\end{ppart}
+\end{proof}
+
+%TODO
 

### 2020-06-11 Math/book.tex
Testing some theorems imperically and expanding on hadamard products

@@
 \title{%
-  Multimatrices and Their Derivatives \\
-  \large An Impractical Guide to Global Conquest}
+  \sout{Machine Learning for Global Conquest} \\
+  Multimatrices and Their Derivatives}
 \author{Ernest Kirstein}
@@
 \DeclareMathOperator{\LMult}{LMult}
+\DeclareMathOperator{\Idx}{Idx}
+\DeclareMathOperator{\size}{size}
 %\newcommand{\mmult}[1]{\stackrel{\times}{#1}}
@@
 \newcommand{\dmult}[1]{\text{\raisebox{1ex}{$\underset{#1}{\,\bullet\,}$}}}
+\newcommand{\shape}[1]{\left|#1\right|}
 
@@
 \chapter*{Preface}
-I was working my way through a hobby programming project, trying to create a so called
-`deep fake' of Danny DeVito's face on Scarlett Johansson's body, and ran into a problem.
-The existing notation for taking derivatives of matrix equations is terrible.
-It's so deliberately obtuse that I could only conclude that some hidden cabal of
-mathematicians is actively working to sabotage the rise of our glorious AI overlords.
+I was working my way through a hobby programming project, trying to create deep fakes of
+\sout{polititians in compromising positions} humorous celebrity mashups, when I ran into a problem.
+The existing notation for derivatives of matrix equations is terrible.
+It's so deliberately obtuse that I can only conclude that some hidden cabal of
+mathematicians is actively working to sabotage \sout{the rise of our glorious AI overlords}
+our machine learning research.
 I, for one, will not stand for such heresy.
@@
 
-Formally, the shape of these two matricies are defined,
-$|B| = |X| = \left< 3,5 \right>$.
+Suppose the shape of these two matricies are defined,
+$\shape{B} = \shape{X} = \left< 3,5 \right>$.
 And each element of $B$ will be the sine of the corresponding element of
@@
 \[
-\mbox{size}\left(\frac{dB}{dX}\right) = \mbox{size}(B) \mbox{size}(X)
+\size\left(\frac{dB}{dX}\right) = \size(B) \size(X)
 \]
@@
 \begin{align*}
-\left|\frac{dB}{dX}\right| &= |B| \oplus |X| \\
+\shape{\frac{dB}{dX}} &= \shape{B} \oplus \shape{X} \\
  &= \left< 3, 5 \right> \oplus \left< 3, 5 \right> \\
@@
 both output and indepenedent variable are preserved and that our notation is
-consistent. Let us declare this to
+consistent.
+
+Let us declare this to
 be our convention. I've typeset it in \LaTeX ~therefore it can no longer be
@@
 
-Our total derivate is therefore a multidimensional object with four indicies.
+So anyways, our total derivate is a multidimensional object with four indicies.
 Suppose we try to pull a single partial derivative from this complete derivative,
@@
 
-Which isn't a huge improvement over our original notation. What would be great is
+Which isn't a huge improvement over the original notation. What would be great is
 if we could define the total derivative without going down into the partial derivatives
@@
 
-The multiplication of traditional matricies is a calculation that, when one first
-encouters it, inspires thoughts such as, ``What the shit?'' or, ``Get me a knife,
-I gotta to stab someone.''
+The multiplication of traditional matricies is a calculation that, when first
+encoutered, inspires thoughts of omnicide.
 
@@
 structurally sound.
+
 Let $|A| = \left<5,7,7\right>$ and $|B| = \left<7,7,2,4\right>$.
@@
 come by). So here is where we leave behind nice graphical representations of
-things, and I'll just define the elements of $A$ and $B$ in the tables below.
+things and I'll just define the elements of $A$ and $B$ in the tables below.
 \begin{table}[h!]
@@
 not (usually) communicative. And it is only weakly associative. That sounds like
-nonsense, and ideed it is, but I shall prove it to you.
+nonsense, and indeed it is, but I shall prove it to you.
 
@@
 \begin{theorem}[Identity Contraction]
-For all $m, n, k \in \mathbb{N}$ and $\vec{x}$ as a valid multimatrix shape,
+For all $m, n, k \in \mathbb{N}$ (note $m$, $n$, and $k$ are non-zero) and $\vec{x}$ as a valid multimatrix shape,
 where $m > k$ and $n > k$,
@@
 
-%TODO
+This is all well and good, but I'm sure what you really want to know is how to find a multiplicative inverse.
+It seams increadibly complicated until you realize that there is a way to relate any multimatrix multiplication
+to a 2d matrix multiplication. We'll first need to define a special function:
+
+\begin{definition}[Indexing Function]
+Let $\vec{x}$ be some shape vector and $\bar{x} \in \Dim(\vec{x})$. Then the indexing function is one which transforms
+that $\bar{x}$ into a unique integer (i.e. it is one-to-one):
+\[
+  \Idx[\vec{x}](\bar{x}) = \sum_{1 \le i \le |\vec{x}|} \left( (\bar{x}[i]-1) \prod_{1 \le j < i} \vec{x}[j] \right)
+\]
+And then inverse function takes an integer and returns a vector in $\Dim(\vec{x})$:
+\[ |\Idx[\vec{x}]^{-1}(n)| = |\vec{x}| \]
+\[
+  \Idx[\vec{x}]^{-1}(n)[i] =
+    \left\lfloor
+      \frac{\remainder\left(n, \prod_{1 \le j \le i} \vec{x}[j]\right)}
+      {\prod_{1 \le k < i} \vec{x}[k]}
+    \right\rfloor + 1
+\]
+Where $\Idx[\vec{x}]^{-1}(n)[i]$ is the $i$th value of the vector output of $\Idx[\vec{x}]^{-1}(n)$.
+Also, $\remainder$ is the remainder function.
+\end{definition}
+
+\begin{landscape}
+Let's prove those properties of the indexing function before moving on. If we prove that the inverse function
+really is an inverse, then that implies the function is one-to-one. So let's just do that:
+
+\begin{proof}
+Let $\bar{x} \in \Dim(\vec{x})$ and let $k$ be any index of $\bar{x}$.
+
+\begin{align*}
+  \Idx[\vec{x}]^{-1}(\Idx[\vec{x}](\bar{x}))[k] &= 
+  \left\lfloor
+    \frac{\remainder\left(
+      \sum_{1 \le i \le |\vec{x}|} \left( (\bar{x}[i]-1) \prod_{1 \le j < i} \vec{x}[j] \right) 
+      , \prod_{1 \le m \le k} \vec{x}[m]\right)}
+    {\prod_{1 \le n < k} \vec{x}[n]}
+  \right\rfloor + 1 \\
+  &=
+  \left\lfloor
+    \frac{\remainder\left(
+      \sum_{1 \le i \le k} \left( (\bar{x}[i]-1) \prod_{1 \le j < i} \vec{x}[j] \right) 
+      , \prod_{1 \le m \le k} \vec{x}[m]\right)}
+    {\prod_{1 \le n < k} \vec{x}[n]}
+  \right\rfloor + 1 \\
+  &=
+  \left\lfloor
+    \frac{
+      \sum_{1 \le i \le k} \left( (\bar{x}[i]-1) \prod_{1 \le j < i} \vec{x}[j] \right) 
+    }
+    {\prod_{1 \le n < k} \vec{x}[n]}
+  \right\rfloor + 1 \\
+  &=
+  \left\lfloor
+    \frac{
+      \sum_{1 \le i < k} \left( (\bar{x}[i]-1) \prod_{1 \le j < i} \vec{x}[j] \right) 
+    }
+    {\prod_{1 \le n < k} \vec{x}[n]}
+    +
+    (\bar{x}[k]-1)
+  \right\rfloor + 1 \\
+  &= \bar{x}[k]-1+1 \\
+  &= \bar{x}[k]
+\end{align*}
+
+A couple of leaps of logic there rely on the fact that 
+\[
+  \sum_{1 \le i \le k} \left( (\bar{x}[i]-1) \prod_{1 \le j < i} \vec{x}[j] \right)
+  < \prod_{1 \le m \le k} \vec{x}[m]
+\]
+Which is true because
+\begin{align*}
+  \sum_{1 \le i \le k} \left( (\bar{x}[i]-1) \prod_{1 \le j < i} \vec{x}[j] \right)
+  &< \prod_{1 \le m \le k} \vec{x}[m] \\
+  \sum_{1 \le i \le k} \left( \bar{x}[i]\prod_{1 \le j < i} \vec{x}[j] - \prod_{1 \le j < i} \vec{x}[j] \right)
+  &< \prod_{1 \le m \le k} \vec{x}[m] \\
+  \sum_{1 \le i \le k} \left( \bar{x}[i]\prod_{1 \le j < i} \vec{x}[j] \right)
+  - \sum_{1 \le i \le k} \left( \prod_{1 \le j < i} \vec{x}[j] \right)
+  &< \prod_{1 \le m \le k} \vec{x}[m] \\
+  \sum_{1 \le i \le k} \left( \prod_{1 \le j < i+1} \vec{x}[j] \right)
+  - \sum_{1 \le i \le k} \left( \prod_{1 \le j < i} \vec{x}[j] \right)
+  &< \prod_{1 \le m \le k} \vec{x}[m] \\
+  \left( \prod_{1 \le j < k+1} \vec{x}[j] \right)
+  + \sum_{1 \le i < k} \left( \prod_{1 \le j < i+1} \vec{x}[j] \right)
+  - \sum_{1 < i \le k} \left( \prod_{1 \le j < i} \vec{x}[j] \right)
+  - 1
+  &< \prod_{1 \le m \le k} \vec{x}[m] \\
+  \left( \prod_{1 \le j \le k} \vec{x}[j] \right)-1
+  + \sum_{1 < i \le k} \left( \prod_{1 \le j < i} \vec{x}[j] \right)
+  - \sum_{1 < i \le k} \left( \prod_{1 \le j < i} \vec{x}[j] \right)
+  &< \prod_{1 \le m \le k} \vec{x}[m] \\
+  \left( \prod_{1 \le j \le k} \vec{x}[j] \right)-1
+  &< \prod_{1 \le m \le k} \vec{x}[m]
+\end{align*}
+Note in the 4th step there that $\bar{x}[i] \le \vec{x}[i]$ so replacing it with $\vec{x}[i]$
+will not increase the maximum value.
+
+So, that concludes the proof. Since the inverse works for any index of $\bar{x}$ we know that the inverse works to restore the
+whole of the vector. Thus, $\Idx[\vec{x}]^{-1}$ is indeed the inverse of $\Idx[\vec{x}]$.
+\end{proof}
+
+TODO:exposition
+
+\begin{theorem}[Index of Concatenated Vectors]
+Let $\vec{a}$ and $\vec{b}$ be any two vectors of natural numbers. Then for all $\bar{a} \in \Dim(\vec{a})$
+and $\bar{b} \in \Dim(\vec{b})$:
+\[ \Idx[\vec{a} \oplus \vec{b}](\bar{a} \oplus \bar{b}) = \Idx[\vec{a}](\bar{a}) + |\Dim(\vec{a})| \Idx[\vec{b}](\bar{b}) \]
+\end{theorem}
+\begin{proof}
+Let $\vec{a}$ and $\vec{b}$ be any two vectors of natural numbers. Then for all $\bar{a} \in \Dim(\vec{a})$
+and $\bar{b} \in \Dim(\vec{b})$:
+\begin{align*}
+  \Idx[\vec{a} \oplus \vec{b}](\bar{a} \oplus \bar{b})
+  &= 
+  \sum_{1 \le i \le |\vec{a} \oplus \vec{b}|} \left( ((\bar{a} \oplus \bar{b})[i]-1) \prod_{1 \le j < i} (\vec{a} \oplus \vec{b})[j] \right) \\
+  &= 
+  \left( \sum_{1 \le i \le |\vec{a}|} \left( ((\bar{a} \oplus \bar{b})[i]-1) \prod_{1 \le j < i} (\vec{a} \oplus \vec{b})[j] \right) \right) +
+  \left( \sum_{|\vec{a}|+1 \le i \le |\vec{a}|+|\vec{b}|} \left( ((\bar{a} \oplus \bar{b})[i]-1) \prod_{1 \le j < i} (\vec{a} \oplus \vec{b})[j] \right) \right)\\
+  &= 
+  \left( \sum_{1 \le i \le |\vec{a}|} \left( (\bar{a}[i]-1) \prod_{1 \le j < i} \vec{a}[j] \right) \right) +
+  \left( \sum_{|\vec{a}|+1 \le i \le |\vec{a}|+|\vec{b}|} \left( (\bar{b}[i-|\vec{a}|]-1) \prod_{1 \le j \le |\vec{a}|} \vec{a}[j] \prod_{1 \le j < i-|\vec{a}|} \vec{b}[j] \right) \right)\\
+  &= 
+  \left( \sum_{1 \le i \le |\vec{a}|} \left( (\bar{a}[i]-1) \prod_{1 \le j < i} \vec{a}[j] \right) \right) +
+  \left( \sum_{1 \le i \le |\vec{b}|} \left( (\bar{b}[i|]-1) |\Dim(\vec{a})| \prod_{1 \le j < i|} \vec{b}[j] \right) \right)\\
+  &= 
+  \Idx[\vec{a}](\bar{a}) +
+  |\Dim(\vec{a})| \sum_{1 \le i \le |\vec{b}|} \left( (\bar{b}[i|]-1) \prod_{1 \le j < i|} \vec{b}[j] \right)\\
+  &= 
+  \Idx[\vec{a}](\bar{a}) +
+  |\Dim(\vec{a})| \Idx[\vec{b}](\bar{b})
+\end{align*}
+\end{proof}
+
+Now you might be wondering what that indexing function has to do with inverting
+multimatricies. I said before that it we would need to show how the multiplication
+of two multimatricies can be converted into an equivelent multiplication of two
+2d matricies. Here's how that's done,
+
+\begin{theorem}[Reshaping Multimatrix Multiplication]
+Let $A$ and $B$ be two multimatricies of shapes $|A| = \vec{a} \oplus \vec{c}$ and
+$|B| = \vec{c} \oplus \vec{b}$, and let $C$ be the multimatrix resulting in the $|\vec{c}|$
+width multiplication of $A$ and $B$, that is,
+\[ A \mmult{|\vec{c}|} B = C \]
+Now, let $\vec{x}$, $\vec{y}$, and $\vec{z}$ be any vectors such that
+$|\Dim(\vec{a})| = |\Dim(\vec{x})|$,
+$|\Dim(\vec{b})| = |\Dim(\vec{y})|$,
+and 
+$|\Dim(\vec{c})| = |\Dim(\vec{z})|$.
+Then for multimatricies $X$, $Y$, and $Z$ defined such that,
+\[\forall i : 0 \le i < \size(A) \]
+\[ X[\Idx[\vec{x} \oplus \vec{z}]^{-1}(i)] = A[\Idx[\vec{a} \oplus \vec{c}]^{-1}(i)] \]
+
+\[\forall j : 0 \le j < \size(B)\]
+\[ Y[\Idx[\vec{z} \oplus \vec{y}]^{-1}(j)] = B[\Idx[\vec{c} \oplus \vec{b}]^{-1}(j)] \]
+
+and,
+
+\[\forall k : 0 \le k < \size(C)\]
+\[ Z[\Idx[\vec{x} \oplus \vec{y}]^{-1}(k)] = C[\Idx[\vec{a} \oplus \vec{b}]^{-1}(k)] \]
+
+it is true that,
+
+\[ X \mmult{|\vec{z}|} Y = Z \]
+\end{theorem}
+\begin{proof}
+Let $A$ and $B$ be two multimatricies of shapes $|A| = \vec{a} \oplus \vec{c}$ and
+$|B| = \vec{c} \oplus \vec{b}$, and let $C$ be the multimatrix resulting from,
+\[ A \mmult{|\vec{c}|} B = C \]
+
+Now, let $\vec{x}$, $\vec{y}$, and $\vec{z}$ be any vectors such that
+$|\Dim(\vec{a})| = |\Dim(\vec{x})|$,
+$|\Dim(\vec{b})| = |\Dim(\vec{y})|$,
+and 
+$|\Dim(\vec{c})| = |\Dim(\vec{z})|$.
+And let multimatricies $X$, $Y$, and $Z$ be defined such that,
+\[\forall i : 0 \le i < \size(A) \]
+\[ X[\Idx[\vec{x} \oplus \vec{z}]^{-1}(i)] = A[\Idx[\vec{a} \oplus \vec{c}]^{-1}(i)] \]
+
+\[\forall j : 0 \le j < \size(B)\]
+\[ Y[\Idx[\vec{z} \oplus \vec{y}]^{-1}(j)] = B[\Idx[\vec{c} \oplus \vec{b}]^{-1}(j)] \]
+
+and,
+
+\[\forall k : 0 \le k < \size(C)\]
+\[ Z[\Idx[\vec{x} \oplus \vec{y}]^{-1}(k)] = C[\Idx[\vec{a} \oplus \vec{b}]^{-1}(k)] \]
+
+Then for all $\bar{a} \in \Dim(\vec{a})$ and $\bar{b} \in \Dim(\vec{b})$,
+
+\begin{align*}
+  (A \mmult{|\vec{c}|} B)[\bar{a} \oplus \bar{b}]
+  &= C[\bar{a} \oplus \bar{b}] \\
+  &=
+  \sum_{\forall \bar{c} \in \Dim(\vec{c})} A[\bar{a} \oplus \bar{c}] B[\bar{c} \oplus \bar{b}] \\
+  &=
+  \sum_{0 \le i_c < |\Dim(\vec{c})|} A[\bar{a} \oplus \Idx[\vec{c}]^{-1}(i_c)] B[\Idx[\vec{c}]^{-1}(i_c) \oplus \bar{b}]
+\end{align*}
+
+Now let $i_a = \Idx[\vec{a}](\bar{a})$ and $i_b = \Idx[\vec{b}](\bar{b})$ and,
+\begin{align*}
+  C[\Idx[\vec{a}  \oplus \vec{b}]^{-1}(i_a + |\Dim(\vec{a})| i_b)]
+  &=
+  \sum_{0 \le i_c < |\Dim(\vec{c})|} A[\Idx[\vec{a}]^{-1}(i_a) \oplus \Idx[\vec{c}]^{-1}(i_c)] B[\Idx[\vec{c}]^{-1}(i_c) \oplus \Idx[\vec{b}]^{-1}(i_b)] \\
+  &=
+  \sum_{0 \le i_c < |\Dim(\vec{c})|} A[\Idx[\vec{a} \oplus \vec{c}]^{-1}(i_a + |\Dim(\vec{a})|i_c)]
+                                     B[\Idx[\vec{c} \oplus \vec{b}]^{-1}(i_c + |\Dim(\vec{c})|i_b)] \\
+  &=
+  \sum_{0 \le i_c < |\Dim(\vec{c})|} X[\Idx[\vec{x} \oplus \vec{z}]^{-1}(i_a + |\Dim(\vec{a})|i_c)]
+                                     Y[\Idx[\vec{z} \oplus \vec{y}]^{-1}(i_c + |\Dim(\vec{c})|i_b)] \\
+  Z[\Idx[\vec{x}  \oplus \vec{y}]^{-1}(i_a + |\Dim(\vec{a})| i_b)]
+  &=
+  \sum_{0 \le i_c < |\Dim(\vec{c})|} X[\Idx[\vec{x} \oplus \vec{z}]^{-1}(i_a + |\Dim(\vec{a})|i_c)]
+                                     Y[\Idx[\vec{z} \oplus \vec{y}]^{-1}(i_c + |\Dim(\vec{c})|i_b)] \\
+  Z[\Idx[\vec{x}  \oplus \vec{y}]^{-1}(i_a + |\Dim(\vec{x})| i_b)]
+  &=
+  \sum_{0 \le i_c < |\Dim(\vec{z})|} X[\Idx[\vec{x} \oplus \vec{z}]^{-1}(i_a + |\Dim(\vec{x})|i_c)]
+                                     Y[\Idx[\vec{z} \oplus \vec{y}]^{-1}(i_c + |\Dim(\vec{z})|i_b)] \\
+  Z[\Idx[\vec{x}]^{-1}(i_a) \oplus \Idx[\vec{y}]^{-1}(i_b)]
+  &=
+  \sum_{0 \le i_c < |\Dim(\vec{z})|} X[\Idx[\vec{x}]^{-1}(i_a) \oplus \Idx[\vec{z}]^{-1}(i_c)]
+                                     Y[\Idx[\vec{z}]^{-1}(i_c) \oplus \Idx[\vec{y}]^{-1}(i_b)]
+\end{align*}
+Then if you let $\bar{x} = \Idx[\vec{x}](i_a)$ and $\bar{y} = \Idx[\vec{y}](i_b)$,
+\begin{align*}
+  Z[\bar{x} \oplus \bar{y}]
+  &=
+  \sum_{0 \le i_c < |\Dim(\vec{z})|} X[\bar{x} \oplus \Idx[\vec{z}]^{-1}(i_c)]
+                                     Y[\Idx[\vec{z}]^{-1}(i_c) \oplus \bar{y}] \\
+  &=
+  \sum_{\forall \bar{z} \in \Dim(\vec{z})} X[\bar{x} \oplus \bar{z}]
+                                     Y[\bar{z} \oplus \bar{y}] \\
+  &= X \mmult{|\vec{z}|} Y
+\end{align*}
+\end{proof}
+\end{landscape}
+
+Therefore for any $\RMult(m,X)$ you can potentially find an inverse with
+multiplication width $n \le ||X||-m$ by simply reshaping the problem into
+one using standard two dimensional matricies wich already has thoroughly
+explored methods for solving.
+For example, to find an $\RMult(n,Y)$ which is the inverse of $\RMult(m,X)$
+you'd reshape $X \mmult{n} Y = \Ident^2(\vec{m})$ into $A \mmult{1} B = \Ident^2(\left<\size(\Dim(\vec{m}))\right>)$
+where $|A| = \left<\size(\Dim(\vec{m} \oplus \vec{x_l})), \size(\Dim(\vec{x_r}))\right>$
+and   $|B| = \left<\size(\Dim(\vec{x_r})),  \size(\Dim(\vec{y}))\right>$.
+Then solve for $B$ and return the problem to the original shape to get $Y$.
+
+%todo: give example
 
@@
 such that,
-\[ |A \dmult{n} B| = \vec{a} \oplus \vec{c} \oplus \vec{b} \]
+\[ |A \dmult{c} B| = \vec{a} \oplus \vec{c} \oplus \vec{b} \]
 And for any $\bar{a} \in \Dim(\vec{a})$, $\bar{b} \in \Dim(\vec{b})$,
@@
 \[
-  (A \dmult{n} B)[\bar{a} \oplus \bar{c} \oplus \bar{b}]
+  (A \dmult{c} B)[\bar{a} \oplus \bar{c} \oplus \bar{b}]
   = A[\bar{a} \oplus \bar{c}] B[\bar{c} \oplus \bar{b}]
@@
 \begin{proof}
-TODO: exercise?
-\end{proof}
-
-TODO: associative?
+Let $|A| = \vec{a}$ and $|B| = \vec{b}$ then,
+\[ |A \dmult{0} B| = \vec{a} \oplus \vec{b} = |A \mmult{0} B| \]
+And for all $\bar{a} \in \Dim(\vec{a})$ and $\bar{b} \in \Dim(\vec{b})$,
+\[ (A \dmult{0} B)[\bar{a} \oplus \bar{b}] = A[\bar{a}] B[\bar{b}] = (A \mmult{0} B)[\bar{a} \oplus \bar{b}] \]
+\end{proof}
+
+TODO: exposition
+
+\begin{theorem}[Hadamard Product Associativity]
+Let $A$, $B$, and $C$ be multimatrixes such that $|A| = \vec{a} \oplus \vec{m}$,
+$|B| = \vec{m} \oplus \vec{b} \oplus \vec{n}$ and $|C| = \vec{n} \oplus \vec{c}$,
+where $|\vec{m}| = m$ and $|\vec{n}| = n$.
+Then $(A \dmult{m} B) \dmult{n} C = A \dmult{m} (B \dmult{n} C)$.
+\end{theorem}
+\begin{proof}
+For all $\bar{a} \in \Dim(\vec{a})$, etc,
+\begin{align*}
+((A \dmult{m} B) \dmult{n} C)[\bar{a} \oplus \bar{m} \oplus \bar{b} \oplus \bar{n} \oplus \bar{c}]
+  &= (A \dmult{m} B)[\bar{a} \oplus \bar{m} \oplus \bar{b} \oplus \bar{n}] C[\bar{n} \oplus \bar{c}] \\
+  &= (A[\bar{a} \oplus \bar{m}] B[\bar{m} \oplus \bar{b} \oplus \bar{n}]) C[\bar{n} \oplus \bar{c}] \\
+  &= A[\bar{a} \oplus \bar{m}] (B[\bar{m} \oplus \bar{b} \oplus \bar{n}] C[\bar{n} \oplus \bar{c}]) \\
+  &= A[\bar{a} \oplus \bar{m}] (B \dmult{n} C)[\bar{m} \oplus \bar{b} \oplus \bar{n} \oplus \bar{c}] \\
+  &= (A \dmult{m} (B \dmult{n} C))[\bar{a} \oplus \bar{m} \oplus \bar{b} \oplus \bar{n} \oplus \bar{c}]
+\end{align*}
+\end{proof}
 
@@
 
-TODO: Communicative property
+TODO: exposition
+
+\begin{theorem}[Communicativity of Hadamard Products]
+If $A$ and $B$ are multimatrices of the same shape, $|A| = |B| = \vec{x}$,
+then $A \dmult{|\vec{x}|} B = B \dmult{|\vec{x}|} A$.
+\end{theorem}
+\begin{proof}
+For any $\bar{x} \in \Dim(\vec{x})$,
+\begin{align*}
+(A \dmult{|\vec{x}|} B)[\bar{x}]
+  &= A[\bar{x}] B[\bar{x}] \\
+  &= B[\bar{x}] A[\bar{x}] \\
+  &= (B \dmult{|\vec{x}|} A)[\bar{x}]
+\end{align*}
+\end{proof}
 
@@
 itself a transpose. So transposes of multimatrcies of shape of length $n$ are
-a closed group under composition. Of.
+a closed group under composition.
 \end{ppart}
@@
 
+%TODO: I think this is even more general.
+% I think that if k = |\vec{a}| mod |\vec{a} \oplus \vec{b}| then
+% \Tran(\Ident^n(\vec{a} \oplus \vec{b}), k) = \Ident^n(\vec{b} \oplus \vec{a})
 \begin{theorem}[Identity Transpose]
@@
 
+\begin{theorem}[Hadamard Multiplication Rule]
+Let $F(X)$ and $G(X)$ be functions of $X$ where
+$|F(X)| = \vec{a} \oplus \vec{c}$ and $|G(X)| = \vec{c} \oplus \vec{b}$
+then,
+\[
+  \frac{d(F(X) \dmult{|\vec{c}|} G(X))}{dX} =
+    F(X) \dmult{|\vec{c}|} \frac{dG}{dX} +
+    \Tran\left(\Tran\left(\frac{dF}{dX}, ||F||\right) \dmult{|\vec{c}|} G(X), ||X||\right)
+\]
+\end{theorem}
+\begin{landscape}
+\begin{proof}
+For $\vec{x} = |X|$ and for $\bar{a} \in \Dim(\vec{a})$ etc,
+\begin{align*}
+\frac{d(F(X) \dmult{|\vec{c}|} G(X))}{dX}[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
+  &= \frac{\partial (F(X) \dmult{|\vec{c}|} G(X))[\bar{a} \oplus \bar{c} \oplus \bar{b}]}{\partial X[\bar{x}]} \\
+  &= \frac{\partial (F(X)[\bar{a} \oplus \bar{c}] G(X)[\bar{c} \oplus \bar{a}])}{\partial X[\bar{x}]} \\
+  &= \frac{\partial F(X)[\bar{a} \oplus \bar{c}]}{\partial X[\bar{x}]} G(X)[\bar{c} \oplus \bar{b}]
+    + F(X)[\bar{a} \oplus \bar{c}] \frac{\partial G(X)[\bar{c} \oplus \bar{b}]}{\partial X[\bar{x}]} \\
+  &= \frac{dF}{dX}[\bar{a} \oplus \bar{c} \oplus \bar{x}] G(X)[\bar{c} \oplus \bar{b}]
+    + F(X)[\bar{a} \oplus \bar{c}] \frac{dG}{dX}[\bar{c} \oplus \bar{b} \oplus \bar{x}] \\
+  &= \frac{dF}{dX}[\bar{a} \oplus \bar{c} \oplus \bar{x}] G(X)[\bar{c} \oplus \bar{b}]
+    + \left(F(X) \dmult{|\vec{c}|} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
+  &= \Tran\left(\frac{dF}{dX}, ||F||\right)[\bar{x} \oplus \bar{a} \oplus \bar{c}] G(X)[\bar{c} \oplus \bar{b}]
+    + \left(F(X) \dmult{|\vec{c}|} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
+  &= \left(\Tran\left(\frac{dF}{dX}, ||F||\right) \dmult{|\vec{c}|} G(X)\right) [\bar{x} \oplus \bar{a} \oplus \bar{c} \oplus \bar{b}]
+    + \left(F(X) \dmult{|\vec{c}|} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
+  &= \Tran\left(\Tran\left(\frac{dF}{dX}, ||F||\right) \dmult{|\vec{c}|} G(X), ||X||\right) [\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
+    + \left(F(X) \dmult{|\vec{c}|} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
+  &= \left(F(X) \dmult{|\vec{c}|} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
+    + \Tran\left(\Tran\left(\frac{dF}{dX}, ||F||\right) \dmult{|\vec{c}|} G(X), ||X||\right) [\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
+  &= \left\{ F(X) \dmult{|\vec{c}|} \frac{dG}{dX}
+    + \Tran\left(\Tran\left(\frac{dF}{dX}, ||F||\right) \dmult{|\vec{c}|} G(X), ||X||\right) \right\}[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
+\end{align*}
+\end{proof}
+\end{landscape}
+
 \begin{theorem}[Chain Rule]
@@
 Let $\Softmax(X)$ be the function
-$\Softmax : \mathbb{R}^{\vec{X}} \to \mathbb{R}^{\vec{X}}$
+$\Softmax : \mathbb{R}^{\vec{x}} \to \mathbb{R}^{\vec{x}}$
 such that $\forall \bar{x} \in \Dim(\vec{x}):$
@@
 \]
-So,
-\begin{alignat}{3}
+That right hand term is a scalar so it does have a multiplicative inverse.
+Next,
+\begin{alignat*}{3}
 	\frac{d\Softmax(X)}{dX}
@@
 	\mmult{||X||} \Softmax(X)
-\end{alignat}
+\end{alignat*}
 Let's just verify that against the Wikipedia \cite{wiki:softmax} result:

### 2020-06-11 MMatrix/src/mmatrix.cc

@@ -3,6 +3,7 @@
 #include <cmath>
 #include <stdexcept>
 #include <iostream>
+#include <sstream>
 
 namespace mmatrix {
 
@@ -10,20 +11,20 @@ using std::string;
 using std::unique_ptr;
 using std::vector;
 
-float MMatrixInterface::get(int i) const {
+MMFloat MMatrixInterface::get(int i) const {
   vector<int> indices(shape().size(), 0);
   FromValueIndex(shape(), i, &indices);
   return get(indices);
 }
-void MMatrixInterface::set(int i, float value) {
+void MMatrixInterface::set(int i, MMFloat value) {
   vector<int> indices(shape().size(), 0);
   FromValueIndex(shape(), i, &indices);
   set(indices, value);
 }
-float MMatrixInterface::get(const vector<int>& indices) const {
+MMFloat MMatrixInterface::get(const vector<int>& indices) const {
   return get(ToValueIndex(shape(), indices));
 }
-void MMatrixInterface::set(const vector<int>& indices, float value) {
+void MMatrixInterface::set(const vector<int>& indices, MMFloat value) {
   set(ToValueIndex(shape(), indices), value);
 }
 
@@ -32,12 +33,12 @@ DenseMMatrix::DenseMMatrix(const vector<int>& shape) : shape_(shape) {
   for (int i = 0; i < shape.size(); i++) {
     total_size *= shape[i];
   }
-  values_ = vector<float>(total_size, 0);
+  values_ = vector<MMFloat>(total_size, 0);
 }
-float DenseMMatrix::get(int i) const {
+MMFloat DenseMMatrix::get(int i) const {
   return values_[i];
 }
-void DenseMMatrix::set(int i, float value) {
+void DenseMMatrix::set(int i, MMFloat value) {
   values_[i] = value;
 }
 const vector<int>& DenseMMatrix::shape() const {
@@ -53,14 +54,14 @@ internal::MMatrixType DenseMMatrix::type() const {
 }
 
 SparseMMatrix::SparseMMatrix(const std::vector<int>& shape) : shape_(shape) {}
-float SparseMMatrix::get(int i) const {
+MMFloat SparseMMatrix::get(int i) const {
   const auto v = values_.find(i);
   if (v != values_.end()) {
     return v->second;
   }
   return 0;
 }
-void SparseMMatrix::set(int i, float value) {
[…]

### 2020-06-11 MMatrix/src/mmatrix.h

@@ -18,20 +18,22 @@ constexpr MMatrixType kMMatrixType_Sparse = 1;
 
 }  // namespace internal
 
+typedef double MMFloat;
+
 class MMatrixInterface {
  public:
   virtual ~MMatrixInterface() = default;
   // Returns the value stored at the given indices.
-  virtual float get(const std::vector<int>& indices) const;
+  virtual MMFloat get(const std::vector<int>& indices) const;
   // Returns the value stored at the given indices represented by i.
   // See ToValueIndex.
-  virtual float get(int i) const;
+  virtual MMFloat get(int i) const;
   // Stores a value at the given indicies represented by i.
   // See ToValueIndex.
-  virtual void set(int i, float value);
+  virtual void set(int i, MMFloat value);
   // Stores a value at the given indicies. Each index must be within it's
   // dimension defined by shape().
-  virtual void set(const std::vector<int>& indices, float value);
+  virtual void set(const std::vector<int>& indices, MMFloat value);
   // Returns the shape (size of dimensions) of this matrix.
   virtual const std::vector<int>& shape() const = 0;
   // Returns the most specific class type of the MMatrix.
@@ -47,14 +49,14 @@ class DenseMMatrix : public MMatrixInterface {
 
   using MMatrixInterface::get;
   using MMatrixInterface::set;
-  float get(int i) const override;
-  void set(int i, float value) override;
+  MMFloat get(int i) const override;
+  void set(int i, MMFloat value) override;
   const std::vector<int>& shape() const override;
   void zero() override;
   internal::MMatrixType type() const override;
 
  private:
-  std::vector<float> values_;
+  std::vector<MMFloat> values_;
   std::vector<int> shape_;
 };
 
@@ -65,8 +67,8 @@ class SparseMMatrix : public MMatrixInterface {
 
   using MMatrixInterface::get;
   using MMatrixInterface::set;
-  float get(int i) const override;
-  void set(int i, float value) override;
+  MMFloat get(int i) const override;
+  void set(int i, MMFloat value) override;
   const std::vector<int>& shape() const override;
   void zero() override;
   internal::MMatrixType type() const override;
@@ -74,15 +76,15 @@ class SparseMMatrix : public MMatrixInterface {
   // Returns the number of non-zero values in the matrix.
   int size() const;
 
[…]

### 2020-06-11 MMatrix/test/test_math.cc

@@ -1,0 +1,336 @@
+#include "mmatrix.h"
+
+#include <iostream>
+#include <cstdlib>
+#include <vector>
+#include <memory>
+#include <functional>
+
+using namespace mmatrix;
+using std::vector;
+using std::unique_ptr;
+using std::rand;
+
+///// Utils
+
+MMFloat randf() {
+  return rand()/static_cast<MMFloat>(RAND_MAX);
+}
+
+vector<int> RandShape(int length = -1 /* rand 0 to 2 */, int max = 5) {
+  if (length == -1) length = rand()%3;
+  vector<int> s;
+  s.reserve(length);
+  for (int i = 0; i < length; i++) {
+    int val = rand()%max+1;
+    s.push_back(val);
+  }
+  return s;
+}
+
+vector<int> RandIndex(const vector<int>& shape) {
+  vector<int> idx;
+  idx.reserve(shape.size());
+  for (int i = 0; i < shape.size(); i++) {
+    idx.push_back(rand()%shape[i]);
+  }
+  return idx;
+}
+
+void RandMatrix(MMatrixInterface* out, MMFloat zerochance = 0) {
+  // zerochance in [0.0,1.0]
+  // 1.0 would mean always zero
+  int ncells = 1;
+  for (int s : out->shape()) {
+    ncells *= s;
+  }
+  for (int i = 0; i < ncells; i++) {
+    if (randf() < zerochance) continue;
+    out->set(i, rand()%11-5);
+  }
+}
+
+// Approximate df/dx(x)[f_index + x_index]
+MMFloat ApproxDerivative(std::function<void(MMatrixInterface*,MMatrixInterface*)> f, MMatrixInterface* out_tmp,
+    MMatrixInterface* x, vector<int> f_index, vector<int> x_index, MMFloat epsilon = 1/static_cast<double>(2>>10)) {
+  MMFloat x1 = x->get(x_index);
+  f(x, out_tmp);
+  MMFloat y1 = out_tmp->get(f_index);
+  MMFloat x2 = x1+epsilon;
+  x->set(x_index, x2);
+  f(x, out_tmp);
+  MMFloat y2 = out_tmp->get(f_index);
+  x->set(x_index, x1);
+  return (y2-y1)/epsilon;
+}
+
+vector<int> ConcatNTimes(int n, const vector<int>& x) {
+  vector<int> out;
+  out.reserve(n*x.size());
[…]

### 2020-06-11 MMatrix/test/test_mmatrix.cc

@@ -55,7 +55,7 @@ void TestDenseMMatrixGetSet() {
   for (int a = 0; a < 3; a++) {
     for (int b = 0; b < 3; b++) {
       for (int c = 0; c < 2; c++) {
-        float expected = a*6+b*2+c+1;
+        MMFloat expected = a*6+b*2+c+1;
         if (m.get({a,b,c}) != expected) {
           std::cerr << "Unexpected result in TestDenseMMatrixGetSet" << std::endl;
           std::exit(0);
@@ -190,11 +190,11 @@ void TestIdentityMultiplication() {
         for (int i3 = 0; i3 < 7; i3++) {
           for (int i4 = 0; i4 < 3; i4++) {
             for (int i5 = 0; i5 < 5; i5++) {
-              float expected = 0;
+              MMFloat expected = 0;
               if (i0 == i3 && i1 == i4 && i2 == i5) {
                 expected = 1;
               }
-              float actual = ident->get({i0, i1, i2, i3, i4, i5});
+              MMFloat actual = ident->get({i0, i1, i2, i3, i4, i5});
               if (actual != expected) {
                 std::cout << "Index: ";
                 for(int i : vector<int>{i0, i1, i2, i3, i4, i5}) {
@@ -332,7 +332,7 @@ void TestAddTo() {
 void TestElementwise() {
   std::cout << "TestElementwise..." << std::endl;
 
-  std::function<float(float)> f = [](float x) { return x*2; };
+  std::function<MMFloat(MMFloat)> f = [](MMFloat x) { return x*2; };
 
   SparseMMatrix m({2,1});
   m.set({0,0}, 1);
@@ -355,7 +355,7 @@ void TestElementwise() {
 void TestTranspose() {
   std::cout << "TestTranspose..." << std::endl;
 
-  std::function<float(float)> f = [](float x) { return x*2; };
+  std::function<MMFloat(MMFloat)> f = [](MMFloat x) { return x*2; };
 
   SparseMMatrix m({5,4,3,2});
   m.set({3,2,1,0}, 1);
@@ -375,6 +375,30 @@ void TestTranspose() {
   }
 }
 
+void CheckEq(const std::vector<int>& out, const std::vector<int>& exp) {
+  if (out.size() != exp.size()) {
+    std::cerr << "Wrong size." << std::endl;
+    std::exit(1);
+  }
[…]

### 2020-07-13 Math/book.tex
Updated math.

@@
 \usepackage[toc,page]{appendix}
+% package used for \llparenthesis
+\usepackage{stmaryrd}
 
@@
 Let $\vec{v}$ be the vector which describes the shape of
-$M$, then $\vec{v} = |M|$. And for any other $\bar{v} \in \mathbb{N}^n$, $\bar{v}$
+$M$, then $\vec{v} = \shape{M}$. And for any other $\bar{v} \in \mathbb{N}^n$, $\bar{v}$
 is a valid index of $M$ if and only if each value of $\bar{v}$ is less than or equal
@@
 We'll use the notation $M[\bar{v}]$ to reference any individual scalar value of $M$
-at indicies $\bar{v} \in \Dim(|M|)$. 
+at indicies $\bar{v} \in \Dim(\shape{M})$. 
 \end{definition}
@@
 means that,
-\[ |M| = \left<5,7,9,2,3\right> \]
-Let's name this shape vector, $|M| = \vec{m}$. Notice that this is
-a 5 dimensional multimatrix because $|\vec{m}| = 5$. Also note the
-subtle difference in $||M||$ which is 5 and $|M|$ which is $\vec{m}$.
+\[ \shape{M} = \left<5,7,9,2,3\right> \]
+Let's name this shape vector, $\shape{M} = \vec{m}$. Notice that this is
+a 5 dimensional multimatrix because $\shape{\vec{m}} = 5$. Also note the
+subtle difference in $\shape{\shape{M}}$ which is 5 and $\shape{M}$ which is $\vec{m}$.
 
@@
 $\mathbb{R}^{\vec{f} \oplus \vec{x}}$. That is,
-\[ |F(X)| = \vec{f} \]
-\[ |X| = \vec{x} \]
-\[ \left|\frac{dF}{dX}\right| = \vec{f} \oplus \vec{x} \]
+\[ \shape{F(X)} = \vec{f} \]
+\[ \shape{X} = \vec{x} \]
+\[ \shape{\frac{dF}{dX}} = \vec{f} \oplus \vec{x} \]
 \[
@@
 f(X) &\in \mathbb{R} \\
-|X| &= \vec{x} \\
-\left|\frac{df}{dX}\right| &= \vec{x}
+\shape{X} &= \vec{x} \\
+\shape{\frac{df}{dX}} &= \vec{x}
 \end{align*}
@@
 \begin{align*}
-|F(x)| &= \vec{f} \\
+\shape{F(x)} &= \vec{f} \\
 x &\in \mathbb{R} \\
-\left|\frac{dF}{dx}\right| &= \vec{f}
+\shape{\frac{dF}{dx}} &= \vec{f}
 \end{align*}
@@
 just multimatricies with 2 dimensions. Then we can say that the total derivative
-of $B$ with respect to $X$ is a multimatrix with shape $|B| \oplus |X|$,
+of $B$ with respect to $X$ is a multimatrix with shape $\shape{B} \oplus \shape{X}$,
 whose elements we can define as,
-\[\forall \bar{b} \in \Dim(|B|), \bar{x} \in \Dim(|X|):\]
+\[\forall \bar{b} \in \Dim(\shape{B}), \bar{x} \in \Dim(\shape{X}):\]
 \begin{align*}
@@
 \[
-\frac{dB}{dX} = \Ident^3(|X|) \mmult{||X||} \cos(X)
+\frac{dB}{dX} = \Ident^3(\shape{X}) \mmult{\shape{\shape{X}}} \cos(X)
 \]
@@
 But that single line will require defining multimatrix multiplication and
-a mysterious, and possibly dangerious, entity call a cubic identity, $\Ident^3(|X|)$.
+a mysterious, and possibly dangerious, entity call a cubic identity, $\Ident^3(\shape{X})$.
 
@@
 Let $F(X)$ be a function from $\mathbb{R}^{\left<3,7,2\right>}$ to
-$\mathbb{R}^{\left<6, 7\right>}$. That is, $|F(X)| = \left<6,7\right>$
-and for any valid input to $F(X)$, $|X| = \left<3,7,2\right>$.
+$\mathbb{R}^{\left<6, 7\right>}$. That is, $\shape{F(X)} = \left<6,7\right>$
+and for any valid input to $F(X)$, $\shape{X} = \left<3,7,2\right>$.
 Then what is the shape of $dF/dX$?
@@
 \[ f(X) = \sum_{\forall \bar{x} \in \Dim(\left<2,3,2\right>)} X[\bar{x}] \]
-What is the shape of $df/dX$? If $\bar{v} \in \Dim(|df/dX|)$ then what is
+What is the shape of $df/dX$? If $\bar{v} \in \Dim(\shape{df/dX})$ then what is
 \[ \frac{df}{dX}[\bar{v}] = ? \]
@@
 for $A \times B = C$ if $A$ has the same number of columns as $B$ has rows.
-That is, if $|A| = \left< r_a, c_a \right>$ and $|B| = \left< r_b, c_b \right>$
+That is, if $\shape{A} = \left< r_a, c_a \right>$ and $\shape{B} = \left< r_b, c_b \right>$
 then $A \times B$ is valid if and only if $c_a = r_b$. And furthermore,
 the remaining dimensions of $A$ and $B$ define the diminsions of $C$,
-$|C| = \left< r_a, c_b \right>$. Each element of $C$ is a sum of the product of
+$\shape{C} = \left< r_a, c_b \right>$. Each element of $C$ is a sum of the product of
 every combination of the corresponding row of $A$ and the corresponding column of
@@
 
-Let $|A| = \left<5,7,7\right>$ and $|B| = \left<7,7,2,4\right>$.
-First of all, can we even multiply the two together? Hm... maybe? $|A|$ ends with
-$\left<\ldots, 7\right>$ and $|B|$ starts with $\left<7,\ldots\right>$ so it would
+Let $\shape{A} = \left<5,7,7\right>$ and $\shape{B} = \left<7,7,2,4\right>$.
+First of all, can we even multiply the two together? Hm... maybe? $\shape{A}$ ends with
+$\left<\ldots, 7\right>$ and $\shape{B}$ starts with $\left<7,\ldots\right>$ so it would
 make sense that we can somehow squish them together into something. By that reasoning,
 the shape of our after-multiplication output would use the remaining dimensions
-$\left<5, 7, 7, 2, 4\right> = |A \times B|$.
-
-But $|A|$ also ends with $\left<\ldots, 7, 7\right>$ and $|B|$ starts with
+$\left<5, 7, 7, 2, 4\right> = \shape{A \times B}$.
+
+But $\shape{A}$ also ends with $\left<\ldots, 7, 7\right>$ and $\shape{B}$ starts with
 $\left<7, 7\ldots\right>$ so maybe our multiplication operation should work on that
-additional dimension, leaving us with $\left<5, 2, 4\right> = |A \times B|$.
+additional dimension, leaving us with $\left<5, 2, 4\right> = \shape{A \times B}$.
 But the first definition looks like it could still be useful! It could let us cover 
@@
 an infinite number of types of multiplication, with a new operator, $\mmult{n}$ where
-$|A \mmult{1} B| = \left<5, 7, 7, 2, 4\right>$ and 
-$|A \mmult{2} B| = \left<5, 2, 4\right>$.
+$\shape{A \mmult{1} B} = \left<5, 7, 7, 2, 4\right>$ and 
+$\shape{A \mmult{2} B} = \left<5, 2, 4\right>$.
 
@@
 \label{mm_mult}
-Let $A$ and $B$ be multimatricies such that $|A| = \vec{a} \oplus \vec{c}$,
-$|B| = \vec{c} \oplus \vec{b}$, and $|\vec{c}| = n$ with
+Let $A$ and $B$ be multimatricies such that $\shape{A} = \vec{a} \oplus \vec{c}$,
+$\shape{B} = \vec{c} \oplus \vec{b}$, and $\shape{\vec{c}} = n$ with
 $n \in \{0\} \cup \mathbb{N}$. We shall call $n$ the 'size' or the 'width'
 or the 'overlap' of the multiplication operation.
-The shape of the result is defined, $|A \mmult{n} B| = \vec{a} \oplus \vec{b}$
+The shape of the result is defined, $\shape{A \mmult{n} B} = \vec{a} \oplus \vec{b}$
 and the value of the result is defined,
@@
 \begin{example}
-Let $|A| = \left<2, 3, 2\right>$ and $|B| = \left<3, 2, 2\right>$. I would
+Let $\shape{A} = \left<2, 3, 2\right>$ and $\shape{B} = \left<3, 2, 2\right>$. I would
 define their values in a three dimensional grid but I fear that my three dimensional
@@
 
-Given $|A|$ and $|B|$, and by our definition of multimatrix multiplication,
-you can see that $|A \mmult{2} B| = \left<2, 2\right>$. And the values of the
+Given $\shape{A}$ and $\shape{B}$, and by our definition of multimatrix multiplication,
+you can see that $\shape{A \mmult{2} B} = \left<2, 2\right>$. And the values of the
 resulting multimatrix are defined:
@@
 if $A$ and $B$ are two dimensional multimatricies with shapes
-$|A| = \left<l_a, r_a\right>$ and $|B| = \left<l_b, r_b\right>$
+$\shape{A} = \left<l_a, r_a\right>$ and $\shape{B} = \left<l_b, r_b\right>$
 their product $A \mmult{1} B$ is valid if and only if $r_a = l_b$ and
-the result is of shape $|A \mmult{1} B| = \left<l_a, r_b\right>$.
+the result is of shape $\shape{A \mmult{1} B} = \left<l_a, r_b\right>$.
 And of course, the value at each index
-$\left<l_c, r_c\right> \in \Dim(|A \mmult{1} B|)$ is,
+$\left<l_c, r_c\right> \in \Dim(\shape{A \mmult{1} B})$ is,
 \[
@@
 around parentheses. Take for example multimatricies $A$, $B$, and $C$ such that,
-$|A| = \left<5,3,2\right>$,
-$|B| = \left<2,7\right>$, and
-$|C| = \left<3,7,2\right>$ where you should be able to see that
+$\shape{A} = \left<5,3,2\right>$,
+$\shape{B} = \left<2,7\right>$, and
+$\shape{C} = \left<3,7,2\right>$ where you should be able to see that
 $(A \mmult{1} B) \mmult{2} C$ is a valid operation since
-$|A \mmult{1} B| = \left<5,3,7\right>$ and
-$|(A \mmult{1} B) \mmult{2} C| = \left<5,2\right>$. But
+$\shape{A \mmult{1} B} = \left<5,3,7\right>$ and
+$\shape{(A \mmult{1} B) \mmult{2} C} = \left<5,2\right>$. But
 $A \mmult{1} (B \mmult{2} C)$ isn't a valid set of operations since even
@@
 Take, for example, multimatricies $A$, $B$, and $C$ such
-that $|A| = \left<2,2,2,2\right>$, $|B| = \left<2,2,2\right>$, and
-$|C| = \left<2,2,2,2\right>$. Let,
+that $\shape{A} = \left<2,2,2,2\right>$, $\shape{B} = \left<2,2,2\right>$, and
+$\shape{C} = \left<2,2,2,2\right>$. Let,
 \[
@@
 If both operations $(A \mmult{m} B) \mmult{n} C$ and $A \mmult{m} (B \mmult{n} C)$
-are valid dimensionally and $m+n \le ||B||$, then,
+are valid dimensionally and $m+n \le \shape{\shape{B}}$, then,
 \[ (A \mmult{m} B) \mmult{n} C = A \mmult{m} (B \mmult{n} C) \]
@@
 $(A \mmult{m} B) \mmult{n} C$ and $A \mmult{m} (B \mmult{n} C)$ are both valid
-and $m + n \le ||B||$.
+and $m + n \le \shape{\shape{B}}$.
 Then the following must be true by the definiton of multimatrix multiplication
@@
 $\vec{b_1}$ such that 
-$|\vec{m}| = m$,
-$|A| = \vec{a} \oplus \vec{m}$,
+$\shape{\vec{m}} = m$,
+$\shape{A} = \vec{a} \oplus \vec{m}$,
 and
-$|B| = \vec{m} \oplus \vec{b_1}$
+$\shape{B} = \vec{m} \oplus \vec{b_1}$
 
@@
 $\vec{c}$ such that
-$|\vec{n}| = n$,
-$|B| = \vec{b_2} \oplus \vec{n}$
+$\shape{\vec{n}} = n$,
+$\shape{B} = \vec{b_2} \oplus \vec{n}$
 and
-$|C| = \vec{n} \oplus \vec{c}$
-
-Since $|B| = \vec{m} \oplus \vec{b_1} = \vec{b_2} \oplus \vec{n}$ and
-$||B|| \ge |\vec{m}| + |\vec{n}|$, it must follow that, there is some vector $\vec{b}$
+$\shape{C} = \vec{n} \oplus \vec{c}$
+
+Since $\shape{B} = \vec{m} \oplus \vec{b_1} = \vec{b_2} \oplus \vec{n}$ and
+$\shape{\shape{B}} \ge \shape{\vec{m}} + \shape{\vec{n}}$, it must follow that, there is some vector $\vec{b}$
 such that,
 \[
- |B| = \vec{m} \oplus \vec{b} \oplus \vec{n}
+ \shape{B} = \vec{m} \oplus \vec{b} \oplus \vec{n}
 \]
 Even if $\vec{b}$ is an empty vector. Then,
-\[ |A \mmult{m} B| = \vec{a} \oplus \vec{b} \oplus \vec{n} \]
-\[ |(A \mmult{m} B) \mmult{n} C| = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
-\[ |B \mmult{n} C| = \vec{m} \oplus \vec{b} \oplus \vec{c} \]
-\[ |A \mmult{m} (B \mmult{n} C)| = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
+\[ \shape{A \mmult{m} B} = \vec{a} \oplus \vec{b} \oplus \vec{n} \]
+\[ \shape{(A \mmult{m} B) \mmult{n} C} = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
+\[ \shape{B \mmult{n} C} = \vec{m} \oplus \vec{b} \oplus \vec{c} \]
+\[ \shape{A \mmult{m} (B \mmult{n} C)} = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
 So,
-\[ |(A \mmult{m} B) \mmult{n} C| = |A \mmult{m} (B \mmult{n} C)| \]
+\[ \shape{(A \mmult{m} B) \mmult{n} C} = \shape{A \mmult{m} (B \mmult{n} C)} \]
 Which is necessary, but not sufficient, for our proof.
@@
 \begin{theorem}[Communicativity of Multiplication]
-Let $|A| = \vec{x}$ and $|B| = \vec{x}$. Then,
-\[ A \mmult{|\vec{x}|} B = B \mmult{|\vec{x}|} A \]
-\end{theorem}
-\begin{proof}
-Let $A$, $B$, and $\vec{x}$ be as described above. Notice that then $|A \mmult{|\vec{x}|} B|$
+Let $\shape{A} = \vec{x}$ and $\shape{B} = \vec{x}$. Then,
+\[ A \mmult{\shape{\vec{x}}} B = B \mmult{\shape{\vec{x}}} A \]
+\end{theorem}
+\begin{proof}
+Let $A$, $B$, and $\vec{x}$ be as described above. Notice that then $\shape{A \mmult{\shape{\vec{x}}} B}$
 results in a zero dimensional multimatrix - a multimatrix with one element which is effectively
@@
 \begin{align*}
-(A \mmult{|\vec{x}|} B)[\{\}]
+(A \mmult{\shape{\vec{x}}} B)[\{\}]
   &= \sum_{\forall \bar{x} \in \Dim(\vec{x})} A[\bar{x}]B[\bar{x}] \\
   &= \sum_{\forall \bar{x} \in \Dim(\vec{x})} B[\bar{x}]A[\bar{x}] \\
-  &= (B \mmult{|\vec{x}|} A)[\{\}]
+  &= (B \mmult{\shape{\vec{x}}} A)[\{\}]
 \end{align*}
@@
 $\vec{v}$. This $\Ident^n(\vec{v})$ is a multimatrix with shape,
-\[ |\Ident^n(\vec{v})| = \bigoplus_{i \in [1, n]} \vec{v} \]
+\[ \shape{\Ident^n(\vec{v})} = \bigoplus_{i \in [1, n]} \vec{v} \]
 That is, it's shape is $n$ successive concatinations of $\vec{v}$.
@@
 \[
- A \mmult{|\vec{m}|} \Ident^2(\vec{m}) = A
+ A \mmult{\shape{\vec{m}}} \Ident^2(\vec{m}) = A
 \]
@@
 \[
- \Ident^2(\vec{n}) \mmult{|\vec{n}|} A = A
+ \Ident^2(\vec{n}) \mmult{\shape{\vec{n}}} A = A
 \]
@@
 \begin{ppart}
-Let $A$ be a matrix with shape $|A| = \vec{a} \oplus \vec{m}$.
+Let $A$ be a matrix with shape $\shape{A} = \vec{a} \oplus \vec{m}$.
 Then by the definition of multimatrix multiplication (Def. \ref{mm_mult}),
@@
 \[
- (A \mmult{|\vec{m}|} \Ident^2(\vec{m}))[\bar{a} \oplus \bar{m_1}]
+ (A \mmult{\shape{\vec{m}}} \Ident^2(\vec{m}))[\bar{a} \oplus \bar{m_1}]
  =
@@
 \begin{align*}
- (A \mmult{|\vec{m}|} \Ident^2(\vec{m}))[\bar{a} \oplus \bar{m_1}]
+ (A \mmult{\shape{\vec{m}}} \Ident^2(\vec{m}))[\bar{a} \oplus \bar{m_1}]
  &=
@@
 \end{align*}
-Therefore $A \mmult{|\vec{m}|} \Ident^2(\vec{m}) = A$
+Therefore $A \mmult{\shape{\vec{m}}} \Ident^2(\vec{m}) = A$
 \end{ppart}
 \begin{ppart}
-Let $A$ be a matrix with shape $|A| = \vec{n} \oplus \vec{a}$.
+Let $A$ be a matrix with shape $\shape{A} = \vec{n} \oplus \vec{a}$.
 Then by the definition of multimatrix multiplication (Def. \ref{mm_mult}),
@@
 \[
- (\Ident^2(\vec{n}) \mmult{|\vec{n}|} A)[\bar{n_1} \oplus \bar{a}]
+ (\Ident^2(\vec{n}) \mmult{\shape{\vec{n}}} A)[\bar{n_1} \oplus \bar{a}]
  =
@@
 \begin{align*}
- (\Ident^2(\vec{n}) \mmult{|\vec{n}|} A)[\bar{n_1} \oplus \bar{a}]
+ (\Ident^2(\vec{n}) \mmult{\shape{\vec{n}}} A)[\bar{n_1} \oplus \bar{a}]
  &=
@@
 \end{align*}
-Therefore $\Ident^2(\vec{n}) \mmult{|\vec{n}|} A = A$
+Therefore $\Ident^2(\vec{n}) \mmult{\shape{\vec{n}}} A = A$
 \end{ppart}
@@
 
-\[A \mmult{|\vec{x}|} X = A \]
+\[A \mmult{\shape{\vec{x}}} X = A \]
 
@@
 
-\[X \mmult{|\vec{x}|} B = B \]
+\[X \mmult{\shape{\vec{x}}} B = B \]
 
@@
 \begin{ppart}
-If for all multimatrixes, $A$, on which $A \mmult{|\vec{x}|} X$ is defined, 
-$A \mmult{|\vec{x}|} X = A$ this implies that, in the case of $A = \Ident^2(\vec{x})$,
-
-\begin{align*}
-  A \mmult{|\vec{x}|} X &= A \\
- \Ident^2(\vec{x}) \mmult{|\vec{x}|} X &= \Ident^2(\vec{x}) \\
+If for all multimatrixes, $A$, on which $A \mmult{\shape{\vec{x}}} X$ is defined, 
+$A \mmult{\shape{\vec{x}}} X = A$ this implies that, in the case of $A = \Ident^2(\vec{x})$,
+
+\begin{align*}
+  A \mmult{\shape{\vec{x}}} X &= A \\
+ \Ident^2(\vec{x}) \mmult{\shape{\vec{x}}} X &= \Ident^2(\vec{x}) \\
   X &= \Ident^2(\vec{x}) 
@@
 \begin{ppart}
-If for all multimatrixes, $B$, on which $X \mmult{|\vec{x}|} B$ is defined, 
-$X \mmult{|\vec{x}|} B = B$ this implies that, in the case of $B = \Ident^2(\vec{x})$,
-
-\begin{align*}
-  X \mmult{|\vec{x}|} B &= B \\
-  X \mmult{|\vec{x}|} \Ident^2(\vec{x}) &= \Ident^2(\vec{x}) \\
+If for all multimatrixes, $B$, on which $X \mmult{\shape{\vec{x}}} B$ is defined, 
+$X \mmult{\shape{\vec{x}}} B = B$ this implies that, in the case of $B = \Ident^2(\vec{x})$,
+
+\begin{align*}
+  X \mmult{\shape{\vec{x}}} B &= B \\
+  X \mmult{\shape{\vec{x}}} \Ident^2(\vec{x}) &= \Ident^2(\vec{x}) \\
   X &= \Ident^2(\vec{x}) 
@@
 Let $X$ be some multimatrix. Then,
-\[ \frac{dX}{dX} = \Ident^2(|X|) \]
-\end{theorem}
-\begin{proof}
-Let $X$ be a multimatrix of shape $|X|=\vec{x}$.
+\[ \frac{dX}{dX} = \Ident^2(\shape{X}) \]
+\end{theorem}
+\begin{proof}
+Let $X$ be a multimatrix of shape $\shape{X}=\vec{x}$.
 By the derivative definition (Def. \ref{mm_derivative}),
@@
 \end{align*}
-Therefore $dX/dX = \Ident^2(|X|)$
+Therefore $dX/dX = \Ident^2(\shape{X})$
 \end{proof}
@@
 Then,
-\[ \frac{dM}{dX} = \Ident^3(|X|) \mmult{||X||} M'(X) \]
+\[ \frac{dM}{dX} = \Ident^3(\shape{X}) \mmult{\shape{\shape{X}}} M'(X) \]
 \end{theorem}
@@
 By the definition of a multimatrix derivative,
-\[ \forall \bar{m} \in \Dim(|M|), \bar{x} \in \Dim(|X|) : \]
+\[ \forall \bar{m} \in \Dim(\shape{M}), \bar{x} \in \Dim(\shape{X}) : \]
 \begin{align*}
@@
 \end{align*}
-Since, by our definition of elementwise function, $|M| = |X|$, we can
+Since, by our definition of elementwise function, $\shape{M} = \shape{X}$, we can
 say that, 
 \begin{align*}
- (\Ident^3(|X|) \mmult{||X||} M'(X))[\bar{m} \oplus \bar{x}]
- &= \sum_{\forall \bar{y} \in \Dim(|X|)}
- \Ident^3(|X|)[\bar{m} \oplus \bar{x} \oplus \bar{y}] M'(X)[\bar{y}] \\
- &= \sum_{\forall \bar{y} \in \Dim(|X|)}
- \Ident^3(|X|)[\bar{m} \oplus \bar{x} \oplus \bar{y}] m'(X[\bar{y}]) \\
+ (\Ident^3(\shape{X}) \mmult{\shape{\shape{X}}} M'(X))[\bar{m} \oplus \bar{x}]
+ &= \sum_{\forall \bar{y} \in \Dim(\shape{X})}
+ \Ident^3(\shape{X})[\bar{m} \oplus \bar{x} \oplus \bar{y}] M'(X)[\bar{y}] \\
+ &= \sum_{\forall \bar{y} \in \Dim(\shape{X})}
+ \Ident^3(\shape{X})[\bar{m} \oplus \bar{x} \oplus \bar{y}] m'(X[\bar{y}]) \\
  &= \sum_{\forall \bar{y} = \bar{m} = \bar{x}}
- \Ident^3(|X|)[\bar{m} \oplus \bar{x} \oplus \bar{y}] m'(X[\bar{y}]) \\
+ \Ident^3(\shape{X})[\bar{m} \oplus \bar{x} \oplus \bar{y}] m'(X[\bar{y}]) \\
  &= \left\{
@@
 \end{align*}
-Therefore $dM/dX = \Ident^3(|X|) \mmult{||X||} M'(X)$
+Therefore $dM/dX = \Ident^3(\shape{X}) \mmult{\shape{\shape{X}}} M'(X)$
 \end{proof}
@@
 where $m > k$ and $n > k$,
-\[ \Ident^m(\vec{x}) \mmult{k|\vec{x}|} \Ident^n(\vec{x}) = \Ident^{m+n-2k}(\vec{x}) \]
+\[ \Ident^m(\vec{x}) \mmult{k\shape{\vec{x}}} \Ident^n(\vec{x}) = \Ident^{m+n-2k}(\vec{x}) \]
 \end{theorem}
@@
 \begin{align*}
-&\left( \Ident^m(\vec{x}) \mmult{k|\vec{x}|} \Ident^n(\vec{x}) \right)
+&\left( \Ident^m(\vec{x}) \mmult{k\shape{\vec{x}}} \Ident^n(\vec{x}) \right)
 [\bar{a_1} \oplus \bar{a_2} \oplus \ldots \bar{b_1} \oplus \bar{b_2} \oplus \ldots] = \\
@@
 \begin{align*}
-\left( \Ident^m(\vec{x}) \mmult{k|\vec{x}|} \Ident^n(\vec{x}) \right)
+\left( \Ident^m(\vec{x}) \mmult{k\shape{\vec{x}}} \Ident^n(\vec{x}) \right)
 [\bar{a_1} \oplus \bar{a_2} \oplus \ldots \bar{b_1} \oplus \bar{b_2} \oplus \ldots] =
@@
 \[
- \left|\left| \Ident^m(\vec{x}) \mmult{k|\vec{x}|} \Ident^n(\vec{x}) \right|\right|
+ \shape{\shape{ \Ident^m(\vec{x}) \mmult{k\shape{\vec{x}}} \Ident^n(\vec{x}) }}
  =
- ||\Ident^m(\vec{x})|| + ||\Ident^n(\vec{x})|| - 2k|\vec{x}|
+ \shape{\shape{\Ident^m(\vec{x})}} + \shape{\shape{\Ident^n(\vec{x})}} - 2k\shape{\vec{x}}
 \]
@@
 
-\[ \Ident^m(\vec{x}) \mmult{k|\vec{x}|} \Ident^n(\vec{x}) = \Ident^{m+n-2k}(\vec{x}) \]
+\[ \Ident^m(\vec{x}) \mmult{k\shape{\vec{x}}} \Ident^n(\vec{x}) = \Ident^{m+n-2k}(\vec{x}) \]
 \end{proof}
@@
 \begin{theorem}[Zero Overlap Multiplication]
-Anyways, if $|A| = \vec{a}$ and $|B| = \vec{b}$, for every $\bar{a} \in \Dim(\vec{a})$
+Anyways, if $\shape{A} = \vec{a}$ and $\shape{B} = \vec{b}$, for every $\bar{a} \in \Dim(\vec{a})$
 and $\bar{b} \in \Dim(\vec{b}):$
@@
 by the tuple,
-\[ \left<m,X\right> \in \{  (\{0\} \cup \mathbb{N}) \times \mathbb{R}^{\vec{m} \oplus \vec{x}}  :  |\vec{m}| = m \} \]
+\[ \left<m,X\right> \in \{  (\{0\} \cup \mathbb{N}) \times \mathbb{R}^{\vec{m} \oplus \vec{x}}  :  \shape{\vec{m}} = m \} \]
 such that,
@@
 by the tuple,
-\[ \left<m,X\right> \in \{  (\{0\} \cup \mathbb{N}) \times \mathbb{R}^{\vec{x} \oplus \vec{m}}  :  |\vec{m}| = m \} \]
+\[ \left<m,X\right> \in \{  (\{0\} \cup \mathbb{N}) \times \mathbb{R}^{\vec{x} \oplus \vec{m}}  :  \shape{\vec{m}} = m \} \]
 such that,
@@
 \begin{theorem}[Relation of Inverse to Identity]
-If $\RMult[n,Y]$ is an inverse of $\RMult[m,X]$ where $|X| = \vec{m} \oplus \vec{x}$ and $|\vec{m}| = m$
+If $\RMult[n,Y]$ is an inverse of $\RMult[m,X]$ where $\shape{X} = \vec{m} \oplus \vec{x}$ and $\shape{\vec{m}} = m$
 then $X \mmult{n} Y = \Ident^2(\vec{m})$.
-And if $\LMult[n,Y]$ is an inverse of $\LMult[m,X]$ where $|X| = \vec{x} \oplus \vec{m}$ and $|\vec{m}| = m$
+And if $\LMult[n,Y]$ is an inverse of $\LMult[m,X]$ where $\shape{X} = \vec{x} \oplus \vec{m}$ and $\shape{\vec{m}} = m$
 then $Y \mmult{n} X = \Ident^2(\vec{m})$.
@@
 \begin{ppart}
-Let $X$ be a multimatrix such that $|X| = \vec{m} \oplus \vec{x}$ and $|\vec{m}| = m$.
+Let $X$ be a multimatrix such that $\shape{X} = \vec{m} \oplus \vec{x}$ and $\shape{\vec{m}} = m$.
 If $\RMult[n,Y]$ is the inverse of $\RMult[m,X]$ then, for all $M$,
@@
 \begin{ppart}
-Let $X$ be a multimatrix such that $|X| = \vec{x} \oplus \vec{m}$ and $|\vec{m}| = m$.
+Let $X$ be a multimatrix such that $\shape{X} = \vec{x} \oplus \vec{m}$ and $\shape{\vec{m}} = m$.
 If $\LMult[n,Y]$ is the inverse of $\LMult[m,X]$ then, for all $M$,
@@
 \begin{theorem}[Shape of Inverses]
-If $\RMult[n,Y]$ is an inverse of $\RMult[m,X]$ where $|X| = \vec{m} \oplus \vec{x}$ and
-$|\vec{m}| = m$ then $n \le ||X||-m$.
-
-Also, if $\LMult[n,Y]$ is an inverse of $\LMult[m,X]$ where $|X| = \vec{x} \oplus \vec{m}$ and
-$|\vec{m}| = m$ then $n \le ||X||-m$.
+If $\RMult[n,Y]$ is an inverse of $\RMult[m,X]$ where $\shape{X} = \vec{m} \oplus \vec{x}$ and
+$\shape{\vec{m}} = m$ then $n \le \shape{\shape{X}}-m$.
+
+Also, if $\LMult[n,Y]$ is an inverse of $\LMult[m,X]$ where $\shape{X} = \vec{x} \oplus \vec{m}$ and
+$\shape{\vec{m}} = m$ then $n \le \shape{\shape{X}}-m$.
 \end{theorem}
@@
 \begin{ppart}
-Let $\RMult[n,Y]$ be an inverse of $\RMult[m,X]$ where $|X| = \vec{m} \oplus \vec{x}$ and
-$|\vec{m}| = m$.
+Let $\RMult[n,Y]$ be an inverse of $\RMult[m,X]$ where $\shape{X} = \vec{m} \oplus \vec{x}$ and
+$\shape{\vec{m}} = m$.
 Let $M$ be some valid input of $\RMult[m,X]$.
-In other words, $|M| = \vec{l} \oplus \vec{m}$ for some $\vec{l}$.
-So $|M \mmult{m} X| = \vec{l} \oplus \vec{x}$.
-Since $\RMult[n,Y]$ is a valid operation on $M \mmult{m} X$, $n \le |\vec{l} \oplus \vec{x}|$.
-And since there is no restriction on $\vec{l}$ it's only useful to say that $n \le |\vec{x}|$.
-Given that $||X|| = |\vec{x}| + m$ it follows that $n \le ||X|| - m$.
+In other words, $\shape{M} = \vec{l} \oplus \vec{m}$ for some $\vec{l}$.
+So $\shape{M \mmult{m} X} = \vec{l} \oplus \vec{x}$.
+Since $\RMult[n,Y]$ is a valid operation on $M \mmult{m} X$, $n \le \shape{\vec{l} \oplus \vec{x}}$.
+And since there is no restriction on $\vec{l}$ it's only useful to say that $n \le \shape{\vec{x}}$.
+Given that $\shape{\shape{X}} = \shape{\vec{x}} + m$ it follows that $n \le \shape{\shape{X}} - m$.
 \end{ppart}
 \begin{ppart}
-Let $\LMult[n,Y]$ be an inverse of $\LMult[m,X]$ where $|X| = \vec{x} \oplus \vec{m}$ and
-$|\vec{m}| = m$.
+Let $\LMult[n,Y]$ be an inverse of $\LMult[m,X]$ where $\shape{X} = \vec{x} \oplus \vec{m}$ and
+$\shape{\vec{m}} = m$.
 Let $M$ be some valid input of $\LMult[m,X]$.
-In other words, $|M| = \vec{m} \oplus \vec{r}$ for some $\vec{r}$.
-So $|X \mmult{m} M| = \vec{x} \oplus \vec{r}$.
-Since $\RMult[n,Y]$ is a valid operation on $X \mmult{m} M$, $n \le |\vec{x} \oplus \vec{r}|$.
-And since there is no restriction on $\vec{r}$ it's only useful to say that $n \le |\vec{x}|$.
-Given that $||X|| = |\vec{x}| + m$ it follows that $n \le ||X|| - m$.
+In other words, $\shape{M} = \vec{m} \oplus \vec{r}$ for some $\vec{r}$.
+So $\shape{X \mmult{m} M} = \vec{x} \oplus \vec{r}$.
+Since $\RMult[n,Y]$ is a valid operation on $X \mmult{m} M$, $n \le \shape{\vec{x} \oplus \vec{r}}$.
+And since there is no restriction on $\vec{r}$ it's only useful to say that $n \le \shape{\vec{x}}$.
+Given that $\shape{\shape{X}} = \shape{\vec{x}} + m$ it follows that $n \le \shape{\shape{X}} - m$.
 \end{ppart}
@@
 \begin{theorem}[Relation of Identity to Inverse]
-If $X \mmult{n} Y = \Ident^2(\vec{m})$, $|\vec{m}| = m$, $|X| = \vec{m} \oplus \vec{x}$,
-and $n \le ||X||-m$, that implies that $\RMult[n, Y]$ is an inverse of $\RMult[m, X]$.
-
-Also,  if $Y \mmult{n} X = \Ident^2(\vec{m})$, $|\vec{m}| = m$, $|X| = \vec{x} \oplus \vec{m}$,
-and $n \le ||X||-m$, that implies that $\LMult[n, Y]$ is an inverse of $\LMult[m, X]$.
+If $X \mmult{n} Y = \Ident^2(\vec{m})$, $\shape{\vec{m}} = m$, $\shape{X} = \vec{m} \oplus \vec{x}$,
+and $n \le \shape{\shape{X}}-m$, that implies that $\RMult[n, Y]$ is an inverse of $\RMult[m, X]$.
+
+Also,  if $Y \mmult{n} X = \Ident^2(\vec{m})$, $\shape{\vec{m}} = m$, $\shape{X} = \vec{x} \oplus \vec{m}$,
+and $n \le \shape{\shape{X}}-m$, that implies that $\LMult[n, Y]$ is an inverse of $\LMult[m, X]$.
 \end{theorem}
@@
 \begin{ppart}
-Let $X \mmult{n} Y = \Ident^2(\vec{m})$, $|\vec{m}| = m$, $|X| = \vec{m} \oplus \vec{x}$, and $n \le ||X||-m$.
-We know that $n \le |\vec{x}|$ since $|\vec{x}| = ||X||-m$.
-Then we can split up $\vec{x}$ into $\vec{x_l} \oplus \vec{x_r}$ where $|\vec{x_r}| = n$.
-So $|Y| = \vec{x_r} \oplus \vec{y}$ for some $\vec{y}$ since $X \mmult{n} Y$ is defined.
-We can then find the shape $|X \mmult{n} Y| = \vec{m} \oplus \vec{x_l} \oplus \vec{y}$.
+Let $X \mmult{n} Y = \Ident^2(\vec{m})$, $\shape{\vec{m}} = m$, $\shape{X} = \vec{m} \oplus \vec{x}$, and $n \le \shape{\shape{X}}-m$.
+We know that $n \le \shape{\vec{x}}$ since $\shape{\vec{x}} = \shape{\shape{X}}-m$.
+Then we can split up $\vec{x}$ into $\vec{x_l} \oplus \vec{x_r}$ where $\shape{\vec{x_r}} = n$.
+So $\shape{Y} = \vec{x_r} \oplus \vec{y}$ for some $\vec{y}$ since $X \mmult{n} Y$ is defined.
+We can then find the shape $\shape{X \mmult{n} Y} = \vec{m} \oplus \vec{x_l} \oplus \vec{y}$.
 Then for any $M$ such that $M \mmult{m} X$ is defined, i.e. any $M$ of shape $\vec{l} \oplus \vec{m}$ for some $\vec{l}$,
 we can tell that $M \mmult{m} (X \mmult{n} Y)$ is also defined.
-And since $n \le ||X||-m$ that implies $n+m \le ||X||$ so $M \mmult{m} (X \mmult{n} Y) = (M \mmult{m} X) \mmult{n} Y$
+And since $n \le \shape{\shape{X}}-m$ that implies $n+m \le \shape{\shape{X}}$ so $M \mmult{m} (X \mmult{n} Y) = (M \mmult{m} X) \mmult{n} Y$
 by Theorem \ref{mm_associativity}.
@@
 \begin{ppart}
-Let $Y \mmult{n} X = \Ident^2(\vec{m})$, $|\vec{m}| = m$, $|X| = \vec{x} \oplus \vec{m}$, and $n \le ||X||-m$.
-We know that $n \le |\vec{x}|$ since $|\vec{x}| = ||X||-m$.
-Then we can split up $\vec{x}$ into $\vec{x_l} \oplus \vec{x_r}$ where $|\vec{x_l}| = n$.
-So $|Y| = \vec{y} \oplus \vec{x_l}$ for some $\vec{y}$ since $Y \mmult{n} X$ is defined.
-We can then find the shape $|Y \mmult{n} X| = \vec{y} \oplus \vec{x_r} \oplus \vec{m}$.
+Let $Y \mmult{n} X = \Ident^2(\vec{m})$, $\shape{\vec{m}} = m$, $\shape{X} = \vec{x} \oplus \vec{m}$, and $n \le \shape{\shape{X}}-m$.
+We know that $n \le \shape{\vec{x}}$ since $\shape{\vec{x}} = \shape{\shape{X}}-m$.
+Then we can split up $\vec{x}$ into $\vec{x_l} \oplus \vec{x_r}$ where $\shape{\vec{x_l}} = n$.
+So $\shape{Y} = \vec{y} \oplus \vec{x_l}$ for some $\vec{y}$ since $Y \mmult{n} X$ is defined.
+We can then find the shape $\shape{Y \mmult{n} X} = \vec{y} \oplus \vec{x_r} \oplus \vec{m}$.
 Then for any $M$ such that $X \mmult{m} M$ is defined, i.e. any $M$ of shape $\vec{m} \oplus \vec{r}$ for some $\vec{r}$,
 we can tell that $(Y \mmult{n} X) \mmult{m} M$ is also defined.
-And since $n \le ||X||-m$ that implies $n+m \le ||X||$ so $(Y \mmult{n} X) \mmult{m} M = Y \mmult{n} (X \mmult{m} M)$
+And since $n \le \shape{\shape{X}}-m$ that implies $n+m \le \shape{\shape{X}}$ so $(Y \mmult{n} X) \mmult{m} M = Y \mmult{n} (X \mmult{m} M)$
 by Theorem \ref{mm_associativity}.
@@
 \[
-  \Idx[\vec{x}](\bar{x}) = \sum_{1 \le i \le |\vec{x}|} \left( (\bar{x}[i]-1) \prod_{1 \le j < i} \vec{x}[j] \right)
+  \Idx[\vec{x}](\bar{x}) = \sum_{1 \le i \le \shape{\vec{x}}} \left( (\bar{x}[i]-1) \prod_{1 \le j < i} \vec{x}[j] \right)
 \]
 And then inverse function takes an integer and returns a vector in $\Dim(\vec{x})$:
-\[ |\Idx[\vec{x}]^{-1}(n)| = |\vec{x}| \]
+\[ \shape{\Idx[\vec{x}]^{-1}(n)} = \shape{\vec{x}} \]
 \[
@@
     \frac{\remainder\left(
-      \sum_{1 \le i \le |\vec{x}|} \left( (\bar{x}[i]-1) \prod_{1 \le j < i} \vec{x}[j] \right) 
+      \sum_{1 \le i \le \shape{\vec{x}}} \left( (\bar{x}[i]-1) \prod_{1 \le j < i} \vec{x}[j] \right) 
       , \prod_{1 \le m \le k} \vec{x}[m]\right)}
@@
 and $\bar{b} \in \Dim(\vec{b})$:
-\[ \Idx[\vec{a} \oplus \vec{b}](\bar{a} \oplus \bar{b}) = \Idx[\vec{a}](\bar{a}) + |\Dim(\vec{a})| \Idx[\vec{b}](\bar{b}) \]
+\[ \Idx[\vec{a} \oplus \vec{b}](\bar{a} \oplus \bar{b}) = \Idx[\vec{a}](\bar{a}) + \shape{\Dim(\vec{a})} \Idx[\vec{b}](\bar{b}) \]
 \end{theorem}
@@
   &= 
-  \sum_{1 \le i \le |\vec{a} \oplus \vec{b}|} \left( ((\bar{a} \oplus \bar{b})[i]-1) \prod_{1 \le j < i} (\vec{a} \oplus \vec{b})[j] \right) \\
-  &= 
-  \left( \sum_{1 \le i \le |\vec{a}|} \left( ((\bar{a} \oplus \bar{b})[i]-1) \prod_{1 \le j < i} (\vec{a} \oplus \vec{b})[j] \right) \right) +
-  \left( \sum_{|\vec{a}|+1 \le i \le |\vec{a}|+|\vec{b}|} \left( ((\bar{a} \oplus \bar{b})[i]-1) \prod_{1 \le j < i} (\vec{a} \oplus \vec{b})[j] \right) \right)\\
-  &= 
-  \left( \sum_{1 \le i \le |\vec{a}|} \left( (\bar{a}[i]-1) \prod_{1 \le j < i} \vec{a}[j] \right) \right) +
-  \left( \sum_{|\vec{a}|+1 \le i \le |\vec{a}|+|\vec{b}|} \left( (\bar{b}[i-|\vec{a}|]-1) \prod_{1 \le j \le |\vec{a}|} \vec{a}[j] \prod_{1 \le j < i-|\vec{a}|} \vec{b}[j] \right) \right)\\
-  &= 
-  \left( \sum_{1 \le i \le |\vec{a}|} \left( (\bar{a}[i]-1) \prod_{1 \le j < i} \vec{a}[j] \right) \right) +
-  \left( \sum_{1 \le i \le |\vec{b}|} \left( (\bar{b}[i|]-1) |\Dim(\vec{a})| \prod_{1 \le j < i|} \vec{b}[j] \right) \right)\\
+  \sum_{1 \le i \le \shape{\vec{a} \oplus \vec{b}}} \left( ((\bar{a} \oplus \bar{b})[i]-1) \prod_{1 \le j < i} (\vec{a} \oplus \vec{b})[j] \right) \\
+  &= 
+  \left( \sum_{1 \le i \le \shape{\vec{a}}} \left( ((\bar{a} \oplus \bar{b})[i]-1) \prod_{1 \le j < i} (\vec{a} \oplus \vec{b})[j] \right) \right) +
+  \left( \sum_{\shape{\vec{a}}+1 \le i \le \shape{\vec{a}}+\shape{\vec{b}}} \left( ((\bar{a} \oplus \bar{b})[i]-1) \prod_{1 \le j < i} (\vec{a} \oplus \vec{b})[j] \right) \right)\\
+  &= 
+  \left( \sum_{1 \le i \le \shape{\vec{a}}} \left( (\bar{a}[i]-1) \prod_{1 \le j < i} \vec{a}[j] \right) \right) +
+  \left( \sum_{\shape{\vec{a}}+1 \le i \le \shape{\vec{a}}+\shape{\vec{b}}} \left( (\bar{b}[i-\shape{\vec{a}}]-1) \prod_{1 \le j \le \shape{\vec{a}}} \vec{a}[j] \prod_{1 \le j < i-\shape{\vec{a}}} \vec{b}[j] \right) \right)\\
+  &= 
+  \left( \sum_{1 \le i \le \shape{\vec{a}}} \left( (\bar{a}[i]-1) \prod_{1 \le j < i} \vec{a}[j] \right) \right) +
+  \left( \sum_{1 \le i \le \shape{\vec{b}}} \left( (\bar{b}[i]-1) \shape{\Dim(\vec{a})} \prod_{1 \le j < i} \vec{b}[j] \right) \right)\\
   &= 
   \Idx[\vec{a}](\bar{a}) +
-  |\Dim(\vec{a})| \sum_{1 \le i \le |\vec{b}|} \left( (\bar{b}[i|]-1) \prod_{1 \le j < i|} \vec{b}[j] \right)\\
+  \shape{\Dim(\vec{a})} \sum_{1 \le i \le \shape{\vec{b}}} \left( (\bar{b}[i]-1) \prod_{1 \le j < i} \vec{b}[j] \right)\\
   &= 
   \Idx[\vec{a}](\bar{a}) +
-  |\Dim(\vec{a})| \Idx[\vec{b}](\bar{b})
+  \shape{\Dim(\vec{a})} \Idx[\vec{b}](\bar{b})
 \end{align*}
@@
 \begin{theorem}[Reshaping Multimatrix Multiplication]
-Let $A$ and $B$ be two multimatricies of shapes $|A| = \vec{a} \oplus \vec{c}$ and
-$|B| = \vec{c} \oplus \vec{b}$, and let $C$ be the multimatrix resulting in the $|\vec{c}|$
+Let $A$ and $B$ be two multimatricies of shapes $\shape{A} = \vec{a} \oplus \vec{c}$ and
+$\shape{B} = \vec{c} \oplus \vec{b}$, and let $C$ be the multimatrix resulting in the $\shape{\vec{c}}$
 width multiplication of $A$ and $B$, that is,
-\[ A \mmult{|\vec{c}|} B = C \]
+\[ A \mmult{\shape{\vec{c}}} B = C \]
 Now, let $\vec{x}$, $\vec{y}$, and $\vec{z}$ be any vectors such that
-$|\Dim(\vec{a})| = |\Dim(\vec{x})|$,
-$|\Dim(\vec{b})| = |\Dim(\vec{y})|$,
+$\shape{\Dim(\vec{a})} = \shape{\Dim(\vec{x})}$,
+$\shape{\Dim(\vec{b})} = \shape{\Dim(\vec{y})}$,
 and 
-$|\Dim(\vec{c})| = |\Dim(\vec{z})|$.
+$\shape{\Dim(\vec{c})} = \shape{\Dim(\vec{z})}$.
 Then for multimatricies $X$, $Y$, and $Z$ defined such that,
@@
 
-\[ X \mmult{|\vec{z}|} Y = Z \]
-\end{theorem}
-\begin{proof}
-Let $A$ and $B$ be two multimatricies of shapes $|A| = \vec{a} \oplus \vec{c}$ and
-$|B| = \vec{c} \oplus \vec{b}$, and let $C$ be the multimatrix resulting from,
-\[ A \mmult{|\vec{c}|} B = C \]
+\[ X \mmult{\shape{\vec{z}}} Y = Z \]
+\end{theorem}
+\begin{proof}
+Let $A$ and $B$ be two multimatricies of shapes $\shape{A} = \vec{a} \oplus \vec{c}$ and
+$\shape{B} = \vec{c} \oplus \vec{b}$, and let $C$ be the multimatrix resulting from,
+\[ A \mmult{\shape{\vec{c}}} B = C \]
 
 Now, let $\vec{x}$, $\vec{y}$, and $\vec{z}$ be any vectors such that
-$|\Dim(\vec{a})| = |\Dim(\vec{x})|$,
-$|\Dim(\vec{b})| = |\Dim(\vec{y})|$,
+$\shape{\Dim(\vec{a})} = \shape{\Dim(\vec{x})}$,
+$\shape{\Dim(\vec{b})} = \shape{\Dim(\vec{y})}$,
 and 
-$|\Dim(\vec{c})| = |\Dim(\vec{z})|$.
+$\shape{\Dim(\vec{c})} = \shape{\Dim(\vec{z})}$.
 And let multimatricies $X$, $Y$, and $Z$ be defined such that,
@@
 \begin{align*}
-  (A \mmult{|\vec{c}|} B)[\bar{a} \oplus \bar{b}]
+  (A \mmult{\shape{\vec{c}}} B)[\bar{a} \oplus \bar{b}]
   &= C[\bar{a} \oplus \bar{b}] \\
@@
   &=
-  \sum_{0 \le i_c < |\Dim(\vec{c})|} A[\bar{a} \oplus \Idx[\vec{c}]^{-1}(i_c)] B[\Idx[\vec{c}]^{-1}(i_c) \oplus \bar{b}]
+  \sum_{0 \le i_c < \shape{\Dim(\vec{c})}} A[\bar{a} \oplus \Idx[\vec{c}]^{-1}(i_c)] B[\Idx[\vec{c}]^{-1}(i_c) \oplus \bar{b}]
 \end{align*}
@@
 \begin{align*}
-  C[\Idx[\vec{a}  \oplus \vec{b}]^{-1}(i_a + |\Dim(\vec{a})| i_b)]
-  &=
-  \sum_{0 \le i_c < |\Dim(\vec{c})|} A[\Idx[\vec{a}]^{-1}(i_a) \oplus \Idx[\vec{c}]^{-1}(i_c)] B[\Idx[\vec{c}]^{-1}(i_c) \oplus \Idx[\vec{b}]^{-1}(i_b)] \\
-  &=
-  \sum_{0 \le i_c < |\Dim(\vec{c})|} A[\Idx[\vec{a} \oplus \vec{c}]^{-1}(i_a + |\Dim(\vec{a})|i_c)]
-                                     B[\Idx[\vec{c} \oplus \vec{b}]^{-1}(i_c + |\Dim(\vec{c})|i_b)] \\
-  &=
-  \sum_{0 \le i_c < |\Dim(\vec{c})|} X[\Idx[\vec{x} \oplus \vec{z}]^{-1}(i_a + |\Dim(\vec{a})|i_c)]
-                                     Y[\Idx[\vec{z} \oplus \vec{y}]^{-1}(i_c + |\Dim(\vec{c})|i_b)] \\
-  Z[\Idx[\vec{x}  \oplus \vec{y}]^{-1}(i_a + |\Dim(\vec{a})| i_b)]
-  &=
-  \sum_{0 \le i_c < |\Dim(\vec{c})|} X[\Idx[\vec{x} \oplus \vec{z}]^{-1}(i_a + |\Dim(\vec{a})|i_c)]
-                                     Y[\Idx[\vec{z} \oplus \vec{y}]^{-1}(i_c + |\Dim(\vec{c})|i_b)] \\
-  Z[\Idx[\vec{x}  \oplus \vec{y}]^{-1}(i_a + |\Dim(\vec{x})| i_b)]
-  &=
-  \sum_{0 \le i_c < |\Dim(\vec{z})|} X[\Idx[\vec{x} \oplus \vec{z}]^{-1}(i_a + |\Dim(\vec{x})|i_c)]
-                                     Y[\Idx[\vec{z} \oplus \vec{y}]^{-1}(i_c + |\Dim(\vec{z})|i_b)] \\
+  C[\Idx[\vec{a}  \oplus \vec{b}]^{-1}(i_a + \shape{\Dim(\vec{a})} i_b)]
+  &=
+  \sum_{0 \le i_c < \shape{\Dim(\vec{c})}} A[\Idx[\vec{a}]^{-1}(i_a) \oplus \Idx[\vec{c}]^{-1}(i_c)] B[\Idx[\vec{c}]^{-1}(i_c) \oplus \Idx[\vec{b}]^{-1}(i_b)] \\
+  &=
+  \sum_{0 \le i_c < \shape{\Dim(\vec{c})}} A[\Idx[\vec{a} \oplus \vec{c}]^{-1}(i_a + \shape{\Dim(\vec{a})}i_c)]
+                                     B[\Idx[\vec{c} \oplus \vec{b}]^{-1}(i_c + \shape{\Dim(\vec{c})}i_b)] \\
+  &=
+  \sum_{0 \le i_c < \shape{\Dim(\vec{c})}} X[\Idx[\vec{x} \oplus \vec{z}]^{-1}(i_a + \shape{\Dim(\vec{a})}i_c)]
+                                     Y[\Idx[\vec{z} \oplus \vec{y}]^{-1}(i_c + \shape{\Dim(\vec{c})}i_b)] \\
+  Z[\Idx[\vec{x}  \oplus \vec{y}]^{-1}(i_a + \shape{\Dim(\vec{a})} i_b)]
+  &=
+  \sum_{0 \le i_c < \shape{\Dim(\vec{c})}} X[\Idx[\vec{x} \oplus \vec{z}]^{-1}(i_a + \shape{\Dim(\vec{a})}i_c)]
+                                     Y[\Idx[\vec{z} \oplus \vec{y}]^{-1}(i_c + \shape{\Dim(\vec{c})}i_b)] \\
+  Z[\Idx[\vec{x}  \oplus \vec{y}]^{-1}(i_a + \shape{\Dim(\vec{x})} i_b)]
+  &=
+  \sum_{0 \le i_c < \shape{\Dim(\vec{z})}} X[\Idx[\vec{x} \oplus \vec{z}]^{-1}(i_a + \shape{\Dim(\vec{x})}i_c)]
+                                     Y[\Idx[\vec{z} \oplus \vec{y}]^{-1}(i_c + \shape{\Dim(\vec{z})}i_b)] \\
   Z[\Idx[\vec{x}]^{-1}(i_a) \oplus \Idx[\vec{y}]^{-1}(i_b)]
   &=
-  \sum_{0 \le i_c < |\Dim(\vec{z})|} X[\Idx[\vec{x}]^{-1}(i_a) \oplus \Idx[\vec{z}]^{-1}(i_c)]
+  \sum_{0 \le i_c < \shape{\Dim(\vec{z})}} X[\Idx[\vec{x}]^{-1}(i_a) \oplus \Idx[\vec{z}]^{-1}(i_c)]
                                      Y[\Idx[\vec{z}]^{-1}(i_c) \oplus \Idx[\vec{y}]^{-1}(i_b)]
@@
   &=
-  \sum_{0 \le i_c < |\Dim(\vec{z})|} X[\bar{x} \oplus \Idx[\vec{z}]^{-1}(i_c)]
+  \sum_{0 \le i_c < \shape{\Dim(\vec{z})}} X[\bar{x} \oplus \Idx[\vec{z}]^{-1}(i_c)]
                                      Y[\Idx[\vec{z}]^{-1}(i_c) \oplus \bar{y}] \\
@@
                                      Y[\bar{z} \oplus \bar{y}] \\
-  &= X \mmult{|\vec{z}|} Y
+  &= X \mmult{\shape{\vec{z}}} Y
 \end{align*}
@@
 Therefore for any $\RMult(m,X)$ you can potentially find an inverse with
-multiplication width $n \le ||X||-m$ by simply reshaping the problem into
+multiplication width $n \le \shape{\shape{X}}-m$ by simply reshaping the problem into
 one using standard two dimensional matricies wich already has thoroughly
@@
 you'd reshape $X \mmult{n} Y = \Ident^2(\vec{m})$ into $A \mmult{1} B = \Ident^2(\left<\size(\Dim(\vec{m}))\right>)$
-where $|A| = \left<\size(\Dim(\vec{m} \oplus \vec{x_l})), \size(\Dim(\vec{x_r}))\right>$
-and   $|B| = \left<\size(\Dim(\vec{x_r})),  \size(\Dim(\vec{y}))\right>$.
+where $\shape{A} = \left<\size(\Dim(\vec{m} \oplus \vec{x_l})), \size(\Dim(\vec{x_r}))\right>$
+and   $\shape{B} = \left<\size(\Dim(\vec{x_r})),  \size(\Dim(\vec{y}))\right>$.
 Then solve for $B$ and return the problem to the original shape to get $Y$.
@@
 In short, if two matricies, $A$ and $B$ have the same shape,
-\[ |A| = |B| = \left<r,c\right> \]
+\[ \shape{A} = \shape{B} = \left<r,c\right> \]
 Then their Hadamard product, $A \bullet B$, is the same shape and each element
@@
 \label{multi_had_prod}
-Let $A$ and $B$ be multimatricies such that $|A| = \vec{a} \oplus \vec{c}$
-and $|B| = \vec{c} \oplus \vec{b}$. Also let $c = |\vec{c}|$.
+Let $A$ and $B$ be multimatricies such that $\shape{A} = \vec{a} \oplus \vec{c}$
+and $\shape{B} = \vec{c} \oplus \vec{b}$. Also let $c = \shape{\vec{c}}$.
 Then, the multimatrix Hadamard product, $A \dmult{c} B$, is a multimatrix
 such that,
-\[ |A \dmult{c} B| = \vec{a} \oplus \vec{c} \oplus \vec{b} \]
+\[ \shape{A \dmult{c} B} = \vec{a} \oplus \vec{c} \oplus \vec{b} \]
 And for any $\bar{a} \in \Dim(\vec{a})$, $\bar{b} \in \Dim(\vec{b})$,
@@
 \begin{proof}
-Let $|A| = \vec{a}$ and $|B| = \vec{b}$ then,
-\[ |A \dmult{0} B| = \vec{a} \oplus \vec{b} = |A \mmult{0} B| \]
+Let $\shape{A} = \vec{a}$ and $\shape{B} = \vec{b}$ then,
+\[ \shape{A \dmult{0} B} = \vec{a} \oplus \vec{b} = \shape{A \mmult{0} B} \]
 And for all $\bar{a} \in \Dim(\vec{a})$ and $\bar{b} \in \Dim(\vec{b})$,
@@
 \begin{theorem}[Hadamard Product Associativity]
-Let $A$, $B$, and $C$ be multimatrixes such that $|A| = \vec{a} \oplus \vec{m}$,
-$|B| = \vec{m} \oplus \vec{b} \oplus \vec{n}$ and $|C| = \vec{n} \oplus \vec{c}$,
-where $|\vec{m}| = m$ and $|\vec{n}| = n$.
+Let $A$, $B$, and $C$ be multimatrixes such that $\shape{A} = \vec{a} \oplus \vec{m}$,
+$\shape{B} = \vec{m} \oplus \vec{b} \oplus \vec{n}$ and $\shape{C} = \vec{n} \oplus \vec{c}$,
+where $\shape{\vec{m}} = m$ and $\shape{\vec{n}} = n$.
 Then $(A \dmult{m} B) \dmult{n} C = A \dmult{m} (B \dmult{n} C)$.
@@
 When $X_1 \ldots X_{m-1}$ are all in $\mathbb{R}^{\vec{x}}$ and
-$|X_m| = \vec{x} \oplus \vec{r}$ for any $\vec{r}$,
+$\shape{X_m} = \vec{x} \oplus \vec{r}$ for any $\vec{r}$,
 \[
   (((\Ident^n(\vec{x})
-  \mmult{|\vec{x}|} X_1) \mmult{|\vec{x}|} X_2) \mmult{|\vec{x}|} X_3)
+  \mmult{\shape{\vec{x}}} X_1) \mmult{\shape{\vec{x}}} X_2) \mmult{\shape{\vec{x}}} X_3)
   \ldots X_m
@@
   \Ident^{n-m}(\vec{x})
-  \dmult{|\vec{x}|} X_1 \dmult{|\vec{x}|} X_2 \dmult{|\vec{x}|} X_3
+  \dmult{\shape{\vec{x}}} X_1 \dmult{\shape{\vec{x}}} X_2 \dmult{\shape{\vec{x}}} X_3
   \ldots X_m
@@
 And when $X_2 \ldots X_m$ are all in $\mathbb{R}^{\vec{x}}$ and
-$|X_1| = \vec{l} \oplus \vec{x}$ for any $\vec{l}$,
-\[
-  X_1 \mmult{|\vec{x}|} (X_2 \mmult{|\vec{x}|} (X_3
-  \ldots (X_m \mmult{|\vec{x}|} 
+$\shape{X_1} = \vec{l} \oplus \vec{x}$ for any $\vec{l}$,
+\[
+  X_1 \mmult{\shape{\vec{x}}} (X_2 \mmult{\shape{\vec{x}}} (X_3
+  \ldots (X_m \mmult{\shape{\vec{x}}} 
   \Ident^n(\vec{x}))))
   =
-  X_1 \dmult{|\vec{x}|} X_2 \dmult{|\vec{x}|} X_3
-  \ldots X_m \dmult{|\vec{x}|} 
+  X_1 \dmult{\shape{\vec{x}}} X_2 \dmult{\shape{\vec{x}}} X_3
+  \ldots X_m \dmult{\shape{\vec{x}}} 
   \Ident^{n-m}(\vec{x})
@@
 \begin{theorem}[Communicativity of Hadamard Products]
-If $A$ and $B$ are multimatrices of the same shape, $|A| = |B| = \vec{x}$,
-then $A \dmult{|\vec{x}|} B = B \dmult{|\vec{x}|} A$.
+If $A$ and $B$ are multimatrices of the same shape, $\shape{A} = \shape{B} = \vec{x}$,
+then $A \dmult{\shape{\vec{x}}} B = B \dmult{\shape{\vec{x}}} A$.
 \end{theorem}
@@
 \begin{align*}
-(A \dmult{|\vec{x}|} B)[\bar{x}]
+(A \dmult{\shape{\vec{x}}} B)[\bar{x}]
   &= A[\bar{x}] B[\bar{x}] \\
   &= B[\bar{x}] A[\bar{x}] \\
-  &= (B \dmult{|\vec{x}|} A)[\bar{x}]
+  &= (B \dmult{\shape{\vec{x}}} A)[\bar{x}]
 \end{align*}
@@
 \begin{exercise}
-Let $A$, $B$, and $C$ be multimatricies such that $|A| = \left<1,2,3\right>$,
-$|B| = \left<3,1,2\right>$ and $|C| = \left<3,2,1\right>$. For each of these
+Let $A$, $B$, and $C$ be multimatricies such that $\shape{A} = \left<1,2,3\right>$,
+$\shape{B} = \left<3,1,2\right>$ and $\shape{C} = \left<3,2,1\right>$. For each of these
 multiplications determine if it is valid, and if so, what the resulting
@@
 	\begin{itemize}
-		\item $|A| = \left<3, 7, 9\right>$
-		\item $|B| = \left<9, 5\right>$
-		\item $|C| = \left<5, 7, 3\right>$
+		\item $\shape{A} = \left<3, 7, 9\right>$
+		\item $\shape{B} = \left<9, 5\right>$
+		\item $\shape{C} = \left<5, 7, 3\right>$
 		\item and $m = n = 1$
@@
 	\begin{itemize}
-		\item $|A| = \left<6, 6, 6\right>$
-		\item $|B| = \left<6, 6, 6\right>$
-		\item $|C| = \left<6, 6, 6\right>$
+		\item $\shape{A} = \left<6, 6, 6\right>$
+		\item $\shape{B} = \left<6, 6, 6\right>$
+		\item $\shape{C} = \left<6, 6, 6\right>$
 		\item and $m = n = 2$
@@
 	\begin{itemize}
-		\item $|A| = \left<3, 5, 3\right>$
-		\item $|B| = \left<5, 3, 11\right>$
-		\item $|C| = \left<11, 2, 7\right>$
+		\item $\shape{A} = \left<3, 5, 3\right>$
+		\item $\shape{B} = \left<5, 3, 11\right>$
+		\item $\shape{C} = \left<11, 2, 7\right>$
 		\item $m = 2$
@@
 	\begin{itemize}
-		\item $|A| = \left<3, 5, 3\right>$
-		\item $|B| = \left<5, 3, 3, 5\right>$
-		\item $|C| = \left<3, 3, 5, 2\right>$
+		\item $\shape{A} = \left<3, 5, 3\right>$
+		\item $\shape{B} = \left<5, 3, 3, 5\right>$
+		\item $\shape{C} = \left<3, 3, 5, 2\right>$
 		\item $m = 2$
@@
 \begin{exercise}
-Let $|X| = \vec{x}$. Simplify the following where possible:
+Let $\shape{X} = \vec{x}$. Simplify the following where possible:
 \begin{enumerate}
-\item $\Ident^5(\vec{x}) \mmult{3 |\vec{x}|} \Ident^3(\vec{x})$
-\item $\Ident^2(\vec{x}) \mmult{|\vec{x}|} X$
-\item $\Ident^3(\vec{x}) \mmult{2|\vec{x}|} X$
-\item $\Ident^2(\vec{x}) \mmult{|\vec{x}|} \left(X \mmult{|\vec{x}|} \Ident^3(|\vec{x}|)
-				\right) \mmult{2|\vec{x}|} \Ident^3(|\vec{x}|)$
+\item $\Ident^5(\vec{x}) \mmult{3 \shape{\vec{x}}} \Ident^3(\vec{x})$
+\item $\Ident^2(\vec{x}) \mmult{\shape{\vec{x}}} X$
+\item $\Ident^3(\vec{x}) \mmult{2\shape{\vec{x}}} X$
+\item $\Ident^2(\vec{x}) \mmult{\shape{\vec{x}}} \left(X \mmult{\shape{\vec{x}}} \Ident^3(\shape{\vec{x}})
+				\right) \mmult{2\shape{\vec{x}}} \Ident^3(\shape{\vec{x}})$
 \end{enumerate}
@@
 \begin{exercise}
-Let $M$ be some multimatrix such that $|M| = \left<5,2,3\right>$. Then what is
+Let $M$ be some multimatrix such that $\shape{M} = \left<5,2,3\right>$. Then what is
 $dM/dM$?
@@
 Let $Y = \tan(X)$ be the elementwise application of the scalar tangent function to
-the elements of $X$, that is, for all $\bar{v} \in \Dim(|X|)$
+the elements of $X$, that is, for all $\bar{v} \in \Dim(\shape{X})$
 \[ Y[\bar{v}] = \tan(X[\bar{v}]) \]
@@
 \begin{proof}
-Let $|A| = \vec{a}$. Then for all $\bar{a} \in \Dim(\vec{a})$,
+Let $\shape{A} = \vec{a}$. Then for all $\bar{a} \in \Dim(\vec{a})$,
 \begin{align*}
@@
 \label{eq_add_sub_thm}
-For any multimatricies $A$ and $B$ where $|A| = |B|$,
+For any multimatricies $A$ and $B$ where $\shape{A} = \shape{B}$,
 \[ A - B = A + (-1)B \]
@@
 \begin{theorem}[Multimatrix on Multimatrix Distributive Property]
-If $|A| = \vec{a} \oplus \vec{n}$ and $|B|=|C|=\vec{n} \oplus \vec{r}$ then,
+If $\shape{A} = \vec{a} \oplus \vec{n}$ and $\shape{B}=\shape{C}=\vec{n} \oplus \vec{r}$ then,
 \[ A \mmult{n} (B + C) = A \mmult{n} B + A \mmult{n} C \]
-Similarly, if $|C| = \vec{n} \oplus \vec{c}$ and $|A|=|B|=\vec{l} \oplus \vec{n}$ then,
+Similarly, if $\shape{C} = \vec{n} \oplus \vec{c}$ and $\shape{A}=\shape{B}=\vec{l} \oplus \vec{n}$ then,
 \[ (A + B) \mmult{n} C = A \mmult{n} C + B \mmult{n} C \]
@@
 \begin{ppart}
-Let $|A| = \vec{a} \oplus \vec{n}$ and $|B|=|C|=\vec{n} \oplus \vec{r}$.
+Let $\shape{A} = \vec{a} \oplus \vec{n}$ and $\shape{B}=\shape{C}=\vec{n} \oplus \vec{r}$.
 So, $\forall \bar{a} \in \Dim(\vec{a}), \bar{r} \in \Dim(\vec{r}) :$
@@
 \begin{ppart}
-Let $|C| = \vec{n} \oplus \vec{c}$ and $|A|=|B|=\vec{l} \oplus \vec{n}$.
+Let $\shape{C} = \vec{n} \oplus \vec{c}$ and $\shape{A}=\shape{B}=\vec{l} \oplus \vec{n}$.
 So, $\forall \bar{c} \in \Dim(\vec{c}), \bar{l} \in \Dim(\vec{l}) :$
@@
 \label{tran_def}
-Let $|X| = \vec{l} \oplus \vec{r}$ where $|\vec{l}| = l$ and $|\vec{r}| = r$
-\[ |\Tran(X, l)| = \vec{r} \oplus \vec{l} \]
+Let $\shape{X} = \vec{l} \oplus \vec{r}$ where $\shape{\vec{l}} = l$ and $\shape{\vec{r}} = r$
+\[ \shape{\Tran(X, l)} = \vec{r} \oplus \vec{l} \]
 And,
@@
 Let's construct some multimatrix, $M$, with a shape:
-\[ |M| = \left<3,2,7,5,9\right> \]
+\[ \shape{M} = \left<3,2,7,5,9\right> \]
 Then lets take the first transpose of that
 multimatrix:
-\[ |\Tran(M, 1)| = \left<2,7,5,9,3\right> \]
+\[ \shape{\Tran(M, 1)} = \left<2,7,5,9,3\right> \]
 And... how about the third:
-\[ |\Tran(M, 3)| = \left<5,9,3,2,7\right> \]
+\[ \shape{\Tran(M, 3)} = \left<5,9,3,2,7\right> \]
 You can see, it's as though I cut off the front of the shape vector and transfered
@@
 For any multimatrix, the following transposes are equivalent,
-\[ \Tran(X, n) = \Tran(X, \remainder(n, ||X||)) \]
-Where $\remainder(n, ||X||)$ is the remainder of $n$ divided by $||X||$.
-That is, a value $0 \le \remainder(n, ||X||) < ||X||$ such that there exists an
-integer $k$ where, $n = k||X|| + \remainder(n, ||X||)$.
+\[ \Tran(X, n) = \Tran(X, \remainder(n, \shape{\shape{X}})) \]
+Where $\remainder(n, \shape{\shape{X}})$ is the remainder of $n$ divided by $\shape{\shape{X}}$.
+That is, a value $0 \le \remainder(n, \shape{\shape{X}}) < \shape{\shape{X}}$ such that there exists an
+integer $k$ where, $n = k\shape{\shape{X}} + \remainder(n, \shape{\shape{X}})$.
 \end{definition}
@@
 index of transpose, $l$, that would be covered by the original definition,
-$0 \le l \le ||X||$, you can see that, in all but one case $\remainder(l, ||X||) = l$.
-The exception, $l = ||X||$ is covered by showing that
-$\remainder(||X||, ||X||) = 0$ and $\Tran(X, 0) = \Tran(X, ||X||)$.
+$0 \le l \le \shape{\shape{X}}$, you can see that, in all but one case $\remainder(l, \shape{\shape{X}}) = l$.
+The exception, $l = \shape{\shape{X}}$ is covered by showing that
+$\remainder(\shape{\shape{X}}, \shape{\shape{X}}) = 0$ and $\Tran(X, 0) = \Tran(X, \shape{\shape{X}})$.
 
@@
 be indicies of transpositions. Then what is $\Tran(\Tran(A, x), y)$?
-To apply the the first transpose we need to break $|A|$ into two vectors,
-so let $|A| = \vec{l} \oplus \vec{r}$ where $|\vec{l}| = x$.
+To apply the the first transpose we need to break $\shape{A}$ into two vectors,
+so let $\shape{A} = \vec{l} \oplus \vec{r}$ where $\shape{\vec{l}} = x$.
 
 Then,
-\[ |\Tran(A, x)| = \vec{r} \oplus \vec{l} \]
+\[ \shape{\Tran(A, x)} = \vec{r} \oplus \vec{l} \]
 And for all
@@
 Now to apply a transposition with index of transposition $y$ to $\Tran(A,x)$
-we need to break up $|\Tran(A,x)|$ into two vector, such as
-$|\Tran(A,x)| = \vec{l}' \oplus \vec{r}'$.
-
-Since we've already shown that $|\Tran(A,x)| = \vec{r} \oplus \vec{l}$
+we need to break up $\shape{\Tran(A,x)}$ into two vector, such as
+$\shape{\Tran(A,x)} = \vec{l}' \oplus \vec{r}'$.
+
+Since we've already shown that $\shape{\Tran(A,x)} = \vec{r} \oplus \vec{l}$
 we end up with two conceptual splits of that shape vector that need to
@@
 
-\begin{case} $|\vec{l}'| \le |\vec{r}|$
-
-Then we can divide $|\Tran(A,x)|$ into three vectors, $\vec{a}$, $\vec{b}$, and $\vec{c}$
+\begin{case} $\shape{\vec{l}'} \le \shape{\vec{r}}$
+
+Then we can divide $\shape{\Tran(A,x)}$ into three vectors, $\vec{a}$, $\vec{b}$, and $\vec{c}$
 such that
-\[ |\Tran(A,x)| = \vec{b} \oplus \vec{c} \oplus \vec{a} \]
+\[ \shape{\Tran(A,x)} = \vec{b} \oplus \vec{c} \oplus \vec{a} \]
 \[ \vec{l}' = \vec{b} \]
@@
 So we can then say,
-\[ |A| = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
+\[ \shape{A} = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
 
 And since,
-\[ |\Tran(\Tran(A, x), y)| = \vec{r}' \oplus \vec{l}' \]
+\[ \shape{\Tran(\Tran(A, x), y)} = \vec{r}' \oplus \vec{l}' \]
 It follows that,
-\[ |\Tran(\Tran(A, x), y)| = \vec{c} \oplus \vec{a} \oplus \vec{b} \]
+\[ \shape{\Tran(\Tran(A, x), y)} = \vec{c} \oplus \vec{a} \oplus \vec{b} \]
 
@@
 See now that this composit operation is also a transposition, $\Tran(A, z)$ where,
-$z = |\vec{a} \oplus \vec{b}|$.
+$z = \shape{\vec{a} \oplus \vec{b}}$.
 So by definition,
 \begin{align*}
-  |\Tran(A, z)|
+  \shape{\Tran(A, z)}
   &=
@@
   &=
-  |\Tran(\Tran(A, x), y)|  
+  \shape{\Tran(\Tran(A, x), y)}  
 \end{align*}
@@
 
-\begin{case} $|\vec{l}'| > |\vec{r}|$
-Then we can divide $|\Tran(A,x)|$ into three vectors, $\vec{a}$, $\vec{b}$, and $\vec{c}$
+\begin{case} $\shape{\vec{l}'} > \shape{\vec{r}}$
+Then we can divide $\shape{\Tran(A,x)}$ into three vectors, $\vec{a}$, $\vec{b}$, and $\vec{c}$
 such that
-\[ |\Tran(A,x)| = \vec{c} \oplus \vec{a} \oplus \vec{b} \]
+\[ \shape{\Tran(A,x)} = \vec{c} \oplus \vec{a} \oplus \vec{b} \]
 \[ \vec{l}' = \vec{c} \oplus \vec{a} \]
@@
 So we can then say,
-\[ |A| = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
+\[ \shape{A} = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
 
 And since,
-\[ |\Tran(\Tran(A, x), y)| = \vec{r}' \oplus \vec{l}' \]
+\[ \shape{\Tran(\Tran(A, x), y)} = \vec{r}' \oplus \vec{l}' \]
 It follows that,
-\[ |\Tran(\Tran(A, x), y)| = \vec{b} \oplus \vec{c} \oplus \vec{a} \]
+\[ \shape{\Tran(\Tran(A, x), y)} = \vec{b} \oplus \vec{c} \oplus \vec{a} \]
 
@@
 See now that this composit operation is also a transposition, $\Tran(A, z)$ where,
-$z = |\vec{a}|$.
+$z = \shape{\vec{a}}$.
 So by definition,
 \begin{align*}
-  |\Tran(A, z)|
+  \shape{\Tran(A, z)}
   &=
@@
 $\Tran_x$ and $\Tran_y$ which we'll apply in series. First remember that
-to define $\Tran_x$ we needed to divide $|A|$ into $|A| = \vec{l} \oplus \vec{r}$
-where $|\vec{l}| = x$. Then we'd say that
-\[ |\Tran(A, x)| = \vec{r} \oplus \vec{l} \]
-Then to further apply $\Tran(\Tran(A, x), y)$ we need to divide $|\Tran(A,x)|$
+to define $\Tran_x$ we needed to divide $\shape{A}$ into $\shape{A} = \vec{l} \oplus \vec{r}$
+where $\shape{\vec{l}} = x$. Then we'd say that
+\[ \shape{\Tran(A, x)} = \vec{r} \oplus \vec{l} \]
+Then to further apply $\Tran(\Tran(A, x), y)$ we need to divide $\shape{\Tran(A,x)}$
 into,
-\[ |\Tran(A, x)| = \vec{l}' \oplus \vec{r}' \]
-Where $|\vec{l}'| = y$.
+\[ \shape{\Tran(A, x)} = \vec{l}' \oplus \vec{r}' \]
+Where $\shape{\vec{l}'} = y$.
 That leads to two cases,
@@
 \setcounter{case}{0}
-\begin{case} $|\vec{l}'| \le |\vec{r}|$
-
-And in this case we showed that we needed to split up $|A|$ into,
-\[ |A| = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
+\begin{case} $\shape{\vec{l}'} \le \shape{\vec{r}}$
+
+And in this case we showed that we needed to split up $\shape{A}$ into,
+\[ \shape{A} = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
 \[ \vec{l}' = \vec{b} \]
@@
 So that,
-\[ |\Tran(A, x)| = \vec{b} \oplus \vec{c} \oplus \vec{a} \]
-\[ |\Tran(\Tran(A, x), y)| = \vec{c} \oplus \vec{a} \oplus \vec{b} \]
+\[ \shape{\Tran(A, x)} = \vec{b} \oplus \vec{c} \oplus \vec{a} \]
+\[ \shape{\Tran(\Tran(A, x), y)} = \vec{c} \oplus \vec{a} \oplus \vec{b} \]
 And note that,
-\[ x = |\vec{a}| \]
-\[ y = |\vec{b}| \]
+\[ x = \shape{\vec{a}} \]
+\[ y = \shape{\vec{b}} \]
 
@@
 that,
-\[ z = |\vec{a} \oplus \vec{b}| \]
+\[ z = \shape{\vec{a} \oplus \vec{b}} \]
 
@@
   z
-  &= |\vec{a} \oplus \vec{b}| \\
-  &= |\vec{a}| + |\vec{b}| \\
+  &= \shape{\vec{a} \oplus \vec{b}} \\
+  &= \shape{\vec{a}} + \shape{\vec{b}} \\
   &= x + y \\
@@
 
-\begin{case} $|\vec{l}'| > |\vec{r}|$
-
-And in this case we showed that we needed to split up $|A|$ into,
-\[ |A| = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
+\begin{case} $\shape{\vec{l}'} > \shape{\vec{r}}$
+
+And in this case we showed that we needed to split up $\shape{A}$ into,
+\[ \shape{A} = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
 \[ \vec{l}' = \vec{c} \oplus \vec{a} \]
@@
 So that,
-\[ |\Tran(A, x)| = \vec{c} \oplus \vec{a} \oplus \vec{b} \]
-\[ |\Tran(\Tran(A, x), y)| = \vec{b} \oplus \vec{c} \oplus \vec{a} \]
+\[ \shape{\Tran(A, x)} = \vec{c} \oplus \vec{a} \oplus \vec{b} \]
+\[ \shape{\Tran(\Tran(A, x), y)} = \vec{b} \oplus \vec{c} \oplus \vec{a} \]
 And note that,
-\[ x = |\vec{a} \oplus \vec{b}| \]
-\[ y = |\vec{c} \oplus \vec{a}| \]
+\[ x = \shape{\vec{a} \oplus \vec{b}} \]
+\[ y = \shape{\vec{c} \oplus \vec{a}} \]
 
@@
 that,
-\[ z = |\vec{a}| \]
+\[ z = \shape{\vec{a}} \]
 
@@
   z
-  &= |\vec{a}| \\
-  &\equiv |\vec{a}| + n \mod n \\
-  &\equiv |\vec{a}| + |\vec{a} \oplus \vec{b} \oplus \vec{c}| \mod n \\
-  &\equiv |\vec{a} \oplus \vec{a} \oplus \vec{b} \oplus \vec{c}| \mod n \\
-  &\equiv |\vec{c} \oplus \vec{a} \oplus \vec{a} \oplus \vec{b}| \mod n \\
-  &\equiv |\vec{c} \oplus \vec{a}| + |\vec{a} \oplus \vec{b}| \mod n \\
+  &= \shape{\vec{a}} \\
+  &\equiv \shape{\vec{a}} + n \mod n \\
+  &\equiv \shape{\vec{a}} + \shape{\vec{a} \oplus \vec{b} \oplus \vec{c}} \mod n \\
+  &\equiv \shape{\vec{a} \oplus \vec{a} \oplus \vec{b} \oplus \vec{c}} \mod n \\
+  &\equiv \shape{\vec{c} \oplus \vec{a} \oplus \vec{a} \oplus \vec{b}} \mod n \\
+  &\equiv \shape{\vec{c} \oplus \vec{a}} + \shape{\vec{a} \oplus \vec{b}} \mod n \\
   &\equiv y + x \mod n \\
@@
 Then see that,
-\[ |\Tran(A, 2)| = \left<7, 5, 11, 3\right> \]
+\[ \shape{\Tran(A, 2)} = \left<7, 5, 11, 3\right> \]
 And applying another transpose,
-\[ |\Tran(\Tran(A, 2), 3)| = \left<3, 7, 5, 11\right> \]
+\[ \shape{\Tran(\Tran(A, 2), 3)} = \left<3, 7, 5, 11\right> \]
 Notice that our corollary says that this double transpose should be
@@
 \begin{align*}
-  |\Tran(A, 1)|
+  \shape{\Tran(A, 1)}
   &= \left<3, 7, 5, 11\right> \\
-  &= |\Tran(\Tran(A, 2), 3)|
+  &= \shape{\Tran(\Tran(A, 2), 3)}
 \end{align*}
@@
 \begin{corollary}[Inverse Transpose]
-Let $A$ be a multimatrix such that $||A|| = n$. And let
+Let $A$ be a multimatrix such that $\shape{\shape{A}} = n$. And let
 $x$ be some integer. Then, the inverse of $\Tran_x$ is
@@
 Let's apply a transpose to it, $\Tran_3$, and we'll get the shape,
-\[ |\Tran(A, 3)| = \left<8,3,2,7,1\right> \]
+\[ \shape{\Tran(A, 3)} = \left<8,3,2,7,1\right> \]
 Now, to get back to $A$ we can apply another transpose $\Tran_{-3}$ according
@@
 \begin{align*}
-  |\Tran(\Tran(A, 3), 2)|
+  \shape{\Tran(\Tran(A, 3), 2)}
   &= \left<2,7,1,8,3\right> \\
-  &= |A|
+  &= \shape{A}
 \end{align*}
@@
 %TODO: I think this is even more general.
-% I think that if k = |\vec{a}| mod |\vec{a} \oplus \vec{b}| then
+% I think that if k = \shape{\vec{a}} mod \shape{\vec{a} \oplus \vec{b}} then
 % \Tran(\Ident^n(\vec{a} \oplus \vec{b}), k) = \Ident^n(\vec{b} \oplus \vec{a})
@@
 shape vector. Then for any integer $k$,
-\[ \Tran(\Ident^n(\vec{x}), k|\vec{x}|) = \Ident^n(\vec{x}) \]
+\[ \Tran(\Ident^n(\vec{x}), k\shape{\vec{x}}) = \Ident^n(\vec{x}) \]
 \end{theorem}
@@
 \begin{align*}
-  \Tran(\Ident^n(\vec{x}), k|\vec{x}|)\left[\bigoplus X'\right]
+  \Tran(\Ident^n(\vec{x}), k\shape{\vec{x}})\left[\bigoplus X'\right]
 	&=
@@
 Therefore
-$\Tran(\Ident^n(\vec{x}), k|\vec{x}|) = \Ident^n(\vec{x})$
+$\Tran(\Ident^n(\vec{x}), k\shape{\vec{x}}) = \Ident^n(\vec{x})$
 \end{proof}
@@
 \label{mm_tran_mult}
-Let $|A| = \vec{a} \oplus \vec{c}$ and $|B| = \vec{c} \oplus \vec{b}$ then
-\[
- \Tran(A \mmult{|\vec{c}|} B, |\vec{a}|)
- =  \Tran(B, |\vec{c}|) \mmult{|\vec{c}|} \Tran(A, |\vec{a}|)
+Let $\shape{A} = \vec{a} \oplus \vec{c}$ and $\shape{B} = \vec{c} \oplus \vec{b}$ then
+\[
+ \Tran(A \mmult{\shape{\vec{c}}} B, \shape{\vec{a}})
+ =  \Tran(B, \shape{\vec{c}}) \mmult{\shape{\vec{c}}} \Tran(A, \shape{\vec{a}})
 \]
@@
 \begin{align*}
-	\Tran(A \mmult{|\vec{c}|} B, |\vec{a}|)[\bar{b} \oplus \bar{a}]
-	&=
-	\left(A \mmult{|\vec{c}|} B \right)[\bar{a} \oplus \bar{b}] \\
+	\Tran(A \mmult{\shape{\vec{c}}} B, \shape{\vec{a}})[\bar{b} \oplus \bar{a}]
+	&=
+	\left(A \mmult{\shape{\vec{c}}} B \right)[\bar{a} \oplus \bar{b}] \\
 	&=
@@
 	\sum_{\forall \bar{c} \in \Dim(\vec{c})}
-	\Tran(B, |\vec{c}|)[\bar{b} \oplus \bar{c}]
-	\Tran(A, |\vec{a}|)[\bar{c} \oplus \bar{a}] \\
-	&=
-	\left(\Tran(B, |\vec{c}|) \mmult{|\vec{c}|} \Tran(A, |\vec{a}|) \right)
+	\Tran(B, \shape{\vec{c}})[\bar{b} \oplus \bar{c}]
+	\Tran(A, \shape{\vec{a}})[\bar{c} \oplus \bar{a}] \\
+	&=
+	\left(\Tran(B, \shape{\vec{c}}) \mmult{\shape{\vec{c}}} \Tran(A, \shape{\vec{a}}) \right)
 	[\bar{b} \oplus \bar{a}]
@@
 \begin{proof}
-Let $|A| = \vec{x} \oplus \vec{a}$ where $|\vec{x}| = x$. Then
+Let $\shape{A} = \vec{x} \oplus \vec{a}$ where $\shape{\vec{x}} = x$. Then
 let $\bar{x} \in \Dim(\vec{x})$ and $\bar{a} \in \Dim(\vec{a})$. So,
@@
 Let $x$ be in $\mathbb{N} \cup \{0\}$ and let $A$ and $B$ be
-multimatricies such that $|A| = |B|$ and $\Tran(A, x)$ is defined.
+multimatricies such that $\shape{A} = \shape{B}$ and $\Tran(A, x)$ is defined.
 Then,
@@
 \begin{exercise}
-Let $A$ be a multimatrix such that $|A| = <1,2,3,4,5>$,
+Let $A$ be a multimatrix such that $\shape{A} = <1,2,3,4,5>$,
 Find the shape of the following trasnposes:
 \begin{enumerate}
-\item $|\Tran(A, 3)| = ?$
-\item $|\Tran(A, 4)| = ?$
-\item $|\Tran(A, 5)| = ?$
-\item $|\Tran(A, 0)| = ?$
+\item $\shape{\Tran(A, 3)} = ?$
+\item $\shape{\Tran(A, 4)} = ?$
+\item $\shape{\Tran(A, 5)} = ?$
+\item $\shape{\Tran(A, 0)} = ?$
 \end{enumerate}
@@
 \label{tran_derivative}
-$|X| = \vec{l} \oplus \vec{r}$
-\[
- \frac{d\Tran(X, |\vec{l}|)}{dX} =
- \Tran(\Ident^2(\vec{r}) \mmult{0} \Ident^2(\vec{l}), |\vec{r}|)
-\]
-\end{theorem}
-\begin{proof}
-\begin{align*}
- \frac{d\Tran(X, |\vec{l}|)}{dX}
+$\shape{X} = \vec{l} \oplus \vec{r}$
+\[
+ \frac{d\Tran(X, \shape{\vec{l}})}{dX} =
+ \Tran(\Ident^2(\vec{r}) \mmult{0} \Ident^2(\vec{l}), \shape{\vec{r}})
+\]
+\end{theorem}
+\begin{proof}
+\begin{align*}
+ \frac{d\Tran(X, \shape{\vec{l}})}{dX}
  [\bar{r_1} \oplus \bar{l_1} \oplus \bar{l_2} \oplus \bar{r_2}]
@@
  &=
-  \Ident^2(|\vec{r}|)[\bar{r_2}\oplus\bar{r_1}]
-  \Ident^2(|\vec{l}|)[\bar{l_1}\oplus\bar{l_2}] \\
+  \Ident^2(\shape{\vec{r}})[\bar{r_2}\oplus\bar{r_1}]
+  \Ident^2(\shape{\vec{l}})[\bar{l_1}\oplus\bar{l_2}] \\
  &=
    \left(
-    \Ident^2(|\vec{r}|)
+    \Ident^2(\shape{\vec{r}})
     \mmult{0}
-    \Ident^2(|\vec{l}|)
+    \Ident^2(\shape{\vec{l}})
   \right)
@@
   \Tran(
-    \Ident^2(|\vec{r}|)
+    \Ident^2(\shape{\vec{r}})
     \mmult{0}
-    \Ident^2(|\vec{l}|)
-  , |\vec{r}|) 
+    \Ident^2(\shape{\vec{l}})
+  , \shape{\vec{r}}) 
  [\bar{r_1} \oplus \bar{l_1} \oplus \bar{l_2} \oplus \bar{r_2}]
@@
 defined. Then,
-\[ \frac{d(A \mmult{n} X)}{dX} = A \mmult{n} \Ident^2(|X|) \]
-\end{theorem}
-\begin{proof}
-Let $|A| = \vec{a} \oplus \vec{n}$ and $|X| = \vec{n} \oplus \vec{x}$
-where $|\vec{n}| = n$ which is equivalent to saying $A \mmult{n} X$ is defined.
+\[ \frac{d(A \mmult{n} X)}{dX} = A \mmult{n} \Ident^2(\shape{X}) \]
+\end{theorem}
+\begin{proof}
+Let $\shape{A} = \vec{a} \oplus \vec{n}$ and $\shape{X} = \vec{n} \oplus \vec{x}$
+where $\shape{\vec{n}} = n$ which is equivalent to saying $A \mmult{n} X$ is defined.
 Also let $\bar{a} \in \Dim(\vec{a})$, $\bar{n} \in \Dim(\vec{n})$,
@@
 \begin{align*}
-  A \mmult{n} \Ident^2(|X|)[\bar{a} \oplus \bar{x}_1 \oplus \bar{n} \oplus \bar{x}_2]
+  A \mmult{n} \Ident^2(\shape{X})[\bar{a} \oplus \bar{x}_1 \oplus \bar{n} \oplus \bar{x}_2]
   &=
@@
   A[\bar{a} \oplus \bar{m}]
-  \Ident^2(|X|)[\bar{m} \oplus \bar{x}_1 \oplus \bar{n} \oplus \bar{x}_2] \\
+  \Ident^2(\shape{X})[\bar{m} \oplus \bar{x}_1 \oplus \bar{n} \oplus \bar{x}_2] \\
   &=
@@
   =
-  A \mmult{n} \Ident^2(|X|)[\bar{a} \oplus \bar{x}_1 \oplus \bar{n} \oplus \bar{x}_2]
+  A \mmult{n} \Ident^2(\shape{X})[\bar{a} \oplus \bar{x}_1 \oplus \bar{n} \oplus \bar{x}_2]
 \]
@@
   =
-  A \mmult{n} \Ident^2(|X|)
+  A \mmult{n} \Ident^2(\shape{X})
 \]
@@
 \label{left_mult_derivative}
-If $|X| = \vec{x} \oplus \vec{n}$ and $|A| = \vec{n} \oplus \vec{a}$
-and $n = |\vec{n}|$ and $a = |\vec{a}|$ then,
-\[ \frac{d(X \mmult{n} A)}{dX} = \Ident^2(|X \mmult{n} A|) \mmult{a} \Tran(A, n) \]
-\end{theorem}
-\begin{proof}
-Let $|X| = \vec{x} \oplus \vec{n}$ and $|A| = \vec{n} \oplus \vec{a}$. Then,
+If $\shape{X} = \vec{x} \oplus \vec{n}$ and $\shape{A} = \vec{n} \oplus \vec{a}$
+and $n = \shape{\vec{n}}$ and $a = \shape{\vec{a}}$ then,
+\[ \frac{d(X \mmult{n} A)}{dX} = \Ident^2(\shape{X \mmult{n} A}) \mmult{a} \Tran(A, n) \]
+\end{theorem}
+\begin{proof}
+Let $\shape{X} = \vec{x} \oplus \vec{n}$ and $\shape{A} = \vec{n} \oplus \vec{a}$. Then,
 for all
@@
 \begin{align*}
-	\left(\Ident^2(|X \mmult{n} A|) \mmult{a} \Tran(A, n)\right)
+	\left(\Ident^2(\shape{X \mmult{n} A}) \mmult{a} \Tran(A, n)\right)
 	[\bar{x}_1 \oplus \bar{a}_1 \oplus \bar{x}_2 \oplus \bar{n}_1]
@@
 	\sum_{\forall \bar{a}_2 \in \Dim(\vec{a}_1)}
-	\Ident^2(|X \mmult{n} A|)[\bar{x}_1 \oplus \bar{a}_1 \oplus \bar{x}_2 \oplus \bar{a}_2]
+	\Ident^2(\shape{X \mmult{n} A})[\bar{x}_1 \oplus \bar{a}_1 \oplus \bar{x}_2 \oplus \bar{a}_2]
 	\Tran(A, n)[\bar{a}_2 \oplus \bar{n}_1] \\
@@
 	=
-	\left(\Ident^2(|X \mmult{n} A|) \mmult{a} \Tran(A, n)\right)
+	\left(\Ident^2(\shape{X \mmult{n} A}) \mmult{a} \Tran(A, n)\right)
 	[\bar{x}_1 \oplus \bar{a}_1 \oplus \bar{x}_2 \oplus \bar{n}_1]
@@
 	=
-	\Ident^2(|X \mmult{n} A|) \mmult{a} \Tran(A, n)
+	\Ident^2(\shape{X \mmult{n} A}) \mmult{a} \Tran(A, n)
 \]
@@
 \begin{proof}
-Let $|F(X)| = |G(X)| = \vec{f}$ and $|X| = \vec{x}$. Then,
+Let $\shape{F(X)} = \shape{G(X)} = \vec{f}$ and $\shape{X} = \vec{x}$. Then,
 $\forall \bar{f} \in \Dim(\vec{f}), \bar{x} \in \Dim(\vec{x}):$
@@
 \begin{proof}
-Let $|F(X)| = \vec{f}$ and $|X| = \vec{x}$. Then
+Let $\shape{F(X)} = \vec{f}$ and $\shape{X} = \vec{x}$. Then
 $\forall \bar{f} \in \Dim(\vec{f}), \bar{x} \in \Dim(\vec{x}):$
@@
 \label{multiplication_rule}
-Let $|F| = \vec{f} \oplus \vec{c}$, $|G| = \vec{c} \oplus \vec{g}$,
-and $|X| = \vec{x}$. Then,
-\begin{align*}
- \frac{d\left(F(X) \mmult{|\vec{c}|} G(X)\right)}{dX} =
- F(X) \mmult{|\vec{c}|} \frac{dG(X)}{dX} +
+Let $\shape{F} = \vec{f} \oplus \vec{c}$, $\shape{G} = \vec{c} \oplus \vec{g}$,
+and $\shape{X} = \vec{x}$. Then,
+\begin{align*}
+ \frac{d\left(F(X) \mmult{\shape{\vec{c}}} G(X)\right)}{dX} =
+ F(X) \mmult{\shape{\vec{c}}} \frac{dG(X)}{dX} +
  \Tran\left(
-   \Tran(G(X), |\vec{c}|)
-     \mmult{|\vec{c}|}
-   \Tran\left(\frac{dF(X)}{dX}, |\vec{f}|\right),
-   |\vec{g} \oplus \vec{x}|
+   \Tran(G(X), \shape{\vec{c}})
+     \mmult{\shape{\vec{c}}}
+   \Tran\left(\frac{dF(X)}{dX}, \shape{\vec{f}}\right),
+   \shape{\vec{g} \oplus \vec{x}}
  \right)
@@
 \begin{align*}
- \frac{d\left(F(X) \mmult{|\vec{c}|} G(X)\right)}{dX}
+ \frac{d\left(F(X) \mmult{\shape{\vec{c}}} G(X)\right)}{dX}
   [\bar{f} \oplus \bar{g} \oplus \bar{x}]
  &= \frac{
-       \partial \left(F(X) \mmult{|\vec{c}|} G(X)\right)[\bar{f} \oplus \bar{g}]
+       \partial \left(F(X) \mmult{\shape{\vec{c}}} G(X)\right)[\bar{f} \oplus \bar{g}]
     }{
@@
  &=
-   \left( F(X) \mmult{|\vec{c}|} \frac{dG(X)}{dX} \right)
+   \left( F(X) \mmult{\shape{\vec{c}}} \frac{dG(X)}{dX} \right)
    [\bar{f} \oplus \bar{g} \oplus \bar{x}]
@@
   \sum_{\forall \bar{c}}
-    \Tran\left(\frac{dF(X)}{dX}, |\vec{f}|\right)
+    \Tran\left(\frac{dF(X)}{dX}, \shape{\vec{f}}\right)
       [\bar{c} \oplus \bar{x} \oplus \bar{f}]
-    \Tran(G(X), |\vec{c}|)[\bar{g} \oplus \bar{c}] \\
+    \Tran(G(X), \shape{\vec{c}})[\bar{g} \oplus \bar{c}] \\
  &=
   \sum_{\forall \bar{c}}
-    \Tran(G(X), |\vec{c}|)[\bar{g} \oplus \bar{c}]
-    \Tran\left(\frac{dF(X)}{dX}, |\vec{f}|\right)
+    \Tran(G(X), \shape{\vec{c}})[\bar{g} \oplus \bar{c}]
+    \Tran\left(\frac{dF(X)}{dX}, \shape{\vec{f}}\right)
       [\bar{c} \oplus \bar{x} \oplus \bar{f}] \\
@@
   \left(
-    \Tran(G(X), |\vec{c}|) \mmult{|\vec{c}|}
-    \Tran\left(\frac{dF(X)}{dX}, |\vec{f}|\right)
+    \Tran(G(X), \shape{\vec{c}}) \mmult{\shape{\vec{c}}}
+    \Tran\left(\frac{dF(X)}{dX}, \shape{\vec{f}}\right)
   \right)[\bar{g} \oplus \bar{x} \oplus \bar{f}] \\
@@
   \Tran\left(
-    \Tran(G(X), |\vec{c}|) \mmult{|\vec{c}|}
-    \Tran\left(\frac{dF(X)}{dX}, |\vec{f}|\right)
-    , |\vec{g} \oplus \vec{x}|
+    \Tran(G(X), \shape{\vec{c}}) \mmult{\shape{\vec{c}}}
+    \Tran\left(\frac{dF(X)}{dX}, \shape{\vec{f}}\right)
+    , \shape{\vec{g} \oplus \vec{x}}
   \right)[\bar{f} \oplus \bar{g} \oplus \bar{x}]
@@
 \begin{alignat*}{3}
- \frac{d\left(F(X) \mmult{|\vec{c}|} G(X)\right)}{dX}
+ \frac{d\left(F(X) \mmult{\shape{\vec{c}}} G(X)\right)}{dX}
   [\bar{f} \oplus \bar{g} \oplus \bar{x}]
   &=&&
-  \left( F(X) \mmult{|\vec{c}|} \frac{dG(X)}{dX} \right)
+  \left( F(X) \mmult{\shape{\vec{c}}} \frac{dG(X)}{dX} \right)
   [\bar{f} \oplus \bar{g} \oplus \bar{x}] \\
@@
   \Tran\left(
-    \Tran(G(X), |\vec{c}|) \mmult{|\vec{c}|}
-    \Tran\left(\frac{dF(X)}{dX}, |\vec{f}|\right)
-    , |\vec{g} \oplus \vec{x}|
+    \Tran(G(X), \shape{\vec{c}}) \mmult{\shape{\vec{c}}}
+    \Tran\left(\frac{dF(X)}{dX}, \shape{\vec{f}}\right)
+    , \shape{\vec{g} \oplus \vec{x}}
   \right)[\bar{f} \oplus \bar{g} \oplus \bar{x}] \\
@@
     \begin{array}{l}
-      \left( F(X) \mmult{|\vec{c}|} \frac{dG(X)}{dX} \right) \\
+      \left( F(X) \mmult{\shape{\vec{c}}} \frac{dG(X)}{dX} \right) \\
       +
       \Tran\left(
-        \Tran(G(X), |\vec{c}|) \mmult{|\vec{c}|}
-        \Tran\left(\frac{dF(X)}{dX}, |\vec{f}|\right)
-        , |\vec{g} \oplus \vec{x}|
+        \Tran(G(X), \shape{\vec{c}}) \mmult{\shape{\vec{c}}}
+        \Tran\left(\frac{dF(X)}{dX}, \shape{\vec{f}}\right)
+        , \shape{\vec{g} \oplus \vec{x}}
       \right)
@@
 Let $F(X)$ and $G(X)$ be functions of $X$ where
-$|F(X)| = \vec{a} \oplus \vec{c}$ and $|G(X)| = \vec{c} \oplus \vec{b}$
+$\shape{F(X)} = \vec{a} \oplus \vec{c}$ and $\shape{G(X)} = \vec{c} \oplus \vec{b}$
 then,
 \[
-  \frac{d(F(X) \dmult{|\vec{c}|} G(X))}{dX} =
-    F(X) \dmult{|\vec{c}|} \frac{dG}{dX} +
-    \Tran\left(\Tran\left(\frac{dF}{dX}, ||F||\right) \dmult{|\vec{c}|} G(X), ||X||\right)
+  \frac{d(F(X) \dmult{\shape{\vec{c}}} G(X))}{dX} =
+    F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX} +
+    \Tran\left(\Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right) \dmult{\shape{\vec{c}}} G(X), \shape{\shape{X}}\right)
 \]
@@
 \begin{proof}
-For $\vec{x} = |X|$ and for $\bar{a} \in \Dim(\vec{a})$ etc,
-\begin{align*}
-\frac{d(F(X) \dmult{|\vec{c}|} G(X))}{dX}[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
-  &= \frac{\partial (F(X) \dmult{|\vec{c}|} G(X))[\bar{a} \oplus \bar{c} \oplus \bar{b}]}{\partial X[\bar{x}]} \\
+For $\vec{x} = \shape{X}$ and for $\bar{a} \in \Dim(\vec{a})$ etc,
+\begin{align*}
+\frac{d(F(X) \dmult{\shape{\vec{c}}} G(X))}{dX}[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
+  &= \frac{\partial (F(X) \dmult{\shape{\vec{c}}} G(X))[\bar{a} \oplus \bar{c} \oplus \bar{b}]}{\partial X[\bar{x}]} \\
   &= \frac{\partial (F(X)[\bar{a} \oplus \bar{c}] G(X)[\bar{c} \oplus \bar{a}])}{\partial X[\bar{x}]} \\
@@
   &= \frac{dF}{dX}[\bar{a} \oplus \bar{c} \oplus \bar{x}] G(X)[\bar{c} \oplus \bar{b}]
-    + \left(F(X) \dmult{|\vec{c}|} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
-  &= \Tran\left(\frac{dF}{dX}, ||F||\right)[\bar{x} \oplus \bar{a} \oplus \bar{c}] G(X)[\bar{c} \oplus \bar{b}]
-    + \left(F(X) \dmult{|\vec{c}|} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
-  &= \left(\Tran\left(\frac{dF}{dX}, ||F||\right) \dmult{|\vec{c}|} G(X)\right) [\bar{x} \oplus \bar{a} \oplus \bar{c} \oplus \bar{b}]
-    + \left(F(X) \dmult{|\vec{c}|} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
-  &= \Tran\left(\Tran\left(\frac{dF}{dX}, ||F||\right) \dmult{|\vec{c}|} G(X), ||X||\right) [\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
-    + \left(F(X) \dmult{|\vec{c}|} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
-  &= \left(F(X) \dmult{|\vec{c}|} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
-    + \Tran\left(\Tran\left(\frac{dF}{dX}, ||F||\right) \dmult{|\vec{c}|} G(X), ||X||\right) [\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
-  &= \left\{ F(X) \dmult{|\vec{c}|} \frac{dG}{dX}
-    + \Tran\left(\Tran\left(\frac{dF}{dX}, ||F||\right) \dmult{|\vec{c}|} G(X), ||X||\right) \right\}[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
+    + \left(F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
+  &= \Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right)[\bar{x} \oplus \bar{a} \oplus \bar{c}] G(X)[\bar{c} \oplus \bar{b}]
+    + \left(F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
+  &= \left(\Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right) \dmult{\shape{\vec{c}}} G(X)\right) [\bar{x} \oplus \bar{a} \oplus \bar{c} \oplus \bar{b}]
+    + \left(F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
+  &= \Tran\left(\Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right) \dmult{\shape{\vec{c}}} G(X), \shape{\shape{X}}\right) [\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
+    + \left(F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
+  &= \left(F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
+    + \Tran\left(\Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right) \dmult{\shape{\vec{c}}} G(X), \shape{\shape{X}}\right) [\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
+  &= \left\{ F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}
+    + \Tran\left(\Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right) \dmult{\shape{\vec{c}}} G(X), \shape{\shape{X}}\right) \right\}[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
 \end{align*}
@@
 \[
-\frac{dF(G(X))}{dX} = \frac{dF}{dG} \mmult{|\vec{g}|} \frac{dG}{dX}
+\frac{dF(G(X))}{dX} = \frac{dF}{dG} \mmult{\shape{\vec{g}}} \frac{dG}{dX}
 \]
@@
 Let $X$ be any multimatrix, then,
-\[\frac{d\Sum(X)}{dX} = 1^{|X|}\]
-\end{theorem}
-\begin{proof}
-Let $|X| = \vec{x}$ and $\bar{x} = \Dim(\vec{x})$. Then,
+\[\frac{d\Sum(X)}{dX} = 1^{\shape{X}}\]
+\end{theorem}
+\begin{proof}
+Let $\shape{X} = \vec{x}$ and $\bar{x} = \Dim(\vec{x})$. Then,
 \begin{align*}
@@
 So,
-\[\frac{d\Sum(X)}{dX} = 1^{|X|}\]
+\[\frac{d\Sum(X)}{dX} = 1^{\shape{X}}\]
 \end{proof}
@@
 \begin{proof}
-Let $|X| = \vec{x}$. Notice that $\SoS(X) = X \mmult{|\vec{x}|} X$ since,
-$|X \mmult{|\vec{x}|} X| = \left<\right>$ and,
-\[
-  \left(X \mmult{|\vec{x}|} X\right)[\left<\right> \oplus \left<\right>]
+Let $\shape{X} = \vec{x}$. Notice that $\SoS(X) = X \mmult{\shape{\vec{x}}} X$ since,
+$\shape{X \mmult{\shape{\vec{x}}} X} = \left<\right>$ and,
+\[
+  \left(X \mmult{\shape{\vec{x}}} X\right)[\left<\right> \oplus \left<\right>]
   =
@@
 \begin{align*}
-  \frac{d\left(X \mmult{|\vec{x}|} X\right)}{dX}
-  &=
-  X \mmult{|\vec{x}|} \frac{dX}{dX} +
+  \frac{d\left(X \mmult{\shape{\vec{x}}} X\right)}{dX}
+  &=
+  X \mmult{\shape{\vec{x}}} \frac{dX}{dX} +
   \Tran\left(
-    \Tran(X, |\vec{x}|)
-      \mmult{|\vec{x}|}
-    \Tran\left(\frac{dX}{dX}, |\vec{x}|\right),
-    |\vec{x} \oplus \vec{x}|
+    \Tran(X, \shape{\vec{x}})
+      \mmult{\shape{\vec{x}}}
+    \Tran\left(\frac{dX}{dX}, \shape{\vec{x}}\right),
+    \shape{\vec{x} \oplus \vec{x}}
   \right) \\
   &=
-  X \mmult{|\vec{x}|} \Ident^2(|X|) +
+  X \mmult{\shape{\vec{x}}} \Ident^2(\shape{X}) +
   \Tran\left(
     X
-      \mmult{|\vec{x}|}
-    \Tran\left(\Ident^2(|X|), |\vec{x}|\right),
-    |\vec{x} \oplus \vec{x}|
+      \mmult{\shape{\vec{x}}}
+    \Tran\left(\Ident^2(\shape{X}), \shape{\vec{x}}\right),
+    \shape{\vec{x} \oplus \vec{x}}
   \right) \\
@@
     X
-      \mmult{|\vec{x}|}
-    \Ident^2(|X|),
-    |\vec{x} \oplus \vec{x}|
+      \mmult{\shape{\vec{x}}}
+    \Ident^2(\shape{X}),
+    \shape{\vec{x} \oplus \vec{x}}
   \right) \\
@@
     X,
-    |\vec{x} \oplus \vec{x}|
+    \shape{\vec{x} \oplus \vec{x}}
   \right) \\
@@
 	&=
-	\Ident^3(|X|) \mmult{||X||} \Softmax(X)
+	\Ident^3(\shape{X}) \mmult{\shape{\shape{X}}} \Softmax(X)
   -\Softmax(X) \mmult{0} \Softmax(X) \\
 	&=
-	\left(\Ident^3(|X|) - \Softmax(X) \mmult{0} \Ident^2(|X|) \right)
-	\mmult{||X||} \Softmax(X)
+	\left(\Ident^3(\shape{X}) - \Softmax(X) \mmult{0} \Ident^2(\shape{X}) \right)
+	\mmult{\shape{\shape{X}}} \Softmax(X)
 \end{align*}
@@
 			\frac{d \exp(X)}{dX}
-			,|\vec{x}|
+			,\shape{\vec{x}}
 		\right)
-		,|\left<\right> \oplus \vec{x}|
+		,\shape{\left<\right> \oplus \vec{x}}
 	\right) \\
@@
 			\frac{d \exp(X)}{dX}
-			,|\vec{x}|
+			,\shape{\vec{x}}
 		\right)
-		,|\vec{x}|
+		,\shape{\vec{x}}
 	\right) \\
@@
 		\Tran\left(
-			\Ident^3(|X|) \mmult{||X||} \exp(X)
-			,|\vec{x}|
+			\Ident^3(\shape{X}) \mmult{\shape{\shape{X}}} \exp(X)
+			,\shape{\vec{x}}
 		\right)
-		,|\vec{x}|
+		,\shape{\vec{x}}
 	\right) \\
@@
 		\mmult{0}
-		1^{|X|}
-		\mmult{||X||}
-		\Ident^3(|X|)
-		\mmult{||X||}
+		1^{\shape{X}}
+		\mmult{\shape{\shape{X}}}
+		\Ident^3(\shape{X})
+		\mmult{\shape{\shape{X}}}
 		\exp(X)
@@
 			\mmult{0}
-			\Ident^3(|X|) \mmult{||X||} \exp(X)
-		,|\vec{x}|
+			\Ident^3(\shape{X}) \mmult{\shape{\shape{X}}} \exp(X)
+		,\shape{\vec{x}}
 		\right)
-		,|\vec{x}|
+		,\shape{\vec{x}}
 	\right) \\
@@
 		\mmult{0}
-		\Ident^2(|X|)
-		\mmult{||X||}
+		\Ident^2(\shape{X})
+		\mmult{\shape{\shape{X}}}
 		\exp(X)
@@
 		\Tran\left(
-			\Ident^3(|X|) \mmult{||X||} \Softmax(X)
-		,|\vec{x}|
+			\Ident^3(\shape{X}) \mmult{\shape{\shape{X}}} \Softmax(X)
+		,\shape{\vec{x}}
 		\right)
-	,|\vec{x}|
+	,\shape{\vec{x}}
 	\right) \\
@@
 	\Tran\left(
-		\Ident^3(|X|) \mmult{||X||} \Softmax(X)
-		,2|\vec{x}|
+		\Ident^3(\shape{X}) \mmult{\shape{\shape{X}}} \Softmax(X)
+		,2\shape{\vec{x}}
 	\right) \\
 	&=&&
-	\Ident^3(|X|) \mmult{||X||} \Softmax(X)
+	\Ident^3(\shape{X}) \mmult{\shape{\shape{X}}} \Softmax(X)
   -\Softmax(X) \mmult{0} \Softmax(X) \\
 	&=&&
-	\Ident^3(|X|) \mmult{||X||} \Softmax(X)
-	-\Softmax(X) \mmult{0} \Ident^2(|X|) \mmult{||X||} \Softmax(X) \\
+	\Ident^3(\shape{X}) \mmult{\shape{\shape{X}}} \Softmax(X)
+	-\Softmax(X) \mmult{0} \Ident^2(\shape{X}) \mmult{\shape{\shape{X}}} \Softmax(X) \\
 	&=&&
-	\left(\Ident^3(|X|) - \Softmax(X) \mmult{0} \Ident^2(|X|) \right)
-	\mmult{||X||} \Softmax(X)
+	\left(\Ident^3(\shape{X}) - \Softmax(X) \mmult{0} \Ident^2(\shape{X}) \right)
+	\mmult{\shape{\shape{X}}} \Softmax(X)
 \end{alignat*}
@@
 	\left\{
-		\left(\Ident^3(|X|) - \Softmax(X) \mmult{0} \Ident^2(|X|) \right)
-		\mmult{||X||} \Softmax(X)
+		\left(\Ident^3(\shape{X}) - \Softmax(X) \mmult{0} \Ident^2(\shape{X}) \right)
+		\mmult{\shape{\shape{X}}} \Softmax(X)
 	\right\}
@@
 	\sum_{\forall \bar{x}_3}
-	\left(\Ident^3(|X|) - \Softmax(X) \mmult{0} \Ident^2(|X|) \right)
+	\left(\Ident^3(\shape{X}) - \Softmax(X) \mmult{0} \Ident^2(\shape{X}) \right)
 	[\bar{x}_1 \oplus \bar{x}_2 \oplus \bar{x}_3]
@@
 connections between them, $W_i$. Finally, there is an activation function
-$a(X) : \mathbb{R}^{|X|} \to \mathbb{R}^{|X|}$ which is an elementwise function,
+$a(X) : \mathbb{R}^{\shape{X}} \to \mathbb{R}^{\shape{X}}$ which is an elementwise function,
 often the sigmoid function, or ReLU, or some variant thereof. It's unimportant for this
@@
 
-\[ L_i = a(L_{i-1} \mmult{||L_{i-1}||} W_i) \]
+\[ L_i = a(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \]
 \end{definition}
 
+\begin{landscape}
 \begin{theorem}[Derivative of FFNN Layer]
-\[ \frac{dL_i}{dW_j} = ? \]
+\[
+  \frac{dL_i}{dW_j}
+	= \left\{
+  \begin{array}{ll}
+		0 & \mbox{if } i < j \\
+    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
+    \mmult{\shape{\shape{L_i}}}
+    \left(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} \Ident^2(\shape{W_i})\right)
+	  & \mbox{if } i = j \\
+    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
+    \mmult{\shape{\shape{L_i}}}
+    \Tran(W_i, \shape{\shape{L_{i-1}}})
+    \mmult{\shape{\shape{L_{i-1}}}}
+    \frac{d L_{i-1}}{dW_j}
+		& \mbox{if } i > j
+  \end{array}
+  \right.
+\]
 \end{theorem}
@@
 $L_i$ does not depend on $W_j$, so 
-$\forall \bar{x} \in \Dim(|L_i|), \bar{y} \in \Dim(|W_j|)$
+$\forall \bar{x} \in \Dim(\shape{L_i}), \bar{y} \in \Dim(\shape{W_j})$
 $\frac{dL_i}{dW_j} = 0$
@@
 \begin{ppart} $i = j$
-TODO
+Then note that $\frac{dL_{i-1}}{dW_j} = 0$ because $L_{i-1}$ does not
+depend on $W_j$. So we can just use the chain rule and the right multiplicative rule to find that,
+\[
+  \frac{dL_i}{dW_{j=i}} =
+    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
+    \mmult{\shape{\shape{L_i}}}
+    \left(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} \Ident^2(\shape{W_i})\right)
+\]
 \end{ppart}
 \begin{ppart} $i > j$
-TODO
+In this case, $L_{i-1}$ depends on $W_j$ but $W_i$ does not. So we can use the chain rule and the
+left multiplicative rule to find that,
+\begin{align*}
+  \frac{dL_i}{dW_{j<i}}
+  &=
+    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
+    \mmult{\shape{\shape{L_i}}}
+    \frac{d (L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i)}{dW_j} \\
+  &=
+    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
+    \mmult{\shape{\shape{L_i}}}
+    \left(
+      \frac{d (L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i)}{dL_{i-1}}
+      \mmult{\shape{\shape{L_{i-1}}}}
+      \frac{dL_{i-1}}{dW_j}
+    \right) \\
+  &=
+    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
+    \mmult{\shape{\shape{L_i}}}
+    \left(
+      \left(
+        \Ident^2(\shape{L_{i}})
+        \mmult{\shape{\shape{W_i}}-\shape{\shape{L_{i-1}}}}
+        \Tran(W_i, \shape{\shape{L_{i-1}}})
+      \right)
+      \mmult{\shape{\shape{L_{i-1}}}}
+      \frac{d L_{i-1}}{dW_j}
+    \right) \\
+  &=
+    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
+    \mmult{\shape{\shape{L_i}}}
+    \left(
+      \left(
+        \Ident^2(\shape{L_{i}})
+        \mmult{\shape{\shape{L_i}}}
+        \Tran(W_i, \shape{\shape{L_{i-1}}})
+      \right)
+      \mmult{\shape{\shape{L_{i-1}}}}
+      \frac{d L_{i-1}}{dW_j}
+    \right) \\
+  &=
+    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
+    \mmult{\shape{\shape{L_i}}}
+    \left(
+      \Tran(W_i, \shape{\shape{L_{i-1}}})
+      \mmult{\shape{\shape{L_{i-1}}}}
+      \frac{d L_{i-1}}{dW_j}
+    \right) \\
+  &=
+    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
+    \mmult{\shape{\shape{L_i}}}
+    \Tran(W_i, \shape{\shape{L_{i-1}}})
+    \mmult{\shape{\shape{L_{i-1}}}}
+    \frac{d L_{i-1}}{dW_j}
+\end{align*}
 \end{ppart}
 \end{proof}
+\end{landscape}
 
@@
   F\left(A+\frac{i}{n}(B-A)\right)
-  \mmult{||X||}
+  \mmult{\shape{\shape{X}}}
   \left(\frac{B-A}{n}\right)
@@
 Maybe... well look at it this way. $F(X)$ is a function which produces some,
-afine-like transformation multimatrix for multimatricies of shape $|X|$,
-since it must have a right hand shape of $\ldots \oplus |X|$. This integration
+afine-like transformation multimatrix for multimatricies of shape $\shape{X}$,
+since it must have a right hand shape of $\ldots \oplus \shape{X}$. This integration
 occures over a linear path of $X$ as it moves from $A$ to $B$ applying that
@@
       F\left(A+\frac{i}{n}(X-A)\right)
-      \mmult{||Y||}
+      \mmult{\shape{\shape{Y}}}
       \left(\frac{X-A}{n}\right)
@@
         F\left(A+\frac{i}{n}(X-A)\right)
-        \mmult{||Y||}
+        \mmult{\shape{\shape{Y}}}
         \left(\frac{X-A}{n}\right)
@@
           F\left(A+\frac{i}{n}(X-A)\right)
-          \mmult{||Y||}
+          \mmult{\shape{\shape{Y}}}
           \left(\frac{X-A}{n}\right)
@@
         F\left(A+\frac{i}{n}(X-A)\right)
-          \mmult{||Y||}
+          \mmult{\shape{\shape{Y}}}
           \frac{d \left(\frac{X-A}{n}\right)}{dX}
@@
         \Tran\left(
-          \Tran\left(\frac{X-A}{n}, ||Y||\right)
-          \mmult{||Y||}
+          \Tran\left(\frac{X-A}{n}, \shape{\shape{Y}}\right)
+          \mmult{\shape{\shape{Y}}}
           \Tran\left(\frac{
             d \left\{F\left(A+\frac{i}{n}(X-A)\right)\right\}
-          }{dX}, |\vec{f}|\right),
-          |\vec{x} \oplus \vec{x}|
+          }{dX}, \shape{\vec{f}}\right),
+          \shape{\vec{x} \oplus \vec{x}}
         \right) \\
@@
         F\left(A+\frac{i}{n}(X-A)\right)
-          \mmult{||Y||}
-          \frac{1}{n}\Ident^2(|X|)
+          \mmult{\shape{\shape{Y}}}
+          \frac{1}{n}\Ident^2(\shape{X})
         \\&&&+
@@
           \frac{X-A}{n}
-          \mmult{||Y||}
+          \mmult{\shape{\shape{Y}}}
           \Tran\left(
             \frac{dF(X)}{dX}
-            \mmult{|X|}
-            \frac{i}{n}\Ident^2(|X|), |\vec{f}|\right),
-          |\vec{x} \oplus \vec{x}|
+            \mmult{\shape{X}}
+            \frac{i}{n}\Ident^2(\shape{X}), \shape{\vec{f}}\right),
+          \shape{\vec{x} \oplus \vec{x}}
         \right) \\
@@
           \frac{X-A}{n}
-          \mmult{||Y||}
+          \mmult{\shape{\shape{Y}}}
           \Tran\left(
             \frac{i}{n}\frac{dF(X)}{dX}
-            , |\vec{f}|\right),
-          |\vec{x} \oplus \vec{x}|
+            , \shape{\vec{f}}\right),
+          \shape{\vec{x} \oplus \vec{x}}
         \right)
@@
 	=
-	F(X) \mmult{||X||} H
+	F(X) \mmult{\shape{\shape{X}}} H
 \]
@@
 \begin{solution}
-\[ \left|\frac{dF}{dX}\right| = \left<6,7,3,7,2\right> \]
+\[ \shape{\frac{dF}{dX}} = \left<6,7,3,7,2\right> \]
 \end{solution}
@@
 \begin{solution}
-\[ \left|\frac{df}{dX}\right| = |X| = \left<2,3,2\right> \]
+\[ \shape{\frac{df}{dX}} = \shape{X} = \left<2,3,2\right> \]
 \[ \frac{df}{dX}[\bar{v}] = 1 \]
@@
 Self Derivative (Thm. \ref{self_derivative})
-\[ \frac{dX}{dX} = \Ident^2(|X|) \]
+\[ \frac{dX}{dX} = \Ident^2(\shape{X}) \]
 \end{drule}
@@
 Elementwise Derivative (Thm. \ref{elementwise_derivative})
-\[ \frac{dM(X)}{dX} = \Ident^3(|X|) \mmult{||X||} M'(X) \]
+\[ \frac{dM(X)}{dX} = \Ident^3(\shape{X}) \mmult{\shape{\shape{X}}} M'(X) \]
 \end{drule}
@@
 (Thm. \ref{tran_derivative})
-\[ |X| = \vec{l} \oplus \vec{r} \]
+\[ \shape{X} = \vec{l} \oplus \vec{r} \]
 Implies,
 \[
- \frac{d\Tran(X, |\vec{l}|)}{dX} =
- \Tran(\Ident^2(\vec{r}) \mmult{0} \Ident^2(\vec{l}), |\vec{r}|)
+ \frac{d\Tran(X, \shape{\vec{l}})}{dX} =
+ \Tran(\Ident^2(\vec{r}) \mmult{0} \Ident^2(\vec{l}), \shape{\vec{r}})
 \]
@@
 (Thm. \ref{right_mult_derivative})
-\[ \frac{d(A \mmult{n} X)}{dX} = A \mmult{n} \Ident^2(|X|) \]
+\[ \frac{d(A \mmult{n} X)}{dX} = A \mmult{n} \Ident^2(\shape{X}) \]
 \end{drule}
@@
 (Thm. \ref{left_mult_derivative})
-\[ \frac{d(X \mmult{n} A)}{dX} = \Ident^2(|X \mmult{n} A|) \mmult{n} \Tran(A, n) \]
+\[ \frac{d(X \mmult{n} A)}{dX} = \Ident^2(\shape{X \mmult{n} A}) \mmult{\shape{\shape{A}}-n} \Tran(A, n) \]
 \end{drule}
@@
 
-Let $|F| = \vec{f} \oplus \vec{c}$, $|G| = \vec{c} \oplus \vec{g}$,
-and $|X| = \vec{x}$. Then,
-\begin{align*}
- \frac{d\left(F(X) \mmult{|\vec{c}|} G(X)\right)}{dX} =&
- F(X) \mmult{|\vec{c}|} \frac{dG(X)}{dX} + \\
+Let $\shape{F} = \vec{f} \oplus \vec{c}$, $\shape{G} = \vec{c} \oplus \vec{g}$,
+and $\shape{X} = \vec{x}$. Then,
+\begin{align*}
+ \frac{d\left(F(X) \mmult{\shape{\vec{c}}} G(X)\right)}{dX} =&
+ F(X) \mmult{\shape{\vec{c}}} \frac{dG(X)}{dX} + \\
  &\Tran\left(
-   \Tran(G(X), |\vec{c}|)
-     \mmult{|\vec{c}|}
-   \Tran\left(\frac{dF(X)}{dX}, |\vec{f}|\right),
-   |\vec{g} \oplus \vec{x}|
+   \Tran(G(X), \shape{\vec{c}})
+     \mmult{\shape{\vec{c}}}
+   \Tran\left(\frac{dF(X)}{dX}, \shape{\vec{f}}\right),
+   \shape{\vec{g} \oplus \vec{x}}
  \right)
@@
 (Thm. \ref{mmm_chain_rule})
-\[ \frac{dF(G(X))}{dX} = \frac{dF}{dG} \mmult{||G||} \frac{dG}{dX} \]
+\[ \frac{dF(G(X))}{dX} = \frac{dF}{dG} \mmult{\shape{\shape{G}}} \frac{dG}{dX} \]
 \end{drule}

### 2020-07-15 MMatrix/src/audio.cc
Started on audio processing.

@@ -1,0 +1,154 @@
+#include "audio.h"
+
+#include <limits>
+#include <string.h>
+#include <cmath>
+
+namespace audio {
+
+
+bool isBigEndian() {
+    union {
+        uint32_t i;
+        char c[4];
+    } bint = {0x01020304};
+
+    return bint.c[0] == 1; 
+}
+
+void ReadWavFile(std::istream& file, WavHdr* hdr, std::vector<double>* samples) {
+  if(isBigEndian()) {
+    throw std::runtime_error("This library is not supported on big endian systems.");
+  }
+
+  // Get file size and read header.
+  file.seekg(0, std::ios::end);
+  int fsize = file.tellg();
+  file.seekg(0);
+  if (fsize < sizeof(WavHdr)) {
+    throw std::runtime_error("Invalid file.");
+  }
+  file.read(reinterpret_cast<char*>(hdr), sizeof(WavHdr));
+  if (hdr->AudioFormat != 1) {
+    throw std::runtime_error("Unsupported wav compression format.");
+  }
+
+  // Calculate sample size from header.
+  int chanSampleSize;
+  if (hdr->bitsPerSample == 8 || hdr->bitsPerSample == 16) {
+    chanSampleSize = hdr->bitsPerSample/8;
+  } else {
+    throw std::runtime_error("Unexpected bits per sample.");
+  }
+  int sampleSize = hdr->NumOfChan*chanSampleSize;
+
+  // Validate header, file size and expected samples 
+  // Subchunk2Size  == NumSamples * NumChannels * BitsPerSample/8
+  // NumSamples == Subchunk2Size / sampleSize
+  if (hdr->Subchunk2Size % sampleSize != 0) {
+    throw std::runtime_error("Invalid Subchunk2Size in wav header.");
+  }
+  if (hdr->Subchunk2Size + sizeof(WavHdr) > fsize) {
+    throw std::runtime_error("Invalid Subchunk2Size for wav file size.");
+  }
+  int expectedSamples = hdr->Subchunk2Size/sampleSize;
+   
+  // Read the samples
+  samples->reserve(expectedSamples);
+  union {
+    uint8_t b8;
+    int16_t b16;
+  } channelSample;
+  double sample;
+  // This is a tremendiously inefficieint way to read a file.
[…]

### 2020-07-15 MMatrix/src/audio.h

@@ -1,0 +1,47 @@
+#ifndef AUDIO_H
+#define AUDIO_H
+
+#include <cstdint>
+#include <iostream>
+#include <vector>
+
+namespace audio {
+
+typedef struct WavHdr {
+  /* RIFF Chunk Descriptor */
+  uint8_t         RIFF[4];        // RIFF Header Magic header
+  uint32_t        ChunkSize;      // RIFF Chunk Size
+  uint8_t         WAVE[4];        // WAVE Header
+  /* "fmt" sub-chunk */
+  uint8_t         fmt[4];         // FMT header
+  uint32_t        Subchunk1Size;  // Size of the fmt chunk
+  uint16_t        AudioFormat;    // Audio format 1=PCM,6=mulaw,7=alaw,     257=IBM Mu-Law, 258=IBM A-Law, 259=ADPCM
+  uint16_t        NumOfChan;      // Number of channels 1=Mono 2=Stereo
+  uint32_t        SamplesPerSec;  // Sampling Frequency in Hz
+  uint32_t        bytesPerSec;    // bytes per second
+  uint16_t        blockAlign;     // 2=16-bit mono, 4=16-bit stereo
+  uint16_t        bitsPerSample;  // Number of bits per sample
+  /* "data" sub-chunk */
+  uint8_t         Subchunk2ID[4]; // "data"  string
+  uint32_t        Subchunk2Size;  // Sampled data length
+} WavHdr;
+
+bool isBigEndian();
+
+void ReadWavFile(std::istream& file, WavHdr* hdr, std::vector<double>* samples);
+
+void WriteWavFile(std::ostream& file, uint32_t sampleRate, int bytesPerSample,
+    const std::vector<double>& samples);
+
+namespace internal {
+
+std::vector<double> GetFrequencyDomain(uint32_t sampleRate);
+
+void fourier_transform(std::vector<double> samples, std::vector<double> frequencies, int delta);
+
+}  // namespace internal
+
+
+}  // namespace audio
+
+#endif

### 2020-07-15 MMatrix/src/wav_example.cc

@@ -1,0 +1,95 @@
+#include "audio.h"
+#include <iostream>
+#include <string>
+#include <fstream>
+#include <cstdint>
+
+using std::cin;
+using std::cout;
+using std::endl;
+using std::fstream;
+using std::string;
+using namespace audio;
+
+// Function prototypes
+int getFileSize(FILE* inFile);
+
+int main(int argc, char* argv[])
+{
+    WavHdr wavHeader;
+    int headerSize = sizeof(WavHdr), filelength = 0;
+
+    const char* filePath;
+    string input;
+    if (argc <= 1)
+    {
+        cout << "Input wave file name: ";
+        cin >> input;
+        cin.get();
+        filePath = input.c_str();
+    }
+    else
+    {
+        filePath = argv[1];
+        cout << "Input wave file name: " << filePath << endl;
+    }
+
+    FILE* wavFile = fopen(filePath, "r");
+    if (wavFile == nullptr)
+    {
+        fprintf(stderr, "Unable to open wave file: %s\n", filePath);
+        return 1;
+    }
+
+    //Read the header
+    size_t bytesRead = fread(&wavHeader, 1, headerSize, wavFile);
+    cout << "Header Read " << bytesRead << " bytes." << endl;
+    if (bytesRead > 0)
+    {
+        //Read the data
+        uint16_t bytesPerSample = wavHeader.bitsPerSample / 8;      //Number     of bytes per sample
+        uint64_t numSamples = wavHeader.ChunkSize / bytesPerSample; //How many samples are in the wav file?
+        static const uint16_t BUFFER_SIZE = 4096;
+        int8_t* buffer = new int8_t[BUFFER_SIZE];
+        while ((bytesRead = fread(buffer, sizeof buffer[0], BUFFER_SIZE / (sizeof buffer[0]), wavFile)) > 0)
+        {
+            /** DO SOMETHING WITH THE WAVE DATA HERE **/
+            cout << "Read " << bytesRead << " bytes." << endl;
+        }
+        delete [] buffer;
+        buffer = nullptr;
+        filelength = getFileSize(wavFile);
+
+        cout << "File is                    :" << filelength << " bytes." << endl;
+        cout << "RIFF header                :" << wavHeader.RIFF[0] << wavHeader.RIFF[1] << wavHeader.RIFF[2] << wavHeader.RIFF[3] << endl;
[…]

### 2020-07-15 MMatrix/test/test_audio.cc

@@ -1,0 +1,52 @@
+#include "audio.h"
+
+#include <cmath>
+#include <fstream>
+#include <iostream>
+#include <sstream>
+
+using namespace audio;
+
+const double pi = std::acos(-1);
+
+void TestWriteRead() {
+  std::cout << "Testing Write & Read..." << std::endl;
+
+  std::stringstream ss;
+
+  // Write out a wave file to ss
+  int sampleRate = 44100;
+  std::vector<double> samplesIn;
+  for (double t = 0; t < 10; t+=1.0/sampleRate) {
+    // A4 frequency is 440
+    samplesIn.push_back(0.5*std::sin(2*pi*440*t));
+  }
+
+  WriteWavFile(ss, sampleRate, 2, samplesIn);
+
+  // Read the wave file in ss
+  ss.seekg(0);
+  WavHdr hdr;
+  std::vector<double> samplesOut;
+  ReadWavFile(ss, &hdr, &samplesOut);
+  if (samplesOut.size() != samplesIn.size()) {
+    std::cerr << "Unexpected samples count: " << samplesOut.size() << std::endl;
+    exit(1);
+  }
+
+  // Verify rough sample consistency (will vary due to compression artifacts).
+  for (int i = 0; i < 10; i++) {
+    if (std::abs(samplesIn[i]-samplesOut[i]) > 0.0001) {
+      std::cerr << "Sample divation out of bounds: " << i
+          << " (" << samplesIn[i] << ", " << samplesOut[i] << ")"
+          << std::endl;
+      exit(0);
+    }
+  }
+}
+
+int main() {
+  TestWriteRead();
+  std::cout << "All tests pass." << std::endl;
+  return 0;
+}

### 2020-08-06 Math/book.tex
About to update computer, saving work.

@@
 Now, not knowing what else to do with the results, I've written this book
-about my amature exploration into multidimensional matricies -
-multimatricies - and how they can simplify derivatives of matrix equations.
+about my exploration into multidimensional matricies,
+multimatricies, and how they can elucidate derivatives of matrix equations.
 
@@
 
-Let one matrix $X$ represent the level of scientific education level of a set of
-undergraduates who work in a densely packed 3 by 5 office.
-Then let $B$ represent the belief each of those undergradutes has in a higher power.
+Let's say we have a small class of undergraduates packed, conveniently in a 3 by 5
+grid. We'll let $X$ be the matrix representing number of semesters of science
+classes each of those student has taken.
+Then let $B$ represent the belief each of those undergradutes has in a higher power,
+thier BHP if you will.
 
@@
 
-Suppose the shape of these two matricies are defined,
-$\shape{B} = \shape{X} = \left< 3,5 \right>$.
-And each element of $B$ will be the sine of the corresponding element of
+Let's formally state the shape of these two matricies,
+$\shape{B} = \shape{X} = \left< 3,5 \right>$. (Throughout this work, I'll be using
+$\shape{M}$ to denote the shape of $M$ rather than the determinate because, frankly, it
+is just comes up more frequently.)
+Each element of $B$ will be the sine of the corresponding element of
 $X$. That is, \[B_{r,c} = \sin(X_{r,c})\]
@@
 $\partial B_{r_1, c_1}/\partial X_{r_2, c_2}$ is defined as the rate of change of
-\textit{one} undergraduate's belief in a higher power with respect to \textit{one}
+\textit{one} undergraduate's BPH with respect to \textit{one}
 undergraduate's education level - it only represents a change to part of the whole
@@
 \]
-Every student's belief in a higher power changes with respect to their own
+Every student's BHP changes with respect to their own
 scientific education level but does not change with respect to other students'
@@
 a row and column but each uniquely indexed cell in this object may have a
-unique value, just like a standard two dimensional matrix. Let's define this
-bit of notation formaly.
+unique value, just like a standard two dimensional matrix.
+
+Programmers might call this object a `tensor' but mathematitians might
+scream at those same programmers, ``WE ALREADY HAVE A DEFINITION OF A TENSOR! DIE!''
+And the ensuing war might wipe out most of the eastern seaboard and would
+certainly not be conductive to a reasonable discussion. To avoid such a
+confrontation I'll be using the incredibly imaginative term `multimatrix'.
+
+Let's define this bit of notation formaly.
 
@@
 
+\begin{definition}[Scalar Filled Multimatrices]
+For convenience, I'll often refer to multimatricies filled with a single value,
+$s \in \mathbb{R}$,
+using the notation $s^{\vec{x}}$ where $\vec{x}$ is some multimatrix shape. So that
+$\shape{s^{\vec{x}}} = \vec{x}$ and for all $\bar{x} \in \Dim(\vec{x})$,
+\[ s^{\vec{x}}[\bar{x}] = s \]
+
+For example, $0^{\left<2,3,2\right>}$ is a multimatrix with shape $\left<2,3,2\right>$
+that is filled with zeros.
+\end{definition}
+
 Now that you seem to understand.. Don't give me that look... well if you're confused
-you should have been asking questions, moving on. Now that \textit{most of you}
-seem to have understood, I'll give you a theorem to prove.
+you should have been asking questions. I don't have time to backtrack now.
+Well, seeing as \textit{most of you} seem to have understood, I'll give you a theorem to prove.
 
@@
 
-Going back to our original motivating problem, we (that is to say, myself and my
-split personalities whom I reference as to give my writing the percieved authority
+Going back to our original motivating problem, we (that is to say, myself and the voices
+in my head whom I reference as to give my writing the percieved authority
 of more than one author) can express our derivative notation thusly,
@@
 
-The multiplication of traditional matricies is a calculation that, when first
-encoutered, inspires thoughts of omnicide.
+The multiplication of traditional matricies is often considered a rather confusing
+proposition, especially when one first encounters it.
 
@@
 \]
-But, $(B \mmult{2} C)[\bar{x}] = 0$ so $(A \mmult{2} (B \mmult{2} C))[\bar{x}] = 0$
+But, $B \mmult{2} C = 0^{\left<2,2,2\right>}$ so $A \mmult{2} (B \mmult{2} C) = 0^{\left<2,2,2\right>}$
 Which goes to show that even though both $(A \mmult{2} B) \mmult{2} C$ and
@@
 Let $A$, $B$, and $\vec{x}$ be as described above. Notice that then $\shape{A \mmult{\shape{\vec{x}}} B}$
-results in a zero dimensional multimatrix - a multimatrix with one element which is effectively
-just a scalar.
-\begin{align*}
-(A \mmult{\shape{\vec{x}}} B)[\{\}]
+results in a zero dimensional multimatrix - a multimatrix with one element which is just a scalar.
+\begin{align*}
+(A \mmult{\shape{\vec{x}}} B)[\left<\right>]
   &= \sum_{\forall \bar{x} \in \Dim(\vec{x})} A[\bar{x}]B[\bar{x}] \\
   &= \sum_{\forall \bar{x} \in \Dim(\vec{x})} B[\bar{x}]A[\bar{x}] \\
-  &= (B \mmult{\shape{\vec{x}}} A)[\{\}]
+  &= (B \mmult{\shape{\vec{x}}} A)[\left<\right>]
 \end{align*}
@@
 $\vec{v}$. This $\Ident^n(\vec{v})$ is a multimatrix with shape,
-\[ \shape{\Ident^n(\vec{v})} = \bigoplus_{i \in [1, n]} \vec{v} \]
+\[ \shape{\Ident^n(\vec{v})} = \bigoplus_{i = 1}^n \vec{v}  = n * \vec{v} \]
 That is, it's shape is $n$ successive concatinations of $\vec{v}$.
 Let each element of $\Ident^n(\vec{v})$ is defined as,
-\[ \forall \bar{v_1}, \bar{v_2}, \ldots, \bar{v_n} \text{ each in } \Dim(\vec{v}) : \]
-\[
- \Ident^n(\vec{v})[\bar{v_1}, \bar{v_2}, \ldots, \bar{v_n}]
+\[ \forall \bar{v_1}, \bar{v_2}, \ldots, \bar{v_n} \text{ each in } \Dim(\vec{v}) \]
+\[ \bigoplus_{i = 1}^n \bar{v_i} = \bar{v_I} \]
+\[
+ \Ident^n(\vec{v})[\bar{v_I}]
  = \left\{
@@
 That definition seems rather arbitrary but stick with me, I know what I'm
-talking about. I've got a \sout{doctorate}
-masters degree in \sout{mathematics} I mean \sout{a real engineering field}, fine, software
-engineering. Whatever. Just look at how the
-square identity it relates to a multiplication operation.
+talking about. What credentials do I have? Totally irrelevant. Stop asking questions.
+
+Now, please direct your attention to this example of how the square identity relates
+to a multiplication operation.
 
@@
 
+Multimatrix identities also have the nice property of being communicative when multiplied
+across multiples of their base shape and completely engulfing a smaller multimatrix.
+
+\begin{theorem}[Communicativity of Multiplicative Identities]
+Let $X$ be a multimatrix of shape $k * \vec{x}$ where $k$ is some natural number.
+Remember (from the identity definition) that the $*$ operator denote successive concatenations of a vector so that,
+\[ k * \vec{x} = \bigoplus_{i=1}^k \vec{x} \]
+Then for any $n \ge k$,
+\[ X \mmult{k \shape{\vec{x}}} \Ident^n(\vec{x}) = \Ident^n(\vec{x}) \mmult{k \shape{\vec{x}}} X \]
+\end{theorem}
+\begin{proof}
+Given that $\shape{X} = k * \vec{x}$ we know that
+$\shape{X \mmult{k \shape{\vec{x}}} \Ident^n(\vec{x})} = (n-k) * \vec{x}$.
+Let $\bar{x}_1, \bar{x}_2 \ldots \bar{x}_{n-k}$ each be index vectors in $\Dim(\vec{x})$,
+for simplicity denoted as,
+\[ \bar{x}_I = \bigoplus_{i=1}^{n-k} \bar{x}_i \]
+We'll also need a similarly denoted $\bar{y}_1 \ldots \bar{y}_k$ for the free indicies of
+the sum below and that shall also be represented as,
+\[ \bar{y}_J = \bigoplus_{j=1}^{k} \bar{y}_j \]
+Then we know that,
+\[
+  \left(X \mmult{k \shape{\vec{x}}} \Ident^n(\vec{x}) \right)[\bar{x}_I]
+  = \sum_{\forall \bar{y}_J} X[\bar{y}_J] \Ident^n(\vec{x})[\bar{y}_J \oplus \bar{x}_I]
+\]
+Notice that $\Ident^n(\vec{x})[\bar{y}_J \oplus \bar{x}_I] = \Ident^n(\vec{x})[\bar{x}_I \oplus \bar{y}_J]$
+since the sub index vectors will always either be equal or not equal, $1$ or $0$, their order doesnt matter.
+So,
+\begin{align*}
+  \left(X \mmult{k \shape{\vec{x}}} \Ident^n(\vec{x}) \right)[\bar{x}_I]
+  &= \sum_{\forall \bar{y}_J} X[\bar{y}_J] \Ident^n(\vec{x})[\bar{x}_I \oplus \bar{y}_J] \\
+  &= \sum_{\forall \bar{y}_J} \Ident^n(\vec{x})[\bar{x}_I \oplus \bar{y}_J] X[\bar{y}_J] \\
+  &= \left(\Ident^n(\vec{x}) \mmult{k \shape{\vec{x}}} X \right)[\bar{x}_I]
+\end{align*}
+\end{proof}
+
 The square identity also pops up in the derivative of a multimatrix
@@
 The cubic identity, strangely enough, appear in the derivative of elementwise
-functions. Which is one of the reaspons I needed to expand my definition of
+functions. Which is one of the reasons I needed to expand my definition of
 identities beyond $\Ident^2(\vec{v})$.
@@
 By the definition of a multimatrix derivative,
-\[ \forall \bar{m} \in \Dim(\shape{M}), \bar{x} \in \Dim(\shape{X}) : \]
+\[ \forall \bar{m}, \bar{x} \in \Dim(\shape{X}) : \]
 \begin{align*}
@@
 
+Another important fact about the identity multimatrix is that it can be
+reduced by multiplication with a $1^{\vec{s}}$ matrix.
+
+\begin{theorem}[Identity Reduction]
+Let $\vec{x}$ be a valid multimatrix shape and $m$ and $n$ be natural numbers
+such that $m < n$.
+Remember (from the identity definition) that the $*$ operator denote successive
+concatenations of a vector so that,
+\[ m*\vec{x} = \bigoplus_{i=1}^{m} \vec{x} \]
+Then,
+\[1^{m*\vec{x}} \mmult{m \shape{\vec{x}}} \Ident^n(\vec{x}) = \Ident^{n-m}(\vec{x})\]
+and,
+\[\Ident^n(\vec{x}) \mmult{m \shape{\vec{x}}} 1^{m*\vec{x}} = \Ident^{n-m}(\vec{x})\]
+\end{theorem}
+\begin{proof}
+\begin{ppart}
+Let $\bar{x}_1, \bar{x}_2 \ldots  \bar{x}_{n-m}$ each in $\Dim(\vec{x})$ and let
+\[\bigoplus_{i = 1}^{n-m} \bar{x}_i = \bar{x}_I \]
+In the sum below, let $\bar{y}_1, \bar{y}_2 \ldots \bar{y}_m$ each in $\Dim(\vec{x})$ be the
+free indicies denoted,
+\[\bigoplus_{j = 1}^m \bar{y}_j = \bar{y}_J \]
+Then,
+\begin{align*}
+  1^{m*\vec{x}} \mmult{m \shape{\vec{x}}} \Ident^n(\vec{x}) [\bar{x}_I] &=
+  \sum_{\forall \bar{y}_J} 1^{m*\vec{x}}[\bar{y}_J] \Ident^n(\vec{x})[\bar{y}_J \oplus \bar{x}_I] \\
+  &=
+  \sum_{\forall \bar{y}_J} (1) \Ident^n(\vec{x})[\bar{y}_J \oplus \bar{x}_I] \\
+  &=
+  \sum_{\forall \bar{y}_J} \Ident^n(\vec{x})[\bar{y}_J \oplus \bar{x}_I] \\
+  &=
+  \left(
+    \sum_{\forall \bar{y}_J, \text{ each } \bar{y}_i \ne \bar{x}_1} \Ident^n(\vec{x})[\bar{y}_J \oplus \bar{x}_I]
+  \right)
+  + \Ident^n(\vec{x})\left[\left( \bigoplus_{j=1}^m \bar{x}_1 \right) \oplus \bar{x}_I\right] \\
+  &= 0 + \Ident^n(\vec{x})\left[\left( \bigoplus_{j=1}^m \bar{x}_1 \right) \oplus \bar{x}_I\right] \\
+  &= \Ident^{n-m}(\vec{x})[\bar{x}_I]
+\end{align*}
+\end{ppart}
+\begin{ppart}
+Let $\bar{x}_1, \bar{x}_2 \ldots \bar{x}_{n-m}$ each in $\Dim(\vec{x})$ and let
+\[\bigoplus_{i = 1}^{n-m} \bar{x}_i = \bar{x}_I \]
+In the sum below, let $\bar{y}_1, \bar{y}_2 \ldots \bar{y}_m$ each in $\Dim(\vec{x})$ be the
+free indicies denoted,
+\[\bigoplus_{j = 1}^m \bar{y}_j = \bar{y}_J \]
+Then,
+\begin{align*}
+  \Ident^n(\vec{x}) \mmult{m \shape{\vec{x}}} 1^{m*\vec{x}} [\bar{x}_I] &=
+  \sum_{\forall \bar{y}_J} \Ident^n(\vec{x})[\bar{x}_I \oplus \bar{y}_J] 1^{m*\vec{x}}[\bar{y}_J] \\
+  &=
+  \sum_{\forall \bar{y}_J} \Ident^n(\vec{x})[\bar{x}_I \oplus \bar{y}_J] (1) \\
+  &=
+  \sum_{\forall \bar{y}_J} \Ident^n(\vec{x})[\bar{x}_I \oplus \bar{y}_J] \\
+  &=
+  \left(
+    \sum_{\forall \bar{y}_J, \text{ each } \bar{y}_i \ne \bar{x}_1} \Ident^n(\vec{x})[\bar{x}_I \oplus \bar{y}_J]
+  \right)
+  + \Ident^n(\vec{x})\left[\bar{x}_I \oplus \bigoplus_{j=1}^m \bar{x}_1 \right] \\
+  &= 0 + \Ident^n(\vec{x})\left[\bar{x}_I \oplus \bigoplus_{j=1}^m \bar{x}_1 \right] \\
+  &= \Ident^{n-m}(\vec{x})[\bar{x}_I]
+\end{align*}
+\end{ppart}
+\end{proof}
+
 Multimatrix identities also tend to cancel eachother out when multiplied by
@@
 \begin{proof}
-Consider that for some indicies
-$\{\bar{a_1}, \bar{a_2}, \ldots \bar{a}_{m-k}\}$
-and $\{\bar{b_1}, \bar{b_2}, \ldots \bar{b}_{n-k}\}$ where each
-$\bar{a_i} \in \Dim(\vec{x})$ and each $\bar{b_i} \in \Dim(\vec{x})$,
-
-\begin{align*}
-&\left( \Ident^m(\vec{x}) \mmult{k\shape{\vec{x}}} \Ident^n(\vec{x}) \right)
-[\bar{a_1} \oplus \bar{a_2} \oplus \ldots \bar{b_1} \oplus \bar{b_2} \oplus \ldots] = \\
-&\sum_{\forall \bar{c_1}, \bar{c_2}, \ldots \bar{c_k} \in \Dim(\vec{x})}
-\Ident^m(\vec{x})
-[\bar{a_1} \oplus \bar{a_2} \oplus \ldots \bar{c_1} \oplus \bar{c_2} \oplus \ldots]
-\Ident^n(\vec{x})
-[\bar{c_1} \oplus \bar{c_2} \oplus \ldots \bar{b_1} \oplus \bar{b_2} \oplus \ldots]
-\end{align*}
-
-Consider that $\Ident^m(\vec{x})
-[\bar{a_1} \oplus \bar{a_2} \oplus \ldots \bar{c_1} \oplus \bar{c_2} \oplus \ldots]$
-will be 0 whenever the any $\bar{c_i} \ne \bar{c_j}$ - we can simplify that to all
-the same $c$.
-
-\begin{align*}
-&\left( \Ident^m(\vec{x}) \mmult{k\shape{\vec{x}}} \Ident^n(\vec{x}) \right)
-[\bar{a_1} \oplus \bar{a_2} \oplus \ldots \bar{b_1} \oplus \bar{b_2} \oplus \ldots] = \\
-&\sum_{\forall \bar{c} \in \Dim(\vec{x})}
-\Ident^m(\vec{x})
-[\bar{a_1} \oplus \bar{a_2} \oplus \ldots \bar{c} \oplus \bar{c} \oplus \ldots]
-\Ident^n(\vec{x})
-[\bar{c} \oplus \bar{c} \oplus \ldots \bar{b_1} \oplus \bar{b_2} \oplus \ldots]
-\end{align*}
-
-Consider also that there can be at most one $\bar{c}$ for which
-$\bar{c} = \bar{a_1} = \bar{a_2} \ldots$. And since our right hand side is
-the sum of products of ones and zeros, we can therefore conclude it is either 1 or 0.
-
-We can futher reason that the right hand side can only be one when all of the
-$\bar{a_i}$ and all of the $\bar{b_i}$ equal $\bar{c}$. Furthermore, if all
-$\bar{a_i}$ and all $\bar{b_i}$ are equal then that $\bar{c}$ must exist since it can
-be any value in the range of all $\bar{a_i}$ and $\bar{b_i}$ and this is not a
-zero width multiplication ($k >= 1$). Therefore,
-
-\begin{align*}
+Consider that for some indicies vectors
+$\bar{a}_1, \bar{a}_2 \ldots \bar{a}_{m-k}$
+and $\bar{b}_1, \bar{b}_2 \ldots \bar{b}_{n-k}$ where each
+$\bar{a_i} \in \Dim(\vec{x})$ and each $\bar{b_i} \in \Dim(\vec{x})$.
+Now let,
+\[ \bigoplus_{i=1}^{m-k} \bar{a}_i = \bar{a}_I \]
+and,
+\[ \bigoplus_{j=1}^{n-k} \bar{b}_j = \bar{b}_J \]
+In the sums below we'll let $\bar{c}_1, \bar{c}_2 \ldots \bar{c}_k$ be free indicies
+each in $\Dim(\vec{x})$ and denote,
+\[ \bigoplus_{l = 1}^k \bar{c}_l = \bar{c}_K \]
+
+Then,
+\[
 \left( \Ident^m(\vec{x}) \mmult{k\shape{\vec{x}}} \Ident^n(\vec{x}) \right)
-[\bar{a_1} \oplus \bar{a_2} \oplus \ldots \bar{b_1} \oplus \bar{b_2} \oplus \ldots] =
-\left\{
+[\bar{a}_I \oplus \bar{b}_J] = 
+\sum_{\forall \bar{c}_K} \Ident^m(\vec{x}) [\bar{a}_I \oplus \bar{c}_K] \Ident^n(\vec{x}) [\bar{c}_K \oplus \bar{b}_J]
+\]
+
+Consider, for any $i$ if $\bar{a}_i \ne \bar{a}_1$ then
+$\Ident^m(\vec{x}) [\bar{a}_I \oplus \bar{c}_K]$ will always be zero.
+Similarly, if for any $j$, $\bar{b}_j \ne \bar{b}_1$ 
+$\Ident^n(\vec{x}) [\bar{c}_K \oplus \bar{b}_J]$ will always be zero.
+
+So, if we let, $\hat{a}_1 = (m-k) * \bar{a}_1$ and $\hat{b}_1 = (n-k) * \bar{b}_1$ then,
+\begin{align*}
+\left( \Ident^m(\vec{x}) \mmult{k\shape{\vec{x}}} \Ident^n(\vec{x}) \right) &
+[\bar{a}_I \oplus \bar{b}_J] = \\
+&\left\{
   \begin{array}{ll}
-    1 & \mbox{if } \bar{a_1} = \bar{a_2} = \ldots = \bar{b_1} = \bar{b_2} = \ldots \\
+    \sum_{\forall \bar{c}_K}
+      \Ident^m(\vec{x}) [\hat{a}_1 \oplus \bar{c}_K] 
+      \Ident^n(\vec{x}) [\bar{c}_K \oplus \hat{b}_1]
+    & \mbox{if } \forall i, j : \bar{a}_i = \bar{a}_1 \mbox{ and } \bar{b}_j = \bar{b}_1 \\
     0 & \mbox{otherwise}
@@
 
-Which is an identity matrix! And since the dimensional rules of multimatrix 
-multiplication show that,
-
-\[
- \shape{\shape{ \Ident^m(\vec{x}) \mmult{k\shape{\vec{x}}} \Ident^n(\vec{x}) }}
- =
- \shape{\shape{\Ident^m(\vec{x})}} + \shape{\shape{\Ident^n(\vec{x})}} - 2k\shape{\vec{x}}
-\]
-
-We've shown that,
-
-\[ \Ident^m(\vec{x}) \mmult{k\shape{\vec{x}}} \Ident^n(\vec{x}) = \Ident^{m+n-2k}(\vec{x}) \]
+Now, for any $\bar{c}_i$ that is not equal to $\bar{a}_1$, 
+$\Ident^m(\vec{x}) [\hat{a}_1 \oplus \bar{c}_K]$ will be zero.
+So, we only need to consider the part of the sum where $\bar{c}_K = k * \bar{a}_1$
+\begin{align*}
+\left( \Ident^m(\vec{x}) \mmult{k\shape{\vec{x}}} \Ident^n(\vec{x}) \right) &
+[\bar{a}_I \oplus \bar{b}_J] = \\
+&\left\{
+  \begin{array}{ll}
+    \Ident^m(\vec{x}) [\hat{a}_1 \oplus (k * \bar{a}_1)] 
+    \Ident^n(\vec{x}) [(k * \bar{a}_1) \oplus \hat{b}_1]
+    & \mbox{if } \forall i, j : \bar{a}_i = \bar{a}_1 \mbox{ and } \bar{b}_j = \bar{b}_1 \\
+    0 & \mbox{otherwise}
+  \end{array}
+\right.
+\end{align*}
+
+But $\Ident^m(\vec{x}) [\hat{a}_1 \oplus (k * \bar{a}_1)]$ is just $1$, so,
+\[
+\left( \Ident^m(\vec{x}) \mmult{k\shape{\vec{x}}} \Ident^n(\vec{x}) \right)
+[\bar{a}_I \oplus \bar{b}_J] =
+\left\{
+  \begin{array}{ll}
+    \Ident^n(\vec{x}) [(k * \bar{a}_1) \oplus \hat{b}_1]
+    & \mbox{if } \forall i, j : \bar{a}_i = \bar{a}_1 \mbox{ and } \bar{b}_j = \bar{b}_1 \\
+    0 & \mbox{otherwise}
+  \end{array}
+\right.
+\]
+
+And $\Ident^n(\vec{x}) [(k * \bar{a}_1) \oplus \hat{b}_1]$ is only $1$ when $\bar{a}_1 = \bar{b}_1$,
+\[
+\left( \Ident^m(\vec{x}) \mmult{k\shape{\vec{x}}} \Ident^n(\vec{x}) \right)
+[\bar{a}_I \oplus \bar{b}_J] =
+\left\{
+  \begin{array}{ll}
+    1 & \mbox{if } \forall i, j : \bar{a}_i = \bar{a}_1 \mbox{ and } \bar{b}_j = \bar{a}_1 \\
+    0 & \mbox{otherwise}
+  \end{array}
+\right.
+\]
+
+Which is exactly equal the result we were looking for,
+\[
+  \left( \Ident^m(\vec{x}) \mmult{k\shape{\vec{x}}} \Ident^n(\vec{x}) \right) [\bar{a}_I \oplus \bar{b}_J]
+  = \Ident^{m+n-2k}(\vec{x}) [\bar{a}_I \oplus \bar{b}_J]
+\]
 \end{proof}
@@
 But actually, you'll find that scalars can be modeled equally well by multricies
-with the shpe $\left<\right>$. It works with multiplication and derivatives. Look:
+with the shape $\left<\right>$. It works with multiplication and derivatives. Look:
 
@@
 communicative.
+
 \begin{theorem}[Communicative Property of Multimatrix Addition]
@@
 
-It's similarly trial to show that multimatrix addition is associative.
+It's similarly trivial to show that multimatrix addition is associative.
 
@@
 
-A little less obvious, in that a coffee-deprived undergraduate might
-struggle with it for a second, is that multimatrix multiplication can be
+A little less obvious is that multimatrix multiplication can be
 distributed over it's addition.
@@
 \begin{landscape}
-\begin{theorem}[Multimatrix on Multimatrix Distributive Property]
+\begin{theorem}[Multiplication Distributive Property]
 If $\shape{A} = \vec{a} \oplus \vec{n}$ and $\shape{B}=\shape{C}=\vec{n} \oplus \vec{r}$ then,
@@
 
-But it should be obvious - seriously, how have you not figured this out yet -
-that that the same applies to scalar  multiplication distributing over multimatrix
-addition..
-\begin{theorem}[Scalar on Multimatrix Distributive Property]
+But it should be obvious that that the same applies to scalar 
+multiplication distributing over multimatrix addition, since
+scalar multiplication is equivalent to multiplication by an
+empty shaped multimatrix.
+
+\begin{corollary}[Scalar on Multimatrix Distributive Property]
 If $s \in \mathbb{R}$ and $A, B \in \mathbb{R}^{\vec{x}}$ then,
 \[ s(A + B) = sA + sB \]
-\end{theorem}
+\end{corollary}
 \begin{proof}
@@
 
+\chapter{Slicing and Dicing}
+
+TODO: cheeky quote
+
+\begin{definition}[Multimatrix Wildcard Notation]
+TODO: rigorous definition
+
+Example:
+$\shape{X[\bar{a} \oplus *^{\vec{s}} \oplus \bar{b}]} = \vec{s}$
+\end{definition}
+
 \chapter{Integration}
 
-I think, I'm not sure but I think, that the integral of a multimatrix function should
-be defined,
-
-\[
- \int_A^B F(X) dX = \lim_{n \to \infty}
+\begin{quote}
+TODO: cheeky quote
+\end{quote}
+
+I'll just throw this out there. I think the integral of a multimatrix function should
+be defined like this,
+
+\begin{definition}[Integration of Multimatrix]
+If $G(X)$ is a multimatrix function of shape $\shape{G(X)} = \vec{g} \oplus \shape{X}$,
+for some shape vector $\vec{g}$, then it can be integrated over $dX$ by,
+\[ \shape{\int_A^B G(X) dX} = \vec{g} \]
+\[
+ \int_A^B G(X) dX = \lim_{n \to \infty}
  \sum_{i=1}^n
-  F\left(A+\frac{i}{n}(B-A)\right)
+  G\left(A+\frac{i}{n}(B-A)\right)
   \mmult{\shape{\shape{X}}}
@@
 \]
-
-Which, I have very little idea what that means geometriclly but
-if you let $G(X) = \int_A^X F(Y) dY$ you seem to end up with $dG/dX = F(X)$.
-
-Maybe... well look at it this way. $F(X)$ is a function which produces some,
-afine-like transformation multimatrix for multimatricies of shape $\shape{X}$,
-since it must have a right hand shape of $\ldots \oplus \shape{X}$. This integration
-occures over a linear path of $X$ as it moves from $A$ to $B$ applying that
-transformation and adding up the results of the transformed multimatricies with
-a weight proportional to the step size... and in the direction of the step.
-
-So, it's sort of like a line integral but not really. They're related somehow.
-
-\begin{landscape}
-Let's see if I can prove that theory,
-\begin{theorem}[Fundamental Rule of Multimatrix Calculus]
-Let $G(X) = \int_A^X F(Y) dY$ then $dG(X)/dX = F(X)$.
-\end{theorem}
-\begin{proof}
-\begin{align*}
-  G(X)
-  &= \int_A^X F(Y) dY \\
-  &= 
-    \lim_{n \to \infty}
-     \sum_{i=1}^n
-      F\left(A+\frac{i}{n}(X-A)\right)
-      \mmult{\shape{\shape{Y}}}
-      \left(\frac{X-A}{n}\right)
-\end{align*}
-\begin{alignat*}{3}
-  \frac{dG(X)}{dX}
-  &=&&
-    \frac{
-      d \left\{
-      \lim_{n \to \infty}
-      \sum_{i=1}^n
-        F\left(A+\frac{i}{n}(X-A)\right)
-        \mmult{\shape{\shape{Y}}}
-        \left(\frac{X-A}{n}\right)
-      \right\}
-    }{dX} \\
-  &=&&
-    \lim_{n \to \infty}
-    \frac{
-      d \left\{
-      \sum_{i=1}^n
-        F\left(A+\frac{i}{n}(X-A)\right)
-        \mmult{\shape{\shape{Y}}}
-        \left(\frac{X-A}{n}\right)
-      \right\}
-    }{dX} \\
-  &=&&
-    \lim_{n \to \infty}
-    \sum_{i=1}^n
-      \frac{
-        d \left\{
-          F\left(A+\frac{i}{n}(X-A)\right)
-          \mmult{\shape{\shape{Y}}}
-          \left(\frac{X-A}{n}\right)
-        \right\}
-      }{dX} \\
-  &=&&
-    \lim_{n \to \infty}
-      \sum_{i=1}^n
-        F\left(A+\frac{i}{n}(X-A)\right)
-          \mmult{\shape{\shape{Y}}}
-          \frac{d \left(\frac{X-A}{n}\right)}{dX}
-        \\&&&+
-        \Tran\left(
-          \Tran\left(\frac{X-A}{n}, \shape{\shape{Y}}\right)
-          \mmult{\shape{\shape{Y}}}
-          \Tran\left(\frac{
-            d \left\{F\left(A+\frac{i}{n}(X-A)\right)\right\}
-          }{dX}, \shape{\vec{f}}\right),
-          \shape{\vec{x} \oplus \vec{x}}
-        \right) \\
-  &=&&
-    \lim_{n \to \infty}
-      \sum_{i=1}^n
-        F\left(A+\frac{i}{n}(X-A)\right)
-          \mmult{\shape{\shape{Y}}}
-          \frac{1}{n}\Ident^2(\shape{X})
-        \\&&&+
-        \Tran\left(
-          \frac{X-A}{n}
-          \mmult{\shape{\shape{Y}}}
-          \Tran\left(
-            \frac{dF(X)}{dX}
-            \mmult{\shape{X}}
-            \frac{i}{n}\Ident^2(\shape{X}), \shape{\vec{f}}\right),
-          \shape{\vec{x} \oplus \vec{x}}
-        \right) \\
-  &=&&
-    \lim_{n \to \infty}
-      \sum_{i=1}^n
-        \frac{1}{n}F\left(A+\frac{i}{n}(X-A)\right)
-        \\&&&+
-        \Tran\left(
-          \frac{X-A}{n}
-          \mmult{\shape{\shape{Y}}}
-          \Tran\left(
-            \frac{i}{n}\frac{dF(X)}{dX}
-            , \shape{\vec{f}}\right),
-          \shape{\vec{x} \oplus \vec{x}}
-        \right)
-\end{alignat*}
-At this point I'm fairly stuck.
-
-Ok, lets think of this in another way. Is this true?
-\[
-	\lim_{\epsilon \to 0}
-	\frac{
-		G(X+\epsilon H) - G(X)
-	}{\epsilon}
-	=
-	F(X) \mmult{\shape{\shape{X}}} H
-\]
-Where $SS(H) = 1$. More specifically, $H = \frac{X-A}{\sqrt{SS(X-A)}}$
-
-\begin{align*}
-\lim_{\epsilon \to 0}
-\frac{
-	G(X+\epsilon H) - G(X)
-}{\epsilon}
-&= 
-\lim_{\epsilon \to 0}
-\frac{
-	\left( \int_A^{X+\epsilon H} F(Y) dY \right) - \left( \int_A^X F(Y) dY \right)
-}{\epsilon} \\
-&= 
-\lim_{\epsilon \to 0}
-\frac{
-	\int_X^{X+\epsilon H} F(Y) dY
-}{\epsilon}
-\end{align*}
-\end{proof}
-\end{landscape}
+\end{definition}
+
+But what does this actually mean? I'll show, below, that this actually breaks down into
+a series of line integrals from over a strait line from $A$ to $B$. It will also be
+shown that the integral of $dF/dX$ will return $F(X) + C$, as one would expect from an
+integral.
+
+\begin{theorem}[Line Integrals Inside Multimatrix Integral]
+If $G(X)$ is an integrable multimatrix function (i.e. it has a shape
+$\shape{G(X)} = \vec{g} \oplus \shape{X}$) then each output element of it's
+integral is a line integral.
+Specifically, for all $\bar{g}$ in $\Dim(\vec{g})$,
+\[ \left(\int_A^B G(X) dX\right)[\bar{g}] = \int_C G(X)[\bar{g} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} dX \]
+Where $C$ is the straight line from $A$ to $B$. And $\mmult{\shape{\shape{X}}} dX$ serves the same notational purpose as
+$\cdot dr$ (see \cite{wiki:line_int}) because multiplication by the entire shape of $X$ is the same as a dot product.
+\end{theorem}
+\begin{proof}
+Let us parameterize $C$ such that $C(t) = A + t(B-A)$. Then $dC/dt = B-A$ and
+we can rewrite the line integral over $C$ as,
+\[ \int_C G(X)[\bar{g} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} dX = \int_0^1 G(C(t))[\bar{g} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} \frac{dC}{dt} dt \]
+TODO
+\end{proof}
+
+TODO:fundamental theorem
 

### 2020-08-06 MMatrix/test/test_audio.cc

@@ -377,20 +377,24 @@ void fft(std::vector<double> s, int N, int a, int b, std::vector<double>* outR, 
     outI->push_back(0);
     return;
   }
-  // How can I be smart about allocating this memory?
-  std::vector<double> evenR, evenI, oddR, oddI;
-  evenR.reserve(N/2);
-  evenI.reserve(N/2);
-  oddR.reserve(N/2);
-  oddI.reserve(N/2);
-  fft(s, N/2, 2*a, b, &evenR, &evenI);
-  fft(s, N/2, 2*a, a+b, &oddR, &oddI);
-  for (int k = 0; k < N; k++) {
-    int km = k%(N/2);
+  int kOff = outR->size();
+  // Calculate even parts
+  fft(s, N/2, 2*a, b, outR, outI);
+  // Calculate odd parts
+  fft(s, N/2, 2*a, a+b, outR, outI);
+  for (int k = 0; k < N/2; k++) {
     double c = std::cos(2*pi*k/N);
     double s = std::sin(2*pi*k/N);
-    outR->push_back(evenR[km]+c*oddR[km]-s*oddI[km]);
-    outI->push_back(evenI[km]+s*oddR[km]+c*oddI[km]);
+    double evenR = (*outR)[k+kOff];
+    double evenI = (*outI)[k+kOff];
+    double oddR = (*outR)[k+N/2+kOff];
+    double oddI = (*outI)[k+N/2+kOff];
+    (*outR)[k+kOff] = evenR+c*oddR-s*oddI;
+    (*outI)[k+kOff] = evenI+s*oddR+c*oddI;
+    (*outR)[k+N/2+kOff] = evenR-c*oddR+s*oddI;
+    (*outI)[k+N/2+kOff] = evenI-s*oddR-c*oddI;
+    //outR->push_back(evenR[km]+c*oddR[km]-s*oddI[km]);
+    //outI->push_back(evenI[km]+s*oddR[km]+c*oddI[km]);
   }
 }
 
@@ -437,9 +441,17 @@ void TestFFT() {
   std::vector<double> sftR, sftI;
   sft(samples, N, 1, 0, &sftR, &sftI);
 
+  /*
+  for (int i = 0; i < N; i++) {
+    std::cout << fftR[i] << '\t' << fftI[i] << '\t';
+    std::cout << sftR[i] << '\t' << sftI[i] << std::endl;
+  }
+  exit(0);
+  // */
+  
[…]

### 2020-08-08 Math/book.tex
Flushing out integration for multimatricies

@@
 
-TODO: cheeky quote
+\begin{displayquote}
+\textbf{Julian Bashir:} They broke seven of your transverse ribs and fractured your clavicle.
+
+\textbf{Elim Garak:} Ah, but I got off several cutting remarks, which no doubt did serious damage to their egos.
+
+(Star Trek Deep Space Nine, Season 4. Episode 1 \& 2 \cite{stds9})
+\end{displayquote}
 
 \begin{definition}[Multimatrix Wildcard Notation]
-TODO: rigorous definition
-
 Example:
@@
 
+\begin{theorem}[Wildcard Multiplication]
+TODO:generalize
+Let $A$ and $X$ be multimatrixes of shape $\shape{A} = \vec{a} \oplus \vec{x}$ and $\shape{X} = \vec{x}$ respectively.
+Then $A[\bar{a} \oplus *^{\vec{x}}] \mmult{\shape{\vec{x}}} X = (A \mmult{\shape{\vec{x}}} X)[\bar{a}]$.
+\end{theorem}
+\begin{proof}
+\begin{align*}
+  A[\bar{a} \oplus *^{\vec{x}}] \mmult{\shape{\vec{x}}} X
+  &=
+  \sum_{\forall \bar{x} \in \Dim(\vec{X})} A[\bar{a} \oplus *^{\vec{x}}][\bar{x}] X[\bar{x}] \\
+  &=
+  \sum_{\forall \bar{x} \in \Dim(\vec{X})} A[\bar{a} \oplus \bar{x}] X[\bar{x}] \\
+  &= (A \mmult{\shape{\vec{x}}} X)[\bar{a}]
+\end{align*}
+\end{proof}
+
 \chapter{Integration}
 
-\begin{quote}
+\begin{displayquote}
 TODO: cheeky quote
-\end{quote}
+\end{displayquote}
 
@@
 
+\begin{landscape}
 But what does this actually mean? I'll show, below, that this actually breaks down into
@@
 \begin{theorem}[Line Integrals Inside Multimatrix Integral]
+\label{line_inside}
 If $G(X)$ is an integrable multimatrix function (i.e. it has a shape
@@
 \[ \int_C G(X)[\bar{g} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} dX = \int_0^1 G(C(t))[\bar{g} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} \frac{dC}{dt} dt \]
-TODO
-\end{proof}
-
-TODO:fundamental theorem
+For which we can write out the Riemann integral \cite{wiki:riemann_int}:
+\begin{align*}
+  \int_0^1 G(C(t))[\bar{g} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} \frac{dC}{dt} dt
+  &=
+  \lim_{n \to \inf} \sum_{i=1}^n G(C(i/n))[\bar{g} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} \frac{dC}{dt}(i/n) \frac{1}{n} \\
+  &=
+  \lim_{n \to \inf} \sum_{i=1}^n G(A + \frac{i}{n}(B-A))[\bar{g} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} \frac{B-A}{n} \\
+  &=
+  \lim_{n \to \inf} \sum_{i=1}^n \left( G(A + \frac{i}{n}(B-A)) \mmult{\shape{\shape{X}}} \frac{B-A}{n} \right)[\bar{g}] \\
+  &=
+  \left( \lim_{n \to \inf} \sum_{i=1}^n G(A + \frac{i}{n}(B-A)) \mmult{\shape{\shape{X}}} \frac{B-A}{n} \right)[\bar{g}] \\
+  &=
+  \left(\int_A^B G(X) dX\right)[\bar{g}] 
+\end{align*}
+\end{proof}
+\end{landscape}
+
+This leads us to my final observation about integrals.
+
+\begin{theorem}[Integral of Multimatrix Derivatives]
+For any multimatrix function $F(X)$,
+\[ \int_A^B \frac{dF}{dX} dX = F(B) - F(A) \]
+\end{theorem}
+\begin{proof}
+We know from the above theorem \ref{line_inside} that for all $\bar{f} \in \Dim(\vec{f})$
+\[ \left(\int_A^B \frac{dF}{dX}(X) dX\right)[\bar{f}] = \int_C \frac{dF}{dX}(X)[\bar{f} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} dX \]
+Notice that $\frac{dF}{dX}(X)[\bar{f} \oplus *^{\shape{X}}]$ is the equivalent
+to the gradient of $F(X)[\bar{f}]$ at $X$ since for all $\bar{x} \in \Dim(\vec{x})$,
+\[ \frac{dF}{dX}(X)[\bar{f} \oplus \bar{x}] = \frac{\partial F[\bar{f}]}{\partial X[\bar{x}]} \]
+Then by the Gradient theorem \cite{wiki:gradient_thm} we can conclude that,
+\[ \left(\int_A^B \frac{dF}{dX}(X) dX\right)[\bar{f}] =  F(B)[\bar{f}] - F(A)[\bar{f}] = \left( F(B)-F(A) \right)[\bar{f}] \]
+So, 
+\[ \int_A^B \frac{dF}{dX} dX = F(B) - F(A) \]
+\end{proof}
 

### 2020-08-10 MMatrix/test/test_audio.cc
Trying my hand at auto tuning.

@@ -371,28 +371,29 @@ void TestDerivFourierDifference() {
   }
 }
 
-void fft(std::vector<double> s, int N, int a, int b, std::vector<double>* outR, std::vector<double>* outI) {
+void fft(const std::vector<double>& s, int N, int a, int b, std::vector<double>* outR, std::vector<double>* outI) {
   if (N == 1) {
     outR->push_back(s[b]);
     outI->push_back(0);
     return;
   }
-  int kOff = outR->size();
+  int kOffR = outR->size();
+  int kOffI = outI->size();
   // Calculate even parts
   fft(s, N/2, 2*a, b, outR, outI);
   // Calculate odd parts
   fft(s, N/2, 2*a, a+b, outR, outI);
   for (int k = 0; k < N/2; k++) {
-    double c = std::cos(2*pi*k/N);
-    double s = std::sin(2*pi*k/N);
-    double evenR = (*outR)[k+kOff];
-    double evenI = (*outI)[k+kOff];
-    double oddR = (*outR)[k+N/2+kOff];
-    double oddI = (*outI)[k+N/2+kOff];
-    (*outR)[k+kOff] = evenR+c*oddR-s*oddI;
-    (*outI)[k+kOff] = evenI+s*oddR+c*oddI;
-    (*outR)[k+N/2+kOff] = evenR-c*oddR+s*oddI;
-    (*outI)[k+N/2+kOff] = evenI-s*oddR-c*oddI;
+    double c = std::cos(-2*pi*k/N);
+    double s = std::sin(-2*pi*k/N);
+    double evenR = (*outR)[k+kOffR];
+    double evenI = (*outI)[k+kOffI];
+    double oddR = (*outR)[k+N/2+kOffR];
+    double oddI = (*outI)[k+N/2+kOffI];
+    (*outR)[k+kOffR] = evenR+c*oddR-s*oddI;
+    (*outI)[k+kOffI] = evenI+s*oddR+c*oddI;
+    (*outR)[k+N/2+kOffR] = evenR-c*oddR+s*oddI;
+    (*outI)[k+N/2+kOffI] = evenI-s*oddR-c*oddI;
     //outR->push_back(evenR[km]+c*oddR[km]-s*oddI[km]);
     //outI->push_back(evenI[km]+s*oddR[km]+c*oddI[km]);
   }
@@ -402,8 +403,8 @@ void sft(std::vector<double> s, int N, int a, int b, std::vector<double>* outR, 
[…]

### 2020-08-16 Math/book.tex
Doing some scratch work.

@@
 \DeclareMathOperator{\Tran}{Tran}
+\DeclareMathOperator{\Part}{Part}
 \DeclareMathOperator{\SoS}{\mathbb{S}}
@@
 \newcommand{\dmult}[1]{\text{\raisebox{1ex}{$\underset{#1}{\,\bullet\,}$}}}
+\newcommand{\mconcat}[1]{\text{\raisebox{1ex}{$\underset{#1}{\oplus}$}}}
 \newcommand{\shape}[1]{\left|#1\right|}
@@
 
-Multimatrix identities also have the nice property of being communicative when multiplied
+Multimatrix identities also have the nice property of being commutative when multiplied
 across multiples of their base shape and completely engulfing a smaller multimatrix.
 
-\begin{theorem}[Communicativity of Multiplicative Identities]
+\begin{theorem}[Commutativity of Multiplicative Identities]
+\label{ident_commute}
 Let $X$ be a multimatrix of shape $k * \vec{x}$ where $k$ is some natural number.
@@
   &= (B \dmult{\shape{\vec{x}}} A)[\bar{x}]
+\end{align*}
+\end{proof}
+
+\begin{theorem}[Cubic Identity Multiplication]
+\label{hada_cubic}
+If $A$ and $B$ are multimatrixes of shaep, $\shape{A} = \vec{a} \oplus \vec{x}$
+and $\shape{B} = \vec{x} \oplus \vec{b}$ respectively. Then,
+\[ A \mmult{\shape{\vec{x}}} \Ident^3(\vec{x}) \mmult{\shape{\vec{x}}} B = A \dmult{\shape{\vec{x}}} B \]
+\end{theorem}
+\begin{proof}
+\[ \shape{A \mmult{\shape{\vec{x}}} \Ident^3(\vec{x}) \mmult{\shape{\vec{x}}} B} = \vec{a} \oplus \vec{x} \oplus \vec{b}  \]
+For all $\bar{a} \in \Dim(\vec{a})$, $\bar{b} \in \Dim(\vec{b})$, and $\bar{x} \in \Dim(\vec{x})$, 
+\begin{align*}
+  (A \mmult{\shape{\vec{x}}} \Ident^3(\vec{x}) \mmult{\shape{\vec{x}}} B)[\bar{a} \oplus \bar{x} \oplus \bar{b}]
+  &= \sum_{\forall \bar{x}_1, \bar{x_2}} A[\bar{a} \oplus \bar{x}_1] \Ident^3(\vec{x})[\bar{x}_1 \oplus \bar{x} \oplus \bar{x}_2] B[\bar{x}_2 \oplus \bar{b}] \\
+  &= A[\bar{a} \oplus \bar{x}] \Ident^3(\vec{x})[\bar{x} \oplus \bar{x} \oplus \bar{x}] B[\bar{x} \oplus \bar{b}] \\
+  &= A[\bar{a} \oplus \bar{x}] B[\bar{x} \oplus \bar{b}] \\
+  &= (A \dmult{\shape{\vec{x}}} B) [\bar{a} \oplus \bar{x} \oplus \bar{b}]
 \end{align*}
@@
 \begin{theorem}[Hadamard Multiplication Rule]
+\label{hadamard_rule}
 Let $F(X)$ and $G(X)$ be functions of $X$ where
@@
 \]
+Now will a little manipulation, keeping in mind how identies are sometimes commutative (Thm. \ref{ident_commute})
+and how cubic identities collapse into hadamard products (Thm. \ref{hada_cubic}),
+\begin{align*}
+  \frac{dL_i}{dW_{j=i}}
+  &=
+    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i)\right) 
+    \mmult{\shape{\shape{L_i}}}
+    \left(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} \Ident^2(\shape{W_i})\right) \\
+  &=
+    \left(a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \mmult{\shape{\shape{L_i}}} \Ident^3(\shape{L_i})\right) 
+    \mmult{\shape{\shape{L_i}}}
+    \left(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} \Ident^2(\shape{W_i})\right) \\
+  &=
+    a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \mmult{\shape{\shape{L_i}}} \Ident^3(\shape{L_i})
+    \mmult{\shape{\shape{L_i}}}
+    \left(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} \Ident^2(\shape{W_i})\right) \\
+  &=
+    a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \dmult{\shape{\shape{L_i}}}
+    \left(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} \Ident^2(\shape{W_i})\right)
+\end{align*}
 \end{ppart}
@@
 
+\begin{definition}[Multimatrix Concatenation]
+Let $A$ and $B$ be multimatricies of shape $\shape{A} = \vec{a}$ and
+$\shape{B} = \vec{b}$ respectively. Then if, for all $i \ne n$,
+$\vec{a}[i] = \vec{b}[i]$, the following operation is valid,
+\[ A \mconcat{n} B \]
+In layman's terms, this is the operation of stacking two similar multimatricies on top of or to the side of one another.
+It's just complicated by this being an opperation in multiple dimensions.
+Formally we'll say that, 
+\[ \shape{\shape{A \mconcat{n} B}} = \shape{\shape{A}} = \shape{\shape{B}} \]
+\[
+  \shape{A \mconcat{n} B}[i] = \left\{
+  \begin{array}{ll}
+	  \vec{a}[i] + \vec{b}[i] & \mbox{if } i = n \\
+	  \vec{a}[i] & \mbox{if } i \ne n
+  \end{array}
+ \right.
+\]
+And for all sub index metricies $\bar{l}$ and $\bar{r}$ of lengths $\shape{\bar{l}} = n-1$ and $\shape{\bar{r}} = \shape{\shape{A}}-n$ respectively,
+and natural number $j \in [1,\vec{a}[n]+\vec{b}[n]]$ such that $\bar{l} \oplus \left<j\right> \oplus \bar{r} \in \Dim(\shape{A \mconcat{n} B})$,
+\[
+  \left(A \mconcat{n} B\right)[\bar{l} \oplus \left<j\right> \oplus \bar{r}] = \left\{
+  \begin{array}{ll}
+	  A[\bar{l} \oplus \left<j\right> \oplus \bar{r}] & \mbox{if } j  \le \vec{a}[n] \\
+	  A[\bar{l} \oplus \left<j-\vec{a}[n]\right> \oplus \bar{r}] & \mbox{if } j > \vec{a}[n]
+  \end{array}
+ \right.
+\]
+\end{definition}
+
+\begin{definition}[Multimatrix Partitions]
+Let $M$ be some multimatrix of shape $\vec{m}$.
+Then for any natural number $n \in [1, \shape{\vec{m}}]$, the dimension,
+and natural number $k \in [1,\vec{m}[n]-1]$, the split,
+\[ \Part(M, n, k) = \{M_1, M_2\} \]
+\[ \Part_1(M, n, k) = M_1 \]
+\[ \Part_2(M, n, k) = M_2 \]
+Where $M_1 \mconcat{n} M_2 = M$ and $\shape{M_1}[n] = k$ (therefore $\shape{M_2}[n] = \vec{m}[n]-k$).
+
+In essence, this is the inverse operation of multimatrix concatenation.
+
+Let $\vec{l}$ and $\vec{r}$ be vectors of length $n-1$ and $\shape{\vec{m}}-n$ respectively
+such that $\vec{l} \oplus \left<\vec{m}[n]\right> \oplus \vec{r} = \vec{m}$ then
+\[ \shape{\Part_1(M, n, k)} = \vec{l} \oplus \left<k\right> \oplus \vec{r} \]
+\[ \shape{\Part_2(M, n, k)} = \vec{l} \oplus \left<\vec{m}[n]-k\right> \oplus \vec{r} \]
+
+For all $\bar{l} \in \Dim(\vec{l})$, $\bar{r} \in \Dim(\vec{r})$, and $j \in [1, k]$,
+\[ \Part_1(M, n, k)[\bar{l} \oplus \left<j\right> \oplus \bar{r}] = M[\bar{l} \oplus \left<j\right> \oplus \bar{r}] \]
+
+And for all $\bar{l} \in \Dim(\vec{l})$, $\bar{r} \in \Dim(\vec{r})$, and $j \in [1, \vec{m}[n]-k]$,
+\[ \Part_2(M, n, k)[\bar{l} \oplus \left<j\right> \oplus \bar{r}] = M[\bar{l} \oplus \left<j+k\right> \oplus \bar{r}] \]
+\end{definition}
+
+\begin{theorem}[Multiplication Over Concatenation Rules]
+Let $A$ and $B$ be multimatricies where $A \mconcat{n} B$ is valid.
+
+For any natural number $m$ where $m < n$,
+if and only if $C$ is a multimatrix for which $C \mmult{m} \left(A \mconcat{n} B\right)$ is valid then,
+\[ C \mmult{m} \left(A \mconcat{n} B\right) = \left(C \mmult{m} A\right) \mconcat{\shape{\shape{C}}+n-2m} \left(C \mmult{m} B\right) \]
+
+And if $m \le \shape{\shape{A}}-n$
+then if and only if  $C$ is a multimatrix for which $\left(A \mconcat{n} B\right) \mmult{m} C$ is valid then,
+\[ \left(A \mconcat{n} B\right) \mmult{m} C = \left(A \mmult{m} C\right) \mconcat{n} \left(B \mmult{m} C\right) \]
+
+And when $m \ge n$, if and only if $C$ is a multimatrix for which $C \mmult{m} \left(A \mconcat{n} B\right)$ is valid,
+then for the multimatrices $C_1$ and $C_2$ defined by,
+\[ \Part(C, \shape{\shape{C}}-m+n, \shape{A}[n]) = \{C_1, C_2\} \]
+\[
+  C \mmult{m} \left(A \mconcat{n} B\right)
+  =
+  \left( C_1 \mmult{m} A \right) + 
+  \left( C_1 \mmult{m} B \right)
+\]
+
+Lastly, when $m > \shape{\shape{A}}-n$, if and only if $C$ is a multimatrix for which $\left(A \mconcat{n} B\right) \mmult{m} C$ is valid,
+then for multimatrices $C_1$ and $C_2$ defined by,
+\[ \Part(C, m+n-\shape{\shape{A}}+1, \shape{A}[n]) = \{C_1, C_2\} \]
+\[
+  \left(A \mconcat{n} B\right) \mmult{m} C
+  =
+  \left( A \mmult{m} C_1 \right) + 
+  \left( B \mmult{m} C_1 \right)
+\]
+\end{theorem}
+\begin{proof}
+\begin{ppart}
+Let $A$ and $B$ be multimatricies where $A \mconcat{n} B$ is valid. 
+Let $m$ be a natural number where $m < n$, and let $C$ be a multimatrix where
+$C \mmult{m} \left(A \mconcat{n} B\right)$ is valid.
+
+Since $A \mconcat{n} B$ is valid, we can describe the shapes of $A$ and $B$ thusly,
+\[ \shape{A} = \vec{l} \oplus \left<a\right> \oplus \vec{r} \]
+\[ \shape{B} = \vec{l} \oplus \left<b\right> \oplus \vec{r} \]
+Where $a$ and $b$ are both natural numbers, $\shape{\vec{l}} = n-1$, and
+$\shape{\vec{r}} = \shape{\shape{A}} - n$. So,
+\[ \shape{A \mconcat{n} B} = \vec{l} \oplus \left<a+b\right> \oplus \vec{r} \]
+
+Now, because $C \mmult{m} \left(A \mconcat{n} B\right)$ is valid, we know that
+there is some division in the shape of $C$ such that,
+\[ \shape{C} = \vec{c} \oplus \vec{m} \]
+For some shape vetors $\vec{c}$ and $\vec{m}$ where $\shape{\vec{m}} = m$ and
+$\shape{\vec{c}} = \shape{\shape{C}}-m$
+We also know that there exists some similar subdivision of $\shape{A \mconcat{n} B}$.
+\[ \shape{A \mconcat{n} B} = \vec{m} \oplus \vec{d} \]
+For some $\vec{d}$. Therefore,
+\[ \vec{m} \oplus \vec{d} = \vec{l} \oplus \left<a + b\right> \oplus \vec{r} \]
+
+Since $m < n$, $\shape{\vec{m}} \le \shape{\vec{l}}$ so $\vec{l}$ can be subdivided
+into,
+\[ \vec{l} = \vec{m} \oplus \vec{e} \]
+For some shape vector $\vec{e}$ where $\shape{\vec{e}} = n-1-m$.
+
+So,
+\[ \shape{A \mconcat{n} B} = \vec{m} \oplus \vec{e} \oplus \left<a+b\right> \oplus \vec{r} \]
+\[ \shape{A} = \vec{m} \oplus \vec{e} \oplus \left<a\right> \oplus \vec{r} \]
+\[ \shape{B} = \vec{m} \oplus \vec{e} \oplus \left<b\right> \oplus \vec{r} \]
+
+Therefore $C \mmult{m} A$ and $C \mmult{m} B$ are both valid operations and,
+\[ \shape{C \mmult{m} A} = \vec{c} \oplus \vec{e} \oplus \left<a\right> \oplus \vec{r} \]
+\[ \shape{C \mmult{m} B} = \vec{c} \oplus \vec{e} \oplus \left<b\right> \oplus \vec{r} \]
+
+Which shows that $(C \mmult{m} A) \mconcat{\shape{\vec{c} \oplus \vec{e}}+1} (C \mmult{m} B)$
+is also valid.
+\[
+  (C \mmult{m} A) \mconcat{(\shape{\shape{C}}-m)+(n-1-m)+1} (C \mmult{m} B)
+  = 
+  (C \mmult{m} A) \mconcat{\shape{\shape{C}}+n-2m} (C \mmult{m} B)
+\]
+
+\begin{landscape}
+Which means that,
+\begin{align*}
+  \shape{C \mmult{m} \left(A \mconcat{n} B\right)}
+  &= \shape{(C \mmult{m} A) \mconcat{\shape{\shape{C}}+n-2m} (C \mmult{m} B)} \\
+  &= \vec{c} \oplus \vec{e} \oplus \left<a+b\right> \oplus \vec{r}
+\end{align*}
+
+Now for any $\bar{c}$, $\bar{e}$, and $\bar{r}$ be in $\Dim(\vec{c})$, $\Dim(\vec{e})$,
+and $\Dim(\vec{r})$ respectively and $k \in [1,a+b]$, then,
+\begin{align*}
+  \left(C \mmult{m} \left(A \mconcat{n} B\right)\right)[\bar{c} \oplus \bar{e} \oplus \left<k\right> \oplus \bar{r}]
+  &= \sum_{\forall \bar{m} \in \Dim(\vec{m})} C[\bar{c} \oplus \bar{m}] \left(A \mconcat{n} B\right)[\bar{m} \oplus \bar{e} \oplus \left<k\right> \oplus \bar{r}] \\
+  &= \left\{
+  \begin{array}{ll}
+    \sum_{\forall \bar{m}} C[\bar{c} \oplus \bar{m}] A[\bar{m} \oplus \bar{e} \oplus \left<k\right> \oplus \bar{r}]
+    & \mbox{if } k \le a \\
+    \sum_{\forall \bar{m}} C[\bar{c} \oplus \bar{m}] B[\bar{m} \oplus \bar{e} \oplus \left<k-a\right> \oplus \bar{r}]
+    & \mbox{if } k > a
+  \end{array}
+  \right. \\
+  &= \left\{
+  \begin{array}{ll}
+    (C \mmult{m} A)[\bar{c} \oplus \bar{e} \oplus \left<k\right> \oplus \bar{r}]
+    & \mbox{if } k \le a \\
+    (C \mmult{m} B)[\bar{c} \oplus \bar{e} \oplus \left<k-a\right> \oplus \bar{r}]
+    & \mbox{if } k > a
+  \end{array}
+  \right. \\
+  &= \left(\left(C \mmult{m} A\right) \mconcat{\shape{\shape{C}}+n-2m} \left(C \mmult{m} B\right)\right)[\bar{c} \oplus \bar{e} \oplus \left<k\right> \oplus \bar{r}]
+\end{align*}
+\end{landscape}
+\end{ppart}
+\begin{ppart}
+TODO: Prove the converse.
+\end{ppart}
+\begin{ppart}
+Let $A$ and $B$ be multimatricies where $A \mconcat{n} B$ is valid. 
+Let $m$ be a natural number where $m \le \shape{\shape{A}}-n$
+and $C$ is a multimatrix for which $\left(A \mconcat{n} B\right) \mmult{m} C$ is valid.
+Then there exit shape vectors $\vec{l}$ and $\vec{r}$ and integers $a$ and $b$ such that,
+
+\[ \shape{A} = \vec{l} \oplus \left<a\right> \oplus \vec{r} \]
+\[ \shape{B} = \vec{l} \oplus \left<b\right> \oplus \vec{r} \]
+\[ \shape{A \mconcat{n} B} = \vec{l} \oplus \left<a+b\right> \oplus \vec{r} \]
+
+Where $\shape{\vec{l}} = n-1$ and $\shape{\vec{r}} = \shape{\shape{A}}-n$.
+
+Then since $\left(A \mconcat{n} B\right) \mmult{m} C$ is valid, $\shape{C}$ can
+be partitioned into $\vec{m}$ and $\vec{c}$ where,
+
+\[ \shape{C} = \vec{m} \oplus \vec{c} \]
+
+And $\shape{\vec{m}} = m$. This also means that,
+
+\[ \shape{A \mconcat{n} B} = \vec{d} \oplus \vec{m} \]
+
+Now since $m \le \shape{\shape{A}}-n$ we can partition $\vec{r}$ like this,
+
+\[ \vec{r} = \vec{e} \oplus \vec{m} \]
+
+So we can use that repartion in our original shape definitions,
+
+\[ \shape{A \mconcat{n} B} = \vec{l} \oplus \left<a+b\right> \oplus \vec{e} \oplus \vec{m} \]
+\[ \shape{A} = \vec{l} \oplus \left<a\right> \oplus \vec{e} \oplus \vec{m} \]
+\[ \shape{B} = \vec{l} \oplus \left<b\right> \oplus \vec{e} \oplus \vec{m} \]
+
+So $A \mmult{m} C$ and $B \mmult{m} C$ are both valid and,
+
+\[ \shape{A \mmult{m} C} = \vec{l} \oplus \left<a\right> \oplus \vec{e} \oplus \vec{c} \]
+\[ \shape{B \mmult{m} C} = \vec{l} \oplus \left<b\right> \oplus \vec{e} \oplus \vec{c} \]
+
+And finally we can see that $(A \mmult{m} C) \mconcat{\shape{\vec{l}}+1} (B \mmult{m} C)$
+is valid and,
+
+\[
+  (A \mmult{m} C) \mconcat{\shape{\vec{l}}+1} (B \mmult{m} C)
+  =
+  (A \mmult{m} C) \mconcat{n} (B \mmult{m} C)
+\]
+
+\begin{align*}
+  \shape{(A \mmult{m} C) \mconcat{n} (B \mmult{m} C)}
+  &= \vec{l} \oplus \left<a+b\right> \oplus \vec{e} \oplus \vec{c} \\
+  &= \shape{(A \mconcat{n} B) \mmult{m} C}
+\end{align*}
+
+\begin{landscape}
+Now for all $\bar{l}$, $\bar{e}$, and $\bar{c}$ are in $\Dim(\vec{l})$, $\Dim(\vec{e})$,
+and $\Dim(\vec{c})$ respectively and all $k \in [1,a+b]$,
+
+\begin{align*}
+  \left(\left(A \mconcat{n} B\right) \mmult{m} C\right)[\bar{l} \oplus \left<k\right> \oplus \bar{e} \oplus \bar{c}]
+  &= \sum_{\forall \bar{m} \in \Dim(\vec{m})} \left(A \mconcat{n} B\right)[\bar{l} \oplus \left<k\right> \oplus \bar{e} \oplus \bar{m}] C[\bar{m} \oplus \bar{c}] \\
+  &= \left\{
+  \begin{array}{ll}
+    \sum_{\forall \bar{m}} A[\bar{l} \oplus \left<k\right> \oplus \bar{e} \oplus \bar{m}] C[\bar{m} \oplus \bar{c}] 
+    & \mbox{if } k \le a \\
+    \sum_{\forall \bar{m}} B[\bar{l} \oplus \left<k-a\right> \oplus \bar{e} \oplus \bar{m}] C[\bar{m} \oplus \bar{c}] 
+    & \mbox{if } k > a
+  \end{array}
+  \right. \\
+  &= \left\{
+  \begin{array}{ll}
+    (A \mmult{m} C)[\bar{l} \oplus \left<k\right> \oplus \bar{e} \oplus \bar{c}]
+    & \mbox{if } k \le a \\
+    (B \mmult{m} C)[\bar{l} \oplus \left<k-a\right> \oplus \bar{e} \oplus \bar{c}]
+    & \mbox{if } k > a
+  \end{array}
+  \right. \\
+  &= 
+    \left(\left(A \mmult{m} C\right) \mconcat{n} \left(B \mmult{m} C\right)\right)
+    [\bar{l} \oplus \left<k\right> \oplus \bar{e} \oplus \bar{c}]
+\end{align*}
+\end{landscape}
+\end{ppart}
+
+\begin{ppart}
+TODO: Prove the converse.
+\end{ppart}
+
+\begin{ppart}
+Let $A$ and $B$ be multimatricies where $A \mconcat{n} B$ is valid. 
+Let $m$ be a natural number where $m \ge n$, and let $C$ be a multimatrix where
+$C \mmult{m} (A \mconcat{n} B)$ is valid.
+
+Then we can partition the shapes of $A$ and $B$ thusly,
+
+\[ \shape{A} = \vec{l} \oplus \left<a\right> \oplus \vec{r} \]
+\[ \shape{B} = \vec{l} \oplus \left<b\right> \oplus \vec{r} \]
+\[ \shape{A \mconcat{n} B} = \vec{l} \oplus \left<a+b\right> \oplus \vec{r} \]
+
+Where $\shape{\vec{l}} = n-1$.
+
+We can also partiton the shapes of $C$ and $(A \mconcat{n} B)$ like this,
+
+\[ \shape{C} = \vec{c} \oplus \vec{m} \]
+\[ \shape{A \mconcat{n} B} = \vec{m} \oplus \vec{d} \]
+
+Where $\shape{\vec{m}} = m$. Now since $m \ge n$ we can know that
+$\shape{\vec{m}} \ge \shape{\vec{l} \oplus \left<a+b\right>}$ 
+so $\vec{m}$ encompases $\vec{l}$, the $n$'th index and potentially part of $\vec{r}$.
+There for if we partition $\vec{r}$ like this,
+
+\[ \vec{r} = \vec{p} \oplus \vec{q} \]
+
+Where,
+
+\[ \vec{m} = \vec{l} \oplus \left<a+b\right> \oplus \vec{p} \]
+
+Then we can define the resulting shape of $C$ like this,
+
+\[ \shape{C} = \vec{c} \oplus \vec{l} \oplus \left<a+b\right> \oplus \vec{p} \]
+
+Since $\shape{\vec{c}} = \shape{\shape{C}}-m$, if we let $C_1$ and $C_2$ be defined by,
+\[ \Part(C, \shape{\shape{C}}-m+n, \shape{A}[n]) = \{C_1, C_2\} \]
+Then,
+\[ \shape{C_1} = \vec{c} \oplus \vec{l} \oplus \left<a\right> \oplus \vec{p} \]
+\[ \shape{C_2} = \vec{c} \oplus \vec{l} \oplus \left<b\right> \oplus \vec{p} \]
+
+Now, let us define $\vec{m}_1$ and $\vec{m}_2$ such that,
+\[ \vec{m}_1 = \vec{l} \oplus \left<a\right> \oplus \vec{p} \]
+\[ \vec{m}_2 = \vec{l} \oplus \left<b\right> \oplus \vec{p} \]
+And notice that $\shape{\vec{m}_1} = \shape{\vec{m}_2} = m$
+
+Next, since $\vec{r} = \vec{p} \oplus \vec{q}$ the shapes of $A$ and $B$ and be described,
+\[ \shape{A} = \vec{l} \oplus \left<a\right> \oplus \vec{p} \oplus \vec{q} = \vec{m}_1 \oplus \vec{q} \]
+\[ \shape{B} = \vec{l} \oplus \left<b\right> \oplus \vec{p} \oplus \vec{q} = \vec{m}_2 \oplus \vec{q} \]
+
+So $C_1 \mmult{m} A$ and $C_2 \mmult{m} B$ are both valid.
+
+\end{ppart}
+\begin{ppart}
+TODO: Prove the converse.
+\end{ppart}
+
+TODO
+\end{proof}
+
 \begin{definition}[Multimatrix Wildcard Notation]
@@
 \begin{drule}
+Hadamard Multiplication Rule
+(Thm. \ref{hadamard_rule})
+If $\shape{F(X)} = \vec{a} \oplus \vec{c}$ and $\shape{G(X)} = \vec{c} \oplus \vec{b}$, then,
+\[
+  \frac{d(F(X) \dmult{\shape{\vec{c}}} G(X))}{dX} =
+    F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX} +
+    \Tran\left(\Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right) \dmult{\shape{\vec{c}}} G(X), \shape{\shape{X}}\right)
+\]
+\end{drule}
+
+\begin{drule}
 Chain Rule
@@
 
+\chapter{Scratch}
+
+What is $A \dmult{m} (B \mmult{n} C)$ ?
+
+\[ \shape{A} = \vec{a} \oplus \vec{m} \]
+\[ \shape{B} = \vec{b} \oplus \vec{n} \]
+\[ \shape{C} = \vec{n} \oplus \vec{c} \]
+
+if $\vec{m} = \vec{b}$ then,
+
+\[ \shape{A \dmult{m} (B \mmult{n} C)} = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
+
+\begin{align*}
+(A \dmult{m} (B \mmult{n} C))[\bar{a} \oplus \bar{b} \oplus \bar{c}]
+  &=
+  A[\bar{a} \oplus \bar{b}] \sum_{\forall \bar{n}} B[\bar{b} \oplus \bar{n}] C[\bar{n} \oplus \bar{c}] \\
+  &=
+  \sum_{\forall \bar{n}} A[\bar{a} \oplus \bar{b}] B[\bar{b} \oplus \bar{n}] C[\bar{n} \oplus \bar{c}] \\
+  &=
+  \sum_{\forall \bar{n}} (A \dmult{m} B)[\bar{a} \oplus \bar{b} \oplus \bar{n}] C[\bar{n} \oplus \bar{c}] \\
+  &= ((A \dmult{m} B) \mmult{n} C)[\bar{a} \oplus \bar{b} \oplus \bar{c}]
+\end{align*}
+
+If $m < \shape{\vec{b}}$ then
+\[ \vec{b} = \vec{m} \oplus \vec{d} \]
+\[ \shape{B} = \vec{m} \oplus \vec{d} \oplus \vec{n} \]
+\[ \shape{A \dmult{m} (B \mmult{n} C)} = \vec{a} \oplus \vec{m} \oplus \vec{d} \oplus \vec{c} \]
+
+\begin{align*}
+(A \dmult{m} (B \mmult{n} C))[\bar{a} \oplus \bar{m} \oplus \bar{d} \oplus \bar{c}]
+  &=
+  A[\bar{a} \oplus \bar{m}] \sum_{\forall \bar{n}} B[\bar{m} \oplus \bar{d} \oplus \bar{n}] C[\bar{n} \oplus \bar{c}] \\
+  &=
+  \sum_{\forall \bar{n}} A[\bar{a} \oplus \bar{m}] B[\bar{m} \oplus \bar{d} \oplus \bar{n}] C[\bar{n} \oplus \bar{c}] \\
+  &=
+  \sum_{\forall \bar{n}} (A \dmult{m} B)[\bar{a} \oplus \bar{m} \oplus \bar{d} \oplus \bar{n}] C[\bar{n} \oplus \bar{c}] \\
+  &= ((A \dmult{m} B) \mmult{n} C)[\bar{a} \oplus \bar{b} \oplus \bar{c}]
+\end{align*}
+
+If $m > \shape{\vec{b}}$ then
+\[ \vec{c} = \vec{l} \oplus \vec{r} \]
+\[ \vec{m} = \vec{b} \oplus \vec{l} \]
+\[ \shape{A \dmult{m} (B \mmult{n} C)} = \vec{a} \oplus \vec{b} \oplus \vec{l} \oplus \vec{r} \]
+
+\begin{align*}
+(A \dmult{m} (B \mmult{n} C))[\bar{a} \oplus \bar{b} \oplus \bar{l} \oplus \bar{r}]
+  &=
+  A[\bar{a} \oplus \bar{b} \oplus \bar{l}] \sum_{\forall \bar{n}} B[\bar{b} \oplus \bar{n}] C[\bar{n} \oplus \bar{l} \oplus \bar{r}] \\
+  &=
+  \sum_{\forall \bar{n}} A[\bar{a} \oplus \bar{b} \oplus \bar{l}] B[\bar{b} \oplus \bar{n}] C[\bar{n} \oplus \bar{l} \oplus \bar{r}] \\
+\end{align*}
+
+What about $A \mmult{a} \Ident^2(\vec{a} \oplus \vec{b})$
+
+\begin{align*}
+\left(A \mmult{a} \Ident^2(\vec{a} \oplus \vec{b}) \right)[\bar{b}_1 \oplus \bar{a} \oplus \bar{b}_2]
+  &= 
+  \sum_{\forall \bar{x}}
+    A[\bar{x}] \Ident^2(\vec{a} \oplus \vec{b})[\bar{x} \oplus \bar{b}_1 \oplus \bar{a} \oplus \bar{b}_2] \\
+  &= 
+  \sum_{\forall \bar{x}}
+    A[\bar{x}] \delta_{\bar{x},\bar{a}} \delta_{\bar{b}_1,\bar{b}_2} \\
+  &=
+  \delta_{\bar{b}_1,\bar{b}_2}
+  \sum_{\forall \bar{x}}
+    A[\bar{x}] \delta_{\bar{x},\bar{a}} \\
+  &=
+  \Ident^2(\vec{b})[\bar{b}_2 \oplus \bar{b}_1]
+  A[\bar{a}] \\
+  &=
+  (\Ident^2(\vec{b}) \mmult{0} A) [\bar{b}_2 \oplus \bar{b}_1 \oplus \bar{a}] \\
+  &=
+  \Tran(\Ident^2(\vec{b}) \mmult{0} A, \shape{\vec{b}})[\bar{b}_1 \oplus \bar{a} \oplus \bar{b}_2] \\
+  &=
+  \Tran(A \mmult{0} \Ident^2(\vec{b}), \shape{\vec{a} \oplus \vec{b}})[\bar{b}_1 \oplus \bar{a} \oplus \bar{b}_2] \\
+  &= 
+  \sum_{\forall \bar{x}}
+    \delta_{\bar{b}_1,\bar{b}_2} \delta_{\bar{a},\bar{x}} A[\bar{x}] \\
+  &= 
+  \sum_{\forall \bar{x}}
+    \Ident^2(\vec{b} \oplus \vec{a})[\bar{b}_1 \oplus \bar{a} \oplus \bar{b}_2 \oplus \bar{x}]
+    A[\bar{x}] \\
+  &= 
+  (\Ident^2(\vec{b} \oplus \vec{a}) \mmult{a} A) [\bar{b}_1 \oplus \bar{a} \oplus \bar{b}_2]
+\end{align*}
+
+So
+\[ A \mmult{a} \Ident^2(\vec{a} \oplus \vec{b}) = \Ident^2(\vec{b} \oplus \vec{a}) \mmult{a} A \]
+
+Now what is $A \dmult{a} \Ident^2(\vec{a} \oplus \vec{b})$...
+
+\begin{align*}
+\left(A \dmult{a} \Ident^2(\vec{a} \oplus \vec{b})\right) [\bar{a}_1 \oplus \bar{b}_1 \oplus \bar{a}_2 \oplus \bar{b}_2]
+  &=
+  A [\bar{a}_1] \Ident^2(\vec{a} \oplus \vec{b}) [\bar{a}_1 \oplus \bar{b}_1 \oplus \bar{a}_2 \oplus \bar{b}_2] \\
+  &=
+  A [\bar{a}_1] \delta_{\bar{a}_1, \bar{a}_2} \delta_{\bar{b}_1, \bar{b}_2}
+\end{align*}
+
+\begin{align*}
+\left( A \dmult{a} \Ident^2(\vec{a} \oplus \vec{b}) \mmult{b} B \right)[\bar{a}_1 \oplus \bar{b} \oplus \bar{a}_2]
+  &=
+  \sum_{\forall \bar{x}} A [\bar{a}_1] \Ident^2(\vec{a} \oplus \vec{b}) [\bar{a}_1 \oplus \bar{b} \oplus \bar{a}_2 \oplus \bar{x}] B[\bar{x}] \\
+  &=
+  \sum_{\forall \bar{x}} A [\bar{a}_1] \delta_{\bar{a}_1, \bar{a}_2} \delta_{\bar{b}, \bar{x}} B[\bar{x}] \\
+  &=
+  A [\bar{a}_1] \delta_{\bar{a}_1, \bar{a}_2} B[\bar{b}] \\
+  &=
+  A [\bar{a}_1] B[\bar{b}] \delta_{\bar{a}_1, \bar{a}_2} \\
+  &=
+  \delta_{\bar{a}_2, \bar{a}_1} A [\bar{a}_2] B[\bar{b}] \\
+  &=
+  \Ident^2(\vec{a})[\bar{a}_2 \oplus \bar{a}_1] A [\bar{a}_1] B[\bar{b}] \\
+  &=
+  \left(\Ident^2(\vec{a}) \dmult{a} A\right) [\bar{a}_2 \oplus \bar{a}_1]B[\bar{b}] \\
+  &=
+  \left(\left(\Ident^2(\vec{a}) \dmult{a} A\right) \dmult{0} B\right) [\bar{a}_2 \oplus \bar{a}_1 \oplus \bar{b}] \\
+  &=
+  \left(\Ident^2(\vec{a}) \dmult{a} A \dmult{0} B\right) [\bar{a}_2 \oplus \bar{a}_1 \oplus \bar{b}] \\
+  &=
+  \Tran\left(\Ident^2(\vec{a}) \dmult{a} A \dmult{0} B, a\right) [\bar{a}_1 \oplus \bar{b} \oplus \bar{a}_2]
+\end{align*}
+
+What about $A \dmult{0} \Tran(B, n)$? Is that just $\Tran(A \dmult{0} B, k)$ ?
+
 \end{appendices}

### 2020-08-23 MMatrix/src/covering.cc
Got coverings working.

@@ -240,4 +240,41 @@ const mmatrix::MMatrixInterface* CoveringMatrices::continuity_deriv() {
   return continuity_deriv_.get();
 }
 
+void CoveringMatrices::set_covering_error_params(double p, double r, double d, double c) {
+  covering_weight_p_ = p;
+  covering_weight_r_ = r;
+  covering_weight_d_ = d;
+  covering_weight_c_ = c;
+  covering_error_state_ = 0;
+  covering_error_deriv_state_ = 0;
+}
+
+double CoveringMatrices::covering_error() {
+  if (covering_error_state_ < cur_state_) {
+    covering_error_ =
+      covering_weight_p_*primary() +
+      covering_weight_r_*regulation() +
+      covering_weight_d_*density() +
+      covering_weight_c_*continuity();
+
+    covering_error_state_ = cur_state_;
+  }
+  return covering_error_;
+}
+
+const mmatrix::MMatrixInterface* CoveringMatrices::covering_error_deriv() {
+  if (covering_error_deriv_state_ < cur_state_) {
+    if (covering_error_deriv_ == nullptr) {
+      covering_error_deriv_ = std::unique_ptr<DenseMMatrix>(new DenseMMatrix(weights()->shape()));
+    }
+
+    Combine({primary_deriv(), regulation_deriv(), density_deriv(), continuity_deriv()},
+      {covering_weight_p_, covering_weight_r_, covering_weight_d_, covering_weight_c_},
+      covering_error_deriv_.get());
+
+    covering_error_deriv_state_ = cur_state_;
+  }
+  return covering_error_deriv_.get();
+}
+
 }  // covering

### 2020-08-23 MMatrix/src/covering.h

@@ -11,6 +11,7 @@ class CoveringMatrices {
  public:
   CoveringMatrices(std::unique_ptr<mmatrix::MMatrixInterface> fourier_basis);
 
+  mmatrix::MMatrixInterface* weights();
   void update_weights(std::function<void(mmatrix::MMatrixInterface*)> update);
 
   // The covering and deriv by  weights
@@ -33,6 +34,7 @@ class CoveringMatrices {
   void set_primary_params(double k);
   double primary();
   const mmatrix::MMatrixInterface* primary_deriv();
+  const mmatrix::MMatrixInterface* fourier_basis_regularized();
 
   // The covering density and deriv by weights
   // 0 <= d <= 1
@@ -44,6 +46,17 @@ class CoveringMatrices {
   double continuity();
   const mmatrix::MMatrixInterface* continuity_deriv();
 
+  // The full covering error and deriv by weights
+  // 0 <= p, r, d, c
+  // p+r+d+c = 1 is ideal to avoid effecting the learning rate
+  // p = primary error weight
+  // r = regulation error weight
+  // d = density error weight
+  // c = continuity error weight
+  void set_covering_error_params(double p, double r, double d, double c);
+  double covering_error();
+  const mmatrix::MMatrixInterface* covering_error_deriv();
+
  private:
 
   // The base fourier transform that we will be attempting to cover.
@@ -51,7 +64,6 @@ class CoveringMatrices {
   // The size of the fourier_basis_
   long size_;
   int cur_state_ = 1;
-  mmatrix::MMatrixInterface* weights();
   std::unique_ptr<mmatrix::DenseMMatrix> weights_;
 
   int sigmoid_state_ = 0;
@@ -71,7 +83,6 @@ class CoveringMatrices {
   double primary_;
   int primary_deriv_state_ = 0;
   bool fourier_basis_regularized_update_needed_ = true;
-  const mmatrix::MMatrixInterface* fourier_basis_regularized();
   std::unique_ptr<mmatrix::DenseMMatrix> fourier_basis_regularized_;
   std::unique_ptr<mmatrix::DenseMMatrix> primary_deriv_;
 
@@ -85,6 +96,15 @@ class CoveringMatrices {
   double continuity_;
   int continuity_deriv_state_ = 0;
   std::unique_ptr<mmatrix::DenseMMatrix> continuity_deriv_;
+
+  double covering_weight_p_ = 0.25;
[…]

### 2020-08-23 MMatrix/src/mmatrix.cc

@@ -329,6 +329,40 @@ void SubFrom(const MMatrixInterface* m, MMatrixInterface* out) {
   }
 }
 
+void Combine(const std::vector<const MMatrixInterface*>& matrices, const std::vector<MMFloat>& consts, MMatrixInterface* out) {
+  bool any_null = false;
+  for (const MMatrixInterface* m : matrices) {
+    if(m == nullptr) {
+      any_null = true;
+      break;
+    }
+  }
+  if (out == nullptr || any_null) {
+    throw std::invalid_argument("Combine cannot take null arguments.");
+  }
+  if (matrices.size() != consts.size()) {
+    throw std::invalid_argument("Combine requires same number of consts as matrices.");
+  }
+
+  if (matrices.empty()) {
+    out->zero();
+    return;
+  }
+  
+  int bound = 1;
+  for (int s : matrices[0]->shape()) {
+    bound *= s;
+  }
+
+  for (int i = 0; i < bound; i++) {
+    double term = 0;
+    for (int m = 0; m < matrices.size(); m++) {
+      term += consts[m]*matrices[m]->get(i);
+    }
+    out->set(i, term);
+  }
+}
+
 double Sum(const MMatrixInterface* m) {
   if (m == nullptr) {
     throw std::invalid_argument("Sum cannot take null arguments.");

### 2020-08-23 MMatrix/src/mmatrix.h

@@ -111,6 +111,8 @@ void AddTo(const MMatrixInterface* m, MMatrixInterface* out);
 // Subtracts m from out
 void SubFrom(const MMatrixInterface* m, MMatrixInterface* out);
 
+void Combine(const std::vector<const MMatrixInterface*>& matrices, const std::vector<MMFloat>& consts, MMatrixInterface* out);
+
 // Returns the sum of each element of m
 double Sum(const MMatrixInterface* m);
 

### 2020-08-23 MMatrix/test/test_audio.cc

@@ -1,5 +1,7 @@
 #include "audio.h"
 
+#include "covering.h"
+
 #include <cmath>
 #include <chrono> 
 #include <cstdlib>
@@ -577,7 +579,7 @@ void partialFT(const std::vector<double>& frequencies, double sampleRate, const 
     double freq = frequencies[f];
     partial.clear();
     partial.reserve(samples.size());
-    partialFT(freq, sampleRate, 5.0/freq, samples, &partial);
+    partialFT(freq, sampleRate, 10.0/freq, samples, &partial);
     for (int s = 0; s < samples.size(); s++) {
       out->set({f, s}, partial[s]);
     }
@@ -1116,6 +1118,82 @@ void AutoTune() {
   }
 }
 
+void TestRealCovering() {
+  std::vector<double> samples;
+  std::srand(314);
+  // 44100 1/second
+  int sampleRate = 44100; //44100;
+  // peaks/second
+  // A0 = 27.5
+  // C8 = 4186
+  //double a4 = 440; // 27.5; // 27.5*std::pow(2, 1/12.0);
+  double c4 = 261.63;
+  double d4 = 293.66;
+  double e4 = 329.63;
+
+
+  std::vector<double> notes{e4, d4, c4, d4, e4};
+  for (int i = 0; i < notes.size(); i++) {
+    pushFrequency(notes[i], sampleRate, 0.25, &samples);
+  }
+
+  {
+    std::ofstream f("sample.wav", std::ios::binary);
+    WriteWavFile(f, sampleRate, 2, samples);
+  }
+
+  auto pft = std::unique_ptr<mmatrix::DenseMMatrix>(
+    new mmatrix::DenseMMatrix({3,static_cast<int>(samples.size())}));
+  
+  std::vector<double> frequencies{c4,d4,e4};
+  std::vector<std::string> fnames{"c4", "d4", "e4"};
+  partialFT(frequencies, sampleRate, samples, pft.get());
+
+  for (int i = 0; i < samples.size(); i++) {
+    if (i%(sampleRate/4) == 0) {
+      std::cout << "--------------" << std::endl;
+    }
+    if (i%100 == 0)
+      std::cout << pft->get({0,i}) <<std::endl;
+  }
+
+  // Calculate the coverings.
+  covering::CoveringMatrices coverings(std::move(pft));
+  coverings.set_primary_params(3.2);
+  coverings.update_weights([&](mmatrix::MMatrixInterface* w) {
[…]

### 2020-08-23 MMatrix/test/test_covering.cc

@@ -11,8 +11,8 @@
 using namespace mmatrix;
 using namespace mmatrix::test;
 
-void TestCoveringErrorDerivative() {
-  std::cout << "Testing Covering Error Derivative..." << std::endl;
+void TestCoveringPrimaryDerivative() {
+  std::cout << "Testing Covering Primary Derivative..." << std::endl;
   std::srand(31415);
   std::vector<int> xShape = {3, 10};
   std::vector<int> fShape = {};
@@ -22,17 +22,17 @@ void TestCoveringErrorDerivative() {
   covering::CoveringMatrices covering(std::move(T));
   covering.set_primary_params(6);
 
-  MMFunction covErr = [&](const MMatrixInterface* x, MMatrixInterface* out) {
+  MMFunction primErr = [&](const MMatrixInterface* x, MMatrixInterface* out) {
     covering.update_weights([&](MMatrixInterface* w) { Copy(x, w);});
     out->set(0, covering.primary());
   };
 
-  MMFunction covErrDeriv = [&](const MMatrixInterface* x, MMatrixInterface* out) {
+  MMFunction primErrDeriv = [&](const MMatrixInterface* x, MMatrixInterface* out) {
     covering.update_weights([&](MMatrixInterface* w) { Copy(x, w);});
     Copy(covering.primary_deriv(), out);
   };
 
-  TestGenericDerivative("Covering Error", xShape, fShape, covErr, covErrDeriv, 10, 10);
+  TestGenericDerivative("Covering Primary", xShape, fShape, primErr, primErrDeriv, 10, 10);
 }
 
 void TestCoveringSigmoidDerivative() {
@@ -118,12 +118,37 @@ void TestCoveringRegulationDerivative() {
   TestGenericDerivative("Covering Regulation", xShape, fShape, regErr, regErrDeriv, 10, 10);
 }
 
+void TestCoveringErrorDerivative() {
+  std::cout << "Testing Covering Error Derivative..." << std::endl;
+  std::srand(31415);
+  std::vector<int> xShape = {3, 10};
+  std::vector<int> fShape = {};
+
+  std::unique_ptr<DenseMMatrix> T(new DenseMMatrix(xShape));
+  RandMatrix(T.get(), 0, 0, 1000);
+  covering::CoveringMatrices covering(std::move(T));
+  covering.set_primary_params(6);
+
+  MMFunction covErr = [&](const MMatrixInterface* x, MMatrixInterface* out) {
[…]

### 2020-08-24 Math/book.tex
Making some math notes.

@@
 \usepackage{stmaryrd}
+\usepackage{hyperref}
 
@@
 \DeclareMathOperator{\size}{size}
+\DeclareMathOperator{\FFT}{FFT}
+\DeclareMathOperator{\IFFT}{IFFT}
 %\newcommand{\mmult}[1]{\stackrel{\times}{#1}}
@@
 
+\chapter{Audio Project}
+
+\begin{landscape}
+\section{2d Derivatives with Fast Fourier Transforms}
+
+According to wikipedia \cite{wiki:fourier}, if $f(x)$ is an absolutely continuous differentiable function, and both $f$ and its derivative $f'$ are integrable.
+Then the Fourier transform of the derivative is given by
+\[ \hat{f'}(\xi) = 2 \pi i \xi \hat{f}(\xi) \]
+
+What that means in practice is that we can approximate the derivative of a sequence, or in our case a multimatrix, using a FFT.
+The method I'm using comes from a youtube series by Steve Brunton \cite{youtube:fourier} which I've found to be particularly helpful.
+
+We'll define a function, $\FFT(X) = F$, and it's inverse, $\IFFT(F) = X$ as the fast fourier transform of $X$ and it's inverse of $F$.
+Specifically, we'll let $X$ be a multimatrix of shape $\shape{X} = \left<N\right>$ where $N = 2^p$ for some $p>1$.
+And we'll let $F$ be a multimatrix representing a similar shape of complex numbers, $\shape{F} = \left<N, 2\right>$ where $F[k,1]$ is
+the real componenet and $F[k,2]$ is the imaginary component. So,
+
+\[ \FFT(X)[k,1] = \sum_{n=1}^{N} X[n] \cos\left(\frac{2 \pi (k-1)(n-1)}{N}\right) \]
+\[ \FFT(X)[k,2] = -\sum_{n=1}^{N} X[n] \sin\left(\frac{2 \pi (k-1)(n-1)}{N}\right) \]
+\begin{align*}
+  \IFFT(F)[n]
+  &= \frac{1}{N} \sum_{k=1}^{N} Real\left( (F[k,1]+i F[k,2]) e^{\frac{2 \pi i (k-1)(n-1)}{N} } \right) \\
+  &= \frac{1}{N} \sum_{k=1}^{N} F[k,1] \cos\left(\frac{2 \pi (k-1)(n-1)}{N}\right) - F[k,2] \sin\left(\frac{2 \pi (k-1)(n-1)}{N}\right)
+\end{align*}
+
+Now if $X[n] = g(n)$ we can compute $X'$ where $X'[n] = g'(n)$ by the calculation,
+
+\[ X' = \IFFT(C(\FFT(X))) \]
+\[ C(F)[k,1] = \frac{-2 \pi (k-1)}{N} F[k,2] \]
+\[ C(F)[k,2] = \frac{2 \pi (k-1)}{N} F[k,1] \]
+
+\end{landscape}
+
+\chapter{Future Subjects of Study}
+
+The association between product spaces and null spaces. So, if we have $\shape{A} = \vec{a} \oplus \vec{n}$
+then we'll define $ProdSpace(A, n)$ and $NullSpace(A, n)$ as the possible outputs of
+\[ A \mmult{n} X = Y \]
+And the possible solutions to,
+\[ A \mmult{n} X = 0 \]
+Respectively where in both cases $\shape{X} = \vec{n}$. 
+Note that $ProdSpace(A, n) \subset R^{\vec{a}}$ and $NullSpace(A, n) \subset R^{\vec{n}}$
+
+Now for any multimatrices $B$ and $C$ of the same shape, $\shape{B} = \shape{C} = \vec{s}$,
+they are defined as 'orthogonal', i.e. $B \bot C$ iff $B \mmult{\shape{s}} C = 0$.
+And two sets are orthogonal if all any member from one is orthogonal to any member of the other.
+
+I hypothesize that,
+\[ProdSpace(A, n) \bot NullSpace(\Tran(A, a), a)\]
+and
+\[NullSpace(A, n) \bot ProdSpace(\Tran(A, a), a)\]
+based on a similar theory for 2d matrices \cite{youtube:orthogonal} (and the fact that the shapes line up nicely).
+
+And from there I think you can derive a solution to the least squares problem for multimatrices.
+
+If $B - A \mmult{n} X = E$ and where you want to minimize $SS(E)$, you could solve this with derivatives
+but, notice that a shortest $E$ is necessarily orthogonal $ProdSpace(A,n)$ by simple geometry since it is a shortest
+vector from $ProdSpace(A,n)$ to $B$. So if our above hypothesis is correct, $B$ is in $NullSpace(\Tran(A,a), a)$
+
+Therefore the solution to $\Tran(A,a) \mmult{a} E = 0$ for $E$ will be the one that minimizes $SS(E)$. So,
+\begin{align*}
+  \Tran(A,a) \mmult{a} E &= 0 \\
+  \Tran(A,a) \mmult{a} (B - A \mmult{n} X) &= 0 \\
+  \Tran(A,a) \mmult{a} B - \Tran(A,a) \mmult{a} (A \mmult{n} X) &= 0 \\
+  \Tran(A,a) \mmult{a} B - \Tran(A,a) \mmult{a} A \mmult{n} X &= 0 \\
+  \Tran(A,a) \mmult{a} B &= \Tran(A,a) \mmult{a} A \mmult{n} X \\
+  \Tran(A,a) \mmult{a} A \mmult{n} X &= \Tran(A,a) \mmult{a} B
+\end{align*}
+
+This brings to mind the fact that multimatrices themselves form a vector space. Basically, for any shape $\vec{x}$
+there is an associated vector space of multimatrices $R^{\vec{x}}$. And I haven't yet explictly stated that. Need to do
+that because I'm pretty sure that's necesary for the shortest path being the one that's orthoganal.
+
+I think need to prove, in the abstract, that if you have a vector field $F$
+and a distance metric $d(u,v)$ and a bilinear form \cite{wiki:bilinear}, $b(u,v)$, such that
+\[ v \bot u \iff b(u,v) = 0 \]
+Then for any $v \in F$ and any sub field $f \subset F$, for all $u \in f$,
+\[ (v-u) \bot u \iff \forall u' \in f - \{u\} : d(u', v) < d(u,v) \]
+That is, $u$ is the closest vector in $f$ to $v$ if and only if it is the orthoganal project of $v$ onto $f$.
+
 \chapter{Scratch}

### 2021-01-03 Math/book.tex
Continuing to work on math.

@@
 \usepackage{hyperref}
+% package used for \shrug
+\usepackage{tikz}
 
@@
 
+\newcommand{\shrug}[1][]{%
+\begin{tikzpicture}[baseline,x=0.8\ht\strutbox,y=0.8\ht\strutbox,line width=0.125ex,#1]
+\def\arm{(-2.5,0.95) to (-2,0.95) (-1.9,1) to (-1.5,0) (-1.35,0) to (-0.8,0)};
+\draw \arm;
+\draw[xscale=-1] \arm;
+\def\headpart{(0.6,0) arc[start angle=-40, end angle=40,x radius=0.6,y radius=0.8]};
+\draw \headpart;
+\draw[xscale=-1] \headpart;
+\def\eye{(-0.075,0.15) .. controls (0.02,0) .. (0.075,-0.15)};
+\draw[shift={(-0.3,0.8)}] \eye;
+\draw[shift={(0,0.85)}] \eye;
+% draw mouth
+\draw (-0.1,0.2) to [out=15,in=-100] (0.4,0.95); 
+\end{tikzpicture}}
+
 \begin{document}
@@
 I was working my way through a hobby programming project, trying to create deep fakes of
-\sout{polititians in compromising positions} humorous celebrity mashups, when I ran into a problem.
+\sout{politicians in compromising positions} humorous celebrity mashups, when I ran into a problem.
 The existing notation for derivatives of matrix equations is terrible.
@@
 
-So, I set out to invent a system of my own. Much to my surprise, some of the
-results with were rather elegant. For example, I stumbled onto a
+So I set out to invent a system of my own. Much to my surprise, some of the
+results were actually kinda neat. For example, I found a
 multidimensional version of the derivative chain rule (Thm. \ref{mmm_chain_rule})
-that's nearly as consise as the same rule for scalars.
+that's nearly as concise as the same rule for scalars.
 
 The ultimate goal of this notation system was to \sout{bring about the downfall
-of humanity} figure out a way to take derivatives
-of matrix equations without having to break apart matricies into their constituent
-parts. I knew that I had succeeded when I was able to derive the derivative of the
-softmax function completely in my own notation (Thm. \ref{softmax_derivative}).
-
-Now, not knowing what else to do with the results, I've written this book
-about my exploration into multidimensional matricies,
-multimatricies, and how they can elucidate derivatives of matrix equations.
+of the military industrial complex} figure out a way to take derivatives
+of matrix equations without having to break apart matrices into their constituent
+parts. I've been able to derive the derivative of the softmax function completely
+in my own notation (Thm. \ref{softmax_derivative}) so I can safely say I succeeded.
+
+Granted, that proof is longer than the original. And harder to follow. So maybe the 
+system isn't exactly ``elegant'' but it does serve its intended purpose as a new lens
+on derivatives involving matrices. It just comes with its own set of
+problems, like an algebra with multiple ternary operators. \shrug
+
+Now, not really knowing what else to do, I've written this book about my exploration into
+multidimensional matrices, `multimatrices', and how they can elucidate
+(or obfuscate) derivatives of matrix equations.
 
@@
 
-To demonstrate how the problem with traditional matricies, let's take a look at a
+To demonstrate the problem with traditional matrices, let's take a look at a
 simple matrix equation.
 
-Let's say we have a small class of undergraduates packed, conveniently in a 3 by 5
-grid. We'll let $X$ be the matrix representing number of semesters of science
-classes each of those student has taken.
-Then let $B$ represent the belief each of those undergradutes has in a higher power,
-thier BHP if you will.
-
-As we all know, Weinersmith's hypothisis states that an undergraduate's belief in a
+Let's say we have a small class of undergraduates packed, conveniently, into a 3 by 5
+seating arrangement. Each of these students is at a different point in their education
+and some of them are taking more classes than others.
+Let's label their total level of education with a matrix, $X$, where each entry
+in the matrix is the number of hours of science classes each student has taken.
+
+As we all know, Weinersmith's hypothesis states that an undergraduate's belief in a
 higher power fluctuates with respect to their scientific education in a sinusoidal
@@
 
-Let's formally state the shape of these two matricies,
-$\shape{B} = \shape{X} = \left< 3,5 \right>$. (Throughout this work, I'll be using
+For a simplified model of this, lets then say that another matrix $B$ represents the
+belief each of our undergraduates has in a higher power, their BHP if you will.
+
+Let's formally state the shape of these two matrices,
+$\shape{B} = \shape{X} = \left< 3,5 \right>$.\footnote{Throughout this work, I'll be using
 $\shape{M}$ to denote the shape of $M$ rather than the determinate because, frankly, it
-is just comes up more frequently.)
+is just comes up more frequently and determinants aren't simple enough to deserve that
+brief of notation when it comes to multimatrices.}
 Each element of $B$ will be the sine of the corresponding element of
@@
 $\partial B_{r_1, c_1}/\partial X_{r_2, c_2}$ is defined as the rate of change of
-\textit{one} undergraduate's BPH with respect to \textit{one}
+\textit{one} undergraduate's BHP with respect to \textit{one}
 undergraduate's education level - it only represents a change to part of the whole
@@
 
-This can also be writen more simply using Kronecker deltas \cite{wiki:kronecker},
-which should make one feel particularly intellegent as Kronecker deltas were used
+This can also be written more simply using Kronecker deltas \cite{wiki:kronecker},
+which should make one feel particularly intelligent as Kronecker deltas were used
 by Einstein (and presumably someone named Kronecker) \cite{wiki:einstein}.
@@
 
-But what about the complete deriative?
-What sort of mathmatical object would represent the entire derivative
+But what about the complete derivative?
+What sort of mathematical object would represent the entire derivative
 of $B$ with respect to $X$?
@@
 If this were a function that mapped a vector to a scalar, you might say that the
-complete derivate was the gradient. But in this case, our function's output is more
+complete derivative was the gradient. But in this case, our function's output is more
 than a simple scalar and even our dependent variable is more complex than a vector.
@@
 
-And so, the size of the complete derivate would be,
+And so, the size of the complete derivative would be,
 \[
@@
 Perhaps we could even let this help us define the `shape' of the complete
-derivative. Note that there seem to be four independent indicies to each element
+derivative. Note that there seem to be four independent indices to each element
 of this matrix, namely $r_1$, $c_1$, $r_2$, and $c_2$.
@@
 dimensionality of the output. What's important is that the dimensionality of
-both output and indepenedent variable are preserved and that our notation is
+both output and independent variable are preserved and that our notation is
 consistent.
@@
 
-So anyways, our total derivate is a multidimensional object with four indicies.
+So anyways, our total derivative is a multidimensional object with four indices.
 Suppose we try to pull a single partial derivative from this complete derivative,
-what could our notation look like? Four underscript indicies would be unwieldy,
+what could our notation look like? Four underscript indices would be unwieldy,
 so maybe something like this:
@@
 And since we're defining our own notation, let's go wild and reference our original
-matricies in a similar manner:
+matrices in a similar manner:
 \[
@@
 
-Programmers might call this object a `tensor' but mathematitians might
+Programmers might call this object a `tensor' but mathematicians might
 scream at those same programmers, ``WE ALREADY HAVE A DEFINITION OF A TENSOR! DIE!''
@@
 
-Let's define this bit of notation formaly.
+Let's define this bit of notation formally.
 
@@
 
-We can further simplify that notation for our set of valid indicies. Let's say we have
+We can further simplify that notation for our set of valid indices. Let's say we have
 some $\vec{v} \in \mathbb{N}^n$ that defines the shape of some matrix. Then we'll
-define the set of valid indicies of that matrix to be $\Dim(\vec{v})$.
+define the set of valid indices of that matrix to be $\Dim(\vec{v})$.
 
 Each value of $M$ is a real value, so we'll define the set of all real valued
-multidimensional matricies with shape $\vec{v}$ as $\mathbb{R}^{\vec{v}}$.
+multidimensional matrices with shape $\vec{v}$ as $\mathbb{R}^{\vec{v}}$.
 
 We'll use the notation $M[\bar{v}]$ to reference any individual scalar value of $M$
-at indicies $\bar{v} \in \Dim(\shape{M})$. 
+at indices $\bar{v} \in \Dim(\shape{M})$. 
 \end{definition}
 
-That's a huge informtion dump so look at an example.
+That's a huge information dump so look at an example.
 
@@
 \begin{definition}[Scalar Filled Multimatrices]
-For convenience, I'll often refer to multimatricies filled with a single value,
+For convenience, I'll often refer to multimatrices filled with a single value,
 $s \in \mathbb{R}$,
@@
 Going back to our original motivating problem, we (that is to say, myself and the voices
-in my head whom I reference as to give my writing the percieved authority
-of more than one author) can express our derivative notation thusly,
+in my head whom I reference as to give my writing the perceived authority
+of more than one author) can express our derivative notation thus,
 
@@
 
-Ok, that's neat and all but what does that actually mean? Can we answer our motivating 
+OK, that's neat and all but what does that actually mean? Can we answer our motivating 
 question?
@@
 Well... sort of. We have to abuse the notation a little and say that $B$ and $X$ are
-just multimatricies with 2 dimensions. Then we can say that the total derivative
+just multimatrices with 2 dimensions. Then we can say that the total derivative
 of $B$ with respect to $X$ is a multimatrix with shape $\shape{B} \oplus \shape{X}$,
@@
 But that single line will require defining multimatrix multiplication and
-a mysterious, and possibly dangerious, entity call a cubic identity, $\Ident^3(\shape{X})$.
+a mysterious, and possibly dangerous, entity call a cubic identity, $\Ident^3(\shape{X})$.
 
@@
 
-The multiplication of traditional matricies is often considered a rather confusing
+The multiplication of traditional matrices is often considered a rather confusing
 proposition, especially when one first encounters it.
@@
 
-Just to review, for two matricies $A$ and $B$, multipication is only defined
+Just to review, for two matrices $A$ and $B$, multiplication is only defined
 for $A \times B = C$ if $A$ has the same number of columns as $B$ has rows.
@@
 then $A \times B$ is valid if and only if $c_a = r_b$. And furthermore,
-the remaining dimensions of $A$ and $B$ define the diminsions of $C$,
+the remaining dimensions of $A$ and $B$ define the dimensions of $C$,
 $\shape{C} = \left< r_a, c_b \right>$. Each element of $C$ is a sum of the product of
@@
 
-Easily done. The hard part isn't doing the calculation. The hard part getting over
-your naive belief that mathematical operations should be rooted in some concrete
-concept rather than ``this is the way it's done because it makes the equations
-work.''
-
-So now consider how we would multiply two matricies $A$ and $B$ if they had more
-than two dimensions. Let's use a concrete example to make the problems more
-structurally sound.
+Easily done. The hard part isn't doing the calculation. The hard part is reframing the
+damn problem in your head as its geometric or `systems of equations' equivalent so that
+the operation is at least somewhat intuitive.
+
+So now consider how we would multiply two matrices $A$ and $B$ if they had more
+than two dimensions. Which doesn't really leverage either of those intuitive
+approaches. Let's use a concrete example to make the problems more structurally sound.
 
@@
 definition seems more... er... multidimensional... but it also seems to
-arbitrarily depend on the shape of the two matricies.
+arbitrarily depend on the shape of the two matrices.
 
 What we really need is an operation which covers both lines of reasoning. To do
-so, we need to compleately abandon conventional algebras, and indeed any hope of
+so, we need to completely abandon conventional algebras, and indeed any hope of
 returning to sanity. We need... a ternary operator.
@@
 
-But the shape is only a small component of the multipliation  operation. Let's
+But the shape is only a small component of the multiplication  operation. Let's
 just jump into the formal definition and I'll explain with an example:
@@
 \label{mm_mult}
-Let $A$ and $B$ be multimatricies such that $\shape{A} = \vec{a} \oplus \vec{c}$,
+Let $A$ and $B$ be multimatrices such that $\shape{A} = \vec{a} \oplus \vec{c}$,
 $\shape{B} = \vec{c} \oplus \vec{b}$, and $\shape{\vec{c}} = n$ with
-$n \in \{0\} \cup \mathbb{N}$. We shall call $n$ the 'size' or the 'width'
-or the 'overlap' of the multiplication operation.
+$n \in \{0\} \cup \mathbb{N}$. We shall call $n$ the `size' or the `width'
+or the `overlap' of the multiplication operation.
 The shape of the result is defined, $\shape{A \mmult{n} B} = \vec{a} \oplus \vec{b}$
@@
 define their values in a three dimensional grid but I fear that my three dimensional
-\LaTeX skills aren't up to the task (and three dimensional monitors are quite hard to
+\LaTeX~ skills aren't up to the task (and three dimensional monitors are quite hard to
 come by). So here is where we leave behind nice graphical representations of
@@
 
-It's important to notice that this operation is identital to standard
+It's important to notice that this operation is identical to standard
 matrix multiplication for two dimensional multimatrices. For instance,
-if $A$ and $B$ are two dimensional multimatricies with shapes
+if $A$ and $B$ are two dimensional multimatrices with shapes
 $\shape{A} = \left<l_a, r_a\right>$ and $\shape{B} = \left<l_b, r_b\right>$
@@
 Multimatrix multiplication may not even make sense dimensionally when you move
-around parentheses. Take for example multimatricies $A$, $B$, and $C$ such that,
+around parentheses. Take for example multimatrices $A$, $B$, and $C$ such that,
 $\shape{A} = \left<5,3,2\right>$,
@@
 may not be associative (Honestly, how could you be so naive?). 
-Take, for example, multimatricies $A$, $B$, and $C$ such
+Take, for example, multimatrices $A$, $B$, and $C$ such
 that $\shape{A} = \left<2,2,2,2\right>$, $\shape{B} = \left<2,2,2\right>$, and
@@
 Which goes to show that even though both $(A \mmult{2} B) \mmult{2} C$ and
-$A \mmult{2} (B \mmult{2} C)$ are valid calculations which result in multimatrixes
+$A \mmult{2} (B \mmult{2} C)$ are valid calculations which result in multimatrices
 of the same dimensionality, they are not equal so multiplicative associativity
@@
 
-However, there are a broad catagory of cases where associativity \textit{does} hold:
+However, there are a broad category of cases where associativity \textit{does} hold:
 
@@
 \label{mm_associativity}
-Let $A$, $B$, and $C$ be multimatricies and $m$ and $n$ in
+Let $A$, $B$, and $C$ be multimatrices and $m$ and $n$ in
 $\{0\} \cup \mathbb{N}$.
@@
 \begin{proof}
-Let $A$, $B$, and $C$ be matricies such that the calculations
+Let $A$, $B$, and $C$ be matrices such that the calculations
 $(A \mmult{m} B) \mmult{n} C$ and $A \mmult{m} (B \mmult{n} C)$ are both valid
 and $m + n \le \shape{\shape{B}}$.
-Then the following must be true by the definiton of multimatrix multiplication
+Then the following must be true by the definition of multimatrix multiplication
 (Def. \ref{mm_mult}).
@@
 
-Looking at each element of the result matricies, let $j$ and $k$ be the values
+Looking at each element of the result matrices, let $j$ and $k$ be the values
 of some parallel cells in $(A \mmult{m} B) \mmult{n} C$ and
-$A \mmult{m} (B \mmult{n} C)$ respectively. Then for some indicies of those cells,
+$A \mmult{m} (B \mmult{n} C)$ respectively. Then for some indices of those cells,
 $\bar{a} \oplus \bar{b} \oplus \bar{c} \in
@@
 Along the same vein, it's also true that there is a consistent time when
-multimatrix multiplication is communicative - when both multimatricies are
+multimatrix multiplication is communicative - when both multimatrices are
 the same shape and the multiplication is combining them completely into a
@@
 
-Multiplicative identities for multimatricies depend on the shape of the
-multimatrix they are being multiplied against, just as for regular matricies.
+Multiplicative identities for multimatrices depend on the shape of the
+multimatrix they are being multiplied against, just as for regular matrices.
 However, the multiplicative identity also greatly depends on the size of
 the particular multiplication operation. Making a confusing and frightening
-situation even more so, like loosing a troup of clowns in children's cancer ward.
+situation even more so, like loosing a troupe of clowns in children's cancer ward.
 
@@
 \[ \shape{\Ident^n(\vec{v})} = \bigoplus_{i = 1}^n \vec{v}  = n * \vec{v} \]
-That is, it's shape is $n$ successive concatinations of $\vec{v}$.
+That is, it's shape is $n$ successive concatenations of $\vec{v}$.
 Let each element of $\Ident^n(\vec{v})$ is defined as,
@@
 \label{mm_ident}
-For all multimaticies, $A$, and all vectors, $\vec{m}$ and $\vec{n}$,  on which
+For all multimatrices, $A$, and all vectors, $\vec{m}$ and $\vec{n}$,  on which
 these operations are valid,
@@
 If there is a matrix $X$ of shape $\vec{x} \oplus \vec{x}$ such that
-for all matricies, $A$, for which the operation is defined,
+for all matrices, $A$, for which the operation is defined,
 
@@
 
-Or if for all matricies, $B$, for which the operation is defined,
+Or if for all matrices, $B$, for which the operation is defined,
 
@@
 \begin{ppart}
-If for all multimatrixes, $A$, on which $A \mmult{\shape{\vec{x}}} X$ is defined, 
+If for all multimatrices, $A$, on which $A \mmult{\shape{\vec{x}}} X$ is defined, 
 $A \mmult{\shape{\vec{x}}} X = A$ this implies that, in the case of $A = \Ident^2(\vec{x})$,
@@
 \begin{ppart}
-If for all multimatrixes, $B$, on which $X \mmult{\shape{\vec{x}}} B$ is defined, 
+If for all multimatrices, $B$, on which $X \mmult{\shape{\vec{x}}} B$ is defined, 
 $X \mmult{\shape{\vec{x}}} B = B$ this implies that, in the case of $B = \Ident^2(\vec{x})$,
@@
 \[ \bar{x}_I = \bigoplus_{i=1}^{n-k} \bar{x}_i \]
-We'll also need a similarly denoted $\bar{y}_1 \ldots \bar{y}_k$ for the free indicies of
+We'll also need a similarly denoted $\bar{y}_1 \ldots \bar{y}_k$ for the free indices of
 the sum below and that shall also be represented as,
@@
 Notice that $\Ident^n(\vec{x})[\bar{y}_J \oplus \bar{x}_I] = \Ident^n(\vec{x})[\bar{x}_I \oplus \bar{y}_J]$
-since the sub index vectors will always either be equal or not equal, $1$ or $0$, their order doesnt matter.
+since the sub index vectors will always either be equal or not equal, $1$ or $0$, their order doesn't matter.
 So,
@@
 In the sum below, let $\bar{y}_1, \bar{y}_2 \ldots \bar{y}_m$ each in $\Dim(\vec{x})$ be the
-free indicies denoted,
+free indices denoted,
 \[\bigoplus_{j = 1}^m \bar{y}_j = \bar{y}_J \]
@@
 
-Multimatrix identities also tend to cancel eachother out when multiplied by
+Multimatrix identities also tend to cancel each other out when multiplied by
 multiples of their base shape lengths.
@@
 \begin{proof}
-Consider that for some indicies vectors
+Consider that for some indices vectors
 $\bar{a}_1, \bar{a}_2 \ldots \bar{a}_{m-k}$
@@
 \[ \bigoplus_{j=1}^{n-k} \bar{b}_j = \bar{b}_J \]
-In the sums below we'll let $\bar{c}_1, \bar{c}_2 \ldots \bar{c}_k$ be free indicies
+In the sums below we'll let $\bar{c}_1, \bar{c}_2 \ldots \bar{c}_k$ be free indices
 each in $\Dim(\vec{x})$ and denote,
@@
 definition (theorem?). Does it still count as a theorem if it only works because
-I tweeked the definition of multimatrix multiplication to make it fit? I feel
+I tweaked the definition of multimatrix multiplication to make it fit? I feel
 a bit like Tommy Wiseau writing my own sex scene into the script... twice... God,
@@
 or right multiplication? Multiplication by what width? It's not clear which of these specifications
-is even required: consider that multiplication is not communicative for regular 2d matricies but
+is even required: consider that multiplication is not communicative for regular 2d matrices but
 those have simple multiplicative inverses (if an inverse exists).
@@
 \begin{theorem}[Shape of Inverses]
+\label{inverse_shape}
 If $\RMult[n,Y]$ is an inverse of $\RMult[m,X]$ where $\shape{X} = \vec{m} \oplus \vec{x}$ and
@@
 This is all well and good, but I'm sure what you really want to know is how to find a multiplicative inverse.
-It seams increadibly complicated until you realize that there is a way to relate any multimatrix multiplication
+It seams incredibly complicated until you realize that there is a way to relate any multimatrix multiplication
 to a 2d matrix multiplication. We'll first need to define a special function:
@@
 Where $\Idx[\vec{x}]^{-1}(n)[i]$ is the $i$th value of the vector output of $\Idx[\vec{x}]^{-1}(n)$.
-Also, $\remainder$ is the remainder function.
+And where, $\remainder$ is the remainder function.
+That is, for integers $a$, $b$, and $c$, $\remainder(a,b) = c$ if and only if $0 \le c < b$
+and there exists an integer $m$ such that $a = mb + c$.
 \end{definition}
@@
 Let's prove those properties of the indexing function before moving on. If we prove that the inverse function
-really is an inverse, then that implies the function is one-to-one. So let's just do that:
-
-\begin{proof}
-Let $\bar{x} \in \Dim(\vec{x})$ and let $k$ be any index of $\bar{x}$.
-
-\begin{align*}
-  \Idx[\vec{x}]^{-1}(\Idx[\vec{x}](\bar{x}))[k] &= 
-  \left\lfloor
-    \frac{\remainder\left(
-      \sum_{1 \le i \le \shape{\vec{x}}} \left( (\bar{x}[i]-1) \prod_{1 \le j < i} \vec{x}[j] \right) 
-      , \prod_{1 \le m \le k} \vec{x}[m]\right)}
-    {\prod_{1 \le n < k} \vec{x}[n]}
-  \right\rfloor + 1 \\
-  &=
-  \left\lfloor
-    \frac{\remainder\left(
-      \sum_{1 \le i \le k} \left( (\bar{x}[i]-1) \prod_{1 \le j < i} \vec{x}[j] \right) 
-      , \prod_{1 \le m \le k} \vec{x}[m]\right)}
-    {\prod_{1 \le n < k} \vec{x}[n]}
-  \right\rfloor + 1 \\
-  &=
-  \left\lfloor
-    \frac{
-      \sum_{1 \le i \le k} \left( (\bar{x}[i]-1) \prod_{1 \le j < i} \vec{x}[j] \right) 
-    }
-    {\prod_{1 \le n < k} \vec{x}[n]}
-  \right\rfloor + 1 \\
-  &=
-  \left\lfloor
-    \frac{
-      \sum_{1 \le i < k} \left( (\bar{x}[i]-1) \prod_{1 \le j < i} \vec{x}[j] \right) 
-    }
-    {\prod_{1 \le n < k} \vec{x}[n]}
-    +
-    (\bar{x}[k]-1)
-  \right\rfloor + 1 \\
-  &= \bar{x}[k]-1+1 \\
-  &= \bar{x}[k]
-\end{align*}
-
-A couple of leaps of logic there rely on the fact that 
+really is an inverse, then that implies the function is one-to-one. So let's start with that:
+
+\begin{proof}
+For this proof, we'll need to know that, for all $\bar{x} \in \Dim(\vec{x})$,
 \[
@@
 \]
-Which is true because
+Which follows from this logic,
 \begin{align*}
@@
   &< \prod_{1 \le m \le k} \vec{x}[m] \\
-  \left( \prod_{1 \le j \le k} \vec{x}[j] \right)-1
+  \left( \prod_{1 \le j < k+1} \vec{x}[j] \right)
+  + \sum_{1 \le (i-1) < k} \left( \prod_{1 \le j < (i-1)+1} \vec{x}[j] \right)
+  - \sum_{1 < i \le k} \left( \prod_{1 \le j < i} \vec{x}[j] \right)
+  - 1
+  &< \prod_{1 \le m \le k} \vec{x}[m] \\
+  \left( \prod_{1 \le j \le k} \vec{x}[j] \right)
   + \sum_{1 < i \le k} \left( \prod_{1 \le j < i} \vec{x}[j] \right)
   - \sum_{1 < i \le k} \left( \prod_{1 \le j < i} \vec{x}[j] \right)
+  -1
   &< \prod_{1 \le m \le k} \vec{x}[m] \\
@@
 \end{align*}
-Note in the 4th step there that $\bar{x}[i] \le \vec{x}[i]$ so replacing it with $\vec{x}[i]$
+Note that, in the 3rd step, $\bar{x}[i] \le \vec{x}[i]$ so replacing it with $\vec{x}[i]$
 will not increase the maximum value.
 
-So, that concludes the proof. Since the inverse works for any index of $\bar{x}$ we know that the inverse works to restore the
+Now, let $\bar{x} \in \Dim(\vec{x})$ and let $k$ be any index of $\bar{x}$.
+Then lets apply the indexing function and its inverse to $\bar{x}$ and see if we get
+back $\bar{x}$. Firstly,
+
+\begin{align*}
+  \Idx[\vec{x}]^{-1}(\Idx[\vec{x}](\bar{x}))[k] &= 
+  \left\lfloor
+    \frac{\remainder\left(
+      \sum_{1 \le i \le \shape{\vec{x}}} \left( (\bar{x}[i]-1) \prod_{1 \le j < i} \vec{x}[j] \right) 
+      , \prod_{1 \le m \le k} \vec{x}[m]\right)}
+    {\prod_{1 \le n < k} \vec{x}[n]}
+  \right\rfloor + 1 \\
+  &=
+  \left\lfloor
+    \frac{\remainder\left(
+      \sum_{1 \le i \le k} \left( (\bar{x}[i]-1) \prod_{1 \le j < i} \vec{x}[j] \right) 
+      , \prod_{1 \le m \le k} \vec{x}[m]\right)}
+    {\prod_{1 \le n < k} \vec{x}[n]}
+  \right\rfloor + 1
+\end{align*}
+Because $\prod_{1 \le j < i} \vec{x}[j]$ is a multiple of $\prod_{1 \le m \le k} \vec{x}[m]$
+when $i > k$ so those terms in the sum will not affect the output of that $\remainder$ operation.
+And since $0 \le \sum_{1 \le i \le k} \left( (\bar{x}[i]-1) \prod_{1 \le j < i} \vec{x}[j] \right) < \prod_{1 \le m \le k} \vec{x}[m]$,
+we can drop that $\remainder$ operation entirely.
+\begin{align*}
+  \Idx[\vec{x}]^{-1}(\Idx[\vec{x}](\bar{x}))[k] &= 
+  \left\lfloor
+    \frac{
+      \sum_{1 \le i \le k} \left( (\bar{x}[i]-1) \prod_{1 \le j < i} \vec{x}[j] \right) 
+    }
+    {\prod_{1 \le n < k} \vec{x}[n]}
+  \right\rfloor + 1 \\
+  &=
+  \left\lfloor
+    \frac{
+      \sum_{1 \le i < k} \left( (\bar{x}[i]-1) \prod_{1 \le j < i} \vec{x}[j] \right) 
+    }
+    {\prod_{1 \le n < k} \vec{x}[n]}
+    +
+    (\bar{x}[k]-1)
+  \right\rfloor + 1 \\
+\end{align*}
+Then with a small change we can use our earlier lemma again to show that the
+residue under that floor function is non negative and less than 1 and things move swiftly from there,
+\begin{align*}
+  \Idx[\vec{x}]^{-1}(\Idx[\vec{x}](\bar{x}))[k] &= 
+  \left\lfloor
+    \frac{
+      \sum_{1 \le i \le k-1} \left( (\bar{x}[i]-1) \prod_{1 \le j < i} \vec{x}[j] \right) 
+    }
+    {\prod_{1 \le n \le k-1} \vec{x}[n]}
+  \right\rfloor
+  +(\bar{x}[k]-1)+1 \\
+  &= 0+\bar{x}[k]-1+1 \\
+  &= \bar{x}[k]
+\end{align*}
+
+Which wraps up the proof. Since the inverse works for any value $k$ of $\bar{x}$ we know that the inverse works to restore the
 whole of the vector. Thus, $\Idx[\vec{x}]^{-1}$ is indeed the inverse of $\Idx[\vec{x}]$.
@@
 
-TODO:exposition
+We'll also need to know how to concatenate vectors under this indexing function for later proofs.
+By which I mean we'll need the following theorem.
 
@@
 Now you might be wondering what that indexing function has to do with inverting
-multimatricies. I said before that it we would need to show how the multiplication
-of two multimatricies can be converted into an equivelent multiplication of two
-2d matricies. Here's how that's done,
+multimatrices. I said before that it we would need to show how the multiplication
+of two multimatrices can be converted into an equivalent multiplication of two
+2d matrices. But the relevant theorem can actually be stated even more generally.
 
 \begin{theorem}[Reshaping Multimatrix Multiplication]
-Let $A$ and $B$ be two multimatricies of shapes $\shape{A} = \vec{a} \oplus \vec{c}$ and
+Any multimatrix multiplication problem can be reshaped into a new multimatrix
+multiplication problem so long as the total number of elements in each of the multimatrices
+is preserved.
+
+Formally, let $A$ and $B$ be two multimatrices of shapes $\shape{A} = \vec{a} \oplus \vec{c}$ and
 $\shape{B} = \vec{c} \oplus \vec{b}$, and let $C$ be the multimatrix resulting in the $\shape{\vec{c}}$
@@
 $\shape{\Dim(\vec{c})} = \shape{\Dim(\vec{z})}$.
-Then for multimatricies $X$, $Y$, and $Z$ defined such that,
+Then for multimatrices $X$, $Y$, and $Z$ defined such that,
 \[\forall i : 0 \le i < \size(A) \]
@@
 \begin{proof}
-Let $A$ and $B$ be two multimatricies of shapes $\shape{A} = \vec{a} \oplus \vec{c}$ and
+Let $A$ and $B$ be two multimatrices of shapes $\shape{A} = \vec{a} \oplus \vec{c}$ and
 $\shape{B} = \vec{c} \oplus \vec{b}$, and let $C$ be the multimatrix resulting from,
@@
 $\shape{\Dim(\vec{c})} = \shape{\Dim(\vec{z})}$.
-And let multimatricies $X$, $Y$, and $Z$ be defined such that,
+And let multimatrices $X$, $Y$, and $Z$ be defined such that,
 \[\forall i : 0 \le i < \size(A) \]
@@
 
-Therefore for any $\RMult(m,X)$ you can potentially find an inverse with
-multiplication width $n \le \shape{\shape{X}}-m$ by simply reshaping the problem into
-one using standard two dimensional matricies wich already has thoroughly
-explored methods for solving.
+Therefore for any $\RMult(m,X)$ or $\LMult(m,X)$ you can find an inverse (if one exists)
+by simply reshaping the problem into one using standard two dimensional matrices.
+A problem which already has thoroughly explored methods for solving.
+
 For example, to find an $\RMult(n,Y)$ which is the inverse of $\RMult(m,X)$
@@
 and   $\shape{B} = \left<\size(\Dim(\vec{x_r})),  \size(\Dim(\vec{y}))\right>$.
-Then solve for $B$ and return the problem to the original shape to get $Y$.
-
-%todo: give example
+Then solve for $B$. And when we return the problem to the original shape, we get $Y$.
+
+\begin{example}
+Lets find all the inverses of $X \mmult{2} A$ where $\shape{A} = <2,2,2,2>$ and
+its values are given by this table:
+\begin{table}[h!]
+\begin{center}
+\begin{tabular}{c c c c | c}
+$\bar{a}[1]$ & $\bar{a}[2]$ & $\bar{a}[3]$ & $\bar{a}[4]$ & $A[\bar{a}]$ \\
+\hline
+1           & 1           & 1           & 1           & -1 \\
+2           & 1           & 1           & 1           & 2 \\
+1           & 2           & 1           & 1           & 0 \\
+2           & 2           & 1           & 1           & 0 \\
+
+1           & 1           & 2           & 1           & 1 \\
+2           & 1           & 2           & 1           & 0.5 \\
+1           & 2           & 2           & 1           & 0 \\
+2           & 2           & 2           & 1           & 0 \\
+
+1           & 1           & 1           & 2           & 0 \\
+2           & 1           & 1           & 2           & 0 \\
+1           & 2           & 1           & 2           & -1 \\
+2           & 2           & 1           & 2           & 2 \\
+
+1           & 1           & 2           & 2           & 0 \\
+2           & 1           & 2           & 2           & 0 \\
+1           & 2           & 2           & 2           & 1 \\
+2           & 2           & 2           & 2           & 0.5
+\end{tabular}
+\end{center}
+\end{table}
+Then by theorem \ref{inverse_shape} we know that the inverses will be of the form,
+$X \mmult{2} A \mmult{2} B$ or $X \mmult{2} A \mmult{1} C$ for multimatrices
+$B$ or $C$ if they exist.
+
+Let's try solving $A \mmult{2} B = \Ident^2(\left<2,2\right>)$ first to get $B$.
+We can first tell that $\shape{B} = \left<2,2,2,2\right>$ based on the shape of $A$ and
+the shape of the RHS.
+This problem can then be reshaped to the following 2d problem,
+
+TODO: what the fuck these numbers are wrong.
+\[
+\left[
+  \begin{array}{c c c c}
+    -1 & 0 & 2 & 0 \\ 
+    0 & -1 & 0 & 2 \\
+    1 & 0 & 0.5 & 0 \\
+    0 & 1 & 0 & 0.5
+  \end{array}
+\right]
+B' =
+\left[
+  \begin{array}{c c c c}
+    1 & 0 & 0 & 0 \\
+    0 & 1 & 0 & 0 \\
+    0 & 0 & 1 & 0 \\
+    0 & 0 & 0 & 1
+  \end{array}
+\right]
+\]
+Which, once solved, yields,
+\[
+B' =
+\left[
+  \begin{array}{c c c c}
+    -1/5 & 0 & 2/5 & 0 \\
+    0 & -1/5 & 0 & 2/5 \\
+    4/5 & 0 & 2/5 & 0 \\
+    0 & 4/5 & 0 & 2/5
+  \end{array}
+\right]
+\]
+Therefore $B$ is,
+\begin{table}[h!]
+\begin{center}
+\begin{tabular}{c c c c | c}
+$\bar{b}[1]$ & $\bar{b}[2]$ & $\bar{b}[3]$ & $\bar{b}[4]$ & $B[\bar{b}]$ \\
+\hline
+1           & 1           & 1           & 1           & -1/5 \\
+1           & 1           & 1           & 2           & 0 \\
+1           & 1           & 2           & 1           & 2/5 \\
+1           & 1           & 2           & 2           & 0 \\
+1           & 2           & 1           & 1           & 0 \\
+1           & 2           & 1           & 2           & -1/5 \\
+1           & 2           & 2           & 1           & 0 \\
+1           & 2           & 2           & 2           & 2/5 \\
+2           & 1           & 1           & 1           & 4/5 \\
+2           & 1           & 1           & 2           & 0 \\
+2           & 1           & 2           & 1           & 2/5 \\
+2           & 1           & 2           & 2           & 0 \\
+2           & 2           & 1           & 1           & 0 \\
+2           & 2           & 1           & 2           & 4/5 \\
+2           & 2           & 2           & 1           & 0 \\
+2           & 2           & 2           & 2           & 2/5 
+\end{tabular}
+\end{center}
+\end{table}
+
+Now to solve for $C$ in $A \mmult{1} C = \Ident^2(\left<2,2\right>0$ we know
+that $\shape{C} = \left<2,2\right>$.
+And if we reshape the problem we get,
+
+\[
+\left[
+  \begin{array}{c c}
+    -1 & 2 \\
+    0 & 0 \\
+    1 & 0.5 \\
+    0 & 0 \\
+    0 & 0 \\
+    -1 & 2 \\
+    0 & 0 \\
+    1 & 0.5
+  \end{array}
+\right]
+C
+=
+\left[
+  \begin{array}{c c}
+    1 & 0 \\
+    0 & 0 \\
+    0 & 1 \\
+    0 & 0 \\
+    0 & 0 \\
+    1 & 0 \\
+    0 & 0 \\
+    0 & 1
+  \end{array}
+\right]
+\]
+And through some miracle (or author fiat) this actually has a solution,
+\[
+  C =
+  \left[
+    \begin{array}{c c}
+      -1/5 & 4/5 \\
+      2/5 & 2/5
+    \end{array}
+  \right]
+\]
+\end{example}
 
@@
 What the hell is a `Hadamard product'? The Hadamard product \cite{wiki:hadamard}
-of two matricies is how one would actually expect matrix multiplication to work.
-
-In short, if two matricies, $A$ and $B$ have the same shape,
+of two matrices is how one would actually expect matrix multiplication to work.
+
+In short, if two matrices, $A$ and $B$ have the same shape,
 \[ \shape{A} = \shape{B} = \left<r,c\right> \]
@@
 
-This seems to extend quite naturally into the world of multimatricies.
+This seems to extend quite naturally into the world of multimatrices.
 But hold on - there's a catch. While the Hadamard product only logically applies
-to regular matricies when their shapes are exactly equal, there are case where
-the Hadamard product can easily be applied to differently shaped multimatricies,
+to regular matrices when their shapes are exactly equal, there are case where
+the Hadamard product can easily be applied to differently shaped multimatrices,
 they just need to have overlapping portions of their shape vectors, just as
@@
 \label{multi_had_prod}
-Let $A$ and $B$ be multimatricies such that $\shape{A} = \vec{a} \oplus \vec{c}$
+Let $A$ and $B$ be multimatrices such that $\shape{A} = \vec{a} \oplus \vec{c}$
 and $\shape{B} = \vec{c} \oplus \vec{b}$. Also let $c = \shape{\vec{c}}$.
@@
 \begin{theorem}[Hadamard Product Associativity]
-Let $A$, $B$, and $C$ be multimatrixes such that $\shape{A} = \vec{a} \oplus \vec{m}$,
+Let $A$, $B$, and $C$ be multimatrices such that $\shape{A} = \vec{a} \oplus \vec{m}$,
 $\shape{B} = \vec{m} \oplus \vec{b} \oplus \vec{n}$ and $\shape{C} = \vec{n} \oplus \vec{c}$,
@@
 \label{hada_cubic}
-If $A$ and $B$ are multimatrixes of shaep, $\shape{A} = \vec{a} \oplus \vec{x}$
+If $A$ and $B$ are multimatrices of shape, $\shape{A} = \vec{a} \oplus \vec{x}$
 and $\shape{B} = \vec{x} \oplus \vec{b}$ respectively. Then,
@@
 \begin{exercise}
-Let $A$, $B$, and $C$ be multimatricies such that $\shape{A} = \left<1,2,3\right>$,
+Let $A$, $B$, and $C$ be multimatrices such that $\shape{A} = \left<1,2,3\right>$,
 $\shape{B} = \left<3,1,2\right>$ and $\shape{C} = \left<3,2,1\right>$. For each of these
@@
 
-\chapter{Other Operations With Multimatricies}
+\chapter{Other Operations With Multimatrices}
 
@@
 
-But actually, you'll find that scalars can be modeled equally well by multricies
+But actually, you'll find that scalars can be modeled equally well by matrices
 with the shape $\left<\right>$. It works with multiplication and derivatives. Look:
@@
 \label{s_mm_mult_equiv}
-For any multiplication operation defined between multimatricies and scalars,
+For any multiplication operation defined between multimatrices and scalars,
 the scalar may be replaced by an equivalent empty-shaped multimatrix whose
@@
 So, $sA = S \mmult{0} A$.
-Finally, by similiar reasoning,
+Finally, by similar reasoning,
 \begin{align*}
@@
 that we would always be able to treat scalars
-as empty-shape multimatricies but let's canonize it.
+as empty-shape multimatrices but let's canonize it.
 
@@
 $\partial F(X[\left<\right>])[\vec{f}] / \partial X[\left<\right>]$ is
-equivalent by definition. By are given $G(X) = F(X[\left<\right>])$ we
+equivalent by definition. By our given $G(X) = F(X[\left<\right>])$ we
 can then also say that,
@@
    C[\bar{x}] = A[\bar{x}] + B[\bar{x}] \]
-In other words, adding two multimatricies (which must be of the same shape) results
+In other words, adding two multimatrices (which must be of the same shape) results
 in a multimatrix of the same shape with elements which are the sum of the corresponding
-elements of the added multimatricies.
+elements of the added multimatrices.
 \end{definition}
@@
 
-The following should be obvious, condesendingly so,
+The following should be obvious, condescendingly so,
 
@@
 \label{eq_add_sub_thm}
-For any multimatricies $A$ and $B$ where $\shape{A} = \shape{B}$,
+For any multimatrices $A$ and $B$ where $\shape{A} = \shape{B}$,
 \[ A - B = A + (-1)B \]
@@
 
-Here's an example - get out your crayons and follow along.
+Here's an example:
 
@@
 \[ \shape{\Tran(M, 3)} = \left<5,9,3,2,7\right> \]
-You can see, it's as though I cut off the front of the shape vector and transfered
+You can see, it's as though I cut off the front of the shape vector and transferred
 it to the end of the vector.
 
-You do the same thing with indicies. So,
+You do the same thing with indices. So,
 \[ M[1,2,3,4,5] = \Tran(M, 3)[4,5,1,2,3] \]
@@
 
-This extension is consisent with the prevous definition because, for any
+This extension is consistent with the previous definition because, for any
 index of transpose, $l$, that would be covered by the original definition,
@@
 
-Thus, we (by which I mean \textit{me} since \textit{you} certainly haven't done any
-of the work) have shown a natural equivalent class \cite{book:abstract} of transpose
-operations. On multimatricies with a shape of some length $n$ there are $n$ unique
+Thus, we have shown a natural equivalent class \cite{book:abstract} of transpose
+operations. On multimatrices with a shape of some length $n$ there are $n$ unique
 transpose; $\Tran(X, i)$ for all $0 \le i < n$. All other transposes are equivalent
@@
 \label{tran_int_iso}
-Let $\mathbb{T}_n$ be the set of possible transpositions on multimatricies with
+Let $\mathbb{T}_n$ be the set of possible transpositions on multimatrices with
 shapes of length $n$. Let $\circ$ be the operation of composition. Then
@@
 that set of transpositions is a group under composition, then I'll need to
-provide a one-to-one and onto map that preseves the respective group operations
+provide a one-to-one and onto map that preserves the respective group operations
 between transpositions and integers mod $n$.
@@
 \begin{ppart}
-To begin, I'll show that the set of all transpositions on multimatricies 
+To begin, I'll show that the set of all transpositions on multimatrices 
 with shapes of length $n$ form a group under composition.
@@
 So, let $A$ be a multimatrix with shape of length $n$. Now let $x$ and $y$
-be indicies of transpositions. Then what is $\Tran(\Tran(A, x), y)$?
+be indices of transpositions. Then what is $\Tran(\Tran(A, x), y)$?
 To apply the the first transpose we need to break $\shape{A}$ into two vectors,
@@
 
-See now that this composit operation is also a transposition, $\Tran(A, z)$ where,
+See now that this composite operation is also a transposition, $\Tran(A, z)$ where,
 $z = \shape{\vec{a} \oplus \vec{b}}$.
@@
 
-See now that this composit operation is also a transposition, $\Tran(A, z)$ where,
+See now that this composite operation is also a transposition, $\Tran(A, z)$ where,
 $z = \shape{\vec{a}}$.
@@
 
-So I've shown that in both cases, the composit function of two transposes is
-itself a transpose. So transposes of multimatrcies of shape of length $n$ are
+So I've shown that in both cases, the composite function of two transposes is
+itself a transpose. So transposes of multimatrices of shape of length $n$ are
 a closed group under composition.
@@
 \[ \phi(\Tran_i) = i \]
-Done. I'm a genious.
-
-Ok, the hard part is showing that it preserves the group operations.
+Done. I'm a genius.
+
+OK, the hard part is showing that it preserves the group operations.
 Let's go back to our example in the first part of this proof. Let $A$ be
-any multimatrix with shape length $n$. Then let there be two transpositons
+any multimatrix with shape length $n$. Then let there be two transpositions
 $\Tran_x$ and $\Tran_y$ which we'll apply in series. First remember that
@@
 
-And we showed that the composit $\Tran_z = \Tran_y \circ \Tran_x$ was such
+And we showed that the composite $\Tran_z = \Tran_y \circ \Tran_x$ was such
 that,
@@
 \begin{proof}
-Consider that for some ordered set of indicies
+Consider that for some ordered set of indices
 $\{\bar{x}_1, \bar{x}_2, \ldots \bar{x}_n\} = X$ such that for each
@@
 
-The above theorem is useful whenever you come accross a transpose of a
+The above theorem is useful whenever you come across a transpose of a
 multimatrix identity.
@@
 Let $x$ be in $\mathbb{N} \cup \{0\}$ and let $A$ and $B$ be
-multimatricies such that $\shape{A} = \shape{B}$ and $\Tran(A, x)$ is defined.
+multimatrices such that $\shape{A} = \shape{B}$ and $\Tran(A, x)$ is defined.
 Then,
@@
 Let $A$ be a multimatrix such that $\shape{A} = <1,2,3,4,5>$,
-Find the shape of the following trasnposes:
+Find the shape of the following transposes:
 \begin{enumerate}
@@
 \label{right_mult_derivative}
-Let $A$ and $X$ be multimatricies such that $A \mmult{n} X$ is
+Let $A$ and $X$ be multimatrices such that $A \mmult{n} X$ is
 defined. Then,
@@
 \]
-Now will a little manipulation, keeping in mind how identies are sometimes commutative (Thm. \ref{ident_commute})
-and how cubic identities collapse into hadamard products (Thm. \ref{hada_cubic}),
+Now will a little manipulation, keeping in mind how identities are sometimes commutative (Thm. \ref{ident_commute})
+and how cubic identities collapse into Hadamard products (Thm. \ref{hada_cubic}),
 \begin{align*}
@@
 
+We all know how matrix multiplication can be done by partitions.
+This chapter explains how that extends to multimatrices.
+So first, let's define some notion of multimatrix partitions and how multimatrices can be put together to form
+larger multimatrices. It's not quite so easy as with regular 2d matrices so we'll even have to be formal
+about how we bring them together:
+
 \begin{definition}[Multimatrix Concatenation]
-Let $A$ and $B$ be multimatricies of shape $\shape{A} = \vec{a}$ and
+Let $A$ and $B$ be multimatrices of shape $\shape{A} = \vec{a}$ and
 $\shape{B} = \vec{b}$ respectively. Then if, for all $i \ne n$,
@@
 \[ A \mconcat{n} B \]
-In layman's terms, this is the operation of stacking two similar multimatricies on top of or to the side of one another.
-It's just complicated by this being an opperation in multiple dimensions.
-Formally we'll say that, 
+And results in a multimatrix such that,
 \[ \shape{\shape{A \mconcat{n} B}} = \shape{\shape{A}} = \shape{\shape{B}} \]
@@
 \]
-And for all sub index metricies $\bar{l}$ and $\bar{r}$ of lengths $\shape{\bar{l}} = n-1$ and $\shape{\bar{r}} = \shape{\shape{A}}-n$ respectively,
+And for all sub index vectors $\bar{l}$ and $\bar{r}$ of lengths $\shape{\bar{l}} = n-1$ and $\shape{\bar{r}} = \shape{\shape{A}}-n$ respectively,
 and natural number $j \in [1,\vec{a}[n]+\vec{b}[n]]$ such that $\bar{l} \oplus \left<j\right> \oplus \bar{r} \in \Dim(\shape{A \mconcat{n} B})$,
@@
 \]
+In layman's terms, this is the operation of stacking two similar multimatrices on top of or to the side of one another.
+It's just complicated by this being an operation in multiple dimensions.
 \end{definition}
@@
 
-\begin{theorem}[Multiplication Over Concatenation Rules]
-Let $A$ and $B$ be multimatricies where $A \mconcat{n} B$ is valid.
-
+\begin{theorem}[Multiplication Over Concatenation Rule 1]
+Let $A$, $B$, and $C$ be multimatrices, and let $m$ and $n$ be
+natural numbers where $0 < m < n$. 
+If either of the following computations  is valid, then it is equivalent to the other:
+\[ C \mmult{m} \left(A \mconcat{n} B\right) = \left(C \mmult{m} A\right) \mconcat{\shape{\shape{C}}+n-2m} \left(C \mmult{m} B\right) \]
+\end{theorem}
+\begin{landscape}
+\begin{proof}
+Let $A$, $B$, and $C$ be multimatrices, and let $m$ and $n$ be
+natural numbers where $0 < m < n$.
+
+\begin{ppart}
+Suppose $C \mmult{m} \left(A \mconcat{n} B\right)$ is a valid computation.
+Then $\shape{C} = \vec{c} \oplus \vec{m}$ and $\shape{A \mconcat{n} B} = \vec{m} \oplus \vec{v}$
+for some vectors $\vec{c}$, $\vec{m}$, and $\vec{v}$ where $\shape{\vec{m}} = m$.
+Also $\shape{A} = \vec{l} \oplus \left<a\right> \oplus \vec{r}$, and $\shape{B} = \vec{l} \oplus \left<b\right> \oplus \vec{r}$
+for some vectors $\vec{l}$ and $\vec{r}$ where $\shape{\vec{l}} = n-1$ and some natural numbers $a$ and $b$.
+And since $m < n$ it follows that $\shape{\vec{m}} \le \shape{\vec{l}}$ so we can split up $\vec{l}$ thus,
+$\vec{l} = \vec{m} \oplus \vec{e}$ for some $\vec{e}$. Which results in the following shapes,
+\[ \shape{A} = \vec{m} \oplus \vec{e} \oplus \left<a\right> \oplus \vec{r} \]
+\[ \shape{B} = \vec{m} \oplus \vec{e} \oplus \left<b\right> \oplus \vec{r} \]
+\[ \shape{C} = \vec{c} \oplus \vec{m} \]
+Let's also note that $\shape{\vec{e}} = n-1-m = n-m-1$ which will be important in the last section of the proof.
+And shows that both $C \mmult{m} A$ and $C \mmult{m} B$ are valid operations where,
+\[ \shape{C \mmult{m} A} = \vec{c} \oplus \vec{e} \oplus \left<a\right> \oplus \vec{r} \]
+\[ \shape{C \mmult{m} B} = \vec{c} \oplus \vec{e} \oplus \left<b\right> \oplus \vec{r} \]
+Where $\shape{\vec{c} \oplus \vec{e}} = \shape{\shape{C}}-m + n-1-m = \shape{\shape{C}}+n-2m-1$,
+so \[ \left(C \mmult{m} A\right) \mconcat{\shape{\shape{C}}+n-2m} \left(C \mmult{m} B\right) \] is a valid computation.
+\end{ppart}
+
+\begin{ppart}
+Suppose $\left(C \mmult{m} A\right) \mconcat{\shape{\shape{C}}+n-2m} \left(C \mmult{m} B\right)$ is a valid computation.
+Then $\shape{C \mmult{m} A} = \vec{f} \oplus \left<a\right> \oplus \vec{r}$ and
+$\shape{C \mmult{m} B} = \vec{f} \oplus \left<b\right> \oplus \vec{r}$ for some
+vectors $\vec{f}$ and $\vec{r}$ where $\shape{\vec{f}} = \shape{\shape{C}}+n-2m-1$ and where $a$ and $b$ are some natural numbers.
+We can also see that $\shape{C} = \vec{c} \oplus \vec{m}$, $\shape{A} = \vec{m} \oplus \vec{a}$, and $\shape{B} = \vec{m} \oplus \vec{b}$
+for some vectors $\vec{a}$, $\vec{b}$, $\vec{c}$, and $\vec{m}$ where $\shape{\vec{m}} = m$.
+Now note that, $\shape{C \mmult{m} A} = \vec{c} \oplus \vec{a}$ and $\shape{C \mmult{m} B} = \vec{c} \oplus \vec{b}$.
+Therefore, 
+\[ \vec{f} \oplus \left<a\right> \oplus \vec{r} = \vec{c} \oplus \vec{a} \]
+\[ \vec{f} \oplus \left<b\right> \oplus \vec{r} = \vec{c} \oplus \vec{b} \]
+Since $\shape{\vec{c}} = \shape{\shape{C}}-m$ and 
+$\shape{\vec{f}} = \shape{\shape{C}}+n-2m-1 = \shape{\shape{C}}-m+(n-m-1)$,
+and we know that $m < n$ so $n-m-1 \ge 0$ it follows that $\shape{\vec{c}} \le \shape{\vec{f}}$
+so we can split up $\vec{f}$ thus, $\vec{f} = \vec{c} \oplus \vec{e}$ for some $\vec{e}$.
+Where,
+\[ \shape{\vec{e}} = \shape{\vec{f}}-\shape{\vec{c}} = \shape{\shape{C}}+n-2m-1 - (\shape{\shape{C}}-m) = n-m-1 \]
+That leaves us with,
+\[ \shape{C \mmult{m} A} = \vec{c} \oplus \vec{e} \oplus \left<a\right> \oplus \vec{r} = \vec{c} \oplus \vec{a}\]
+\[ \shape{C \mmult{m} B} = \vec{c} \oplus \vec{e} \oplus \left<b\right> \oplus \vec{r} = \vec{c} \oplus \vec{b}\]
+Therefore,
+\[ \vec{a} = \vec{e} \oplus \left<a\right> \oplus \vec{r} \]
+\[ \vec{b} = \vec{e} \oplus \left<b\right> \oplus \vec{r} \]
+And so,
+\[ \shape{A} = \vec{m} \oplus \vec{e} \oplus \left<a\right> \oplus \vec{r} \]
+\[ \shape{B} = \vec{m} \oplus \vec{e} \oplus \left<b\right> \oplus \vec{r} \]
+\[ \shape{C} = \vec{c} \oplus \vec{m} \]
+Since $\shape{\vec{m} \oplus \vec{e}} = m+n-m-1 = n-1$, we know that $A \mconcat{n} B$ is valid and,
+\[ \shape{A \mconcat{n} B} = \vec{m} \oplus \vec{e} \oplus \left<a+b\right> \oplus \vec{r} \]
+And so, $C \mmult{m} \left(A \mconcat{n} B\right)$ is also valid.
+\end{ppart}
+
+\begin{ppart}
+In either of the above cases we were able to breakdown the shapes of our matrices thus,
+\[ \shape{A} = \vec{m} \oplus \vec{e} \oplus \left<a\right> \oplus \vec{r} \]
+\[ \shape{B} = \vec{m} \oplus \vec{e} \oplus \left<b\right> \oplus \vec{r} \]
+\[ \shape{C} = \vec{c} \oplus \vec{m} \]
+Where $\shape{\vec{m}} = m$ and $\shape{\vec{e}} = n-m-1$
+
+So,
+\[ \shape{A \mconcat{n} B} = \vec{m} \oplus \vec{e} \oplus \left<a+b\right> \oplus \vec{r} \]
+\[ \shape{C \mmult{m} \left(A \mconcat{n} B\right)} = \vec{c} \oplus \vec{e} \oplus \left<a+b\right> \oplus \vec{r} \]
+\[ \shape{C \mmult{m} A} = \vec{c} \oplus \vec{e} \oplus \left<a\right> \oplus \vec{r} \]
+\[ \shape{C \mmult{m} B} = \vec{c} \oplus \vec{e} \oplus \left<b\right> \oplus \vec{r} \]
+\[ \shape{\left(C \mmult{m} A\right) \mconcat{\shape{\shape{C}}+n-2m} \left(C \mmult{m} B\right)} = \vec{c} \oplus \vec{e} \oplus \left<a+b\right> \oplus \vec{r} \]
+
+Now for all vectors, $\bar{c} \in \Dim(\vec{c})$, $\bar{e} \in \Dim(\vec{e})$, and $\bar{r} \in \Dim(\vec{r})$,
+\begin{align*}
+  \left(C \mmult{m} \left(A \mconcat{n} B\right)\right)[\bar{c} \oplus \bar{e} \oplus \left<i\right> \oplus \bar{r}]
+  &= \sum_{\forall \bar{m} \in \Dim(\vec{m})} C[\bar{c} \oplus \bar{m}] \left(A \mconcat{n} B\right)[\bar{m} \oplus \bar{e} \oplus \left<i\right> \oplus \bar{r}] \\
+  &= \left\{
+    \begin{array}{ll}
+      \sum_{\forall \bar{m}} C[\bar{c} \oplus \bar{m}] A[\bar{m} \oplus \bar{e} \oplus \left<i\right> \oplus \bar{r}]
+      & \mbox{if } i \le a \\
+      \sum_{\forall \bar{m}} C[\bar{c} \oplus \bar{m}] B[\bar{m} \oplus \bar{e} \oplus \left<i-a\right> \oplus \bar{r}]
+      & \mbox{if } i > a
+    \end{array}
+  \right. \\
+  &= \left\{
+    \begin{array}{ll}
+      \left(C \mmult{m} A\right)[\bar{c} \oplus \bar{e} \oplus \left<i\right> \oplus \bar{r}]
+      & \mbox{if } i \le a \\
+      \left(C \mmult{m} B\right)[\bar{c} \oplus \bar{e} \oplus \left<i-a\right> \oplus \bar{r}]
+      & \mbox{if } i > a
+    \end{array}
+  \right. \\
+  &= \left(\left(C \mmult{m} A\right) \mconcat{\shape{\shape{C}}+n-2m} \left(C \mmult{m} B\right)\right)[\bar{c} \oplus \bar{e} \oplus \left<i\right> \oplus \bar{r}]
+\end{align*}
+\end{ppart}
+
+\end{proof}
+
+\begin{theorem}[Multiplication Over Concatenation Rule 2]
+Let $A$, $B$, and $C$ be multimatrices, and let $m$ and $n$ be
+natural numbers where $0 < n \le m$. 
+If either of the following computations is valid, then it is equivalent to the other:
+\[
+  C \mmult{m} \left(A \mconcat{n} B\right)
+  =
+  \left( C_1 \mmult{m} A \right) + 
+  \left( C_2 \mmult{m} B \right)
+\]
+\[ \Part(C, \shape{\shape{C}}-m+n, \shape{A}[n]) = \left\{ C_1, C_2 \right\} \]
+\end{theorem}
+\begin{proof}
+Let $A$, $B$, and $C$ be multimatrices, and let $m$ and $n$ be
+natural numbers where $0 < n \le m$.
+
+\begin{ppart}
+Suppose $C \mmult{m} \left(A \mconcat{n} B\right)$ is a valid computation.
+Then $\shape{C} = \vec{c} \oplus \vec{m}$ and $\shape{A \mconcat{n} B} = \vec{m} \oplus \vec{d}$ for
+some vectors $\vec{c}$, $\vec{m}$, and $\vec{d}$ where $\shape{\vec{m}} = m$.
+We also know $\shape{A} = \vec{l} \oplus \left< a \right> \oplus \vec{r}$ and
+$\shape{B} = \vec{l} \oplus \left< b \right> \oplus \vec{r}$
+for some vectors $\vec{l}$ and  $\vec{r}$ and some natural numbers $a$ and $b$ where
+$\shape{\vec{l}} = n-1$.
+And since $n \le m$ it follows that $\shape{\vec{l}}+1 \le \shape{\vec{m}}$.
+Now remember that,
+\[ \shape{A \mconcat{n} B} = \vec{m} \oplus \vec{d} = \vec{l} \oplus \left< a+b \right> \oplus \vec{r} \]
+Therefore we can break up $\vec{m}$ into $\vec{l} \oplus \left< a+b \right> \oplus \vec{e}$ for some
+$\vec{e}$ and say that,
+\[ \shape{A \mconcat{n} B} = \vec{l} \oplus \left< a+b \right> \oplus \vec{e} \oplus \vec{f} \]
+\[ \shape{A} = \vec{l} \oplus \left< a \right> \oplus \vec{e} \oplus \vec{f} \]
+\[ \shape{B} = \vec{l} \oplus \left< b \right> \oplus \vec{e} \oplus \vec{f} \]
+For some $\vec{f}$ and,
+\[ \shape{C} = \vec{c} \oplus \vec{l} \oplus \left< a+b \right> \oplus \vec{e} \]
+So we can partition $C$ thus,
+\[ \Part(C, \shape{\vec{c} \oplus \vec{l}}+1, a) = \left\{ C_1, C_2 \right\} \]
+\[ \shape{C_1} = \vec{c} \oplus \vec{l} \oplus \left< a \right> \oplus \vec{e} \]
+\[ \shape{C_2} = \vec{c} \oplus \vec{l} \oplus \left< b \right> \oplus \vec{e} \]
+Note that $\shape{A}[n] = a$ and $\shape{\vec{c}} = \shape{\shape{C}}-m$ so,
+\[ \Part(C, \shape{\vec{c} \oplus \vec{l}}+1, a) = \Part(C, \shape{\shape{C}}-m+n, \shape{A}[n]) \]
+And because,
+\[ \shape{\vec{m}} = \shape{\vec{l} \oplus \left< a+b \right> \oplus \vec{e}} =
+   \shape{\vec{l} \oplus \left< a \right> \oplus \vec{e}} = \shape{\vec{l} \oplus \left< b \right> \oplus \vec{e}} = m \]
+It also follows that each of these are valid operations,
+\[ C_1 \mmult{m} A \]
+\[ C_2 \mmult{m} B \]
+Where,
+\[ \shape{C_1 \mmult{m} A} = \vec{c} \oplus \vec{f} \]
+\[ \shape{C_2 \mmult{m} B} = \vec{c} \oplus \vec{f} \]
+And since the shapes are equal, we can also perform the following operation,
+\[ \left(C_1 \mmult{m} A\right) + \left(C_2 \mmult{m} B\right) \]
+\end{ppart}
+
+\begin{ppart}
+Suppose $\left(C_1 \mmult{m} A\right) + \left(C_2 \mmult{m} B\right)$ is a valid operation
+where $\Part(C, \shape{\shape{C}}-m+n, \shape{A}[n]) = \left\{ C_1, C_2 \right\}$.
+Therefore $\shape{C_1 \mmult{m} A} = \shape{C_2 \mmult{m} B}$ and,
+\[ \shape{C_1} = \vec{c}_1 \oplus \vec{m}_1 \]
+\[ \shape{A} = \vec{m}_1 \oplus \vec{a} \]
+\[ \shape{C_2} = \vec{c}_2 \oplus \vec{m}_2 \]
+\[ \shape{B} = \vec{m}_2 \oplus \vec{b} \]
+For some shape vectors $\vec{c}_1$, $\vec{c}_2$, $\vec{m}_1$, $\vec{m}_2$, $\vec{a}$, and $\vec{b}$ where $\shape{\vec{m}_1} = \shape{\vec{m}_2} = m$.
+And because that addition is valid we also know that,
+\[ \vec{c}_1 \oplus \vec{a} = \vec{c}_2 \oplus \vec{b} \]
+And since $C_1$ and $C_2$ are partitions of $C$, their shapes are the same size, i.e. $\shape{\shape{C_1}} = \shape{\shape{C_2}}$.
+Therefore $\shape{\vec{c}_1} = \shape{\vec{c}_2}$ so the division between $\vec{c}_1$ and $\vec{a}$ and between
+$\vec{c}_2$ and $\vec{b}$ are in the same relative location. Which means that
+we can simplify by stating that,
+\[ \shape{C_1} = \vec{c} \oplus \vec{m}_1 \]
+\[ \shape{A} = \vec{m}_1 \oplus \vec{f} \]
+\[ \shape{C_2} = \vec{c} \oplus \vec{m}_2 \]
+\[ \shape{B} = \vec{m}_2 \oplus \vec{f} \]
+For some new vectors $\vec{c}$ and $\vec{f}$ such that $\vec{c}_1 = \vec{c}_2 = \vec{c}$ and $\vec{a} = \vec{b} = \vec{f}$.
+
+Now because of the concatenation constraint we know that,
+$\shape{C} = \vec{d} \oplus \left< a+b \right> \oplus \vec{e}$ for some vectors $\vec{d}$ and $\vec{e}$ and
+natural numbers $a$ and $b$ where $\shape{\vec{d}} = \shape{\shape{C}}-m+n-1$ and $a = \shape{A}[n]$.
+And further, we know that,
+\[ \shape{C_1} = \vec{d} \oplus \left< a \right> \oplus \vec{e} \]
+\[ \shape{C_2} = \vec{d} \oplus \left< b \right> \oplus \vec{e} \]
+\[ \shape{C} = \vec{d} \oplus \left< a+b \right> \oplus \vec{e} \]
+Where $\shape{\vec{e}} = \shape{\shape{C}}-(\shape{\shape{C}}-m+n-1+1) = m-n$.
+Note that $\shape{\vec{c}} = \shape{\shape{C}}-m$ so we can also say that $\shape{\vec{l}} = \shape{\vec{c}}+n-1$
+So we can divide $\vec{d}$ thus, $\vec{d} = \vec{c} \oplus \vec{l}$ for some vector $\vec{l}$ where $\shape{\vec{l}} = n-1$.
+Then,
+\[ \shape{C_1} = \vec{c} \oplus \vec{m}_1 = \vec{c} \oplus \vec{l} \oplus \left< a \right> \oplus \vec{e} \]
+\[ \shape{C_2} = \vec{c} \oplus \vec{m}_2 = \vec{c} \oplus \vec{l} \oplus \left< b \right> \oplus \vec{e} \]
+So we know that, $\vec{m}_1 = \vec{l} \oplus \left< a \right> \oplus \vec{e}$ and $\vec{m}_2 = \vec{l} \oplus \left< b \right> \oplus \vec{e}$
+which means that,
+\[ \shape{A} = \vec{l} \oplus \left< a \right> \oplus \vec{e} \oplus \vec{f} \]
+\[ \shape{B} = \vec{l} \oplus \left< b \right> \oplus \vec{e} \oplus \vec{f} \]
+And since $\shape{\vec{l}} = n-1$ the operation $A \mconcat{n} B$ is valid and,
+\[ \shape{A \mconcat{n} B} = \vec{l} \oplus \left< a+b \right> \oplus \vec{e} \oplus \vec{f} \]
+And since,
+\[ \shape{C} = \vec{c} \oplus \vec{l} \oplus \left< a+b \right> \oplus \vec{e} \]
+Where $\shape{\vec{l} \oplus \left<a+b\right> \oplus \vec{e}} = n-1 + 1 + m-n = m$ so the final operation $C \mmult{m} \left(A \mconcat{n} B\right)$ is valid.
+\end{ppart}
+
+\begin{ppart}
+In either of the above cases, we can divide our given matrices thus,
+\[ \shape{A} = \vec{l} \oplus \left< a \right> \oplus \vec{e} \oplus \vec{f} \]
+\[ \shape{B} = \vec{l} \oplus \left< b \right> \oplus \vec{e} \oplus \vec{f} \]
+\[ \shape{C_1} = \vec{c} \oplus \vec{l} \oplus \left< a \right> \oplus \vec{e} \]
+\[ \shape{C_2} = \vec{c} \oplus \vec{l} \oplus \left< b \right> \oplus \vec{e} \]
+With,
+\[ \shape{C \mmult{m} \left(A \mconcat{n} B\right)} = \shape{\left(C_1 \mmult{m} A\right) + \left(C_2 \mmult{m} B\right)} = \vec{c} \oplus \vec{f} \]
+Let $\bar{c} \in \Dim(\vec{c})$ and $\bar{f} \in \Dim(\vec{f})$ then,
+\begin{align*}
+  \left(C \mmult{m} \left(A \mconcat{n} B\right)\right)[\bar{c} \oplus \bar{f}]
+  &=
+    \sum_{\forall \bar{l} \in \Dim(\vec{l}), k \in [1,a+b], \bar{e} \in \Dim(\vec{e})}
+      C[\bar{c} \oplus \bar{l} \oplus \left<k\right> \oplus \bar{e}]
+      \left(A \mconcat{n} B\right)[\bar{l} \oplus \left<k\right> \oplus \bar{e} \oplus \bar{f}]
+\end{align*}
+\end{ppart}
+
+\end{proof}
+
+\end{landscape}
+
+\begin{theorem}[Bla]
 For any natural number $m$ where $m < n$,
@@
 \begin{ppart}
-Let $A$ and $B$ be multimatricies where $A \mconcat{n} B$ is valid. 
+Let $A$ and $B$ be multimatrices where $A \mconcat{n} B$ is valid. 
 Let $m$ be a natural number where $m < n$, and let $C$ be a multimatrix where
@@
 
-Since $A \mconcat{n} B$ is valid, we can describe the shapes of $A$ and $B$ thusly,
+Since $A \mconcat{n} B$ is valid, we can describe the shapes of $A$ and $B$ thus,
 \[ \shape{A} = \vec{l} \oplus \left<a\right> \oplus \vec{r} \]
@@
 \[ \shape{C} = \vec{c} \oplus \vec{m} \]
-For some shape vetors $\vec{c}$ and $\vec{m}$ where $\shape{\vec{m}} = m$ and
+For some shape vectors $\vec{c}$ and $\vec{m}$ where $\shape{\vec{m}} = m$ and
 $\shape{\vec{c}} = \shape{\shape{C}}-m$
@@
 \begin{ppart}
-Let $A$ and $B$ be multimatricies where $A \mconcat{n} B$ is valid. 
+Let $A$ and $B$ be multimatrices where $A \mconcat{n} B$ is valid. 
 Let $m$ be a natural number where $m \le \shape{\shape{A}}-n$
@@
 
-So we can use that repartion in our original shape definitions,
+So we can use that repartition in our original shape definitions,
 
@@
 \begin{ppart}
-Let $A$ and $B$ be multimatricies where $A \mconcat{n} B$ is valid. 
+Let $A$ and $B$ be multimatrices where $A \mconcat{n} B$ is valid. 
 Let $m$ be a natural number where $m \ge n$, and let $C$ be a multimatrix where
@@
 
-Then we can partition the shapes of $A$ and $B$ thusly,
+Then we can partition the shapes of $A$ and $B$ thus,
 
@@
 
-We can also partiton the shapes of $C$ and $(A \mconcat{n} B)$ like this,
+We can also partition the shapes of $C$ and $(A \mconcat{n} B)$ like this,
 
@@
 $\shape{\vec{m}} \ge \shape{\vec{l} \oplus \left<a+b\right>}$ 
-so $\vec{m}$ encompases $\vec{l}$, the $n$'th index and potentially part of $\vec{r}$.
+so $\vec{m}$ encompasses $\vec{l}$, the $n$'th index and potentially part of $\vec{r}$.
 There for if we partition $\vec{r}$ like this,
@@
 TODO:generalize
-Let $A$ and $X$ be multimatrixes of shape $\shape{A} = \vec{a} \oplus \vec{x}$ and $\shape{X} = \vec{x}$ respectively.
+Let $A$ and $X$ be multimatrices of shape $\shape{A} = \vec{a} \oplus \vec{x}$ and $\shape{X} = \vec{x}$ respectively.
 Then $A[\bar{a} \oplus *^{\vec{x}}] \mmult{\shape{\vec{x}}} X = (A \mmult{\shape{\vec{x}}} X)[\bar{a}]$.
@@
 
-According to wikipedia \cite{wiki:fourier}, if $f(x)$ is an absolutely continuous differentiable function, and both $f$ and its derivative $f'$ are integrable.
+According to Wikipedia \cite{wiki:fourier}, if $f(x)$ is an absolutely continuous differentiable function, and both $f$ and its derivative $f'$ are integrable.
 Then the Fourier transform of the derivative is given by
@@
 What that means in practice is that we can approximate the derivative of a sequence, or in our case a multimatrix, using a FFT.
-The method I'm using comes from a youtube series by Steve Brunton \cite{youtube:fourier} which I've found to be particularly helpful.
-
-We'll define a function, $\FFT(X) = F$, and it's inverse, $\IFFT(F) = X$ as the fast fourier transform of $X$ and it's inverse of $F$.
+The method I'm using comes from a YouTube series by Steve Brunton \cite{youtube:fourier} which I've found to be particularly helpful.
+
+We'll define a function, $\FFT(X) = F$, and it's inverse, $\IFFT(F) = X$ as the fast Fourier transform of $X$ and it's inverse of $F$.
 Specifically, we'll let $X$ be a multimatrix of shape $\shape{X} = \left<N\right>$ where $N = 2^p$ for some $p>1$.
 And we'll let $F$ be a multimatrix representing a similar shape of complex numbers, $\shape{F} = \left<N, 2\right>$ where $F[k,1]$ is
-the real componenet and $F[k,2]$ is the imaginary component. So,
+the real component and $F[k,2]$ is the imaginary component. So,
 
@@
 This brings to mind the fact that multimatrices themselves form a vector space. Basically, for any shape $\vec{x}$
-there is an associated vector space of multimatrices $R^{\vec{x}}$. And I haven't yet explictly stated that. Need to do
-that because I'm pretty sure that's necesary for the shortest path being the one that's orthoganal.
+there is an associated vector space of multimatrices $R^{\vec{x}}$. And I haven't yet explicitly stated that. Need to do
+that because I'm pretty sure that's necessary for the shortest path being the one that's orthogonal.
 
@@
 \[ (v-u) \bot u \iff \forall u' \in f - \{u\} : d(u', v) < d(u,v) \]
-That is, $u$ is the closest vector in $f$ to $v$ if and only if it is the orthoganal project of $v$ onto $f$.
+That is, $u$ is the closest vector in $f$ to $v$ if and only if it is the orthogonal project of $v$ onto $f$.
 

### 2021-01-03 MMatrix/src/mmatrix.cc

@@ -575,7 +575,19 @@ void Copy(const MMatrixInterface* m, MMatrixInterface* out) {
   }
 }
 
-void Invert(int n, MMatrixInterface* m, MMatrixInterface* out) {
+void Reshape(const MMatrixInterface* m, MMatrixInterface* out) {
+  // TODO: improve for sparse matrices
+  // TODO: shape checks
+  int ncells = 1;
+  for (int i = 0; i < m->shape().size(); i++) {
+    ncells *= m->shape()[i];
+  }
+  for (int i = 0; i < ncells; i++) {
+    out->set(i, m->get(i));
+  }
+}
+
+bool Invert(int n, MMatrixInterface* m, MMatrixInterface* out) {
   // The size of m is N*N
   int N;
   {
@@ -599,6 +611,7 @@ void Invert(int n, MMatrixInterface* m, MMatrixInterface* out) {
     }
     N = static_cast<int>(N1);
   }
+
 
   // Set up NxN inverse
   out->zero();
@@ -643,7 +656,7 @@ void Invert(int n, MMatrixInterface* m, MMatrixInterface* out) {
         out->set(pr+N*c, tmp);
       }
     }
-    
+
     // Divide that row by it's pivot
     double pivot = m->get(pr+N*pc);
     m->set(pr+N*pc, 1);
@@ -670,7 +683,7 @@ void Invert(int n, MMatrixInterface* m, MMatrixInterface* out) {
   // Verify that the RRE form is invertable
   for (int i = 0; i < N; i++) {
     if (m->get(i+N*i) != 1) {
-      throw std::runtime_error("Not an invertable matrix.");
+      return false;
     }
   }
 
@@ -720,6 +733,7 @@ void Invert(int n, MMatrixInterface* m, MMatrixInterface* out) {
     // Go up to the next pivot row
     pr--;
   }
+  return true;
 }
 
 }  // namespace mmatrix

### 2021-01-03 MMatrix/src/mmatrix.h

@@ -144,10 +144,12 @@ std::string DebugString(const MMatrixInterface* m);
 std::string DebugString(const std::vector<int>& v);
 
 void Copy(const MMatrixInterface* m, MMatrixInterface* out);
+void Reshape(const MMatrixInterface* m, MMatrixInterface* out);
 
 // Inverts the given matrix on the n'th pivot.
 // The input m is destoryed in this process.
-void Invert(int n, MMatrixInterface* m, MMatrixInterface* out);
+// Returns true if the input was successfuly inverted, false otherwise.
+bool Invert(int n, MMatrixInterface* m, MMatrixInterface* out);
 
 }  // namespace mmatrix
 

### 2021-01-03 MMatrix/test/test_math.cc

@@ -266,15 +266,180 @@ void TestIdentityContraction() {
   }
 }
 
+void InverseExample() {
+  DenseMMatrix a({4,4});
+  a.set({0,0}, -1);
+  a.set({0,1}, 2);
+  a.set({0,2}, 1);
+  a.set({0,3}, 0);
+  a.set({1,0}, 0);
+  a.set({1,1}, -1);
+  a.set({1,2}, 0);
+  a.set({1,3}, 1);
+  a.set({2,0}, 2);
+  a.set({2,1}, 0);
+  a.set({2,2}, 0.5);
+  a.set({2,3}, 0);
+  a.set({3,0}, 0);
+  a.set({3,1}, 2);
+  a.set({3,2}, 0);
+  a.set({3,3}, 0.5);
 
+  DenseMMatrix inv({4,4});
+
+  if (!Invert(1, &a, &inv)) {
+    std::cerr << "Err." << std::endl;
+    exit(1);
+  }
+
+  for(int r = 0; r < 4; r++) {
+    for(int c = 0; c < 4; c++) {
+      std::cout << inv.get({r,c}) << "  ";
+    }
+    std::cout << std::endl;
+  }
+}
+
+void InverseExampleCheck() {
+  DenseMMatrix a({2,2,2,2});
+  a.set({0,0,0,0}, 2);
+  a.set({0,0,0,1}, -2);
+  a.set({0,0,1,0}, 0);
+  a.set({0,0,1,1}, 2);
+  a.set({0,1,0,0}, -2);
+  a.set({0,1,0,1}, 0);
+  a.set({0,1,1,0}, -1);
+  a.set({0,1,1,1}, 1);
+  a.set({1,0,0,0}, 0);
+  a.set({1,0,0,1}, -1);
+  a.set({1,0,1,0}, 1);
+  a.set({1,0,1,1}, 0);
+  a.set({1,1,0,0}, 1);
+  a.set({1,1,0,1}, -2);
+  a.set({1,1,1,0}, 1);
+  a.set({1,1,1,1}, -2);
+
+  DenseMMatrix b({2,2,2,2});
+  b.set({0,0,0,0}, 1/6.);
+  b.set({0,0,0,1}, -1/3.);
+  b.set({0,0,1,0}, -1/3.);
+  b.set({0,0,1,1}, 0);
+  b.set({0,1,0,0}, -1/6.);
[…]

### 2021-01-05 Math/book.tex
Updating book.

@@
 1           & 1           & 1           & 1           & -1 \\
-2           & 1           & 1           & 1           & 2 \\
-1           & 2           & 1           & 1           & 0 \\
+2           & 1           & 1           & 1           & 0 \\
+1           & 2           & 1           & 1           & 1 \\
 2           & 2           & 1           & 1           & 0 \\
 
-1           & 1           & 2           & 1           & 1 \\
-2           & 1           & 2           & 1           & 0.5 \\
+1           & 1           & 2           & 1           & 0 \\
+2           & 1           & 2           & 1           & -1 \\
 1           & 2           & 2           & 1           & 0 \\
-2           & 2           & 2           & 1           & 0 \\
-
-1           & 1           & 1           & 2           & 0 \\
+2           & 2           & 2           & 1           & 1 \\
+
+1           & 1           & 1           & 2           & 2 \\
 2           & 1           & 1           & 2           & 0 \\
-1           & 2           & 1           & 2           & -1 \\
-2           & 2           & 1           & 2           & 2 \\
+1           & 2           & 1           & 2           & 1/2 \\
+2           & 2           & 1           & 2           & 0 \\
 
 1           & 1           & 2           & 2           & 0 \\
-2           & 1           & 2           & 2           & 0 \\
-1           & 2           & 2           & 2           & 1 \\
-2           & 2           & 2           & 2           & 0.5
+2           & 1           & 2           & 2           & 2 \\
+1           & 2           & 2           & 2           & 0 \\
+2           & 2           & 2           & 2           & 1/2
 \end{tabular}
@@
 the shape of the RHS.
-This problem can then be reshaped to the following 2d problem,
-
-TODO: what the fuck these numbers are wrong.
+This problem can then be reshaped into a problem where $A' \mmult{1} B' = I'$
+Where $\shape{A'} = \left<4,4\right>$ is defined like this,
+
+\begin{table}[h!]
+\begin{center}
+\begin{tabular}{c c | c}
+$\bar{a}'[1]$ & $\bar{a}'[2]$ & $A'[\bar{a}']$ \\
+\hline
+1           & 1           & -1 \\
+2           & 1           & 0 \\
+3           & 1           & 1 \\
+4           & 1           & 0 \\
+
+1           & 2           & 0 \\
+2           & 2           & -1 \\
+3           & 2           & 0 \\
+4           & 2           & 1 \\
+
+1           & 3           & 2 \\
+2           & 3           & 0 \\
+3           & 3           & 1/2 \\
+4           & 3           & 0 \\
+
+1           & 4           & 0 \\
+2           & 4           & 2 \\
+3           & 4           & 0 \\
+4           & 4           & 1/2
+\end{tabular}
+\end{center}
+\end{table}
+
+With $\Ident^2(\left<2,2\right>)$ being reshaped into $I'$ similarly to form this equation,
+
 \[
@@
     0 & -1 & 0 & 2 \\
-    1 & 0 & 0.5 & 0 \\
-    0 & 1 & 0 & 0.5
+    1 & 0 & 1/2 & 0 \\
+    0 & 1 & 0 & 1/2 \\
   \end{array}
@@
   \begin{array}{c c c c}
-    -1/5 & 0 & 2/5 & 0 \\
-    0 & -1/5 & 0 & 2/5 \\
-    4/5 & 0 & 2/5 & 0 \\
-    0 & 4/5 & 0 & 2/5
+    -1/5 & 0 & 4/5 & 0 \\
+    0 & -1/5 & 0 & 4/5 \\
+    2/5 & 0 & 2/5 & 0 \\ 
+    0 & 2/5 & 0 & 2/5
   \end{array}
@@
 \]
-Therefore $B$ is,
+
+Therefore $B$ is as shown in the table below.
 \begin{table}[h!]
@@
 1           & 1           & 1           & 1           & -1/5 \\
-1           & 1           & 1           & 2           & 0 \\
-1           & 1           & 2           & 1           & 2/5 \\
+2           & 1           & 1           & 1           & 0 \\
+1           & 2           & 1           & 1           & 2/5 \\
+2           & 2           & 1           & 1           & 0 \\
+1           & 1           & 2           & 1           & 0 \\
+2           & 1           & 2           & 1           & -1/5 \\
+1           & 2           & 2           & 1           & 0 \\
+2           & 2           & 2           & 1           & 2/5 \\
+1           & 1           & 1           & 2           & 4/5 \\
+2           & 1           & 1           & 2           & 0 \\
+1           & 2           & 1           & 2           & 2/5 \\
+2           & 2           & 1           & 2           & 0 \\
 1           & 1           & 2           & 2           & 0 \\
-1           & 2           & 1           & 1           & 0 \\
-1           & 2           & 1           & 2           & -1/5 \\
-1           & 2           & 2           & 1           & 0 \\
-1           & 2           & 2           & 2           & 2/5 \\
-2           & 1           & 1           & 1           & 4/5 \\
-2           & 1           & 1           & 2           & 0 \\
-2           & 1           & 2           & 1           & 2/5 \\
-2           & 1           & 2           & 2           & 0 \\
-2           & 2           & 1           & 1           & 0 \\
-2           & 2           & 1           & 2           & 4/5 \\
-2           & 2           & 2           & 1           & 0 \\
+2           & 1           & 2           & 2           & 4/5 \\
+1           & 2           & 2           & 2           & 0 \\
 2           & 2           & 2           & 2           & 2/5
@@
     0 & 0 \\
-    1 & 0.5 \\
+    1 & 1/2 \\
     0 & 0 \\
@@
     0 & 0 \\
-    1 & 0.5
+    1 & 1/2 \\
   \end{array}
@@
 \end{example}
+
+TODO: can you turn a smaller inverse multimatrix into a larger inverse?
 

### 2021-01-05 MMatrix/test/test_math.cc

@@ -269,20 +269,20 @@ void TestIdentityContraction() {
 void InverseExample() {
   DenseMMatrix a({4,4});
   a.set({0,0}, -1);
-  a.set({0,1}, 2);
-  a.set({0,2}, 1);
-  a.set({0,3}, 0);
   a.set({1,0}, 0);
-  a.set({1,1}, -1);
-  a.set({1,2}, 0);
-  a.set({1,3}, 1);
-  a.set({2,0}, 2);
-  a.set({2,1}, 0);
-  a.set({2,2}, 0.5);
-  a.set({2,3}, 0);
+  a.set({2,0}, 1);
   a.set({3,0}, 0);
-  a.set({3,1}, 2);
+  a.set({0,1}, 0);
+  a.set({1,1}, -1);
+  a.set({2,1}, 0);
+  a.set({3,1}, 1);
+  a.set({0,2}, 2);
+  a.set({1,2}, 0);
+  a.set({2,2}, 0.5);
   a.set({3,2}, 0);
+  a.set({0,3}, 0);
+  a.set({1,3}, 2);
+  a.set({2,3}, 0);
   a.set({3,3}, 0.5);
 
   DenseMMatrix inv({4,4});
@@ -301,41 +301,42 @@ void InverseExample() {
 }
 
 void InverseExampleCheck() {
+  std::cout << "InverseExampleCheck..." << std::endl;
   DenseMMatrix a({2,2,2,2});
-  a.set({0,0,0,0}, 2);
-  a.set({0,0,0,1}, -2);
-  a.set({0,0,1,0}, 0);
-  a.set({0,0,1,1}, 2);
-  a.set({0,1,0,0}, -2);
-  a.set({0,1,0,1}, 0);
-  a.set({0,1,1,0}, -1);
-  a.set({0,1,1,1}, 1);
+  a.set({0,0,0,0}, -1);
   a.set({1,0,0,0}, 0);
-  a.set({1,0,0,1}, -1);
-  a.set({1,0,1,0}, 1);
-  a.set({1,0,1,1}, 0);
-  a.set({1,1,0,0}, 1);
-  a.set({1,1,0,1}, -2);
+  a.set({0,1,0,0}, 1);
+  a.set({1,1,0,0}, 0);
+  a.set({0,0,1,0}, 0);
+  a.set({1,0,1,0}, -1);
+  a.set({0,1,1,0}, 0);
[…]

### 2021-01-05 MMatrix/test/test_mmatrix.cc

@@ -455,6 +455,36 @@ void TestHMultiply() {
   }
 }
 
+void TestReshape() {
+  std::cout << "TestReshape..." << std::endl;
+  DenseMMatrix a({2,2,2,2});
+  a.set({0,0,0,0}, 0);
+  a.set({1,0,0,0}, 1);
+  a.set({0,1,0,0}, 2);
+  a.set({1,1,0,0}, 3);
+  a.set({0,0,1,0}, 4);
+  a.set({1,0,1,0}, 5);
+  a.set({0,1,1,0}, 6);
+  a.set({1,1,1,0}, 7);
+  a.set({0,0,0,1}, 8);
+  a.set({1,0,0,1}, 9);
+  a.set({0,1,0,1}, 10);
+  a.set({1,1,0,1}, 11);
+  a.set({0,0,1,1}, 12);
+  a.set({1,0,1,1}, 13);
+  a.set({0,1,1,1}, 14);
+  a.set({1,1,1,1}, 15);
+  
+  DenseMMatrix b({4,4});
+  Reshape(&a, &b);
+  for (int r = 0; r < b.shape()[0]; r++) {
+    for (int c = 0; c < b.shape()[1]; c++) {
+      std::cout << b.get({r,c}) << "  ";
+    }
+    std::cout << std::endl;
+  }
+}
+
 int main() {
   TestToFromVIndex();
   TestDenseMMatrixGetSet();
@@ -469,6 +499,7 @@ int main() {
   TestConcat();
   TestInverse();
   TestHMultiply();
+  //TestReshape();
   // Requires instrumenting matrix multiplication
   //ManualTestSparseSwitch();
   std::cout << "All tests pass." << std::endl;

### 2021-03-03 Math/book.tex
Havent saved in a while.

@@
 \newcommand{\shape}[1]{\left|#1\right|}
+\newcommand{\transpose}[2]{{#1}^{\{#2\}}}
+
+\let\oldemptyset\emptyset
+\let\emptyset\varnothing
 
@@
 
-We can define the total derivative for those cases as well.
+We can define the total derivative for those cases as well if we model scalar
+values as multimatrices of empty shapes. That leads to the following definitions,
 
@@
 Let $f(X)$ be some function from $\mathbb{R}^{\vec{x}}$ to $\mathbb{R}$.
-The complete derivative of $f$ with respect to $X$ is therefore in
+As we can model $f$ as a multimatrix of shape $\left<\right>$,
+the complete derivative of $f$ with respect to $X$ is therefore in
 $\mathbb{R}^{\vec{x}}$. That is,
 \begin{align*}
-f(X) &\in \mathbb{R} \\
+\shape{f(X)} &= \left<\right> \\
 \shape{X} &= \vec{x} \\
-\shape{\frac{df}{dX}} &= \vec{x}
+\shape{\frac{df}{dX}} &= \vec{x} \oplus \left<\right> = \vec{x}
 \end{align*}
@@
 Let $F(x)$ be some function from $\mathbb{R}$ to $\mathbb{R}^{\vec{f}}$.
-The complete derivative of $F$ with respect to $X$ is therefore in
+As we can model $x$ as a multimatrix of shape $\left<\right>$,
+the complete derivative of $F$ with respect to $x$ is therefore in
 $\mathbb{R}^{\vec{f}}$. That is,
@@
 \shape{F(x)} &= \vec{f} \\
-x &\in \mathbb{R} \\
-\shape{\frac{dF}{dx}} &= \vec{f}
+\shape{x} &= \left<\right> \\
+\shape{\frac{dF}{dx}} &= \left<\right> \oplus \vec{f} = \vec{f}
 \end{align*}
@@
 Easily done. The hard part isn't doing the calculation. The hard part is reframing the
-damn problem in your head as its geometric or `systems of equations' equivalent so that
-the operation is at least somewhat intuitive.
+damn thing in your head as a geometric transformation or as part of some
+systems of equations to make the operation more intuitive.
 
 So now consider how we would multiply two matrices $A$ and $B$ if they had more
-than two dimensions. Which doesn't really leverage either of those intuitive
+than two dimensions. Which doesn't really seem to leverage either of those intuitive
 approaches. Let's use a concrete example to make the problems more structurally sound.
@@
 \]
+
+The operator $\mmult{n}$ will also be used directly on shape vectors to denote
+what would happen to those shape vectors under the multimatrix multiplication operation.
+Thus, for any vectors $\vec{a}$, $\vec{b}$, and $\vec{c}$,
+\[ (\vec{a} \oplus \vec{c}) \mmult{\shape{\vec{c}}} (\vec{c} \oplus \vec{b}) = \vec{a} \oplus \vec{b} \]
 \end{definition}
@@
 Given $\shape{A}$ and $\shape{B}$, and by our definition of multimatrix multiplication,
-you can see that $\shape{A \mmult{2} B} = \left<2, 2\right>$. And the values of the
+you can see that $\shape{A \mmult{2} B} = \left<2,3,2\right> \mmult{2} \left<3,2,2\right> = \left<2, 2\right>$. And the values of the
 resulting multimatrix are defined:
@@
 their product $A \mmult{1} B$ is valid if and only if $r_a = l_b$ and
-the result is of shape $\shape{A \mmult{1} B} = \left<l_a, r_b\right>$.
+the result is of shape,
+\[ \shape{A \mmult{1} B} = \left<l_a, r_a\right> \mmult{1} \left<l_b, r_b\right> = \left<l_a, r_b\right> \]
 And of course, the value at each index
@@
 All of which would be the same if this was regular matrix multiplication.
+
+TODO: explain how this type of multiplication works as a system of equations
+
+TODO: explain how this type of multiplication works geometrically
 
@@
 two multiplicative inverse I can think of off the top of my head;
-$\RMult[2,\Ident^2(\left<2,2\right)]$ or
+$\RMult[2,\Ident^2(\left<2,2\right>)]$ or
 $\RMult[1,\Ident^2(\left<2\right>)]$.
@@
 
-TODO: exposition
+The Hadamard product, like the regular product, is only sometimes associative. Consider, for example,
+the case where $\shape{A} = \left< 3, 2 \right>$, $\shape{B} = \left< 2 \right>$, and $\shape{C} = \left<2, 3\right>$.
+Then $(A \dmult{1} B) \dmult{2} C$ is valid but $A \dmult{1} (B \dmult{2} C)$ is not because
+$B \dmult{2} C$ doesn't work.
 
 \begin{theorem}[Hadamard Product Associativity]
-Let $A$, $B$, and $C$ be multimatrices such that $\shape{A} = \vec{a} \oplus \vec{m}$,
-$\shape{B} = \vec{m} \oplus \vec{b} \oplus \vec{n}$ and $\shape{C} = \vec{n} \oplus \vec{c}$,
-where $\shape{\vec{m}} = m$ and $\shape{\vec{n}} = n$.
-Then $(A \dmult{m} B) \dmult{n} C = A \dmult{m} (B \dmult{n} C)$.
+Let $A$, $B$, and $C$ be multimatrices and $m$ and $n$ integers such that
+$m \le \shape{\shape{B}}$ and $n \le \shape{\shape{B}}$.
+Then if either $(A \dmult{m} B) \dmult{n} C$ or $A \dmult{m} (B \dmult{n} C)$ is valid,
+the other is also valid and
+\[ (A \dmult{m} B) \dmult{n} C = A \dmult{m} (B \dmult{n} C) \]
 \end{theorem}
 \begin{proof}
-For all $\bar{a} \in \Dim(\vec{a})$, etc,
-\begin{align*}
-((A \dmult{m} B) \dmult{n} C)[\bar{a} \oplus \bar{m} \oplus \bar{b} \oplus \bar{n} \oplus \bar{c}]
-  &= (A \dmult{m} B)[\bar{a} \oplus \bar{m} \oplus \bar{b} \oplus \bar{n}] C[\bar{n} \oplus \bar{c}] \\
-  &= (A[\bar{a} \oplus \bar{m}] B[\bar{m} \oplus \bar{b} \oplus \bar{n}]) C[\bar{n} \oplus \bar{c}] \\
-  &= A[\bar{a} \oplus \bar{m}] (B[\bar{m} \oplus \bar{b} \oplus \bar{n}] C[\bar{n} \oplus \bar{c}]) \\
-  &= A[\bar{a} \oplus \bar{m}] (B \dmult{n} C)[\bar{m} \oplus \bar{b} \oplus \bar{n} \oplus \bar{c}] \\
-  &= (A \dmult{m} (B \dmult{n} C))[\bar{a} \oplus \bar{m} \oplus \bar{b} \oplus \bar{n} \oplus \bar{c}]
-\end{align*}
+\begin{ppart}
+Let $A$, $B$, and $C$ be multimatrices and $m$ and $n$ integers
+$m \le \shape{\shape{B}}$ and $n \le \shape{\shape{B}}$ such that
+$(A \dmult{m} B) \dmult{n} C$ is valid.
+We can therefore construct the following shape vectors from the definition of the Hadamard product.
+\[ \shape{A \dmult{m} B} = \vec{a} \oplus \vec{m} \oplus \vec{b} \]
+\[ \shape{A} = \vec{a} \oplus \vec{m} \]
+\[ \shape{B} = \vec{m} \oplus \vec{b} \]
+\[ \shape{(A \dmult{m} B) \dmult{n} C} = \vec{l} \oplus \vec{n} \oplus \vec{c} \]
+\[ \shape{A \dmult{m} B} = \vec{l} \oplus \vec{n} \]
+\[ \shape{C} = \vec{n} \oplus \vec{c} \]
+Where $\shape{\vec{m}} = m$ and $\shape{\vec{n}} = n$. 
+Then since $\vec{a} \oplus \vec{m} \oplus \vec{b} = \vec{l} \oplus \vec{n}$ we can divide this further into two
+separate cases.
+\begin{case} $\shape{\vec{b}} \ge \shape{\vec{n}}$
+
+Then we can divide $\vec{b}$ into $\vec{b} = \vec{b}_c \oplus \vec{n}$
+Therefore,
+\[ \shape{B} = \vec{m} \oplus \vec{b}_c \oplus \vec{n} \]
+\[ \shape{A \dmult{m} B} = \vec{a} \oplus \vec{m} \oplus \vec{b}_c \oplus \vec{n} = \vec{l} \oplus \vec{n} \]
+\[ \vec{l} = \vec{a} \oplus \vec{m} \oplus \vec{b}_c \]
+\[ \shape{(A \dmult{m} B) \dmult{n} C} = \vec{a} \oplus \vec{m} \oplus \vec{b}_c \oplus \vec{n} \oplus \vec{c} \]
+So, $B \dmult{n} C$ is valid and,
+\[ \shape{B \dmult{n} C} = \vec{m} \oplus \vec{b}_c \oplus \vec{n} \oplus \vec{c} \]
+Which means that $A \dmult{m} (B \dmult{n} C)$ is also valid and,
+\[ \shape{A \dmult{m} (B \dmult{n} C)} = \vec{a} \oplus \vec{m} \oplus \vec{b}_c \oplus \vec{n} \oplus \vec{c} \]
+
+Now consider that for all $\bar{a}$, $\bar{m}$, $\bar{b}_c$, $\bar{n}$, and $\bar{c}$ in
+$\Dim(\vec{a})$, $\Dim(\vec{m})$, $\Dim(\vec{b}_c)$, $\Dim(\vec{n})$ and $\Dim(\vec{c})$ respectively,
+\begin{align*}
+  ((A \dmult{m} B) \dmult{n} C)[\bar{a} \oplus \bar{m} \oplus \bar{b}_c \oplus \bar{n} \oplus \bar{c}]
+  &=
+  (A \dmult{m} B)[\bar{a} \oplus \bar{m} \oplus \bar{b}_c \oplus \bar{n}]C[\bar{n} \oplus \bar{c}] \\
+  &=
+  A[\bar{a} \oplus \bar{m}]B[\bar{m} \oplus \bar{b}_c \oplus \bar{n}]C[\bar{n} \oplus \bar{c}] \\
+  &=
+  A[\bar{a} \oplus \bar{m}](B \dmult{n} C)[\bar{m} \oplus \bar{b}_c \oplus \bar{n} \oplus \bar{c}] \\
+  &=
+  (A \dmult{m} (B \dmult{n} C))[\bar{a} \oplus \bar{m} \oplus \bar{b}_c \oplus \bar{n} \oplus \bar{c}]
+\end{align*}
+
+So in this case, $(A \dmult{m} B) \dmult{n} C = A \dmult{m} (B \dmult{n} C)$.
+\end{case}
+\begin{case} $\shape{\vec{b}} < \shape{\vec{n}}$
+
+Then we can divide $\vec{n}$ into $\vec{n} = \vec{n}_l \oplus \vec{b}$.
+So,
+\begin{align*}
+  \vec{a} \oplus \vec{m} \oplus \vec{b} &= \vec{l} \oplus \vec{n}_l \oplus \vec{b} \\
+  \vec{a} \oplus \vec{m} &= \vec{l} \oplus \vec{n}_l
+\end{align*}
+
+Then because we have the constraint that $n \le \shape{\shape{B}}$
+\begin{align*}
+  n &\le \shape{\shape{B}} \\
+  \shape{\vec{n}} &\le \shape{\vec{m} \oplus \vec{b}} \\
+  \shape{\vec{n}_l \oplus \vec{b}} &\le \shape{\vec{m} \oplus \vec{b}} \\
+  \shape{\vec{n}_l} &\le \shape{\vec{m}}
+\end{align*}
+
+And so $\vec{m}$ can be divided into $\vec{m} = \vec{m}_l \oplus \vec{n}_l$,
+resulting in,
+\[ \shape{B} = \vec{m}_l \oplus \vec{n}_l \oplus \vec{b} = \vec{m}_l \oplus \vec{n} \]
+So $B \dmult{n} C$ is a valid operation and,
+\[ \shape{B \dmult{n} C} = \vec{m_l} \oplus \vec{n} \oplus \vec{c} = \vec{m} \oplus \vec{b} \oplus \vec{c} \]
+Which further shows that $A \dmult{m} (B \dmult{n} C)$ is also a valid operation and,
+\begin{align*}
+  \vec{a} \oplus \vec{m} &= \vec{l} \oplus \vec{n}_l \\
+  \vec{a} \oplus \vec{m}_l \oplus \vec{n}_l &= \vec{l} \oplus \vec{n}_l \\
+  \vec{a} \oplus \vec{m}_l &= \vec{l}
+\end{align*}
+So,
+\begin{align*}
+  \shape{(A \dmult{m} B) \dmult{n} C}
+  &= \vec{l} \oplus \vec{n} \oplus \vec{c} \\
+  &= \vec{a} \oplus \vec{m}_l \oplus \vec{n}_l \oplus \vec{b} \oplus \vec{c} \\
+  &= \shape{A \dmult{m} (B \dmult{n} C)}
+\end{align*}
+
+Now consider that for all $\bar{a}$, $\bar{m}_l$, $\bar{n}_l$, $\bar{b}$, and $\bar{c}$ in
+$\Dim(\vec{a})$, $\Dim(\vec{m}_l)$, $\Dim(\vec{n}_l)$, $\Dim(\vec{b})$ and $\Dim(\vec{c})$ respectively,
+\begin{align*}
+  ((A \dmult{m} B) \dmult{n} C)[\bar{a} \oplus \bar{m}_l \oplus \bar{n}_l \oplus \bar{b} \oplus \bar{c}]
+  &=
+  (A \dmult{m} B)[\bar{a} \oplus \bar{m}_l \oplus \bar{n}_l \oplus \bar{b}] C[\bar{n}_l \oplus \bar{b} \oplus \bar{c}] \\
+  &=
+  A[\bar{a} \oplus \bar{m}_l \oplus \bar{n}_l] B[\bar{m}_l \oplus \bar{n}_l \oplus \bar{b}] C[\bar{n}_l \oplus \bar{b} \oplus \bar{c}] \\
+  &=
+  A[\bar{a} \oplus \bar{m}_l \oplus \bar{n}_l] (B \dmult{n} C)[\bar{m}_l \oplus \bar{n}_l \oplus \bar{b} \oplus \bar{c}] \\
+  &=
+  (A \dmult{m} (B \dmult{n} C))[\bar{a} \oplus \bar{m}_l \oplus \bar{n}_l \oplus \bar{b} \oplus \bar{c}]
+\end{align*}
+So in this case, $(A \dmult{m} B) \dmult{n} C = A \dmult{m} (B \dmult{n} C)$.
+\end{case}
+\end{ppart}
+\begin{ppart}
+Let $A$, $B$, and $C$ be multimatrices and $m$ and $n$ integers
+$m \le \shape{\shape{B}}$ and $n \le \shape{\shape{B}}$ such that
+$A \dmult{m} (B \dmult{n} C)$ is valid.
+
+We can therefore construct the following shape vectors from the definition of the Hadamard product.
+\[ \shape{B \dmult{n} C} =  \vec{b} \oplus \vec{n} \oplus \vec{c} \]
+\[ \shape{B} =  \vec{b} \oplus \vec{n} \]
+\[ \shape{C} =  \vec{n} \oplus \vec{c} \]
+\[ \shape{A \dmult{m} (B \dmult{n} C)} =  \vec{a} \oplus \vec{m} \oplus \vec{r} \]
+\[ \shape{A} =  \vec{a} \oplus \vec{m} \]
+\[ \shape{B \dmult{n} C} =  \vec{m} \oplus \vec{r} \]
+
+Where $\shape{\vec{m}} = m$ and $\shape{\vec{n}} = n$. 
+Then since $\vec{b} \oplus \vec{n} \oplus \vec{c} = \vec{m} \oplus \vec{r}$ we can divide this further into two
+separate cases.
+
+\setcounter{case}{0}
+\begin{case} $\shape{\vec{b}} \ge \shape{\vec{m}}$
+
+In this case we can split up $\vec{b}$ into $\vec{b} = \vec{m} \oplus \vec{b}_c$. Then,
+\[ \shape{B} = \vec{m} \oplus \vec{b}_c \oplus \vec{n} \]
+\[ \shape{B \dmult{n} C} = \vec{m} \oplus \vec{b}_c \oplus \vec{n} \oplus \vec{c} = \vec{m} \oplus \vec{r} \]
+\[ \vec{r} = \vec{b}_c \oplus \vec{n} \oplus \vec{c} \]
+\[ \shape{A \dmult{m} (B \dmult{n} C)} = \vec{a} \oplus \vec{m} \oplus \vec{b}_r \oplus \vec{n} \oplus \vec{c} \]
+
+Which means that $A \dmult{m} B$ is valid and,
+\[ \shape{A \dmult{m} B} = \vec{a} \oplus \vec{m} \oplus \vec{b}_c \oplus \vec{n} \]
+Which means that $(A \dmult{m} B) \dmult{n} C$ is also valid and,
+\[ \shape{(A \dmult{m} B) \dmult{n} C} = \vec{a} \oplus \vec{m} \oplus \vec{b}_c \oplus \vec{n} \oplus \vec{c} \]
+
+Now by the same argument as part 1, case 1, it follows that $A \dmult{m} (B \dmult{n} C) = (A \dmult{m} B) \dmult{n} C$.
+\end{case}
+\begin{case} $\shape{\vec{b}} < \shape{\vec{m}}$
+
+Then we can divide $\vec{m}$ into $\vec{m} = \vec{b} \oplus \vec{m}_r$.
+So,
+\begin{align*}
+  \vec{b} \oplus \vec{n} \oplus \vec{c} &= \vec{b} \oplus \vec{m}_r \oplus \vec{r} \\
+  \vec{n} \oplus \vec{c} &= \vec{m}_r \oplus \vec{r}
+\end{align*}
+
+Then because we have the constraint that $m \le \shape{\shape{B}}$
+\begin{align*}
+  m &\le \shape{\shape{B}} \\
+  \shape{\vec{m}} &\le \shape{\vec{b} \oplus \vec{n}} \\
+  \shape{\vec{b} \oplus \vec{m}_r} &\le \shape{\vec{b} \oplus \vec{n}} \\
+  \shape{\vec{m}_r} &\le \shape{\vec{n}}
+\end{align*}
+
+And so $\vec{n}$ can be divided into $\vec{n} = \vec{m}_r \oplus \vec{n}_r$,
+resulting in,
+\[ \shape{B} = \vec{b} \oplus \vec{m}_r \oplus \vec{n}_r = \vec{m} \oplus \vec{n}_r \]
+So $A \dmult{m} B$ is a valid operation and,
+\[ \shape{A \dmult{m} B} = \vec{a} \oplus \vec{m} \oplus \vec{n}_r = \vec{a} \oplus \vec{b} \oplus \vec{n} \]
+Which further shows that $(A \dmult{m} B) \dmult{n} C$ is also a valid operation and,
+\begin{align*}
+  \vec{n} \oplus \vec{c} &= \vec{m}_r \oplus \vec{r} \\
+  \vec{m}_r \oplus \vec{n}_r \oplus \vec{c} &= \vec{m}_r \oplus \vec{r} \\
+  \vec{n}_r \oplus \vec{c} &= \vec{r}
+\end{align*}
+So,
+\begin{align*}
+  \shape{A \dmult{m} (B \dmult{n} C)}
+  &= \vec{a} \oplus \vec{m} \oplus \vec{r} \\
+  &= \vec{a} \oplus \vec{b} \oplus \vec{m}_r \oplus \vec{n}_r \oplus \vec{c} \\
+  &= \shape{(A \dmult{m} B) \dmult{n} C}
+\end{align*}
+
+Now consider that for all $\bar{a}$, $\bar{b}$, $\bar{m}_r$, $\bar{n}_r$, and $\bar{c}$ in
+$\Dim(\vec{a})$, $\Dim(\vec{b})$, $\Dim(\vec{m}_r)$, $\Dim(\vec{n}_r)$ and $\Dim(\vec{c})$ respectively,
+\begin{align*}
+  (A \dmult{m} (B \dmult{n} C))[\bar{a} \oplus \bar{b} \oplus \bar{m}_r \oplus \bar{n}_r \oplus \bar{c}]
+  &= A[\bar{a} \oplus \bar{b} \oplus \bar{m}_r] (B \dmult{n} C)[\bar{b} \oplus \bar{m}_r \oplus \bar{n}_r \oplus \bar{c}] \\
+  &= A[\bar{a} \oplus \bar{b} \oplus \bar{m}_r] B[\bar{b} \oplus \bar{m}_r \oplus \bar{n}_r] C[\bar{m}_r \oplus \bar{n}_r \oplus \bar{c}] \\
+  &= (A \dmult{m} B)[\bar{a} \oplus \bar{b} \oplus \bar{m}_r \oplus \bar{n}_r] C[\bar{m}_r \oplus \bar{n}_r \oplus \bar{c}] \\
+  &= ((A \dmult{m} B) \dmult{n} C)[\bar{a} \oplus \bar{b} \oplus \bar{m}_r \oplus \bar{n}_r \oplus \bar{c}]
+\end{align*}
+
+So $A \dmult{m} (B \dmult{n} C) = (A \dmult{m} B) \dmult{n} C$.
+\end{case}
+\end{ppart}
+Which concludes the proof, as it is now shown that in both directions when $m \le \shape{\shape{B}}$ and $n \le \shape{\shape{B}}$,
+$(A \dmult{m} B) \dmult{n} C = A \dmult{m} (B \dmult{n} C)$.
 \end{proof}
@@
 
-\begin{theorem}[Equivalent Hadamard Product and Multiplication Chains]
-When $X_1 \ldots X_{m-1}$ are all in $\mathbb{R}^{\vec{x}}$ and
-$\shape{X_m} = \vec{x} \oplus \vec{r}$ for any $\vec{r}$,
-\[
-  (((\Ident^n(\vec{x})
-  \mmult{\shape{\vec{x}}} X_1) \mmult{\shape{\vec{x}}} X_2) \mmult{\shape{\vec{x}}} X_3)
-  \ldots X_m
-  =
-  \Ident^{n-m}(\vec{x})
-  \dmult{\shape{\vec{x}}} X_1 \dmult{\shape{\vec{x}}} X_2 \dmult{\shape{\vec{x}}} X_3
-  \ldots X_m
-\]
-And when $X_2 \ldots X_m$ are all in $\mathbb{R}^{\vec{x}}$ and
-$\shape{X_1} = \vec{l} \oplus \vec{x}$ for any $\vec{l}$,
-\[
-  X_1 \mmult{\shape{\vec{x}}} (X_2 \mmult{\shape{\vec{x}}} (X_3
-  \ldots (X_m \mmult{\shape{\vec{x}}} 
-  \Ident^n(\vec{x}))))
-  =
-  X_1 \dmult{\shape{\vec{x}}} X_2 \dmult{\shape{\vec{x}}} X_3
-  \ldots X_m \dmult{\shape{\vec{x}}} 
-  \Ident^{n-m}(\vec{x})
-\]
+\begin{theorem}[Identity Multiplication and Hadamard Reductions]
+Consider $\shape{X} = (k * \vec{x}) \oplus \vec{r}$ for any vectors $\vec{x}$ and $\vec{r}$
+and natural number $k$. And let $n \ge k$. Then,
+\[ \Ident^n(\vec{x}) \mmult{k\shape{\vec{x}}} X = \Ident^{n-k}(\vec{x}) \dmult{k\shape{\vec{x}}} X \]
+
+Or when $\shape{X} = \vec{l} \oplus (k * \vec{x})$ for any vectors $\vec{x}$ and $\vec{l}$
+and natural number $k$. And let $n \ge k$. Then,
+\[ X \mmult{k\shape{\vec{x}}} \Ident^n(\vec{x}) = X \dmult{k\shape{\vec{x}}} \Ident^{n-k}(\vec{x}) \]
 \end{theorem}
+\begin{landscape}
 \begin{proof}
-TODO 
+\begin{ppart}
+Let $\shape{X} = (k * \vec{x}) \oplus \vec{r}$ for any vectors $\vec{x}$ and $\vec{r}$
+and natural number $k$. And let $n > k$.
+Then let all $\bar{r} \in \Dim(\vec{r})$ and all $\bar{x}_i \in \Dim(\vec{x})$ for $1 \le i \le n-k$ and let
+$\bar{c}_{[a,b]}$ denote the following in general,
+\[ \bar{c}_{[a,b]} = \bigoplus_{i \in [a,b]} \bar{c}_i \]
+\begin{align*}
+  \left(\Ident^n(\vec{x}) \mmult{\shape{\vec{x}}} X\right)[\bar{x}_{[1,n-k]} \oplus \bar{r}]
+  =& \sum_{\forall \bar{c}_j \in \Dim(\vec{x}), j \in [n-k+1, n]} \Ident^n(\vec{x})[\bar{x}_{[1,n-k]} \oplus \bar{c}_{[n-k+1,n]}] X[\bar{c}_{[n-k+1,n]} \oplus \bar{r}] \\
+  =& \Ident^n(\vec{x})[\bar{x}_{[1,n-k]} \oplus (k * \bar{x}_1)] X[(k * \bar{x}_1) \oplus \bar{r}] \\
+  &+ \sum_{\forall \bar{c}_j, \bar{c}_j \ne \bar{x}_1}
+    \Ident^n(\vec{x})[\bar{x}_{[1,n-k]} \oplus \bar{c}_{[n-k+1,n]}] X[\bar{c}_{[n-k+1,n]} \oplus \bar{r}] \\
+  =& \Ident^{n-k}(\vec{x})[\bar{x}_{[1,n-k]}] X[(k * \bar{x}_1) \oplus \bar{r}]
+    + \sum_{\forall \bar{c}_j, \bar{c}_j \ne \bar{x}_1}
+    (0) X[\bar{c}_{[n-k+1,n]} \oplus \bar{r}] \\
+  =& \Ident^{n-k}(\vec{x})[\bar{x}_{[1,n-k]}] X[(k * \bar{x}_1) \oplus \bar{r}] \\
+  =& 
+    \left\{
+      \begin{array}{ll}
+        X[(k * \bar{x}_1) \oplus \bar{r}] & \mbox{if } \forall i \in [2,n-k] : \bar{x}_i = \bar{x}_1 \\
+        0 & \mbox{otherwise}
+      \end{array}
+    \right. \\
+  =& \Ident^{n-k}(\vec{x})[\bar{x}_{[1,n-k]}] X[\bar{x}_{[1,n-k]} \oplus \bar{r}] \\
+  =& \left(\Ident^{n-k}(\vec{x}) \dmult{k\shape{\vec{x}}} X\right)[\bar{x}_{[1,n-k]} \oplus \bar{r}]
+\end{align*}
+So $\Ident^n(\vec{x}) \mmult{\shape{\vec{x}}} X = \Ident^{n-k}(\vec{x}) \dmult{k\shape{\vec{x}}} X$.
+\end{ppart}
+\begin{ppart}
+Let $\shape{X} = \vec{l} \oplus (k * \vec{x})$ for any vectors $\vec{x}$ and $\vec{l}$
+and natural number $k$. And let $n > k$.
+Then let all $\bar{l} \in \Dim(\vec{l})$ and all $\bar{x}_i \in \Dim(\vec{x})$ for $k+1 \le i \le n$ and let
+$\bar{c}_{[a,b]}$ denote the following in general,
+\[ \bar{c}_{[a,b]} = \bigoplus_{i \in [a,b]} \bar{c}_i \]
+\begin{align*}
+  \left(X \mmult{\shape{\vec{x}}} \Ident^n(\vec{x})\right)[\bar{l} \oplus \bar{x}_{[k+1,n]}]
+  =& \sum_{\forall \bar{c}_j \in \Dim(\vec{x}), j \in [1, k]} X[\bar{l} \oplus \bar{c}_{[1,k]}] \Ident^n(\vec{x})[\bar{c}_{[1,k]} \oplus \bar{x}_{[k+1,n]}] \\
+  =& X[\bar{l} \oplus (k*\bar{x}_{k+1})] \Ident^n(\vec{x})[(k*\bar{x}_{k+1}) \oplus \bar{x}_{[k+1,n]}] \\
+   & +\sum_{\forall \bar{c}_j \ne \bar{x}_{k+1}} X[\bar{l} \oplus \bar{c}_{[1,k]}] \Ident^n(\vec{x})[\bar{c}_{[1,k]} \oplus \bar{x}_{[k+1,n]}] \\
+  =& X[\bar{l} \oplus (k*\bar{x}_{k+1})] \Ident^{n-k}(\vec{x})[\bar{x}_{[k+1,n]}]
+     +\sum_{\forall \bar{c}_j \ne \bar{x}_{k+1}} X[\bar{l} \oplus \bar{c}_{[1,k]}] (0) \\
+  =& X[\bar{l} \oplus (k*\bar{x}_{k+1})] \Ident^{n-k}(\vec{x})[\bar{x}_{[k+1,n]}] \\
+  =& 
+    \left\{
+      \begin{array}{ll}
+        X[\bar{l} \oplus (k * \bar{x}_{k+1})] & \mbox{if } \forall i \in [k+2,n] : \bar{x}_i = \bar{x}_{k+1} \\
+        0 & \mbox{otherwise}
+      \end{array}
+    \right. \\
+  =& X[\bar{l} \oplus \bar{x}_{[k+1,n]}] \Ident^{n-k}(\vec{x})[\bar{x}_{[k+1,n]}] \\
+  =& \left(X \dmult{k\shape{\vec{x}}} \Ident^{n-k}(\vec{x})\right)[\bar{l} \oplus \bar{x}_{[k+1,n]}]
+\end{align*}
+So $X \mmult{\shape{\vec{x}}} \Ident^n(\vec{x}) = X \dmult{k\shape{\vec{x}}} \Ident^{n-k}(\vec{x})$.
+\end{ppart}
 \end{proof}
+\end{landscape}
 
@@
 \end{proof}
+
+TODO: When are Hadamard products and regular products associative?
+
+\begin{theorem}[Associativity of Mixed Hadamard and Regular Products]
+Consider multimatrices $A$, $B$, and $C$ and non-negative integers $n$ and $m$
+such that $m+n \le \shape{\shape{B}}$.
+
+If either $(A \mmult{m} B) \dmult{n} C$ or $A \mmult{m} (B \dmult{n} C)$ is
+valid, then the other is also valid and,
+\[ (A \mmult{m} B) \dmult{n} C = A \mmult{m} (B \dmult{n} C) \]
+
+If either $(A \dmult{n} B) \mmult{m} C$ or $A \dmult{n} (B \mmult{m} C)$ is
+valid, then the other is also valid and,
+\[ (A \dmult{n} B) \mmult{m} C = A \dmult{n} (B \mmult{m} C) \]
+\end{theorem}
+\begin{proof}
+\begin{ppart}
+Let $A$, $B$, and $C$ be multimatrices and let $n$ and $m$ be non-negative integers that $m+n \le \shape{\shape{B}}$.
+Then let it be true that either $(A \mmult{m} B) \dmult{n} C$ or $A \mmult{m} (B \dmult{n} C)$ is valid.
+Since $0 < m$, $0 < n$, and $m + n \le \shape{\shape{B}}$, we know we can divide $\shape{B}$ thusly,
+\[ \shape{B} = \vec{m} \oplus \vec{b} \oplus \vec{n} \]
+Where $\shape{\vec{m}} = m$ and $\shape{\vec{n}} = n$.
+
+\begin{case} $(A \mmult{m} B) \dmult{n} C$ is valid.
+
+By our definitions of multiplication,
+\[ \shape{A \mmult{m} B} = \vec{a} \oplus \vec{b} \oplus \vec{n} \]
+\[ \shape{A} = \vec{a} \oplus \vec{m} \]
+\[ \shape{(A \mmult{m} B) \dmult{n} C} = \vec{a} \oplus \vec{b} \oplus \vec{n} \oplus \vec{c} \]
+\[ \shape{C} = \vec{n} \oplus \vec{c} \]
+For some vectors $\vec{a}$ and $\vec{c}$. 
+Therefore $B \dmult{n} C$ is valid and,
+\[ \shape{B \dmult{n} C} = \vec{m} \oplus \vec{b} \oplus \vec{n} \oplus \vec{c} \]
+So, $A \mmult{m} (B \dmult{n} C)$ is valid and,
+\[ \shape{A \mmult{m} (B \dmult{n} C)} = \shape{(A \mmult{m} B) \dmult{n} C} = \vec{a} \oplus \vec{b} \oplus \vec{n} \oplus \vec{c} \]
+\end{case}
+\begin{case} $A \mmult{m} (B \dmult{n} C)$ is valid.
+
+By our definitions of multiplication,
+\[ \shape{B \dmult{n} C} = \vec{m} \oplus \vec{b} \oplus \vec{n} \oplus \vec{c} \]
+\[ \shape{C} = \vec{n} \oplus \vec{c} \]
+\[ \shape{A \mmult{m} (B \dmult{n} C)} = \vec{a} \oplus \vec{b} \oplus \vec{n} \oplus \vec{c} \]
+\[ \shape{A} = \vec{a} \oplus \vec{m} \]
+For some vectors $\vec{a}$ and $\vec{c}$. 
+Therefore $A \mmult{m} B$ is valid and,
+\[ \shape{A \mmult{m} B} = \vec{a} \oplus \vec{b} \oplus \vec{n} \]
+So, $(A \mmult{m} B) \dmult{n} C$ is valid and,
+\[ \shape{(A \mmult{m} B) \dmult{n} C} = \shape{A \mmult{m} (B \dmult{n} C)} = \vec{a} \oplus \vec{b} \oplus \vec{n} \oplus \vec{c} \]
+\end{case}
+
+So in either case, the validity of the one implies the validity of the other. And with, conveniently, the same shape breakdown.
+
+Now, for all $\bar{a} \in \Dim(\vec{a})$, $\bar{b} \in \Dim(\vec{b})$, $\bar{n} \in \Dim(\vec{n})$, and $\bar{c} \in \Dim(\vec{c})$,
+\begin{align*}
+  \left((A \mmult{m} B) \dmult{n} C\right)[\bar{a} \oplus \bar{b} \oplus \bar{n} \oplus \bar{c}]
+  &= (A \mmult{m} B)[\bar{a} \oplus \bar{b} \oplus \bar{n}] C[\bar{n} \oplus \bar{c}] \\
+  &= \left(\sum_{\forall \bar{m} \in \Dim(\vec{m})} A[\bar{a} \oplus \bar{m}] B[\bar{m} \oplus \bar{b} \oplus \bar{n}]\right) C[\bar{n} \oplus \bar{c}] \\
+  &= \sum_{\forall \bar{m}} A[\bar{a} \oplus \bar{m}] B[\bar{m} \oplus \bar{b} \oplus \bar{n}] C[\bar{n} \oplus \bar{c}] \\
+  &= \sum_{\forall \bar{m}} A[\bar{a} \oplus \bar{m}] (B \dmult{n} C)[\bar{m} \oplus \bar{b} \oplus \bar{n} \oplus \bar{c}] \\
+  &= \left(A \mmult{m} (B \dmult{n} C)\right)[\bar{a} \oplus \bar{b} \oplus \bar{n} \oplus \bar{c}]
+\end{align*}
+
+So $(A \mmult{m} B) \dmult{n} C = A \mmult{m} (B \dmult{n} C)$.
+\end{ppart}
+\setcounter{case}{0}
+Let $A$, $B$, and $C$ be multimatrices and let $n$ and $m$ be non-negative integers that $m+n \le \shape{\shape{B}}$.
+Then let it be true that either $(A \dmult{n} B) \mmult{m} C$ or $A \dmult{n} (B \mmult{m} C)$ is valid.
+Since $0 < m$, $0 < n$, and $m + n \le \shape{\shape{B}}$, we know we can divide $\shape{B}$ thusly,
+\[ \shape{B} = \vec{n} \oplus \vec{b} \oplus \vec{m} \]
+Where $\shape{\vec{m}} = m$ and $\shape{\vec{n}} = n$.
+
+\begin{case} $(A \dmult{n} B) \mmult{m} C$ is valid.
+
+By our definitions of multiplication,
+\[ \shape{A \dmult{n} B} = \vec{a} \oplus \vec{n} \oplus \vec{b} \oplus \vec{m} \]
+\[ \shape{A} = \vec{a} \oplus \vec{n} \]
+\[ \shape{(A \dmult{n} B) \mmult{m} C} = \vec{a} \oplus \vec{n} \oplus \vec{b} \oplus \vec{c} \]
+\[ \shape{C} = \vec{m} \oplus \vec{c} \]
+For some vectors $\vec{a}$ and $\vec{c}$. 
+Therefore $B \mmult{m} C$ is valid and,
+\[ \shape{B \mmult{m} C} = \vec{n} \oplus \vec{b} \oplus \vec{c} \]
+So, $A \dmult{n} (B \mmult{m} C)$ is valid and,
+\[ \shape{A \dmult{n} (B \mmult{m} C)} = \shape{(A \dmult{n} B) \mmult{m} C} = \vec{a} \oplus \vec{n} \oplus \vec{b} \oplus \vec{c} \]
+\end{case}
+\begin{case} $A \dmult{n} (B \mmult{m} C)$ is valid.
+
+By our definitions of multiplication,
+\[ \shape{B \mmult{m} C} = \vec{n} \oplus \vec{b} \oplus \vec{c} \]
+\[ \shape{C} = \vec{m} \oplus \vec{c} \]
+\[ \shape{A \dmult{n} (B \mmult{m} C)} = \vec{a} \oplus \vec{n} \oplus \vec{b} \oplus \vec{c} \]
+\[ \shape{A} = \vec{a} \oplus \vec{n} \]
+For some vectors $\vec{a}$ and $\vec{c}$. 
+Therefore $A \dmult{n} B$ is valid and,
+\[ \shape{A \dmult{n} B} = \vec{a} \oplus \vec{n} \oplus \vec{b} \]
+So, $(A \dmult{n} B) \mmult{m} C$ is valid and,
+\[ \shape{(A \dmult{n} B) \mmult{m} C} = \shape{A \dmult{n} (B \mmult{m} C)} = \vec{a} \oplus \vec{n} \oplus \vec{b} \oplus \vec{c} \]
+\end{case}
+
+So in either case, the validity of the one implies the validity of the other. And with, conveniently, the same shape breakdown.
+
+Now, for all $\bar{a} \in \Dim(\vec{a})$, $\bar{n} \in \Dim(\vec{n})$, $\bar{b} \in \Dim(\vec{b})$, and $\bar{c} \in \Dim(\vec{c})$,
+\begin{align*}
+  \left((A \dmult{n} B) \mmult{m} C\right)[\bar{a} \oplus \bar{n} \oplus \bar{b} \oplus \bar{c}]
+  &=
+  \sum_{\forall \bar{m} \in \Dim(\vec{m})} (A \dmult{n} B)[\bar{a} \oplus \bar{n} \oplus \bar{b} \oplus \bar{m}] C[\bar{m} \oplus \bar{n}] \\
+  &=
+  \sum_{\forall \bar{m}} A[\bar{a} \oplus \bar{n}] B[\bar{n} \oplus \bar{b} \oplus \bar{m}] C[\bar{m} \oplus \bar{n}] \\
+  &=
+  A[\bar{a} \oplus \bar{n}] \sum_{\forall \bar{m}} B[\bar{n} \oplus \bar{b} \oplus \bar{m}] C[\bar{m} \oplus \bar{n}] \\
+  &=
+  A[\bar{a} \oplus \bar{n}] (B \mmult{m} C)[\bar{n} \oplus \bar{b} \oplus \bar{n}] \\
+  &= \left( A \dmult{n} (B \mmult{m} C) \right)[\bar{a} \oplus \bar{n} \oplus \bar{b} \oplus \bar{n}]
+\end{align*}
+
+So $(A \dmult{n} B) \mmult{m} C = A \dmult{n} (B \mmult{m} C)$.
+\end{proof}
+
+TODO: Exposition: I think the following follows from the associativity of mixed products and contraction of identities
 
@@
 \label{tran_def}
-Let $\shape{X} = \vec{l} \oplus \vec{r}$ where $\shape{\vec{l}} = l$ and $\shape{\vec{r}} = r$
-\[ \shape{\Tran(X, l)} = \vec{r} \oplus \vec{l} \]
+Let $\shape{X} = \vec{a} \oplus \vec{b}$ where $\shape{\vec{a}} = a$,
+\[ \shape{\transpose{X}{a}} = \vec{b} \oplus \vec{a} \]
 And,
-\[ \forall \bar{l} \in \Dim(\vec{l}), \bar{r} \in \Dim(\vec{r}) : \]
-\[ \Tran(X, l)[\bar{r} \oplus \bar{l}] = X[\bar{l} \oplus \bar{r}] \]
-We call $l$ the index of transpose.
+\[ \forall \bar{a} \in \Dim(\vec{a}), \bar{b} \in \Dim(\vec{b}) : \]
+\[ \transpose{X}{a}[\bar{b} \oplus \bar{a}] = X[\bar{a} \oplus \bar{b}] \]
+We call $a$ the index of transpose.
 \end{definition}
@@
 multimatrix:
-\[ \shape{\Tran(M, 1)} = \left<2,7,5,9,3\right> \]
+\[ \shape{\transpose{M}{1}} = \left<2,7,5,9,3\right> \]
 And... how about the third:
-\[ \shape{\Tran(M, 3)} = \left<5,9,3,2,7\right> \]
+\[ \shape{\transpose{M}{3}} = \left<5,9,3,2,7\right> \]
 You can see, it's as though I cut off the front of the shape vector and transferred
@@
 You do the same thing with indices. So,
-\[ M[1,2,3,4,5] = \Tran(M, 3)[4,5,1,2,3] \]
+\[ M[1,2,3,4,5] = \transpose{M}{3}[4,5,1,2,3] \]
 \end{example}
@@
 For any multimatrix, the following transposes are equivalent,
-\[ \Tran(X, n) = \Tran(X, \remainder(n, \shape{\shape{X}})) \]
+\[ \transpose{X}{n} = \transpose{X}{\remainder(n, \shape{\shape{X}})} \]
 Where $\remainder(n, \shape{\shape{X}})$ is the remainder of $n$ divided by $\shape{\shape{X}}$.
@@
 The exception, $l = \shape{\shape{X}}$ is covered by showing that
-$\remainder(\shape{\shape{X}}, \shape{\shape{X}}) = 0$ and $\Tran(X, 0) = \Tran(X, \shape{\shape{X}})$.
+$\remainder(\shape{\shape{X}}, \shape{\shape{X}}) = 0$ and $\transpose{X}{0} = \transpose{X}{\shape{\shape{X}}}$.
 
@@
 operations. On multimatrices with a shape of some length $n$ there are $n$ unique
-transpose; $\Tran(X, i)$ for all $0 \le i < n$. All other transposes are equivalent
+transpose; $\transpose{X}{i}$ for all $0 \le i < n$. All other transposes are equivalent
 to one of these base transposes by our extended definition.
@@
 So, let $A$ be a multimatrix with shape of length $n$. Now let $x$ and $y$
-be indices of transpositions. Then what is $\Tran(\Tran(A, x), y)$?
+be indices of transpositions. Then what is $\transpose{\transpose{A}{x}}{y}$?
 To apply the the first transpose we need to break $\shape{A}$ into two vectors,
@@
 Then,
-\[ \shape{\Tran(A, x)} = \vec{r} \oplus \vec{l} \]
+\[ \shape{\transpose{A}{x}} = \vec{r} \oplus \vec{l} \]
 And for all
 $\bar{l} \in \Dim(\vec{l})$ and $\bar{r} \in \Dim(\vec{r})$,
-\[ \Tran(A, x)[\bar{r} \oplus \bar{l}] = A[\bar{l} \oplus \bar{r}] \]
-
-Now to apply a transposition with index of transposition $y$ to $\Tran(A,x)$
-we need to break up $\shape{\Tran(A,x)}$ into two vector, such as
-$\shape{\Tran(A,x)} = \vec{l}' \oplus \vec{r}'$.
-
-Since we've already shown that $\shape{\Tran(A,x)} = \vec{r} \oplus \vec{l}$
+\[ \transpose{A}{x}[\bar{r} \oplus \bar{l}] = A[\bar{l} \oplus \bar{r}] \]
+
+Now to apply a transposition with index of transposition $y$ to $\transpose{A}{x}$
+we need to break up $\shape{\transpose{A}{x}}$ into two vector, such as
+$\shape{\transpose{A}{x}} = \vec{l}' \oplus \vec{r}'$.
+
+Since we've already shown that $\shape{\transpose{A}{x}} = \vec{r} \oplus \vec{l}$
 we end up with two conceptual splits of that shape vector that need to
@@
 
-Then we can divide $\shape{\Tran(A,x)}$ into three vectors, $\vec{a}$, $\vec{b}$, and $\vec{c}$
+Then we can divide $\shape{\transpose{A}{x}}$ into three vectors, $\vec{a}$, $\vec{b}$, and $\vec{c}$
 such that
-\[ \shape{\Tran(A,x)} = \vec{b} \oplus \vec{c} \oplus \vec{a} \]
+\[ \shape{\transpose{A}{x}} = \vec{b} \oplus \vec{c} \oplus \vec{a} \]
 \[ \vec{l}' = \vec{b} \]
@@
 And since,
-\[ \shape{\Tran(\Tran(A, x), y)} = \vec{r}' \oplus \vec{l}' \]
+\[ \shape{\transpose{\transpose{A}{x}}{y}} = \vec{r}' \oplus \vec{l}' \]
 It follows that,
-\[ \shape{\Tran(\Tran(A, x), y)} = \vec{c} \oplus \vec{a} \oplus \vec{b} \]
+\[ \shape{\transpose{\transpose{A}{x}}{y}} = \vec{c} \oplus \vec{a} \oplus \vec{b} \]
 
@@
 \begin{align*}
-  \Tran(\Tran(A, x), y)[\bar{c} \oplus \bar{a} \oplus \bar{b}]
-  &=
-  \Tran(A, x)[\bar{b} \oplus \bar{c} \oplus \bar{a}] \\
+  \transpose{\transpose{A}{x}}{y}[\bar{c} \oplus \bar{a} \oplus \bar{b}]
+  &=
+  \transpose{A}{x}[\bar{b} \oplus \bar{c} \oplus \bar{a}] \\
   &=
@@
 
-See now that this composite operation is also a transposition, $\Tran(A, z)$ where,
+See now that this composite operation is also a transposition, $\transpose{A}{z}$ where,
 $z = \shape{\vec{a} \oplus \vec{b}}$.
@@
 \begin{align*}
-  \shape{\Tran(A, z)}
+  \shape{\transpose{A}{z}}
   &=
@@
   &=
-  \shape{\Tran(\Tran(A, x), y)}  
+  \shape{\transpose{\transpose{A}{x}}{y}}  
 \end{align*}
@@
 \begin{align*}
-  \Tran(A, z)[\bar{c} \oplus \bar{a} \oplus \bar{b}]
+  \transpose{A}{z}[\bar{c} \oplus \bar{a} \oplus \bar{b}]
   &=
@@
   &=
-  \Tran(\Tran(A, x), y)[\bar{c} \oplus \bar{a} \oplus \bar{b}]
+  \transpose{\transpose{A}{x}}{y}[\bar{c} \oplus \bar{a} \oplus \bar{b}]
 \end{align*}
@@
 \begin{case} $\shape{\vec{l}'} > \shape{\vec{r}}$
-Then we can divide $\shape{\Tran(A,x)}$ into three vectors, $\vec{a}$, $\vec{b}$, and $\vec{c}$
+Then we can divide $\shape{\transpose{A}{x}}$ into three vectors, $\vec{a}$, $\vec{b}$, and $\vec{c}$
 such that
-\[ \shape{\Tran(A,x)} = \vec{c} \oplus \vec{a} \oplus \vec{b} \]
+\[ \shape{\transpose{A}{x}} = \vec{c} \oplus \vec{a} \oplus \vec{b} \]
 \[ \vec{l}' = \vec{c} \oplus \vec{a} \]
@@
 And since,
-\[ \shape{\Tran(\Tran(A, x), y)} = \vec{r}' \oplus \vec{l}' \]
+\[ \shape{\transpose{\transpose{A}{x}}{y}} = \vec{r}' \oplus \vec{l}' \]
 It follows that,
-\[ \shape{\Tran(\Tran(A, x), y)} = \vec{b} \oplus \vec{c} \oplus \vec{a} \]
+\[ \shape{\transpose{\transpose{A}{x}}{y}} = \vec{b} \oplus \vec{c} \oplus \vec{a} \]
 
@@
 \begin{align*}
-  \Tran(\Tran(A, x), y)[\bar{b} \oplus \bar{c} \oplus \bar{a}]
-  &=
-  \Tran(A, x)[\bar{c} \oplus \bar{a} \oplus \bar{b}] \\
+  \transpose{\transpose{A}{x}}{y}[\bar{b} \oplus \bar{c} \oplus \bar{a}]
+  &=
+  \transpose{A}{x}[\bar{c} \oplus \bar{a} \oplus \bar{b}] \\
   &=
@@
 
-See now that this composite operation is also a transposition, $\Tran(A, z)$ where,
+See now that this composite operation is also a transposition, $\transpose{A}{z}$ where,
 $z = \shape{\vec{a}}$.
@@
 \begin{align*}
-  \Tran(A, z)[\bar{b} \oplus \bar{c} \oplus \bar{a}]
+  \transpose{A}{z}[\bar{b} \oplus \bar{c} \oplus \bar{a}]
   &=
@@
   &=
-  \Tran(\Tran(A, x), y)[\bar{b} \oplus \bar{c} \oplus \bar{a}]
+  \transpose{\transpose{A}{x}}{y}[\bar{b} \oplus \bar{c} \oplus \bar{a}]
 \end{align*}
@@
 $\phi: \mathbb{T}_n \to \mathbb{Z}_n$ for which
-\[ \phi(\Tran_y \circ \Tran_x) = \phi(\Tran(y)) + \phi(\Tran(x)) \]
+\[ \phi(\Tran_y \circ \Tran_x) = \phi(\Tran_y) + \phi(\Tran_x) \]
 Which is the definition of an isomorphism.
@@
 where $\shape{\vec{l}} = x$. Then we'd say that
-\[ \shape{\Tran(A, x)} = \vec{r} \oplus \vec{l} \]
-Then to further apply $\Tran(\Tran(A, x), y)$ we need to divide $\shape{\Tran(A,x)}$
+\[ \shape{\transpose{A}{x}} = \vec{r} \oplus \vec{l} \]
+Then to further apply $\transpose{\transpose{A}{x}}{y}$ we need to divide $\shape{\transpose{A}{x}}$
 into,
-\[ \shape{\Tran(A, x)} = \vec{l}' \oplus \vec{r}' \]
+\[ \shape{\transpose{A}{x}} = \vec{l}' \oplus \vec{r}' \]
 Where $\shape{\vec{l}'} = y$.
@@
 So that,
-\[ \shape{\Tran(A, x)} = \vec{b} \oplus \vec{c} \oplus \vec{a} \]
-\[ \shape{\Tran(\Tran(A, x), y)} = \vec{c} \oplus \vec{a} \oplus \vec{b} \]
+\[ \shape{\transpose{A}{x}} = \vec{b} \oplus \vec{c} \oplus \vec{a} \]
+\[ \shape{\transpose{\transpose{A}{x}}{y}} = \vec{c} \oplus \vec{a} \oplus \vec{b} \]
 And note that,
@@
 So that,
-\[ \shape{\Tran(A, x)} = \vec{c} \oplus \vec{a} \oplus \vec{b} \]
-\[ \shape{\Tran(\Tran(A, x), y)} = \vec{b} \oplus \vec{c} \oplus \vec{a} \]
+\[ \shape{\transpose{A}{x}} = \vec{c} \oplus \vec{a} \oplus \vec{b} \]
+\[ \shape{\transpose{\transpose{A}{x}}{y}} = \vec{b} \oplus \vec{c} \oplus \vec{a} \]
 And note that,
@@
 in other words), it is always true that
-\[ \Tran(\Tran(A, x),y) = \Tran(A, \remainder(x+y,n)) \]
+\[ \transpose{\transpose{A}{x}}{y} = \transpose{A}{\remainder(x+y,n)} \]
 \end{corollary}
@@
 Then see that,
-\[ \shape{\Tran(A, 2)} = \left<7, 5, 11, 3\right> \]
+\[ \shape{\transpose{A}{2}} = \left<7, 5, 11, 3\right> \]
 And applying another transpose,
-\[ \shape{\Tran(\Tran(A, 2), 3)} = \left<3, 7, 5, 11\right> \]
+\[ \shape{\transpose{\transpose{A}{2}}{3}} = \left<3, 7, 5, 11\right> \]
 Notice that our corollary says that this double transpose should be
-equal to the transpose $\Tran(A, \remainder(2+3, 4))$ which would
-be $\Tran(A, 1)$ and indeed it is:
-\begin{align*}
-  \shape{\Tran(A, 1)}
+equal to the transpose $\transpose{A}{\remainder(2+3, 4)}$ which would
+be $\transpose{A}{1}$ and indeed it is:
+\begin{align*}
+  \shape{\transpose{A}{1}}
   &= \left<3, 7, 5, 11\right> \\
-  &= \shape{\Tran(\Tran(A, 2), 3)}
+  &= \shape{\transpose{\transpose{A}{2}}{3}}
 \end{align*}
@@
 $\Tran_{-x}$. That is,
-\[ \Tran(\Tran(A, x), -x) = X \]
+\[ \transpose{\transpose{A}{x}}{-x} = X \]
 \end{corollary}
@@
 Let's apply a transpose to it, $\Tran_3$, and we'll get the shape,
-\[ \shape{\Tran(A, 3)} = \left<8,3,2,7,1\right> \]
+\[ \shape{\transpose{A}{3}} = \left<8,3,2,7,1\right> \]
 Now, to get back to $A$ we can apply another transpose $\Tran_{-3}$ according
@@
 \begin{align*}
-  \shape{\Tran(\Tran(A, 3), 2)}
+  \shape{\transpose{\transpose{A}{3}}{2}}
   &= \left<2,7,1,8,3\right> \\
@@
 shape vector. Then for any integer $k$,
-\[ \Tran(\Ident^n(\vec{x}), k\shape{\vec{x}}) = \Ident^n(\vec{x}) \]
+\[ \transpose{\Ident^n(\vec{x})}{k\shape{\vec{x}}} = \Ident^n(\vec{x}) \]
 \end{theorem}
@@
 \begin{align*}
-  \Tran(\Ident^n(\vec{x}), k\shape{\vec{x}})\left[\bigoplus X'\right]
+  \transpose{\Ident^n(\vec{x})}{k\shape{\vec{x}}}\left[\bigoplus X'\right]
 	&=
@@
 Therefore
-$\Tran(\Ident^n(\vec{x}), k\shape{\vec{x}}) = \Ident^n(\vec{x})$
+$\transpose{\Ident^n(\vec{x})}{k\shape{\vec{x}}} = \Ident^n(\vec{x})$
 \end{proof}
@@
 \label{mm_tran_mult}
-Let $\shape{A} = \vec{a} \oplus \vec{c}$ and $\shape{B} = \vec{c} \oplus \vec{b}$ then
-\[
- \Tran(A \mmult{\shape{\vec{c}}} B, \shape{\vec{a}})
- =  \Tran(B, \shape{\vec{c}}) \mmult{\shape{\vec{c}}} \Tran(A, \shape{\vec{a}})
+Let $\shape{A} = \vec{a} \oplus \vec{c}$ and $\shape{B} = \vec{c} \oplus \vec{b}$ and let,
+$\shape{\vec{a}} = a$, and $\shape{\vec{c}} = c$, then
+\[
+ \transpose{\left(A \mmult{c} B\right)}{a}
+ =  \transpose{B}{c} \mmult{c} \transpose{A}{a}
 \]
@@
 \begin{align*}
-	\Tran(A \mmult{\shape{\vec{c}}} B, \shape{\vec{a}})[\bar{b} \oplus \bar{a}]
+	\transpose{\left(A \mmult{c} B\right)}{a}[\bar{b} \oplus \bar{a}]
 	&=
@@
 	\sum_{\forall \bar{c} \in \Dim(\vec{c})}
-	\Tran(B, \shape{\vec{c}})[\bar{b} \oplus \bar{c}]
-	\Tran(A, \shape{\vec{a}})[\bar{c} \oplus \bar{a}] \\
-	&=
-	\left(\Tran(B, \shape{\vec{c}}) \mmult{\shape{\vec{c}}} \Tran(A, \shape{\vec{a}}) \right)
+	\transpose{B}{c}[\bar{b} \oplus \bar{c}]
+	\transpose{A}{a}[\bar{c} \oplus \bar{a}] \\
+	&=
+	\left(\transpose{B}{c} \mmult{c} \transpose{A}{a}\right)
 	[\bar{b} \oplus \bar{a}]
@@
 Let $s$ be a scalar, $x$ be in $\mathbb{N} \cup \{0\}$, and $A$ be
-a multimatrix on which $\Tran(A, x)$ is defined. Then,
-\[ s\Tran(A, x) = \Tran(sA, x) \]
+a multimatrix on which $\transpose{A}{x}$ is defined. Then,
+\[ s\left(\transpose{A}{x}\right) = \transpose{(sA)}{x} \]
 \end{theorem}
@@
 \begin{align*}
-  (s\Tran(A, x))[\bar{a} \oplus \bar{x}]
-  &= s \Tran(A, x)[\bar{a} \oplus \bar{x}] \\
+  \left(s\left(\transpose{A}{x}\right)\right)[\bar{a} \oplus \bar{x}]
+  &= s \left(\transpose{A}{x}\right)[\bar{a} \oplus \bar{x}] \\
   &= s A[\bar{x} \oplus \bar{a}] \\
   &= (s A)[\bar{x} \oplus \bar{a}] \\
-  &= \Tran(sA, x)[\bar{a} \oplus \bar{x}]
-\end{align*}
-Therefore $s\Tran(A, x) = \Tran(sA, x)$.
+  &= \transpose{(sA)}{x}[\bar{a} \oplus \bar{x}]
+\end{align*}
+Therefore $s\left(\transpose{A}{x}\right) = \transpose{(sA)}{x}$.
 \end{proof}
@@
 Let $x$ be in $\mathbb{N} \cup \{0\}$ and let $A$ and $B$ be
-multimatrices such that $\shape{A} = \shape{B}$ and $\Tran(A, x)$ is defined.
+multimatrices such that $\shape{A} = \shape{B}$ and $\transpose{A}{x}$ is defined.
 Then,
-\[ \Tran(A, x) + \Tran(B, x) = \Tran(A+B, x) \]
+\[ \transpose{A}{x} + \transpose{B}{x} = \transpose{(A+B)}{x} \]
 \end{theorem}
@@
 Prove Theorem \ref{com_add_tran_thm} which is that,
-\[ \Tran(A, x) + \Tran(B, x) = \Tran(A+B, x) \]
+\[ \transpose{A}{x} + \transpose{B}{x} = \transpose{(A+B)}{x} \]
 \end{exercise}
@@
 \begin{exercise}
-Let $A$ be a multimatrix such that $\shape{A} = <1,2,3,4,5>$,
+Let $A$ be a multimatrix such that $\shape{A} = \left<1,2,3,4,5\right>$,
 Find the shape of the following transposes:
 \begin{enumerate}
-\item $\shape{\Tran(A, 3)} = ?$
-\item $\shape{\Tran(A, 4)} = ?$
-\item $\shape{\Tran(A, 5)} = ?$
-\item $\shape{\Tran(A, 0)} = ?$
+\item $\shape{\transpose{A}{3}} = ?$
+\item $\shape{\transpose{A}{4}} = ?$
+\item $\shape{\transpose{A}{5}} = ?$
+\item $\shape{\transpose{A}{0}} = ?$
 \end{enumerate}
@@
 Find the value, in terms of $M$, of the following equations.
-For example $\Tran(M, 1)[2,3,4,5,1] = M[1,2,3,4,5]$
+For example $\transpose{M}{1}[2,3,4,5,1] = M[1,2,3,4,5]$
 \begin{enumerate}
-\item $\Tran(M, 3)[1,2,3,4] = ?$
-\item $\Tran(M, 0)[6,5,3] = ?$
-\item $\Tran(M, 2)[1,1,1] = ?$
+\item $\transpose{M}{3}[1,2,3,4] = ?$
+\item $\transpose{M}{0}[6,5,3] = ?$
+\item $\transpose{M}{2}[1,1,1] = ?$
 \end{enumerate}
@@
 \label{tran_derivative}
-$\shape{X} = \vec{l} \oplus \vec{r}$
-\[
- \frac{d\Tran(X, \shape{\vec{l}})}{dX} =
- \Tran(\Ident^2(\vec{r}) \mmult{0} \Ident^2(\vec{l}), \shape{\vec{r}})
+Let $\shape{X} = \vec{l} \oplus \vec{r}$ with $\shape{\vec{l}} = l$ and $\shape{\vec{r}} = r$ then,
+\[
+ \frac{d\transpose{X}{l}}{dX} =
+ \transpose{\left(\Ident^2(\vec{r}) \mmult{0} \Ident^2(\vec{l})\right)}{r}
 \]
@@
 \begin{proof}
-\begin{align*}
- \frac{d\Tran(X, \shape{\vec{l}})}{dX}
- [\bar{r_1} \oplus \bar{l_1} \oplus \bar{l_2} \oplus \bar{r_2}]
- &= \delta_{\bar{r_1}\bar{r_2}} \delta_{\bar{l_1}\bar{l_2}} \\
- &= \delta_{\bar{r_2}\bar{r_1}} \delta_{\bar{l_1}\bar{l_2}} \\
- &=
-  \Ident^2(\shape{\vec{r}})[\bar{r_2}\oplus\bar{r_1}]
-  \Ident^2(\shape{\vec{l}})[\bar{l_1}\oplus\bar{l_2}] \\
+Let $\shape{X} = \vec{l} \oplus \vec{r}$ with $\shape{\vec{l}} = l$ and $\shape{\vec{r}} = r$.
+Then for all $\bar{r}_1, \bar{r}_2 \in \Dim(\vec{\vec{r}})$ and $\bar{l}_1, \bar{l}_2 \in \Dim(\vec{\vec{l}})$,
+\begin{align*}
+ \frac{d\transpose{X}{l}}{dX}
+ [\bar{r}_1 \oplus \bar{l}_1 \oplus \bar{l}_2 \oplus \bar{r}_2]
+ &= \delta_{\bar{r}_1\bar{r}_2} \delta_{\bar{l}_1\bar{l}_2} \\
+ &= \delta_{\bar{r}_2\bar{r}_1} \delta_{\bar{l}_1\bar{l}_2} \\
+ &=
+  \Ident^2(\vec{r})[\bar{r_2}\oplus\bar{r_1}]
+  \Ident^2(\vec{l})[\bar{l_1}\oplus\bar{l_2}] \\
  &=
    \left(
-    \Ident^2(\shape{\vec{r}})
+    \Ident^2(\vec{r})
     \mmult{0}
-    \Ident^2(\shape{\vec{l}})
+    \Ident^2(\vec{l})
   \right)
-  [\bar{r_2}\oplus\bar{r_1}\oplus\bar{l_1}\oplus\bar{l_2}] \\
- &=
-  \Tran(
-    \Ident^2(\shape{\vec{r}})
+  [\bar{r}_2 \oplus \bar{r}_1 \oplus \bar{l}_1 \oplus \bar{l}_2] \\
+ &=
+  \transpose{\left(
+    \Ident^2(\vec{r})
     \mmult{0}
-    \Ident^2(\shape{\vec{l}})
-  , \shape{\vec{r}}) 
+    \Ident^2(\vec{l})
+  \right)}{r}
   [\bar{r_1} \oplus \bar{l_1} \oplus \bar{l_2} \oplus \bar{r_2}]
@@
 and $n = \shape{\vec{n}}$ and $a = \shape{\vec{a}}$ then,
-\[ \frac{d(X \mmult{n} A)}{dX} = \Ident^2(\shape{X \mmult{n} A}) \mmult{a} \Tran(A, n) \]
+\[ \frac{d(X \mmult{n} A)}{dX} = \Ident^2(\shape{X \mmult{n} A}) \mmult{a} \transpose{A}{n} \]
 \end{theorem}
@@
 \begin{align*}
-	\left(\Ident^2(\shape{X \mmult{n} A}) \mmult{a} \Tran(A, n)\right)
+	\left(\Ident^2(\shape{X \mmult{n} A}) \mmult{a} \transpose{A}{n}\right)
 	[\bar{x}_1 \oplus \bar{a}_1 \oplus \bar{x}_2 \oplus \bar{n}_1]
@@
 	\Ident^2(\shape{X \mmult{n} A})[\bar{x}_1 \oplus \bar{a}_1 \oplus \bar{x}_2 \oplus \bar{a}_2]
-	\Tran(A, n)[\bar{a}_2 \oplus \bar{n}_1] \\
+	\transpose{A}{n}[\bar{a}_2 \oplus \bar{n}_1] \\
 	&=
@@
 	\delta_{\bar{x}_1 \bar{x}_2} \delta_{\bar{a}_1 \bar{a}_2}
-	\Tran(A, n)[\bar{a}_2 \oplus \bar{n}_1] \\
+	\transpose{A}{n}[\bar{a}_2 \oplus \bar{n}_1] \\
 	&=
@@
 	=
-	\left(\Ident^2(\shape{X \mmult{n} A}) \mmult{a} \Tran(A, n)\right)
+	\left(\Ident^2(\shape{X \mmult{n} A}) \mmult{a} \transpose{A}{n}\right)
 	[\bar{x}_1 \oplus \bar{a}_1 \oplus \bar{x}_2 \oplus \bar{n}_1]
@@
 	=
-	\Ident^2(\shape{X \mmult{n} A}) \mmult{a} \Tran(A, n)
+	\Ident^2(\shape{X \mmult{n} A}) \mmult{a} \transpose{A}{n}
 \]
@@
 Let $\shape{F} = \vec{f} \oplus \vec{c}$, $\shape{G} = \vec{c} \oplus \vec{g}$,
-and $\shape{X} = \vec{x}$. Then,
-\begin{align*}
- \frac{d\left(F(X) \mmult{\shape{\vec{c}}} G(X)\right)}{dX} =
- F(X) \mmult{\shape{\vec{c}}} \frac{dG(X)}{dX} +
- \Tran\left(
-   \Tran(G(X), \shape{\vec{c}})
-     \mmult{\shape{\vec{c}}}
-   \Tran\left(\frac{dF(X)}{dX}, \shape{\vec{f}}\right),
-   \shape{\vec{g} \oplus \vec{x}}
- \right)
+and $\shape{X} = \vec{x}$.
+Also let $\shape{\vec{f}} = f$, $\shape{\vec{c}} = c$ and $\shape{\vec{g}} = g$.
+Then,
+\begin{align*}
+  \frac{d\left(F(X) \mmult{c} G(X)\right)}{dX} =
+  F(X) \mmult{c} \frac{dG(X)}{dX} +
+  \transpose{\left(
+     \transpose{G(X)}{c}
+       \mmult{c}
+     \transpose{\left( \frac{dF(X)}{dX} \right)}{f}
+  \right)}
+  {g+x}
 \end{align*}
@@
 \begin{align*}
- \frac{d\left(F(X) \mmult{\shape{\vec{c}}} G(X)\right)}{dX}
+ \frac{d\left(F(X) \mmult{c} G(X)\right)}{dX}
   [\bar{f} \oplus \bar{g} \oplus \bar{x}]
  &= \frac{
-       \partial \left(F(X) \mmult{\shape{\vec{c}}} G(X)\right)[\bar{f} \oplus \bar{g}]
+       \partial \left(F(X) \mmult{c} G(X)\right)[\bar{f} \oplus \bar{g}]
     }{
@@
  &=
-   \left( F(X) \mmult{\shape{\vec{c}}} \frac{dG(X)}{dX} \right)
+   \left( F(X) \mmult{c} \frac{dG(X)}{dX} \right)
    [\bar{f} \oplus \bar{g} \oplus \bar{x}]
@@
   \sum_{\forall \bar{c}}
-    \Tran\left(\frac{dF(X)}{dX}, \shape{\vec{f}}\right)
+    \transpose{\left(\frac{dF(X)}{dX}\right)}{f}
       [\bar{c} \oplus \bar{x} \oplus \bar{f}]
-    \Tran(G(X), \shape{\vec{c}})[\bar{g} \oplus \bar{c}] \\
+    \transpose{G(X)}{c}[\bar{g} \oplus \bar{c}] \\
  &=
   \sum_{\forall \bar{c}}
-    \Tran(G(X), \shape{\vec{c}})[\bar{g} \oplus \bar{c}]
-    \Tran\left(\frac{dF(X)}{dX}, \shape{\vec{f}}\right)
+    \transpose{G(X)}{c}[\bar{g} \oplus \bar{c}]
+    \transpose{\left(\frac{dF(X)}{dX}\right)}{f}
       [\bar{c} \oplus \bar{x} \oplus \bar{f}] \\
@@
   \left(
-    \Tran(G(X), \shape{\vec{c}}) \mmult{\shape{\vec{c}}}
-    \Tran\left(\frac{dF(X)}{dX}, \shape{\vec{f}}\right)
+    \transpose{G(X)}{c} \mmult{c}
+    \transpose{\left(\frac{dF(X)}{dX}\right)}{f}
   \right)[\bar{g} \oplus \bar{x} \oplus \bar{f}] \\
  &= 
-  \Tran\left(
-    \Tran(G(X), \shape{\vec{c}}) \mmult{\shape{\vec{c}}}
-    \Tran\left(\frac{dF(X)}{dX}, \shape{\vec{f}}\right)
-    , \shape{\vec{g} \oplus \vec{x}}
-  \right)[\bar{f} \oplus \bar{g} \oplus \bar{x}]
+  \transpose{\left(
+    \transpose{G(X)}{c} \mmult{c}
+    \transpose{\left(\frac{dF(X)}{dX}\right)}{f}
+  \right)}{g+x}
+  [\bar{f} \oplus \bar{g} \oplus \bar{x}]
 \end{align*}
@@
 \begin{alignat*}{3}
- \frac{d\left(F(X) \mmult{\shape{\vec{c}}} G(X)\right)}{dX}
+ \frac{d\left(F(X) \mmult{c} G(X)\right)}{dX}
   [\bar{f} \oplus \bar{g} \oplus \bar{x}]
   &=&&
-  \left( F(X) \mmult{\shape{\vec{c}}} \frac{dG(X)}{dX} \right)
+  \left( F(X) \mmult{c} \frac{dG(X)}{dX} \right)
   [\bar{f} \oplus \bar{g} \oplus \bar{x}] \\
   &&&+
-  \Tran\left(
-    \Tran(G(X), \shape{\vec{c}}) \mmult{\shape{\vec{c}}}
-    \Tran\left(\frac{dF(X)}{dX}, \shape{\vec{f}}\right)
-    , \shape{\vec{g} \oplus \vec{x}}
-  \right)[\bar{f} \oplus \bar{g} \oplus \bar{x}] \\
+  \transpose{\left(
+    \transpose{G(X)}{c} \mmult{c}
+    \transpose{\left(\frac{dF(X)}{dX}\right)}{f}
+  \right)}{g+x}
+  [\bar{f} \oplus \bar{g} \oplus \bar{x}] \\
   &=&&
@@
     \begin{array}{l}
-      \left( F(X) \mmult{\shape{\vec{c}}} \frac{dG(X)}{dX} \right) \\
+      \left( F(X) \mmult{c} \frac{dG(X)}{dX} \right) \\
       +
-      \Tran\left(
-        \Tran(G(X), \shape{\vec{c}}) \mmult{\shape{\vec{c}}}
-        \Tran\left(\frac{dF(X)}{dX}, \shape{\vec{f}}\right)
-        , \shape{\vec{g} \oplus \vec{x}}
-      \right)
+      \transpose{\left(
+        \transpose{G(X)}{c} \mmult{c}
+        \transpose{\left(\frac{dF(X)}{dX}\right)}{f}
+      \right)}{g+x}
     \end{array}
@@
 Let $F(X)$ and $G(X)$ be functions of $X$ where
-$\shape{F(X)} = \vec{a} \oplus \vec{c}$ and $\shape{G(X)} = \vec{c} \oplus \vec{b}$
-then,
-\[
-  \frac{d(F(X) \dmult{\shape{\vec{c}}} G(X))}{dX} =
-    F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX} +
-    \Tran\left(\Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right) \dmult{\shape{\vec{c}}} G(X), \shape{\shape{X}}\right)
+$\shape{F(X)} = \vec{a} \oplus \vec{c}$ and $\shape{G(X)} = \vec{c} \oplus \vec{b}$.
+And let $\shape{\shape{X}} = x$, $\shape{\shape{F(X)}} = f$, and $\shape{\vec{c}} = c$.
+Then,
+\[
+  \frac{d(F(X) \dmult{c} G(X))}{dX} =
+    F(X) \dmult{c} \frac{dG}{dX} +
+    \transpose{\left(\transpose{\left(\frac{dF}{dX}\right)}{f} \dmult{c} G(X)\right)}{x}
 \]
@@
 \begin{align*}
-\frac{d(F(X) \dmult{\shape{\vec{c}}} G(X))}{dX}[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
-  &= \frac{\partial (F(X) \dmult{\shape{\vec{c}}} G(X))[\bar{a} \oplus \bar{c} \oplus \bar{b}]}{\partial X[\bar{x}]} \\
+\frac{d(F(X) \dmult{c} G(X))}{dX}[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
+  &= \frac{\partial (F(X) \dmult{c} G(X))[\bar{a} \oplus \bar{c} \oplus \bar{b}]}{\partial X[\bar{x}]} \\
   &= \frac{\partial (F(X)[\bar{a} \oplus \bar{c}] G(X)[\bar{c} \oplus \bar{a}])}{\partial X[\bar{x}]} \\
@@
   &= \frac{dF}{dX}[\bar{a} \oplus \bar{c} \oplus \bar{x}] G(X)[\bar{c} \oplus \bar{b}]
-    + \left(F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
-  &= \Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right)[\bar{x} \oplus \bar{a} \oplus \bar{c}] G(X)[\bar{c} \oplus \bar{b}]
-    + \left(F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
-  &= \left(\Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right) \dmult{\shape{\vec{c}}} G(X)\right) [\bar{x} \oplus \bar{a} \oplus \bar{c} \oplus \bar{b}]
-    + \left(F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
-  &= \Tran\left(\Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right) \dmult{\shape{\vec{c}}} G(X), \shape{\shape{X}}\right) [\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
-    + \left(F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
-  &= \left(F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
-    + \Tran\left(\Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right) \dmult{\shape{\vec{c}}} G(X), \shape{\shape{X}}\right) [\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
-  &= \left\{ F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}
-    + \Tran\left(\Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right) \dmult{\shape{\vec{c}}} G(X), \shape{\shape{X}}\right) \right\}[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
+    + \left(F(X) \dmult{c} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
+  &= \transpose{\left(\frac{dF}{dX}\right)}{f}[\bar{x} \oplus \bar{a} \oplus \bar{c}] G(X)[\bar{c} \oplus \bar{b}]
+    + \left(F(X) \dmult{c} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
+  &= \left(\transpose{\left(\frac{dF}{dX}\right)}{f} \dmult{c} G(X)\right) [\bar{x} \oplus \bar{a} \oplus \bar{c} \oplus \bar{b}]
+    + \left(F(X) \dmult{c} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
+  &= \transpose{\left(\transpose{\left(\frac{dF}{dX}\right)}{f} \dmult{c} G(X)\right)}{x}[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
+    + \left(F(X) \dmult{c} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
+  &= \left(F(X) \dmult{c} \frac{dG}{dX}\right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
+    + \transpose{\left(\transpose{\left(\frac{dF}{dX}\right)}{f} \dmult{c} G(X)\right)}{x} [\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}] \\
+  &= \left( F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX}
+    + \transpose{\left(\transpose{\left(\frac{dF}{dX}\right)}{f} \dmult{c} G(X)\right)}{x} \right)[\bar{a} \oplus \bar{c} \oplus \bar{b} \oplus \bar{x}]
 \end{align*}
@@
   X \mmult{\shape{\vec{x}}} \frac{dX}{dX} +
-  \Tran\left(
-    \Tran(X, \shape{\vec{x}})
+  \transpose{\left(
+    \transpose{X}{\shape{\vec{x}}}
       \mmult{\shape{\vec{x}}}
-    \Tran\left(\frac{dX}{dX}, \shape{\vec{x}}\right),
-    \shape{\vec{x} \oplus \vec{x}}
-  \right) \\
+    \transpose{\left(\frac{dX}{dX}\right)}{\shape{\vec{x}}}
+  \right)}{\shape{\vec{x} \oplus \vec{x}}} \\
   &=
   X \mmult{\shape{\vec{x}}} \Ident^2(\shape{X}) +
-  \Tran\left(
+  \transpose{\left(
     X
       \mmult{\shape{\vec{x}}}
-    \Tran\left(\Ident^2(\shape{X}), \shape{\vec{x}}\right),
-    \shape{\vec{x} \oplus \vec{x}}
-  \right) \\
+    \transpose{\Ident^2(\shape{X})}{\shape{\vec{x}}}
+  \right)}{\shape{\vec{x} \oplus \vec{x}}} \\
   &=
   X +
-  \Tran\left(
+  \transpose{\left(
     X
       \mmult{\shape{\vec{x}}}
-    \Ident^2(\shape{X}),
-    \shape{\vec{x} \oplus \vec{x}}
-  \right) \\
+    \Ident^2(\shape{X})
+  \right)}{\shape{\vec{x} \oplus \vec{x}}} \\
   &=
   X +
-  \Tran\left(
-    X,
-    \shape{\vec{x} \oplus \vec{x}}
-  \right) \\
+  \transpose{X}{\shape{\vec{x} \oplus \vec{x}}} \\
   &= X + X \\
@@
 	\nonumber\\&&&+
-	\Tran\left(
-		\Tran\left(
+	\transpose{\left(
+		\transpose{\left(
 			\left( \Sum(\exp(X)) \right)^{-1}
-			,0
-		\right)
+    \right)}{0}
 		\mmult{0}
-		\Tran\left(
+		\transpose{\left(
 			\frac{d \exp(X)}{dX}
-			,\shape{\vec{x}}
-		\right)
-		,\shape{\left<\right> \oplus \vec{x}}
-	\right) \\
+    \right)}{
+		  \shape{\vec{x}}
+    }
+  \right)}{
+	  \shape{\left<\right> \oplus \vec{x}}
+	} \\
 	&=&&
@@
 	\nonumber\\&&&+
-	\Tran\left(
+	\transpose{\left(
 		\left( \Sum(\exp(X)) \right)^{-1}
 		\mmult{0}
-		\Tran\left(
+		\transpose{\left(
 			\frac{d \exp(X)}{dX}
-			,\shape{\vec{x}}
-		\right)
-		,\shape{\vec{x}}
-	\right) \\
+    \right)}{
+			\shape{\vec{x}}
+	  }
+  \right)}{
+		\shape{\vec{x}}
+	}  \\
 	&=&&
@@
 	\nonumber\\&&&+
-	\Tran\left(
+	\transpose{\left(
 		\left( \Sum(\exp(X)) \right)^{-1}
 		\mmult{0}
-		\Tran\left(
+		\transpose{\left(
 			\Ident^3(\shape{X}) \mmult{\shape{\shape{X}}} \exp(X)
-			,\shape{\vec{x}}
-		\right)
-		,\shape{\vec{x}}
-	\right) \\
+    \right)}{
+			\shape{\vec{x}}
+		}
+  \right)}{
+		\shape{\vec{x}}
+	} \\
 	&=&&
@@
 	\nonumber\\&&&+
-	\Tran\left(
-		\Tran\left(
+	\transpose{\left(
+		\transpose{\left(
 			\left( \Sum(\exp(X)) \right)^{-1}
@@
 			\Ident^3(\shape{X}) \mmult{\shape{\shape{X}}} \exp(X)
-		,\shape{\vec{x}}
-		\right)
-		,\shape{\vec{x}}
-	\right) \\
+    \right)}{
+		  \shape{\vec{x}}
+	  }	
+  \right)}{
+		\shape{\vec{x}}
+	} \\
 	&=&&
@@
 	\nonumber\\&&&+
-	\Tran\left(
-		\Tran\left(
+	\transpose{\left(
+		\transpose{\left(
 			\Ident^3(\shape{X}) \mmult{\shape{\shape{X}}} \Softmax(X)
-		,\shape{\vec{x}}
-		\right)
-	,\shape{\vec{x}}
-	\right) \\
+    \right)}{
+		  \shape{\vec{x}}
+		}
+  \right)}{
+	  \shape{\vec{x}}
+	} \\
 	&=&&
@@
 	+
-	\Tran\left(
+	\transpose{\left(
 		\Ident^3(\shape{X}) \mmult{\shape{\shape{X}}} \Softmax(X)
-		,2\shape{\vec{x}}
-	\right) \\
+  \right)}{
+		2\shape{\vec{x}}
+	} \\
 	&=&&
@@
     \mmult{\shape{\shape{L_i}}}
-    \Tran(W_i, \shape{\shape{L_{i-1}}})
+    \transpose{W_i}{\shape{\shape{L_{i-1}}}}
     \mmult{\shape{\shape{L_{i-1}}}}
@@
         \mmult{\shape{\shape{W_i}}-\shape{\shape{L_{i-1}}}}
-        \Tran(W_i, \shape{\shape{L_{i-1}}})
+        \transpose{W_i}{\shape{\shape{L_{i-1}}}}
       \right)
@@
         \mmult{\shape{\shape{L_i}}}
-        \Tran(W_i, \shape{\shape{L_{i-1}}})
+        \transpose{W_i}{\shape{\shape{L_{i-1}}}}
       \right)
@@
     \left(
-      \Tran(W_i, \shape{\shape{L_{i-1}}})
+      \transpose{W_i}{\shape{\shape{L_{i-1}}}}
       \mmult{\shape{\shape{L_{i-1}}}}
@@
 
-\end{landscape}
-
-\begin{theorem}[Bla]
-For any natural number $m$ where $m < n$,
-if and only if $C$ is a multimatrix for which $C \mmult{m} \left(A \mconcat{n} B\right)$ is valid then,
-\[ C \mmult{m} \left(A \mconcat{n} B\right) = \left(C \mmult{m} A\right) \mconcat{\shape{\shape{C}}+n-2m} \left(C \mmult{m} B\right) \]
-
-And if $m \le \shape{\shape{A}}-n$
-then if and only if  $C$ is a multimatrix for which $\left(A \mconcat{n} B\right) \mmult{m} C$ is valid then,
+\begin{theorem}[Multiplication Over Concatenation Rule 3]
+Let $A$, $B$, and $C$ be multimatrices, and let $m$ and $n$ be
+natural numbers where $0 < m \le \shape{\shape{A}}-n$. 
+If either of the following computations  is valid, then it is equivalent to the other:
 \[ \left(A \mconcat{n} B\right) \mmult{m} C = \left(A \mmult{m} C\right) \mconcat{n} \left(B \mmult{m} C\right) \]
-
-And when $m \ge n$, if and only if $C$ is a multimatrix for which $C \mmult{m} \left(A \mconcat{n} B\right)$ is valid,
-then for the multimatrices $C_1$ and $C_2$ defined by,
-\[ \Part(C, \shape{\shape{C}}-m+n, \shape{A}[n]) = \{C_1, C_2\} \]
-\[
-  C \mmult{m} \left(A \mconcat{n} B\right)
-  =
-  \left( C_1 \mmult{m} A \right) + 
-  \left( C_1 \mmult{m} B \right)
-\]
-
-Lastly, when $m > \shape{\shape{A}}-n$, if and only if $C$ is a multimatrix for which $\left(A \mconcat{n} B\right) \mmult{m} C$ is valid,
-then for multimatrices $C_1$ and $C_2$ defined by,
-\[ \Part(C, m+n-\shape{\shape{A}}+1, \shape{A}[n]) = \{C_1, C_2\} \]
+\end{theorem}
+
+\begin{theorem}[Multiplication Over Concatenation Rule 4]
+Let $A$, $B$, and $C$ be multimatrices, and let $m$ and $n$ be
+natural numbers where $0 < \shape{\shape{A}}-n < m$. 
+If either of the following computations is valid, then it is equivalent to the other:
 \[
@@
   \left( A \mmult{m} C_1 \right) + 
-  \left( B \mmult{m} C_1 \right)
-\]
+  \left( B \mmult{m} C_2 \right)
+\]
+\[ \Part(C, m+n-\shape{\shape{A}}+1, \shape{A}[n]) = \left\{ C_1, C_2 \right\} \]
 \end{theorem}
-\begin{proof}
-\begin{ppart}
-Let $A$ and $B$ be multimatrices where $A \mconcat{n} B$ is valid. 
-Let $m$ be a natural number where $m < n$, and let $C$ be a multimatrix where
-$C \mmult{m} \left(A \mconcat{n} B\right)$ is valid.
-
-Since $A \mconcat{n} B$ is valid, we can describe the shapes of $A$ and $B$ thus,
-\[ \shape{A} = \vec{l} \oplus \left<a\right> \oplus \vec{r} \]
-\[ \shape{B} = \vec{l} \oplus \left<b\right> \oplus \vec{r} \]
-Where $a$ and $b$ are both natural numbers, $\shape{\vec{l}} = n-1$, and
-$\shape{\vec{r}} = \shape{\shape{A}} - n$. So,
-\[ \shape{A \mconcat{n} B} = \vec{l} \oplus \left<a+b\right> \oplus \vec{r} \]
-
-Now, because $C \mmult{m} \left(A \mconcat{n} B\right)$ is valid, we know that
-there is some division in the shape of $C$ such that,
-\[ \shape{C} = \vec{c} \oplus \vec{m} \]
-For some shape vectors $\vec{c}$ and $\vec{m}$ where $\shape{\vec{m}} = m$ and
-$\shape{\vec{c}} = \shape{\shape{C}}-m$
-We also know that there exists some similar subdivision of $\shape{A \mconcat{n} B}$.
-\[ \shape{A \mconcat{n} B} = \vec{m} \oplus \vec{d} \]
-For some $\vec{d}$. Therefore,
-\[ \vec{m} \oplus \vec{d} = \vec{l} \oplus \left<a + b\right> \oplus \vec{r} \]
-
-Since $m < n$, $\shape{\vec{m}} \le \shape{\vec{l}}$ so $\vec{l}$ can be subdivided
-into,
-\[ \vec{l} = \vec{m} \oplus \vec{e} \]
-For some shape vector $\vec{e}$ where $\shape{\vec{e}} = n-1-m$.
-
-So,
-\[ \shape{A \mconcat{n} B} = \vec{m} \oplus \vec{e} \oplus \left<a+b\right> \oplus \vec{r} \]
-\[ \shape{A} = \vec{m} \oplus \vec{e} \oplus \left<a\right> \oplus \vec{r} \]
-\[ \shape{B} = \vec{m} \oplus \vec{e} \oplus \left<b\right> \oplus \vec{r} \]
-
-Therefore $C \mmult{m} A$ and $C \mmult{m} B$ are both valid operations and,
-\[ \shape{C \mmult{m} A} = \vec{c} \oplus \vec{e} \oplus \left<a\right> \oplus \vec{r} \]
-\[ \shape{C \mmult{m} B} = \vec{c} \oplus \vec{e} \oplus \left<b\right> \oplus \vec{r} \]
-
-Which shows that $(C \mmult{m} A) \mconcat{\shape{\vec{c} \oplus \vec{e}}+1} (C \mmult{m} B)$
-is also valid.
-\[
-  (C \mmult{m} A) \mconcat{(\shape{\shape{C}}-m)+(n-1-m)+1} (C \mmult{m} B)
-  = 
-  (C \mmult{m} A) \mconcat{\shape{\shape{C}}+n-2m} (C \mmult{m} B)
-\]
-
-\begin{landscape}
-Which means that,
-\begin{align*}
-  \shape{C \mmult{m} \left(A \mconcat{n} B\right)}
-  &= \shape{(C \mmult{m} A) \mconcat{\shape{\shape{C}}+n-2m} (C \mmult{m} B)} \\
-  &= \vec{c} \oplus \vec{e} \oplus \left<a+b\right> \oplus \vec{r}
-\end{align*}
-
-Now for any $\bar{c}$, $\bar{e}$, and $\bar{r}$ be in $\Dim(\vec{c})$, $\Dim(\vec{e})$,
-and $\Dim(\vec{r})$ respectively and $k \in [1,a+b]$, then,
-\begin{align*}
-  \left(C \mmult{m} \left(A \mconcat{n} B\right)\right)[\bar{c} \oplus \bar{e} \oplus \left<k\right> \oplus \bar{r}]
-  &= \sum_{\forall \bar{m} \in \Dim(\vec{m})} C[\bar{c} \oplus \bar{m}] \left(A \mconcat{n} B\right)[\bar{m} \oplus \bar{e} \oplus \left<k\right> \oplus \bar{r}] \\
-  &= \left\{
-  \begin{array}{ll}
-    \sum_{\forall \bar{m}} C[\bar{c} \oplus \bar{m}] A[\bar{m} \oplus \bar{e} \oplus \left<k\right> \oplus \bar{r}]
-    & \mbox{if } k \le a \\
-    \sum_{\forall \bar{m}} C[\bar{c} \oplus \bar{m}] B[\bar{m} \oplus \bar{e} \oplus \left<k-a\right> \oplus \bar{r}]
-    & \mbox{if } k > a
-  \end{array}
-  \right. \\
-  &= \left\{
-  \begin{array}{ll}
-    (C \mmult{m} A)[\bar{c} \oplus \bar{e} \oplus \left<k\right> \oplus \bar{r}]
-    & \mbox{if } k \le a \\
-    (C \mmult{m} B)[\bar{c} \oplus \bar{e} \oplus \left<k-a\right> \oplus \bar{r}]
-    & \mbox{if } k > a
-  \end{array}
-  \right. \\
-  &= \left(\left(C \mmult{m} A\right) \mconcat{\shape{\shape{C}}+n-2m} \left(C \mmult{m} B\right)\right)[\bar{c} \oplus \bar{e} \oplus \left<k\right> \oplus \bar{r}]
-\end{align*}
+
 \end{landscape}
-\end{ppart}
-\begin{ppart}
-TODO: Prove the converse.
-\end{ppart}
-\begin{ppart}
-Let $A$ and $B$ be multimatrices where $A \mconcat{n} B$ is valid. 
-Let $m$ be a natural number where $m \le \shape{\shape{A}}-n$
-and $C$ is a multimatrix for which $\left(A \mconcat{n} B\right) \mmult{m} C$ is valid.
-Then there exit shape vectors $\vec{l}$ and $\vec{r}$ and integers $a$ and $b$ such that,
-
-\[ \shape{A} = \vec{l} \oplus \left<a\right> \oplus \vec{r} \]
-\[ \shape{B} = \vec{l} \oplus \left<b\right> \oplus \vec{r} \]
-\[ \shape{A \mconcat{n} B} = \vec{l} \oplus \left<a+b\right> \oplus \vec{r} \]
-
-Where $\shape{\vec{l}} = n-1$ and $\shape{\vec{r}} = \shape{\shape{A}}-n$.
-
-Then since $\left(A \mconcat{n} B\right) \mmult{m} C$ is valid, $\shape{C}$ can
-be partitioned into $\vec{m}$ and $\vec{c}$ where,
-
-\[ \shape{C} = \vec{m} \oplus \vec{c} \]
-
-And $\shape{\vec{m}} = m$. This also means that,
-
-\[ \shape{A \mconcat{n} B} = \vec{d} \oplus \vec{m} \]
-
-Now since $m \le \shape{\shape{A}}-n$ we can partition $\vec{r}$ like this,
-
-\[ \vec{r} = \vec{e} \oplus \vec{m} \]
-
-So we can use that repartition in our original shape definitions,
-
-\[ \shape{A \mconcat{n} B} = \vec{l} \oplus \left<a+b\right> \oplus \vec{e} \oplus \vec{m} \]
-\[ \shape{A} = \vec{l} \oplus \left<a\right> \oplus \vec{e} \oplus \vec{m} \]
-\[ \shape{B} = \vec{l} \oplus \left<b\right> \oplus \vec{e} \oplus \vec{m} \]
-
-So $A \mmult{m} C$ and $B \mmult{m} C$ are both valid and,
-
-\[ \shape{A \mmult{m} C} = \vec{l} \oplus \left<a\right> \oplus \vec{e} \oplus \vec{c} \]
-\[ \shape{B \mmult{m} C} = \vec{l} \oplus \left<b\right> \oplus \vec{e} \oplus \vec{c} \]
-
-And finally we can see that $(A \mmult{m} C) \mconcat{\shape{\vec{l}}+1} (B \mmult{m} C)$
-is valid and,
-
-\[
-  (A \mmult{m} C) \mconcat{\shape{\vec{l}}+1} (B \mmult{m} C)
-  =
-  (A \mmult{m} C) \mconcat{n} (B \mmult{m} C)
-\]
-
-\begin{align*}
-  \shape{(A \mmult{m} C) \mconcat{n} (B \mmult{m} C)}
-  &= \vec{l} \oplus \left<a+b\right> \oplus \vec{e} \oplus \vec{c} \\
-  &= \shape{(A \mconcat{n} B) \mmult{m} C}
-\end{align*}
-
-\begin{landscape}
-Now for all $\bar{l}$, $\bar{e}$, and $\bar{c}$ are in $\Dim(\vec{l})$, $\Dim(\vec{e})$,
-and $\Dim(\vec{c})$ respectively and all $k \in [1,a+b]$,
-
-\begin{align*}
-  \left(\left(A \mconcat{n} B\right) \mmult{m} C\right)[\bar{l} \oplus \left<k\right> \oplus \bar{e} \oplus \bar{c}]
-  &= \sum_{\forall \bar{m} \in \Dim(\vec{m})} \left(A \mconcat{n} B\right)[\bar{l} \oplus \left<k\right> \oplus \bar{e} \oplus \bar{m}] C[\bar{m} \oplus \bar{c}] \\
-  &= \left\{
-  \begin{array}{ll}
-    \sum_{\forall \bar{m}} A[\bar{l} \oplus \left<k\right> \oplus \bar{e} \oplus \bar{m}] C[\bar{m} \oplus \bar{c}] 
-    & \mbox{if } k \le a \\
-    \sum_{\forall \bar{m}} B[\bar{l} \oplus \left<k-a\right> \oplus \bar{e} \oplus \bar{m}] C[\bar{m} \oplus \bar{c}] 
-    & \mbox{if } k > a
-  \end{array}
-  \right. \\
-  &= \left\{
-  \begin{array}{ll}
-    (A \mmult{m} C)[\bar{l} \oplus \left<k\right> \oplus \bar{e} \oplus \bar{c}]
-    & \mbox{if } k \le a \\
-    (B \mmult{m} C)[\bar{l} \oplus \left<k-a\right> \oplus \bar{e} \oplus \bar{c}]
-    & \mbox{if } k > a
-  \end{array}
-  \right. \\
-  &= 
-    \left(\left(A \mmult{m} C\right) \mconcat{n} \left(B \mmult{m} C\right)\right)
-    [\bar{l} \oplus \left<k\right> \oplus \bar{e} \oplus \bar{c}]
-\end{align*}
-\end{landscape}
-\end{ppart}
-
-\begin{ppart}
-TODO: Prove the converse.
-\end{ppart}
-
-\begin{ppart}
-Let $A$ and $B$ be multimatrices where $A \mconcat{n} B$ is valid. 
-Let $m$ be a natural number where $m \ge n$, and let $C$ be a multimatrix where
-$C \mmult{m} (A \mconcat{n} B)$ is valid.
-
-Then we can partition the shapes of $A$ and $B$ thus,
-
-\[ \shape{A} = \vec{l} \oplus \left<a\right> \oplus \vec{r} \]
-\[ \shape{B} = \vec{l} \oplus \left<b\right> \oplus \vec{r} \]
-\[ \shape{A \mconcat{n} B} = \vec{l} \oplus \left<a+b\right> \oplus \vec{r} \]
-
-Where $\shape{\vec{l}} = n-1$.
-
-We can also partition the shapes of $C$ and $(A \mconcat{n} B)$ like this,
-
-\[ \shape{C} = \vec{c} \oplus \vec{m} \]
-\[ \shape{A \mconcat{n} B} = \vec{m} \oplus \vec{d} \]
-
-Where $\shape{\vec{m}} = m$. Now since $m \ge n$ we can know that
-$\shape{\vec{m}} \ge \shape{\vec{l} \oplus \left<a+b\right>}$ 
-so $\vec{m}$ encompasses $\vec{l}$, the $n$'th index and potentially part of $\vec{r}$.
-There for if we partition $\vec{r}$ like this,
-
-\[ \vec{r} = \vec{p} \oplus \vec{q} \]
-
-Where,
-
-\[ \vec{m} = \vec{l} \oplus \left<a+b\right> \oplus \vec{p} \]
-
-Then we can define the resulting shape of $C$ like this,
-
-\[ \shape{C} = \vec{c} \oplus \vec{l} \oplus \left<a+b\right> \oplus \vec{p} \]
-
-Since $\shape{\vec{c}} = \shape{\shape{C}}-m$, if we let $C_1$ and $C_2$ be defined by,
-\[ \Part(C, \shape{\shape{C}}-m+n, \shape{A}[n]) = \{C_1, C_2\} \]
-Then,
-\[ \shape{C_1} = \vec{c} \oplus \vec{l} \oplus \left<a\right> \oplus \vec{p} \]
-\[ \shape{C_2} = \vec{c} \oplus \vec{l} \oplus \left<b\right> \oplus \vec{p} \]
-
-Now, let us define $\vec{m}_1$ and $\vec{m}_2$ such that,
-\[ \vec{m}_1 = \vec{l} \oplus \left<a\right> \oplus \vec{p} \]
-\[ \vec{m}_2 = \vec{l} \oplus \left<b\right> \oplus \vec{p} \]
-And notice that $\shape{\vec{m}_1} = \shape{\vec{m}_2} = m$
-
-Next, since $\vec{r} = \vec{p} \oplus \vec{q}$ the shapes of $A$ and $B$ and be described,
-\[ \shape{A} = \vec{l} \oplus \left<a\right> \oplus \vec{p} \oplus \vec{q} = \vec{m}_1 \oplus \vec{q} \]
-\[ \shape{B} = \vec{l} \oplus \left<b\right> \oplus \vec{p} \oplus \vec{q} = \vec{m}_2 \oplus \vec{q} \]
-
-So $C_1 \mmult{m} A$ and $C_2 \mmult{m} B$ are both valid.
-
-\end{ppart}
-\begin{ppart}
-TODO: Prove the converse.
-\end{ppart}
-
-TODO
-\end{proof}
 
 \begin{definition}[Multimatrix Wildcard Notation]
-Example:
-$\shape{X[\bar{a} \oplus *^{\vec{s}} \oplus \bar{b}]} = \vec{s}$
+Let $X$ be a multimatrix of where $\shape{X} = \vec{a} \oplus \vec{s} \oplus \vec{b}$,
+And let $\bar{a} \in \Dim(\vec{a})$ and $\bar{b} \in \Dim(\vec{b})$. Then,
+$X[\bar{a} \oplus *^{\vec{s}} \oplus \bar{b}]$ defines a multimatrix that is a
+subset of $X$ where,
+\[ \shape{X[\bar{a} \oplus *^{\vec{s}} \oplus \bar{b}]} = \vec{s} \]
+And for all $\bar{s} \in \Dim(\vec{s})$,
+\[ X[\bar{a} \oplus *^{\vec{s}} \oplus \bar{b}][\bar{s}] = X[\bar{a} \oplus \bar{s} \oplus \bar{b}] \]
 \end{definition}
@@
   &=
-  \lim_{n \to \inf} \sum_{i=1}^n G(C(i/n))[\bar{g} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} \frac{dC}{dt}(i/n) \frac{1}{n} \\
-  &=
-  \lim_{n \to \inf} \sum_{i=1}^n G(A + \frac{i}{n}(B-A))[\bar{g} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} \frac{B-A}{n} \\
-  &=
-  \lim_{n \to \inf} \sum_{i=1}^n \left( G(A + \frac{i}{n}(B-A)) \mmult{\shape{\shape{X}}} \frac{B-A}{n} \right)[\bar{g}] \\
-  &=
-  \left( \lim_{n \to \inf} \sum_{i=1}^n G(A + \frac{i}{n}(B-A)) \mmult{\shape{\shape{X}}} \frac{B-A}{n} \right)[\bar{g}] \\
+  \lim_{n \to \infty} \sum_{i=1}^n G(C(i/n))[\bar{g} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} \frac{dC}{dt}(i/n) \frac{1}{n} \\
+  &=
+  \lim_{n \to \infty} \sum_{i=1}^n G(A + \frac{i}{n}(B-A))[\bar{g} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} \frac{B-A}{n} \\
+  &=
+  \lim_{n \to \infty} \sum_{i=1}^n \left( G(A + \frac{i}{n}(B-A)) \mmult{\shape{\shape{X}}} \frac{B-A}{n} \right)[\bar{g}] \\
+  &=
+  \left( \lim_{n \to \infty} \sum_{i=1}^n G(A + \frac{i}{n}(B-A)) \mmult{\shape{\shape{X}}} \frac{B-A}{n} \right)[\bar{g}] \\
   &=
@@
 \[ \left(\int_A^B \frac{dF}{dX}(X) dX\right)[\bar{f}] = \int_C \frac{dF}{dX}(X)[\bar{f} \oplus *^{\shape{X}}] \mmult{\shape{\shape{X}}} dX \]
-Notice that $\frac{dF}{dX}(X)[\bar{f} \oplus *^{\shape{X}}]$ is the equivalent
-to the gradient of $F(X)[\bar{f}]$ at $X$ since for all $\bar{x} \in \Dim(\vec{x})$,
+Notice that $\frac{dF}{dX}(X)[\bar{f} \oplus *^{\shape{X}}]$ is equivalent
+to the gradient of $F(X)[\bar{f}]$ at $X$ since for all $\bar{x} \in \Dim(\shape{X})$,
 \[ \frac{dF}{dX}(X)[\bar{f} \oplus \bar{x}] = \frac{\partial F[\bar{f}]}{\partial X[\bar{x}]} \]
@@
 \[ \shape{X} = \vec{l} \oplus \vec{r} \]
+\[ \shape{\vec{l}} = l \]
+\[ \shape{\vec{r}} = r \]
 Implies,
 \[
- \frac{d\Tran(X, \shape{\vec{l}})}{dX} =
- \Tran(\Ident^2(\vec{r}) \mmult{0} \Ident^2(\vec{l}), \shape{\vec{r}})
+  \frac{d\transpose{X}{l}}{dX} =
+  \transpose{\left(\Ident^2(\vec{r}) \mmult{0} \Ident^2(\vec{l})\right)}{r}
 \]
@@
 (Thm. \ref{left_mult_derivative})
-\[ \frac{d(X \mmult{n} A)}{dX} = \Ident^2(\shape{X \mmult{n} A}) \mmult{\shape{\shape{A}}-n} \Tran(A, n) \]
+\[ \frac{d(X \mmult{n} A)}{dX} = \Ident^2(\shape{X \mmult{n} A}) \mmult{\shape{\shape{A}}-n} \transpose{A}{n} \]
 \end{drule}
@@
 Let $\shape{F} = \vec{f} \oplus \vec{c}$, $\shape{G} = \vec{c} \oplus \vec{g}$,
-and $\shape{X} = \vec{x}$. Then,
-\begin{align*}
- \frac{d\left(F(X) \mmult{\shape{\vec{c}}} G(X)\right)}{dX} =&
- F(X) \mmult{\shape{\vec{c}}} \frac{dG(X)}{dX} + \\
- &\Tran\left(
-   \Tran(G(X), \shape{\vec{c}})
-     \mmult{\shape{\vec{c}}}
-   \Tran\left(\frac{dF(X)}{dX}, \shape{\vec{f}}\right),
-   \shape{\vec{g} \oplus \vec{x}}
- \right)
+$\shape{X} = \vec{x}$, $\shape{\vec{x}} = x$, $\shape{\vec{c}} = c$, $\shape{\vec{f}} = f$, and $\shape{\vec{g}} = g$. Then,
+\begin{align*}
+ \frac{d\left(F(X) \mmult{c} G(X)\right)}{dX} =&
+ F(X) \mmult{c} \frac{dG(X)}{dX} + \\
+ &\transpose{\left(
+   \transpose{G(X)}{c}
+     \mmult{c}
+   \transpose{\left(
+      \frac{dF(X)}{dX}
+   \right)}{f}
+  \right)}{g+x}
 \end{align*}
@@
 (Thm. \ref{hadamard_rule})
-If $\shape{F(X)} = \vec{a} \oplus \vec{c}$ and $\shape{G(X)} = \vec{c} \oplus \vec{b}$, then,
-\[
-  \frac{d(F(X) \dmult{\shape{\vec{c}}} G(X))}{dX} =
-    F(X) \dmult{\shape{\vec{c}}} \frac{dG}{dX} +
-    \Tran\left(\Tran\left(\frac{dF}{dX}, \shape{\shape{F}}\right) \dmult{\shape{\vec{c}}} G(X), \shape{\shape{X}}\right)
+If $\shape{F(X)} = \vec{a} \oplus \vec{c}$ and $\shape{G(X)} = \vec{c} \oplus \vec{b}$,
+and $\shape{\shape{X}} = x$, $\shape{\vec{c}} = c$, and $\shape{\shape{F(X)}} = f$ then,
+\[
+  \frac{d(F(X) \dmult{c} G(X))}{dX} =
+    F(X) \dmult{c} \frac{dG}{dX} +
+    \transpose{\left(
+      \transpose{\left(\frac{dF}{dX}\right)}{f} \dmult{c} G(X)
+    \right)}{x}
 \]
@@
 they are defined as 'orthogonal', i.e. $B \bot C$ iff $B \mmult{\shape{s}} C = 0$.
-And two sets are orthogonal if all any member from one is orthogonal to any member of the other.
+
+If $V$ is a vector space in $\mathbb{R}^{\vec{v}}$ then $V^{\bot}$ is the
+orthoganal complement of $V$ composed of all multimatrices in $\mathbb{R}^{\vec{v}}$, $X$, 
+such that for all $Y \in V$, $X \bot Y$.
 
 I hypothesize that,
-\[ProdSpace(A, n) \bot NullSpace(\Tran(A, a), a)\]
+\[ProdSpace(A, n) \bot NullSpace(\transpose{A}{a}, a)\]
 and
-\[NullSpace(A, n) \bot ProdSpace(\Tran(A, a), a)\]
+\[NullSpace(A, n) \bot ProdSpace(\transpose{A}{a}, a)\]
 based on a similar theory for 2d matrices \cite{youtube:orthogonal} (and the fact that the shapes line up nicely).
@@
 but, notice that a shortest $E$ is necessarily orthogonal $ProdSpace(A,n)$ by simple geometry since it is a shortest
-vector from $ProdSpace(A,n)$ to $B$. So if our above hypothesis is correct, $B$ is in $NullSpace(\Tran(A,a), a)$
-
-Therefore the solution to $\Tran(A,a) \mmult{a} E = 0$ for $E$ will be the one that minimizes $SS(E)$. So,
-\begin{align*}
-  \Tran(A,a) \mmult{a} E &= 0 \\
-  \Tran(A,a) \mmult{a} (B - A \mmult{n} X) &= 0 \\
-  \Tran(A,a) \mmult{a} B - \Tran(A,a) \mmult{a} (A \mmult{n} X) &= 0 \\
-  \Tran(A,a) \mmult{a} B - \Tran(A,a) \mmult{a} A \mmult{n} X &= 0 \\
-  \Tran(A,a) \mmult{a} B &= \Tran(A,a) \mmult{a} A \mmult{n} X \\
-  \Tran(A,a) \mmult{a} A \mmult{n} X &= \Tran(A,a) \mmult{a} B
+vector from $ProdSpace(A,n)$ to $B$. So if our above hypothesis is correct, $B$ is in $NullSpace(\transpose{A}{a}, a)$
+
+Therefore the solution to $\transpose{A}{a} \mmult{a} E = 0$ for $E$ will be the one that minimizes $SS(E)$. So,
+\begin{align*}
+  \transpose{A}{a} \mmult{a} E &= 0 \\
+  \transpose{A}{a} \mmult{a} (B - A \mmult{n} X) &= 0 \\
+  \transpose{A}{a} \mmult{a} B - \transpose{A}{a} \mmult{a} (A \mmult{n} X) &= 0 \\
+  \transpose{A}{a} \mmult{a} B - \transpose{A}{a} \mmult{a} A \mmult{n} X &= 0 \\
+  \transpose{A}{a} \mmult{a} B &= \transpose{A}{a} \mmult{a} A \mmult{n} X \\
+  \transpose{A}{a} \mmult{a} A \mmult{n} X &= \transpose{A}{a} \mmult{a} B
 \end{align*}
@@
 
-I think need to prove, in the abstract, that if you have a vector field $F$
-and a distance metric $d(u,v)$ and a bilinear form \cite{wiki:bilinear}, $b(u,v)$, such that
-\[ v \bot u \iff b(u,v) = 0 \]
-Then for any $v \in F$ and any sub field $f \subset F$, for all $u \in f$,
-\[ (v-u) \bot u \iff \forall u' \in f - \{u\} : d(u', v) < d(u,v) \]
-That is, $u$ is the closest vector in $f$ to $v$ if and only if it is the orthogonal project of $v$ onto $f$.
-
 \chapter{Scratch}
 
-What is $A \dmult{m} (B \mmult{n} C)$ ?
-
-\[ \shape{A} = \vec{a} \oplus \vec{m} \]
-\[ \shape{B} = \vec{b} \oplus \vec{n} \]
-\[ \shape{C} = \vec{n} \oplus \vec{c} \]
-
-if $\vec{m} = \vec{b}$ then,
-
-\[ \shape{A \dmult{m} (B \mmult{n} C)} = \vec{a} \oplus \vec{b} \oplus \vec{c} \]
-
-\begin{align*}
-(A \dmult{m} (B \mmult{n} C))[\bar{a} \oplus \bar{b} \oplus \bar{c}]
-  &=
-  A[\bar{a} \oplus \bar{b}] \sum_{\forall \bar{n}} B[\bar{b} \oplus \bar{n}] C[\bar{n} \oplus \bar{c}] \\
-  &=
-  \sum_{\forall \bar{n}} A[\bar{a} \oplus \bar{b}] B[\bar{b} \oplus \bar{n}] C[\bar{n} \oplus \bar{c}] \\
-  &=
-  \sum_{\forall \bar{n}} (A \dmult{m} B)[\bar{a} \oplus \bar{b} \oplus \bar{n}] C[\bar{n} \oplus \bar{c}] \\
-  &= ((A \dmult{m} B) \mmult{n} C)[\bar{a} \oplus \bar{b} \oplus \bar{c}]
-\end{align*}
-
-If $m < \shape{\vec{b}}$ then
-\[ \vec{b} = \vec{m} \oplus \vec{d} \]
-\[ \shape{B} = \vec{m} \oplus \vec{d} \oplus \vec{n} \]
-\[ \shape{A \dmult{m} (B \mmult{n} C)} = \vec{a} \oplus \vec{m} \oplus \vec{d} \oplus \vec{c} \]
-
-\begin{align*}
-(A \dmult{m} (B \mmult{n} C))[\bar{a} \oplus \bar{m} \oplus \bar{d} \oplus \bar{c}]
-  &=
-  A[\bar{a} \oplus \bar{m}] \sum_{\forall \bar{n}} B[\bar{m} \oplus \bar{d} \oplus \bar{n}] C[\bar{n} \oplus \bar{c}] \\
-  &=
-  \sum_{\forall \bar{n}} A[\bar{a} \oplus \bar{m}] B[\bar{m} \oplus \bar{d} \oplus \bar{n}] C[\bar{n} \oplus \bar{c}] \\
-  &=
-  \sum_{\forall \bar{n}} (A \dmult{m} B)[\bar{a} \oplus \bar{m} \oplus \bar{d} \oplus \bar{n}] C[\bar{n} \oplus \bar{c}] \\
-  &= ((A \dmult{m} B) \mmult{n} C)[\bar{a} \oplus \bar{b} \oplus \bar{c}]
-\end{align*}
-
-If $m > \shape{\vec{b}}$ then
-\[ \vec{c} = \vec{l} \oplus \vec{r} \]
-\[ \vec{m} = \vec{b} \oplus \vec{l} \]
-\[ \shape{A \dmult{m} (B \mmult{n} C)} = \vec{a} \oplus \vec{b} \oplus \vec{l} \oplus \vec{r} \]
-
-\begin{align*}
-(A \dmult{m} (B \mmult{n} C))[\bar{a} \oplus \bar{b} \oplus \bar{l} \oplus \bar{r}]
-  &=
-  A[\bar{a} \oplus \bar{b} \oplus \bar{l}] \sum_{\forall \bar{n}} B[\bar{b} \oplus \bar{n}] C[\bar{n} \oplus \bar{l} \oplus \bar{r}] \\
-  &=
-  \sum_{\forall \bar{n}} A[\bar{a} \oplus \bar{b} \oplus \bar{l}] B[\bar{b} \oplus \bar{n}] C[\bar{n} \oplus \bar{l} \oplus \bar{r}] \\
-\end{align*}
-
-What about $A \mmult{a} \Ident^2(\vec{a} \oplus \vec{b})$
-
-\begin{align*}
-\left(A \mmult{a} \Ident^2(\vec{a} \oplus \vec{b}) \right)[\bar{b}_1 \oplus \bar{a} \oplus \bar{b}_2]
-  &= 
-  \sum_{\forall \bar{x}}
-    A[\bar{x}] \Ident^2(\vec{a} \oplus \vec{b})[\bar{x} \oplus \bar{b}_1 \oplus \bar{a} \oplus \bar{b}_2] \\
-  &= 
-  \sum_{\forall \bar{x}}
-    A[\bar{x}] \delta_{\bar{x},\bar{a}} \delta_{\bar{b}_1,\bar{b}_2} \\
-  &=
-  \delta_{\bar{b}_1,\bar{b}_2}
-  \sum_{\forall \bar{x}}
-    A[\bar{x}] \delta_{\bar{x},\bar{a}} \\
-  &=
-  \Ident^2(\vec{b})[\bar{b}_2 \oplus \bar{b}_1]
-  A[\bar{a}] \\
-  &=
-  (\Ident^2(\vec{b}) \mmult{0} A) [\bar{b}_2 \oplus \bar{b}_1 \oplus \bar{a}] \\
-  &=
-  \Tran(\Ident^2(\vec{b}) \mmult{0} A, \shape{\vec{b}})[\bar{b}_1 \oplus \bar{a} \oplus \bar{b}_2] \\
-  &=
-  \Tran(A \mmult{0} \Ident^2(\vec{b}), \shape{\vec{a} \oplus \vec{b}})[\bar{b}_1 \oplus \bar{a} \oplus \bar{b}_2] \\
-  &= 
-  \sum_{\forall \bar{x}}
-    \delta_{\bar{b}_1,\bar{b}_2} \delta_{\bar{a},\bar{x}} A[\bar{x}] \\
-  &= 
-  \sum_{\forall \bar{x}}
-    \Ident^2(\vec{b} \oplus \vec{a})[\bar{b}_1 \oplus \bar{a} \oplus \bar{b}_2 \oplus \bar{x}]
-    A[\bar{x}] \\
-  &= 
-  (\Ident^2(\vec{b} \oplus \vec{a}) \mmult{a} A) [\bar{b}_1 \oplus \bar{a} \oplus \bar{b}_2]
-\end{align*}
-
-So
-\[ A \mmult{a} \Ident^2(\vec{a} \oplus \vec{b}) = \Ident^2(\vec{b} \oplus \vec{a}) \mmult{a} A \]
-
-Now what is $A \dmult{a} \Ident^2(\vec{a} \oplus \vec{b})$...
-
-\begin{align*}
-\left(A \dmult{a} \Ident^2(\vec{a} \oplus \vec{b})\right) [\bar{a}_1 \oplus \bar{b}_1 \oplus \bar{a}_2 \oplus \bar{b}_2]
-  &=
-  A [\bar{a}_1] \Ident^2(\vec{a} \oplus \vec{b}) [\bar{a}_1 \oplus \bar{b}_1 \oplus \bar{a}_2 \oplus \bar{b}_2] \\
-  &=
-  A [\bar{a}_1] \delta_{\bar{a}_1, \bar{a}_2} \delta_{\bar{b}_1, \bar{b}_2}
-\end{align*}
-
-\begin{align*}
-\left( A \dmult{a} \Ident^2(\vec{a} \oplus \vec{b}) \mmult{b} B \right)[\bar{a}_1 \oplus \bar{b} \oplus \bar{a}_2]
-  &=
-  \sum_{\forall \bar{x}} A [\bar{a}_1] \Ident^2(\vec{a} \oplus \vec{b}) [\bar{a}_1 \oplus \bar{b} \oplus \bar{a}_2 \oplus \bar{x}] B[\bar{x}] \\
-  &=
-  \sum_{\forall \bar{x}} A [\bar{a}_1] \delta_{\bar{a}_1, \bar{a}_2} \delta_{\bar{b}, \bar{x}} B[\bar{x}] \\
-  &=
-  A [\bar{a}_1] \delta_{\bar{a}_1, \bar{a}_2} B[\bar{b}] \\
-  &=
-  A [\bar{a}_1] B[\bar{b}] \delta_{\bar{a}_1, \bar{a}_2} \\
-  &=
-  \delta_{\bar{a}_2, \bar{a}_1} A [\bar{a}_2] B[\bar{b}] \\
-  &=
-  \Ident^2(\vec{a})[\bar{a}_2 \oplus \bar{a}_1] A [\bar{a}_1] B[\bar{b}] \\
-  &=
-  \left(\Ident^2(\vec{a}) \dmult{a} A\right) [\bar{a}_2 \oplus \bar{a}_1]B[\bar{b}] \\
-  &=
-  \left(\left(\Ident^2(\vec{a}) \dmult{a} A\right) \dmult{0} B\right) [\bar{a}_2 \oplus \bar{a}_1 \oplus \bar{b}] \\
-  &=
-  \left(\Ident^2(\vec{a}) \dmult{a} A \dmult{0} B\right) [\bar{a}_2 \oplus \bar{a}_1 \oplus \bar{b}] \\
-  &=
-  \Tran\left(\Ident^2(\vec{a}) \dmult{a} A \dmult{0} B, a\right) [\bar{a}_1 \oplus \bar{b} \oplus \bar{a}_2]
-\end{align*}
-
-What about $A \dmult{0} \Tran(B, n)$? Is that just $\Tran(A \dmult{0} B, k)$ ?
+Investigating the determinant.
+
+I think, unfortunately, that the determinant of a multimatrix will best be defined as
+equal to the determinant of the equivalent 2d matrix.
+
+Because if $M$ is a multimatrix of shape $\shape{M} = \vec{a} \oplus \vec{b}$ where
+\[\prod \vec{a}[i] = \prod \vec{b}[j]\]
+Then $\RMult[\shape{\vec{a}},M]$ has an inverse $\RMult[\shape{\vec{b}},N]$
+where $\shape{N} = \vec{b} \oplus \vec{a}$ if and only if the
+equivalent square 2d matrix to $M$ has an inverse, i.e. it's determinant is non-zero and defined.
+
+That depends on proving that inverses of smaller product overlaps always imply
+that there is a square inverse, however.
+
+\begin{landscape}
+
+For any given $\vec{a} \oplus \vec{b}$ there always exist a function $f(m, n)$ such that,
+\begin{align*}
+  \Idx^{-1}[\vec{a} \oplus \vec{b}]\left(f(\Idx[\vec{a}](\bar{a}), \Idx[\vec{b}](\bar{b}))\right) &= \bar{a} \oplus \bar{b} \\
+  f(\Idx[\vec{a}](\bar{a}), \Idx[\vec{b}](\bar{b})) &= \Idx[\vec{a} \oplus \vec{b}](\bar{a} \oplus \bar{b}) \\
+  f(m, n) &= \Idx[\vec{a} \oplus \vec{b}](\Idx^{-1}[\vec{a}](m) \oplus \Idx^{-1}[\vec{b}](n))
+\end{align*}
+
+For an indexing function to be valid for reshaping it must be true that,
+for any $\alpha$ and $\beta$ in $\mathbb{N}$ there exists a function $f(m, n)$ with domain $m \in [0,\alpha-1]$ and $n \in [0,\beta-1]$
+and range $[0, \alpha \beta - 1]$ such that if $\vec{a}$ and $\vec{b}$ satisfy $\size(\Dim(\vec{a})) = \alpha$ and $\size(\Dim(\vec{b})) = \beta$
+then for all $\bar{a} \in \Dim(\vec{a})$ and $\bar{b} \in \Dim(\vec{b})$,
+\[ \Idx^{-1}[\vec{a} \oplus \vec{b}]\left(f(\Idx[\vec{a}](\bar{a}), \Idx[\vec{b}](\bar{b}))\right) = \bar{a} \oplus \bar{b} \]
+
+\begin{align*}
+  C[\bar{a} \oplus \bar{b}]
+  &=
+  \sum_{\forall \bar{c} \in \Dim(\vec{c})} A[\bar{a} \oplus \bar{c}] B[\bar{c} \oplus \bar{b}] \\
+  &=
+  \sum_{\forall \bar{c}}
+  A[\Idx^{-1}[\vec{a} \oplus \vec{c}](
+    f(
+      \Idx[\vec{a}](\bar{a}),
+      \Idx[\vec{c}](\bar{c})
+    )
+  )]
+  B[\Idx^{-1}[\vec{c} \oplus \vec{b}](
+    g(
+      \Idx[\vec{c}](\bar{c}),
+      \Idx[\vec{b}](\bar{b})
+    )
+  )] \\
+  &=
+  \sum_{\forall i_c \in [0:\size(\Dim(\vec{c}))-1]}
+  A[\Idx^{-1}[\vec{a} \oplus \vec{c}](
+    f(
+      \Idx[\vec{a}](\bar{a}),
+      i_c
+    )
+  )]
+  B[\Idx^{-1}[\vec{c} \oplus \vec{b}](
+    g(
+      i_c,
+      \Idx[\vec{b}](\bar{b})
+    )
+  )] \\
+  &=
+  \sum_{\forall i_c \in [0:\size(\Dim(\vec{c}))-1]}
+  X[\Idx^{-1}[\vec{x} \oplus \vec{z}](
+    f(
+      \Idx[\vec{a}](\bar{a}),
+      i_c
+    )
+  )]
+  Y[\Idx^{-1}[\vec{z} \oplus \vec{y}](
+    g(
+      i_c,
+      \Idx[\vec{b}](\bar{b})
+    )
+  )] \\
+  &=
+  \sum_{\forall i_z \in [0:\size(\Dim(\vec{z}))-1]}
+  X[\Idx^{-1}[\vec{x} \oplus \vec{z}](
+    f(
+      \Idx[\vec{a}](\bar{a}),
+      i_z
+    )
+  )]
+  Y[\Idx^{-1}[\vec{z} \oplus \vec{y}](
+    g(
+      i_z,
+      \Idx[\vec{b}](\bar{b})
+    )
+  )] \\
+  &=
+  \sum_{\forall i_z \in [0:\size(\Dim(\vec{z}))-1]}
+  X[\Idx^{-1}[\vec{x} \oplus \vec{z}](
+    f(
+      \Idx[\vec{x}](\bar{x}),
+      i_z
+    )
+  )]
+  Y[\Idx^{-1}[\vec{z} \oplus \vec{y}](
+    g(
+      i_z,
+      \Idx[\vec{y}](\bar{y})
+    )
+  )] \\
+  &=
+  \sum_{\forall \bar{z} \in \Dim(\vec{z})}
+  X[\Idx^{-1}[\vec{x} \oplus \vec{z}](
+    f(
+      \Idx[\vec{x}](\bar{x}),
+      \Idx[\vec{z}](\bar{z})
+    )
+  )]
+  Y[\Idx^{-1}[\vec{z} \oplus \vec{y}](
+    g(
+      \Idx[\vec{z}](\bar{z}),
+      \Idx[\vec{y}](\bar{y})
+    )
+  )] \\
+  &=
+  \sum_{\forall \bar{z} \in \Dim(\vec{z})}
+  X[\bar{x} \oplus \bar{z}]
+  Y[\bar{z} \oplus \bar{y}]
+\end{align*}
+
+So, let's investigate if a `smaller' inverse can be transformed into a larger one.
+Consider $\RMult[a, X]$ with inverse $\RMult[b, Y]$ such that $b < \shape{\shape{X}}-a$
+
+Then for all multimatrices $A$,
+\[ A \mmult{a} X \mmult{b} Y = A \]
+By definition.
+
+Now, can we construct a $\RMult[c, Z]$ where $c = \shape{\shape{X}}-a$ from $\RMult[b,Y]$?
+
+Let's have $\shape{X} = \vec{a} \oplus \vec{x}$, $\shape{\vec{a}} = a$.
+And, for our base case, assume that $\size(\Dim(\vec{a})) = \size(\Dim(\vec{x}))$.
+
+\[ X \mmult{b} Y = \Ident^2(\vec{a}) \]
+\[ \shape{X \mmult{b} Y} = \vec{a} \oplus \vec{a} \]
+\[ \shape{X} = \vec{l} \oplus \vec{b} \]
+\[ \shape{Y} = \vec{b} \oplus \vec{y} \]
+\[ \vec{l} \oplus \vec{y} = \vec{a} \oplus \vec{a} \]
+\begin{align*}
+  \shape{\vec{b}} &< \shape{\vec{a} \oplus \vec{x}}-a \\
+  b &< x \\
+\end{align*}
+\[ \vec{l} \oplus \vec{b} = \vec{a} \oplus \vec{x} \]
+\[ \vec{l}_l \oplus \vec{l}_r \oplus \vec{b} = \vec{a} \oplus \vec{x} \]
+\[ \vec{l}_l = \vec{a} \]
+\[ \vec{l}_r \oplus \vec{b} = \vec{x} \]
+\[ \vec{l}_r \oplus \vec{b} = \vec{x}_l \oplus \vec{x}_r \]
+\[ \vec{b} = \vec{x}_r \]
+
+Therefore, not only is $\size(\Dim(\vec{b})) < \size(\Dim(\vec{x}))$, but $\size(\Dim(\vec{b}))$ divides $\size(\Dim(\vec{x}))$.
+
+Since,
+\begin{align*}
+  c &= \shape{\shape{X}}-a \\
+  c &= \shape{\vec{a} \oplus \vec{x}}-a \\
+  c &= \shape{\vec{x}}
+\end{align*}
+\[ X \mmult{c} Z = \Ident^2(\vec{a}) \]
+\[ \shape{X \mmult{c} Z} = \vec{a} \oplus \vec{a} \]
+\[ \shape{X} = \vec{p} \oplus \vec{c} \]
+\[ \shape{Z} = \vec{c} \oplus \vec{z} \]
+\[ \vec{p} \oplus \vec{z} = \vec{a} \oplus \vec{a} \]
+\[ \vec{p} \oplus \vec{c} = \vec{a} \oplus \vec{x} \]
+And since $c = \shape{\vec{x}}$
+\[ \vec{p} = \vec{a} \]
+\[ \vec{c} = \vec{x} \]
+So,
+\[ \vec{z} = \vec{a} \]
+\[ \shape{Z} = \vec{x} \oplus \vec{a} = \shape{\transpose{X}{a}} \]
+
+If $Z$ exists, then,
+\[ X \mmult{b} Y = X \mmult{c} Z \]
+
+I think I need to look at the rank of the multimatrices. Do multimatrices even have a fixed rank? I think multiplication operations do, but not multimatrices.
+
+So the rank of $\RMult[a, X]$ is the rank of the associated 2d matrix formed of shape
+\[ \left<\size(\Dim(\vec{a})), \size(\Dim(\vec{x}))\right> \]
+
+Now, for $A$ in $\mathbb{R}^{\vec{a}}$, $A \mmult{a} X \mmult{b} Y = A$. Therefore the range of $\RMult[a,X]$ must be of the same dimensionality of $\mathbb{R}^{\vec{a}}$.
+
+Ooooo, got a brain bomb,
+\[ |X| = \vec{a} \oplus \vec{x} \oplus \vec{a} \oplus \vec{x} \]
+I think this shape is necessary for $Y$ (an inverse that doesn't cover the full shape) to exists,
+\[ |Y| = \vec{x} \oplus \vec{x} \]
+\[ |Z| = \vec{a} \oplus \vec{x} \oplus \vec{a} \oplus \vec{x} \]
+\[ Z[\bar{a}_1 \oplus \bar{x}_1 \oplus \bar{a}_2 \oplus  \vec{x}_2] = \delta_{\bar{a}_1, \bar{a}_2} Y[\bar{x}_1 \oplus \bar{x}_2] \]
+
+And $\det(Z) = \det(Y)^{\size(\Dim(\vec{a}))}$
+
+If $\shape{A} = \vec{b} \oplus \vec{a} \oplus \vec{x}$ then,
+\[ \shape{A \mmult{a} X} = \vec{b} \oplus \vec{a} \oplus \vec{x} \]
+\[ \shape{A \mmult{a} X \mmult{x} Y} = \vec{b} \oplus \vec{a} \oplus \vec{x} \]
+\[ (A \mmult{a} X)[\bar{b} \oplus \bar{a} \oplus *^{\vec{x}}] \mmult{x} Y = A[\bar{b} \oplus \bar{a} \oplus *^{\vec{x}}] \]
+Seems important, but how do we progress?
+
+\begin{align*}
+  Z[\bar{a}_1 \oplus \bar{x}_1 \oplus \bar{a}_2 \oplus  \bar{x}_2]
+  &= \delta_{\bar{a}_1, \bar{a}_2} Y[\bar{x}_1 \oplus \bar{x}_2] \\
+  &= \Ident^2(\vec{a})[\bar{a}_2 \oplus \bar{a}_1] Y[\bar{x}_1 \oplus \bar{x}_2] \\
+  &= (\Ident^2(\vec{a}) \mmult{0} Y)[\bar{a}_2 \oplus \bar{a}_1 \oplus \bar{x}_1 \oplus \bar{x}_2]
+\end{align*}
+So, $Z$ is some permutation of $\Ident^2(\vec{a}) \mmult{0} Y$.
+
+Maybe I can prove that, if $C$ is a permutation of $\Ident^2(\vec{a}) \mmult{0} B$ then, $A \mmult{?} C = A \mmult{?} B$ in general?
+
+If $\sigma$ is a permutation, then $\transpose{C}{\sigma}$ is defined as,
+\[ \shape{\transpose{C}{\sigma}}[i] = \shape{C}[\sigma(i)] \]
+\[ \bar{c}_\sigma[i] = \bar{c}[\sigma(i)] \]
+\[ \transpose{C}{\sigma}[\bar{c}_\sigma] = C[\bar{c}] \]
+
+So if $\sigma = (1 ~ 2 ~ 3)$ and $\shape{C} = \left<1,2,3\right>$ then,
+\[ \shape{\transpose{C}{\sigma}} = \left<2, 3, 1\right> \]
+If $\sigma$ is a specific type of cyclic permutation then it just applies a transposition.
+Specifically, if it's a permutation in the group generated by $(1 ~ 2 ~ 3 ~ \ldots ~ n)$.
+
+No wait, I can do this easier if I just show that since,
+\[ (A \mmult{a} X)[\bar{b} \oplus \bar{a} \oplus *^{\vec{x}}] \mmult{x} Y = A[\bar{b} \oplus \bar{a} \oplus *^{\vec{x}}] \]
+If we let $B_i$, and $A_i$ be a partitions of $A \mmult{a} X$ and $A$ respectively for $1 \le i \le \size(\Dim(\vec{a}))$
+where,
+\[ B_i[\bar{b} \oplus (\left<1\right>*\shape{\vec{a}}) \oplus \bar{x}] = (A \mmult{a} X)[\bar{b} \oplus \Idx^{-1}[\vec{a}](i) \oplus \bar{x}] \]
+\[ A_i[\bar{b} \oplus (\left<1\right>*\shape{\vec{a}}) \oplus \bar{x}] = A[\bar{b} \oplus \Idx^{-1}[\vec{a}](i) \oplus \bar{x}] \]
+Then a reshaping of $Y$ into $Y'$ where,
+\[ \shape{Y'} = (\left<1\right>*a) \oplus \vec{x} \oplus (\left<1\right>*a) \oplus \vec{x} \]
+\[ Y'[(\left<1\right>*a) \oplus \bar{x}_1 \oplus (\left<1\right>*a) \oplus \bar{x}_2] = Y[\bar{x}_1 \oplus \bar{x}_2] \]
+Can be multiplied,
+\[ B_i \mmult{a+x} Y' = A_i \]
+And then those partitions can be joined back together in some way that results in $Z$. 
+I think there could be a general rule I could come up with for that process.
+
+\pagebreak
+
+\[
+  \frac{dL_i}{dW_{j<i}} =
+      \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
+      \mmult{\shape{\shape{L_i}}}
+      \transpose{W_i}{\shape{\shape{L_{i-1}}}}
+      \mmult{\shape{\shape{L_{i-1}}}}
+      \frac{d L_{i-1}}{dW_j}
+\]
+So,
+\begin{align*}
+  \frac{dL_i}{dW_j}[\bar{l}_i \oplus \bar{w}_j]
+  &= 
+  \left(
+    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right) 
+    \mmult{\shape{\shape{L_i}}}
+    \transpose{W_i}{\shape{\shape{L_{i-1}}}}
+    \mmult{\shape{\shape{L_{i-1}}}}
+    \frac{d L_{i-1}}{dW_j}
+  \right)[\bar{l}_i \oplus \bar{w}_j] \\
+  &= 
+  \sum_{\bar{m} \in \Dim(\shape{L_i}), \bar{n} \in \Dim(\shape{L_{i-1}})}
+    \left(\Ident^3(\shape{L_i}) \mmult{\shape{\shape{L_i}}} a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i) \right)[\bar{l}_i \oplus \bar{m}]
+    \transpose{W_i}{\shape{\shape{L_{i-1}}}} [\bar{m} \oplus \bar{n}]
+    \frac{d L_{i-1}}{dW_j} [\bar{n} \oplus \bar{w}_j] \\
+  &=
+  \sum_{\bar{m}, \bar{n},\bar{c} \in \Dim(\shape{L_i})}
+    \Ident^3(\shape{L_i})[\bar{l}_i \oplus \bar{m} \oplus \bar{c}]
+    a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i)[\bar{c}]
+    \transpose{W_i}{\shape{\shape{L_{i-1}}}} [\bar{m} \oplus \bar{n}]
+    \frac{d L_{i-1}}{dW_j} [\bar{n} \oplus \bar{w}_j] \\
+  &=
+  \sum_{\bar{n}}
+    a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i)[\bar{l}_i]
+    \transpose{W_i}{\shape{\shape{L_{i-1}}}} [\bar{l}_i \oplus \bar{n}]
+    \frac{d L_{i-1}}{dW_j} [\bar{n} \oplus \bar{w}_j] \\
+  &=
+  a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i)[\bar{l}_i]
+  \sum_{\bar{n}}
+    \transpose{W_i}{\shape{\shape{L_{i-1}}}} [\bar{l}_i \oplus \bar{n}]
+    \frac{d L_{i-1}}{dW_j} [\bar{n} \oplus \bar{w}_j] \\
+  &=
+  a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i)[\bar{l}_i]
+  \left(
+    \transpose{W_i}{\shape{\shape{L_{i-1}}}} 
+    \mmult{\shape{\shape{L_i}}}
+    \frac{d L_{i-1}}{dW_j}
+  \right) [\bar{l}_i \oplus \bar{w}_j] \\
+  &=
+  \left(
+    a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i)
+    \dmult{\shape{\shape{L_i}}}
+    \transpose{W_i}{\shape{\shape{L_{i-1}}}} 
+    \mmult{\shape{\shape{L_i}}}
+    \frac{d L_{i-1}}{dW_j}
+  \right) [\bar{l}_i \oplus \bar{w}_j]
+\end{align*}
+So,
+\[ 
+  \frac{dL_i}{dW_{j<i}}
+  = 
+  a'(L_{i-1} \mmult{\shape{\shape{L_{i-1}}}} W_i)
+  \dmult{\shape{\shape{L_i}}}
+  \transpose{W_i}{\shape{\shape{L_{i-1}}}} 
+  \mmult{\shape{\shape{L_i}}}
+  \frac{d L_{i-1}}{dW_j}
+\]
+
+\pagebreak
+
+Let $\shape{A} = \vec{a}$ and $\shape{B} = \vec{a} \oplus \vec{b}$. Why does,
+\[ (\Ident^3(\vec{a}) \mmult{a} A) \mmult{a} B = A \dmult{a} B \]
+
+% ac xc cb -> bc xc ca -> ba -> ab
+
+\begin{align*}
+  (\Ident^3(\vec{a}) \mmult{a} A) \mmult{a} B
+  &=
+  \transpose{(\transpose{A}{a} \mmult{a} \transpose{\Ident^3(\vec{a})}{3*a-a})}{a-a} \mmult{a} B \\
+  &=
+  \transpose{(A \mmult{a} \transpose{\Ident^3(\vec{a})}{2a})}{0} \mmult{a} B \\
+  &=
+  A \mmult{a} \Ident^3(\vec{a}) \mmult{a} B \\
+  &=
+  A \dmult{a} B
+\end{align*}
+
+\pagebreak
+
+If $\shape{A} = \vec{a}$ does it follow that,
+\[ \Ident^3(\vec{a}) \mmult{a} A = \Ident^2(\vec{a}) \dmult{a} A \]
+
+\begin{align*}
+  (\Ident^3(\vec{a}) \mmult{a} A)[\bar{a}_1 \oplus \bar{a}_2]
+  &=
+  \sum_{\bar{a}_3} \Ident^3(\vec{a})[\bar{a}_1 \oplus \bar{a}_2 \oplus \bar{a}_3] A[\bar{a}_3] \\
+  &=
+  \Ident^3(\vec{a})[\bar{a}_1 \oplus \bar{a}_2 \oplus \bar{a}_2] A[\bar{a}_2] \\
+  &=
+  \Ident^2(\vec{a})[\bar{a}_1 \oplus \bar{a}_2] A[\bar{a}_2] \\
+  &=
+  (\Ident^2(\vec{a}) \dmult{a} A)[\bar{a}_1 \oplus \bar{a}_2]
+\end{align*}
+
+\pagebreak
+
+I think, in general, if an identity is consumed by multiples of it's base in multiplication operations, the operation can be reduced to an operation
+involving hadamard products and what's left of the identity.
+
+Let's check edge cases.  Does the identity only consume up the branch?
+
+So if $\shape{A_2} = \vec{a} \oplus \vec{a}$ does,
+
+\[ \Ident^4(\vec{a}) \mmult{2a} (A_2 \mmult{a} A_2)  = A_2 \mmult{a} A_2 \]
+
+Well, yes because, 
+\[ \Ident^4(\vec{a}) \mmult{2a} (A_2 \mmult{a} A_2)  = \Ident^2(\vec{a} \oplus \vec{a}) \mmult{2a} (A_2 \mmult{a} A_2) \]
+
+But maybe that's not a good edge case.
+
+\pagebreak
+
+Is it true that,
+\[ \frac{dX}{dY} = \left(\transpose{\left(\frac{dY}{dX}\right)}{\shape{\shape{Y}}}\right)^{-1} \]
+
+\begin{align*}
+  \transpose{\left(\frac{dY}{dX}\right)}{\shape{\shape{Y}}} [\bar{x} \oplus \bar{y}]
+  &=
+  \frac{dY}{dX}[\bar{y} \oplus \bar{x}] \\
+  &=
+  \frac{\partial Y[\bar{y}]}{\partial X[\bar{x}]} \\
+  \left(\transpose{\left(\frac{dY}{dX}\right)}{\shape{\shape{Y}}}\right)^{-1} [\bar{x} \oplus \bar{y}]
+  &=
+  \frac{\partial X[\bar{x}]}{\partial Y[\bar{y}]} \\
+  &=
+  \frac{dX}{dY}[\bar{x} \oplus \bar{y}] \\
+\end{align*}
+
+\pagebreak
+
+Suppose we have $F$ being a multimatrix that is a result of products of integer size multiples of $\shape{\vec{a}}$.
+Each leaf of the product tree will either be an identity with base shape $\vec{a}$ or an arbitrary multimatrix, $M_k$. 
+Then,
+\[ F[P] = \sum_{\{ \bar{a}_i \}} \prod_{\{ S_j\}} \delta_{S_j} \prod_{\{T_k\}} M_k[ T_k \cup P^{\lnot a}_k ] \]
+
+Where $P$ is an arbitrary vector that is composed of some non-overlapping subvectors in $\Dim(\vec{a})$, $P^a$, and some other non-overlapping subvectors, $P^{\lnot a}$
+
+$P^a$ and $P^{\lnot a}$ are disjoint and $P^a \cup P^{\lnot a} = P$.
+
+Each $S_j$ is a subset of $\{\bar{a}_i\} \cup P^a$.
+
+Each $S_j$ is disjoint from each other $S_l$ because if they were not, they could be combined.
+
+$P^{\lnot a}_k$ is a subset of $P^{\lnot a}$.
+
+Each $T_k$ is a subset of $\{\bar{a}_i\} \cup P^a$.
+
+To total union of all $P^{\lnot a}_k$ is equal to $P^{\lnot a}$.
+
+$P$ and $\{ \bar{a}_i \}$ are disjoint.
+
+Note that the equivalence class I'm working under is such that all instantiations of the values of these variables would make them equal,
+not that just one instantiation may be equal.
+
+Is it true that $\sum_{\{a_i\}} \delta_{S \cup a}  M[T \cup a \cup P^{\lnot a}] = \sum_{a} M[T \cup a \cup P^{\lnot a}]$? Not unless $S$ is disjoint from $P^a$. 
+Then it must be true that, in the reduced form, every for every $S_j$, $S_j \cap P^a \ne \emptyset$
+
+\pagebreak
+
+Alright, I'm not making much traction on that. The more important question seems to be, for the expression,
+\[ F[\gamma(\{\bar{p}_i\})] = \sum_{\{\bar{a}_i\}} \prod_j M_j[\sigma_j(S_j \cup P_j)] \]
+Where $\gamma$ and each $\sigma_j$ are concatenation orderings, $S_j \subseteq \{\bar{a}_i\}$, and $P_j \subseteq \{\bar{p}_i\}$,
+when can this expression be decomposed into products and hadamard products?
+
+\[ \shape{W} = \vec{f} \oplus \vec{a} \oplus \vec{b} \]
+\[ \shape{X} = \vec{b} \oplus \vec{c} \]
+\[ \shape{Y} = \vec{a} \oplus \vec{d} \]
+\[ \shape{Z} = \vec{d} \oplus \vec{c} \oplus \vec{e} \]
+\[ \shape{(W \mmult{b} X) \mmult{a+c} (Y \mmult{d} Z)} = \bar{f} \oplus \vec{e} \]
+\begin{align*}
+  F[\bar{f} \oplus \bar{e}]
+  &=
+  \sum_{\bar{a}, \bar{b}, \bar{c}, \bar{d}}
+  W[\bar{f} \oplus \bar{a} \oplus \bar{b}]
+  X[\bar{b} \oplus \bar{c}]
+  Y[\bar{a} \oplus \bar{d}]
+  Z[\bar{d} \oplus \bar{c} \oplus \bar{e}] \\
+  &=
+  \sum_{\bar{a}, \bar{c}, \bar{d}}
+  \left(
+    \sum_{\bar{b}}
+    W[\bar{f} \oplus \bar{a} \oplus \bar{b}]
+    X[\bar{b} \oplus \bar{c}]
+  \right)
+  Y[\bar{a} \oplus \bar{d}]
+  Z[\bar{d} \oplus \bar{c} \oplus \bar{e}] \\
+  &=
+  \sum_{\bar{a}, \bar{c}, \bar{d}}
+  (W \mmult{b} X)[\bar{f} \oplus \bar{a} \oplus \bar{c}]
+  Y[\bar{a} \oplus \bar{d}]
+  Z[\bar{d} \oplus \bar{c} \oplus \bar{e}] \\
+  &=
+  \sum_{\bar{a}, \bar{c}}
+  (W \mmult{b} X)[\bar{f} \oplus \bar{a} \oplus \bar{c}]
+  \left(
+    \sum_{\bar{d}}
+    Y[\bar{a} \oplus \bar{d}]
+    Z[\bar{d} \oplus \bar{c} \oplus \bar{e}]
+  \right) \\
+  &=
+  \sum_{\bar{a}, \bar{c}}
+  (W \mmult{b} X)[\bar{f} \oplus \bar{a} \oplus \bar{c}]
+  (Y \mmult{d} Z)[\bar{a} \oplus \bar{c} \oplus \bar{e}] \\
+  &=
+  \left((W \mmult{b} X) \mmult{a+c} (Y \mmult{d} Z)\right)[\bar{f} \oplus \bar{e}]
+\end{align*}
+
+\pagebreak
+
+What was that other example I had?
+\[ (\Ident^3(\vec{a}) \mmult{a} A) \mmult{2a} \Ident^3(\vec{a}) = A \]
+Because,
+\begin{align*}
+  ((\Ident^3(\vec{a}) \mmult{a} A) \mmult{2a} \Ident^3(\vec{a}))[\bar{a}_0]
+  &=
+  \sum_{\bar{a}_1, \bar{a}_2} 
+  (\Ident^3(\vec{a}) \mmult{a} A)[\bar{a}_1 \oplus \bar{a}_2]
+  \Ident^3(\vec{a})[\bar{a}_1 \oplus \bar{a}_2 \oplus \bar{a}_0] \\
+  &=
+  \sum_{\bar{a}_1, \bar{a}_2} 
+  \left(
+    \sum_{\bar{a}_3}
+    \Ident^3(\vec{a})[\bar{a}_1 \oplus \bar{a}_2 \oplus \bar{a}_3]
+    A[\bar{a}_3]
+  \right)
+  \Ident^3(\vec{a})[\bar{a}_1 \oplus \bar{a}_2 \oplus \bar{a}_0] \\
+  &=
+  \sum_{\bar{a}_1, \bar{a}_2, \bar{a}_3} 
+  \Ident^3(\vec{a})[\bar{a}_1 \oplus \bar{a}_2 \oplus \bar{a}_3]
+  A[\bar{a}_3]
+  \Ident^3(\vec{a})[\bar{a}_1 \oplus \bar{a}_2 \oplus \bar{a}_0] \\
+  &=
+  \sum_{\bar{a}_1, \bar{a}_2, \bar{a}_3} 
+  \delta_{\bar{a}_1, \bar{a}_2, \bar{a}_3}
+  A[\bar{a}_3]
+  \delta_{\bar{a}_1, \bar{a}_2, \bar{a}_0} \\
+  &=
+  \sum_{\bar{a}_1, \bar{a}_2, \bar{a}_3} 
+  \delta_{\bar{a}_0, \bar{a}_1, \bar{a}_2, \bar{a}_3}
+  A[\bar{a}_3] \\
+  &=
+  \left(
+    \sum_{\bar{a}_1=\bar{a}_2=\bar{a}_3=\bar{a}_0} 
+    (1)
+    A[\bar{a}_3]
+  \right)
+  +
+  0 \\
+  &=
+  A[\bar{a}_0]
+\end{align*}
+I'm having a hard time even describing what I'm seeing here.
+
+\pagebreak
+Well, what are the rules for adding deltas.
+Consider.
+\[
+  \sum_{\{\bar{a}_i\}} \delta_{S} \delta_{T} X[\{\bar{a}_i\}]
+\]
+What if $S,T \subset \{\bar{a}_i\}$ and $S \cap T \ne \emptyset$?
+\begin{align*}
+  \sum_{\{\bar{a}_i\}} \delta_S \delta_T X[\{\bar{a}_i\}]
+  &=
+  \sum_{\{\bar{a}_i\}-S, \forall x,y \in S : x=y}
+  \delta_T X[(\{\bar{a}_i\}-S) \cup S^{=}] \\
+  &=
+  \sum_{\{\bar{a}_i\}-S-T, \forall x,y \in S : x=y, \forall x,y \in T : x=y}
+  X[(\{\bar{a}_i\}-S-T) \cup S^{=} \cup T^{=}] \\
+  &=
+  \sum_{\{\bar{a}_i\}-(S \cup T), \forall x,y \in S \cup T : x=y}
+  X[(\{\bar{a}_i\}-(S \cup T)) \cup (S \cup T)^{=}] \\
+  &=
+  \sum_{\{\bar{a}_i\}}
+  \delta_{S \cup T}
+  X[\{\bar{a}_i\}]
+\end{align*}
+
+\end{landscape}
+
+I had a bit of a revelation. Using five theorems, you can completely do this identity reduction.
+
+\begin{enumerate}
+\item ``Identity Multiplication and Hadamard Reductions''
+\item ``Hadamard Product Associativity''
+\item ``Associativity of Multimatrix Multiplication''
+\item ``Associativity of Mixed Hadamard and Regular Products''
+\item ``Communicativity of Hadamard Products''
+\end{enumerate}
+
+For example, let $\shape{A} = \shape{B} = \shape{C} = \vec{a}$,
+
+\begin{align*}
+  (A \mmult{a} \Ident^4(\vec{a}) \mmult{a} B) \mmult{a} C
+  &=
+  (A \dmult{a} \Ident^3 \mmult{a} B) \mmult{a} C \\
+  &=
+  (A \dmult{a} \Ident^2 \dmult{a} B) \mmult{a} C \\
+  &=
+  (A \dmult{a} (\Ident^2 \dmult{a} B)) \mmult{a} C \\
+  &=
+  (A \dmult{a} (B \dmult{a} \Ident^2)) \mmult{a} C \\
+  &=
+  A \dmult{a} B \dmult{a} \Ident^2 \mmult{a} C \\
+  &=
+  A \dmult{a} B \dmult{a} (\Ident^2 \mmult{a} C) \\
+  &=
+  A \dmult{a} B \dmult{a} C
+\end{align*}
+
+\pagebreak
+
+I keep having to re-derive this, so I'll record the convolution formula here:
+
+Let $O$ be the output, $I$ be the input, and $K$ be the kernel. 
+\[ \shape{O} = \shape{I} - \shape{K} + \bar{1} \]
+\[ \shape{\shape{O}} = \shape{\shape{I}} = \shape{\shape{K}} = \shape{\shape{\bar{1}}} = d \]
+\[
+  O[\bar{y}] =
+  a\left(
+    \sum_{\forall \bar{x} \text{ s.t } \bar{x}-\bar{y}+\bar{1} \in \Dim(\shape{K})} 
+    I[\bar{y}] K[\bar{x}-\bar{y}+\bar{1}]
+  \right)
+\]
+\[ \shape{C} = \shape{I} \oplus \shape{O} \oplus \shape{K} \]
+\[
+  C[\bar{x} \oplus \bar{y} \oplus \bar{z}] = 
+  \left\{
+    \begin{array}{ll}
+      1  & \mbox{if } \bar{x}-\bar{y}+\bar{1} \in \Dim(\shape{K}) \mbox{ and } \bar{x}-\bar{y}+\bar{1}=\bar{z} \\
+      0 & \mbox{otherwise}
+    \end{array}
+  \right.
+\]
+\[ O = a\left( I \mmult{d} C \mmult{d} K \right) \]
+\[
+  O[\bar{y}] =
+  a\left(
+    \sum_{\forall \bar{x}, \bar{z}}
+      I[\bar{y}]
+      C[\bar{x} \oplus \bar{y} \oplus \bar{z}]
+      K[\bar{z}]
+  \right)
+\]
+
+\begin{landscape}
+\begin{align*}
+  \sum_{\forall \bar{x}, \bar{z}}
+    I[\bar{y}]
+    C[\bar{x} \oplus \bar{y} \oplus \bar{z}]
+    K[\bar{z}]
+  &=
+  \left(
+    \sum_{\forall \bar{x},\bar{z} \text{ s.t } \bar{x}-\bar{y}+\bar{1} \in \Dim(\shape{K}) \text{ and } \bar{z} = \bar{x}-\bar{y}+\bar{1}}
+      I[\bar{y}]
+      (1)
+      K[\bar{z}]
+  \right) + (0) \\
+  &=
+  \sum_{\forall \bar{x},\bar{z} \text{ s.t } \bar{x}-\bar{y}+\bar{1} \in \Dim(\shape{K}) \text{ and } \bar{z} = \bar{x}-\bar{y}+\bar{1}}
+    I[\bar{y}]
+    K[\bar{z}] \\
+  &=
+  \sum_{\forall \bar{x} \text{ s.t } \bar{x}-\bar{y}+\bar{1} \in \Dim(\shape{K})}
+    I[\bar{y}]
+    K[\bar{x}-\bar{y}+\bar{1}]
+\end{align*}
+\end{landscape}
 

### 2021-11-04 Math/book.tex
Backing up changes. No idea what's changed.

@@
 
+(Side note. I found an alternative definition of orthoganal in this video: \url{https://youtu.be/ACZC_XEyg9U?t=1427}
+That said $R^TR = I$ says $R$ is orthoganal because the transformation this matrix represents preserves the inner product
+between two vectors. IE, $(Ra)^T(Rb) = a^Tb$. I wonder how this relates.)
+
 And from there I think you can derive a solution to the least squares problem for multimatrices.
@@
 
+The attention mechanisms from \href{https://www.youtube.com/watch?v=yGTUuEx3GkA}{this} webseries
+translates really well into multimatrices.
+
+Let's represent the word embeddings of some sentence as $V$ where $\shape{V} = \left<d, n\right>$ where $d$ is the dimensionality of
+the embeddings and $n$ is the number of words. Then,
+
+\begin{align*}
+  W[i,j]
+  &=
+  \sum_k
+  V[k, i]
+  V[k, j] \\
+  &=
+  \sum_k
+  \transpose{V}{1}[i, k]
+  V[k, j] \\
+  &= (\transpose{V}{1} \mmult{1} V)[i,j]
+\end{align*}
+
+And
+\begin{align*}
+  W'[i,j] &= \frac{
+    W[i,j]
+  }{
+    \sum_k W[k,j]
+  } \\
+  &= 
+  \frac{
+    W[i,j]
+  }{
+   \sum_k 1^{\left<k\right>}[k] W[k,j]
+  } \\
+  &= 
+  \frac{
+    W[i,j]
+  }{
+    (1^{\left<k\right>} \mmult{1} W)[j]
+  } \\
+  &= 
+  W[i,j]
+  (1^{\left<k\right>} \mmult{1} W)^{-1}[j] \\
+  &= 
+  W \dmult{1} (1^{\left<k\right>} \mmult{1} W)^{-1} [i,j]
+\end{align*}
+
+And,
+\begin{align*}
+  Y[i,*]
+  &=
+  \sum_j W'[i,j] V[j,*] \\
+  &=
+  (W \mmult{1} V)[i,*]
+\end{align*}
+
+So our resulting formula are,
+\[ W = \transpose{V}{1} \mmult{1} V \]
+\[ W' = W \dmult{1} (1^{\left<k\right>} \mmult{1} W)^{-1} \]
+\[ Y = W' \mmult{1} V \]
+
+Or in one line,
+
+\[ Y = \transpose{V}{1} \mmult{1} V \dmult{1} (1^{\left<k\right>} \mmult{1} \transpose{V}{1} \mmult{1} V)^{-1} \mmult{1} V \]
+
+\pagebreak
+
+And in the \href{https://www.youtube.com/watch?v=tIvKXrEDMhk}{next} video we see the introduction
+of the $W_k$ key, $W_q$, query, and $W_v$ value matrices such that,
+
+\[ W = \transpose{\left(W_q \mmult{1} V\right)}{1} \mmult{1} \left(W_k \mmult{1} V\right) \]
+\[ W' = W \dmult{1} (1^{\left<k\right>} \mmult{1} W)^{-1} \]
+\[ Y = W' \mmult{1} \left(W_v \mmult{1} V \right) \]
+
+Multiheaded attention simply uses multiple layers of the attention mechanism along with some way to 
+reduce the attention down to a single layer.
+
+\[ \shape{W_k} = \shape{W_q} = \shape{W_v} = \left<h,d,d\right> \]
+\[ \shape{W} = \shape{W'} = \left<h,n,n\right> \]
+\[ \shape{Y} = \left<d,n,h\right> \]
+\[ W = \transpose{\left(W_q \mmult{1} V\right)}{2} \mmult{1} \left(W_k \mmult{1} V\right) \]
+\[ W[h,*^{\left<n,n\right>}] = \transpose{\left(W_q[h,*^{\left<d,d\right>}] \mmult{1} V\right)}{1} \mmult{1} \left(W_k[h,*^{\left<d,d\right>}] \mmult{1} V\right) \]
+\begin{align*}
+  W[\bar{h}, n_1, n_2]
+  &=
+  \sum_k
+  (W_q[\bar{h},*] \mmult{1} V)[k, n_1]
+  (W_k[\bar{h},*] \mmult{1} V)[k, n_2] \\
+  &=
+  \sum_{k}
+  (W_q \mmult{1} V)[\bar{h}, k, n_1]
+  (W_k \mmult{1} V)[\bar{h}, k, n_2] \\
+  &=
+  \sum_{k,l}
+  (W_q \mmult{1} V)[l, k, n_1]
+  (W_k \mmult{1} V)[\bar{h}, k, n_2]
+  \delta_{\bar{h},l} \\
+  &=
+  \sum_{k,l}
+  \transpose{(W_q \mmult{1} V)}{2}[n_1, l, k]
+  \transpose{(W_k \mmult{1} V)}{1}[k, n_2, \bar{h}]
+  \delta_{\bar{h},l} \\
+  &=
+  \sum_{l}
+  \left(
+    \transpose{(W_q \mmult{1} V)}{2}
+    \mmult{1}
+    \transpose{(W_k \mmult{1} V)}{1}
+  \right)[n_1, l, n_2, \bar{h}] 
+  \delta_{\bar{h},l} \\
+  &=
+  \sum_{l}
+  \transpose{\left(
+    \transpose{(W_q \mmult{1} V)}{2}
+    \mmult{1}
+    \transpose{(W_k \mmult{1} V)}{1}
+  \right)}{2}[n_2, \bar{h}, n_1, l] 
+  \delta_{l, \bar{h}} \\
+  &=
+  ?
+\end{align*}
+Ugh, this seems to require a new operation. Because what is,
+\[ C[\bar{a}] = \sum_{\forall \bar{c}} A[\bar{a} \oplus \bar{c}] B[\bar{a} \oplus \bar{c}] \]
+It's like a mix between the regular and hadamard products.
+\[ C = A \otimes B \]
+Maybe?
+
 \end{appendices}
